### 2018-07-13 tex/paper.tex
paper sketch

\documentclass[11pt,a4paper]{article}
\usepackage{color}
\usepackage{amsmath, amsthm, amssymb, amsfonts, verbatim}
\usepackage{graphicx}

\title{Assessing glymphatic transport velocities by adjoint methods}

\renewcommand{\comment}[1]{\textcolor{red}{#1}}

\author{Lars Magnus Valnes, Sebastian K. Mitusch, Geir A. Ringstad, Per Kristian Eide, Simon W. Funke, Kent-Andre Mardal }

\begin{document}
\maketitle

\begin{abstract}
\end{abstract}
\section{Introduction}

The discovery of the paravascular pathway in 2011~\cite{iliff2012paravascular} propose a novel component
crucial to the metabolism of the brain which may potientially provide an explanation for the accumulation of
waste such as amyloid beta in elderly, ultimately leading to diseases such as Alzheimer and Parkinson. 
In the rest of our body, the lymphatic system plays an important role
in the clearance of metabolic waste, but there are no lymphs within the brain. This fact is puzzling in particular because
the brain requires around 10 times more energy per volume than the result of the body. The paravascular 
pathway is proposed important to waste clearance and has therefore been named the \emph{glymphatic system}.

The pioneering works of Sykov{\'a} and Nicholson~\cite{sykova2008diffusion} demonstrated
that diffusion was a governing transport mechanism in the brain. However, 
the clearance of CSF-tracers during sleep~\cite{xie2013sleep} in mice demonstrated transportation
much faster what could be explained by diffusion and it was proposed that arterial pulsation powered
accelrated perivascular flow combined convective interstitial flow. Several modelling attempts
have put the theory to the test~\cite{asgari2016glymphatic, smith2017glymphatic, holter2017interstitial}, 
but so far computational modeling have failed to adequately described the mechanism.

Transportation by diffusion is in the order of XXX\comment{Lars: hente fra R. Thorne / Nicholson}. 
However, in \cite{xie2013sleep} a 60% coverage of 3kDa Texas Red Dextran of a $200 \mu m$ cube was demostrated in approximately 
20 minutes. As such, the transportation is XXX faster than what diffusion would provide. Furthermore, 
in \cite{eidevalnes} it was demonstrated that X Da Gadovist was brainwide in 8 hours after injection in the lumbar region.

Paragraph about timescales etc.

The purpose of this paper is to attempt to assess transportation speed in terms of an apparent diffusion coefficient 
by using adjoint methods provided by \cite{} for optimizing the coefficient with respect to data. As
such a coefficient larger than commonly reported values of diffusion would suggest that at the
timescale of minutes to hours there is indeed a glymphatic transportation which may potentially 
be responsible for metabolic waste.

An outline of the paper is as follows. In Section 2 we descibe the medical images and their modality,  
and the mathematical methodology used for determining the apparent diffusion coefficients.

\section{Methods}

\begin{itemize}
\item describe the imaging, shortly with ref to JCI  
\item describe the abstract mathematical problem to be solved, ie. PDE constrained opt problem where we 
address coefficients and bc  
\item the details: finite element, reduced problem, BFGS,  
\end{itemize}

\begin{figure}
\includegraphics[width=0.95\textwidth]{GMRI.png} 
\label{fig1} 
\caption{\comment{lars, we will need some new images since I believe this is stolen from JCI}}
\end{figure}

\comment{Lars: bilde av konkret mesh }

\section{Results}
\begin{itemize}
\item 2D experiments as have already been done (with and without noise/ with and without observations everywhere in time) 
\item 2D experiments should highlight the impact of the regularization parameter wrt number of iterations and diffusion 
coeff 
\item 3D experiments based on data generated  
\item 3D experiments based on real data (\comment{lars: we need to try testing this}) 
\end{itemize}

\section{Discussion}

\bibliographystyle{amsplain}
\bibliography{references}

\end{document}

### 2018-09-05 forward_problem.py
some updates

@@ -9,11 +9,11 @@ def initialize_mesh(mesh_file): # Lars : Endret
     mesh = Mesh()
 
     hdf = HDF5File(mesh.mpi_comm(), "mesh_invers_contrast.h5", "r")
-    hdf.read(mesh, "/mesh", False)  
-    subdomains = CellFunction("size_t", mesh)
-    hdf.read(subdomains, "/subdomains")
-    boundaries = FacetFunction("size_t", mesh)
-    hdf.read(boundaries, "/boundaries")
+    hdf.read(mesh, "/mesh", False, annotate=False)
+    subdomains = MeshFunction("size_t", mesh, mesh.topology().dim())
+    hdf.read(subdomains, "/subdomains", annotate=False)
+    boundaries = MeshFunction("size_t", mesh, mesh.topology().dim() - 1)
+    hdf.read(boundaries, "/boundaries", annotate=False)
     # Define measures with subdomains
     dx = Measure("dx", domain=mesh, subdomain_data=subdomains)
     ds = Measure("ds", domain=mesh, subdomain_data=boundaries)
@@ -212,9 +212,9 @@ def functional(mesh_config, V, D, g_list, tau, obs_file, alpha=0.0, beta=0.0, gr
                 weight = 1.0
 
             # Add regularisation
-            self.J += 1 / 2 * weight * self.dt * assemble(self.g ** 2 * self.ds(1)) * self.alpha
+            self.J += 1 / 2 * weight * self.dt * assemble(self.g ** 2 * self.ds(1) + grad(self.g) ** 2 * self.ds(1)) * self.alpha
             if self.current_g_index > 1:
-                g_prev = self.g_list[self.current_g_index - 1]
+                g_prev = self.g_list[self.current_g_index - 2]
                 self.J += 1 / 2 * weight * self.dt * assemble(((self.g - g_prev) / self.dt) ** 2 * self.ds(1)) * self.beta
 
         def next_bc(self):
@@ -282,18 +282,19 @@ def save_control_values(m, results_folder_save):
         myfile.close()
 
 
-def load_control_values(k, results_folder_load):
+def load_control_values(k, V, results_folder_load):
     m = []
     myfile = open("results/{}/opt_consts.txt".format(results_folder_load), "r")
     lines = myfile.readlines()
     for i in lines:
         m.append(Constant(float(i)))
     myfile.close()
+    l = len(m)
 
[…]

### 2018-09-05 main.py

@@ -17,10 +17,50 @@ def initial_condition(V, mesh_config):
     return interpolate(init, V)
 
 
-def bc(g):
-    for g_i in g:
-        g_i.vector()[:] = 1
+def bc(g, V):
+    l = len(g)
+    for i in range(l):
+        #p = (i + 1)/float(l)
+        #if i > l/2:
+        #    p = (l - i + 1)/l
+        #expr = Expression("sin(x[0])*sin(x[0])*cos(x[1])*cos(x[1])*sin(pi*i)", i=i/float(l), degree=1)
+        #k = interpolate(expr, V)
+        g_i = g[i]
+        #g_i.vector()[:] = k.vector()
+        if i < l/2:
+            g_i.vector()[:] = i
+        else:
+            g_i.vector()[:] = l - i
     return g
+
+
+def bc_guess(g, obs_file, tau, k):
+    d = Function(g[0].function_space())
+    dt = tau[-1]/k
+    obs_file = HDF5File(mpi_comm_world(), obs_file, 'r')
+    next_tau = 0
+    t = 0.0
+    for i in range(k):
+        t += dt
+        obs_file.read(d, str(tau[next_tau]))
+        g[i].vector()[:] = d.vector()[:]
+
+        if abs(t - tau[next_tau]) < abs(t + dt - tau[next_tau]):
+            next_tau += 1
+    return g
+
+
+iter_cnt = 0
+def iter_cb(m):
+    global iter_cnt
+    iter_cnt += 1
+    print("Coeffs-Iter: {} | Constant({}) | Constant({}) | Constant({})".format(iter_cnt, float(m[0]), float(m[1]), float(m[2])))
+    from pyadjoint.reduced_functional_numpy import ReducedFunctionalNumPy
+    NumRF = ReducedFunctionalNumPy(Jhat)
+    ds = mesh_config["ds"]
+    fenics_m = NumRF.set_local([control.copy_data() for control in Jhat.controls], m)
+    print("DirichletBC-Iter: {} | {}".format(iter_cnt, sum([assemble((fenics_m[i] - correct_g[i-2])**2*ds(1)) for i in range(3, len(fenics_m))])/sum([assemble(correct_g[i-2]**2*ds(1)) for i in range(3, len(fenics_m)) ]) ))
+
 
 if __name__ == "__main__":
     from forward_problem import initialize_mesh, load_control_values, save_control_values, generate_observations, functional, gradient
@@ -40,6 +80,7 @@ if __name__ == "__main__":
[…]

### 2018-09-05 tex/paper.tex

@@
 
+The model considers multiple domains.
+
+The sub-domains
+
+The observations are taken form
+
+\subsection*{Data}
+
+\subsection*{Mathematical Model}
+The objective function was defined as 
+\begin{equation}
+\min_{u,g} F = \quad \sum\limits_i\sp{n} \int\limits_{\Omega} |u(t_i) - u_{obs}(t_i)| \mathrm{d}\Omega + \frac{\alpha}{2} \int\limits_{0}\sp{T} || g ||_{L\sp{2}(\partial\Omega)} \mathrm{d}t + \frac{\beta}{2} \int\limits_{0}\sp{T} || \dot{g} ||_{L\sp{2}(\partial\Omega)}\mathrm{d}t
+\end{equation}
+subjugated by   
+\begin{equation}
+\begin{aligned}
+\frac{\partial u}{\partial t} = \nabla \cdot  D_i \nabla u \qquad \text{in} \qquad \Omega \times \left\lbrace 0 , T \right)  \\
+u=g(t) \qquad \text{on} \qquad \partial\Omega  \times \left\lbrace 0 , T \right) 
+\end{aligned}
+\label{Eq::PDE}
+\end{equation}
+with the domain $\Omega$ contains three sub domains, each with a different diffusion coefficient.
+We denote the csf domain as $\Omega_1$, the grey matter as $\Omega_2$ and the white matter as $\Omega_3$.
+
+Thus the determination of noise sensitivity was conducted by adding noise to the manufactured solution.
+The manufactured solution was obtained by forward computation of Eq.\ref{Eq::PDE} with following Dirichlet boundary condition
+\begin{equation}
+g(t)_{\partial \Omega_1} = 0.3 + 0.01t  \qquad  0 \leq t \leq 110.0.
+\end{equation}
+and diffusion coefficients 
+\begin{equation}
+D_c = 1000 
+\end{equation}
+
+The finite element
+
+Dolfin adjoint was used to construct a reduced function,
+
+The scipy optimize library was used, and minimize algorithm used L-BFGS-S.
+
 \begin{itemize}
@@
 
+The L-BFGS-B algorithm does not scale the control parameters, thus the step size . This poses a problem with a large difference in the control parameters,
+
 \bibliographystyle{amsplain}

### 2018-09-05 main.py
small bugfix in iteration callback

@@ -59,7 +59,7 @@ def iter_cb(m):
     NumRF = ReducedFunctionalNumPy(Jhat)
     ds = mesh_config["ds"]
     fenics_m = NumRF.set_local([control.copy_data() for control in Jhat.controls], m)
-    print("DirichletBC-Iter: {} | {}".format(iter_cnt, sum([assemble((fenics_m[i] - correct_g[i-2])**2*ds(1)) for i in range(3, len(fenics_m))])/sum([assemble(correct_g[i-2]**2*ds(1)) for i in range(3, len(fenics_m)) ]) ))
+    print("DirichletBC-Iter: {} | {}".format(iter_cnt, sum([assemble((fenics_m[i] - correct_g[i-3])**2*ds(1)) for i in range(3, len(fenics_m))])/sum([assemble(correct_g[i-3]**2*ds(1)) for i in range(3, len(fenics_m)) ]) ))
 
 
 if __name__ == "__main__":

### 2018-09-05 forward_problem.py
Changes

@@ -1,3 +1,4 @@
+# -*- coding: utf-8 -*-
 from dolfin import *
 from fenics_adjoint import *
 
@@ -242,22 +243,25 @@ def generate_observations(mesh_config, V, D, g_list, ic, tau, output_file):
             self.obs_file = HDF5File(mpi_comm_world(), obs_file, 'w')
             self.dt = tau[-1]/float(len(g_list))
             self.ic = ic
-            self.obs_file.write(ic, "0")
+            self.obs_file.write(ic, "0.0")
+            #self.pvd = File("sol.pvd") 
+            self.Exp = Expression("A+B*t-C*t*t", A=0.3, B=0.167,C=0.007 , t=0.0 , degree=1)
+
 
         def should_stop(self):
-            return not self.next_tau < len(self.tau)
+            return not self.t < self.tau[-1]
 
         def advance_time(self):
             self.t += self.dt
+            self.Exp.t = self.t
+            self.g_list[self.current_g_index].interpolate(self.Exp)
             self.g = self.g_list[self.current_g_index]
             self.current_g_index += 1
 
-        def handle_solution(self, U):
-            if abs(self.t - self.tau[self.next_tau]) < abs(self.t + self.dt - self.tau[self.next_tau]): # Enklere ? 
-                self.obs_file.write(U, str(self.tau[self.next_tau]))  # Write observation
-                # Move on to next observation
-                self.next_tau += 1
 
+        def handle_solution(self, U):
+            self.obs_file.write(U, str(self.t) ) # Write observation
+            #self.pvd << (U,self.t)
         def next_bc(self):
             return DirichletBC(self.V, self.g, self.boundaries, 1)
 

### 2018-09-05 main.py

@@ -82,7 +82,7 @@ if __name__ == "__main__":
     parser.add_argument("--generate-observations", default=False, type=bool)
     parser.add_argument("--maxiter", default=50, type=int)
     Z = parser.parse_args()
-
+    print Z
     mesh_config = initialize_mesh(Z.mesh)
 
     V = FunctionSpace(mesh_config["mesh"], "CG", 1)

### 2018-09-05 forward_problem.py
read first timestep

@@ -180,7 +180,7 @@ def functional(mesh_config, V, D, g_list, tau, obs_file, alpha=0.0, beta=0.0, gr
             self.obs_file = HDF5File(mpi_comm_world(), obs_file, 'r')
             self.t = tau[0]
             self.dt =( tau[-1] - tau[0] )/float(len(g_list)) # Lars : Endring for en mer generalisert metode (tau[0] = 0 )
-            self.obs_file.read(self.ic, "0")
+            self.obs_file.read(self.ic, str(self.t) )
             self.gradient = [1.0, 1.0, 1.0]
 
         def scale(self, i):

### 2018-09-05 forward_problem.py
Observation times to the first desimal

@@ -260,7 +260,7 @@ def generate_observations(mesh_config, V, D, g_list, ic, tau, output_file):
 
 
         def handle_solution(self, U):
-            self.obs_file.write(U, str(self.t) ) # Write observation
+            self.obs_file.write(U, "%0.1f"%self.t ) # Write observation
             #self.pvd << (U,self.t)
         def next_bc(self):
             return DirichletBC(self.V, self.g, self.boundaries, 1)

### 2018-09-07 forward_problem.py
Updates

@@ -189,11 +189,11 @@ def functional(mesh_config, V, D, g_list, tau, obs_file, alpha=0.0, beta=0.0, gr
             return 1.0
 
         def should_stop(self):
-            return not self.next_tau < len(self.tau)
+            return not self.next_tau <= len(self.tau)
 
         def advance_time(self):
             self.t += self.dt
-            self.obs_file.read(self.g_list[self.current_g_index], str(self.tau[self.next_tau])) # Lars Next guess ?
+            self.obs_file.read(self.g_list[self.current_g_index], str(self.tau[self.next_tau])) 
             self.g = self.g_list[self.current_g_index]
             self.current_g_index += 1
 
@@ -215,10 +215,10 @@ def functional(mesh_config, V, D, g_list, tau, obs_file, alpha=0.0, beta=0.0, gr
                 weight = 1.0
 
             # Add regularisation
-            self.J += 1 / 2 * weight * self.dt * assemble(self.g ** 2 * self.ds(1) + grad(self.g) ** 2 * self.ds(1)) * self.alpha
+            self.J += 1 / 2 * weight * self.dt * assemble(self.g ** 2 * self.ds(1) + grad(self.g) ** 2 * self.ds) * self.alpha
             if self.current_g_index > 1:
                 g_prev = self.g_list[self.current_g_index - 2]
-                self.J += 1 / 2 * weight * self.dt * assemble(((self.g - g_prev) / self.dt) ** 2 * self.ds(1)) * self.beta
+                self.J += 1 / 2 * weight * self.dt * assemble(((self.g - g_prev) / self.dt) ** 2 * self.ds) * self.beta
 
         def next_bc(self):           
             return DirichletBC(self.V, self.g, self.boundaries, 1)
@@ -241,26 +241,27 @@ def generate_observations(mesh_config, V, D, g_list, ic, tau, output_file):
             self.current_g_index = 0
             self.J = 0.0
             self.obs_file = HDF5File(mpi_comm_world(), obs_file, 'w')
-            self.dt = tau[-1]/float(len(g_list))
+            self.dt = (tau[-1]-tau[0])/float(len(g_list))
             self.ic = ic
             self.obs_file.write(ic, "0.0")
             #self.pvd = File("sol.pvd") 
-            self.Exp = Expression("A+B*t-C*t*t", A=0.3, B=0.167,C=0.007 , t=0.0 , degree=1)
[…]

### 2018-09-07 main.py

@@ -17,20 +17,16 @@ def initial_condition(V, mesh_config):
     return interpolate(init, V)
 
 
-def bc(g, V):
-    l = len(g)
-    for i in range(l):
-        #p = (i + 1)/float(l)
-        #if i > l/2:
-        #    p = (l - i + 1)/l
-        #expr = Expression("sin(x[0])*sin(x[0])*cos(x[1])*cos(x[1])*sin(pi*i)", i=i/float(l), degree=1)
-        #k = interpolate(expr, V)
-        g_i = g[i]
-        #g_i.vector()[:] = k.vector()
-        if i < l/2:
-            g_i.vector()[:] = i
-        else:
-            g_i.vector()[:] = l - i
+def bc(g, V,tau,k, mesh_config):
+    t = tau[0]
+    dt = (tau[-1]-tau[0])/k
+    Exp = Expression("A+B*t-C*t*t", A=0.3, B=0.167,C=0.007 , t=0.0 , degree=1)
+    for i in range(k):
+        Exp.t= t
+        bc = DirichletBC(V, Exp, mesh_config["boundaries"], 1)
+        bc.apply(g[i].vector())
+        t+=dt
+        
     return g
 
 
@@ -57,9 +53,10 @@ def iter_cb(m):
     print("Coeffs-Iter: {} | Constant({}) | Constant({}) | Constant({})".format(iter_cnt, float(m[0]), float(m[1]), float(m[2])))
     from pyadjoint.reduced_functional_numpy import ReducedFunctionalNumPy
     NumRF = ReducedFunctionalNumPy(Jhat)
+    print("Functional-value: {} | {} ".format(iter_cnt,Jhat.functional) )
     ds = mesh_config["ds"]
     fenics_m = NumRF.set_local([control.copy_data() for control in Jhat.controls], m)
-    print("DirichletBC-Iter: {} | {}".format(iter_cnt, sum([assemble((fenics_m[i] - correct_g[i-3])**2*ds(1)) for i in range(3, len(fenics_m))])/sum([assemble(correct_g[i-3]**2*ds(1)) for i in range(3, len(fenics_m)) ]) ))
+    print("DirichletBC-Iter: {} | {}".format(iter_cnt, sum([assemble((fenics_m[i] - correct_g[i-3])**2*ds) for i in range(3, len(fenics_m))])/sum([assemble(correct_g[i-3]**2*ds) for i in range(3, len(fenics_m)) ]) ))
[…]

### 2018-09-07 inverse3D-abel.sh
Updates

@@ -22,19 +22,21 @@
 ## Set up job environment
 source /cluster/bin/jobsetup
 
-source ~johannr/pyadjoint-brain-inversion-mod-fenics-2017.1.0.abel.gnu.conf
+source ~larsmva/pyadjoint-brain-inversion-mod-fenics-2017.2.abel.intel.conf
 
 # Define what to do when job is finished (or crashes)
-cleanup "mkdir -p $HOME/results"
-cleanup "cp -r $SCRATCH/Res* $HOME/results" 
-cleanup "cp -r $SCRATCH/U.xdmf  $HOME/ECCM"
+cleanup "mkdir -p $HOME/Results"
+cleanup "cp -r $SCRATCH/slurm* $PWD" 
+echo $PWD
 echo "SCRATCH is $SCRATCH"
 
 # Copy necessary files to $SCRATCH
 cp mesh_invers_contrast.h5 forward_problem.py main.py U.xdmf $SCRATCH
 
+echo "${@:4}"
 cd $SCRATCH
 ls
 echo $SCRATCH
-mpirun --bind-to none python main.py --alpha=$1 --beta=$2 --noise=$3 --num=$4 --tol=$5
+mpirun --bind-to none python3 main.py --alpha $1 --beta $2 --noise $3 --num $4 --tol "${@:4}"
+
 

### 2018-09-07 inverse3D-abel.sh
correct arguments

@@ -26,7 +26,7 @@ source ~larsmva/pyadjoint-brain-inversion-mod-fenics-2017.2.abel.intel.conf
 
 # Define what to do when job is finished (or crashes)
 cleanup "mkdir -p $HOME/Results"
-cleanup "cp -r $SCRATCH/slurm* $PWD" 
+cleanup "cp -r $SCRATCH/slurm* $HOME" 
 echo $PWD
 echo "SCRATCH is $SCRATCH"
 
@@ -37,6 +37,6 @@ echo "${@:4}"
 cd $SCRATCH
 ls
 echo $SCRATCH
-mpirun --bind-to none python3 main.py --alpha $1 --beta $2 --noise $3 --num $4 --tol "${@:4}"
+mpirun --bind-to none python3 main.py --alpha $1 --beta $2 --noise $3 --k $4 --tau "${@:4}"
 
 

### 2018-09-07 inverse3D-abel.sh
Updates

@@ -37,6 +37,6 @@ echo "${@:4}"
 cd $SCRATCH
 ls
 echo $SCRATCH
-mpirun --bind-to none python3 main.py --alpha $1 --beta $2 --noise $3 --k $4 --tau "${@:4}"
+mpirun --bind-to none python3 main.py --alpha $1 --beta $2 --noise $3 --k $4 --tau "${@:5}"
 
 

### 2018-09-07 forward_problem.py
Updates

@@ -200,7 +200,7 @@ def functional(mesh_config, V, D, g_list, tau, obs_file, alpha=0.0, beta=0.0, gr
         def handle_solution(self, U):
             if abs(self.t - self.tau[self.next_tau]) < abs(self.t + self.dt - self.tau[self.next_tau]): #Lars :  Enklere ? 
                 # If t is closest to next observation then compute misfit.
-                self.obs_file.read(self.d, str(self.tau[self.next_tau]))  # Read observation
+                self.obs_file.read(self.d, "%0.2f"%(self.tau[self.next_tau]))  # Read observation
                 self.J += assemble((U - self.d) ** 2 * self.dx)
 
                 # Move on to next observation

### 2018-09-07 main.py
Update

@@ -38,7 +38,7 @@ def bc_guess(g, obs_file, tau, k):
     t = 0.0
     for i in range(k):
         t += dt
-        obs_file.read(d, str(tau[next_tau]))
+        obs_file.read(d,"%0.2f"%(tau[next_tau]))
         g[i].vector()[:] = d.vector()[:]
 
         if abs(t - tau[next_tau]) < abs(t + dt - tau[next_tau]):

### 2018-09-07 forward_problem.py
Update

@@ -180,7 +180,7 @@ def functional(mesh_config, V, D, g_list, tau, obs_file, alpha=0.0, beta=0.0, gr
             self.obs_file = HDF5File(mpi_comm_world(), obs_file, 'r')
             self.t = tau[0]
             self.dt =( tau[-1] - tau[0] )/float(len(g_list)) # Lars : Endring for en mer generalisert metode (tau[0] = 0 )
-            self.obs_file.read(self.ic, str(self.t) )
+            self.obs_file.read(self.ic, "0.2%f"%(self.t) )
             self.gradient = [1.0, 1.0, 1.0]
 
         def scale(self, i):

### 2018-09-07 forward_problem.py
Resolved error of loading observations

@@ -180,7 +180,7 @@ def functional(mesh_config, V, D, g_list, tau, obs_file, alpha=0.0, beta=0.0, gr
             self.obs_file = HDF5File(mpi_comm_world(), obs_file, 'r')
             self.t = tau[0]
             self.dt =( tau[-1] - tau[0] )/float(len(g_list)) # Lars : Endring for en mer generalisert metode (tau[0] = 0 )
-            self.obs_file.read(self.ic, "0.2%f"%(self.t) )
+            self.obs_file.read(self.ic, "%0.2f"%(self.t) )
             self.gradient = [1.0, 1.0, 1.0]
 
         def scale(self, i):
@@ -189,11 +189,11 @@ def functional(mesh_config, V, D, g_list, tau, obs_file, alpha=0.0, beta=0.0, gr
             return 1.0
 
         def should_stop(self):
-            return not self.next_tau <= len(self.tau)
+            return not self.next_tau < len(self.tau) -self.dt/2
 
         def advance_time(self):
             self.t += self.dt
-            self.obs_file.read(self.g_list[self.current_g_index], str(self.tau[self.next_tau])) 
+            self.obs_file.read(self.g_list[self.current_g_index], "%0.2f"%(self.tau[self.next_tau])) 
             self.g = self.g_list[self.current_g_index]
             self.current_g_index += 1
 

### 2018-09-13 inverse3D-abel.sh
sbatch file

@@ -22,7 +22,14 @@
 ## Set up job environment
 source /cluster/bin/jobsetup
 
+#source ~johannr/pyadjoint-brain-inversion-mod-fenics-2017.1.0.abel.gnu.conf
+#source ~johannr/pyadjoint-brain-inversion-mod-fenics-2017.1.0.abel.gnu.conf
+#source ~larsmva/pyadjoint-brain-inversion-mod-fenics-2017.2.abel.intel.conf
+
 source ~larsmva/pyadjoint-brain-inversion-mod-fenics-2017.2.abel.intel.conf
+
+
+#source  ~johannr/pyadjoint-2018.03.19-fenics-2017.1.0.abel.gnu.conf
 
 # Define what to do when job is finished (or crashes)
 cleanup "mkdir -p $HOME/Results"

### 2018-09-15 forward_problem.py
update

@@ -48,7 +48,7 @@ def forward_problem(context):
     bc = DirichletBC(V, 0, context.boundaries, 1)
     bc.apply(A)
     # Define solver. Use GMRES iterative method with AMG preconditioner.
-    solver = LinearSolver(mpi_comm_self(), *context.linear_solver_args)
+    solver = LinearSolver(mpi_comm_self(), "gmres")
     solver.set_operator(A)
 
     while not context.should_stop():
@@ -60,9 +60,9 @@ def forward_problem(context):
         b = assemble(L)
         A.bcs = [bc]
         bc.apply(b)
-
+    
         # Solve linear system for this timestep
-        solver.solve(U.vector(), b,annotate =True)
+        solver.solve(U.vector(), b)
 
         context.handle_solution(U)
          
@@ -103,74 +103,6 @@ class Context(object):
     def return_value(self):
         return None
 
-
-def gradient(mesh_config, V, D, g_list, tau, obs_file, alpha=0.0, beta=0.0):
-    class GradientContext(Context):
-        def __init__(self, mesh_config, V, D, g_list, tau, obs_file, alpha=0.0, beta=0.0):
-            super(GradientContext, self).__init__(mesh_config, V, D, g_list)
-            self.tau = tau
-            self.next_tau = 0
-            self.g = None
-            self.current_g_index = 0
-            self.J = 0.0
-            self.d = Function(self.V)
-            self.alpha = alpha
-            self.beta = beta
-            self.obs_file = HDF5File(mpi_comm_world(), obs_file, 'r')
-            self.dt = tau[-1]/float(len(g_list))
-            self.obs_file.read(self.ic, "0")
-
-
-
-        def should_stop(self):
-            return not self.next_tau < len(self.tau)
-
-        def advance_time(self):
-            self.t += self.dt
-            self.g = self.g_list[self.current_g_index]
-            self.current_g_index += 1
-
-        def handle_solution(self, U):
-            if abs(self.t - self.tau[self.next_tau]) < abs(self.t + self.dt - self.tau[self.next_tau]): # Lars : Enklere?
-                # If t is closest to next observation then compute misfit.
-                self.obs_file.read(self.d, str(self.tau[self.next_tau]))  # Read observation
-                self.J += assemble((U - self.d) ** 2 * self.dx)
-
-                # Move on to next observation
-                self.next_tau += 1
-
[…]

### 2018-09-15 main.py

@@ -34,7 +34,7 @@ def bc_guess(g, obs_file, tau, k):
     d = Function(g[0].function_space())
     dt = (tau[-1] -tau[0])/k
     obs_file = HDF5File(mpi_comm_world(), obs_file, 'r')
-    next_tau = 0
+    next_tau = 1
     t = tau[0]
     for i in range(k):
         t += dt
@@ -60,16 +60,17 @@ def iter_cb(m):
 
 
 if __name__ == "__main__":
-    from forward_problem import initialize_mesh, load_control_values, save_control_values, generate_observations, functional, gradient
+    from forward_problem import initialize_mesh, load_control_values, save_control_values, generate_observations, functional
     import argparse
-
+    import sys 
+    print( sys.version )
     parser = argparse.ArgumentParser()
     parser.add_argument('--alpha', default=0.0001, type=float)
     parser.add_argument('--num', default=0, type=int)
     parser.add_argument('--beta', default=0.001, type=float)
     parser.add_argument('--noise', default=0.0, type=float)
     parser.add_argument('--tol', default=0.001, type=float)
-    parser.add_argument('--D', default=[1000, 2, 1], type=float, nargs=3)
+    parser.add_argument('--D', default=[1000, 1, 1], type=float, nargs=3)
     parser.add_argument('--mesh', default="mesh_invers_contrast.h5", type=str)
     parser.add_argument("--tau", nargs="+", type=float)
     parser.add_argument("--k", type=int)
@@ -77,7 +78,7 @@ if __name__ == "__main__":
     parser.add_argument("--load-control-values-file", default=None, type=str)
     parser.add_argument("--save-control-values-file", default=None, type=str)
     parser.add_argument("--generate-observations", default=False, type=bool)
-    parser.add_argument("--maxiter", default=200, type=int)
+    parser.add_argument("--maxiter", default=1000, type=int)
     parser.add_argument("--dx", default=0.0, type=float)
     Z = parser.parse_args()
     print(Z)
@@ -110,6 +111,7 @@ if __name__ == "__main__":
     else:
         g = bc_guess(g, Z.obs_file, tau, k)
 
+
         J = functional(mesh_config, V, D, g, tau, Z.obs_file, Z.alpha, Z.beta, None)
 
[…]

### 2018-09-15 tex/paper.tex
text update

@@
 
-The model considers multiple domains.
-
-The sub-domains
-
-The observations are taken form
-
 \subsection*{Data}
@@
 with the domain $\Omega$ contains three sub domains, each with a different diffusion coefficient.
-We denote the csf domain as $\Omega_1$, the grey matter as $\Omega_2$ and the white matter as $\Omega_3$.
+We denote the Cerebral Spinal fluid (CSF) domain as $\Omega_1$, the grey matter as $\Omega_2$ and the white matter as $\Omega_3$.
 
-Thus the determination of noise sensitivity was conducted by adding noise to the manufactured solution.
-The manufactured solution was obtained by forward computation of Eq.\ref{Eq::PDE} with following Dirichlet boundary condition
+The manufactured observations was obtained by forward computation of Eq.\ref{Eq::PDE} with the Dirichlet boundary condition defined as
 \begin{equation}
-g(t)_{\partial \Omega_1} = 0.3 + 0.01t  \qquad  0 \leq t \leq 110.0.
+g(t)_{\partial \Omega_1} = 0.3 +0.167t - 0.007t\sp{2} \qquad  0 \leq t \leq 24.
 \end{equation}
-and diffusion coefficients 
+The timestep was $dt = 0.02$, and the diffusion coefficients were selected to be 
 \begin{equation}
-D_c = 1000 
+D_{\Omega_1} = 1000 \quad , \quad D_{\Omega_2} = 4.0 \quad , \quad D_{\Omega_3} = 8.0 
 \end{equation}  
+The magnitude order of the diffusion coefficient are chosen so that they resemble diffusion coefficient in csf, grey and white matter.
+The forward simulation gave a total of 120 possible observation time points.
+These points will be denoted as $\tau$.
 
-The finite element
+The mesh was constructed by using the MRI of a patient diagnosed with iNPH.
+The software Freesurfer was used in segmentation and creating the polyhedral surfaces of the white and grey matter.
+Then the use of T2 weighted MRI was used to segment the csf compartment surrounding the cerebral.
+The polyhedral surfaces was use of CGAL [?], was used to construed the the mesh.
+The computational requirement for the resulting mesh was significant, therefore a submesh was also constructed, see Fig.
+??
+.
 
-Dolfin adjoint was used to construct a reduced function,
+P1 finite elements were used, and the dolfin adjoint [?] was used to construct a reduced function. Furthermore, the scipy optimize library was used to minimize the functional using L-BFGS-B algorithm.
 
-The scipy optimize library was used, and minimize algorithm used L-BFGS-S.
+\section*{Non-linear relation}
+The MR images that are provided by Oslo University Hospital Rikshospitalet and can be seen in Fig.?? .
+
+The software Freesurfer was used to segment and align each of the observations, which made it possible to estimate voxelwise intensity increase due to tracer concentrations.
+
+The relation between intensity and concentration is non-linear, and best be de
 
@@
 
+\begin{figure}
+\includegraphics[width=0.3\textwidth]{mesh-eps-converted-to.pdf} 
+\label{fig1} 
+\caption{\comment{lars, we will need some new images since I believe this is stolen from JCI}}
+\end{figure}
+
 \section{Results}
@@
 
+The results.
+
+The optimal relaxation parameters was investigated by using 10 evenly spaced time points as observations. Then estimate the corresponding controls, while varying the relaxation parameters.
+
+The dependency on the spacing and distribution of $tau$ was done by using the optimal relaxation parameters and consider number of time points equal to the number of observations.
+
+The dependency of time steps were computed by increasing the times
+
+The dependency on noise was done by adding randomly distributed noise to the observations.
+
+There are some extreme cases that require some considerations, namely :
+
+no observations around 12, i.e. can the parameters be estimated if there exists a hole in the observations.
+
+Is estimating parameters between 2
+\begin{table}
+\centering
+\caption{ }
+\resizebox{\textwidth}{!}{\begin{tabular}{*{8}c}
+$\alpha$ & $\beta$ & k & $\tau$ & iter & $ D_{\Omega_1} = 1000$ & $ D_{\Omega_2} = 4.0 $ & $D_{\Omega_3} = 8.0 $ \\
+\hline
+ 1.0 & 1.0 &10 &10 & 801& 3152.55150305 & 5.66843317507 & 9.10176601537 \\
+ 1.0 & 0.1 &10 &10 & 846& 2890.10652122 & 5.8333990243 & 9.14516904881   \\
+ 1.0 & 0.01 &10 &10 & 1001& 2374.75510786 & 5.90748588887 & 9.1624514977  \\ 
+ 1.0 & 0.001 &10 &10 & 987& 3012.94145621 & 5.84828588848 & 9.14780994071 \\
+ 1.0 & 0.0001 &10 &10 & 1001& 2846.67368004 & 5.86716070687 & 9.1516059019 \\
+ 1.0 & 1e-05 &10 &10 & 1001& 2488.99687704 & 5.89553108585 & 9.16094907807 \\
+ 1.0 & 1e-06 &10 &10 & 1001& 2572.74685463 & 5.88550285289 & 9.15701445733 \\
+ 0.1 & 1.0 &10 &10 & 525& 1165.00025805 & 4.55541673123 & 8.51469574502 \\
+ 0.1 & 0.1 &10 &10 & 899& 1098.5603179 & 4.5965351918 & 8.60353462124 \\
+ 0.1 & 0.01 &10 &10 & 792& 1148.68286947 & 4.58961131725 & 8.60923608344 \\ 
+ 0.1 & 0.001 &10 &10 & 768& 1133.11485657 & 4.59512891707 & 8.61427396989 \\
+ 0.1 & 0.0001 &10 &10 & 840& 1152.61459776 & 4.5895138786 & 8.61107565287 \\
+ 0.1 & 1e-05 &10 &10 & 739& 1145.12699776 & 4.59168203791 & 8.61245925367 \\
+ 0.1 & 1e-06 &10 &10 & 697& 1127.51137739 & 4.59724924241 & 8.6163255093 \\
+ 0.01 & 1.0 &10 &10 & 130& 1000.69417631 & 4.45194182806 & 8.48016213899 \\
+ 0.01 & 0.1 &10 &10 & 204& 1001.45906364 & 4.44288397852 & 8.55964437402 \\
+ 0.01 & 0.01 &10 &10 & 384& 1004.91771072 & 4.44039285507 & 8.57773362809 \\
+ 0.01 & 0.001 &10 &10 & 455& 1006.92821746 & 4.4401364227 & 8.57964644068 \\
+ 0.01 & 0.0001 &10 &10 & 382& 1005.46132856 & 4.44059403278 & 8.58161935877 \\
+ 0.01 & 1e-05 &10 &10 & 389& 1005.48872458 & 4.44091328174 & 8.58070451064 \\
+ 0.01 & 1e-06 &10 &10 & 320& 1003.88180045 & 4.44140148563 & 8.57914151398 \\
+ 0.001 & 1.0 &10 &10 & 144& 1000.72690068 & 4.43617090765 & 8.47356658247 \\
+ 0.001 & 0.1 &10 &10 & 188& 1001.11632883 & 4.42560354452 & 8.55339645884 \\
+ 0.001 & 0.01 &10 &10 & 242& 1002.06937059 & 4.42388003439 & 8.57511846108 \\
+ 0.001 & 0.001 &10 &10 & 332& 1005.24945351 & 4.42278572482 & 8.58013052115 \\
+ 0.001 & 0.0001 &10 &10 & 432& 1008.05660576 & 4.42186842634 & 8.58305135552 \\
+ 0.001 & 1e-05 &10 &10 & 360& 1006.05061062 & 4.42295196846 & 8.57964172911 \\
+ 0.001 & 1e-06 &10 &10 & 363& 1006.70468432 & 4.42251369108 & 8.58151348789 \\
+ 0.0001 & 1.0 &10 &10 & 157& 1000.83218743 & 4.43452507573 & 8.47318916943 \\
+ 0.0001 & 0.1 &10 &10 & 131& 1000.56624899 & 4.42351929725 & 8.55256760219 \\
+ 0.0001 & 0.01 &10 &10 & 174& 1001.0091989 & 4.42260942583 & 8.57478259945 \\
+ 0.0001 & 0.001 &10 &10 & 136& 1000.57577092 & 4.4239534819 & 8.57151355191 \\
+ 0.0001 & 0.0001 &10 &10 & 283& 1003.03255695 & 4.42248562737 & 8.5786695754 \\
+ 0.0001 & 1e-05 &10 &10 & 284& 1003.54402535 & 4.42227734882 & 8.58311915306 \\
+ 0.0001 & 1e-06 &10 &10 & 289& 1003.03642353 & 4.42224580212 & 8.58006825258 \\
+ 1e-05 & 1.0 &10 &10 & 151& 1000.79310038 & 4.43448500449 & 8.47338153139 \\
+ 1e-05 & 0.1 &10 &10 & 140& 1000.70858373 & 4.42340629909 & 8.55312689863 \\
+ 1e-05 & 0.01 &10 &10 & 203& 1001.34714912 & 4.42253540005 & 8.57470943099 \\
+ 1e-05 & 0.001 &10 &10 & 215& 1001.75591211 & 4.42292580709 & 8.58079455564 \\
+ 1e-05 & 0.0001 &10 &10 & 208& 1001.41103854 & 4.42264942624 & 8.58064686718 \\
+ 1e-05 & 1e-05 &10 &10 & 218& 1001.73103534 & 4.42318548221 & 8.57843152546 \\
+ 1e-05 & 1e-06 &10 &10 & 191& 1001.33680306 & 4.42244263068 & 8.58128891831 \\
+ 1e-06 & 1.0 &10 &10 & 115& 1000.47868283 & 4.43456295486 & 8.47226911091 \\
+ 1e-06 & 0.1 &10 &10 & 158& 1000.8203239 & 4.42368702618 & 8.55236552474 \\
+ 1e-06 & 0.01 &10 &10 & 142& 1000.64224198 & 4.42327990324 & 8.57047799569 \\
+ 1e-06 & 0.001 &10 &10 & 149& 1000.64956243 & 4.42317461499 & 8.57554522252 \\
+ 1e-06 & 0.0001 &10 &10 & 179& 1001.07075407 & 4.42262619987 & 8.57788936678 \\
+ 1e-06 & 1e-05 &10 &10 & 254& 1002.49656481 & 4.42254606227 & 8.58162265954 \\
+ 1e-06 & 1e-06 &10 &10 & 228& 1001.78781526 & 4.42297193581 & 8.57946804203 \\
+\end{tabular}}
+\label{Tab::1}
+\end{table}
+
 \section{Discussion}
@@
 The L-BFGS-B algorithm does not scale the control parameters, thus the step size . This poses a problem with a large difference in the control parameters,
+
+There is a need for observable change in order to estimate the parameters.
+But considering the magnitude difference between diffusion coefficients.
+It is clear that the observable change is in different timescales.
+This prompted that in using actual data, we will only consider a mesh with 2 subdomains that have diffusion coefficient of similar magnitude.
 

### 2018-09-15 make_plot.py

@@ -1,0 +1,123 @@
+
+
+
+
+
+def read_functional(filename):
+    """
+    Require the tag of f= followed by value 
+    
+   
+    """
+    import numpy as np
+    array=[]
+    legend=[0.0,0.0,0.0,0.0]
+    with open(filename) as f:
+         lines = f.readlines()
+         for line in lines:
+
+             if "f=" in line:
+                 array.append(float(line[23:35].replace("D","e")))
+             elif "Namespace" in line:
+ 
+                 legend[0] =line[line.rfind("alpha")+6:line.find("," ,line.find("alpha"))]
+                 legend[1] =line[line.rfind("beta")+5:line.find("," ,line.find("beta"))]
+                 legend[2] =line[line.rfind("k=")+2:line.find("," ,line.find("k="))]
+                 legend[3] =len(eval(line[line.rfind("tau=")+4:line.find("]" ,line.find("tau="))+1]))
+
+                 print legend
+    return np.array(array),legend
+
+
+
+def store_last_val(array,legend):
+    with open("list_end.txt", "a") as myfile:
+          print legend[0],legend[1],legend[2], legend[3],len(array[:,0]),array[-1,0],array[-1,1],array[-1,2] 
+          myfile.write("{} & {} &{} &{} & {}& {} & {} & {} \n ".format(legend[0],legend[1],legend[2], legend[3],len(array[:,0]),array[-1,0],array[-1,1],array[-1,2] ) )
+
+
+
+
+def extract_float(string):
+    beg = string.find("(")+1
+    end = string.find(")")
+    return float(string[beg:end])
+
+def read_slurm(filename):
+
+    """
+    Require the tag of DiffusionCoeffients followed by an array 
+    
+   
+    """
+    import numpy as np
+    array = []
+    legend=[0.0,0.0,0.0,0.0]
+    with open(filename) as f:
+         lines = f.readlines()
+         for line in lines:
+
+             
+             if "Coeffs-Iter" in line:
+                 spl0 , spl1 ,spl2 ,spl3 = line.split("|")
+                 
+                 D1=extract_float(spl1)
+                 D2=extract_float(spl2)
+                 D3=extract_float(spl3) 
+                 array.append([0,D1,D2,D3])
+
+             if "Functional-value" in line:
+                 array[-1][0]= float(line.split("|")[1])
+             
+             elif "Namespace" in line:
+                 legend[0] =line[line.rfind("alpha")+6:line.find("," ,line.find("alpha"))]
[…]

### 2018-09-17 tex/paper.tex
Text Update

@@
 
+The first observation will be considered the initial conditions of the equation, additionally the initial conditions of the manufactured observations are not considered.  
+\begin{equation}
+\tau := \lbrace  0 < t  \leq 24.0\rbrace
+\end{equation}
+This means that the objective functional will consider one less observation.
+However, this can be modified by adding the initial conditions as a optimization parameter.
+This means the timesteps will not be the same as the manufactured solution.
+
+This incoherence will also be investigated, and an adaptive timestep approach can be considered dependent on the results.
+
+ Furthermore, the $g$ value will be sett equal to the next observation.
+
+The initial values of the optimalization was set to $1000,2,1$,
+
 P1 finite elements were used, and the dolfin adjoint [?] was used to construct a reduced function. Furthermore, the scipy optimize library was used to minimize the functional using L-BFGS-B algorithm.
@@
 Is estimating parameters between 2
+
 \begin{table}
 \centering
-\caption{ }
+\caption{Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$ and number of observation $\tau$ with the resulting number of iterations and estimated optimal parameters for the diffusion coefficients.
+}
 \resizebox{\textwidth}{!}{\begin{tabular}{*{8}c}
@@
 
+\begin{table}
+\centering
+\caption{ }
+\resizebox{\textwidth}{!}{\begin{tabular}{*{8}c}
+$\alpha$ & $\beta$ & k & $\tau$ & iter & $ D_{\Omega_1} = 1000$ & $ D_{\Omega_2} = 4.0 $ & $D_{\Omega_3} = 8.0 $ \\
+\hline
+ 0.1 & 1.0 &40 &10 & 743& 1187.4771691 & 4.35026181483 & 8.09946730636 \\ 
+ 0.1 & 0.1 &40 &10 & 932& 1555.16869771 & 6.09495269829 & 8.50884374613 \\ 
+ 0.1 & 0.01 &40 &10 & 1001& 3568.28083904 & 29.3015755902 & 44.1578313645 \\ 
+ 0.1 & 0.001 &40 &10 & 1001& 3910.1049326 & 35.4922989536 & 56.545598289 \\ 
+ 0.1 & 0.0001 &40 &10 & 1001& 4628.35215443 & 39.7391559549 & 63.5747349342 \\ 
+ 0.1 & 1e-05 &40 &10 & 1001& 4402.68260002 & 38.7772764366 & 62.3107416526 \\ 
+ 0.1 & 1e-06 &40 &10 & 1001& 4048.23822112 & 36.8496309935 & 58.8659971438 \\ 
+ 0.01 & 1.0 &40 &10 & 291& 1000.67788636 & 4.02002908826 & 7.98566981348 \\ 
+ 0.01 & 0.1 &40 &10 & 185& 1000.41583989 & 4.15725853533 & 8.04068211749 \\ 
+ 0.01 & 0.01 &40 &10 & 770& 1010.05721903 & 4.46873471103 & 8.23345999428 \\ 
+ 0.01 & 0.001 &40 &10 & 906& 1035.3816137 & 5.23577439946 & 8.93787811692 \\ 
+ 0.01 & 0.0001 &40 &10 & 933& 1054.26269562 & 5.75801399377 & 9.64500568339 \\ 
+ 0.01 & 1e-05 &40 &10 & 816& 1047.05756594 & 5.84828880596 & 9.82387355658 \\ 
+ 0.01 & 1e-06 &40 &10 & 788& 1040.16446365 & 5.75691158325 & 9.6813276929 \\ 
+ 0.001 & 1.0 &40 &10 & 221& 1000.18451793 & 3.98737893359 & 7.97554944332 \\ 
+ 0.001 & 0.1 &40 &10 & 330& 1000.32828904 & 4.04755624182 & 8.0244839499 \\ 
+ 0.001 & 0.01 &40 &10 & 362& 1000.3803523 & 4.11154445121 & 8.11157880655 \\ 
+ 0.001 & 0.001 &40 &10 & 657& 1001.71334392 & 4.19267152271 & 8.27191901359 \\ 
+ 0.001 & 0.0001 &40 &10 & 1001& 1004.86321852 & 4.26170953011 & 8.44356313497 \\ 
+ 0.001 & 1e-05 &40 &10 & 815& 1004.02931722 & 4.37346057066 & 8.57873677626 \\ 
+ 0.001 & 1e-06 &40 &10 & 802& 1004.22491712 & 4.37575380922 & 8.58549567766 \\ 
+ 0.0001 & 1.0 &40 &10 & 172& 1000.08077115 & 3.98137276814 & 7.97389541303 \\ 
+ 0.0001 & 0.1 &40 &10 & 284& 1000.13089398 & 4.03045319152 & 8.02261617711 \\ 
+ 0.0001 & 0.01 &40 &10 & 330& 1000.10285205 & 4.08364875893 & 8.09505305597 \\ 
+ 0.0001 & 0.001 &40 &10 & 559& 1000.5278853 & 4.10885628451 & 8.19383426091 \\ 
+ 0.0001 & 0.0001 &40 &10 & 342& 1000.14882303 & 4.11658048605 & 8.17742760473 \\ 
+ 0.0001 & 1e-05 &40 &10 & 321& 1000.08672575 & 4.05337754766 & 8.14081741343 \\ 
+ 0.0001 & 1e-06 &40 &10 & 551& 1000.58380151 & 4.09044639474 & 8.25619973521 \\ 
+ 1e-05 & 1.0 &40 &10 & 173& 1000.08653936 & 3.98154190918 & 7.97388822692 \\ 
+ 1e-05 & 0.1 &40 &10 & 343& 1000.20326692 & 4.03035382968 & 8.02271998911 \\ 
+ 1e-05 & 0.01 &40 &10 & 419& 1000.31305287 & 4.07478958493 & 8.10307012855 \\ 
+ 1e-05 & 0.001 &40 &10 & 437& 1000.2320762 & 4.08452785122 & 8.16938871213 \\ 
+ 1e-05 & 0.0001 &40 &10 & 374& 1000.11697131 & 4.07952084401 & 8.15715261877 \\ 
+ 1e-05 & 1e-05 &40 &10 & 463& 1000.29010188 & 4.08615998822 & 8.20191735247 \\ 
+ 1e-05 & 1e-06 &40 &10 & 624& 1000.69464905 & 4.08563263518 & 8.25675573539 \\ 
+ 1e-06 & 1.0 &40 &10 & 232& 1000.18034176 & 3.98264060176 & 7.97405892351 \\ 
+ 1e-06 & 0.1 &40 &10 & 287& 1000.15080505 & 4.02963675823 & 8.02269997607 \\ 
+ 1e-06 & 0.01 &40 &10 & 403& 1000.24828839 & 4.07422258869 & 8.09935561335 \\ 
+ 1e-06 & 0.001 &40 &10 & 363& 1000.16258199 & 4.10092887055 & 8.17481714787 \\ 
+ 1e-06 & 0.0001 &40 &10 & 413& 1000.21453049 & 4.09366239057 & 8.19045283723 \\ 
+ 1e-06 & 1e-05 &40 &10 & 474& 1000.34636737 & 4.09817444633 & 8.22081707472 \\ 
+ 1e-06 & 1e-06 &40 &10 & 475& 1000.33096416 & 4.0786358152 & 8.20801753144 \\ 
+\end{tabular}}
+\label{Tab::1}
+\end{table}
+
+\begin{table}
+\centering
+\caption{ $\tau = [1.0, 1.2, 1.4, 2.8, 4.6, 9.6, 14.4, 18.6, 22.2, 24.0] $}
+\resizebox{\textwidth}{!}{\begin{tabular}{*{7}c}
+$\alpha$ & $\beta$ & k & iter & $ D_{\Omega_1} = 1000$ & $ D_{\Omega_2} = 4.0 $ & $D_{\Omega_3} = 8.0 $ \\
+\hline
+ 0.0001 & 1.0  &20 & 352& 1005.22142783 & 3.82672281427 & 7.96012835843 \\ 
+ 0.0001 & 0.1  &20 & 424& 1000.74372847 & 3.48769752552 & 7.46363505824 \\ 
+ 0.0001 & 0.01 &20 & 709& 996.472422218 & 3.28651606815 & 6.89922591307 \\ 
+ 1e-05 & 1.0   &20 & 359& 1005.8332351 & 3.82683123783 & 7.96093977635 \\ 
+ 1e-05 & 0.1   &20 & 413& 1000.71223403 & 3.48709269446 & 7.46388730417 \\ 
+ 1e-05 & 0.01  &20 & 866& 995.496494833 & 3.28703772862 & 6.89839201709 \\ 
+ 1e-06 & 1.0   &20 & 330& 1005.36588332 & 3.82652618763 & 7.95958068842 \\ 
+ 1e-06 & 0.1   &20 & 390& 1000.66722857 & 3.48707900673 & 7.46307424723 \\ 
+ 1e-06 & 0.01  &20 & 577& 997.407662104 & 3.28668627585 & 6.90093340281 \\ 
+ 0.0001 & 1.0  &40 & 720& 1144.48441614 & 4.11378216282 & 8.06601345536 \\ 
+ 0.0001 & 0.1  &40 & 275& 1002.81529271 & 4.01476313602 & 7.99370457785 \\ 
+ 0.0001 & 0.01 &40 & 309& 1003.01379879 & 3.89792451751 & 7.84348036932 \\ 
+ 1e-05 & 1.0   &40 & 574& 1114.40281674 & 4.11652975001 & 8.06793246669 \\ 
+ 1e-05 & 0.1   &40 & 402& 1005.8301423 & 4.01204511666 & 7.98950535021 \\ 
+ 1e-05 & 0.01  &40 & 415& 1005.8339426 & 3.89483734096 & 7.83476748243 \\ 
+ 1e-06 & 1.0   &40 & 648& 1124.35106201 & 4.1148536647 & 8.06730484009 \\ 
+ 1e-06 & 0.1   &40 & 324& 1004.23408094 & 4.01236138465 & 7.99051228829 \\ 
+ 1e-06 & 0.01  &40 & 444& 1007.3125095 & 3.89431330176 & 7.83169391549 \\ 
+\end{tabular}}
+\label{Tab::1}
+\end{table} 
 \section{Discussion}
+
+\begin{table}
+\centering
+\caption{ $\tau =[1.2, 1.4, 1.8, 2.4, 3.6, 5.4, 7.6, 17.2, 18.6, 20.4, 22.4, 24.0] $}
+\resizebox{\textwidth}{!}{\begin{tabular}{*{7}c}
+$\alpha$ & $\beta$ & k & iter & $ D_{\Omega_1} = 1000$ & $ D_{\Omega_2} = 4.0 $ & $D_{\Omega_3} = 8.0 $ \\
+\hline
+ 0.0001 & 1.0 &40 &  423& 1016.53589451 & 4.09744503422 & 8.10477831272 \\ 
+ 0.0001 & 0.1 &40 & 256& 1002.72187136 & 4.01772473372 & 8.01115341448 \\ 
+ 0.0001 & 0.01 &40& 255& 1001.77895566 & 3.940658633 & 7.89664871352 \\ 
+ 1e-05 & 1.0 &40  & 390& 1011.67921461 & 4.09786927743 & 8.10526579439 \\ 
+ 1e-05 & 0.1 &40  & 225& 1001.94506087 & 4.01805587572 & 8.01180925344 \\ 
+ 1e-05 & 0.01 &40 & 209& 1001.27411467 & 3.94131058751 & 7.90365080657 \\ 
+ 1e-06 & 1.0 &40  & 413& 1017.04677284 & 4.097319886 & 8.10398937661 \\ 
+ 1e-06 & 0.1 &40  & 240& 1002.43313972 & 4.01777944191 & 8.01163086184 \\ 
+ 1e-06 & 0.01 &40 & 356& 1003.33076616 & 3.93893764944 & 7.88611881889 \\ 
+\end{tabular}}
+\label{Tab::1}
+\end{table} 
+\section{Discussion}
+
+ 0.0001 & 1.0 &20 &[0.2, 1.2, 2.4, 3.6, 4.8, 6.0, 7.2, 8.4, 9.6, 10.8, 12.0, 13.2, 14.4, 15.6, 16.8, 17.0, 19.2, 20.4, 21.6, 22.8, 24.0] & 153& 999.888464905 & 4.02189206656 & 8.01937098574 \\ 
+ 0.0001 & 0.1 &20 &[0.2, 1.2, 2.4, 3.6, 4.8, 6.0, 7.2, 8.4, 9.6, 10.8, 12.0, 13.2, 14.4, 15.6, 16.8, 17.0, 19.2, 20.4, 21.6, 22.8, 24.0] & 82& 999.92653104 & 4.0172778853 & 8.02072488205 \\ 
+ 0.0001 & 0.01 &20 &[0.2, 1.2, 2.4, 3.6, 4.8, 6.0, 7.2, 8.4, 9.6, 10.8, 12.0, 13.2, 14.4, 15.6, 16.8, 17.0, 19.2, 20.4, 21.6, 22.8, 24.0] & 183& 999.601435216 & 4.0167801622 & 8.02099543744 \\ 
+ 1e-05 & 1.0 &20 &[0.2, 1.2, 2.4, 3.6, 4.8, 6.0, 7.2, 8.4, 9.6, 10.8, 12.0, 13.2, 14.4, 15.6, 16.8, 17.0, 19.2, 20.4, 21.6, 22.8, 24.0] & 170& 999.857251969 & 4.02183073053 & 8.0193786719 \\ 
+ 1e-05 & 0.1 &20 &[0.2, 1.2, 2.4, 3.6, 4.8, 6.0, 7.2, 8.4, 9.6, 10.8, 12.0, 13.2, 14.4, 15.6, 16.8, 17.0, 19.2, 20.4, 21.6, 22.8, 24.0] & 145& 999.723425171 & 4.01725503821 & 8.02073378231 \\ 
+ 1e-05 & 0.01 &20 &[0.2, 1.2, 2.4, 3.6, 4.8, 6.0, 7.2, 8.4, 9.6, 10.8, 12.0, 13.2, 14.4, 15.6, 16.8, 17.0, 19.2, 20.4, 21.6, 22.8, 24.0] & 189& 999.686295266 & 4.0167215691 & 8.02087841472 \\ 
+ 1e-06 & 1.0 &20 &[0.2, 1.2, 2.4, 3.6, 4.8, 6.0, 7.2, 8.4, 9.6, 10.8, 12.0, 13.2, 14.4, 15.6, 16.8, 17.0, 19.2, 20.4, 21.6, 22.8, 24.0] & 252& 999.744572206 & 4.02186634423 & 8.01936617912 \\ 
+ 1e-06 & 0.1 &20 &[0.2, 1.2, 2.4, 3.6, 4.8, 6.0, 7.2, 8.4, 9.6, 10.8, 12.0, 13.2, 14.4, 15.6, 16.8, 17.0, 19.2, 20.4, 21.6, 22.8, 24.0] & 167& 999.698939533 & 4.01722486087 & 8.02076770928 \\ 
+ 1e-06 & 0.01 &20 &[0.2, 1.2, 2.4, 3.6, 4.8, 6.0, 7.2, 8.4, 9.6, 10.8, 12.0, 13.2, 14.4, 15.6, 16.8, 17.0, 19.2, 20.4, 21.6, 22.8, 24.0] & 145& 999.76147155 & 4.01667474386 & 8.02102893936 \\
+
+ \begin{table}
+\centering
+\caption{ $\tau = [2.4, 4.8, 7.2, 9.6, 12.0, 14.4, 16.8, 19.2, 21.6, 24.0] $}
+\resizebox{\textwidth}{!}{\begin{tabular}{*{7}c}
+$\alpha$ & $\beta$ & k & iter & $ D_{\Omega_1} = 1000$ & $ D_{\Omega_2} = 4.0 $ & $D_{\Omega_3} = 8.0 $ \\
+\hline
+ 0.001 & 1.0 &11   & 535& 1155.41620776 & 4.56890164554 & 8.74862316292 \\ 
+ 0.001 & 0.1 &11  & 692& 1138.18797804 & 4.77615608916 & 9.1001502642 \\ 
+ 0.001 & 0.01 &11 & 620& 1109.09332378 & 4.83440528908 & 9.23937192655 \\ 
+ 0.0001 & 1.0 &11 & 512& 1177.95965037 & 4.56118986925 & 8.74503026051 \\ 
+ 0.0001 & 0.1 &11 & 796& 1167.15728007 & 4.76942041977 & 9.09708917746 \\ 
+ 0.0001 & 0.01&11 & 726& 1147.45125238 & 4.82397769456 & 9.23132854631 \\ 
+ 1e-05 & 1.0 &11  & 547& 1150.09091484 & 4.56745099896 & 8.74784724393 \\ 
+ 1e-05 & 0.1 &11  & 774& 1209.27556281 & 4.7599962838 & 9.09240730332 \\ 
+ 1e-05 & 0.01 &11 & 963& 1178.62113472 & 4.81968561039 & 9.22165857548 \\ 
+ 1e-06 & 1.0 &11  & 516& 1178.30282045 & 4.56182347972 & 8.74408755566 \\ 
+ 1e-06 & 0.1 &11  & 690& 1169.85258682 & 4.76763208109 & 9.09437803203 \\ 
+ 1e-06 & 0.01 &11 & 885& 1161.54226173 & 4.82290410594 & 9.23253559953 \\ 
+ 0.001 & 1.0 &10  & 144& 1000.72690068 & 4.43617090765 & 8.47356658247 \\ 
+ 0.001 & 0.1 &10  & 188& 1001.11632883 & 4.42560354452 & 8.55339645884 \\ 
+ 0.001 & 0.01 &10 & 242& 1002.06937059 & 4.42388003439 & 8.57511846108 \\ 
+ 0.0001 & 1.0 &10 & 157& 1000.83218743 & 4.43452507573 & 8.47318916943 \\ 
+ 0.0001 & 0.1 &10 & 131& 1000.56624899 & 4.42351929725 & 8.55256760219 \\ 
+ 0.0001 & 0.01&10 & 174& 1001.0091989 & 4.42260942583 & 8.57478259945 \\ 
+ 1e-05 & 1.0 &10  & 151& 1000.79310038 & 4.43448500449 & 8.47338153139 \\ 
+ 1e-05 & 0.1 &10  & 140& 1000.70858373 & 4.42340629909 & 8.55312689863 \\ 
+ 1e-05 & 0.01 &10 & 203& 1001.34714912 & 4.42253540005 & 8.57470943099 \\ 
+ 1e-06 & 1.0 &10  & 115& 1000.47868283 & 4.43456295486 & 8.47226911091 \\ 
+ 1e-06 & 0.1 &10  & 158& 1000.8203239 & 4.42368702618 & 8.55236552474 \\ 
+ 1e-06 & 0.01 &10 & 142& 1000.64224198 & 4.42327990324 & 8.57047799569 \\ 
+ 0.001 & 1.0 &10  & 127& 1000.57534928 & 4.43620469807 & 8.47334881884 \\ 
+ 0.001 & 0.1 &10  & 209& 1001.40602027 & 4.42496040369 & 8.55523771434 \\ 
+ 0.001 & 0.01 &10 & 212& 1001.64339174 & 4.42433050528 & 8.57315746956 \\ 
+ 0.0001 & 1.0 &9  & 110& 999.72163906 & 4.11479310934 & 8.33462232991 \\ 
+ 0.0001 & 0.1 &9  & 105& 999.69280754 & 4.1045396919 & 8.33774014666 \\ 
+ 0.0001 & 0.01 &9 &  88& 999.772427775 & 4.10360542672 & 8.33814068545 \\ 
+ 1e-05 & 1.0 &9   & 129& 999.64486142 & 4.11473526399 & 8.33422818516 \\ 
+ 1e-05 & 0.1 &9   & 127& 999.585578036 & 4.10455462113 & 8.3375263256 \\ 
+ 1e-05 & 0.01 &9  &  91& 999.743943666 & 4.10325272534 & 8.33837761724 \\ 
+ 1e-06 & 1.0 &9   & 138& 999.565361602 & 4.11477304552 & 8.3344417303 \\ 
+ 1e-06 & 0.1 &9   & 127& 999.556729496 & 4.10443164325 & 8.33788684648 \\ 
+ 1e-06 & 0.01 &9  & 142& 999.44777782 & 4.10347962986 & 8.33800635508 \\ 
+\end{tabular}}
+\label{Tab::Incoherence}
+\end{table} 
+\section{Discussion}
+
+The timestep incoherence between observations and Eq.\ref{Eq::PDE} was not initially considered, since the actual data do not maintain a constant timestep of the observations.
+However, due to the implementation this effect became apparent when the number of timesteps changed.
+In Tab.\ref{Tab::Incoherence} we can see that changing the number of timesteps with 1 can improve or worsen the process significantly, both parameter estimation and number of iterations.
+This effect mainly comes from the proximity of the observation timepoint it is.
+Therefore selecting more number of timesteps than observation points seems proficient.
+However, using adaptive timestepping can provide means to decrease the number of iterations, but would require
+
+The Eq.\ref{Eq::PDE} was discretized using first order Euler, thus the approximation
+
+We can see in Fig.??, that increasing the number of timesteps will improve the estimation of diffusion coefficients.
+
+The manufactured observations were constructed by imposing a quadratic function ??
+as Dirichlet boundary conditions.
+Thus the number of time steps will affect the approximation of the boundary conditions
+
+Thus
 
@@
 
+The case of an observation vacancy did not show any clear discrepancy in the objective function, see Fig.
+??.
+However, there is a divergent tendency in the estimation of $D_{\Omega_1}$, see Fig.??.
+This same tendency can be seen in Fig.
+??
+with .
+Although this behavior  ...
+
+The corresponding objective function does not exhibit any discrepancy, thus the object functions dependency on $D_{\Omega_1}$ is small.
+
+Or rather the observation function does not compute a difference.
+The observation function require that the parameters presence in the observations are distinct.
+This is not the case for cube that reach equilibrium after one timestep.
+
+The mesh cells are of the order $\mathrm{mm}$ and the timesteps are of order $0.1$. The number of cells representing the csf is 15000.
+
 \bibliographystyle{amsplain}

### 2018-09-17 make_plot.py

@@ -32,8 +32,8 @@ def read_functional(filename):
 
 def store_last_val(array,legend):
     with open("list_end.txt", "a") as myfile:
-          print legend[0],legend[1],legend[2], legend[3],len(array[:,0]),array[-1,0],array[-1,1],array[-1,2] 
-          myfile.write("{} & {} &{} &{} & {}& {} & {} & {} \n ".format(legend[0],legend[1],legend[2], legend[3],len(array[:,0]),array[-1,0],array[-1,1],array[-1,2] ) )
+          print legend[0],legend[1],legend[2], legend[3],len(array[:,0]),array[-1,1],array[-1,2],array[-1,3] 
+          myfile.write("{} & {} &{} &{} & {}& {} & {} & {} \\\\ \n ".format(legend[0],legend[1],legend[2], legend[3],len(array[:,0]),array[-1,1],array[-1,2],array[-1,3] ) )
 
 
 
@@ -70,17 +70,26 @@ def read_slurm(filename):
                  array[-1][0]= float(line.split("|")[1])
              
              elif "Namespace" in line:
-                 legend[0] =line[line.rfind("alpha")+6:line.find("," ,line.find("alpha"))]
-                 legend[1] =line[line.rfind("beta")+5:line.find("," ,line.find("beta"))]
-                 legend[2] =line[line.rfind("k=")+2:line.find("," ,line.find("k="))]
-                 legend[3] =len(eval(line[line.rfind("tau=")+4:line.find("]" ,line.find("tau="))+1]))
+                 legend[0] =float(line[line.rfind("alpha")+6:line.find("," ,line.find("alpha"))])
+                 legend[1] =float(line[line.rfind("beta")+5:line.find("," ,line.find("beta"))])
+                 legend[2] =int(line[line.rfind("k=")+2:line.find("," ,line.find("k="))])
+                 legend[3] =eval(line[line.rfind("tau=")+4:line.find("]" ,line.find("tau="))+1])
 
-                 print legend
+             
     return np.array(array),legend
 
 
+def regular(legend):
+    return legend[3]==[2.4, 4.8, 7.2, 9.6, 12.0, 14.4, 16.8, 19.2, 21.6, 24.0]
 
+def hole(legend):
[…]

### 2018-09-17 forward_problem.py
Full boundary control

@@ -46,7 +46,9 @@ def forward_problem(context):
 
     A = assemble(a)
     bc = DirichletBC(V, 0, context.boundaries, 1)
-    bc.apply(A)
+    for bc in bcs :
+        bc.apply(A)
+
     # Define solver. Use GMRES iterative method with AMG preconditioner.
     solver = LinearSolver(mpi_comm_self(), "gmres")
     solver.set_operator(A)
@@ -58,8 +60,9 @@ def forward_problem(context):
 
         # Assemble RHS and apply DirichletBC
         b = assemble(L)
-        A.bcs = [bc]
-        bc.apply(b)
+        A.bcs = bcs
+        for bc in bcs:
+            bc.apply(b)
     
         # Solve linear system for this timestep
         solver.solve(U.vector(), b)
@@ -79,7 +82,7 @@ class Context(object):
         self.g_list = g_list
         self.t = 0                                
         self.ic = Function(self.V,annotate=True)
-        self.linear_solver_args = ("gmres", "amg")
+        self.linear_solver_args = ("gmres")
 
     def scale(self, i):
         return 1.0
@@ -148,7 +151,7 @@ def functional(mesh_config, V, D, g_list, tau, obs_file, alpha=0.0, beta=0.0, gr
                 self.next_tau += 1
 
             # Choose time integral weights
-            if self.t <= self.dt or self.next_tau >= len(self.tau):
+            if self.t <= self.tau[0] + self.dt or self.t > self.tau[-1] - self.dt/2 :
                 # If endpoints use 0.5 weight
                 weight = 0.5
             else:
@@ -156,13 +159,13 @@ def functional(mesh_config, V, D, g_list, tau, obs_file, alpha=0.0, beta=0.0, gr
                 weight = 1.0
 
             # Add regularisation
-            self.J += 1 / 2 * weight * self.dt * assemble(self.g ** 2 * self.ds(1) ) * self.alpha
+            self.J += 1 / 2 * weight * self.dt * assemble(self.g ** 2 * self.ds ) * self.alpha
             if self.current_g_index > 1:
                 g_prev = self.g_list[self.current_g_index - 2]
-                self.J += 1 / 2 * weight * self.dt * assemble(((self.g - g_prev) / self.dt) ** 2 * self.ds(1)) * self.beta
+                self.J += 1 / 2 * weight * self.dt * assemble(((self.g - g_prev) / self.dt) ** 2 * self.ds) * self.beta
 
         def next_bc(self):          
[…]

### 2018-09-18 forward_problem.py
Full Boundary Control

@@ -45,18 +45,18 @@ def forward_problem(context):
     L = U_prev * v * dx
 
     A = assemble(a)
-    bc = DirichletBC(V, 0, context.boundaries, 1)
+    bcs = [ DirichletBC(V, 0, context.boundaries, i) for i in range(1,4)]
     for bc in bcs :
         bc.apply(A)
 
     # Define solver. Use GMRES iterative method with AMG preconditioner.
-    solver = LinearSolver(mpi_comm_self(), "gmres")
+    solver = LinearSolver(mpi_comm_self(), "gmres","hypr_amg")
     solver.set_operator(A)
 
     while not context.should_stop():
         U_prev.assign(U,annotate =True)
         context.advance_time()
-        bc = context.next_bc()
+        bcs = context.next_bc()
 
         # Assemble RHS and apply DirichletBC
         b = assemble(L)
@@ -77,6 +77,7 @@ class Context(object):
         self.ds = mesh_config["ds"]
         self.dx = mesh_config["dx"]
         self.boundaries = mesh_config["boundaries"]
+
         self.V = V
         self.D = D
         self.g_list = g_list
@@ -127,7 +128,7 @@ def functional(mesh_config, V, D, g_list, tau, obs_file, alpha=0.0, beta=0.0, gr
 
             self.obs_file.read(self.ic, "%0.2f"%(self.t) )
 
-            self.gradient = [1.0, 1.0, 1.0]
+            self.gradient = [100.0, 1.0, 1.0]
             
         def scale(self, i):
             if self.gradient is not None:
@@ -144,8 +145,7 @@ def functional(mesh_config, V, D, g_list, tau, obs_file, alpha=0.0, beta=0.0, gr
 
         def handle_solution(self, U):
             if abs(self.t - self.tau[self.next_tau]) < abs(self.t + self.dt - self.tau[self.next_tau]): 
-                # If t is closest to next observation then compute misfit.
-                self.obs_file.read(self.d, "%0.2f"%(self.tau[self.next_tau]))  # Read observation
+                self.obs_file.read(self.d, "%0.2f"%(self.tau[self.next_tau]))  
                 self.J += assemble((U - self.d) ** 2 * self.dx) 
                 # Move on to next observation
                 self.next_tau += 1

### 2018-09-18 main.py

@@ -110,8 +110,6 @@ if __name__ == "__main__":
         exit()
     else:
         g = bc_guess(g, Z.obs_file, tau, k)
-
-
         J = functional(mesh_config, V, D, g, tau, Z.obs_file, Z.alpha, Z.beta, None)
 
     ctrls = ([Control(D[i]) for i in range(1, 4)]

### 2018-09-18 forward_problem.py
Add Fix

@@ -50,7 +50,7 @@ def forward_problem(context):
         bc.apply(A)
 
     # Define solver. Use GMRES iterative method with AMG preconditioner.
-    solver = LinearSolver(mpi_comm_self(), "gmres","hypr_amg")
+    solver = LinearSolver(mpi_comm_self(), "gmres")
     solver.set_operator(A)
 
     while not context.should_stop():

### 2018-09-18 forward_problem.py
Added noise

@@ -33,6 +33,8 @@ def forward_problem(context):
     # Solution at current and previous time
     U_prev = Function(V)
     U      = Function(V)
+
+    context.initial_conditions()
     U.assign(context.ic)
 
     dt = context.dt
@@ -107,15 +109,13 @@ class Context(object):
     def return_value(self):
         return None
 
-def functional(mesh_config, V, D, g_list, tau, obs_file, alpha=0.0, beta=0.0, gradient=None):
+def functional(mesh_config, V, D, g_list, tau, obs_file, alpha=0.0, beta=0.0, gradient=None, noise=None):
     class FunctionalContext(Context):
         def __init__(self, mesh_config, V, D, g_list, tau, obs_file, alpha=0.0, beta=0.0, gradient=None):
             super(FunctionalContext, self).__init__(mesh_config, V, D, g_list)
             self.tau = tau
             self.next_tau = 1 
             self.g = Function(self.V)
-
-
             self.current_g_index = 0
             self.J = 0.0
             self.d = Function(self.V)
@@ -126,10 +126,17 @@ def functional(mesh_config, V, D, g_list, tau, obs_file, alpha=0.0, beta=0.0, gr
             self.dt =( tau[-1] - tau[0] )/float(len(g_list)) 
 
 
+            self.noise = noise
+ 
             self.obs_file.read(self.ic, "%0.2f"%(self.t) )
-
             self.gradient = [100.0, 1.0, 1.0]
             
+        def initial_conditions(self):
+            self.obs_file.read(self.ic, "%0.2f"%(self.tau[0]))
+            if self.noise: 
+               self.ic.vector()[:]+=self.noise[0].vector()[:]
+
+
         def scale(self, i):
             if self.gradient is not None:
                 return abs(float(self.gradient[i]))
@@ -146,6 +153,8 @@ def functional(mesh_config, V, D, g_list, tau, obs_file, alpha=0.0, beta=0.0, gr
         def handle_solution(self, U):
             if abs(self.t - self.tau[self.next_tau]) < abs(self.t + self.dt - self.tau[self.next_tau]): 
                 self.obs_file.read(self.d, "%0.2f"%(self.tau[self.next_tau]))  
+                if self.noise:
+                   self.d.vector()[:]+=self.noise[self.next_tau].vector()[:]
                 self.J += assemble((U - self.d) ** 2 * self.dx) 
                 # Move on to next observation
                 self.next_tau += 1

### 2018-09-18 main.py

@@ -10,6 +10,11 @@ class InitialConditions(Expression):
             values[0] = 0
 
 
+def add_noise(noise):
+     for i in noise:
+         i.vector()[:]+=Z.noise*(0.5-random.random(i.vector().size()) )
+
+
 def initial_condition(V, mesh_config):
     subdomains = mesh_config["subdomains"]
     init = InitialConditions(degree=1)
@@ -30,7 +35,7 @@ def bc(g, V,tau,k, mesh_config):
     return g
 
 
-def bc_guess(g, obs_file, tau, k):
+def bc_guess(g, obs_file, tau, k,noise):
     d = Function(g[0].function_space())
     dt = (tau[-1] -tau[0])/k
     obs_file = HDF5File(mpi_comm_world(), obs_file, 'r')
@@ -40,6 +45,8 @@ def bc_guess(g, obs_file, tau, k):
         t += dt
         obs_file.read(d,"%0.2f"%(tau[next_tau]))
         g[i].vector()[:] = d.vector()[:]
+        if noise:
+           g[i].vector()[:]+= noise[next_tau].vector()[:]
 
         if abs(t - tau[next_tau]) < abs(t + dt - tau[next_tau]):
             next_tau += 1
@@ -61,6 +68,7 @@ def iter_cb(m):
 
 if __name__ == "__main__":
     from forward_problem import initialize_mesh, load_control_values, save_control_values, generate_observations, functional
+    from numpy import random
     import argparse
     import sys 
     print( sys.version )
@@ -91,7 +99,7 @@ if __name__ == "__main__":
 
     # Observation timepoints
     if Z.dx!=0.0 : # dx can be simpler 
-       k = int( (Z.tau[-1] - Z.tau[0])/dx +0.5 )
+       k = int( (Z.tau[-1] - Z.tau[0])/dx)
        tau =[ Z.tau[0] + dx*i for i in range(k)]   
     else : 
        k = Z.k
@@ -102,15 +110,23 @@ if __name__ == "__main__":
     g = [Function(V) for _ in range(k)]
     correct_g = [Function(V) for _ in range(k)]
     correct_g = bc(correct_g, V,tau,k, mesh_config)
-    
+    # Noise 
+
+    if Z.noise!=0.0:
+       noise = [ Function(V) for _ in tau]
+       add_noise(noise)
+    else : 
+       noise = None
+
+
     if Z.generate_observations:
[…]

### 2018-09-18 main.py
Opt crit changed

@@ -137,7 +137,7 @@ if __name__ == "__main__":
     Jhat.optimize()
 
     
-    opt_ctrls = minimize(Jhat, method="L-BFGS-B", callback = iter_cb, options={"disp": True, "maxiter": Z.maxiter, "gtol": 1.0e-2})
+    opt_ctrls = minimize(Jhat, method="L-BFGS-B", callback = iter_cb, options={"disp": True, "maxiter": Z.maxiter, "gtol": 1.0e-1})
 
     #print("[Constant({}), Constant({}), Constant({})]".format(float(opt_ctrls[0]), float(opt_ctrls[1]), float(opt_ctrls[2])))
     #print(

### 2018-09-18 inverse3D-abel.sh
correct

@@ -44,6 +44,6 @@ echo "${@:4}"
 cd $SCRATCH
 ls
 echo $SCRATCH
-mpirun --bind-to none python3 main.py --alpha $1 --beta $2 --noise $3 --k $4 --tau "${@:5}"
+python3 main.py --alpha $1 --beta $2 --noise $3 --k $4 --tau "${@:5}"
 
 

### 2018-09-18 main.py
Adding noise fix

@@ -10,9 +10,10 @@ class InitialConditions(Expression):
             values[0] = 0
 
 
-def add_noise(noise):
+def add_noise(noise,amp): 
+     from numpy import random
      for i in noise:
-         i.vector()[:]+=Z.noise*(0.5-random.random(i.vector().size()) )
+         i.vector().add_local( amp*(0.5-random.random(i.vector().local_size()) ) )
 
 
 def initial_condition(V, mesh_config):
@@ -68,7 +69,6 @@ def iter_cb(m):
 
 if __name__ == "__main__":
     from forward_problem import initialize_mesh, load_control_values, save_control_values, generate_observations, functional
-    from numpy import random
     import argparse
     import sys 
     print( sys.version )
@@ -114,7 +114,7 @@ if __name__ == "__main__":
 
     if Z.noise!=0.0:
        noise = [ Function(V) for _ in tau]
-       add_noise(noise)
+       add_noise(noise,Z.noise)
     else : 
        noise = None
 

### 2018-09-19 main.py
Scaling

@@ -78,7 +78,7 @@ if __name__ == "__main__":
     parser.add_argument('--beta', default=0.001, type=float)
     parser.add_argument('--noise', default=0.0, type=float)
     parser.add_argument('--tol', default=0.001, type=float)
-    parser.add_argument('--D', default=[1000, 1, 1], type=float, nargs=3)
+    parser.add_argument('--D', default=[1, 1, 1], type=float, nargs=3)
     parser.add_argument('--mesh', default="mesh_invers_contrast.h5", type=str)
     parser.add_argument("--tau", nargs="+", type=float)
     parser.add_argument("--k", type=int)

### 2018-09-19 forward_problem.py
For 2 subdomains

@@ -12,7 +12,7 @@ def initialize_mesh(mesh_file): # Lars : Endret
     # Import mesh and subdomains
     mesh = Mesh()
 
-    hdf = HDF5File(mesh.mpi_comm(), "mesh_invers_contrast.h5", "r")
+    hdf = HDF5File(mesh.mpi_comm(), mesh_file, "r")
     hdf.read(mesh, "/mesh", False, annotate=False)
     subdomains = MeshFunction("size_t", mesh, mesh.topology().dim())
     hdf.read(subdomains, "/subdomains", annotate=False)
@@ -42,12 +42,12 @@ def forward_problem(context):
     dx = context.dx
 
     # Define bilinear form, handling each subdomain 1, 2, and 3 in separate integrals.
-    a = u * v * dx + sum([dt * context.scale(j-1) * D[j] * inner(grad(v), grad(u)) * dx(j) for j in range(1, 4)])
+    a = u * v * dx + sum([dt * context.scale(j-1) * D[j] * inner(grad(v), grad(u)) * dx(j) for j in range(1, 3)])
     # Define linear form.
     L = U_prev * v * dx
 
     A = assemble(a)
-    bcs = [ DirichletBC(V, 0, context.boundaries, i) for i in range(1,4)]
+    bcs = [ DirichletBC(V, 0, context.boundaries, i) for i in range(1,3)]
     for bc in bcs :
         bc.apply(A)
 
@@ -129,7 +129,7 @@ def functional(mesh_config, V, D, g_list, tau, obs_file, alpha=0.0, beta=0.0, gr
             self.noise = noise
  
             self.obs_file.read(self.ic, "%0.2f"%(self.t) )
-            self.gradient = [100.0, 1.0, 1.0]
+            self.gradient = None
             
         def initial_conditions(self):
             self.obs_file.read(self.ic, "%0.2f"%(self.tau[0]))
@@ -174,7 +174,7 @@ def functional(mesh_config, V, D, g_list, tau, obs_file, alpha=0.0, beta=0.0, gr
                 self.J += 1 / 2 * weight * self.dt * assemble(((self.g - g_prev) / self.dt) ** 2 * self.ds) * self.beta
 
         def next_bc(self):          
-            return  [ DirichletBC(self.V, self.g, self.boundaries, i) for i in range(1,4)]
+            return  [ DirichletBC(self.V, self.g, self.boundaries, i) for i in range(1,3)]
 
         def return_value(self):
             self.obs_file.close()

### 2018-09-19 main.py

@@ -58,13 +58,13 @@ iter_cnt = 0
 def iter_cb(m):
     global iter_cnt
     iter_cnt += 1
-    print("Coeffs-Iter: {} | Constant({}) | Constant({}) | Constant({})".format(iter_cnt, float(m[0]), float(m[1]), float(m[2])))
+    print("Coeffs-Iter: {} | Constant({}) | Constant({}) | Constant({})".format(iter_cnt, float(m[0]), float(m[1]) )
     from pyadjoint.reduced_functional_numpy import ReducedFunctionalNumPy
     NumRF = ReducedFunctionalNumPy(Jhat)
     ds = mesh_config["ds"]
     fenics_m = NumRF.set_local([control.copy_data() for control in Jhat.controls], m)
     print("Functional-value: {} | {} ".format(iter_cnt, NumRF(m)) )
-    print("DirichletBC-Iter: {} | {}".format(iter_cnt, sum([assemble((fenics_m[i] - correct_g[i-3])**2*ds) for i in range(3, len(fenics_m))])/sum([assemble(correct_g[i-3]**2*ds) for i in range(3, len(fenics_m)) ]) ))
+    print("DirichletBC-Iter: {} | {}".format(iter_cnt, sum([assemble((fenics_m[i] - correct_g[i-3])**2*ds) for i in range(2, len(fenics_m))])/sum([assemble(correct_g[i-3]**2*ds) for i in range(3, len(fenics_m)) ]) ))
 
 
 if __name__ == "__main__":
@@ -78,7 +78,7 @@ if __name__ == "__main__":
     parser.add_argument('--beta', default=0.001, type=float)
     parser.add_argument('--noise', default=0.0, type=float)
     parser.add_argument('--tol', default=0.001, type=float)
-    parser.add_argument('--D', default=[1, 1, 1], type=float, nargs=3)
+    parser.add_argument('--D', default=[1, 1], type=float, nargs=2)
     parser.add_argument('--mesh', default="mesh_invers_contrast.h5", type=str)
     parser.add_argument("--tau", nargs="+", type=float)
     parser.add_argument("--k", type=int)
@@ -95,7 +95,7 @@ if __name__ == "__main__":
     V = FunctionSpace(mesh_config["mesh"], "CG", 1)
 
     # Diffusion coefficients
-    D = {1: Constant(Z.D[0]), 2: Constant(Z.D[1]), 3: Constant(Z.D[2])}
[…]

### 2018-09-19 main.py
Fix error

@@ -58,7 +58,7 @@ iter_cnt = 0
 def iter_cb(m):
     global iter_cnt
     iter_cnt += 1
-    print("Coeffs-Iter: {} | Constant({}) | Constant({}) | Constant({})".format(iter_cnt, float(m[0]), float(m[1]) )
+    print("Coeffs-Iter: {} | Constant({}) | Constant({}) | Constant({})".format(iter_cnt, float(m[0]), float(m[1]) ) )
     from pyadjoint.reduced_functional_numpy import ReducedFunctionalNumPy
     NumRF = ReducedFunctionalNumPy(Jhat)
     ds = mesh_config["ds"]

### 2018-09-21 main.py
commit

@@ -58,7 +58,7 @@ iter_cnt = 0
 def iter_cb(m):
     global iter_cnt
     iter_cnt += 1
-    print("Coeffs-Iter: {} | Constant({}) | Constant({}) | Constant({})".format(iter_cnt, float(m[0]), float(m[1]) ) )
+    print("Coeffs-Iter: {} | Constant({}) | Constant({})".format(iter_cnt, float(m[0]), float(m[1]) ) )
     from pyadjoint.reduced_functional_numpy import ReducedFunctionalNumPy
     NumRF = ReducedFunctionalNumPy(Jhat)
     ds = mesh_config["ds"]

### 2018-09-22 forward_problem.py
Linear interpolation

@@ -47,9 +47,8 @@ def forward_problem(context):
     L = U_prev * v * dx
 
     A = assemble(a)
-    bcs = [ DirichletBC(V, 0, context.boundaries, i) for i in range(1,4)]
-    for bc in bcs :
-        bc.apply(A)
+    bc = DirichletBC(V, 0, context.boundaries, 1)
+    bc.apply(A)
 
     # Define solver. Use GMRES iterative method with AMG preconditioner.
     solver = LinearSolver(mpi_comm_self(), "gmres")
@@ -65,11 +64,10 @@ def forward_problem(context):
         A.bcs = bcs
         for bc in bcs:
             bc.apply(b)
-    
         # Solve linear system for this timestep
         solver.solve(U.vector(), b)
 
-        context.handle_solution(U)
+        context.handle_solution(U,U_prev)
          
     return context.return_value()
 
@@ -129,7 +127,7 @@ def functional(mesh_config, V, D, g_list, tau, obs_file, alpha=0.0, beta=0.0, gr
             self.noise = noise
  
             self.obs_file.read(self.ic, "%0.2f"%(self.t) )
-            self.gradient = [100.0, 1.0, 1.0]
+            self.gradient = [1.0, 1.0, 1.0]
             
         def initial_conditions(self):
             self.obs_file.read(self.ic, "%0.2f"%(self.tau[0]))
@@ -150,15 +148,33 @@ def functional(mesh_config, V, D, g_list, tau, obs_file, alpha=0.0, beta=0.0, gr
             self.g  = self.g_list[self.current_g_index]
             self.current_g_index += 1
 
-        def handle_solution(self, U):
-            if abs(self.t - self.tau[self.next_tau]) < abs(self.t + self.dt - self.tau[self.next_tau]): 
+        def handle_observations(self,U, U_prev):
+            Dt = ( self.tau[self.next_tau] - self.t )  
+           
+            if  round(self.t,2) <= self.tau[self.next_tau] and self.tau[self.next_tau] < round(self.t+self.dt,2)  : 
+                print(self.tau[self.next_tau] - self.t)
                 self.obs_file.read(self.d, "%0.2f"%(self.tau[self.next_tau]))  
                 if self.noise:
                    self.d.vector()[:]+=self.noise[self.next_tau].vector()[:]
+
+                Ulin = Dt/self.dt*U +  (self.dt - Dt)/self.dt*U_prev       
                 self.J += assemble((U - self.d) ** 2 * self.dx) 
[…]

### 2018-09-22 main.py

@@ -81,7 +81,8 @@ if __name__ == "__main__":
     parser.add_argument('--D', default=[1, 1, 1], type=float, nargs=3)
     parser.add_argument('--mesh', default="mesh_invers_contrast.h5", type=str)
     parser.add_argument("--tau", nargs="+", type=float)
-    parser.add_argument("--k", type=int)
+    parser.add_argument("--k",default=1, type=int)
+    parser.add_argument("--K",default=0, type=int)
     parser.add_argument("--obs-file", default="U.xdmf", type=str)
     parser.add_argument("--load-control-values-file", default=None, type=str)
     parser.add_argument("--save-control-values-file", default=None, type=str)
@@ -97,22 +98,20 @@ if __name__ == "__main__":
     # Diffusion coefficients
     D = {1: Constant(Z.D[0]), 2: Constant(Z.D[1]), 3: Constant(Z.D[2])}
 
-    # Observation timepoints
-    if Z.dx!=0.0 : # dx can be simpler 
-       k = int( (Z.tau[-1] - Z.tau[0])/dx)
-       tau =[ Z.tau[0] + dx*i for i in range(k)]   
-    else : 
-       k = Z.k
-       tau = Z.tau
-
+    tau = Z.tau
+    # Number timepoints
+    if Z.K==0:
+      k = int(len(tau)-1)*Z.k
+    else :
+      k =Z.K
     # Boundary conditions
-
+      
     g = [Function(V) for _ in range(k)]
     correct_g = [Function(V) for _ in range(k)]
     correct_g = bc(correct_g, V,tau,k, mesh_config)
     # Noise 
 
-    if Z.noise!=0.0:
+    if Z.noise!=0:
        noise = [ Function(V) for _ in tau]
        add_noise(noise,Z.noise)
     else : 

### 2018-09-24 forward_problem.py
Fixed bug

@@ -149,16 +149,16 @@ def functional(mesh_config, V, D, g_list, tau, obs_file, alpha=0.0, beta=0.0, gr
             self.current_g_index += 1
 
         def handle_observations(self,U, U_prev):
-            Dt = ( self.tau[self.next_tau] - self.t )  
+            Dt = ( self.t - self.tau[self.next_tau])  
            
-            if  round(self.t,2) <= self.tau[self.next_tau] and self.tau[self.next_tau] < round(self.t+self.dt,2)  : 
-                print(self.tau[self.next_tau] - self.t)
+            if  round(self.t-self.dt,2) <= self.tau[self.next_tau] and self.tau[self.next_tau] < round(self.t,2)  : 
+            
                 self.obs_file.read(self.d, "%0.2f"%(self.tau[self.next_tau]))  
                 if self.noise:
                    self.d.vector()[:]+=self.noise[self.next_tau].vector()[:]
-
-                Ulin = Dt/self.dt*U +  (self.dt - Dt)/self.dt*U_prev       
-                self.J += assemble((U - self.d) ** 2 * self.dx) 
+                
+                Ulin = Dt/self.dt*U_prev +  (self.dt - Dt)/self.dt*U       
+                self.J += assemble((Ulin - self.d) ** 2 * self.dx) 
                 # Move on to next observation
                 self.next_tau += 1
                 # Check if there is another observations in time step
@@ -166,8 +166,8 @@ def functional(mesh_config, V, D, g_list, tau, obs_file, alpha=0.0, beta=0.0, gr
                     self.handle_observations(U, U_prev)
 
         def handle_solution(self, U, U_prev):
-
-           # tau > t and tau < t+dt --> t < tau < t +dt --> 0 < (tau-t) < dt
+           # advanced time 
+           # tau > t-dt and tau < t --> t-dt < tau < t --> -dt < (tau-t) < 0 -> 0< t-tau < dt
 
            # self.t - self.tau = 0 -->  U_prev else  self.t -self.tau =dt -->  U 
 

### 2018-09-24 forward_problem.py
AMG added

@@ -51,9 +51,16 @@ def forward_problem(context):
     bc.apply(A)
 
     # Define solver. Use GMRES iterative method with AMG preconditioner.
-    solver = LinearSolver(mpi_comm_self(), "gmres")
+    solver = LinearSolver(mpi_comm_self(), "gmres", "amg")
     solver.set_operator(A)
+    solver.parameters['absolute_tolerance'] = 10**-6  
 
+    solver.parameters['maximum_iterations'] = 100  
+    solver.parameters['monitor_convergence'] = True  
+    solver.parameters['nonzero_initial_guess'] = False # this may be used to speed up  
+
+    solver.parameters['relative_tolerance'] = 10**-6
+    solver.parameters['report'] = True 
     while not context.should_stop():
         U_prev.assign(U,annotate =True)
         context.advance_time()

### 2018-09-24 forward_problem.py
AMG removed

@@ -51,7 +51,7 @@ def forward_problem(context):
     bc.apply(A)
 
     # Define solver. Use GMRES iterative method with AMG preconditioner.
-    solver = LinearSolver(mpi_comm_self(), "gmres", "amg")
+    solver = LinearSolver(mpi_comm_self(), "gmres")
     solver.set_operator(A)
     solver.parameters['absolute_tolerance'] = 10**-6  
 

### 2018-09-24 inverse3D-abel.sh

@@ -44,6 +44,6 @@ echo "${@:4}"
 cd $SCRATCH
 ls
 echo $SCRATCH
-python3 main.py --alpha $1 --beta $2 --noise $3 --k $4 --tau "${@:5}"
+python3 main.py --alpha $1 --beta $2 --noise $3 --K $4 --tau "${@:5}"
 
 

### 2018-09-24 tex/paper.tex
add text
update

@@
 
+\section*{Manufactured Solution}
 The manufactured observations was obtained by forward computation of Eq.\ref{Eq::PDE} with the Dirichlet boundary condition defined as
@@
 The forward simulation gave a total of 120 possible observation time points.
-These points will be denoted as $\tau$.
+These points
+will be denoted as $\tau$.
 
@@
 Then the use of T2 weighted MRI was used to segment the csf compartment surrounding the cerebral.
-The polyhedral surfaces was use of CGAL [?], was used to construed the the mesh.
+The polyhedral surfaces was used with CGAL[?] to construed the mesh.
 The computational requirement for the resulting mesh was significant, therefore a submesh was also constructed, see Fig.
-??
-.
+??.
 
-The first observation will be considered the initial conditions of the equation, additionally the initial conditions of the manufactured observations are not considered.  
-\begin{equation}
-\tau := \lbrace  0 < t  \leq 24.0\rbrace
-\end{equation}
-This means that the objective functional will consider one less observation.
-However, this can be modified by adding the initial conditions as a optimization parameter.
-This means the timesteps will not be the same as the manufactured solution.
+\section*{Implementation}
+The code used the FEniCS project to contruct the PDE, using backwards Euler time discretization and first order continuous galerkin finite elements.
+The module dolfin adjoint [?] was used to construct a reduced functional, and the optimization used the scipy optimize library to minimize the functional using L-BFGS-B algorithm.
 
-This incoherence will also be investigated, and an adaptive timestep approach can be considered dependent on the results.
+The implementation used the first observation as initial conditions of Eq.\ref{Eq::PDE}, and for each timestep, the next observation was used as the Dirichlet boundary conditions.
 
- Furthermore, the $g$ value will be sett equal to the next observation.
-
-The initial values of the optimalization was set to $1000,2,1$,
-
-P1 finite elements were used, and the dolfin adjoint [?] was used to construct a reduced function. Furthermore, the scipy optimize library was used to minimize the functional using L-BFGS-B algorithm.
+The initial values of the optimization algorithm was chosen to be $1,1,1$.
+Furthermore, to obtain faster convergence in the optimization, the diffusion coefficients was scaled to have the same magnitude, i.e.
+$D_{\Omega_1}$ was scaled, so that $D_{\Omega_1} = D\sp{u}_{\Omega_1}*100$.
 
 \section*{Non-linear relation}
-The MR images that are provided by Oslo University Hospital Rikshospitalet and can be seen in Fig.?? .
-
+The MR images are provided by Oslo University Hospital Rikshospitalet and can be seen in Fig.??.
 The software Freesurfer was used to segment and align each of the observations, which made it possible to estimate voxelwise intensity increase due to tracer concentrations.
-
-The relation between intensity and concentration is non-linear, and best be de
+The tracer causes the longitudinal(spin-lattice) relaxation time $T_{1}$ to shorten with the following relation
+\begin{equation}
+\frac{1}{T_{1}\sp{c}} = \frac{1}{T_{1}\sp{0}} + r_{1}*C .
+\label{EQ::contrast}
+\end{equation}
+with the superscripts indicating with contrast and without contrast and $r_1$ as the relaxivity constant for the MRI-contrast in a medium.
+The relation between intensity and concentration is non-linear, and is expressed with the following equations.
+The signal intensity $SI$ of the sequence is given by
+\begin{equation}
+SI = M_{n} \sin \theta e\sp{ - TE/T_2\sp{*} },
+\label{EQ::SI_T2}
+\end{equation}
+with  $TE$ and $\theta$ respectively denoting the echo time and the flip angle.
+Also $T2\sp{*}$ is transverse magnetization caused by a combination of spin-spin relaxation and magnetic field inhomogeneity.
+It is defined as
+\begin{equation}
+\frac{1}{T_2\sp{*}} = \frac{1}{T_2} + \gamma \Delta B_{in} ,
+\end{equation}
+with $T2$ transverse (spin-spin) relaxation time, $\gamma$ is the gyromagnetic ratio and $\Delta B_{in}$ is the magnetic field inhomogeneity
+across a voxel. % We will assume that the field inhomogeneity is constant.
+We will simplify the expression by neglecting the T2 term in the signal,
+given that $TE <<T_2\sp{*}$ for this MRI sequence. Thus Eq. \ref{EQ::SI_T2} becomes 
+\begin{equation}
+SI = M_{n} \sin \theta.
+\label{EQ::SI}
+\end{equation}
+In article [?] term $M_n$ is the magnetization in the the n-echo given as 
+\begin{equation}
+M_{n} = M_{0}  \left[ (1-\beta)\frac{(1-(\alpha \beta)\sp{n-1} }{1-\alpha\beta} + (\alpha \beta)\sp{n-1}(1-\gamma) + \gamma ( \alpha \beta)\sp{n-1} \frac{M_{e}}{M_{0}}  \right]   
+\end{equation}
+with 
+\begin{equation}
+\frac{M_{e}}{M_{0}} = - \left[ \frac{ 1 -\delta + \alpha \delta (1-\beta ) \frac{1-\alpha\beta\sp{m}}{1-\alpha \beta} + \alpha\delta(\alpha\beta)\sp{m-1} - \alpha\sp{m}\rho}{1 +\rho \alpha\sp{m} } \right].
+\end{equation}
+Using the following definitions
+\begin{equation}
+\begin{aligned}
+\alpha &= \cos ( \theta ) \\
+\beta  &= e\sp{- \sp{T_b}/_{T_1}\sp{0} } \\
+\delta &= e\sp{- \sp{T_a}/_{T_1}\sp{0} } \\
+\gamma &= e\sp{- \sp{T_w}/_{T_1}\sp{0} } \\
+\rho   &= e\sp{- \sp{TR}/_{T_1}\sp{0} }  \\
+T_w    &= TR - T_a -T_b(m-1)       .\\
+\end{aligned}
+\end{equation}
+Here $T_b$ is known as the echo spacing, $T_a$ is the inversion time, $T_w$ the time delay, $TR$ as the repetition time, $m$ is the number of echo spacings and $T1$ is the longitudinal(spin-lattice) relaxation time for a given medium.
+The $M_0$ is a calibration constant of the magnetization.
+The center echo denoted as $n=\sp{m}/_2$ will be the signal that we will consider when estimating MRI-contrast.
 
@@
 
- 0.0001 & 1.0 &20 &[0.2, 1.2, 2.4, 3.6, 4.8, 6.0, 7.2, 8.4, 9.6, 10.8, 12.0, 13.2, 14.4, 15.6, 16.8, 17.0, 19.2, 20.4, 21.6, 22.8, 24.0] & 153& 999.888464905 & 4.02189206656 & 8.01937098574 \\ 
- 0.0001 & 0.1 &20 &[0.2, 1.2, 2.4, 3.6, 4.8, 6.0, 7.2, 8.4, 9.6, 10.8, 12.0, 13.2, 14.4, 15.6, 16.8, 17.0, 19.2, 20.4, 21.6, 22.8, 24.0] & 82& 999.92653104 & 4.0172778853 & 8.02072488205 \\ 
- 0.0001 & 0.01 &20 &[0.2, 1.2, 2.4, 3.6, 4.8, 6.0, 7.2, 8.4, 9.6, 10.8, 12.0, 13.2, 14.4, 15.6, 16.8, 17.0, 19.2, 20.4, 21.6, 22.8, 24.0] & 183& 999.601435216 & 4.0167801622 & 8.02099543744 \\ 
- 1e-05 & 1.0 &20 &[0.2, 1.2, 2.4, 3.6, 4.8, 6.0, 7.2, 8.4, 9.6, 10.8, 12.0, 13.2, 14.4, 15.6, 16.8, 17.0, 19.2, 20.4, 21.6, 22.8, 24.0] & 170& 999.857251969 & 4.02183073053 & 8.0193786719 \\ 
- 1e-05 & 0.1 &20 &[0.2, 1.2, 2.4, 3.6, 4.8, 6.0, 7.2, 8.4, 9.6, 10.8, 12.0, 13.2, 14.4, 15.6, 16.8, 17.0, 19.2, 20.4, 21.6, 22.8, 24.0] & 145& 999.723425171 & 4.01725503821 & 8.02073378231 \\ 
- 1e-05 & 0.01 &20 &[0.2, 1.2, 2.4, 3.6, 4.8, 6.0, 7.2, 8.4, 9.6, 10.8, 12.0, 13.2, 14.4, 15.6, 16.8, 17.0, 19.2, 20.4, 21.6, 22.8, 24.0] & 189& 999.686295266 & 4.0167215691 & 8.02087841472 \\ 
- 1e-06 & 1.0 &20 &[0.2, 1.2, 2.4, 3.6, 4.8, 6.0, 7.2, 8.4, 9.6, 10.8, 12.0, 13.2, 14.4, 15.6, 16.8, 17.0, 19.2, 20.4, 21.6, 22.8, 24.0] & 252& 999.744572206 & 4.02186634423 & 8.01936617912 \\ 
- 1e-06 & 0.1 &20 &[0.2, 1.2, 2.4, 3.6, 4.8, 6.0, 7.2, 8.4, 9.6, 10.8, 12.0, 13.2, 14.4, 15.6, 16.8, 17.0, 19.2, 20.4, 21.6, 22.8, 24.0] & 167& 999.698939533 & 4.01722486087 & 8.02076770928 \\ 
- 1e-06 & 0.01 &20 &[0.2, 1.2, 2.4, 3.6, 4.8, 6.0, 7.2, 8.4, 9.6, 10.8, 12.0, 13.2, 14.4, 15.6, 16.8, 17.0, 19.2, 20.4, 21.6, 22.8, 24.0] & 145& 999.76147155 & 4.01667474386 & 8.02102893936 \\
-
  \begin{table}
@@
 
+In Fig.??, we let the 
+The addition of scaling the parameter $D_{\Omega_1}$ was done, such that all the diffusion parameters were in the same order of magnitude.
+
 There is a need for observable change in order to estimate the parameters.

### 2018-09-24 forward_problem.py
updates

@@ -53,14 +53,14 @@ def forward_problem(context):
     # Define solver. Use GMRES iterative method with AMG preconditioner.
     solver = LinearSolver(mpi_comm_self(), "gmres")
     solver.set_operator(A)
-    solver.parameters['absolute_tolerance'] = 10**-6  
+    #solver.parameters['absolute_tolerance'] = 10**-6  
 
-    solver.parameters['maximum_iterations'] = 100  
-    solver.parameters['monitor_convergence'] = True  
-    solver.parameters['nonzero_initial_guess'] = False # this may be used to speed up  
+    #solver.parameters['maximum_iterations'] = 100  
+    #solver.parameters['monitor_convergence'] = True  
+    #solver.parameters['nonzero_initial_guess'] = False # this may be used to speed up  
 
-    solver.parameters['relative_tolerance'] = 10**-6
-    solver.parameters['report'] = True 
+    #solver.parameters['relative_tolerance'] = 10**-6
+    #solver.parameters['report'] = True 
     while not context.should_stop():
         U_prev.assign(U,annotate =True)
         context.advance_time()
@@ -134,8 +134,11 @@ def functional(mesh_config, V, D, g_list, tau, obs_file, alpha=0.0, beta=0.0, gr
             self.noise = noise
  
             self.obs_file.read(self.ic, "%0.2f"%(self.t) )
-            self.gradient = [1.0, 1.0, 1.0]
-            
+
+            self.gradient = gradient 
+     
+
+  
         def initial_conditions(self):
             self.obs_file.read(self.ic, "%0.2f"%(self.tau[0]))
             if self.noise: 
@@ -144,6 +147,7 @@ def functional(mesh_config, V, D, g_list, tau, obs_file, alpha=0.0, beta=0.0, gr
 
         def scale(self, i):
             if self.gradient is not None:
+                print  ( abs(float(self.gradient[i])) ) 
                 return abs(float(self.gradient[i]))
             return 1.0
 

### 2018-09-24 main.py

@@ -79,6 +79,7 @@ if __name__ == "__main__":
     parser.add_argument('--noise', default=0.0, type=float)
     parser.add_argument('--tol', default=0.001, type=float)
     parser.add_argument('--D', default=[1, 1, 1], type=float, nargs=3)
+    parser.add_argument('--scale', default=[100, 1, 1], type=float, nargs=3)
     parser.add_argument('--mesh', default="mesh_invers_contrast.h5", type=str)
     parser.add_argument("--tau", nargs="+", type=float)
     parser.add_argument("--k",default=1, type=int)
@@ -125,7 +126,7 @@ if __name__ == "__main__":
         exit()
     else:
         g = bc_guess(g, Z.obs_file, tau, k, noise)
-        J = functional(mesh_config, V, D, g, tau, Z.obs_file, Z.alpha, Z.beta,None, noise=noise)
+        J = functional(mesh_config, V, D, g, tau, Z.obs_file, Z.alpha, Z.beta, noise=noise, gradient=Z.scale)
 
     ctrls = ([Control(D[i]) for i in range(1, 4)]
              + [Control(g_i) for g_i in g])

### 2018-09-27 tex/paper.tex
text update
Text update

--- 2018-09-15 tex/paper.tex
@@
 \usepackage{graphicx}
-
+\usepackage[table,x11names]{xcolor}
 \title{Assessing glymphatic transport velocities by adjoint methods}
@@
 \subsection*{Data}
+The data consist of a total of 10 MRI observations, including a baseline MRI taken before tracer was injected.
+The observation points are distributed with 5 observations within 1-2 hours after injection, 1 observation in the timeframes 2-4 hours, 6-9 hours, 24 hours and 48 hours.
 
@@
 \min_{u,g} F = \quad \sum\limits_i\sp{n} \int\limits_{\Omega} |u(t_i) - u_{obs}(t_i)| \mathrm{d}\Omega + \frac{\alpha}{2} \int\limits_{0}\sp{T} || g ||_{L\sp{2}(\partial\Omega)} \mathrm{d}t + \frac{\beta}{2} \int\limits_{0}\sp{T} || \dot{g} ||_{L\sp{2}(\partial\Omega)}\mathrm{d}t
+\label{EQ::objf}
 \end{equation}
@@
 The forward simulation gave a total of 120 possible observation time points.
-These points will be denoted as $\tau$.
+These points
+will be denoted as $\tau$.
 
-The mesh was constructed by using the MRI of a patient diagnosed with iNPH.
+The mesh is patient-specific and was constructed by using the MRI of a patient diagnosed with iNPH.
 The software Freesurfer was used in segmentation and creating the polyhedral surfaces of the white and grey matter.
 Then the use of T2 weighted MRI was used to segment the csf compartment surrounding the cerebral.
-The polyhedral surfaces was use of CGAL [?], was used to construed the the mesh.
+(BrainMesh code accessibility ?
+) CGAL[?] was used to combine the polyhedral surfaces and to construed the mesh.
 The computational requirement for the resulting mesh was significant, therefore a submesh was also constructed, see Fig.
-??
-.
+??.
 
-P1 finite elements were used, and the dolfin adjoint [?] was used to construct a reduced function. Furthermore, the scipy optimize library was used to minimize the functional using L-BFGS-B algorithm.
+\section*{Implementation}
+The code used the FEniCS project to sole the PDE, using backwards Euler time discretization and first order continuous Galerkin finite elements.
+The module dolfin adjoint [?] was used to compute the reduced functional, and the optimization used the scipy optimize library to minimize the functional using L-BFGS-B algorithm.
+
+The implementation used the first observation as initial conditions of Eq.\ref{Eq::PDE}, and for each timestep, the next observation was used as the Dirichlet boundary condition.
+The Dirichlet boundary condition was imposed on the external boundary for the domain $D_{\Omega_1}$.
+
+Linear interpolation of the forward problem was used to compute the difference from the observation,
+
+The initial values of the optimization algorithm was chosen to be $1,1,1$.
+Furthermore, to obtain faster convergence in the optimization, the diffusion coefficients was scaled to have the same magnitude, i.e.
+$D_{\Omega_1}$ was scaled, so that $D_{\Omega_1} = D\sp {s}_{\Omega_1}100$.
+
+The noise susceptibility was also tested by adding an uniform distribution noise term to the observations.
+The noise term was constructed using numpy random and multiplied with a noise amplitude.
+The noise amplitudes were chosen to be $ 5\%, 10\%, 50\%, 100\%$ of the maximum initial boundary conditions, so that negative concentrations are avoided.
 
 \section*{Non-linear relation}
-The MR images that are provided by Oslo University Hospital Rikshospitalet and can be seen in Fig.?? .
+The MR images are provided by Oslo University Hospital Rikshospitalet and can be seen in Fig.??.
+The software Freesurfer was used to segment and align each of the observations, which made it possible to estimate voxelwise intensity increase.
+The tracer causes the longitudinal(spin-lattice) relaxation time $T_{1}$ to shorten with the following relation
+\begin{equation}
+\frac{1}{T_{1}\sp{c}} = \frac{1}{T_{1}\sp{0}} + r_{1}*C .
+\label{EQ::contrast}
+\end{equation}
+The superscripts indicating with contrast and without contrast and $r_1$ as the relaxivity constant for the MRI-contrast in a medium.
+The relation between intensity and the relaxation time is non-linear, and is expressed with the following equations.
+The signal intensity $SI$ of the sequence is given by
+\begin{equation}
+SI = M_{n} \sin \theta e\sp{ - TE/T_2\sp{*} },
+\label{EQ::SI_T2}
+\end{equation}
+with  $TE$ and $\theta$ respectively denoting the echo time and the flip angle.
+Also $T2\sp{*}$ is transverse magnetization caused by a combination of spin-spin relaxation and magnetic field inhomogeneity.
+It is defined as
+\begin{equation}
+\frac{1}{T_2\sp{*}} = \frac{1}{T_2} + \gamma \Delta B_{in} ,
+\end{equation}
+with $T2$ transverse (spin-spin) relaxation time, $\gamma$ is the gyromagnetic ratio and $\Delta B_{in}$ is the magnetic field inhomogeneity across a voxel.
+The expression can be simplified by neglecting the $T2$ term in the signal, since $TE <<T_2\sp{*}$ for this MRI sequence.
+Thus Eq.
+\ref{EQ::SI_T2} becomes
+\begin{equation}
+SI = M_{n} \sin \theta.
+\label{EQ::SI}
+\end{equation}
+In article [?], the term $M_n$ is defined as the magnetization for the n-echo 
+\begin{equation}
+M_{n} = M_{0}  \left[ (1-\beta)\frac{(1-(\alpha \beta)\sp{n-1} }{1-\alpha\beta} + (\alpha \beta)\sp{n-1}(1-\gamma) + \gamma ( \alpha \beta)\sp{n-1} \frac{M_{e}}{M_{0}}  \right]   
+\end{equation}
+with 
+\begin{equation}
+\frac{M_{e}}{M_{0}} = - \left[ \frac{ 1 -\delta + \alpha \delta (1-\beta ) \frac{1-\alpha\beta\sp{m}}{1-\alpha \beta} + \alpha\delta(\alpha\beta)\sp{m-1} - \alpha\sp{m}\rho}{1 +\rho \alpha\sp{m} } \right].
+\end{equation}
+Using the following definitions
+\begin{equation}
+\begin{aligned}
+\alpha &= \cos ( \theta ) \\
+\beta  &= e\sp{- \sp{T_b}/_{T_1}\sp{0} } \\
+\delta &= e\sp{- \sp{T_a}/_{T_1}\sp{0} } \\
+\gamma &= e\sp{- \sp{T_w}/_{T_1}\sp{0} } \\
+\rho   &= e\sp{- \sp{TR}/_{T_1}\sp{0} }  \\
+T_w    &= TR - T_a -T_b(m-1)       .\\
+\end{aligned}
+\end{equation}
+Here $T_b$ is known as the echo spacing, $T_a$ is the inversion time, $T_w$ the time delay, $TR$ as the repetition time, $m$ is the number of echo spacings and $T1$ is the longitudinal(spin-lattice) relaxation time for a given medium.
+The $M_0$ is a calibration constant of the magnetization.
+The center echo denoted as $n=\sp{m}/_2$ will be the signal that we will consider when estimating MRI-contrast.
+Given Eq.\ref{EQ::SI} we have that relative intensity increase can be written as
+\begin{equation}
+\frac{SI\sp{c}}{SI\sp{0}} = \frac{ M_{n}\sp{c} \sin (\theta)}{ M_{n}\sp{0} \sin (\theta) } ,
+\end{equation}
+We define that  
+\begin{equation}
+f(T_1) = M_{n}/M_{0} ,
+\label{FIG::F}
+\end{equation}
+which gives the following relation 
+\begin{equation}
+\frac{f(T_{1}\sp{c} ) }{f(T_{1}\sp{0})}  = \frac{SI\sp{c}}{SI\sp{0}} 
+\end{equation}
+Thus we can express the $T_1$ change due to contrast as 
+\begin{equation}
+f ( T_{1}\sp{c} ) = \frac{SI\sp{c}}{SI\sp{0}} f(T_{1}\sp{0}) 
+\end{equation}
+and we can then estimate concentration using Eq.\ref{EQ::contrast} if we know $T_{1}\sp{0}$. The $T_{1}\sp{0}$ was obtained using MRI.
 
-The software Freesurfer was used to segment and align each of the observations, which made it possible to estimate voxelwise intensity increase due to tracer concentrations.
-
-The relation between intensity and concentration is non-linear, and best be de
-
+The convergence of L-BFGS-B algorithm can be seen in Fig.??. 
 \begin{itemize}
@@
 
-The results.
-
-The optimal relaxation parameters was investigated by using 10 evenly spaced time points as observations. Then estimate the corresponding controls, while varying the relaxation parameters.
-
-The dependency on the spacing and distribution of $tau$ was done by using the optimal relaxation parameters and consider number of time points equal to the number of observations.
-
-The dependency of time steps were computed by increasing the times
-
-The dependency on noise was done by adding randomly distributed noise to the observations.
-
-There are some extreme cases that require some considerations, namely :
-
-no observations around 12, i.e. can the parameters be estimated if there exists a hole in the observations.
-
-Is estimating parameters between 2
 \begin{table}
 \centering
-\caption{ }
+\caption{Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$ and number of observation $\tau$ with the resulting number of iterations and estimated optimal parameters for the diffusion coefficients.
+}
 \resizebox{\textwidth}{!}{\begin{tabular}{*{8}c}
-$\alpha$ & $\beta$ & k & $\tau$ & iter & $ D_{\Omega_1} = 1000$ & $ D_{\Omega_2} = 4.0 $ & $D_{\Omega_3} = 8.0 $ \\
+$\alpha$ & $\beta$ & k  & iter & $ D_{\Omega_1} = 1000$ & $ D_{\Omega_2} = 4.0 $ & $D_{\Omega_3} = 8.0 $ & $g$ \\
 \hline
- 1.0 & 1.0 &10 &10 & 801& 3152.55150305 & 5.66843317507 & 9.10176601537 \\
- 1.0 & 0.1 &10 &10 & 846& 2890.10652122 & 5.8333990243 & 9.14516904881   \\
- 1.0 & 0.01 &10 &10 & 1001& 2374.75510786 & 5.90748588887 & 9.1624514977  \\ 
- 1.0 & 0.001 &10 &10 & 987& 3012.94145621 & 5.84828588848 & 9.14780994071 \\
- 1.0 & 0.0001 &10 &10 & 1001& 2846.67368004 & 5.86716070687 & 9.1516059019 \\
- 1.0 & 1e-05 &10 &10 & 1001& 2488.99687704 & 5.89553108585 & 9.16094907807 \\
- 1.0 & 1e-06 &10 &10 & 1001& 2572.74685463 & 5.88550285289 & 9.15701445733 \\
- 0.1 & 1.0 &10 &10 & 525& 1165.00025805 & 4.55541673123 & 8.51469574502 \\
- 0.1 & 0.1 &10 &10 & 899& 1098.5603179 & 4.5965351918 & 8.60353462124 \\
- 0.1 & 0.01 &10 &10 & 792& 1148.68286947 & 4.58961131725 & 8.60923608344 \\ 
- 0.1 & 0.001 &10 &10 & 768& 1133.11485657 & 4.59512891707 & 8.61427396989 \\
- 0.1 & 0.0001 &10 &10 & 840& 1152.61459776 & 4.5895138786 & 8.61107565287 \\
- 0.1 & 1e-05 &10 &10 & 739& 1145.12699776 & 4.59168203791 & 8.61245925367 \\
- 0.1 & 1e-06 &10 &10 & 697& 1127.51137739 & 4.59724924241 & 8.6163255093 \\
- 0.01 & 1.0 &10 &10 & 130& 1000.69417631 & 4.45194182806 & 8.48016213899 \\
- 0.01 & 0.1 &10 &10 & 204& 1001.45906364 & 4.44288397852 & 8.55964437402 \\
- 0.01 & 0.01 &10 &10 & 384& 1004.91771072 & 4.44039285507 & 8.57773362809 \\
- 0.01 & 0.001 &10 &10 & 455& 1006.92821746 & 4.4401364227 & 8.57964644068 \\
- 0.01 & 0.0001 &10 &10 & 382& 1005.46132856 & 4.44059403278 & 8.58161935877 \\
- 0.01 & 1e-05 &10 &10 & 389& 1005.48872458 & 4.44091328174 & 8.58070451064 \\
- 0.01 & 1e-06 &10 &10 & 320& 1003.88180045 & 4.44140148563 & 8.57914151398 \\
- 0.001 & 1.0 &10 &10 & 144& 1000.72690068 & 4.43617090765 & 8.47356658247 \\
- 0.001 & 0.1 &10 &10 & 188& 1001.11632883 & 4.42560354452 & 8.55339645884 \\
- 0.001 & 0.01 &10 &10 & 242& 1002.06937059 & 4.42388003439 & 8.57511846108 \\
- 0.001 & 0.001 &10 &10 & 332& 1005.24945351 & 4.42278572482 & 8.58013052115 \\
- 0.001 & 0.0001 &10 &10 & 432& 1008.05660576 & 4.42186842634 & 8.58305135552 \\
- 0.001 & 1e-05 &10 &10 & 360& 1006.05061062 & 4.42295196846 & 8.57964172911 \\
- 0.001 & 1e-06 &10 &10 & 363& 1006.70468432 & 4.42251369108 & 8.58151348789 \\
- 0.0001 & 1.0 &10 &10 & 157& 1000.83218743 & 4.43452507573 & 8.47318916943 \\
- 0.0001 & 0.1 &10 &10 & 131& 1000.56624899 & 4.42351929725 & 8.55256760219 \\
- 0.0001 & 0.01 &10 &10 & 174& 1001.0091989 & 4.42260942583 & 8.57478259945 \\
- 0.0001 & 0.001 &10 &10 & 136& 1000.57577092 & 4.4239534819 & 8.57151355191 \\
- 0.0001 & 0.0001 &10 &10 & 283& 1003.03255695 & 4.42248562737 & 8.5786695754 \\
- 0.0001 & 1e-05 &10 &10 & 284& 1003.54402535 & 4.42227734882 & 8.58311915306 \\
- 0.0001 & 1e-06 &10 &10 & 289& 1003.03642353 & 4.42224580212 & 8.58006825258 \\
- 1e-05 & 1.0 &10 &10 & 151& 1000.79310038 & 4.43448500449 & 8.47338153139 \\
- 1e-05 & 0.1 &10 &10 & 140& 1000.70858373 & 4.42340629909 & 8.55312689863 \\
- 1e-05 & 0.01 &10 &10 & 203& 1001.34714912 & 4.42253540005 & 8.57470943099 \\
- 1e-05 & 0.001 &10 &10 & 215& 1001.75591211 & 4.42292580709 & 8.58079455564 \\
- 1e-05 & 0.0001 &10 &10 & 208& 1001.41103854 & 4.42264942624 & 8.58064686718 \\
- 1e-05 & 1e-05 &10 &10 & 218& 1001.73103534 & 4.42318548221 & 8.57843152546 \\
- 1e-05 & 1e-06 &10 &10 & 191& 1001.33680306 & 4.42244263068 & 8.58128891831 \\
- 1e-06 & 1.0 &10 &10 & 115& 1000.47868283 & 4.43456295486 & 8.47226911091 \\
- 1e-06 & 0.1 &10 &10 & 158& 1000.8203239 & 4.42368702618 & 8.55236552474 \\
- 1e-06 & 0.01 &10 &10 & 142& 1000.64224198 & 4.42327990324 & 8.57047799569 \\
- 1e-06 & 0.001 &10 &10 & 149& 1000.64956243 & 4.42317461499 & 8.57554522252 \\
- 1e-06 & 0.0001 &10 &10 & 179& 1001.07075407 & 4.42262619987 & 8.57788936678 \\
- 1e-06 & 1e-05 &10 &10 & 254& 1002.49656481 & 4.42254606227 & 8.58162265954 \\
- 1e-06 & 1e-06 &10 &10 & 228& 1001.78781526 & 4.42297193581 & 8.57946804203 \\
+\rowcolor{red} 1.0e+00 	 & 1.0e+00 	 & 10 & 239 	 & +4.227 & +0.304 & +0.092 & +0.589 \\ 
+\rowcolor{red} 1.0e+00 	 & 1.0e-01 	 & 10 & 234 	 & +4.272 & +0.305 & +0.091 & +0.596 \\ 
+\rowcolor{red} 1.0e+00 	 & 1.0e-02 	 & 10 & 225 	 & +4.271 & +0.305 & +0.091 & +0.597 \\ 
+\rowcolor{red} 1.0e+00 	 & 1.0e-03 	 & 10 & 235 	 & +4.600 & +0.304 & +0.090 & +0.597 \\ 
+\rowcolor{red} 1.0e+00 	 & 1.0e-04 	 & 10 & 207 	 & +4.489 & +0.304 & +0.090 & +0.597 \\ 
+\rowcolor{red} 1.0e+00 	 & 1.0e-05 	 & 10 & 193 	 & +4.271 & +0.305 & +0.090 & +0.597 \\ 
+\rowcolor{red} 1.0e+00 	 & 1.0e-06 	 & 10 & 184 	 & +4.460 & +0.304 & +0.090 & +0.597 \\ 
+ 1.0e-01 	 & 1.0e+00 	 & 10 & 166 	 & +0.128 & +0.093 & +0.041 & +0.488 \\ 
+ 1.0e-01 	 & 1.0e-01 	 & 10 & 162 	 & +0.122 & +0.093 & +0.041 & +0.506 \\ 
+ 1.0e-01 	 & 1.0e-02 	 & 10 & 180 	 & +0.122 & +0.093 & +0.041 & +0.515 \\ 
+ 1.0e-01 	 & 1.0e-03 	 & 10 & 183 	 & +0.123 & +0.093 & +0.041 & +0.516 \\ 
+ 1.0e-01 	 & 1.0e-04 	 & 10 & 188 	 & +0.123 & +0.093 & +0.040 & +0.516 \\ 
+ 1.0e-01 	 & 1.0e-05 	 & 10 & 198 	 & +0.123 & +0.093 & +0.040 & +0.516 \\ 
+ 1.0e-02 	 & 1.0e+00 	 & 10 & 153 	 & +0.015 & +0.067 & +0.039 & +0.481 \\ 
+ 1.0e-02 	 & 1.0e-01 	 & 10 & 166 	 & +0.005 & +0.065 & +0.039 & +0.483 \\ 
+ 1.0e-02 	 & 1.0e-02 	 & 10 & 222 	 & +0.005 & +0.065 & +0.039 & +0.501 \\ 
+ 1.0e-02 	 & 1.0e-03 	 & 10 & 227 	 & +0.005 & +0.065 & +0.039 & +0.510 \\ 
+ 1.0e-02 	 & 1.0e-04 	 & 10 & 163 	 & +0.006 & +0.065 & +0.039 & +0.509 \\ 
+ 1.0e-02 	 & 1.0e-05 	 & 10 & 188 	 & +0.005 & +0.065 & +0.039 & +0.510 \\ 
+ 1.0e-03 	 & 1.0e+00 	 & 10 & 168 	 & +0.005 & +0.064 & +0.039 & +0.481 \\ 
+ 1.0e-03 	 & 1.0e-01 	 & 10 & 230 	 & -0.005 & +0.063 & +0.039 & +0.481 \\ 
+ 1.0e-03 	 & 1.0e-02 	 & 10 & 89 	 & -0.007 & +0.063 & +0.039 & +0.488 \\ 
+ 1.0e-03 	 & 1.0e-03 	 & 10 & 77 	 & -0.005 & +0.062 & +0.039 & +0.488 \\ 
+ 1.0e-03 	 & 1.0e-04 	 & 10 & 107 	 & -0.006 & +0.062 & +0.039 & +0.489 \\ 
+ 1.0e-03 	 & 1.0e-05 	 & 10 & 140 	 & -0.006 & +0.062 & +0.039 & +0.490 \\ 
+ 1.0e-04 	 & 1.0e+00 	 & 10 & 179 	 & +0.003 & +0.064 & +0.039 & +0.481 \\ 
+ 1.0e-04 	 & 1.0e-01 	 & 10 & 215 	 & -0.005 & +0.062 & +0.039 & +0.481 \\ 
+ 1.0e-04 	 & 1.0e-02 	 & 10 & 190 	 & -0.007 & +0.062 & +0.039 & +0.482 \\ 
+ 1.0e-04 	 & 1.0e-03 	 & 10 & 124 	 & -0.008 & +0.062 & +0.039 & +0.488 \\ 
+ 1.0e-04 	 & 1.0e-04 	 & 10 & 106 	 & -0.007 & +0.062 & +0.039 & +0.488 \\ 
+ 1.0e-04 	 & 1.0e-05 	 & 10 & 97 	 & -0.008 & +0.062 & +0.039 & +0.488 \\ 
+ 1.0e-05 	 & 1.0e+00 	 & 10 & 193 	 & +0.003 & +0.064 & +0.039 & +0.481 \\ 
+ 1.0e-05 	 & 1.0e-01 	 & 10 & 174 	 & -0.007 & +0.062 & +0.039 & +0.481 \\ 
+ 1.0e-05 	 & 1.0e-02 	 & 10 & 180 	 & -0.008 & +0.062 & +0.039 & +0.482 \\ 
+ 1.0e-05 	 & 1.0e-03 	 & 10 & 70 	 & -0.007 & +0.062 & +0.039 & +0.488 \\ 
+ 1.0e-05 	 & 1.0e-04 	 & 10 & 77 	 & -0.007 & +0.062 & +0.039 & +0.488 \\ 
+ 1.0e-05 	 & 1.0e-05 	 & 10 & 100 	 & -0.008 & +0.062 & +0.039 & +0.488 \\ 
+ 1.0e-06 	 & 1.0e+00 	 & 10 & 209 	 & +0.004 & +0.064 & +0.039 & +0.482 \\ 
+ 1.0e-06 	 & 1.0e-01 	 & 10 & 187 	 & -0.006 & +0.062 & +0.039 & +0.481 \\ 
+ 1.0e-06 	 & 1.0e-02 	 & 10 & 205 	 & -0.008 & +0.062 & +0.039 & +0.482 \\ 
+ 1.0e-06 	 & 1.0e-03 	 & 10 & 79 	 & -0.006 & +0.062 & +0.039 & +0.488 \\ 
+ 1.0e-06 	 & 1.0e-04 	 & 10 & 107 	 & -0.007 & +0.062 & +0.039 & +0.488 \\ 
+ 1.0e-06 	 & 1.0e-05 	 & 10 & 110 	 & -0.007 & +0.062 & +0.039 & +0.488 \\ 
 \end{tabular}}
@@
 
+\begin{table}
+\centering
+\caption{Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$ and number of observation $\tau$ with the resulting number of iterations and estimated optimal parameters for the diffusion coefficients.
+}
+\resizebox{\textwidth}{!}{\begin{tabular}{*{8}c}
+$\alpha$ & $\beta$ & k  & iter & $ D_{\Omega_1} = 1000$ & $ D_{\Omega_2} = 4.0 $ & $D_{\Omega_3} = 8.0 $ & $g$ \\
+\hline
+ 1.0e-01 	 & 1.0e+00 	 & 20 & 221 	 & +0.155 & +0.056 & +0.020 & +0.464 \\ 
+ 1.0e-01 	 & 1.0e-01 	 & 20 & 218 	 & +0.422 & +0.185 & +0.029 & +0.485 \\ 
+ 1.0e-01 	 & 1.0e-02 	 & 20 & 332 	 & +0.925 & +0.484 & +0.047 & +0.569 \\ 
+ 1.0e-01 	 & 1.0e-03 	 & 20 & 327 	 & +1.140 & +0.629 & +0.057 & +0.608 \\ 
+ 1.0e-01 	 & 1.0e-04 	 & 20 & 320 	 & +1.175 & +0.652 & +0.059 & +0.615 \\ 
+ 1.0e-01 	 & 1.0e-05 	 & 20 & 308 	 & +1.173 & +0.654 & +0.059 & +0.615 \\ 
+ 1.0e-02 	 & 1.0e+00 	 & 20 & 251 	 & +0.008 & +0.009 & +0.014 & +0.460 \\ 
+ 1.0e-02 	 & 1.0e-01 	 & 20 & 214 	 & +0.062 & +0.029 & +0.009 & +0.457 \\ 
+ 1.0e-02 	 & 1.0e-02 	 & 20 & 331 	 & +0.155 & +0.080 & +0.003 & +0.475 \\ 
+ 1.0e-02 	 & 1.0e-03 	 & 20 & 537 	 & +0.209 & +0.113 & -0.000 & +0.537 \\ 
+ 1.0e-02 	 & 1.0e-04 	 & 20 & 488 	 & +0.222 & +0.122 & -0.001 & +0.561 \\ 
+ 1.0e-02 	 & 1.0e-05 	 & 20 & 512 	 & +0.223 & +0.121 & -0.001 & +0.567 \\ 
+ 1.0e-03 	 & 1.0e+00 	 & 20 & 256 	 & -0.006 & +0.004 & +0.013 & +0.461 \\ 
+ 1.0e-03 	 & 1.0e-01 	 & 20 & 258 	 & +0.032 & +0.012 & +0.008 & +0.459 \\ 
+ 1.0e-03 	 & 1.0e-02 	 & 20 & 287 	 & +0.077 & +0.029 & +0.005 & +0.458 \\ 
+ 1.0e-03 	 & 1.0e-03 	 & 20 & 331 	 & +0.107 & +0.044 & +0.003 & +0.471 \\ 
+ 1.0e-03 	 & 1.0e-04 	 & 20 & 576 	 & +0.095 & +0.041 & +0.004 & +0.520 \\ 
+ 1.0e-03 	 & 1.0e-05 	 & 20 & 507 	 & +0.089 & +0.044 & +0.004 & +0.530 \\ 
+ 1.0e-04 	 & 1.0e+00 	 & 20 & 187 	 & -0.007 & +0.004 & +0.013 & +0.461 \\ 
+ 1.0e-04 	 & 1.0e-01 	 & 20 & 315 	 & +0.028 & +0.010 & +0.008 & +0.459 \\ 
+ 1.0e-04 	 & 1.0e-02 	 & 20 & 396 	 & +0.067 & +0.023 & +0.005 & +0.459 \\ 
+ 1.0e-04 	 & 1.0e-03 	 & 20 & 242 	 & +0.103 & +0.038 & +0.003 & +0.463 \\ 
+ 1.0e-04 	 & 1.0e-04 	 & 20 & 207 	 & +0.100 & +0.035 & +0.003 & +0.466 \\ 
+ 1.0e-04 	 & 1.0e-05 	 & 20 & 457 	 & +0.080 & +0.035 & +0.003 & +0.483 \\ 
+ 1.0e-05 	 & 1.0e+00 	 & 20 & 215 	 & -0.006 & +0.004 & +0.013 & +0.461 \\ 
+ 1.0e-05 	 & 1.0e-01 	 & 20 & 244 	 & +0.028 & +0.010 & +0.008 & +0.459 \\ 
+ 1.0e-05 	 & 1.0e-02 	 & 20 & 399 	 & +0.070 & +0.024 & +0.005 & +0.460 \\ 
+ 1.0e-05 	 & 1.0e-03 	 & 20 & 267 	 & +0.108 & +0.040 & +0.003 & +0.463 \\ 
+ 1.0e-05 	 & 1.0e-04 	 & 20 & 361 	 & +0.089 & +0.034 & +0.003 & +0.473 \\ 
+ 1.0e-05 	 & 1.0e-05 	 & 20 & 298 	 & +0.101 & +0.036 & +0.003 & +0.473 \\ 
+ 1.0e-06 	 & 1.0e+00 	 & 20 & 240 	 & -0.007 & +0.004 & +0.013 & +0.461 \\ 
+ 1.0e-06 	 & 1.0e-01 	 & 20 & 269 	 & +0.027 & +0.009 & +0.008 & +0.459 \\ 
+ 1.0e-06 	 & 1.0e-02 	 & 20 & 314 	 & +0.070 & +0.025 & +0.005 & +0.459 \\ 
+ 1.0e-06 	 & 1.0e-03 	 & 20 & 214 	 & +0.102 & +0.038 & +0.002 & +0.462 \\ 
+ 1.0e-06 	 & 1.0e-04 	 & 20 & 437 	 & +0.079 & +0.032 & +0.004 & +0.475 \\ 
+ 1.0e-06 	 & 1.0e-05 	 & 20 & 353 	 & +0.088 & +0.033 & +0.005 & +0.478 \\ 
+\end{tabular}}
+\label{Tab::1}
+\end{table}
+
+\begin{table}
+\centering
+\caption{Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$ and number of observation $\tau$ with the resulting number of iterations and estimated optimal parameters for the diffusion coefficients.
+Noise 0.015 amp }
+\resizebox{\textwidth}{!}{\begin{tabular}{*{8}c}
+$\alpha$ & $\beta$ & k  & iter & $ D_{\Omega_1} $ & $ D_{\Omega_2} $ & $D_{\Omega_3} $ & $g$ \\
+\hline
+ 1.0e+00 	 & 1.0e+00 	 & 10 & 205 	 & +4.270 & +0.303 & +0.091 & +0.589 \\ 
+ 1.0e+00 	 & 1.0e-01 	 & 10 & 190 	 & +4.270 & +0.306 & +0.091 & +0.596 \\ 
+ 1.0e+00 	 & 1.0e-02 	 & 10 & 244 	 & +4.523 & +0.304 & +0.091 & +0.597 \\ 
+ 1.0e+00 	 & 1.0e-03 	 & 10 & 204 	 & +4.275 & +0.306 & +0.091 & +0.597 \\ 
+ 1.0e+00 	 & 1.0e-04 	 & 10 & 205 	 & +4.272 & +0.306 & +0.090 & +0.597 \\ 
+ 1.0e+00 	 & 1.0e-05 	 & 10 & 185 	 & +4.272 & +0.305 & +0.090 & +0.597 \\ 
+ 1.0e+00 	 & 1.0e-06 	 & 10 & 223 	 & +4.538 & +0.303 & +0.091 & +0.597 \\ 
+ 1.0e-01 	 & 1.0e+00 	 & 10 & 179 	 & +0.125 & +0.095 & +0.040 & +0.488 \\ 
+ 1.0e-01 	 & 1.0e-01 	 & 10 & 141 	 & +0.123 & +0.093 & +0.040 & +0.506 \\ 
+ 1.0e-01 	 & 1.0e-02 	 & 10 & 201 	 & +0.124 & +0.093 & +0.040 & +0.515 \\ 
+ 1.0e-01 	 & 1.0e-03 	 & 10 & 207 	 & +0.126 & +0.093 & +0.041 & +0.516 \\ 
+ 1.0e-01 	 & 1.0e-04 	 & 10 & 162 	 & +0.125 & +0.093 & +0.040 & +0.516 \\ 
+ 1.0e-01 	 & 1.0e-05 	 & 10 & 209 	 & +0.121 & +0.093 & +0.041 & +0.516 \\ 
+ 1.0e-01 	 & 1.0e-06 	 & 10 & 147 	 & +0.123 & +0.093 & +0.041 & +0.516 \\ 
+ 1.0e-02 	 & 1.0e+00 	 & 10 & 221 	 & +0.017 & +0.067 & +0.039 & +0.481 \\ 
+ 1.0e-02 	 & 1.0e-01 	 & 10 & 138 	 & +0.005 & +0.065 & +0.040 & +0.483 \\ 
+ 1.0e-02 	 & 1.0e-02 	 & 10 & 174 	 & +0.006 & +0.065 & +0.040 & +0.500 \\ 
+ 1.0e-02 	 & 1.0e-03 	 & 10 & 227 	 & +0.007 & +0.066 & +0.039 & +0.510 \\ 
+ 1.0e-02 	 & 1.0e-04 	 & 10 & 164 	 & +0.004 & +0.065 & +0.040 & +0.509 \\ 
+ 1.0e-02 	 & 1.0e-05 	 & 10 & 223 	 & +0.006 & +0.065 & +0.040 & +0.512 \\ 
+ 1.0e-02 	 & 1.0e-06 	 & 10 & 179 	 & +0.007 & +0.065 & +0.040 & +0.510 \\ 
+ 1.0e-03 	 & 1.0e+00 	 & 10 & 178 	 & +0.005 & +0.064 & +0.039 & +0.481 \\ 
+ 1.0e-03 	 & 1.0e-01 	 & 10 & 182 	 & -0.007 & +0.062 & +0.040 & +0.481 \\ 
+ 1.0e-03 	 & 1.0e-02 	 & 10 & 94 	 & -0.006 & +0.062 & +0.038 & +0.487 \\ 
+ 1.0e-03 	 & 1.0e-03 	 & 10 & 108 	 & -0.005 & +0.063 & +0.039 & +0.489 \\ 
+ 1.0e-03 	 & 1.0e-04 	 & 10 & 136 	 & -0.008 & +0.062 & +0.040 & +0.490 \\ 
+ 1.0e-03 	 & 1.0e-05 	 & 10 & 93 	 & -0.006 & +0.063 & +0.040 & +0.489 \\ 
+ 1.0e-03 	 & 1.0e-06 	 & 10 & 81 	 & -0.006 & +0.062 & +0.040 & +0.489 \\ 
+ 1.0e-04 	 & 1.0e+00 	 & 10 & 166 	 & +0.007 & +0.064 & +0.039 & +0.482 \\ 
+ 1.0e-04 	 & 1.0e-01 	 & 10 & 273 	 & -0.007 & +0.062 & +0.040 & +0.481 \\ 
+ 1.0e-04 	 & 1.0e-02 	 & 10 & 103 	 & -0.004 & +0.062 & +0.040 & +0.487 \\ 
+ 1.0e-04 	 & 1.0e-03 	 & 10 & 147 	 & -0.008 & +0.062 & +0.039 & +0.488 \\ 
+ 1.0e-04 	 & 1.0e-04 	 & 10 & 103 	 & -0.007 & +0.062 & +0.039 & +0.488 \\ 
+ 1.0e-04 	 & 1.0e-05 	 & 10 & 136 	 & -0.007 & +0.063 & +0.039 & +0.488 \\ 
+ 1.0e-04 	 & 1.0e-06 	 & 10 & 103 	 & -0.010 & +0.062 & +0.040 & +0.488 \\ 
+ 1.0e-05 	 & 1.0e+00 	 & 10 & 230 	 & +0.001 & +0.064 & +0.038 & +0.482 \\ 
+ 1.0e-05 	 & 1.0e-01 	 & 10 & 237 	 & -0.009 & +0.062 & +0.040 & +0.481 \\ 
+ 1.0e-05 	 & 1.0e-02 	 & 10 & 172 	 & -0.008 & +0.062 & +0.039 & +0.482 \\ 
+ 1.0e-05 	 & 1.0e-03 	 & 10 & 116 	 & -0.009 & +0.063 & +0.039 & +0.488 \\ 
+ 1.0e-05 	 & 1.0e-04 	 & 10 & 124 	 & -0.007 & +0.062 & +0.040 & +0.488 \\ 
+ 1.0e-05 	 & 1.0e-05 	 & 10 & 97 	 & -0.007 & +0.063 & +0.038 & +0.488 \\ 
+ 1.0e-05 	 & 1.0e-06 	 & 10 & 129 	 & -0.007 & +0.062 & +0.039 & +0.488 \\ 
+ 1.0e-06 	 & 1.0e+00 	 & 10 & 199 	 & +0.002 & +0.063 & +0.039 & +0.482 \\ 
+ 1.0e-06 	 & 1.0e-01 	 & 10 & 245 	 & -0.005 & +0.063 & +0.039 & +0.481 \\ 
+ 1.0e-06 	 & 1.0e-02 	 & 10 & 206 	 & -0.003 & +0.062 & +0.039 & +0.482 \\ 
+ 1.0e-06 	 & 1.0e-03 	 & 10 & 159 	 & -0.007 & +0.062 & +0.040 & +0.488 \\ 
+ 1.0e-06 	 & 1.0e-04 	 & 10 & 124 	 & -0.011 & +0.062 & +0.040 & +0.488 \\ 
+ 1.0e-06 	 & 1.0e-05 	 & 10 & 93 	 & -0.007 & +0.061 & +0.039 & +0.488 \\ 
+ 1.0e-06 	 & 1.0e-06 	 & 10 & 115 	 & -0.009 & +0.062 & +0.039 & +0.488 \\ 
+\end{tabular}}
+\label{Tab::1}
+\end{table}
+
+\begin{table}
+\centering
+\caption{Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$ and number of observation $\tau$ with the resulting number of iterations and estimated optimal parameters for the diffusion coefficients.
+Noise 0.15 amp }
+\resizebox{\textwidth}{!}{\begin{tabular}{*{8}c}
+$\alpha$ & $\beta$ & k  & iter & $ D_{\Omega_1} $ & $ D_{\Omega_2} $ & $D_{\Omega_3} $ & $g$ \\
+\hline
+ 1.0e+00 	 & 1.0e+00 	 & 10 & 215 	 & +4.279 & +0.304 & +0.089 & +0.592 \\ 
+ 1.0e+00 	 & 1.0e-01 	 & 10 & 174 	 & +3.667 & +0.319 & +0.092 & +0.599 \\ 
+ 1.0e+00 	 & 1.0e-02 	 & 10 & 168 	 & +3.722 & +0.311 & +0.087 & +0.600 \\ 
+ 1.0e+00 	 & 1.0e-03 	 & 10 & 197 	 & +4.219 & +0.305 & +0.092 & +0.601 \\ 
+ 1.0e+00 	 & 1.0e-04 	 & 10 & 200 	 & +4.302 & +0.295 & +0.095 & +0.601 \\ 
+ 1.0e+00 	 & 1.0e-05 	 & 10 & 190 	 & +4.281 & +0.307 & +0.090 & +0.601 \\ 
+ 1.0e+00 	 & 1.0e-06 	 & 10 & 211 	 & +4.310 & +0.301 & +0.085 & +0.600 \\ 
+ 1.0e-01 	 & 1.0e+00 	 & 10 & 126 	 & +0.129 & +0.092 & +0.039 & +0.493 \\ 
+ 1.0e-01 	 & 1.0e-01 	 & 10 & 205 	 & +0.134 & +0.091 & +0.047 & +0.512 \\ 
+ 1.0e-01 	 & 1.0e-02 	 & 10 & 232 	 & +0.150 & +0.093 & +0.042 & +0.521 \\ 
+ 1.0e-01 	 & 1.0e-03 	 & 10 & 219 	 & +0.155 & +0.085 & +0.040 & +0.524 \\ 
+ 1.0e-01 	 & 1.0e-04 	 & 10 & 181 	 & +0.153 & +0.091 & +0.040 & +0.523 \\ 
+ 1.0e-01 	 & 1.0e-05 	 & 10 & 176 	 & +0.111 & +0.098 & +0.037 & +0.523 \\ 
+ 1.0e-01 	 & 1.0e-06 	 & 10 & 151 	 & +0.155 & +0.092 & +0.043 & +0.523 \\ 
+ 1.0e-02 	 & 1.0e+00 	 & 10 & 214 	 & +0.014 & +0.066 & +0.038 & +0.486 \\ 
+ 1.0e-02 	 & 1.0e-01 	 & 10 & 139 	 & +0.007 & +0.072 & +0.034 & +0.490 \\ 
+ 1.0e-02 	 & 1.0e-02 	 & 10 & 235 	 & +0.032 & +0.076 & +0.041 & +0.512 \\ 
+ 1.0e-02 	 & 1.0e-03 	 & 10 & 282 	 & +0.002 & +0.067 & +0.041 & +0.519 \\ 
+ 1.0e-02 	 & 1.0e-04 	 & 10 & 353 	 & +0.002 & +0.060 & +0.043 & +0.523 \\ 
+ 1.0e-02 	 & 1.0e-05 	 & 10 & 324 	 & +0.043 & +0.067 & +0.042 & +0.521 \\ 
+ 1.0e-02 	 & 1.0e-06 	 & 10 & 261 	 & +0.028 & +0.069 & +0.037 & +0.525 \\ 
+ 1.0e-03 	 & 1.0e+00 	 & 10 & 222 	 & +0.013 & +0.061 & +0.035 & +0.488 \\ 
+ 1.0e-03 	 & 1.0e-01 	 & 10 & 227 	 & +0.002 & +0.069 & +0.041 & +0.489 \\ 
+ 1.0e-03 	 & 1.0e-02 	 & 10 & 341 	 & -0.015 & +0.066 & +0.038 & +0.496 \\ 
+ 1.0e-03 	 & 1.0e-03 	 & 10 & 309 	 & -0.018 & +0.067 & +0.033 & +0.516 \\ 
+ 1.0e-03 	 & 1.0e-04 	 & 10 & 406 	 & -0.034 & +0.057 & +0.049 & +0.545 \\ 
+ 1.0e-03 	 & 1.0e-05 	 & 10 & 400 	 & +0.011 & +0.057 & +0.042 & +0.545 \\ 
+ 1.0e-03 	 & 1.0e-06 	 & 10 & 349 	 & -0.004 & +0.071 & +0.042 & +0.539 \\ 
+ 1.0e-04 	 & 1.0e+00 	 & 10 & 186 	 & -0.031 & +0.069 & +0.039 & +0.487 \\ 
+ 1.0e-04 	 & 1.0e-01 	 & 10 & 230 	 & -0.004 & +0.067 & +0.030 & +0.489 \\ 
+ 1.0e-04 	 & 1.0e-02 	 & 10 & 264 	 & -0.032 & +0.057 & +0.044 & +0.493 \\ 
+ 1.0e-04 	 & 1.0e-03 	 & 10 & 302 	 & -0.026 & +0.059 & +0.039 & +0.511 \\ 
+ 1.0e-04 	 & 1.0e-04 	 & 10 & 417 	 & -0.020 & +0.058 & +0.040 & +0.577 \\ 
+ 1.0e-04 	 & 1.0e-05 	 & 10 & 598 	 & +0.004 & +0.063 & +0.041 & +0.703 \\ 
+ 1.0e-04 	 & 1.0e-06 	 & 10 & 554 	 & +0.011 & +0.059 & +0.038 & +0.647 \\ 
+ 1.0e-05 	 & 1.0e+00 	 & 10 & 232 	 & +0.019 & +0.060 & +0.039 & +0.487 \\ 
+ 1.0e-05 	 & 1.0e-01 	 & 10 & 216 	 & +0.011 & +0.066 & +0.040 & +0.489 \\ 
+ 1.0e-05 	 & 1.0e-02 	 & 10 & 340 	 & -0.044 & +0.068 & +0.042 & +0.493 \\ 
+ 1.0e-05 	 & 1.0e-03 	 & 10 & 369 	 & +0.000 & +0.063 & +0.034 & +0.518 \\ 
+ 1.0e-05 	 & 1.0e-04 	 & 10 & 561 	 & +0.005 & +0.060 & +0.031 & +0.652 \\ 
+\rowcolor{red} 1.0e-05 	 & 1.0e-05 	 & 10 & 1001 	 & -0.002 & +0.066 & +0.037 & +1.226 \\ 
+\rowcolor{red} 1.0e-05 	 & 1.0e-06 	 & 10 & 856 	 & -0.001 & +0.065 & +0.040 & +1.025 \\ 
+ 1.0e-06 	 & 1.0e+00 	 & 10 & 146 	 & +0.046 & +0.061 & +0.032 & +0.488 \\ 
+ 1.0e-06 	 & 1.0e-01 	 & 10 & 287 	 & -0.008 & +0.063 & +0.040 & +0.488 \\ 
+ 1.0e-06 	 & 1.0e-02 	 & 10 & 295 	 & +0.025 & +0.068 & +0.039 & +0.493 \\ 
+ 1.0e-06 	 & 1.0e-03 	 & 10 & 252 	 & +0.032 & +0.061 & +0.041 & +0.510 \\ 
+ 1.0e-06 	 & 1.0e-04 	 & 10 & 520 	 & +0.021 & +0.061 & +0.042 & +0.620 \\ 
+\rowcolor{red} 1.0e-06 	 & 1.0e-05 	 & 10 & 1001 	 & -0.013 & +0.063 & +0.041 & +1.170 \\ 
+ \rowcolor{red}1.0e-06 	 & 1.0e-06 	 & 10 & 821 	 & -0.008 & +0.066 & +0.033 & +1.079 \\ 
+\end{tabular}}
+\label{Tab::1}
+\end{table} 
+%\begin{table}
+%\centering
+%\caption{ $\tau = [1.0, 1.2, 1.4, 2.8, 4.6, 9.6, 14.4, 18.6, 22.2, 24.0] $}
+%\resizebox{\textwidth}{!}{\begin{tabular}{*{7}c}
+%$\alpha$ & $\beta$ & k & iter & $ D_{\Omega_1} = 1000$ & $ D_{\Omega_2} = 4.0 $ & $D_{\Omega_3} = 8.0 $ \\
+%\hline
+%
+%\label{Tab::1}
+%\end{table} 
+%\section{Discussion}
+%
+%
+%\begin{table}
+%\centering
+%\caption{ $\tau =[1.2, 1.4, 1.8, 2.4, 3.6, 5.4, 7.6, 17.2, 18.6, 20.4, 22.4, 24.0] $}
+%\resizebox{\textwidth}{!}{\begin{tabular}{*{7}c}
+%$\alpha$ & $\beta$ & k & iter & $ D_{\Omega_1} = 1000$ & $ D_{\Omega_2} = 4.0 $ & $D_{\Omega_3} = 8.0 $ \\
+%\hline
+%
+%\end{tabular}}
+%\label{Tab::1}
+%\end{table} 
 \section{Discussion}
 
-The L-BFGS-B algorithm does not scale the control parameters, thus the step size . This poses a problem with a large difference in the control parameters,
+ \begin{table}
+\centering
+\caption{ $\tau = [2.4, 4.8, 7.2, 9.6, 12.0, 14.4, 16.8, 19.2, 21.6, 24.0] $}
+\resizebox{\textwidth}{!}{\begin{tabular}{*{8}c}
+$\alpha$ & $\beta$ & k & iter & $ D_{\Omega_1} = 1000$ & $ D_{\Omega_2} = 4.0 $ & $D_{\Omega_3} = 8.0 $ & $g$ \\
+\hline
+ 1.0e-04 	 & 1.0e+00 	 & 40 & 234 	 & -0.017 & -0.019 & +0.005 & +0.459 \\ 
+ 1.0e-04 	 & 1.0e-01 	 & 40 & 415 	 & +0.001 & -0.007 & +0.004 & +0.457 \\ 
+ 1.0e-04 	 & 1.0e-02 	 & 40 & 370 	 & +0.006 & +0.004 & +0.002 & +0.455 \\ 
+ 1.0e-05 	 & 1.0e+00 	 & 40 & 296 	 & -0.017 & -0.019 & +0.005 & +0.459 \\ 
+ 1.0e-05 	 & 1.0e-01 	 & 40 & 343 	 & +0.001 & -0.007 & +0.004 & +0.457 \\ 
+ 1.0e-05 	 & 1.0e-02 	 & 40 & 348 	 & +0.006 & +0.005 & +0.003 & +0.454 \\ 
+ 1.0e-06 	 & 1.0e+00 	 & 40 & 311 	 & -0.019 & -0.019 & +0.005 & +0.459 \\ 
+ 1.0e-06 	 & 1.0e-01 	 & 40 & 429 	 & -0.000 & -0.007 & +0.004 & +0.457 \\ 
+ 1.0e-06 	 & 1.0e-02 	 & 40 & 454 	 & +0.002 & +0.001 & +0.002 & +0.456 \\
 
-There is a need for observable change in order to estimate the parameters.
-But considering the magnitude difference between diffusion coefficients.
-It is clear that the observable change is in different timescales.
-This prompted that in using actual data, we will only consider a mesh with 2 subdomains that have diffusion coefficient of similar magnitude.
+\end{tabular}}
+\label{Tab::Incoherence}
+\end{table} 
+\section{Discussion}
+
+In Tab.
+??
+we observe that the optimal relaxation parameters are found for $\alpha := \lbrace 1.e-4 1.e-5 1.e-6 \rbrace$ and $\beta := \lbrace 1.0 0.1 0.01 \rbrace$.
+This will be the region of interest for the relaxation parameters.
+
+The dependency on number of timesteps can be seen in Fig.??.
 

### 2018-09-27 make_plot.py
Update

@@ -33,7 +33,7 @@ def read_functional(filename):
 def store_last_val(array,legend):
     with open("list_end.txt", "a") as myfile:
           print legend[0],legend[1],legend[2], legend[3],len(array[:,0]),array[-1,1],array[-1,2],array[-1,3] 
-          myfile.write("{} & {} &{} &{} & {}& {} & {} & {} \\\\ \n ".format(legend[0],legend[1],legend[2], legend[3],len(array[:,0]),array[-1,1],array[-1,2],array[-1,3] ) )
+          myfile.write("{:.1e} \t & {:.1e} \t & {} & {} \t & {:+.3f} & {:+.3f} & {:+.3f} & {:+.3f} \\\\ \n ".format(legend[0],legend[1],legend[2],len(array[:,0]), (array[-1,1]-10.)/10. , (array[-1,2] -4.)/4.,(array[-1,3]-8.)/8. ,array[-1,4]) )
 
 
 
@@ -52,7 +52,7 @@ def read_slurm(filename):
     """
     import numpy as np
     array = []
-    legend=[0.0,0.0,0.0,0.0]
+    legend=[0.0,0.0,0.0,0.0,0.0]
     with open(filename) as f:
          lines = f.readlines()
          for line in lines:
@@ -64,18 +64,19 @@ def read_slurm(filename):
                  D1=extract_float(spl1)
                  D2=extract_float(spl2)
                  D3=extract_float(spl3) 
-                 array.append([0,D1,D2,D3])
+                 array.append([0,D1,D2,D3,0])
 
              if "Functional-value" in line:
                  array[-1][0]= float(line.split("|")[1])
-             
+             if "DirichletBC-Iter" in line:
+                 array[-1][4]= float(line.split("|")[1])
              elif "Namespace" in line:
                  legend[0] =float(line[line.rfind("alpha")+6:line.find("," ,line.find("alpha"))])
                  legend[1] =float(line[line.rfind("beta")+5:line.find("," ,line.find("beta"))])
-                 legend[2] =int(line[line.rfind("k=")+2:line.find("," ,line.find("k="))])
+                 legend[2] =int(line[line.rfind("K=")+2:line.find("," ,line.find("K="))])
                  legend[3] =eval(line[line.rfind("tau=")+4:line.find("]" ,line.find("tau="))+1])
-
-             
+                 legend[4] =float(line[line.rfind("noise=")+6:line.find("," ,line.find("noise="))])
+                 
     return np.array(array),legend
 
 
[…]

### 2018-09-27 main.py
fix

@@ -64,7 +64,7 @@ def iter_cb(m):
     ds = mesh_config["ds"]
     fenics_m = NumRF.set_local([control.copy_data() for control in Jhat.controls], m)
     print("Functional-value: {} | {} ".format(iter_cnt, NumRF(m)) )
-    print("DirichletBC-Iter: {} | {}".format(iter_cnt, sum([assemble((fenics_m[i] - correct_g[i-3])**2*ds) for i in range(3, len(fenics_m))])/sum([assemble(correct_g[i-3]**2*ds) for i in range(3, len(fenics_m)) ]) ))
+    print("DirichletBC-Iter: {} | {}".format(iter_cnt, sum([assemble((fenics_m[i] - correct_g[i-3])**2*ds(1)) for i in range(3, len(fenics_m))])/sum([assemble(correct_g[i-3]**2*ds(1)) for i in range(3, len(fenics_m)) ]) ))
 
 
 if __name__ == "__main__":

### 2018-10-01 tex/paper.tex
Updated tables
updated the first few pages

@@
 
-The discovery of the paravascular pathway in 2011~\cite{iliff2012paravascular} propose a novel component
-crucial to the metabolism of the brain which may potientially provide an explanation for the accumulation of
-waste such as amyloid beta in elderly, ultimately leading to diseases such as Alzheimer and Parkinson. 
-In the rest of our body, the lymphatic system plays an important role
-in the clearance of metabolic waste, but there are no lymphs within the brain. This fact is puzzling in particular because
-the brain requires around 10 times more energy per volume than the result of the body. The paravascular 
-pathway is proposed important to waste clearance and has therefore been named the \emph{glymphatic system}.
+The discovery of the paravascular pathway in 2011~\cite{iliff2012paravascular} which later was found to be particularly active during sleep~\cite{xie2013sleep}. 
+It has been proposed that this pathway plays an important role in the waste
+clearance of the brain. In particular, since the brain lack a lymphatic system, 
+which elsewhere in our body plays a crucial role in waste clearance, the system has been called the glymphatic system~\cite{jessen2015glymphatic}.  
+The glymphatic system remains controversial and modeling attempts
+has so far mostly failed to explain the biomechanics of the system~\cite{holter2017interstitial, smith2017glymphatic}. A proper biomechanical 
+understanding of the pathway has significant potential because
+dementia such as Alzheimer´s and Parkinson´s diseases are
+associated with accumulation of metabolic waste such as
+amyloid-beta and CSF-tau.
 
-The pioneering works of Sykov{\'a} and Nicholson~\cite{sykova2008diffusion} demonstrated
-that diffusion was a governing transport mechanism in the brain. However, 
-the clearance of CSF-tracers during sleep~\cite{xie2013sleep} in mice demonstrated transportation
-much faster what could be explained by diffusion and it was proposed that arterial pulsation powered
-accelrated perivascular flow combined convective interstitial flow. Several modelling attempts
-have put the theory to the test~\cite{asgari2016glymphatic, smith2017glymphatic, holter2017interstitial}, 
-but so far computational modeling have failed to adequately described the mechanism.
+In \cite{ringstad2018brain} brainwide distribution of MRI-contrast was demonstrated during 24 hours after lumbar contrast injection.
+Brain wide distribution by diffusion alone was deemed unlikely by the authors (some of which are part
+of this study as well). The argument was based on analytical considerations where it was calculated that 50\% contrast enrichment would occur after 
+55 hours using the error function which is valid for planar diffusion. However, 
+the surface of the brain is folded and is around five times larger than 
+a corresponding surface of a ball with the same volume. Hence, 
+a more rigorous modeling attempt is warrented. Complicating factors
+are however that the contrast in the surrounding CSF is heterogenous
+and changes significantly during the 24 hours of the investigations. 
+Furthermore, images were obtained only at a few time-points during the investigations in \cite{ringstad2018brain}.
 
-Transportation by diffusion is in the order of XXX\comment{Lars: hente fra R. Thorne / Nicholson}. 
-However, in \cite{xie2013sleep} a 60% coverage of 3kDa Texas Red Dextran of a $200 \mu m$ cube was demostrated in approximately 
-20 minutes. As such, the transportation is XXX faster than what diffusion would provide. Furthermore, 
-in \cite{eidevalnes} it was demonstrated that X Da Gadovist was brainwide in 8 hours after injection in the lumbar region.
+Our purpose in this paper is to attempt a more rigorous methodology 
+for assessing the apparent diffusion process. To this end we employ
+adjoint methods to determine the apparent diffusion coefficient 
+that would explain the tracer distribution.
 
-Paragraph about timescales etc.
-
-The purpose of this paper is to attempt to assess transportation speed in terms of an apparent diffusion coefficient 
-by using adjoint methods provided by \cite{} for optimizing the coefficient with respect to data. As
-such a coefficient larger than commonly reported values of diffusion would suggest that at the
-timescale of minutes to hours there is indeed a glymphatic transportation which may potentially 
-be responsible for metabolic waste.
-
-An outline of the paper is as follows. In Section 2 we descibe the medical images and their modality,  
-and the mathematical methodology used for determining the apparent diffusion coefficients.
-
-\section{Methods}
+\section{Methodology}
 
@@
 The observation points are distributed with 5 observations within 1-2 hours after injection, 1 observation in the timeframes 2-4 hours, 6-9 hours, 24 hours and 48 hours.
+Figure ~\ref{fig1} shows the distribution of tracers during 24 hours, see also~\cite{ringstad2017glymphatic}.
+
+\begin{figure}
+\includegraphics[width=0.95\textwidth]{GMRI.png} 
+\label{fig1} 
+\caption{\comment{lars, we will need some new images since I believe this is stolen from JCI. Also include a zoom on the region of interest}}
+\end{figure}
 
 \subsection*{Mathematical Model}
+In order to assess whether the contrast distribution shown 
+in Figure \ref{fig1} is governed by a diffusion process we
+aim to solve a PDE constrained optimization problem where
+the contrast distribution, boundary conditions, and apparent
+diffusion coefficition are solved for by optimizing with
+respect to the observed contrast distribution.  
 The objective function was defined as 
@@
 \end{equation}
-subjugated by   
+subject to 
 \begin{equation}
@@
 \end{equation}
-with the domain $\Omega$ contains three sub domains, each with a different diffusion coefficient.
+Here $u$ is the contrast distribution, $D_i$ is the apparent diffusion 
+coefficient, and $g$ is the boundary condition. Furthermore,  
+the domain $\Omega$ contains three sub domains, each with a different diffusion coefficient.
 We denote the Cerebral Spinal fluid (CSF) domain as $\Omega_1$, the grey matter as $\Omega_2$ and the white matter as $\Omega_3$.
+The apparent
+diffusion constant is assumed constant within the CSF, grey and 
+white matter but each region may have different constants.  
+The $\alpha$ and $\beta$ parameters are regularization parameters 
+and $u_{obs}$ are observations at certain time-points.
 
-\section*{Manufactured Solution}
+\subsection*{Manufactured Solution}
+In order to verify our strategy and test the dependency of the
+regularization paramters, we perform a test case with a
+known solution.  
 The manufactured observations was obtained by forward computation of Eq.\ref{Eq::PDE} with the Dirichlet boundary condition defined as
@@
 \hline
-\rowcolor{red} 1.0e+00 	 & 1.0e+00 	 & 10 & 239 	 & +4.227 & +0.304 & +0.092 & +0.589 \\ 
-\rowcolor{red} 1.0e+00 	 & 1.0e-01 	 & 10 & 234 	 & +4.272 & +0.305 & +0.091 & +0.596 \\ 
-\rowcolor{red} 1.0e+00 	 & 1.0e-02 	 & 10 & 225 	 & +4.271 & +0.305 & +0.091 & +0.597 \\ 
-\rowcolor{red} 1.0e+00 	 & 1.0e-03 	 & 10 & 235 	 & +4.600 & +0.304 & +0.090 & +0.597 \\ 
-\rowcolor{red} 1.0e+00 	 & 1.0e-04 	 & 10 & 207 	 & +4.489 & +0.304 & +0.090 & +0.597 \\ 
-\rowcolor{red} 1.0e+00 	 & 1.0e-05 	 & 10 & 193 	 & +4.271 & +0.305 & +0.090 & +0.597 \\ 
-\rowcolor{red} 1.0e+00 	 & 1.0e-06 	 & 10 & 184 	 & +4.460 & +0.304 & +0.090 & +0.597 \\ 
- 1.0e-01 	 & 1.0e+00 	 & 10 & 166 	 & +0.128 & +0.093 & +0.041 & +0.488 \\ 
- 1.0e-01 	 & 1.0e-01 	 & 10 & 162 	 & +0.122 & +0.093 & +0.041 & +0.506 \\ 
- 1.0e-01 	 & 1.0e-02 	 & 10 & 180 	 & +0.122 & +0.093 & +0.041 & +0.515 \\ 
- 1.0e-01 	 & 1.0e-03 	 & 10 & 183 	 & +0.123 & +0.093 & +0.041 & +0.516 \\ 
- 1.0e-01 	 & 1.0e-04 	 & 10 & 188 	 & +0.123 & +0.093 & +0.040 & +0.516 \\ 
- 1.0e-01 	 & 1.0e-05 	 & 10 & 198 	 & +0.123 & +0.093 & +0.040 & +0.516 \\ 
- 1.0e-02 	 & 1.0e+00 	 & 10 & 153 	 & +0.015 & +0.067 & +0.039 & +0.481 \\ 
- 1.0e-02 	 & 1.0e-01 	 & 10 & 166 	 & +0.005 & +0.065 & +0.039 & +0.483 \\ 
- 1.0e-02 	 & 1.0e-02 	 & 10 & 222 	 & +0.005 & +0.065 & +0.039 & +0.501 \\ 
- 1.0e-02 	 & 1.0e-03 	 & 10 & 227 	 & +0.005 & +0.065 & +0.039 & +0.510 \\ 
- 1.0e-02 	 & 1.0e-04 	 & 10 & 163 	 & +0.006 & +0.065 & +0.039 & +0.509 \\ 
- 1.0e-02 	 & 1.0e-05 	 & 10 & 188 	 & +0.005 & +0.065 & +0.039 & +0.510 \\ 
- 1.0e-03 	 & 1.0e+00 	 & 10 & 168 	 & +0.005 & +0.064 & +0.039 & +0.481 \\ 
- 1.0e-03 	 & 1.0e-01 	 & 10 & 230 	 & -0.005 & +0.063 & +0.039 & +0.481 \\ 
- 1.0e-03 	 & 1.0e-02 	 & 10 & 89 	 & -0.007 & +0.063 & +0.039 & +0.488 \\ 
- 1.0e-03 	 & 1.0e-03 	 & 10 & 77 	 & -0.005 & +0.062 & +0.039 & +0.488 \\ 
- 1.0e-03 	 & 1.0e-04 	 & 10 & 107 	 & -0.006 & +0.062 & +0.039 & +0.489 \\ 
- 1.0e-03 	 & 1.0e-05 	 & 10 & 140 	 & -0.006 & +0.062 & +0.039 & +0.490 \\ 
- 1.0e-04 	 & 1.0e+00 	 & 10 & 179 	 & +0.003 & +0.064 & +0.039 & +0.481 \\ 
- 1.0e-04 	 & 1.0e-01 	 & 10 & 215 	 & -0.005 & +0.062 & +0.039 & +0.481 \\ 
- 1.0e-04 	 & 1.0e-02 	 & 10 & 190 	 & -0.007 & +0.062 & +0.039 & +0.482 \\ 
- 1.0e-04 	 & 1.0e-03 	 & 10 & 124 	 & -0.008 & +0.062 & +0.039 & +0.488 \\ 
- 1.0e-04 	 & 1.0e-04 	 & 10 & 106 	 & -0.007 & +0.062 & +0.039 & +0.488 \\ 
- 1.0e-04 	 & 1.0e-05 	 & 10 & 97 	 & -0.008 & +0.062 & +0.039 & +0.488 \\ 
- 1.0e-05 	 & 1.0e+00 	 & 10 & 193 	 & +0.003 & +0.064 & +0.039 & +0.481 \\ 
- 1.0e-05 	 & 1.0e-01 	 & 10 & 174 	 & -0.007 & +0.062 & +0.039 & +0.481 \\ 
- 1.0e-05 	 & 1.0e-02 	 & 10 & 180 	 & -0.008 & +0.062 & +0.039 & +0.482 \\ 
- 1.0e-05 	 & 1.0e-03 	 & 10 & 70 	 & -0.007 & +0.062 & +0.039 & +0.488 \\ 
- 1.0e-05 	 & 1.0e-04 	 & 10 & 77 	 & -0.007 & +0.062 & +0.039 & +0.488 \\ 
- 1.0e-05 	 & 1.0e-05 	 & 10 & 100 	 & -0.008 & +0.062 & +0.039 & +0.488 \\ 
- 1.0e-06 	 & 1.0e+00 	 & 10 & 209 	 & +0.004 & +0.064 & +0.039 & +0.482 \\ 
- 1.0e-06 	 & 1.0e-01 	 & 10 & 187 	 & -0.006 & +0.062 & +0.039 & +0.481 \\ 
- 1.0e-06 	 & 1.0e-02 	 & 10 & 205 	 & -0.008 & +0.062 & +0.039 & +0.482 \\ 
- 1.0e-06 	 & 1.0e-03 	 & 10 & 79 	 & -0.006 & +0.062 & +0.039 & +0.488 \\ 
- 1.0e-06 	 & 1.0e-04 	 & 10 & 107 	 & -0.007 & +0.062 & +0.039 & +0.488 \\ 
- 1.0e-06 	 & 1.0e-05 	 & 10 & 110 	 & -0.007 & +0.062 & +0.039 & +0.488 \\ 
+\rowcolor{red}  1.0e+00 	 & 1.0e+00 	 & 10 & 225 	 & +4.148 & +0.304 & +0.092 & +0.135 \\ 
+\rowcolor{red}  1.0e+00 	 & 1.0e-01 	 & 10 & 206 	 & +4.272 & +0.305 & +0.091 & +0.142 \\ 
+\rowcolor{red}  1.0e+00 	 & 1.0e-02 	 & 10 & 233 	 & +4.272 & +0.305 & +0.091 & +0.143 \\ 
+\rowcolor{red}  1.0e+00 	 & 1.0e-03 	 & 10 & 208 	 & +4.437 & +0.305 & +0.091 & +0.143 \\ 
+\rowcolor{red}  1.0e+00 	 & 1.0e-04 	 & 10 & 204 	 & +4.271 & +0.306 & +0.091 & +0.143 \\ 
+\rowcolor{red}  1.0e+00 	 & 1.0e-05 	 & 10 & 203 	 & +4.400 & +0.305 & +0.091 & +0.143 \\ 
+\rowcolor{red}  1.0e+00 	 & 1.0e-06 	 & 10 & 222 	 & +4.584 & +0.304 & +0.090 & +0.143 \\
+
+ 1.0e-01 	 & 1.0e+00 	 & 10 & 207 	 & +0.127 & +0.093 & +0.041 & +0.027 \\ 
+ 1.0e-01 	 & 1.0e-01 	 & 10 & 196 	 & +0.121 & +0.093 & +0.041 & +0.046 \\ 
+ 1.0e-01 	 & 1.0e-02 	 & 10 & 232 	 & +0.123 & +0.093 & +0.041 & +0.056 \\ 
+ 1.0e-01 	 & 1.0e-03 	 & 10 & 183 	 & +0.122 & +0.093 & +0.040 & +0.057 \\ 
+ 1.0e-01 	 & 1.0e-04 	 & 10 & 212 	 & +0.122 & +0.093 & +0.040 & +0.057 \\ 
+ 1.0e-01 	 & 1.0e-05 	 & 10 & 168 	 & +0.122 & +0.093 & +0.041 & +0.057 \\
+ 1.0e-01 	 & 1.0e-06 	 & 10 & 195 	 & +0.122 & +0.093 & +0.041 & +0.057 \\
+
+ 1.0e-02 	 & 1.0e+00 	 & 10 & 227 	 & +0.015 & +0.067 & +0.039 & +0.018 \\ 
+ 1.0e-02 	 & 1.0e-01 	 & 10 & 153 	 & +0.006 & +0.065 & +0.039 & +0.021 \\ 
+ 1.0e-02 	 & 1.0e-02 	 & 10 & 184 	 & +0.005 & +0.065 & +0.039 & +0.039 \\ 
+ 1.0e-02 	 & 1.0e-03 	 & 10 & 176 	 & +0.004 & +0.065 & +0.039 & +0.048 \\ 
+ 1.0e-02 	 & 1.0e-04 	 & 10 & 195 	 & +0.005 & +0.065 & +0.039 & +0.049 \\ 
+ 1.0e-02 	 & 1.0e-05 	 & 10 & 215 	 & +0.004 & +0.065 & +0.039 & +0.051 \\ 
+ 1.0e-02 	 & 1.0e-06 	 & 10 & 205 	 & +0.005 & +0.065 & +0.039 & +0.050 \\
+
+ 1.0e-03 	 & 1.0e+00 	 & 10 & 179 	 & +0.004 & +0.064 & +0.039 & +0.019 \\ 
+ 1.0e-03 	 & 1.0e-01 	 & 10 & 221 	 & -0.005 & +0.063 & +0.039 & +0.018 \\ 
+ 1.0e-03 	 & 1.0e-02 	 & 10 & 89 	 & -0.007 & +0.063 & +0.039 & +0.026 \\ 
+ 1.0e-03 	 & 1.0e-03 	 & 10 & 77 	 & -0.005 & +0.062 & +0.039 & +0.027 \\ 
+ 1.0e-03 	 & 1.0e-04 	 & 10 & 100 	 & -0.006 & +0.062 & +0.039 & +0.027 \\ 
+ 1.0e-03 	 & 1.0e-05 	 & 10 & 105 	 & -0.006 & +0.062 & +0.039 & +0.027 \\ 
+ 1.0e-03 	 & 1.0e-06 	 & 10 & 123 	 & -0.007 & +0.062 & +0.039 & +0.028 \\
+
+ 1.0e-04 	 & 1.0e+00 	 & 10 & 236 	 & +0.004 & +0.063 & +0.039 & +0.019 \\ 
+ 1.0e-04 	 & 1.0e-01 	 & 10 & 195 	 & -0.006 & +0.062 & +0.039 & +0.018 \\ 
+ 1.0e-04 	 & 1.0e-02 	 & 10 & 152 	 & -0.006 & +0.062 & +0.039 & +0.022 \\ 
+ 1.0e-04 	 & 1.0e-03 	 & 10 & 119 	 & -0.008 & +0.062 & +0.039 & +0.026 \\ 
+ 1.0e-04 	 & 1.0e-04 	 & 10 & 106 	 & -0.007 & +0.062 & +0.039 & +0.026 \\ 
+ 1.0e-04 	 & 1.0e-05 	 & 10 & 109 	 & -0.007 & +0.062 & +0.039 & +0.026 \\ 
+ 1.0e-04 	 & 1.0e-06 	 & 10 & 99 	 & -0.008 & +0.062 & +0.039 & +0.026 \\
+
+ 1.0e-05 	 & 1.0e+00 	 & 10 & 139 	 & +0.004 & +0.063 & +0.039 & +0.019 \\ 
+ 1.0e-05 	 & 1.0e-01 	 & 10 & 170 	 & -0.006 & +0.062 & +0.039 & +0.018 \\ 
+ 1.0e-05 	 & 1.0e-02 	 & 10 & 182 	 & -0.007 & +0.062 & +0.039 & +0.020 \\ 
+ 1.0e-05 	 & 1.0e-03 	 & 10 & 70 	 & -0.007 & +0.062 & +0.039 & +0.026 \\ 
+ 1.0e-05 	 & 1.0e-04 	 & 10 & 77 	 & -0.007 & +0.062 & +0.039 & +0.026 \\ 
+ 1.0e-05 	 & 1.0e-05 	 & 10 & 104 	 & -0.008 & +0.062 & +0.039 & +0.026 \\ 
+ 1.0e-05 	 & 1.0e-06 	 & 10 & 92 	 & -0.007 & +0.062 & +0.039 & +0.026 \\
+
+ 1.0e-06 	 & 1.0e+00 	 & 10 & 163 	 & +0.003 & +0.064 & +0.039 & +0.019 \\ 
+ 1.0e-06 	 & 1.0e-01 	 & 10 & 218 	 & -0.006 & +0.062 & +0.039 & +0.018 \\ 
+ 1.0e-06 	 & 1.0e-02 	 & 10 & 134 	 & -0.008 & +0.062 & +0.039 & +0.023 \\ 
+ 1.0e-06 	 & 1.0e-03 	 & 10 & 79 	 & -0.006 & +0.062 & +0.039 & +0.026 \\ 
+ 1.0e-06 	 & 1.0e-04 	 & 10 & 107 	 & -0.007 & +0.062 & +0.039 & +0.026 \\ 
+ 1.0e-06 	 & 1.0e-05 	 & 10 & 103 	 & -0.008 & +0.062 & +0.039 & +0.026 \\ 
+ 1.0e-06 	 & 1.0e-06 	 & 10 & 91 	 & -0.008 & +0.062 & +0.039 & +0.026 \\  
 \end{tabular}}
@@
 \caption{Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$ and number of observation $\tau$ with the resulting number of iterations and estimated optimal parameters for the diffusion coefficients.
-Noise 0.15 amp }
+Noise 0.03 amp }
 \resizebox{\textwidth}{!}{\begin{tabular}{*{8}c}
@@
 \hline
- 1.0e+00 	 & 1.0e+00 	 & 10 & 215 	 & +4.279 & +0.304 & +0.089 & +0.592 \\ 
- 1.0e+00 	 & 1.0e-01 	 & 10 & 174 	 & +3.667 & +0.319 & +0.092 & +0.599 \\ 
- 1.0e+00 	 & 1.0e-02 	 & 10 & 168 	 & +3.722 & +0.311 & +0.087 & +0.600 \\ 
- 1.0e+00 	 & 1.0e-03 	 & 10 & 197 	 & +4.219 & +0.305 & +0.092 & +0.601 \\ 
- 1.0e+00 	 & 1.0e-04 	 & 10 & 200 	 & +4.302 & +0.295 & +0.095 & +0.601 \\ 
- 1.0e+00 	 & 1.0e-05 	 & 10 & 190 	 & +4.281 & +0.307 & +0.090 & +0.601 \\ 
- 1.0e+00 	 & 1.0e-06 	 & 10 & 211 	 & +4.310 & +0.301 & +0.085 & +0.600 \\ 
- 1.0e-01 	 & 1.0e+00 	 & 10 & 126 	 & +0.129 & +0.092 & +0.039 & +0.493 \\ 
- 1.0e-01 	 & 1.0e-01 	 & 10 & 205 	 & +0.134 & +0.091 & +0.047 & +0.512 \\ 
- 1.0e-01 	 & 1.0e-02 	 & 10 & 232 	 & +0.150 & +0.093 & +0.042 & +0.521 \\ 
- 1.0e-01 	 & 1.0e-03 	 & 10 & 219 	 & +0.155 & +0.085 & +0.040 & +0.524 \\ 
- 1.0e-01 	 & 1.0e-04 	 & 10 & 181 	 & +0.153 & +0.091 & +0.040 & +0.523 \\ 
- 1.0e-01 	 & 1.0e-05 	 & 10 & 176 	 & +0.111 & +0.098 & +0.037 & +0.523 \\ 
- 1.0e-01 	 & 1.0e-06 	 & 10 & 151 	 & +0.155 & +0.092 & +0.043 & +0.523 \\ 
- 1.0e-02 	 & 1.0e+00 	 & 10 & 214 	 & +0.014 & +0.066 & +0.038 & +0.486 \\ 
- 1.0e-02 	 & 1.0e-01 	 & 10 & 139 	 & +0.007 & +0.072 & +0.034 & +0.490 \\ 
- 1.0e-02 	 & 1.0e-02 	 & 10 & 235 	 & +0.032 & +0.076 & +0.041 & +0.512 \\ 
- 1.0e-02 	 & 1.0e-03 	 & 10 & 282 	 & +0.002 & +0.067 & +0.041 & +0.519 \\ 
- 1.0e-02 	 & 1.0e-04 	 & 10 & 353 	 & +0.002 & +0.060 & +0.043 & +0.523 \\ 
- 1.0e-02 	 & 1.0e-05 	 & 10 & 324 	 & +0.043 & +0.067 & +0.042 & +0.521 \\ 
- 1.0e-02 	 & 1.0e-06 	 & 10 & 261 	 & +0.028 & +0.069 & +0.037 & +0.525 \\ 
- 1.0e-03 	 & 1.0e+00 	 & 10 & 222 	 & +0.013 & +0.061 & +0.035 & +0.488 \\ 
- 1.0e-03 	 & 1.0e-01 	 & 10 & 227 	 & +0.002 & +0.069 & +0.041 & +0.489 \\ 
- 1.0e-03 	 & 1.0e-02 	 & 10 & 341 	 & -0.015 & +0.066 & +0.038 & +0.496 \\ 
- 1.0e-03 	 & 1.0e-03 	 & 10 & 309 	 & -0.018 & +0.067 & +0.033 & +0.516 \\ 
- 1.0e-03 	 & 1.0e-04 	 & 10 & 406 	 & -0.034 & +0.057 & +0.049 & +0.545 \\ 
- 1.0e-03 	 & 1.0e-05 	 & 10 & 400 	 & +0.011 & +0.057 & +0.042 & +0.545 \\ 
- 1.0e-03 	 & 1.0e-06 	 & 10 & 349 	 & -0.004 & +0.071 & +0.042 & +0.539 \\ 
- 1.0e-04 	 & 1.0e+00 	 & 10 & 186 	 & -0.031 & +0.069 & +0.039 & +0.487 \\ 
- 1.0e-04 	 & 1.0e-01 	 & 10 & 230 	 & -0.004 & +0.067 & +0.030 & +0.489 \\ 
- 1.0e-04 	 & 1.0e-02 	 & 10 & 264 	 & -0.032 & +0.057 & +0.044 & +0.493 \\ 
- 1.0e-04 	 & 1.0e-03 	 & 10 & 302 	 & -0.026 & +0.059 & +0.039 & +0.511 \\ 
- 1.0e-04 	 & 1.0e-04 	 & 10 & 417 	 & -0.020 & +0.058 & +0.040 & +0.577 \\ 
- 1.0e-04 	 & 1.0e-05 	 & 10 & 598 	 & +0.004 & +0.063 & +0.041 & +0.703 \\ 
- 1.0e-04 	 & 1.0e-06 	 & 10 & 554 	 & +0.011 & +0.059 & +0.038 & +0.647 \\ 
- 1.0e-05 	 & 1.0e+00 	 & 10 & 232 	 & +0.019 & +0.060 & +0.039 & +0.487 \\ 
- 1.0e-05 	 & 1.0e-01 	 & 10 & 216 	 & +0.011 & +0.066 & +0.040 & +0.489 \\ 
- 1.0e-05 	 & 1.0e-02 	 & 10 & 340 	 & -0.044 & +0.068 & +0.042 & +0.493 \\ 
- 1.0e-05 	 & 1.0e-03 	 & 10 & 369 	 & +0.000 & +0.063 & +0.034 & +0.518 \\ 
- 1.0e-05 	 & 1.0e-04 	 & 10 & 561 	 & +0.005 & +0.060 & +0.031 & +0.652 \\ 
-\rowcolor{red} 1.0e-05 	 & 1.0e-05 	 & 10 & 1001 	 & -0.002 & +0.066 & +0.037 & +1.226 \\ 
-\rowcolor{red} 1.0e-05 	 & 1.0e-06 	 & 10 & 856 	 & -0.001 & +0.065 & +0.040 & +1.025 \\ 
- 1.0e-06 	 & 1.0e+00 	 & 10 & 146 	 & +0.046 & +0.061 & +0.032 & +0.488 \\ 
- 1.0e-06 	 & 1.0e-01 	 & 10 & 287 	 & -0.008 & +0.063 & +0.040 & +0.488 \\ 
- 1.0e-06 	 & 1.0e-02 	 & 10 & 295 	 & +0.025 & +0.068 & +0.039 & +0.493 \\ 
- 1.0e-06 	 & 1.0e-03 	 & 10 & 252 	 & +0.032 & +0.061 & +0.041 & +0.510 \\ 
- 1.0e-06 	 & 1.0e-04 	 & 10 & 520 	 & +0.021 & +0.061 & +0.042 & +0.620 \\ 
-\rowcolor{red} 1.0e-06 	 & 1.0e-05 	 & 10 & 1001 	 & -0.013 & +0.063 & +0.041 & +1.170 \\ 
- \rowcolor{red}1.0e-06 	 & 1.0e-06 	 & 10 & 821 	 & -0.008 & +0.066 & +0.033 & +1.079 \\ 
+ 1.0e+00 	 & 1.0e+00 	 & 10 & 218 	 & +4.266 & +0.304 & +0.092 & +0.135 \\ 
+ 1.0e+00 	 & 1.0e-01 	 & 10 & 223 	 & +4.565 & +0.304 & +0.090 & +0.142 \\ 
+ 1.0e+00 	 & 1.0e-02 	 & 10 & 199 	 & +4.268 & +0.305 & +0.090 & +0.143 \\ 
+ 1.0e+00 	 & 1.0e-03 	 & 10 & 222 	 & +4.274 & +0.305 & +0.090 & +0.143 \\ 
+ 1.0e+00 	 & 1.0e-04 	 & 10 & 211 	 & +4.448 & +0.306 & +0.090 & +0.143 \\ 
+ 1.0e+00 	 & 1.0e-05 	 & 10 & 227 	 & +4.527 & +0.304 & +0.090 & +0.143 \\ 
+ 1.0e+00 	 & 1.0e-06 	 & 10 & 263 	 & +4.266 & +0.306 & +0.091 & +0.143 \\ 
+ 1.0e-01 	 & 1.0e+00 	 & 10 & 167 	 & +0.131 & +0.093 & +0.041 & +0.027 \\ 
+ 1.0e-01 	 & 1.0e-01 	 & 10 & 195 	 & +0.125 & +0.093 & +0.039 & +0.046 \\ 
+ 1.0e-01 	 & 1.0e-02 	 & 10 & 218 	 & +0.126 & +0.093 & +0.040 & +0.056 \\ 
+ 1.0e-01 	 & 1.0e-03 	 & 10 & 161 	 & +0.129 & +0.094 & +0.040 & +0.057 \\ 
+ 1.0e-01 	 & 1.0e-04 	 & 10 & 180 	 & +0.135 & +0.092 & +0.042 & +0.057 \\ 
+ 1.0e-01 	 & 1.0e-05 	 & 10 & 169 	 & +0.123 & +0.093 & +0.041 & +0.057 \\ 
+ 1.0e-01 	 & 1.0e-06 	 & 10 & 201 	 & +0.119 & +0.093 & +0.040 & +0.057 \\ 
+ 1.0e-02 	 & 1.0e+00 	 & 10 & 183 	 & +0.013 & +0.067 & +0.040 & +0.018 \\ 
+ 1.0e-02 	 & 1.0e-01 	 & 10 & 149 	 & +0.002 & +0.066 & +0.038 & +0.021 \\ 
+ 1.0e-02 	 & 1.0e-02 	 & 10 & 185 	 & -0.005 & +0.065 & +0.040 & +0.040 \\ 
+ 1.0e-02 	 & 1.0e-03 	 & 10 & 213 	 & +0.004 & +0.066 & +0.038 & +0.049 \\ 
+ 1.0e-02 	 & 1.0e-04 	 & 10 & 151 	 & +0.008 & +0.066 & +0.039 & +0.047 \\ 
+ 1.0e-02 	 & 1.0e-05 	 & 10 & 197 	 & +0.004 & +0.064 & +0.040 & +0.051 \\ 
+ 1.0e-02 	 & 1.0e-06 	 & 10 & 185 	 & +0.012 & +0.063 & +0.038 & +0.049 \\ 
+ 1.0e-03 	 & 1.0e+00 	 & 10 & 183 	 & +0.007 & +0.062 & +0.038 & +0.019 \\ 
+ 1.0e-03 	 & 1.0e-01 	 & 10 & 181 	 & -0.011 & +0.063 & +0.039 & +0.019 \\ 
+ 1.0e-03 	 & 1.0e-02 	 & 10 & 122 	 & -0.008 & +0.063 & +0.040 & +0.025 \\ 
+ 1.0e-03 	 & 1.0e-03 	 & 10 & 158 	 & -0.004 & +0.062 & +0.040 & +0.028 \\ 
+ 1.0e-03 	 & 1.0e-04 	 & 10 & 168 	 & -0.013 & +0.063 & +0.038 & +0.029 \\ 
+ 1.0e-03 	 & 1.0e-05 	 & 10 & 120 	 & -0.010 & +0.063 & +0.040 & +0.028 \\ 
+ 1.0e-03 	 & 1.0e-06 	 & 10 & 132 	 & -0.002 & +0.062 & +0.039 & +0.028 \\ 
+ 1.0e-04 	 & 1.0e+00 	 & 10 & 176 	 & +0.000 & +0.063 & +0.039 & +0.019 \\ 
+ 1.0e-04 	 & 1.0e-01 	 & 10 & 180 	 & -0.001 & +0.062 & +0.039 & +0.019 \\ 
+ 1.0e-04 	 & 1.0e-02 	 & 10 & 120 	 & +0.000 & +0.063 & +0.039 & +0.024 \\ 
+ 1.0e-04 	 & 1.0e-03 	 & 10 & 119 	 & -0.004 & +0.062 & +0.039 & +0.026 \\ 
+ 1.0e-04 	 & 1.0e-04 	 & 10 & 77 	 & -0.005 & +0.061 & +0.038 & +0.027 \\ 
+ 1.0e-04 	 & 1.0e-05 	 & 10 & 104 	 & -0.004 & +0.062 & +0.038 & +0.027 \\ 
+ 1.0e-04 	 & 1.0e-06 	 & 10 & 109 	 & -0.007 & +0.062 & +0.039 & +0.027 \\ 
+ 1.0e-05 	 & 1.0e+00 	 & 10 & 220 	 & +0.005 & +0.063 & +0.039 & +0.019 \\ 
+ 1.0e-05 	 & 1.0e-01 	 & 10 & 193 	 & -0.009 & +0.062 & +0.039 & +0.019 \\ 
+ 1.0e-05 	 & 1.0e-02 	 & 10 & 163 	 & -0.013 & +0.063 & +0.039 & +0.021 \\ 
+ 1.0e-05 	 & 1.0e-03 	 & 10 & 115 	 & -0.007 & +0.063 & +0.040 & +0.026 \\ 
+ 1.0e-05 	 & 1.0e-04 	 & 10 & 82 	 & -0.007 & +0.062 & +0.038 & +0.027 \\ 
+ 1.0e-05 	 & 1.0e-05 	 & 10 & 145 	 & -0.001 & +0.062 & +0.039 & +0.027 \\ 
+ 1.0e-05 	 & 1.0e-06 	 & 10 & 147 	 & -0.012 & +0.061 & +0.040 & +0.027 \\ 
+ 1.0e-06 	 & 1.0e+00 	 & 10 & 138 	 & +0.002 & +0.063 & +0.039 & +0.019 \\ 
+ 1.0e-06 	 & 1.0e-01 	 & 10 & 184 	 & -0.006 & +0.063 & +0.039 & +0.019 \\ 
+ 1.0e-06 	 & 1.0e-02 	 & 10 & 83 	 & -0.006 & +0.063 & +0.040 & +0.025 \\ 
+ 1.0e-06 	 & 1.0e-03 	 & 10 & 91 	 & -0.013 & +0.063 & +0.039 & +0.026 \\ 
+ 1.0e-06 	 & 1.0e-04 	 & 10 & 109 	 & -0.005 & +0.062 & +0.038 & +0.027 \\ 
+ 1.0e-06 	 & 1.0e-05 	 & 10 & 116 	 & -0.007 & +0.063 & +0.039 & +0.027 \\ 
+ 1.0e-06 	 & 1.0e-06 	 & 10 & 108 	 & +0.001 & +0.062 & +0.040 & +0.027 \\ 
+\end{tabular}}
+\label{Tab::1}
+\end{table} 
+\begin{table}
+\centering
+\caption{Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$ and number of observation $\tau$ with the resulting number of iterations and estimated optimal parameters for the diffusion coefficients.
+Noise 0.3 amp }
+\resizebox{\textwidth}{!}{\begin{tabular}{*{8}c}
+$\alpha$ & $\beta$ & k  & iter & $ D_{\Omega_1} $ & $ D_{\Omega_2} $ & $D_{\Omega_3} $ & $g$ \\
+\hline
+ 1.0e+00 	 & 1.0e+00 	 & 10 & 212 	 & +4.268 & +0.310 & +0.073 & +0.138 \\ 
+ 1.0e+00 	 & 1.0e-01 	 & 10 & 211 	 & +4.122 & +0.302 & +0.085 & +0.146 \\ 
+ 1.0e+00 	 & 1.0e-02 	 & 10 & 221 	 & +4.773 & +0.298 & +0.089 & +0.147 \\ 
+ 1.0e+00 	 & 1.0e-03 	 & 10 & 257 	 & +4.872 & +0.301 & +0.090 & +0.147 \\ 
+ 1.0e+00 	 & 1.0e-04 	 & 10 & 238 	 & +4.186 & +0.293 & +0.097 & +0.148 \\ 
+ 1.0e+00 	 & 1.0e-05 	 & 10 & 204 	 & +4.251 & +0.313 & +0.085 & +0.147 \\ 
+ 1.0e+00 	 & 1.0e-06 	 & 10 & 223 	 & +4.493 & +0.310 & +0.085 & +0.147 \\ 
+ 1.0e-01 	 & 1.0e+00 	 & 10 & 145 	 & +0.126 & +0.100 & +0.054 & +0.035 \\ 
+ 1.0e-01 	 & 1.0e-01 	 & 10 & 199 	 & +0.115 & +0.125 & +0.026 & +0.060 \\ 
+ 1.0e-01 	 & 1.0e-02 	 & 10 & 217 	 & +0.128 & +0.092 & +0.036 & +0.071 \\ 
+ 1.0e-01 	 & 1.0e-03 	 & 10 & 242 	 & +0.109 & +0.093 & +0.031 & +0.073 \\ 
+ 1.0e-01 	 & 1.0e-04 	 & 10 & 275 	 & +0.187 & +0.094 & +0.028 & +0.073 \\ 
+ 1.0e-01 	 & 1.0e-05 	 & 10 & 237 	 & +0.048 & +0.099 & +0.039 & +0.073 \\ 
+ 1.0e-01 	 & 1.0e-06 	 & 10 & 225 	 & +0.092 & +0.111 & +0.055 & +0.073 \\ 
+ 1.0e-02 	 & 1.0e+00 	 & 10 & 208 	 & +0.017 & +0.075 & +0.037 & +0.029 \\ 
+ 1.0e-02 	 & 1.0e-01 	 & 10 & 199 	 & -0.013 & +0.068 & +0.046 & +0.040 \\ 
+ 1.0e-02 	 & 1.0e-02 	 & 10 & 348 	 & -0.043 & +0.073 & +0.041 & +0.063 \\ 
+ 1.0e-02 	 & 1.0e-03 	 & 10 & 400 	 & +0.056 & +0.058 & +0.031 & +0.075 \\ 
+ 1.0e-02 	 & 1.0e-04 	 & 10 & 393 	 & -0.050 & +0.088 & +0.044 & +0.077 \\ 
+ 1.0e-02 	 & 1.0e-05 	 & 10 & 359 	 & +0.022 & +0.068 & +0.027 & +0.076 \\ 
+ 1.0e-02 	 & 1.0e-06 	 & 10 & 369 	 & +0.001 & +0.074 & +0.024 & +0.076 \\ 
+ 1.0e-03 	 & 1.0e+00 	 & 10 & 207 	 & -0.001 & +0.065 & +0.051 & +0.029 \\ 
+ 1.0e-03 	 & 1.0e-01 	 & 10 & 280 	 & +0.028 & +0.051 & +0.053 & +0.038 \\ 
+ 1.0e-03 	 & 1.0e-02 	 & 10 & 565 	 & -0.059 & +0.076 & +0.033 & +0.053 \\ 
+ 1.0e-03 	 & 1.0e-03 	 & 10 & 673 	 & -0.035 & +0.066 & +0.032 & +0.108 \\ 
+ 1.0e-03 	 & 1.0e-04 	 & 10 & 604 	 & -0.026 & +0.061 & +0.049 & +0.182 \\ 
+ 1.0e-03 	 & 1.0e-05 	 & 10 & 666 	 & +0.012 & +0.070 & +0.038 & +0.182 \\ 
+ 1.0e-03 	 & 1.0e-06 	 & 10 & 893 	 & +0.027 & +0.070 & +0.022 & +0.180 \\ 
+ 1.0e-04 	 & 1.0e+00 	 & 10 & 204 	 & +0.015 & +0.062 & +0.043 & +0.030 \\ 
+ 1.0e-04 	 & 1.0e-01 	 & 10 & 269 	 & +0.005 & +0.057 & +0.037 & +0.038 \\ 
+ 1.0e-04 	 & 1.0e-02 	 & 10 & 559 	 & -0.072 & +0.067 & +0.044 & +0.050 \\ 
+ 1.0e-04 	 & 1.0e-03 	 & 10 & 691 	 & -0.023 & +0.055 & +0.040 & +0.175 \\ 
+\rowcolor{red}  1.0e-04 	 & 1.0e-04 	 & 10 & 1001 	 & -0.012 & +0.066 & +0.030 & +0.745 \\ 
+\rowcolor{red}  1.0e-04 	 & 1.0e-05 	 & 10 & 1001 	 & +0.038 & +0.057 & +0.034 & +1.113 \\ 
+\rowcolor{red} 1.0e-04 	 & 1.0e-06 	 & 10 & 1001 	 & +0.015 & +0.063 & +0.035 & +1.127 \\ 
+ 1.0e-05 	 & 1.0e+00 	 & 10 & 184 	 & -0.025 & +0.076 & +0.041 & +0.029 \\ 
+ 1.0e-05 	 & 1.0e-01 	 & 10 & 357 	 & -0.011 & +0.070 & +0.052 & +0.038 \\ 
+ 1.0e-05 	 & 1.0e-02 	 & 10 & 399 	 & +0.041 & +0.075 & +0.042 & +0.049 \\ 
+ 1.0e-05 	 & 1.0e-03 	 & 10 & 689 	 & +0.044 & +0.062 & +0.020 & +0.172 \\ 
+\rowcolor{red} 1.0e-05 	 & 1.0e-04 	 & 10 & 915 	 & +0.030 & +0.077 & +0.039 & +1.027 \\ 
+\rowcolor{red} 1.0e-05 	 & 1.0e-05 	 & 10 & 1001 	 & +0.017 & +0.061 & +0.045 & +1.953 \\ 
+\rowcolor{red}  1.0e-05 	 & 1.0e-06 	 & 10 & 1001 	 & -0.018 & +0.071 & +0.045 & +2.545 \\ 
+ 1.0e-06 	 & 1.0e+00 	 & 10 & 177 	 & +0.060 & +0.069 & +0.039 & +0.029 \\ 
+ 1.0e-06 	 & 1.0e-01 	 & 10 & 302 	 & +0.011 & +0.039 & +0.039 & +0.038 \\ 
+ 1.0e-06 	 & 1.0e-02 	 & 10 & 457 	 & +0.011 & +0.055 & +0.036 & +0.050 \\ 
+ 1.0e-06 	 & 1.0e-03 	 & 10 & 738 	 & -0.022 & +0.055 & +0.042 & +0.172 \\ 
+\rowcolor{red}  1.0e-06 	 & 1.0e-04 	 & 10 & 1001 	 & -0.043 & +0.042 & +0.054 & +1.180 \\ 
+\rowcolor{red}  1.0e-06 	 & 1.0e-05 	 & 10 & 1001 	 & +0.006 & +0.052 & +0.033 & +3.365 \\ 
+\rowcolor{red}  1.0e-06 	 & 1.0e-06 	 & 10 & 1001 	 & -0.002 & +0.065 & +0.051 & +3.402 \\ 
 \end{tabular}}

### 2018-10-01 tex/paper.tex
updaet

@@
 
-The discovery of the paravascular pathway in 2011~\cite{iliff2012paravascular} which later was found to be particularly active during sleep~\cite{xie2013sleep}. 
+A novel pathway called the paravascular pathway was discoved in 2011~\cite{iliff2012paravascular} and later found to be particularly active during sleep~\cite{xie2013sleep}. 
 It has been proposed that this pathway plays an important role in the waste

### 2018-10-01 tex/paper.tex
text added

--- 2018-10-01 tex/paper.tex
@@
 \usepackage[table,x11names]{xcolor}
+\usepackage{geometry}
 \title{Assessing glymphatic transport velocities by adjoint methods}
@@
 
-The discovery of the paravascular pathway in 2011~\cite{iliff2012paravascular} which later was found to be particularly active during sleep~\cite{xie2013sleep}. 
-It has been proposed that this pathway plays an important role in the waste
-clearance of the brain. In particular, since the brain lack a lymphatic system, 
-which elsewhere in our body plays a crucial role in waste clearance, the system has been called the glymphatic system~\cite{jessen2015glymphatic}.  
-The glymphatic system remains controversial and modeling attempts
-has so far mostly failed to explain the biomechanics of the system~\cite{holter2017interstitial, smith2017glymphatic}. A proper biomechanical 
-understanding of the pathway has significant potential because
-dementia such as Alzheimer´s and Parkinson´s diseases are
-associated with accumulation of metabolic waste such as
-amyloid-beta and CSF-tau.
+The discovery of the paravascular pathway in 2011~\cite{iliff2012paravascular} propose a novel component
+crucial to the metabolism of the brain which may potientially provide an explanation for the accumulation of
+waste such as amyloid beta in elderly, ultimately leading to diseases such as Alzheimer and Parkinson. 
+In the rest of our body, the lymphatic system plays an important role
+in the clearance of metabolic waste, but there are no lymphs within the brain. This fact is puzzling in particular because
+the brain requires around 10 times more energy per volume than the result of the body. The paravascular 
+pathway is proposed important to waste clearance and has therefore been named the \emph{glymphatic system}.
 
-In \cite{ringstad2018brain} brainwide distribution of MRI-contrast was demonstrated during 24 hours after lumbar contrast injection.
-Brain wide distribution by diffusion alone was deemed unlikely by the authors (some of which are part
-of this study as well). The argument was based on analytical considerations where it was calculated that 50\% contrast enrichment would occur after 
-55 hours using the error function which is valid for planar diffusion. However, 
-the surface of the brain is folded and is around five times larger than 
-a corresponding surface of a ball with the same volume. Hence, 
-a more rigorous modeling attempt is warrented. Complicating factors
-are however that the contrast in the surrounding CSF is heterogenous
-and changes significantly during the 24 hours of the investigations. 
-Furthermore, images were obtained only at a few time-points during the investigations in \cite{ringstad2018brain}.
+The pioneering works of Sykov{\'a} and Nicholson~\cite{sykova2008diffusion} demonstrated
+that diffusion was a governing transport mechanism in the brain. However, 
+the clearance of CSF-tracers during sleep~\cite{xie2013sleep} in mice demonstrated transportation
+much faster what could be explained by diffusion and it was proposed that arterial pulsation powered
+accelrated perivascular flow combined convective interstitial flow. Several modelling attempts
+have put the theory to the test~\cite{asgari2016glymphatic, smith2017glymphatic, holter2017interstitial}, 
+but so far computational modeling have failed to adequately described the mechanism.
 
-Our purpose in this paper is to attempt a more rigorous methodology 
-for assessing the apparent diffusion process. To this end we employ
-adjoint methods to determine the apparent diffusion coefficient 
-that would explain the tracer distribution.
+Transportation by diffusion is in the order of XXX\comment{Lars: hente fra R. Thorne / Nicholson}. 
+However, in \cite{xie2013sleep} a 60% coverage of 3kDa Texas Red Dextran of a $200 \mu m$ cube was demostrated in approximately 
+20 minutes. As such, the transportation is XXX faster than what diffusion would provide. Furthermore, 
+in \cite{eidevalnes} it was demonstrated that X Da Gadovist was brainwide in 8 hours after injection in the lumbar region.
 
-\section{Methodology}
+Paragraph about timescales etc.
+
+The purpose of this paper is to attempt to assess transportation speed in terms of an apparent diffusion coefficient 
+by using adjoint methods provided by \cite{} for optimizing the coefficient with respect to data. As
+such a coefficient larger than commonly reported values of diffusion would suggest that at the
+timescale of minutes to hours there is indeed a glymphatic transportation which may potentially 
+be responsible for metabolic waste.
+
+An outline of the paper is as follows. In Section 2 we descibe the medical images and their modality,  
+and the mathematical methodology used for determining the apparent diffusion coefficients.
+
+\section{Methods}
 
@@
 The observation points are distributed with 5 observations within 1-2 hours after injection, 1 observation in the timeframes 2-4 hours, 6-9 hours, 24 hours and 48 hours.
-Figure ~\ref{fig1} shows the distribution of tracers during 24 hours, see also~\cite{ringstad2017glymphatic}.
-
-\begin{figure}
-\includegraphics[width=0.95\textwidth]{GMRI.png} 
-\label{fig1} 
-\caption{\comment{lars, we will need some new images since I believe this is stolen from JCI. Also include a zoom on the region of interest}}
-\end{figure}
 
 \subsection*{Mathematical Model}
-In order to assess whether the contrast distribution shown 
-in Figure \ref{fig1} is governed by a diffusion process we
-aim to solve a PDE constrained optimization problem where
-the contrast distribution, boundary conditions, and apparent
-diffusion coefficition are solved for by optimizing with
-respect to the observed contrast distribution.  
 The objective function was defined as 
@@
 \end{equation}
-subject to 
+subjugated by   
 \begin{equation}
@@
 \end{equation}
-Here $u$ is the contrast distribution, $D_i$ is the apparent diffusion 
-coefficient, and $g$ is the boundary condition. Furthermore,  
-the domain $\Omega$ contains three sub domains, each with a different diffusion coefficient.
+with the domain $\Omega$ contains three sub domains, each with a different diffusion coefficient.
 We denote the Cerebral Spinal fluid (CSF) domain as $\Omega_1$, the grey matter as $\Omega_2$ and the white matter as $\Omega_3$.
-The apparent
-diffusion constant is assumed constant within the CSF, grey and 
-white matter but each region may have different constants.  
-The $\alpha$ and $\beta$ parameters are regularization parameters 
-and $u_{obs}$ are observations at certain time-points.
 
-\subsection*{Manufactured Solution}
-In order to verify our strategy and test the dependency of the
-regularization paramters, we perform a test case with a
-known solution.  
+\section*{Manufactured Solution}
 The manufactured observations was obtained by forward computation of Eq.\ref{Eq::PDE} with the Dirichlet boundary condition defined as
@@
 g(t)_{\partial \Omega_1} = 0.3 +0.167t - 0.007t\sp{2} \qquad  0 \leq t \leq 24.
+\label{EQ::DIRI}
 \end{equation}
@@
 \section*{Implementation}
-The code used the FEniCS project to sole the PDE, using backwards Euler time discretization and first order continuous Galerkin finite elements.
+The code used the FEniCS project to solve the PDE, using backwards Euler time discretization and first order continuous Galerkin finite elements.
 The module dolfin adjoint [?] was used to compute the reduced functional, and the optimization used the scipy optimize library to minimize the functional using L-BFGS-B algorithm.
@@
 
-Linear interpolation of the forward problem was used to compute the difference from the observation,
-
+The times in the forward simulation do not always overlap with observations times. Thus a linear interpolation of the forward problem was used to compute the difference from the observation, i.e 
+\begin{equation}
+u        d U_prev + \Delta t - dt U.
+\end{equation}
+Here $dt$ is forward timestep and $\Delta t$ is the difference between ?? 
 The initial values of the optimization algorithm was chosen to be $1,1,1$.
@@
 The noise term was constructed using numpy random and multiplied with a noise amplitude.
-The noise amplitudes were chosen to be $ 5\%, 10\%, 50\%, 100\%$ of the maximum initial boundary conditions, so that negative concentrations are avoided.
+The noise amplitudes were chosen to be $ 10\%, 50\%, 100\%$ of the maximum initial boundary conditions, so that negative concentrations are avoided.
+
+The real data observations had observation times that had an unevenly distribution over 24 hours.
+Thus having  constant time between observations is not realsitic.
+Therefore the number of observation and the unevenly distribution of them will be tested.
+To accurately depict the real data observations.
 
@@
 
+\subsection{The relaxation parameters}
+The relaxation parameters needs to be calibrated depending on the problem, and thus the diffusion parameters were computed by large range of relaxation parameters values.
+The results are shown in Tab.\ref{Tab::1}, and it is shown in red that $\alpha=1.0$ have large discrepancy in the parameters values of $D_{\Omega_1}$.
+
+\subsection{The number of timessteps}
+The first results focus on the accuracy of the minimization based on the number of time steps.
+It can be assumed that the error decreases  while the number of time steps increases since the Dirichlet boundary condition in Eq.\ref{EQ::DIRI} are quadratic, while the forward problem is a linear approximation.
+
+This can be seen in Tab.??, Tab.??
+
+In Tab.\ref{Tab::1}, we can see that the
+
+\subsection{The number of observations}
+The number of observations can also be considered an important aspect, since the number of observations can be limited. Thus the number of observations set to $5,10 $ and $20$, and
+
+\subsection{The noise susceptibility}
+
+The noise susceptibility can be seen in Tab. ?? and Tab. ??, and we see that a noise amplitude of $10 \%$ does not lead to significant change
+
+\section{Discussion}
+
+The diffusion equation does not pose any difficulties numerically
+
+This method can be adapted to
+
+\newpage 
+\newgeometry{top=0.5cm}
+
 \begin{table}
@@
 }
-\resizebox{\textwidth}{!}{\begin{tabular}{*{8}c}
+\resizebox{0.9\textwidth}{!}{\begin{tabular}{*{8}c}
 $\alpha$ & $\beta$ & k  & iter & $ D_{\Omega_1} = 1000$ & $ D_{\Omega_2} = 4.0 $ & $D_{\Omega_3} = 8.0 $ & $g$ \\
@@
 \centering
-\caption{Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$ and number of observation $\tau$ with the resulting number of iterations and estimated optimal parameters for the diffusion coefficients.
-}
+\caption{ tau = double  }
 \resizebox{\textwidth}{!}{\begin{tabular}{*{8}c}
-$\alpha$ & $\beta$ & k  & iter & $ D_{\Omega_1} = 1000$ & $ D_{\Omega_2} = 4.0 $ & $D_{\Omega_3} = 8.0 $ & $g$ \\
+$\alpha$ & $\beta$ & k  & iter & $ D_{\Omega_1} = 1000$ & $ D_{\Omega_2} = 4.0 $ & $D_{\Omega_3} = 8.0 $ & wrong$g$ \\
 \hline
- 1.0e-01 	 & 1.0e+00 	 & 20 & 221 	 & +0.155 & +0.056 & +0.020 & +0.464 \\ 
- 1.0e-01 	 & 1.0e-01 	 & 20 & 218 	 & +0.422 & +0.185 & +0.029 & +0.485 \\ 
- 1.0e-01 	 & 1.0e-02 	 & 20 & 332 	 & +0.925 & +0.484 & +0.047 & +0.569 \\ 
- 1.0e-01 	 & 1.0e-03 	 & 20 & 327 	 & +1.140 & +0.629 & +0.057 & +0.608 \\ 
- 1.0e-01 	 & 1.0e-04 	 & 20 & 320 	 & +1.175 & +0.652 & +0.059 & +0.615 \\ 
- 1.0e-01 	 & 1.0e-05 	 & 20 & 308 	 & +1.173 & +0.654 & +0.059 & +0.615 \\ 
- 1.0e-02 	 & 1.0e+00 	 & 20 & 251 	 & +0.008 & +0.009 & +0.014 & +0.460 \\ 
- 1.0e-02 	 & 1.0e-01 	 & 20 & 214 	 & +0.062 & +0.029 & +0.009 & +0.457 \\ 
- 1.0e-02 	 & 1.0e-02 	 & 20 & 331 	 & +0.155 & +0.080 & +0.003 & +0.475 \\ 
- 1.0e-02 	 & 1.0e-03 	 & 20 & 537 	 & +0.209 & +0.113 & -0.000 & +0.537 \\ 
- 1.0e-02 	 & 1.0e-04 	 & 20 & 488 	 & +0.222 & +0.122 & -0.001 & +0.561 \\ 
- 1.0e-02 	 & 1.0e-05 	 & 20 & 512 	 & +0.223 & +0.121 & -0.001 & +0.567 \\ 
- 1.0e-03 	 & 1.0e+00 	 & 20 & 256 	 & -0.006 & +0.004 & +0.013 & +0.461 \\ 
- 1.0e-03 	 & 1.0e-01 	 & 20 & 258 	 & +0.032 & +0.012 & +0.008 & +0.459 \\ 
- 1.0e-03 	 & 1.0e-02 	 & 20 & 287 	 & +0.077 & +0.029 & +0.005 & +0.458 \\ 
- 1.0e-03 	 & 1.0e-03 	 & 20 & 331 	 & +0.107 & +0.044 & +0.003 & +0.471 \\ 
- 1.0e-03 	 & 1.0e-04 	 & 20 & 576 	 & +0.095 & +0.041 & +0.004 & +0.520 \\ 
- 1.0e-03 	 & 1.0e-05 	 & 20 & 507 	 & +0.089 & +0.044 & +0.004 & +0.530 \\ 
- 1.0e-04 	 & 1.0e+00 	 & 20 & 187 	 & -0.007 & +0.004 & +0.013 & +0.461 \\ 
- 1.0e-04 	 & 1.0e-01 	 & 20 & 315 	 & +0.028 & +0.010 & +0.008 & +0.459 \\ 
- 1.0e-04 	 & 1.0e-02 	 & 20 & 396 	 & +0.067 & +0.023 & +0.005 & +0.459 \\ 
- 1.0e-04 	 & 1.0e-03 	 & 20 & 242 	 & +0.103 & +0.038 & +0.003 & +0.463 \\ 
- 1.0e-04 	 & 1.0e-04 	 & 20 & 207 	 & +0.100 & +0.035 & +0.003 & +0.466 \\ 
- 1.0e-04 	 & 1.0e-05 	 & 20 & 457 	 & +0.080 & +0.035 & +0.003 & +0.483 \\ 
- 1.0e-05 	 & 1.0e+00 	 & 20 & 215 	 & -0.006 & +0.004 & +0.013 & +0.461 \\ 
- 1.0e-05 	 & 1.0e-01 	 & 20 & 244 	 & +0.028 & +0.010 & +0.008 & +0.459 \\ 
- 1.0e-05 	 & 1.0e-02 	 & 20 & 399 	 & +0.070 & +0.024 & +0.005 & +0.460 \\ 
- 1.0e-05 	 & 1.0e-03 	 & 20 & 267 	 & +0.108 & +0.040 & +0.003 & +0.463 \\ 
- 1.0e-05 	 & 1.0e-04 	 & 20 & 361 	 & +0.089 & +0.034 & +0.003 & +0.473 \\ 
- 1.0e-05 	 & 1.0e-05 	 & 20 & 298 	 & +0.101 & +0.036 & +0.003 & +0.473 \\ 
- 1.0e-06 	 & 1.0e+00 	 & 20 & 240 	 & -0.007 & +0.004 & +0.013 & +0.461 \\ 
- 1.0e-06 	 & 1.0e-01 	 & 20 & 269 	 & +0.027 & +0.009 & +0.008 & +0.459 \\ 
- 1.0e-06 	 & 1.0e-02 	 & 20 & 314 	 & +0.070 & +0.025 & +0.005 & +0.459 \\ 
- 1.0e-06 	 & 1.0e-03 	 & 20 & 214 	 & +0.102 & +0.038 & +0.002 & +0.462 \\ 
- 1.0e-06 	 & 1.0e-04 	 & 20 & 437 	 & +0.079 & +0.032 & +0.004 & +0.475 \\ 
- 1.0e-06 	 & 1.0e-05 	 & 20 & 353 	 & +0.088 & +0.033 & +0.005 & +0.478 \\ 
+ 1.0e-05 	 & 1.0e-02 	 & 20 & 429 	 & +0.003 & +0.018 & +0.005 & +0.007 \\ 
+ 1.0e-06 	 & 1.0e+00 	 & 20 & 219 	 & -0.008 & +0.016 & +0.009 & +0.006 \\ 
+ 1.0e-06 	 & 1.0e-02 	 & 20 & 386 	 & +0.003 & +0.018 & +0.005 & +0.007 \\ 
 \end{tabular}}
-\label{Tab::1}
+\label{Tab::2}
+\end{table}
+
+\begin{table}
+\centering
+\caption{ tau = double  }
+\resizebox{\textwidth}{!}{\begin{tabular}{*{8}c}
+$\alpha$ & $\beta$ & k  & iter & $ D_{\Omega_1} = 1000$ & $ D_{\Omega_2} = 4.0 $ & $D_{\Omega_3} = 8.0 $ & wrong$g$ \\
+\hline
+ 1.0e-05 	 & 1.0e-03 	 & 40 & 210 	 & +0.019 & +0.005 & -0.001 & +0.002 \\ 
+ 1.0e-05 	 & 1.0e-01 	 & 40 & 597 	 & +0.006 & +0.015 & -0.008 & +0.017 \\ 
+ 1.0e-06 	 & 1.0e-02 	 & 40 & 910 	 & +0.046 & +0.047 & -0.020 & +0.065 \\ 
+\end{tabular}}
+\label{Tab::2}
 \end{table}
@@
 \resizebox{\textwidth}{!}{\begin{tabular}{*{8}c}
-$\alpha$ & $\beta$ & k  & iter & $ D_{\Omega_1} $ & $ D_{\Omega_2} $ & $D_{\Omega_3} $ & $g$ \\
+$\alpha$ & $\beta$ & k  & iter & $ D_{\Omega_1} $ & $ D_{\Omega_2} $ & $D_{\Omega_3} $ & wrong $g$ \\
 \hline
- 1.0e+00 	 & 1.0e+00 	 & 10 & 205 	 & +4.270 & +0.303 & +0.091 & +0.589 \\ 
- 1.0e+00 	 & 1.0e-01 	 & 10 & 190 	 & +4.270 & +0.306 & +0.091 & +0.596 \\ 
- 1.0e+00 	 & 1.0e-02 	 & 10 & 244 	 & +4.523 & +0.304 & +0.091 & +0.597 \\ 
- 1.0e+00 	 & 1.0e-03 	 & 10 & 204 	 & +4.275 & +0.306 & +0.091 & +0.597 \\ 
- 1.0e+00 	 & 1.0e-04 	 & 10 & 205 	 & +4.272 & +0.306 & +0.090 & +0.597 \\ 
- 1.0e+00 	 & 1.0e-05 	 & 10 & 185 	 & +4.272 & +0.305 & +0.090 & +0.597 \\ 
- 1.0e+00 	 & 1.0e-06 	 & 10 & 223 	 & +4.538 & +0.303 & +0.091 & +0.597 \\ 
- 1.0e-01 	 & 1.0e+00 	 & 10 & 179 	 & +0.125 & +0.095 & +0.040 & +0.488 \\ 
- 1.0e-01 	 & 1.0e-01 	 & 10 & 141 	 & +0.123 & +0.093 & +0.040 & +0.506 \\ 
- 1.0e-01 	 & 1.0e-02 	 & 10 & 201 	 & +0.124 & +0.093 & +0.040 & +0.515 \\ 
- 1.0e-01 	 & 1.0e-03 	 & 10 & 207 	 & +0.126 & +0.093 & +0.041 & +0.516 \\ 
- 1.0e-01 	 & 1.0e-04 	 & 10 & 162 	 & +0.125 & +0.093 & +0.040 & +0.516 \\ 
- 1.0e-01 	 & 1.0e-05 	 & 10 & 209 	 & +0.121 & +0.093 & +0.041 & +0.516 \\ 
- 1.0e-01 	 & 1.0e-06 	 & 10 & 147 	 & +0.123 & +0.093 & +0.041 & +0.516 \\ 
- 1.0e-02 	 & 1.0e+00 	 & 10 & 221 	 & +0.017 & +0.067 & +0.039 & +0.481 \\ 
- 1.0e-02 	 & 1.0e-01 	 & 10 & 138 	 & +0.005 & +0.065 & +0.040 & +0.483 \\ 
- 1.0e-02 	 & 1.0e-02 	 & 10 & 174 	 & +0.006 & +0.065 & +0.040 & +0.500 \\ 
- 1.0e-02 	 & 1.0e-03 	 & 10 & 227 	 & +0.007 & +0.066 & +0.039 & +0.510 \\ 
- 1.0e-02 	 & 1.0e-04 	 & 10 & 164 	 & +0.004 & +0.065 & +0.040 & +0.509 \\ 
- 1.0e-02 	 & 1.0e-05 	 & 10 & 223 	 & +0.006 & +0.065 & +0.040 & +0.512 \\ 
- 1.0e-02 	 & 1.0e-06 	 & 10 & 179 	 & +0.007 & +0.065 & +0.040 & +0.510 \\ 
- 1.0e-03 	 & 1.0e+00 	 & 10 & 178 	 & +0.005 & +0.064 & +0.039 & +0.481 \\ 
- 1.0e-03 	 & 1.0e-01 	 & 10 & 182 	 & -0.007 & +0.062 & +0.040 & +0.481 \\ 
- 1.0e-03 	 & 1.0e-02 	 & 10 & 94 	 & -0.006 & +0.062 & +0.038 & +0.487 \\ 
- 1.0e-03 	 & 1.0e-03 	 & 10 & 108 	 & -0.005 & +0.063 & +0.039 & +0.489 \\ 
- 1.0e-03 	 & 1.0e-04 	 & 10 & 136 	 & -0.008 & +0.062 & +0.040 & +0.490 \\ 
- 1.0e-03 	 & 1.0e-05 	 & 10 & 93 	 & -0.006 & +0.063 & +0.040 & +0.489 \\ 
- 1.0e-03 	 & 1.0e-06 	 & 10 & 81 	 & -0.006 & +0.062 & +0.040 & +0.489 \\ 
- 1.0e-04 	 & 1.0e+00 	 & 10 & 166 	 & +0.007 & +0.064 & +0.039 & +0.482 \\ 
- 1.0e-04 	 & 1.0e-01 	 & 10 & 273 	 & -0.007 & +0.062 & +0.040 & +0.481 \\ 
- 1.0e-04 	 & 1.0e-02 	 & 10 & 103 	 & -0.004 & +0.062 & +0.040 & +0.487 \\ 
- 1.0e-04 	 & 1.0e-03 	 & 10 & 147 	 & -0.008 & +0.062 & +0.039 & +0.488 \\ 
- 1.0e-04 	 & 1.0e-04 	 & 10 & 103 	 & -0.007 & +0.062 & +0.039 & +0.488 \\ 
- 1.0e-04 	 & 1.0e-05 	 & 10 & 136 	 & -0.007 & +0.063 & +0.039 & +0.488 \\ 
- 1.0e-04 	 & 1.0e-06 	 & 10 & 103 	 & -0.010 & +0.062 & +0.040 & +0.488 \\ 
- 1.0e-05 	 & 1.0e+00 	 & 10 & 230 	 & +0.001 & +0.064 & +0.038 & +0.482 \\ 
- 1.0e-05 	 & 1.0e-01 	 & 10 & 237 	 & -0.009 & +0.062 & +0.040 & +0.481 \\ 
- 1.0e-05 	 & 1.0e-02 	 & 10 & 172 	 & -0.008 & +0.062 & +0.039 & +0.482 \\ 
- 1.0e-05 	 & 1.0e-03 	 & 10 & 116 	 & -0.009 & +0.063 & +0.039 & +0.488 \\ 
- 1.0e-05 	 & 1.0e-04 	 & 10 & 124 	 & -0.007 & +0.062 & +0.040 & +0.488 \\ 
- 1.0e-05 	 & 1.0e-05 	 & 10 & 97 	 & -0.007 & +0.063 & +0.038 & +0.488 \\ 
- 1.0e-05 	 & 1.0e-06 	 & 10 & 129 	 & -0.007 & +0.062 & +0.039 & +0.488 \\ 
- 1.0e-06 	 & 1.0e+00 	 & 10 & 199 	 & +0.002 & +0.063 & +0.039 & +0.482 \\ 
- 1.0e-06 	 & 1.0e-01 	 & 10 & 245 	 & -0.005 & +0.063 & +0.039 & +0.481 \\ 
- 1.0e-06 	 & 1.0e-02 	 & 10 & 206 	 & -0.003 & +0.062 & +0.039 & +0.482 \\ 
- 1.0e-06 	 & 1.0e-03 	 & 10 & 159 	 & -0.007 & +0.062 & +0.040 & +0.488 \\ 
- 1.0e-06 	 & 1.0e-04 	 & 10 & 124 	 & -0.011 & +0.062 & +0.040 & +0.488 \\ 
- 1.0e-06 	 & 1.0e-05 	 & 10 & 93 	 & -0.007 & +0.061 & +0.039 & +0.488 \\ 
- 1.0e-06 	 & 1.0e-06 	 & 10 & 115 	 & -0.009 & +0.062 & +0.039 & +0.488 \\ 
+
 \end{tabular}}
-\label{Tab::1}
+\label{Tab::3}
 \end{table}
 
+\newpage
 \begin{table}
@@
 Noise 0.03 amp }
-\resizebox{\textwidth}{!}{\begin{tabular}{*{8}c}
-$\alpha$ & $\beta$ & k  & iter & $ D_{\Omega_1} $ & $ D_{\Omega_2} $ & $D_{\Omega_3} $ & $g$ \\
+\resizebox{0.8\textwidth}{!}{\begin{tabular}{*{8}c}
+$\alpha$ & $\beta$ & k  & iter & $ D_{\Omega_1} $ & $ D_{\Omega_2} $ & $D_{\Omega_3} $ & wrong $g$ \\
 \hline
@@
  1.0e+00 	 & 1.0e-06 	 & 10 & 263 	 & +4.266 & +0.306 & +0.091 & +0.143 \\
+
  1.0e-01 	 & 1.0e+00 	 & 10 & 167 	 & +0.131 & +0.093 & +0.041 & +0.027 \\ 
@@
  1.0e-01 	 & 1.0e-06 	 & 10 & 201 	 & +0.119 & +0.093 & +0.040 & +0.057 \\
+
  1.0e-02 	 & 1.0e+00 	 & 10 & 183 	 & +0.013 & +0.067 & +0.040 & +0.018 \\ 
@@
  1.0e-02 	 & 1.0e-06 	 & 10 & 185 	 & +0.012 & +0.063 & +0.038 & +0.049 \\
+
  1.0e-03 	 & 1.0e+00 	 & 10 & 183 	 & +0.007 & +0.062 & +0.038 & +0.019 \\ 
@@
  1.0e-03 	 & 1.0e-06 	 & 10 & 132 	 & -0.002 & +0.062 & +0.039 & +0.028 \\
+
  1.0e-04 	 & 1.0e+00 	 & 10 & 176 	 & +0.000 & +0.063 & +0.039 & +0.019 \\ 
@@
  1.0e-04 	 & 1.0e-06 	 & 10 & 109 	 & -0.007 & +0.062 & +0.039 & +0.027 \\
+
  1.0e-05 	 & 1.0e+00 	 & 10 & 220 	 & +0.005 & +0.063 & +0.039 & +0.019 \\ 
@@
  1.0e-05 	 & 1.0e-06 	 & 10 & 147 	 & -0.012 & +0.061 & +0.040 & +0.027 \\
+
  1.0e-06 	 & 1.0e+00 	 & 10 & 138 	 & +0.002 & +0.063 & +0.039 & +0.019 \\ 
@@
 \end{tabular}}
-\label{Tab::1}
+\label{Tab::4}
 \end{table} 
-\begin{table}
+\begin{table}[t]
 \centering
@@
 Noise 0.3 amp }
-\resizebox{\textwidth}{!}{\begin{tabular}{*{8}c}
+\resizebox{0.8\textwidth}{!}{\begin{tabular}{*{8}c}
 $\alpha$ & $\beta$ & k  & iter & $ D_{\Omega_1} $ & $ D_{\Omega_2} $ & $D_{\Omega_3} $ & $g$ \\
@@
  1.0e-03 	 & 1.0e-02 	 & 10 & 565 	 & -0.059 & +0.076 & +0.033 & +0.053 \\ 
- 1.0e-03 	 & 1.0e-03 	 & 10 & 673 	 & -0.035 & +0.066 & +0.032 & +0.108 \\ 
- 1.0e-03 	 & 1.0e-04 	 & 10 & 604 	 & -0.026 & +0.061 & +0.049 & +0.182 \\ 
- 1.0e-03 	 & 1.0e-05 	 & 10 & 666 	 & +0.012 & +0.070 & +0.038 & +0.182 \\ 
- 1.0e-03 	 & 1.0e-06 	 & 10 & 893 	 & +0.027 & +0.070 & +0.022 & +0.180 \\ 
+ \rowcolor{orange} 1.0e-03 	 & 1.0e-03 	 & 10 & 673 	 & -0.035 & +0.066 & +0.032 & +0.108 \\ 
+ \rowcolor{orange} 1.0e-03 	 & 1.0e-04 	 & 10 & 604 	 & -0.026 & +0.061 & +0.049 & +0.182 \\ 
+ \rowcolor{orange} 1.0e-03 	 & 1.0e-05 	 & 10 & 666 	 & +0.012 & +0.070 & +0.038 & +0.182 \\ 
+ \rowcolor{orange} 1.0e-03 	 & 1.0e-06 	 & 10 & 893 	 & +0.027 & +0.070 & +0.022 & +0.180 \\ 
  1.0e-04 	 & 1.0e+00 	 & 10 & 204 	 & +0.015 & +0.062 & +0.043 & +0.030 \\ 
@@
  1.0e-04 	 & 1.0e-02 	 & 10 & 559 	 & -0.072 & +0.067 & +0.044 & +0.050 \\ 
- 1.0e-04 	 & 1.0e-03 	 & 10 & 691 	 & -0.023 & +0.055 & +0.040 & +0.175 \\ 
+\rowcolor{orange} 1.0e-04 	 & 1.0e-03 	 & 10 & 691 	 & -0.023 & +0.055 & +0.040 & +0.175 \\ 
 \rowcolor{red}  1.0e-04 	 & 1.0e-04 	 & 10 & 1001 	 & -0.012 & +0.066 & +0.030 & +0.745 \\ 
@@
  1.0e-05 	 & 1.0e-02 	 & 10 & 399 	 & +0.041 & +0.075 & +0.042 & +0.049 \\ 
- 1.0e-05 	 & 1.0e-03 	 & 10 & 689 	 & +0.044 & +0.062 & +0.020 & +0.172 \\ 
+ \rowcolor{orange} 1.0e-05 	 & 1.0e-03 	 & 10 & 689 	 & +0.044 & +0.062 & +0.020 & +0.172 \\ 
 \rowcolor{red} 1.0e-05 	 & 1.0e-04 	 & 10 & 915 	 & +0.030 & +0.077 & +0.039 & +1.027 \\ 
@@
  1.0e-06 	 & 1.0e-02 	 & 10 & 457 	 & +0.011 & +0.055 & +0.036 & +0.050 \\ 
- 1.0e-06 	 & 1.0e-03 	 & 10 & 738 	 & -0.022 & +0.055 & +0.042 & +0.172 \\ 
+\rowcolor{orange} 1.0e-06 	 & 1.0e-03 	 & 10 & 738 	 & -0.022 & +0.055 & +0.042 & +0.172 \\ 
 \rowcolor{red}  1.0e-06 	 & 1.0e-04 	 & 10 & 1001 	 & -0.043 & +0.042 & +0.054 & +1.180 \\ 
@@
 \end{tabular}}
-\label{Tab::1}
+\label{Tab::5}
 \end{table} 
@@
 \centering
-\caption{ $\tau = [2.4, 4.8, 7.2, 9.6, 12.0, 14.4, 16.8, 19.2, 21.6, 24.0] $}
+\caption{ $\tau = [0.8, 1.0, 1.2, 1.8, 2.4, 3.6, 5.4, 7.6, 24.0] $}
 \resizebox{\textwidth}{!}{\begin{tabular}{*{8}c}
@@
 \hline
- 1.0e-04 	 & 1.0e+00 	 & 40 & 234 	 & -0.017 & -0.019 & +0.005 & +0.459 \\ 
- 1.0e-04 	 & 1.0e-01 	 & 40 & 415 	 & +0.001 & -0.007 & +0.004 & +0.457 \\ 
- 1.0e-04 	 & 1.0e-02 	 & 40 & 370 	 & +0.006 & +0.004 & +0.002 & +0.455 \\ 
- 1.0e-05 	 & 1.0e+00 	 & 40 & 296 	 & -0.017 & -0.019 & +0.005 & +0.459 \\ 
- 1.0e-05 	 & 1.0e-01 	 & 40 & 343 	 & +0.001 & -0.007 & +0.004 & +0.457 \\ 
- 1.0e-05 	 & 1.0e-02 	 & 40 & 348 	 & +0.006 & +0.005 & +0.003 & +0.454 \\ 
- 1.0e-06 	 & 1.0e+00 	 & 40 & 311 	 & -0.019 & -0.019 & +0.005 & +0.459 \\ 
- 1.0e-06 	 & 1.0e-01 	 & 40 & 429 	 & -0.000 & -0.007 & +0.004 & +0.457 \\ 
- 1.0e-06 	 & 1.0e-02 	 & 40 & 454 	 & +0.002 & +0.001 & +0.002 & +0.456 \\
-
+ 1.0e-04 	 & 1.0e-02 	 & 40 & 283 	 & -0.059 & -0.020 & -0.027 & +0.331 \\ 
+ \rowcolor{red} 1.0e-04 	 & 1.0e-03 	 & 40 & 247 	 & -0.062 & -0.023 & -0.030 & +0.407 \\ 
+ 1.0e-05 	 & 1.0e-02 	 & 40 & 400 	 & -0.059 & -0.020 & -0.027 & +0.260 \\ 
+\rowcolor{red}  1.0e-05 	 & 1.0e-03 	 & 40 & 183 	 & -0.063 & -0.023 & -0.029 & +0.404 \\ 
+ 1.0e-06 	 & 1.0e+00 	 & 40 & 618 	 & -0.034 & -0.006 & -0.022 & +0.058 \\ 
+ 1.0e-06 	 & 1.0e-01 	 & 40 & 826 	 & -0.046 & -0.013 & -0.024 & +0.070 \\ 
+ 1.0e-06 	 & 1.0e-02 	 & 40 & 632 	 & -0.058 & -0.020 & -0.027 & +0.183 \\ 
+\rowcolor{red}  1.0e-06 	 & 1.0e-03 	 & 40 & 234 	 & -0.062 & -0.023 & -0.030 & +0.398 \\ 
 \end{tabular}}

### 2018-10-01 tex/paper.tex

@@
 
-The discovery of the paravascular pathway in 2011~\cite{iliff2012paravascular} propose a novel component
-crucial to the metabolism of the brain which may potientially provide an explanation for the accumulation of
-waste such as amyloid beta in elderly, ultimately leading to diseases such as Alzheimer and Parkinson. 
-In the rest of our body, the lymphatic system plays an important role
-in the clearance of metabolic waste, but there are no lymphs within the brain. This fact is puzzling in particular because
-the brain requires around 10 times more energy per volume than the result of the body. The paravascular 
-pathway is proposed important to waste clearance and has therefore been named the \emph{glymphatic system}.
+A novel pathway called the paravascular pathway was discoved in 2011~\cite{iliff2012paravascular} and later found to be particularly active during sleep~\cite{xie2013sleep}. 
+It has been proposed that this pathway plays an important role in the waste
+clearance of the brain. In particular, since the brain lack a lymphatic system, 
+which elsewhere in our body plays a crucial role in waste clearance, the system has been called the glymphatic system~\cite{jessen2015glymphatic}.  
+The glymphatic system remains controversial and modeling attempts
+has so far mostly failed to explain the biomechanics of the system~\cite{holter2017interstitial, smith2017glymphatic}. A proper biomechanical 
+understanding of the pathway has significant potential because
+dementia such as Alzheimer´s and Parkinson´s diseases are
+associated with accumulation of metabolic waste such as
+amyloid-beta and CSF-tau.
 
-The pioneering works of Sykov{\'a} and Nicholson~\cite{sykova2008diffusion} demonstrated
-that diffusion was a governing transport mechanism in the brain. However, 
-the clearance of CSF-tracers during sleep~\cite{xie2013sleep} in mice demonstrated transportation
-much faster what could be explained by diffusion and it was proposed that arterial pulsation powered
-accelrated perivascular flow combined convective interstitial flow. Several modelling attempts
-have put the theory to the test~\cite{asgari2016glymphatic, smith2017glymphatic, holter2017interstitial}, 
-but so far computational modeling have failed to adequately described the mechanism.
+In \cite{ringstad2018brain} brainwide distribution of MRI-contrast was demonstrated during 24 hours after lumbar contrast injection.
+Brain wide distribution by diffusion alone was deemed unlikely by the authors (some of which are part
+of this study as well). The argument was based on analytical considerations where it was calculated that 50\% contrast enrichment would occur after 
+55 hours using the error function which is valid for planar diffusion. However, 
+the surface of the brain is folded and is around five times larger than 
+a corresponding surface of a ball with the same volume. Hence, 
+a more rigorous modeling attempt is warrented. Complicating factors
+are however that the contrast in the surrounding CSF is heterogenous
+and changes significantly during the 24 hours of the investigations. 
+Furthermore, images were obtained only at a few time-points during the investigations in \cite{ringstad2018brain}.
 
-Transportation by diffusion is in the order of XXX\comment{Lars: hente fra R. Thorne / Nicholson}. 
-However, in \cite{xie2013sleep} a 60% coverage of 3kDa Texas Red Dextran of a $200 \mu m$ cube was demostrated in approximately 
-20 minutes. As such, the transportation is XXX faster than what diffusion would provide. Furthermore, 
-in \cite{eidevalnes} it was demonstrated that X Da Gadovist was brainwide in 8 hours after injection in the lumbar region.
+Our purpose in this paper is to attempt a more rigorous methodology 
+for assessing the apparent diffusion process. To this end we employ
+adjoint methods to determine the apparent diffusion coefficient 
+that would explain the tracer distribution.
 
-Paragraph about timescales etc.
-
-The purpose of this paper is to attempt to assess transportation speed in terms of an apparent diffusion coefficient 
-by using adjoint methods provided by \cite{} for optimizing the coefficient with respect to data. As
-such a coefficient larger than commonly reported values of diffusion would suggest that at the
-timescale of minutes to hours there is indeed a glymphatic transportation which may potentially 
-be responsible for metabolic waste.
-
-An outline of the paper is as follows. In Section 2 we descibe the medical images and their modality,  
-and the mathematical methodology used for determining the apparent diffusion coefficients.
-
-\section{Methods}
+\section{Methodology}
 

### 2018-10-02 tex/paper.tex
Bilder

--- 2018-10-01 tex/paper.tex
@@
 Transportation by diffusion is in the order of XXX\comment{Lars: hente fra R. Thorne / Nicholson}. 
-However, in \cite{xie2013sleep} a 60% coverage of 3kDa Texas Red Dextran of a $200 \mu m$ cube was demostrated in approximately 
+However, in \cite{xie2013sleep} a $60\%$ coverage of 3kDa Texas Red Dextran of a $200 \mu m$ cube was demostrated in approximately 
 20 minutes. As such, the transportation is XXX faster than what diffusion would provide. Furthermore, 
@@
 
-An outline of the paper is as follows. In Section 2 we descibe the medical images and their modality,  
+An outline of the paper is as follows. In Section 2 we describe the medical images and their modality,  
 and the mathematical methodology used for determining the apparent diffusion coefficients.
@@
 \begin{equation}
-u        d U_prev + \Delta t - dt U.
+u_{linear} = \frac{\Delta t}{dt} U_prev + \frac{dt - \Delta t }{dt} U.
 \end{equation}
-Here $dt$ is forward timestep and $\Delta t$ is the difference between ?? 
+Here $dt$ is forward timestep and $\Delta t$ is the difference between observation time and forward time. 
 The initial values of the optimization algorithm was chosen to be $1,1,1$.
@@
 \begin{figure}
-\includegraphics[width=0.95\textwidth]{GMRI.png} 
+\includegraphics[width=0.95\textwidth]{PatID-68-new-100.png} 
 \label{fig1} 
-\caption{\comment{lars, we will need some new images since I believe this is stolen from JCI}}
+\caption{Shows the percentage intensity increase from baseline at different observation times. }
 \end{figure}
 
-\comment{Lars: bilde av konkret mesh  }
+\begin{figure}
+\includegraphics[width=0.95\textwidth]{Zoom-PatID-68.png} 
+\label{fig1} 
+\caption{Shows the percentage intensity increase from baseline at different observation times in the area corresponding to the generated mesh that is marked red in the left panel.}
+\end{figure}
 
@@
 \label{fig1} 
-\caption{\comment{lars, we will need some new images since I believe this is stolen from JCI}}
+\caption{Shows the mesh created from the baseline MR image with 3 domains. ( wrap ?? ) }
 \end{figure}
@@
 
-\begin{table}
-\centering
-\caption{ tau = double  }
-\resizebox{\textwidth}{!}{\begin{tabular}{*{8}c}
-$\alpha$ & $\beta$ & k  & iter & $ D_{\Omega_1} = 1000$ & $ D_{\Omega_2} = 4.0 $ & $D_{\Omega_3} = 8.0 $ & wrong$g$ \\
-\hline
- 1.0e-05 	 & 1.0e-02 	 & 20 & 429 	 & +0.003 & +0.018 & +0.005 & +0.007 \\ 
- 1.0e-06 	 & 1.0e+00 	 & 20 & 219 	 & -0.008 & +0.016 & +0.009 & +0.006 \\ 
- 1.0e-06 	 & 1.0e-02 	 & 20 & 386 	 & +0.003 & +0.018 & +0.005 & +0.007 \\ 
-\end{tabular}}
-\label{Tab::2}
-\end{table}
-
-\begin{table}
-\centering
-\caption{ tau = double  }
-\resizebox{\textwidth}{!}{\begin{tabular}{*{8}c}
-$\alpha$ & $\beta$ & k  & iter & $ D_{\Omega_1} = 1000$ & $ D_{\Omega_2} = 4.0 $ & $D_{\Omega_3} = 8.0 $ & wrong$g$ \\
-\hline
- 1.0e-05 	 & 1.0e-03 	 & 40 & 210 	 & +0.019 & +0.005 & -0.001 & +0.002 \\ 
- 1.0e-05 	 & 1.0e-01 	 & 40 & 597 	 & +0.006 & +0.015 & -0.008 & +0.017 \\ 
- 1.0e-06 	 & 1.0e-02 	 & 40 & 910 	 & +0.046 & +0.047 & -0.020 & +0.065 \\ 
-\end{tabular}}
-\label{Tab::2}
-\end{table}
-
-\begin{table}
-\centering
-\caption{Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$ and number of observation $\tau$ with the resulting number of iterations and estimated optimal parameters for the diffusion coefficients.
-Noise 0.015 amp }
-\resizebox{\textwidth}{!}{\begin{tabular}{*{8}c}
-$\alpha$ & $\beta$ & k  & iter & $ D_{\Omega_1} $ & $ D_{\Omega_2} $ & $D_{\Omega_3} $ & wrong $g$ \\
-\hline
-
-\end{tabular}}
-\label{Tab::3}
-\end{table}
-
 \newpage
@@
 \centering
-\caption{Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$ and number of observation $\tau$ with the resulting number of iterations and estimated optimal parameters for the diffusion coefficients.
-Noise 0.03 amp }
+\caption{Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$, the resulting number of iterations, the relative error of the estimated optimal parameters for the diffusion coefficients and the relative error for $g$.
+The noise amplitude was set to 0.03, and $\tau =[2.4, 4.8, 7.2, 9.6, 12.0, 14.4, 16.8, 19.2, 21.6, 24.0]$ }
 \resizebox{0.8\textwidth}{!}{\begin{tabular}{*{8}c}
@@
 \centering
-\caption{Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$ and number of observation $\tau$ with the resulting number of iterations and estimated optimal parameters for the diffusion coefficients.
-Noise 0.3 amp }
+\caption{Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$, the resulting number of iterations, the relative error of the estimated optimal parameters for the diffusion coefficients and the relative error for $g$.
+The noise amplitude was set to 0.3, and $\tau =[2.4, 4.8, 7.2, 9.6, 12.0, 14.4, 16.8, 19.2, 21.6, 24.0]$  }
 \resizebox{0.8\textwidth}{!}{\begin{tabular}{*{8}c}
@@
 \end{table}
-%\begin{table}
-%\centering
-%\caption{ $\tau = [1.0, 1.2, 1.4, 2.8, 4.6, 9.6, 14.4, 18.6, 22.2, 24.0] $}
-%\resizebox{\textwidth}{!}{\begin{tabular}{*{7}c}
-%$\alpha$ & $\beta$ & k & iter & $ D_{\Omega_1} = 1000$ & $ D_{\Omega_2} = 4.0 $ & $D_{\Omega_3} = 8.0 $ \\
-%\hline
-%
-%\label{Tab::1}
-%\end{table} 
-%\section{Discussion}
-%
-%
-%\begin{table}
-%\centering
-%\caption{ $\tau =[1.2, 1.4, 1.8, 2.4, 3.6, 5.4, 7.6, 17.2, 18.6, 20.4, 22.4, 24.0] $}
-%\resizebox{\textwidth}{!}{\begin{tabular}{*{7}c}
-%$\alpha$ & $\beta$ & k & iter & $ D_{\Omega_1} = 1000$ & $ D_{\Omega_2} = 4.0 $ & $D_{\Omega_3} = 8.0 $ \\
-%\hline
-%
-%\end{tabular}}
-%\label{Tab::1}
-%\end{table} 
-\section{Discussion}
 
@@
 \centering
-\caption{ $\tau = [0.8, 1.0, 1.2, 1.8, 2.4, 3.6, 5.4, 7.6, 24.0] $}
+\caption{ $\tau = [4.8, 9.6, 14.4, 19.2, 24.0]$}
 \resizebox{\textwidth}{!}{\begin{tabular}{*{8}c}
-$\alpha$ & $\beta$ & k & iter & $ D_{\Omega_1} = 1000$ & $ D_{\Omega_2} = 4.0 $ & $D_{\Omega_3} = 8.0 $ & $g$ \\
+$\alpha$ & $\beta$ & k & iter & $ D_{\Omega_1} = 1000$ & $ D_{\Omega_2} = 4.0 $ & $D_{\Omega_3} = 8.0 $ \\
 \hline
+ 1.0e-04 	 & 1.0e+00 	 & 10 & 161 	 & +0.081 & +0.027 & +0.049 & +0.023 \\ 
+ 1.0e-04 	 & 1.0e-01 	 & 10 & 185 	 & +0.123 & +0.046 & +0.037 & +0.021 \\ 
+ 1.0e-04 	 & 1.0e-02 	 & 10 & 265 	 & +0.160 & +0.082 & +0.033 & +0.016 \\ 
+ 1.0e-05 	 & 1.0e+00 	 & 10 & 192 	 & +0.083 & +0.026 & +0.049 & +0.023 \\ 
+ 1.0e-05 	 & 1.0e-01 	 & 10 & 223 	 & +0.118 & +0.047 & +0.037 & +0.020 \\ 
+ 1.0e-05 	 & 1.0e-02 	 & 10 & 267 	 & +0.159 & +0.084 & +0.033 & +0.016 \\ 
+ 1.0e-06 	 & 1.0e+00 	 & 10 & 176 	 & +0.082 & +0.026 & +0.049 & +0.023 \\ 
+ 1.0e-06 	 & 1.0e-01 	 & 10 & 229 	 & +0.120 & +0.046 & +0.037 & +0.021 \\ 
+ 1.0e-06 	 & 1.0e-02 	 & 10 & 253 	 & +0.156 & +0.080 & +0.033 & +0.018 \\ 
+ 1.0e-04 	 & 1.0e+00 	 & 20 & 202 	 & +0.007 & -0.050 & +0.017 & +0.028 \\ 
+ 1.0e-04 	 & 1.0e-01 	 & 20 & 336 	 & +0.028 & -0.009 & +0.009 & +0.023 \\
+ 1.0e-04 	 & 1.0e-02 	 & 20 & 320 	 & +0.025 & +0.025 & +0.015 & +0.013 \\ 
+ 1.0e-05 	 & 1.0e+00 	 & 20 & 195 	 & +0.007 & -0.051 & +0.017 & +0.029 \\ 
+ 1.0e-05 	 & 1.0e-01 	 & 20 & 320 	 & +0.029 & -0.011 & +0.009 & +0.026 \\ 
+ 1.0e-05 	 & 1.0e-02 	 & 20 & 351 	 & +0.023 & +0.017 & +0.011 & +0.019 \\ 
+ 1.0e-06 	 & 1.0e+00 	 & 20 & 224 	 & +0.007 & -0.051 & +0.017 & +0.029 \\ 
+ 1.0e-06 	 & 1.0e-01 	 & 20 & 334 	 & +0.027 & -0.012 & +0.009 & +0.026 \\ 
+ 1.0e-06 	 & 1.0e-02 	 & 20 & 340 	 & +0.020 & +0.016 & +0.012 & +0.019 \\ 
+ 1.0e-04 	 & 1.0e+00 	 & 40 & 308 	 & -0.032 & -0.081 & +0.002 & +0.031 \\ 
+ 1.0e-04 	 & 1.0e-01 	 & 40 & 379 	 & -0.004 & -0.033 & -0.006 & +0.026 \\ 
+ 1.0e-04 	 & 1.0e-02 	 & 40 & 377 	 & +0.006 & +0.006 & -0.001 & +0.008 \\ 
+ 1.0e-05 	 & 1.0e+00 	 & 40 & 212 	 & -0.034 & -0.083 & +0.001 & +0.031 \\ 
+ 1.0e-05 	 & 1.0e-01 	 & 40 & 396 	 & -0.007 & -0.036 & -0.006 & +0.028 \\ 
+ 1.0e-05 	 & 1.0e-02 	 & 40 & 374 	 & +0.009 & +0.007 & -0.003 & +0.014 \\ 
+ 1.0e-06 	 & 1.0e+00 	 & 40 & 226 	 & -0.034 & -0.082 & +0.001 & +0.031 \\ 
+ 1.0e-06 	 & 1.0e-01 	 & 40 & 313 	 & -0.007 & -0.037 & -0.006 & +0.030 \\ 
+ 1.0e-06 	 & 1.0e-02 	 & 40 & 368 	 & +0.006 & +0.006 & -0.004 & +0.013 \\ 
+\end{tabular}}
+\end{table}
+
+\begin{table}
+\centering
+\caption{ Shows the $\tau = [1.2, 2.4, 3.6, 4.8, 6.0, 7.2, 8.4, 9.6, 10.8, 12.0, 13.2, 14.4, 15.6, 16.8, 17.0, 19.2, 20.4, 21.6, 22.8, 24.0] $}
+\resizebox{\textwidth}{!}{\begin{tabular}{*{8}c}
+$\alpha$ & $\beta$ & k & iter & $ D_{\Omega_1} = 1000$ & $ D_{\Omega_2} = 4.0 $ & $D_{\Omega_3} = 8.0 $ \\
+\hline
+ 1.0e-04 	 & 1.0e+00 	 & 10 & 246 	 & -0.046 & +0.038 & +0.023 & +0.031 \\ 
+ 1.0e-04 	 & 1.0e-01 	 & 10 & 292 	 & -0.052 & +0.038 & +0.024 & +0.032 \\ 
+ 1.0e-04 	 & 1.0e-02 	 & 10 & 338 	 & -0.053 & +0.038 & +0.024 & +0.032 \\ 
+ 1.0e-05 	 & 1.0e+00 	 & 10 & 290 	 & -0.047 & +0.038 & +0.023 & +0.031 \\ 
+ 1.0e-05 	 & 1.0e-01 	 & 10 & 316 	 & -0.052 & +0.038 & +0.024 & +0.032 \\ 
+ 1.0e-05 	 & 1.0e-02 	 & 10 & 389 	 & -0.052 & +0.038 & +0.024 & +0.033 \\ 
+ 1.0e-06 	 & 1.0e+00 	 & 10 & 282 	 & -0.047 & +0.038 & +0.023 & +0.031 \\ 
+ 1.0e-06 	 & 1.0e-01 	 & 10 & 308 	 & -0.052 & +0.038 & +0.024 & +0.032 \\ 
+ 1.0e-06 	 & 1.0e-02 	 & 10 & 285 	 & -0.052 & +0.038 & +0.024 & +0.032 \\ 
+ 1.0e-04 	 & 1.0e+00 	 & 20 & 228 	 & -0.008 & +0.016 & +0.009 & +0.006 \\ 
+ 1.0e-04 	 & 1.0e-01 	 & 20 & 331 	 & -0.001 & +0.018 & +0.006 & +0.006 \\ 
+ 1.0e-04 	 & 1.0e-02 	 & 20 & 367 	 & +0.003 & +0.018 & +0.005 & +0.007 \\ 
+ 1.0e-05 	 & 1.0e+00 	 & 20 & 194 	 & -0.008 & +0.016 & +0.009 & +0.006 \\ 
+ 1.0e-05 	 & 1.0e-01 	 & 20 & 312 	 & -0.001 & +0.018 & +0.006 & +0.006 \\ 
+ 1.0e-05 	 & 1.0e-02 	 & 20 & 266 	 & +0.004 & +0.018 & +0.005 & +0.007 \\ 
+ 1.0e-06 	 & 1.0e+00 	 & 20 & 179 	 & -0.008 & +0.016 & +0.009 & +0.006 \\ 
+ 1.0e-06 	 & 1.0e-01 	 & 20 & 245 	 & -0.002 & +0.018 & +0.006 & +0.006 \\ 
+ 1.0e-06 	 & 1.0e-02 	 & 20 & 362 	 & +0.003 & +0.018 & +0.005 & +0.007 \\ 
+ 1.0e-04 	 & 1.0e+00 	 & 40 & 279 	 & -0.007 & +0.000 & +0.003 & +0.002 \\ 
+ 1.0e-04 	 & 1.0e-01 	 & 40 & 313 	 & +0.004 & +0.003 & +0.000 & +0.002 \\ 
+ 1.0e-04 	 & 1.0e-02 	 & 40 & 273 	 & +0.017 & +0.006 & -0.001 & +0.001 \\ 
+ 1.0e-05 	 & 1.0e+00 	 & 40 & 238 	 & -0.007 & +0.000 & +0.002 & +0.002 \\ 
+ 1.0e-05 	 & 1.0e-01 	 & 40 & 317 	 & +0.004 & +0.003 & +0.000 & +0.002 \\ 
+ 1.0e-05 	 & 1.0e-02 	 & 40 & 336 	 & +0.015 & +0.005 & -0.001 & +0.001 \\ 
+ 1.0e-06 	 & 1.0e+00 	 & 40 & 261 	 & -0.007 & +0.000 & +0.002 & +0.002 \\ 
+ 1.0e-06 	 & 1.0e-01 	 & 40 & 318 	 & +0.004 & +0.003 & +0.000 & +0.002 \\ 
+ 1.0e-06 	 & 1.0e-02 	 & 40 & 375 	 & +0.015 & +0.005 & -0.001 & +0.001 \\ 
+\end{tabular}}
+\end{table}
+
+\begin{table}
+\centering
+\caption{$\tau = [0.8, 1.0, 1.2, 1.8, 2.4, 3.6, 5.4, 7.6, 24.0] $ noise 0.0}
+\resizebox{\textwidth}{!}{\begin{tabular}{*{8}c}
+$\alpha$ & $\beta$ & k & iter & $ D_{\Omega_1} = 1000$ & $ D_{\Omega_2} = 4.0 $ & $D_{\Omega_3} = 8.0 $ \\
+ 1.0e-04 	 & 1.0e+00 	 & 40 & 517 	 & -0.034 & -0.006 & -0.022 & +0.058 \\ 
+ 1.0e-04 	 & 1.0e-01 	 & 40 & 660 	 & -0.045 & -0.013 & -0.024 & +0.052 \\ 
  1.0e-04 	 & 1.0e-02 	 & 40 & 283 	 & -0.059 & -0.020 & -0.027 & +0.331 \\ 
- \rowcolor{red} 1.0e-04 	 & 1.0e-03 	 & 40 & 247 	 & -0.062 & -0.023 & -0.030 & +0.407 \\ 
+ 1.0e-05 	 & 1.0e+00 	 & 40 & 588 	 & -0.034 & -0.006 & -0.022 & +0.060 \\ 
+ 1.0e-05 	 & 1.0e-01 	 & 40 & 686 	 & -0.046 & -0.013 & -0.024 & +0.067 \\ 
  1.0e-05 	 & 1.0e-02 	 & 40 & 400 	 & -0.059 & -0.020 & -0.027 & +0.260 \\ 
-\rowcolor{red}  1.0e-05 	 & 1.0e-03 	 & 40 & 183 	 & -0.063 & -0.023 & -0.029 & +0.404 \\ 
  1.0e-06 	 & 1.0e+00 	 & 40 & 618 	 & -0.034 & -0.006 & -0.022 & +0.058 \\ 
@@
  1.0e-06 	 & 1.0e-02 	 & 40 & 632 	 & -0.058 & -0.020 & -0.027 & +0.183 \\
-\rowcolor{red}  1.0e-06 	 & 1.0e-03 	 & 40 & 234 	 & -0.062 & -0.023 & -0.030 & +0.398 \\ 
+
 \end{tabular}}
-\label{Tab::Incoherence}
+\label{Tab::1}
 \end{table} 
-\section{Discussion}
+\begin{table}
+\centering
+\caption{$\tau = [0.8, 1.0, 1.2, 1.8, 2.4, 3.6, 5.4, 7.6, 24.0] $ noise 0.3}
+\resizebox{\textwidth}{!}{\begin{tabular}{*{8}c}
+$\alpha$ & $\beta$ & k & iter & $ D_{\Omega_1} = 1000$ & $ D_{\Omega_2} = 4.0 $ & $D_{\Omega_3} = 8.0 $ \\
+\hline
+ 1.0e-04 	 & 1.0e+00 	 & 40 & 519 	 & +0.003 & +0.029 & +0.035 & +0.067 \\ 
+ 1.0e-04 	 & 1.0e-01 	 & 40 & 653 	 & -0.096 & +0.015 & +0.016 & +0.070 \\ 
+\rowcolor{red}  1.0e-04 	 & 1.0e-02 	 & 40 & 575 	 & -0.050 & -0.001 & +0.057 & +0.281 \\ 
+ 1.0e-05 	 & 1.0e+00 	 & 40 & 585 	 & -0.050 & -0.007 & +0.017 & +0.068 \\ 
+ 1.0e-05 	 & 1.0e-01 	 & 40 & 871 	 & -0.023 & +0.024 & +0.019 & +0.079 \\ 
+\rowcolor{red}  1.0e-05 	 & 1.0e-02 	 & 40 & 466 	 & -0.045 & +0.042 & +0.019 & +0.281 \\ 
+ 1.0e-06 	 & 1.0e+00 	 & 40 & 584 	 & -0.045 & +0.019 & +0.006 & +0.071 \\ 
+ 1.0e-06 	 & 1.0e-01 	 & 40 & 546 	 & +0.005 & +0.019 & -0.001 & +0.079 \\ 
+\rowcolor{red}  1.0e-06 	 & 1.0e-02 	 & 40 & 648 	 & -0.074 & -0.008 & +0.041 & +0.227 \\ 
+\end{tabular}}
+\label{Tab::1}
+\end{table}
 

### 2018-10-02 tex/paper.tex
slettet text tilbake

@@
 
-The discovery of the paravascular pathway in 2011~\cite{iliff2012paravascular} propose a novel component
-crucial to the metabolism of the brain which may potientially provide an explanation for the accumulation of
-waste such as amyloid beta in elderly, ultimately leading to diseases such as Alzheimer and Parkinson. 
-In the rest of our body, the lymphatic system plays an important role
-in the clearance of metabolic waste, but there are no lymphs within the brain. This fact is puzzling in particular because
-the brain requires around 10 times more energy per volume than the result of the body. The paravascular 
-pathway is proposed important to waste clearance and has therefore been named the \emph{glymphatic system}.
+A novel pathway called the paravascular pathway was discoved in 2011~\cite{iliff2012paravascular} and later found to be particularly active during sleep~\cite{xie2013sleep}.
 
-The pioneering works of Sykov{\'a} and Nicholson~\cite{sykova2008diffusion} demonstrated
-that diffusion was a governing transport mechanism in the brain. However, 
-the clearance of CSF-tracers during sleep~\cite{xie2013sleep} in mice demonstrated transportation
-much faster what could be explained by diffusion and it was proposed that arterial pulsation powered
-accelrated perivascular flow combined convective interstitial flow. Several modelling attempts
-have put the theory to the test~\cite{asgari2016glymphatic, smith2017glymphatic, holter2017interstitial}, 
-but so far computational modeling have failed to adequately described the mechanism.
-
-Transportation by diffusion is in the order of XXX\comment{Lars: hente fra R. Thorne / Nicholson}. 
-However, in \cite{xie2013sleep} a $60\%$ coverage of 3kDa Texas Red Dextran of a $200 \mu m$ cube was demostrated in approximately 
-20 minutes. As such, the transportation is XXX faster than what diffusion would provide. Furthermore, 
-in \cite{eidevalnes} it was demonstrated that X Da Gadovist was brainwide in 8 hours after injection in the lumbar region.
-
-Paragraph about timescales etc.
-
-The purpose of this paper is to attempt to assess transportation speed in terms of an apparent diffusion coefficient 
-by using adjoint methods provided by \cite{} for optimizing the coefficient with respect to data. As
-such a coefficient larger than commonly reported values of diffusion would suggest that at the
-timescale of minutes to hours there is indeed a glymphatic transportation which may potentially 
-be responsible for metabolic waste.
-
-An outline of the paper is as follows. In Section 2 we describe the medical images and their modality,  
-and the mathematical methodology used for determining the apparent diffusion coefficients.
-
-\section{Methods}
+It has been proposed that this pathway plays an important role in the waste
+clearance of the brain. In particular, since the brain lack a lymphatic system, 
+which elsewhere in our body plays a crucial role in waste clearance, the system has been called the glymphatic system~\cite{jessen2015glymphatic}.  
+The glymphatic system remains controversial and modeling attempts
+has so far mostly failed to explain the biomechanics of the system~\cite{holter2017interstitial, smith2017glymphatic}. A proper biomechanical 
+understanding of the pathway has significant potential because
+dementia such as Alzheimer´s and Parkinson´s diseases are
+associated with accumulation of metabolic waste such as
+amyloid-beta and CSF-tau.  
+In \cite{ringstad2018brain} brainwide distribution of MRI-contrast was demonstrated during 24 hours after lumbar contrast injection.
+Brain wide distribution by diffusion alone was deemed unlikely by the authors (some of which are part
+of this study as well). The argument was based on analytical considerations where it was calculated that 50\% contrast enrichment would occur after 
+55 hours using the error function which is valid for planar diffusion. However, 
+the surface of the brain is folded and is around five times larger than 
+a corresponding surface of a ball with the same volume. Hence, 
+a more rigorous modeling attempt is warrented. Complicating factors
+are however that the contrast in the surrounding CSF is heterogenous
+and changes significantly during the 24 hours of the investigations. 
+Furthermore, images were obtained only at a few time-points during the investigations in \cite{ringstad2018brain}.  
+Our purpose in this paper is to attempt a more rigorous methodology 
+for assessing the apparent diffusion process. To this end we employ
+adjoint methods to determine the apparent diffusion coefficient 
+that would explain the tracer distribution.
 
@@
 The observation points are distributed with 5 observations within 1-2 hours after injection, 1 observation in the timeframes 2-4 hours, 6-9 hours, 24 hours and 48 hours.
+Figure ~\ref{fig1} shows the distribution of tracers during 24 hours, see also~\cite{ringstad2017glymphatic}.
 
 \subsection*{Mathematical Model}
+In order to assess whether the contrast distribution shown 
+in Figure \ref{fig1} is governed by a diffusion process we
+aim to solve a PDE constrained optimization problem where
+the contrast distribution, boundary conditions, and apparent
+diffusion coefficient are solved for by optimizing with
+respect to the observed contrast distribution. 
 The objective function was defined as 
@@
 \end{equation}
-subjugated by   
+subject to   
 \begin{equation}
@@
 
-\section*{Manufactured Solution}
+Here $u$ is the contrast distribution, $D_i$ is the apparent diffusion 
+coefficient, and $g$ is the boundary condition. Furthermore,  
+the domain $\Omega$ contains three sub domains, each with a different diffusion coefficient.
+We denote the Cerebral Spinal fluid (CSF) domain as $\Omega_1$, the grey matter as $\Omega_2$ and the white matter as $\Omega_3$.
+The apparent
+diffusion constant is assumed constant within the CSF, grey and 
+white matter but each region may have different constants.  
+The $\alpha$ and $\beta$ parameters are regularization parameters 
+and $u_{obs}$ are observations at certain time-points. 
+\subsection*{Manufactured Solution}
+In order to verify our strategy and test the dependency of the
+regularization paramters, we perform a test case with a
+known solution.  
 The manufactured observations was obtained by forward computation of Eq.\ref{Eq::PDE} with the Dirichlet boundary condition defined as

### 2018-10-03 tex/paper.tex
updates

@@
 \renewcommand{\comment}[1]{\textcolor{red}{#1}}
+
+\newcommand{\kam}[1]{\textcolor{blue}{#1}}
 
@@
 A novel pathway called the paravascular pathway was discoved in 2011~\cite{iliff2012paravascular} and later found to be particularly active during sleep~\cite{xie2013sleep}.  
-
 It has been proposed that this pathway plays an important role in the waste
@@
 
-\subsection*{Data}
-The data consist of a total of 10 MRI observations, including a baseline MRI taken before tracer was injected.
+\subsection*{MRI Data}
+\begin{figure}
+\includegraphics[width=0.95\textwidth]{PatID-68-new-100.png} 
+\label{fig1} 
+\caption{Shows the percentage intensity increase from baseline at different observation times. }
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=0.95\textwidth]{Zoom-PatID-68.png} 
+\label{fig2} 
+\caption{Shows the percentage intensity increase from baseline at different observation times in the slice (marked red in the left panel) used in the subsequent analysis.}
+\end{figure}
+Figure ~\ref{fig1} shows the distribution of tracers during 24 hours, see also~\cite{ringstad2017glymphatic} for further information on the imaging procedure.   
+Our data (not all shown) consist of a total of 10 MRI observations, including a baseline MRI taken before tracer was injected.
 The observation points are distributed with 5 observations within 1-2 hours after injection, 1 observation in the timeframes 2-4 hours, 6-9 hours, 24 hours and 48 hours.
-Figure ~\ref{fig1} shows the distribution of tracers during 24 hours, see also~\cite{ringstad2017glymphatic}.
+Figure ~\ref{fig2} shows the slice selected for our computations. 
+The software Freesurfer was used to segment and align each of the observations, which made it possible to estimate voxelwise intensity increase.
 
@@
 and $u_{obs}$ are observations at certain time-points.
-\subsection*{Manufactured Solution}
-In order to verify our strategy and test the dependency of the
-regularization paramters, we perform a test case with a
-known solution.  
-The manufactured observations was obtained by forward computation of Eq.\ref{Eq::PDE} with the Dirichlet boundary condition defined as
-\begin{equation}
-g(t)_{\partial \Omega_1} = 0.3 +0.167t - 0.007t\sp{2} \qquad  0 \leq t \leq 24.
-\label{EQ::DIRI}
-\end{equation}
-The timestep was $dt = 0.02$, and the diffusion coefficients were selected to be 
-\begin{equation}
-D_{\Omega_1} = 1000 \quad , \quad D_{\Omega_2} = 4.0 \quad , \quad D_{\Omega_3} = 8.0 
-\end{equation}  
-The magnitude order of the diffusion coefficient are chosen so that they resemble diffusion coefficient in csf, grey and white matter.
-The forward simulation gave a total of 120 possible observation time points.
-These points
-will be denoted as $\tau$.
-
-The mesh is patient-specific and was constructed by using the MRI of a patient diagnosed with iNPH.
-The software Freesurfer was used in segmentation and creating the polyhedral surfaces of the white and grey matter.
-Then the use of T2 weighted MRI was used to segment the csf compartment surrounding the cerebral.
-(BrainMesh code accessibility ?
-) CGAL[?] was used to combine the polyhedral surfaces and to construed the mesh.
-The computational requirement for the resulting mesh was significant, therefore a submesh was also constructed, see Fig.
-??.
 
@@
 The code used the FEniCS project to solve the PDE, using backwards Euler time discretization and first order continuous Galerkin finite elements.
-The module dolfin adjoint [?] was used to compute the reduced functional, and the optimization used the scipy optimize library to minimize the functional using L-BFGS-B algorithm.
+The module dolfin adjoint ~\cite{farrell2013automated} \kam{correct ref?} was used to solve the PDE constrained optimization problem via  using L-BFGS-B algorithm via scipy.
 
@@
 Here $dt$ is forward timestep and $\Delta t$ is the difference between observation time and forward time.
+\kam{This has to be made clearer.
+Earlier we used $u_{obs}$ for observation.
+Also this also only applies if $t_i$ is close to the observations, right?}
 The initial values of the optimization algorithm was chosen to be $1,1,1$.
@@
 
-\section*{Non-linear relation}
-The MR images are provided by Oslo University Hospital Rikshospitalet and can be seen in Fig.??.
-The software Freesurfer was used to segment and align each of the observations, which made it possible to estimate voxelwise intensity increase.
+\subsection*{Contrast concentration - Image Intensity Relation}
+Below, we briefly describe the relationship between the imaging intensity 
+seen in Figures \ref{fig1} and \ref{fig2} and the underlying contrast 
+concentration. 
 The tracer causes the longitudinal(spin-lattice) relaxation time $T_{1}$ to shorten with the following relation
@@
 
-The convergence of L-BFGS-B algorithm can be seen in Fig.??. 
-\begin{itemize}
-\item describe the imaging, shortly with ref to JCI  
-\item describe the abstract mathematical problem to be solved, ie. PDE constrained opt problem where we 
-address coefficients and bc  
-\item the details: finite element, reduced problem, BFGS,  
-\end{itemize}
+\subsection{PDE constrained optimization algorithm}
 
-\begin{figure}
-\includegraphics[width=0.95\textwidth]{PatID-68-new-100.png} 
-\label{fig1} 
-\caption{Shows the percentage intensity increase from baseline at different observation times. }
-\end{figure}
+Noen detaljer her om element methode, optimerings algoritme, prekondisjonering
+grid, osv.
 
-\begin{figure}
-\includegraphics[width=0.95\textwidth]{Zoom-PatID-68.png} 
-\label{fig1} 
-\caption{Shows the percentage intensity increase from baseline at different observation times in the area corresponding to the generated mesh that is marked red in the left panel.}
-\end{figure}
+\subsection*{Manufactured Solution}
+In order to verify our strategy and test the dependency of the
+regularization paramters, we perform a test case with a
+known solution.  
+The manufactured observations was obtained by forward computation of Eq.\ref{Eq::PDE} with the Dirichlet boundary condition defined as
+\begin{equation}
+g(t)_{\partial \Omega_1} = 0.3 +0.167t - 0.007t\sp{2} \qquad  0 \leq t \leq 24.
+\label{EQ::DIRI}
+\end{equation}
+The timestep was $dt = 0.02$, and the diffusion coefficients were selected to be 
+\begin{equation}
+D_{\Omega_1} = 1000 \quad , \quad D_{\Omega_2} = 4.0 \quad , \quad D_{\Omega_3} = 8.0 
+\end{equation}  
+The magnitude order of the diffusion coefficient are chosen so that they resemble diffusion coefficient in csf, grey and white matter.
+The forward simulation gave a total of 120 possible observation time points.
+These points
+will be denoted as $\tau$.
 
+The mesh is patient-specific and was constructed by using the MRI of a patient diagnosed with iNPH.
+The software Freesurfer was used in segmentation and creating the polyhedral surfaces of the white and grey matter.
+Then the use of T2 weighted MRI was used to segment the csf compartment surrounding the cerebral.
+(BrainMesh code accessibility ?
+) CGAL[?] was used to combine the polyhedral surfaces and to construed the mesh.
+The computational requirement for the resulting mesh was significant, therefore a submesh was also constructed, see Fig.
+??.
 \begin{figure}
 \includegraphics[width=0.3\textwidth]{mesh-eps-converted-to.pdf} 
-\label{fig1} 
+\label{figmesh} 
 \caption{Shows the mesh created from the baseline MR image with 3 domains. ( wrap ?? ) }

### 2018-10-03 forward_problem.py
stores obs and finalstate

@@ -136,7 +136,7 @@ def functional(mesh_config, V, D, g_list, tau, obs_file, alpha=0.0, beta=0.0, gr
             self.obs_file.read(self.ic, "%0.2f"%(self.t) )
 
             self.gradient = gradient 
-     
+            self.save = File( "Results-{}-{}-{}/observation.pvd".format( self.alpha, self.beta, self.noise) )
 
   
         def initial_conditions(self):
@@ -168,6 +168,10 @@ def functional(mesh_config, V, D, g_list, tau, obs_file, alpha=0.0, beta=0.0, gr
                 if self.noise:
                    self.d.vector()[:]+=self.noise[self.next_tau].vector()[:]
                 
+
+                self.save << ( self.d , self.t)
+
+
                 Ulin = Dt/self.dt*U_prev +  (self.dt - Dt)/self.dt*U       
                 self.J += assemble((Ulin - self.d) ** 2 * self.dx) 
                 # Move on to next observation

### 2018-10-03 inverse3D-abel.sh

@@ -34,6 +34,7 @@ source ~larsmva/pyadjoint-brain-inversion-mod-fenics-2017.2.abel.intel.conf
 # Define what to do when job is finished (or crashes)
 cleanup "mkdir -p $HOME/Results"
 cleanup "cp -r $SCRATCH/slurm* $HOME" 
+cleanup "cp -r $SCRATCH/Res* $HOME/Results" 
 echo $PWD
 echo "SCRATCH is $SCRATCH"
 

### 2018-10-03 main.py

@@ -145,4 +145,12 @@ if __name__ == "__main__":
     if Z.save_control_values_file is not None:
         save_control_values(opt_ctrls, Z.save_control_values_file)
 
+    tape = get_working_tape()
+
+    from fenics_adjoint.solving import SolveBlock
+    s_blocks = [block for block in tape._blocks if isinstance(block, SolveBlock)]
+    states = [block.get_outputs()[0].saved_output for block in s_blocks]
+    out =        File("Results-{}-{}-{}/finalstate.pvd".format(Z.alpha,Z.beta, noise) )
+    for i in states : 
+        out << i
 

### 2018-10-03 forward_problem.py
Fixed bug

@@ -114,9 +114,9 @@ class Context(object):
     def return_value(self):
         return None
 
-def functional(mesh_config, V, D, g_list, tau, obs_file, alpha=0.0, beta=0.0, gradient=None, noise=None):
+def functional(mesh_config, V, D, g_list, tau, obs_file, alpha=0.0, beta=0.0, gradient=None, noise=None,save=None):
     class FunctionalContext(Context):
-        def __init__(self, mesh_config, V, D, g_list, tau, obs_file, alpha=0.0, beta=0.0, gradient=None):
+        def __init__(self, mesh_config, V, D, g_list, tau, obs_file, alpha=0.0, beta=0.0, gradient=None ):
             super(FunctionalContext, self).__init__(mesh_config, V, D, g_list)
             self.tau = tau
             self.next_tau = 1 
@@ -136,7 +136,7 @@ def functional(mesh_config, V, D, g_list, tau, obs_file, alpha=0.0, beta=0.0, gr
             self.obs_file.read(self.ic, "%0.2f"%(self.t) )
 
             self.gradient = gradient 
-            self.save = File( "Results-{}-{}-{}/observation.pvd".format( self.alpha, self.beta, self.noise) )
+            self.save = save
 
   
         def initial_conditions(self):
@@ -168,8 +168,8 @@ def functional(mesh_config, V, D, g_list, tau, obs_file, alpha=0.0, beta=0.0, gr
                 if self.noise:
                    self.d.vector()[:]+=self.noise[self.next_tau].vector()[:]
                 
-
-                self.save << ( self.d , self.t)
+                if self.save:
+                   self.save << ( self.d , self.t)
 
 
                 Ulin = Dt/self.dt*U_prev +  (self.dt - Dt)/self.dt*U       

### 2018-10-03 main.py

@@ -119,6 +119,8 @@ if __name__ == "__main__":
        noise = None
 
 
+    save = File( "Results-{}-{}-{}/observation.pvd".format( Z.alpha, Z.beta,Z.noise ) )
+
     if Z.generate_observations:
         ic = initial_condition(V, mesh_config)
         g = bc(g, V,tau,k, mesh_config)
@@ -126,7 +128,7 @@ if __name__ == "__main__":
         exit()
     else:
         g = bc_guess(g, Z.obs_file, tau, k, noise)
-        J = functional(mesh_config, V, D, g, tau, Z.obs_file, Z.alpha, Z.beta, noise=noise, gradient=Z.scale)
+        J = functional(mesh_config, V, D, g, tau, Z.obs_file, Z.alpha, Z.beta, noise=noise, gradient=Z.scale, save=save)
 
     ctrls = ([Control(D[i]) for i in range(1, 4)]
              + [Control(g_i) for g_i in g])
@@ -150,7 +152,7 @@ if __name__ == "__main__":
     from fenics_adjoint.solving import SolveBlock
     s_blocks = [block for block in tape._blocks if isinstance(block, SolveBlock)]
     states = [block.get_outputs()[0].saved_output for block in s_blocks]
-    out =        File("Results-{}-{}-{}/finalstate.pvd".format(Z.alpha,Z.beta, noise) )
+    out =        File("Results-{}-{}-{}/finalstate.pvd".format(Z.alpha,Z.beta, Z.noise) )
     for i in states : 
         out << i
 

### 2018-10-03 forward_problem.py
Fix

@@ -162,7 +162,7 @@ def functional(mesh_config, V, D, g_list, tau, obs_file, alpha=0.0, beta=0.0, gr
         def handle_observations(self,U, U_prev):
             Dt = ( self.t - self.tau[self.next_tau])  
            
-            if  round(self.t-self.dt,2) <= self.tau[self.next_tau] and self.tau[self.next_tau] < round(self.t,2)  : 
+            if  round(self.t-self.dt,2) < self.tau[self.next_tau] and self.tau[self.next_tau] <= round(self.t,2)  : 
             
                 self.obs_file.read(self.d, "%0.2f"%(self.tau[self.next_tau]))  
                 if self.noise:

### 2018-10-03 main.py
added save to praser

@@ -89,7 +89,8 @@ if __name__ == "__main__":
     parser.add_argument("--save-control-values-file", default=None, type=str)
     parser.add_argument("--generate-observations", default=False, type=bool)
     parser.add_argument("--maxiter", default=1000, type=int)
-    parser.add_argument("--dx", default=0.0, type=float)
+    parser.add_argument("--dx", default=0.0, type=float) 
+    parser.add_argument("--save",default=False, type=bool)
     Z = parser.parse_args()
     print(Z)
     mesh_config = initialize_mesh(Z.mesh)
@@ -117,9 +118,11 @@ if __name__ == "__main__":
        add_noise(noise,Z.noise)
     else : 
        noise = None
-
-
-    save = File( "Results-{}-{}-{}/observation.pvd".format( Z.alpha, Z.beta,Z.noise ) )
+  
+    if Z.save:
+       save = File( "Results-{}-{}-{}-{}/observation.pvd".format( Z.alpha, Z.beta,Z.noise,k ) )
+    else:
+       save = None
 
     if Z.generate_observations:
         ic = initial_condition(V, mesh_config)
@@ -147,12 +150,14 @@ if __name__ == "__main__":
     if Z.save_control_values_file is not None:
         save_control_values(opt_ctrls, Z.save_control_values_file)
 
-    tape = get_working_tape()
 
-    from fenics_adjoint.solving import SolveBlock
-    s_blocks = [block for block in tape._blocks if isinstance(block, SolveBlock)]
-    states = [block.get_outputs()[0].saved_output for block in s_blocks]
-    out =        File("Results-{}-{}-{}/finalstate.pvd".format(Z.alpha,Z.beta, Z.noise) )
-    for i in states : 
-        out << i
+    if Z.save:
+       tape = get_working_tape()
+
+       from fenics_adjoint.solving import SolveBlock
+       s_blocks = [block for block in tape._blocks if isinstance(block, SolveBlock)]
+       states = [block.get_outputs()[0].saved_output for block in s_blocks]
+       out =        File("Results-{}-{}-{}-{}/finalstate.pvd".format(Z.alpha,Z.beta, Z.noise,k) )
+       for i in states : 
+           out << i
 

### 2018-10-03 inverse_contrast-save.sh
new abel script

@@ -1,0 +1,50 @@
+#!/bin/bash
+# Job name:
+#SBATCH --job-name=kent
+#
+# Project:
+#SBATCH --account=nn9279k
+# Wall clock limit:
+#SBATCH --time='24:00:00'
+#
+# Max memory usage per task:
+#SBATCH --mem-per-cpu=16000M
+#
+# Number of tasks (cores):
+##SBATCH --nodes=1 --ntasks=4
+#SBATCH --ntasks=1
+##SBATCH --hint=compute_bound
+#SBATCH --cpus-per-task=1
+#SBTACH --outfile=ValuesA$1B$2N$3.out
+#SBATCH --partition=long
+##SBATCH --output=output.$SCRATCH 
+
+## Set up job environment
+source /cluster/bin/jobsetup
+
+#source ~johannr/pyadjoint-brain-inversion-mod-fenics-2017.1.0.abel.gnu.conf
+#source ~johannr/pyadjoint-brain-inversion-mod-fenics-2017.1.0.abel.gnu.conf
+#source ~larsmva/pyadjoint-brain-inversion-mod-fenics-2017.2.abel.intel.conf
+
+source ~larsmva/pyadjoint-brain-inversion-mod-fenics-2017.2.abel.intel.conf
+
+
+#source  ~johannr/pyadjoint-2018.03.19-fenics-2017.1.0.abel.gnu.conf
+
+# Define what to do when job is finished (or crashes)
+cleanup "mkdir -p $HOME/Results"
+cleanup "cp -r $SCRATCH/slurm* $HOME" 
+cleanup "cp -r $SCRATCH/Res* $HOME/Results" 
+echo $PWD
+echo "SCRATCH is $SCRATCH"
+
+# Copy necessary files to $SCRATCH
+cp mesh_invers_contrast.h5 forward_problem.py main.py U.xdmf $SCRATCH
+
+echo "${@:4}"
+cd $SCRATCH
+ls
+echo $SCRATCH
+python3 main.py --save True --alpha $1 --beta $2 --noise $3 --K $4 --tau "${@:5}"
+
+

### 2018-10-03 forward_problem.py
Fix

@@ -169,7 +169,7 @@ def functional(mesh_config, V, D, g_list, tau, obs_file, alpha=0.0, beta=0.0, gr
                    self.d.vector()[:]+=self.noise[self.next_tau].vector()[:]
                 
                 if self.save:
-                   self.save << ( self.d , self.t)
+                   self.save << ( self.d ,self.tau[self.next_tau])
 
 
                 Ulin = Dt/self.dt*U_prev +  (self.dt - Dt)/self.dt*U       

### 2018-10-03 inverse_contrast-save.sh

@@ -45,6 +45,6 @@ echo "${@:4}"
 cd $SCRATCH
 ls
 echo $SCRATCH
-python3 main.py --save True --alpha $1 --beta $2 --noise $3 --K $4 --tau "${@:5}"
+python3 main.py --save True --alpha $1 --beta $2 --noise $3 --k $4 --tau "${@:5}"
 
 

### 2018-10-07 forward_problem.py
updates

@@ -12,7 +12,7 @@ def initialize_mesh(mesh_file): # Lars : Endret
     # Import mesh and subdomains
     mesh = Mesh()
 
-    hdf = HDF5File(mesh.mpi_comm(), "mesh_invers_contrast.h5", "r")
+    hdf = HDF5File(mesh.mpi_comm(), mesh_file, "r")
     hdf.read(mesh, "/mesh", False, annotate=False)
     subdomains = MeshFunction("size_t", mesh, mesh.topology().dim())
     hdf.read(subdomains, "/subdomains", annotate=False)
@@ -172,8 +172,11 @@ def functional(mesh_config, V, D, g_list, tau, obs_file, alpha=0.0, beta=0.0, gr
                    self.save << ( self.d ,self.tau[self.next_tau])
 
 
-                Ulin = Dt/self.dt*U_prev +  (self.dt - Dt)/self.dt*U       
-                self.J += assemble((Ulin - self.d) ** 2 * self.dx) 
+                Ulin = Dt/self.dt*U_prev +  (self.dt - Dt)/self.dt*U   
+
+    
+                self.J += assemble((Ulin - self.d) ** 2 * self.dx(2)) 
+                self.J += assemble((Ulin - self.d) ** 2 * self.dx(3)) 
                 # Move on to next observation
                 self.next_tau += 1
                 # Check if there is another observations in time step

### 2018-10-07 main.py

@@ -37,15 +37,17 @@ def bc(g, V,tau,k, mesh_config):
 
 
 def bc_guess(g, obs_file, tau, k,noise):
-    d = Function(g[0].function_space())
+    #d = Function(g[0].function_space())
+    
     dt = (tau[-1] -tau[0])/k
     obs_file = HDF5File(mpi_comm_world(), obs_file, 'r')
     next_tau = 1
     t = tau[0]
     for i in range(k):
         t += dt
-        obs_file.read(d,"%0.2f"%(tau[next_tau]))
-        g[i].vector()[:] = d.vector()[:]
+        obs_file.read(g[i],"%0.2f"%(tau[next_tau]))
+        #g[i].vector()[:] = d.vector()[:]
+
         if noise:
            g[i].vector()[:]+= noise[next_tau].vector()[:]
 
@@ -64,7 +66,6 @@ def iter_cb(m):
     ds = mesh_config["ds"]
     fenics_m = NumRF.set_local([control.copy_data() for control in Jhat.controls], m)
     print("Functional-value: {} | {} ".format(iter_cnt, NumRF(m)) )
-    print("DirichletBC-Iter: {} | {}".format(iter_cnt, sum([assemble((fenics_m[i] - correct_g[i-3])**2*ds(1)) for i in range(3, len(fenics_m))])/sum([assemble(correct_g[i-3]**2*ds(1)) for i in range(3, len(fenics_m)) ]) ))
 
 
 if __name__ == "__main__":
@@ -78,9 +79,9 @@ if __name__ == "__main__":
     parser.add_argument('--beta', default=0.001, type=float)
     parser.add_argument('--noise', default=0.0, type=float)
     parser.add_argument('--tol', default=0.001, type=float)
-    parser.add_argument('--D', default=[1, 1, 1], type=float, nargs=3)
-    parser.add_argument('--scale', default=[100, 1, 1], type=float, nargs=3)
-    parser.add_argument('--mesh', default="mesh_invers_contrast.h5", type=str)
+    parser.add_argument('--D', default=[1,1, 1], type=float, nargs=2)
+    parser.add_argument('--scale', default=[100,1, 1], type=float, nargs=2)
+    parser.add_argument('--mesh', default="mesh2domain.h5", type=str)
     parser.add_argument("--tau", nargs="+", type=float)
     parser.add_argument("--k",default=1, type=int)
[…]

### 2018-10-07 tex/paper.tex
update
Lagt til bilder

@@
 \section*{Implementation}
+
 The code used the FEniCS project to solve the PDE, using backwards Euler time discretization and first order continuous Galerkin finite elements.
-The module dolfin adjoint ~\cite{farrell2013automated} \kam{correct ref?} was used to solve the PDE constrained optimization problem via  using L-BFGS-B algorithm via scipy.
+The module dolfin adjoint ~\cite{farrell2013automated} \kam{correct ref?} was used to solve the PDE constrained optimization problem with the L-BFGS-B algorithm via scipy.
 
@@
 
-The times in the forward simulation do not always overlap with observations times. Thus a linear interpolation of the forward problem was used to compute the difference from the observation, i.e 
+The observations $u_{obs}$ have fixed time-points $t_i$, these time-points may not correspond to the time discretization in the forward problem.
+Therefore, after each time step $dt$ in Eq\ref{Eq::PDE}, it was checked if the time step contained the next observation.
+If it did, then a linear interpolation of the current solution $u$ and previous solution $u_prev$ was used approximate the solution corresponding to $t_i$.
+The linear interpolation was given as
 \begin{equation}
-u_{linear} = \frac{\Delta t}{dt} U_prev + \frac{dt - \Delta t }{dt} U.
+u_{linear} = \frac{\Delta t}{dt} U_{prev} + \frac{dt - \Delta t }{dt} U,
 \end{equation}
-Here $dt$ is forward timestep and $\Delta t$ is the difference between observation time and forward time.
-\kam{This has to be made clearer.
-Earlier we used $u_{obs}$ for observation.
-Also this also only applies if $t_i$ is close to the observations, right?}
+with $\Delta t$ is the difference between observation time and the time in the forward problem.
+
+ \kam{This has to be made clearer. Earlier we used $u_{obs}$ for observation. Also this also only applies if $t_i$ is close to the observations, right?}
+
 The initial values of the optimization algorithm was chosen to be $1,1,1$.
@@
 The real data observations had observation times that had an unevenly distribution over 24 hours.
-Thus having  constant time between observations is not realsitic.
+Thus having  constant time between observations is not realistic.
 Therefore the number of observation and the unevenly distribution of them will be tested.
@@
 
+\kam{check that all symbols are explained here}
+
 \subsection{PDE constrained optimization algorithm}
 
+\kam{
 Noen detaljer her om element methode, optimerings algoritme, prekondisjonering
 grid, osv. 
+}
+
+The gird
 
@@
 This method can be adapted to
+
+\begin{figure}
+\centering
+\includegraphics[scale=0.2]{27-12-hours-scale-0-1-3.png}  
+\caption{The upper row shows the manufactured observation, A ) Shows the manufactured observation at time-point 24 with no noise added.
+B) Shows the manufactured observation at time-point 24 with an noise amplitude of 0.15 {\color{red} explain noise amplitude}.
+C)Shows the manufactures observation at time-point 24 with noise amplitude of 0.3.
+The lower row shows the results with optimized parameter obtained with $alpha=0.0001$, $\beta=1.0$ and $k=27$.
+D) Shows the  .
+E)  Shows the  F)  Shows the  }
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[scale=0.2]{27-24-hours-scale-0-1.png}
+\caption{The upper row shows the manufactured observation, A ) Shows the manufactured observation at time-point 24 with no noise added.
+B) Shows the manufactured observation at time-point 24 with a noise amplitude of 0.15 {\color{red} explain noise ampliutde}.
+C)Shows the manufactures observation at time-point 24 with noise amplitude of 0.3.
+The lower row shows the results with optimized parameter obtained with $alpha=0.0001$, $\beta=1.0$ and $k=27$.
+D) Shows the  .
+E)  Shows the  F)  Shows the  }
+\end{figure}
 

### 2018-10-08 main.py
3domain, no csf weight

@@ -37,7 +37,7 @@ def bc(g, V,tau,k, mesh_config):
 
 
 def bc_guess(g, obs_file, tau, k,noise):
-    #d = Function(g[0].function_space())
+    d = Function(g[0].function_space())
     
     dt = (tau[-1] -tau[0])/k
     obs_file = HDF5File(mpi_comm_world(), obs_file, 'r')
@@ -45,11 +45,8 @@ def bc_guess(g, obs_file, tau, k,noise):
     t = tau[0]
     for i in range(k):
         t += dt
-        obs_file.read(g[i],"%0.2f"%(tau[next_tau]))
-        #g[i].vector()[:] = d.vector()[:]
-
-        if noise:
-           g[i].vector()[:]+= noise[next_tau].vector()[:]
+        obs_file.read(d,"%0.2f"%(tau[next_tau]))
+        g[i].vector()[:] = d.vector()[:]
 
         if abs(t - tau[next_tau]) < abs(t + dt - tau[next_tau]):
             next_tau += 1

### 2018-10-08 forward_problem.py
2 domain real data

@@ -42,13 +42,14 @@ def forward_problem(context):
     dx = context.dx
 
     # Define bilinear form, handling each subdomain 1, 2, and 3 in separate integrals.
-    a = u * v * dx + sum([dt * context.scale(j-1) * D[j] * inner(grad(v), grad(u)) * dx(j) for j in range(1, 4)])
+    a = u * v * dx + sum([dt * context.scale(j-1) * D[j] * inner(grad(v), grad(u)) * dx(j) for j in range(1, 3)])
     # Define linear form.
     L = U_prev * v * dx
 
     A = assemble(a)
-    bc = DirichletBC(V, 0, context.boundaries, 1)
-    bc.apply(A)
+    bcs = [DirichletBC(V, 0, context.boundaries, 1),DirichletBC(V, 0, context.boundaries, 2)]
+    for bc in bcs: 
+        bc.apply(A)
 
     # Define solver. Use GMRES iterative method with AMG preconditioner.
     solver = LinearSolver(mpi_comm_self(), "gmres")
@@ -175,8 +176,7 @@ def functional(mesh_config, V, D, g_list, tau, obs_file, alpha=0.0, beta=0.0, gr
                 Ulin = Dt/self.dt*U_prev +  (self.dt - Dt)/self.dt*U   
 
     
-                self.J += assemble((Ulin - self.d) ** 2 * self.dx(2)) 
-                self.J += assemble((Ulin - self.d) ** 2 * self.dx(3)) 
+                self.J += assemble((Ulin - self.d) ** 2 * self.dx) 
                 # Move on to next observation
                 self.next_tau += 1
                 # Check if there is another observations in time step
@@ -202,13 +202,13 @@ def functional(mesh_config, V, D, g_list, tau, obs_file, alpha=0.0, beta=0.0, gr
                 weight = 1.0
 
             # Add regularisation
-            self.J += 1 / 2 * weight * self.dt * assemble(self.g ** 2 * self.ds(1) ) * self.alpha
+            self.J += 1 / 2 * weight * self.dt * assemble(self.g ** 2 * self.ds ) * self.alpha
             if self.current_g_index > 1:
                 g_prev = self.g_list[self.current_g_index - 2]
-                self.J += 1 / 2 * weight * self.dt * assemble(((self.g - g_prev) / self.dt) ** 2 * self.ds(1)) * self.beta
[…]

### 2018-10-08 main.py

@@ -79,8 +79,8 @@ if __name__ == "__main__":
     parser.add_argument('--beta', default=0.001, type=float)
     parser.add_argument('--noise', default=0.0, type=float)
     parser.add_argument('--tol', default=0.001, type=float)
-    parser.add_argument('--D', default=[1,1, 1], type=float, nargs=2)
-    parser.add_argument('--scale', default=[100,1, 1], type=float, nargs=2)
+    parser.add_argument('--D', default=[1, 1], type=float, nargs=2)
+    parser.add_argument('--scale', default=[1, 1], type=float, nargs=2)
     parser.add_argument('--mesh', default="mesh2domain.h5", type=str)
     parser.add_argument("--tau", nargs="+", type=float)
     parser.add_argument("--k",default=1, type=int)
@@ -101,7 +101,7 @@ if __name__ == "__main__":
     V = FunctionSpace(mesh_config["mesh"], "CG", 1)
 
     # Diffusion coefficients
-    D = {1: Constant(Z.D[0]), 2: Constant(Z.D[1]), 3 :Constant(Z.D[2]) }
+    D = {1: Constant(Z.D[0]), 2: Constant(Z.D[1])}
 
     tau = Z.tau
     # Number timepoints
@@ -135,7 +135,7 @@ if __name__ == "__main__":
         g = bc_guess(g, Z.obs_file, tau, k, noise)
         J = functional(mesh_config, V, D, g, tau, Z.obs_file, Z.alpha, Z.beta, noise=noise, gradient=Z.scale, save=save)
 
-    ctrls = ([Control(D[i]) for i in range(1, 4)]
+    ctrls = ([Control(D[i]) for i in range(1, 3)]
              + [Control(g_i) for g_i in g])
 
     print("J = ", J)

### 2018-10-08 forward_problem.py
boundary guess mod

@@ -57,8 +57,8 @@ def forward_problem(context):
     #solver.parameters['absolute_tolerance'] = 10**-6  
 
     #solver.parameters['maximum_iterations'] = 100  
-    #solver.parameters['monitor_convergence'] = True  
-    #solver.parameters['nonzero_initial_guess'] = False # this may be used to speed up  
+    solver.parameters['monitor_convergence'] = True  
+    solver.parameters['nonzero_initial_guess'] = False # this may be used to speed up  
 
     #solver.parameters['relative_tolerance'] = 10**-6
     #solver.parameters['report'] = True 

### 2018-10-08 main.py

@@ -36,8 +36,16 @@ def bc(g, V,tau,k, mesh_config):
     return g
 
 
+
+def contains_observation(t,tau,dt,next_tau):
+ 
+    if abs(t - tau[next_tau]) < abs(t + dt - tau[next_tau]):  
+       next_tau = contains_observation(t,tau,dt,next_tau+1)
+
+    return next_tau
+
 def bc_guess(g, obs_file, tau, k,noise):
-    #d = Function(g[0].function_space())
+    #d = Function(g[0].function_space()) # Needs more presentable code
     
     dt = (tau[-1] -tau[0])/k
     obs_file = HDF5File(mpi_comm_world(), obs_file, 'r')
@@ -51,8 +59,9 @@ def bc_guess(g, obs_file, tau, k,noise):
         if noise:
            g[i].vector()[:]+= noise[next_tau].vector()[:]
 
-        if abs(t - tau[next_tau]) < abs(t + dt - tau[next_tau]):
-            next_tau += 1
+        next_tau = contains_observation(t,tau,dt,next_tau)
+
+
     return g
 
 
@@ -60,12 +69,8 @@ iter_cnt = 0
 def iter_cb(m):
     global iter_cnt
     iter_cnt += 1
-    print("Coeffs-Iter: {} | Constant({}) | Constant({}) | Constant({})".format(iter_cnt, float(m[0]), float(m[1]), float(m[2])))
-    from pyadjoint.reduced_functional_numpy import ReducedFunctionalNumPy
-    NumRF = ReducedFunctionalNumPy(Jhat)
-    ds = mesh_config["ds"]
-    fenics_m = NumRF.set_local([control.copy_data() for control in Jhat.controls], m)
-    print("Functional-value: {} | {} ".format(iter_cnt, NumRF(m)) )
+    print("Coeffs-Iter: {} | Constant({}) | Constant({}) ".format(iter_cnt, float(m[0]), float(m[1])))
+
 
 
 if __name__ == "__main__":
@@ -144,7 +149,7 @@ if __name__ == "__main__":
     Jhat.optimize()
 
     
-    opt_ctrls = minimize(Jhat, method="L-BFGS-B", callback = iter_cb, options={"disp": True, "maxiter": Z.maxiter, "gtol": 1.0e-2})
[…]

### 2018-10-08 forward_problem.py
Abel run reelle data

@@ -54,13 +54,13 @@ def forward_problem(context):
     # Define solver. Use GMRES iterative method with AMG preconditioner.
     solver = LinearSolver(mpi_comm_self(), "gmres")
     solver.set_operator(A)
-    #solver.parameters['absolute_tolerance'] = 10**-6  
+    solver.parameters['absolute_tolerance'] = 10**-6  
 
     #solver.parameters['maximum_iterations'] = 100  
     solver.parameters['monitor_convergence'] = True  
     solver.parameters['nonzero_initial_guess'] = False # this may be used to speed up  
 
-    #solver.parameters['relative_tolerance'] = 10**-6
+    solver.parameters['relative_tolerance'] = 10**-6
     #solver.parameters['report'] = True 
     while not context.should_stop():
         U_prev.assign(U,annotate =True)
@@ -164,7 +164,7 @@ def functional(mesh_config, V, D, g_list, tau, obs_file, alpha=0.0, beta=0.0, gr
             Dt = ( self.t - self.tau[self.next_tau])  
            
             if  round(self.t-self.dt,2) < self.tau[self.next_tau] and self.tau[self.next_tau] <= round(self.t,2)  : 
-            
+                print("Observation :", self.tau[self.next_tau] , self.t)
                 self.obs_file.read(self.d, "%0.2f"%(self.tau[self.next_tau]))  
                 if self.noise:
                    self.d.vector()[:]+=self.noise[self.next_tau].vector()[:]

### 2018-10-08 main.py

@@ -39,6 +39,10 @@ def bc(g, V,tau,k, mesh_config):
 
 def contains_observation(t,tau,dt,next_tau):
  
+    if  len(tau) <= next_tau:
+        return next_tau
+
+
     if abs(t - tau[next_tau]) < abs(t + dt - tau[next_tau]):  
        next_tau = contains_observation(t,tau,dt,next_tau+1)
 
@@ -61,7 +65,6 @@ def bc_guess(g, obs_file, tau, k,noise):
 
         next_tau = contains_observation(t,tau,dt,next_tau)
 
-
     return g
 
 
@@ -70,7 +73,11 @@ def iter_cb(m):
     global iter_cnt
     iter_cnt += 1
     print("Coeffs-Iter: {} | Constant({}) | Constant({}) ".format(iter_cnt, float(m[0]), float(m[1])))
-
+    from pyadjoint.reduced_functional_numpy import ReducedFunctionalNumPy
+    NumRF = ReducedFunctionalNumPy(Jhat)
+    #ds = mesh_config["ds"]
+    #fenics_m = NumRF.set_local([control.copy_data() for control in Jhat.controls], m)
+    print("Functional-value: {} | {} ".format(iter_cnt, NumRF(m)) )
 
 
 if __name__ == "__main__":
@@ -90,7 +97,7 @@ if __name__ == "__main__":
     parser.add_argument("--tau", nargs="+", type=float)
     parser.add_argument("--k",default=1, type=int)
     parser.add_argument("--K",default=0, type=int)
-    parser.add_argument("--obs-file", default="U.xdmf", type=str)
+    parser.add_argument("--obs-file", default="Cestimated.xdmf", type=str)
     parser.add_argument("--load-control-values-file", default=None, type=str)
     parser.add_argument("--save-control-values-file", default=None, type=str)
     parser.add_argument("--generate-observations", default=False, type=bool)

### 2018-10-08 reelle_data-save.sh

@@ -1,0 +1,50 @@
+#!/bin/bash
+# Job name:
+#SBATCH --job-name=kent
+#
+# Project:
+#SBATCH --account=nn9279k
+# Wall clock limit:
+#SBATCH --time='24:00:00'
+#
+# Max memory usage per task:
+#SBATCH --mem-per-cpu=16000M
+#
+# Number of tasks (cores):
+##SBATCH --nodes=1 --ntasks=4
+#SBATCH --ntasks=1
+##SBATCH --hint=compute_bound
+#SBATCH --cpus-per-task=1
+#SBTACH --outfile=ValuesA$1B$2N$3.out
+#SBATCH --partition=long
+##SBATCH --output=output.$SCRATCH 
+
+## Set up job environment
+source /cluster/bin/jobsetup
+
+#source ~johannr/pyadjoint-brain-inversion-mod-fenics-2017.1.0.abel.gnu.conf
+#source ~johannr/pyadjoint-brain-inversion-mod-fenics-2017.1.0.abel.gnu.conf
+#source ~larsmva/pyadjoint-brain-inversion-mod-fenics-2017.2.abel.intel.conf
+
+source ~larsmva/pyadjoint-brain-inversion-mod-fenics-2017.2.abel.intel.conf
+
+
+#source  ~johannr/pyadjoint-2018.03.19-fenics-2017.1.0.abel.gnu.conf
+
+# Define what to do when job is finished (or crashes)
+cleanup "mkdir -p $HOME/Results"
+cleanup "cp -r $SCRATCH/slurm* $HOME" 
+cleanup "cp -r $SCRATCH/Res* $HOME/Results" 
+echo $PWD
+echo "SCRATCH is $SCRATCH"
+
+# Copy necessary files to $SCRATCH
+cp mesh2domain.h5 forward_problem.py main.py Cestimated.xdmf $SCRATCH
+
+echo "${@:4}"
+cd $SCRATCH
+ls
+echo $SCRATCH
+python3 main.py --save True --alpha $1 --beta $2 --noise $3 --k $4 --tau "${@:5}" 
+
+

### 2018-10-08 tex/paper.tex
T1mapping, DTI and references

@@
 \section*{Implementation}
-
 The code used the FEniCS project to solve the PDE, using backwards Euler time discretization and first order continuous Galerkin finite elements.
-The module dolfin adjoint ~\cite{farrell2013automated} \kam{correct ref?} was used to solve the PDE constrained optimization problem with the L-BFGS-B algorithm via scipy.
+The module dolfin adjoint ~\cite{farrell2013automated} \kam{correct ref?} was used to solve the PDE constrained optimization problem with the L-BFGS-B algorithm in the python module scipy.
 
@@
 \end{equation}
-In article [?], the term $M_n$ is defined as the magnetization for the n-echo 
+In article  \cite{MPRAGE}, the term $M_n$ is defined as the magnetization for the n-echo 
 \begin{equation}
@@
 f(T_1) = M_{n}/M_{0} ,
-\label{FIG::F}
+\label{Eq::F}
 \end{equation}
@@
 \end{equation}
+The difference in $S_0$ between observation times were adjusted for in \citep{eidevalnes}.  
 Thus we can express the $T_1$ change due to contrast as 
@@
 \end{equation}
-and we can then estimate concentration using Eq.\ref{EQ::contrast} if we know $T_{1}\sp{0}$. The $T_{1}\sp{0}$ was obtained using MRI.
+and we can then estimate concentration using Eq.\ref{EQ::contrast} if we know $T_{1}\sp{0}$.
+The $T_{1}\sp{0}$ values were obtained by T1 mapping the brain using a MRI sequence known as MOLLI5(3)3 \cite{TAYLOR201667}.
+This makes it possible to also take into account patients specific characteristic, such as tissue damage.
+Tissue damage, such as edema, will cause the intensity in the MRI to differ from healthy white matter tissue.
+Indicating that the tissue composition in the edema is different, and subsequently have different T1 relaxation times, which will give a wrong estimation of the MRI contrast.
+
+In \cite{XU2011827} the concentration was computed {\color{red} not used, due to calibration requirements. But could be used.}.
+
+In [nicholsen ], it is shown that the macroscopic diffusion in the brain can be considered a hindered diffusion with an apparent diffusion coefficient.
+This means that the diffusion parameters in Eq\ref{Eq::PDE}....
+.
+The apparent diffusion coefficient  $D_{adc}$ is defined as
+\begin{equation}
+D = D \lambda\sp{2} fill in subscript,
+\end{equation} 
+with $\lambda$ defined as tourtosity of the brain and $D_{free}$ the free diffusion coefficients.  The tourtosity is a structural parameter, ...
+
+In the acquired data, the MPRAGE had a high signal to noise ratio and the T1 mapping had low signal in the CSF.
+This made it difficult to estimate the concentration in the CSF compartment.
+Thus an additional mesh without the CSF compartment was constructed, see Fig.
+??.
+
+Thus the optimized parameters will be compared with the apparent diffusion coefficient obtained form DTI cite DTI. The DTI measure the apparent diffusion coefficient 
+Therefore the Stokes-Einstein relation [cite] can be used to estimate the apparent diffusion coefficient for whit and grey matter.
 

### 2018-10-09 tex/paper.tex
revised intro

--- 2018-10-03 tex/paper.tex
@@
 
-\author{Lars Magnus Valnes, Sebastian K. Mitusch, Geir A. Ringstad, Per Kristian Eide, Simon W. Funke, Kent-Andre Mardal }
+\author{Lars Magnus Valnes, Sebastian K. Mitusch, Geir A. Ringstad, \\ 
+Per Kristian Eide, Simon W. Funke, Kent-Andre Mardal }
 
@@
 The glymphatic system remains controversial and modeling attempts
-has so far mostly failed to explain the biomechanics of the system~\cite{holter2017interstitial, smith2017glymphatic}. A proper biomechanical 
+has so far mostly failed to explain the biomechanics of the system~\cite{asgari2016glymphatic, holter2017interstitial, smith2017glymphatic}\kam{Lars: vi trenger flere her}. A proper biomechanical 
 understanding of the pathway has significant potential because
@@
 amyloid-beta and CSF-tau.
+
 In \cite{ringstad2018brain} brainwide distribution of MRI-contrast was demonstrated during 24 hours after lumbar contrast injection.
@@
 Furthermore, images were obtained only at a few time-points during the investigations in \cite{ringstad2018brain}.
+
+The pioneering works of Sykov{\'a} and Nicholson~\cite{sykova2008diffusion} demonstrated
+that diffusion was a governing transport mechanism in the brain and estimated to be on the order
+of XXX. This is confirmed with DTI where values of young and healthy are typically around XXX
+while values in dementia typically are XXX \kam{Geir vet du dette?}. Of course diffusion coefficient 
+measured by DTI at a time-scale of XXX \kam{tall her} may not be representative for the process on a
+longer time-scale, at least if the paravascular pathway plays an important role. The fact that the vasculature (mostly 
+the capillary network) occupy around 3\% of the brain volume and the paravascular network is bound to be substatantially
+smaller potentially render it invisible for the DTI investigation while still effective on longer time scales.
+
 Our purpose in this paper is to attempt a more rigorous methodology 
@@
 \subsection*{Mathematical Model}
-In order to assess whether the contrast distribution shown 
-in Figure \ref{fig1} is governed by a diffusion process we
-aim to solve a PDE constrained optimization problem where
+In order to estimate the apparent diffusion coefficient involved in the contrast transportation shown 
+in Figure \ref{fig1} we assume that the process is governed by a diffusion equation and  
+solve a PDE constrained optimization problem where
 the contrast distribution, boundary conditions, and apparent
@@
 
+\kam{check that all symbols are explained here}
+
 \subsection{PDE constrained optimization algorithm}
 
+\kam{
 Noen detaljer her om element methode, optimerings algoritme, prekondisjonering
 grid, osv. 
+}
 

### 2018-10-09 tex/paper.tex
update update

@@
 \end{figure}
-Figure ~\ref{fig1} shows the distribution of tracers during 24 hours, see also~\cite{ringstad2017glymphatic} for further information on the imaging procedure.   
+Figure ~\ref{fig1} shows the distribution of tracers during 24 hours, see also~\cite{ringstad2018brain} for further information on the imaging procedure.   
 Our data (not all shown) consist of a total of 10 MRI observations, including a baseline MRI taken before tracer was injected.
@@
 \end{equation}
-The difference in $S_0$ between observation times were adjusted for in \citep{eidevalnes}.  
+The difference in $S_0$ between observation times were adjusted for in \citep{ringstad2018brain}.  
 Thus we can express the $T_1$ change due to contrast as 
@@
 \centering
-\includegraphics[scale=0.2]{27-12-hours-scale-0-1-3.png}  
+\includegraphics[scale=0.4]{27-12-hours-scale-0-1-3.png}  
 \caption{The upper row shows the manufactured observation, A ) Shows the manufactured observation at time-point 24 with no noise added.
@@
 \centering
-\includegraphics[scale=0.2]{27-24-hours-scale-0-1.png}
+\includegraphics[scale=0.4]{27-24-hours-scale-0-1.png}
 \caption{The upper row shows the manufactured observation, A ) Shows the manufactured observation at time-point 24 with no noise added.

### 2018-10-09 tex/paper.tex
text added

@@
 
-The observations $u_{obs}$ have fixed time-points $t_i$, these time-points may not correspond to the time discretization in the forward problem.
+Each observations $u_{obs}$ have a fixed time-point $t_i$, these time-points may not overlap with the time discretization in the forward problem.
 Therefore, after each time step $dt$ in Eq\ref{Eq::PDE}, it was checked if the time step contained the next observation.
-If it did, then a linear interpolation of the current solution $u$ and previous solution $u_prev$ was used approximate the solution corresponding to $t_i$.
+If it did, then a linear interpolation of the current solution $u$ and previous solution $U_{prev}$ was used approximate the solution corresponding to $t_i$.
 The linear interpolation was given as
 \begin{equation}
-u_{linear} = \frac{\Delta t}{dt} U_{prev} + \frac{dt - \Delta t }{dt} U,
+u_{linear}(t) = \frac{\Delta t}{dt} U_{prev}(t) + \frac{dt - \Delta t }{dt} U(t), t \in \lbrace 
 \end{equation}
@@
 To accurately depict the real data observations.
+
+The
 
@@
 \end{equation}
-The difference in $S_0$ between observation times were adjusted for in \citep{ringstad2018brain}.  
+The difference in $S_0$ between observation times were adjusted for in \cite{ringstad2018brain}.  
 Thus we can express the $T_1$ change due to contrast as 
@@
 The $T_{1}\sp{0}$ values were obtained by T1 mapping the brain using a MRI sequence known as MOLLI5(3)3 \cite{TAYLOR201667}.
-This makes it possible to also take into account patients specific characteristic, such as tissue damage.
-Tissue damage, such as edema, will cause the intensity in the MRI to differ from healthy white matter tissue.
-Indicating that the tissue composition in the edema is different, and subsequently have different T1 relaxation times, which will give a wrong estimation of the MRI contrast.
+This makes it possible to  take into account patients specific characteristic, such as tissue damage.
+There are several forms of tissue damage, one is edema, which can be observed in the MRI due to a lower intensity in the white matter compared to healthy white matter tissue.
+This means that the damaged tissue also have different T1 relaxation times, which will give wrong estimation of tracer concentration.
 
@@
 Thus the optimized parameters will be compared with the apparent diffusion coefficient obtained form DTI cite DTI. The DTI measure the apparent diffusion coefficient
-Therefore the Stokes-Einstein relation [cite] can be used to estimate the apparent diffusion coefficient for whit and grey matter.
+
+The Stokes-Einstein relation combined with correlation between weight and radius of particles can be used to estimate the diffusion coefficient for Gadovist (600 Da) \cite{VALENCIA2011129}.
+This gives a estimated free diffusion coefficient of
+$  25.72 e-5 \mathrm{mm\sp{2}/s}$.
 
@@
 
+The relative error norm for a scalar is defined as 
+\begin{equation}
+|| X ||_{RE} = \frac{X_{found} -X_{true} }{ X_true }
+\end{equation}
+with $X$ as an arbitrary scalar parameter.
+
+The relative error norm for the boundary is defined as 
+\begin{equation}
+|| g ||_{RE(\Omega_1)} = \frac{||g_{found} -g_{true}||_{L(\Omega_1)} }{ ||g_{true}|| }
+\end{equation}
+with $X$ as a vector.
 \subsection{The relaxation parameters}
-The relaxation parameters needs to be calibrated depending on the problem, and thus the diffusion parameters were computed by large range of relaxation parameters values.
-The results are shown in Tab.\ref{Tab::1}, and it is shown in red that $\alpha=1.0$ have large discrepancy in the parameters values of $D_{\Omega_1}$.
+
+The robustness of the objective functional defined in Eq.\ref{Eq::F} is dependent on the regularization parameters $\alpha$ and $\beta$.
+Therefore it is important to select regularization parameter values to ensure effective and accurate convergence.
+The evaluation of different regularization parameters was done by solving the optimization  with  different values of $\alpha$ and $\beta$ and compare the resulting states and the manufactured solution.
+The observation times were selected with $t_i \in  \rbrace 2.4, 4.8, 7.2, 9.6, 12.0, 14.4, 16.8, 19.2, 21.6, 24.0 \lbrace$, and the number of time-steps in the forward problem was set to $k= 10$.
+
+The results are shown in Tab.\ref{Tab::1} together with the number of iteration used to reach the convergence criteria.
+It can be observed for $\alpha= 1.0$ that there is a significant relative error for $D_{\Omega_1}$.
+The other control parameters also showed an increased error compared to other values of $\alpha$.
+The remaining values of the regularization parameters give small relative error.
+
+\subsection{The noise susceptibility}
+
+The MRI data contains noise, hence an investigation to the noise susceptibility is needed.
+This is done by adding uniform noise in the range $\brace -n_{amp} , n_{amp} \rbrace $, with $n_{amp}$ defined as noise amplitude, to the manufactured observations.
+Then the optimization was solved by varying the regularization parameters $\alpha$ and $\beta$.
+
+In Tab.\ref{Tab::Noise0.03}, we can see that a noise amplitude of 0.03, (10$\%$ of maximum initial condition) had negligible effect on the relative error.
+However, in Tab.\ref{Tab::Noise0.3} the noise amplitude was increased to 0.3 (100$\%$ of maximum initial condition) and it is observed that for  $\alpha < 1.0e-3$  $\beta < 1.0e-3$ the optimization failed to converge before reaching maximum iteration of 1000 steps.
+Furthermore, the relative boundary error $||g||_{RE(\Omega)}$ is  larger for lower values of $\beta$.
 
 \subsection{The number of timessteps}
-The first results focus on the accuracy of the minimization based on the number of time steps.
-It can be assumed that the error decreases  while the number of time steps increases since the Dirichlet boundary condition in Eq.\ref{EQ::DIRI} are quadratic, while the forward problem is a linear approximation.
 
-This can be seen in Tab.??, Tab.??
+The PDE uses backward Euler, which is a linear approximation in time.
+This means that the increasing the number of timesteps will allow for a better temporal approximation, but will also increase the computational cost.
+Thus finding the best number of timesteps can be beneficial.
 
@@
 \subsection{The number of observations}
-The number of observations can also be considered an important aspect, since the number of observations can be limited. Thus the number of observations set to $5,10 $ and $20$, and
 
-\subsection{The noise susceptibility}
+The dependency on observations is relevant, since the number of observations of MRI data is limited.
+This was investigated by changing the number of observations, and examine the resulting states.
+The number of observation were chosen to be 5, 10  and 20, and times were set to be evenly spaced.
 
-The noise susceptibility can be seen in Tab. ?? and Tab. ??, and we see that a noise amplitude of $10 \%$ does not lead to significant change
+The results are shown in Tab.??, Tab.\ref{TAB::double} and Tab.\ref{TAB::half}. 
+\subsection{Sparse observations}
+
+The MRI data contains observations after the injection of CSF tracer.
+These observation are unevenly distributed in time, and thus there are large time intervals with no observations.
+Thus the effect of this temporal gap in the observations will be evaluated.
+This is done by selecting the observation times as follows  $t_i = [0.8, 1.0, 1.2, 1.8, 2.4, 3.6, 5.4, 7.6, 24.0]$.
+Furthermore, the optimal regularization parameters and noise susceptibility was also checked.
+
+\subsection{MRI Data}
+
+The MRI data consisted of the observations at times $t_i \in \lbrace 0.00, 0.16, 0.39, 0.55, 0.77, 2.09, 6.05, 24.06, 47.84, 698.02 \rbrace (hours)$ and $t_i=0.00$ was the observation 1-2 hours after the tracer was injected.
+There was no signifcant visible change in the tracer between the observations at $\lbrace 0.16, 0.39, 0.55, 0.77 \rbrace$.
+This prompted the focus on the observation times  $0.00 2.09, 6.05, 24.06, 47.84$, which can be seen in Fig.??.
+
+The time range for the selected observations
 
 \section{Discussion}
-
-The diffusion equation does not pose any difficulties numerically
-
-This method can be adapted to
 
@@
 \centering
-\caption{Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$ and number of observation $\tau$ with the resulting number of iterations and estimated optimal parameters for the diffusion coefficients.
+\caption{Shows the regularization parameters $\alpha$ and $\beta$, number of timesteps $k$ and number of observation $\tau$ with the resulting number of iterations and the relative error for the control parameters.
 }
 \resizebox{0.9\textwidth}{!}{\begin{tabular}{*{8}c}
-$\alpha$ & $\beta$ & k  & iter & $ D_{\Omega_1} = 1000$ & $ D_{\Omega_2} = 4.0 $ & $D_{\Omega_3} = 8.0 $ & $g$ \\
+$\alpha$ & $\beta$ & k  & iter & $ ||D_{\Omega_1}||$ & $ ||D_{\Omega_2}|| $ & $||D_{\Omega_3}||$ & $||g||$ \\
 \hline
 \rowcolor{red}  1.0e+00 	 & 1.0e+00 	 & 10 & 225 	 & +4.148 & +0.304 & +0.092 & +0.135 \\ 
-\rowcolor{red}  1.0e+00 	 & 1.0e-01 	 & 10 & 206 	 & +4.272 & +0.305 & +0.091 & +0.142 \\ 
+%\rowcolor{red}  1.0e+00 	 & 1.0e-01 	 & 10 & 206 	 & +4.272 & +0.305 & +0.091 & +0.142 \\ 
 \rowcolor{red}  1.0e+00 	 & 1.0e-02 	 & 10 & 233 	 & +4.272 & +0.305 & +0.091 & +0.143 \\ 
-\rowcolor{red}  1.0e+00 	 & 1.0e-03 	 & 10 & 208 	 & +4.437 & +0.305 & +0.091 & +0.143 \\ 
+%\rowcolor{red}  1.0e+00 	 & 1.0e-03 	 & 10 & 208 	 & +4.437 & +0.305 & +0.091 & +0.143 \\ 
 \rowcolor{red}  1.0e+00 	 & 1.0e-04 	 & 10 & 204 	 & +4.271 & +0.306 & +0.091 & +0.143 \\ 
-\rowcolor{red}  1.0e+00 	 & 1.0e-05 	 & 10 & 203 	 & +4.400 & +0.305 & +0.091 & +0.143 \\ 
+%\rowcolor{red}  1.0e+00 	 & 1.0e-05 	 & 10 & 203 	 & +4.400 & +0.305 & +0.091 & +0.143 \\ 
 \rowcolor{red}  1.0e+00 	 & 1.0e-06 	 & 10 & 222 	 & +4.584 & +0.304 & +0.090 & +0.143 \\
@@
  1.0e-01 	 & 1.0e+00 	 & 10 & 207 	 & +0.127 & +0.093 & +0.041 & +0.027 \\ 
- 1.0e-01 	 & 1.0e-01 	 & 10 & 196 	 & +0.121 & +0.093 & +0.041 & +0.046 \\ 
+ %1.0e-01 	 & 1.0e-01 	 & 10 & 196 	 & +0.121 & +0.093 & +0.041 & +0.046 \\ 
  1.0e-01 	 & 1.0e-02 	 & 10 & 232 	 & +0.123 & +0.093 & +0.041 & +0.056 \\ 
- 1.0e-01 	 & 1.0e-03 	 & 10 & 183 	 & +0.122 & +0.093 & +0.040 & +0.057 \\ 
+ %1.0e-01 	 & 1.0e-03 	 & 10 & 183 	 & +0.122 & +0.093 & +0.040 & +0.057 \\ 
  1.0e-01 	 & 1.0e-04 	 & 10 & 212 	 & +0.122 & +0.093 & +0.040 & +0.057 \\ 
- 1.0e-01 	 & 1.0e-05 	 & 10 & 168 	 & +0.122 & +0.093 & +0.041 & +0.057 \\
+ %1.0e-01 	 & 1.0e-05 	 & 10 & 168 	 & +0.122 & +0.093 & +0.041 & +0.057 \\
  1.0e-01 	 & 1.0e-06 	 & 10 & 195 	 & +0.122 & +0.093 & +0.041 & +0.057 \\
@@
  1.0e-02 	 & 1.0e+00 	 & 10 & 227 	 & +0.015 & +0.067 & +0.039 & +0.018 \\ 
- 1.0e-02 	 & 1.0e-01 	 & 10 & 153 	 & +0.006 & +0.065 & +0.039 & +0.021 \\ 
+ %1.0e-02 	 & 1.0e-01 	 & 10 & 153 	 & +0.006 & +0.065 & +0.039 & +0.021 \\ 
  1.0e-02 	 & 1.0e-02 	 & 10 & 184 	 & +0.005 & +0.065 & +0.039 & +0.039 \\ 
- 1.0e-02 	 & 1.0e-03 	 & 10 & 176 	 & +0.004 & +0.065 & +0.039 & +0.048 \\ 
+ %1.0e-02 	 & 1.0e-03 	 & 10 & 176 	 & +0.004 & +0.065 & +0.039 & +0.048 \\ 
  1.0e-02 	 & 1.0e-04 	 & 10 & 195 	 & +0.005 & +0.065 & +0.039 & +0.049 \\ 
- 1.0e-02 	 & 1.0e-05 	 & 10 & 215 	 & +0.004 & +0.065 & +0.039 & +0.051 \\ 
+ %1.0e-02 	 & 1.0e-05 	 & 10 & 215 	 & +0.004 & +0.065 & +0.039 & +0.051 \\ 
  1.0e-02 	 & 1.0e-06 	 & 10 & 205 	 & +0.005 & +0.065 & +0.039 & +0.050 \\
@@
  1.0e-03 	 & 1.0e+00 	 & 10 & 179 	 & +0.004 & +0.064 & +0.039 & +0.019 \\ 
- 1.0e-03 	 & 1.0e-01 	 & 10 & 221 	 & -0.005 & +0.063 & +0.039 & +0.018 \\ 
+ %1.0e-03 	 & 1.0e-01 	 & 10 & 221 	 & -0.005 & +0.063 & +0.039 & +0.018 \\ 
  1.0e-03 	 & 1.0e-02 	 & 10 & 89 	 & -0.007 & +0.063 & +0.039 & +0.026 \\ 
- 1.0e-03 	 & 1.0e-03 	 & 10 & 77 	 & -0.005 & +0.062 & +0.039 & +0.027 \\ 
+ %1.0e-03 	 & 1.0e-03 	 & 10 & 77 	 & -0.005 & +0.062 & +0.039 & +0.027 \\ 
  1.0e-03 	 & 1.0e-04 	 & 10 & 100 	 & -0.006 & +0.062 & +0.039 & +0.027 \\ 
- 1.0e-03 	 & 1.0e-05 	 & 10 & 105 	 & -0.006 & +0.062 & +0.039 & +0.027 \\ 
+ %1.0e-03 	 & 1.0e-05 	 & 10 & 105 	 & -0.006 & +0.062 & +0.039 & +0.027 \\ 
  1.0e-03 	 & 1.0e-06 	 & 10 & 123 	 & -0.007 & +0.062 & +0.039 & +0.028 \\
@@
  1.0e-04 	 & 1.0e+00 	 & 10 & 236 	 & +0.004 & +0.063 & +0.039 & +0.019 \\ 
- 1.0e-04 	 & 1.0e-01 	 & 10 & 195 	 & -0.006 & +0.062 & +0.039 & +0.018 \\ 
+ %1.0e-04 	 & 1.0e-01 	 & 10 & 195 	 & -0.006 & +0.062 & +0.039 & +0.018 \\ 
  1.0e-04 	 & 1.0e-02 	 & 10 & 152 	 & -0.006 & +0.062 & +0.039 & +0.022 \\ 
- 1.0e-04 	 & 1.0e-03 	 & 10 & 119 	 & -0.008 & +0.062 & +0.039 & +0.026 \\ 
+ %1.0e-04 	 & 1.0e-03 	 & 10 & 119 	 & -0.008 & +0.062 & +0.039 & +0.026 \\ 
  1.0e-04 	 & 1.0e-04 	 & 10 & 106 	 & -0.007 & +0.062 & +0.039 & +0.026 \\ 
- 1.0e-04 	 & 1.0e-05 	 & 10 & 109 	 & -0.007 & +0.062 & +0.039 & +0.026 \\ 
+ %1.0e-04 	 & 1.0e-05 	 & 10 & 109 	 & -0.007 & +0.062 & +0.039 & +0.026 \\ 
  1.0e-04 	 & 1.0e-06 	 & 10 & 99 	 & -0.008 & +0.062 & +0.039 & +0.026 \\
@@
  1.0e-05 	 & 1.0e+00 	 & 10 & 139 	 & +0.004 & +0.063 & +0.039 & +0.019 \\ 
- 1.0e-05 	 & 1.0e-01 	 & 10 & 170 	 & -0.006 & +0.062 & +0.039 & +0.018 \\ 
+ %1.0e-05 	 & 1.0e-01 	 & 10 & 170 	 & -0.006 & +0.062 & +0.039 & +0.018 \\ 
  1.0e-05 	 & 1.0e-02 	 & 10 & 182 	 & -0.007 & +0.062 & +0.039 & +0.020 \\ 
- 1.0e-05 	 & 1.0e-03 	 & 10 & 70 	 & -0.007 & +0.062 & +0.039 & +0.026 \\ 
+ %1.0e-05 	 & 1.0e-03 	 & 10 & 70 	 & -0.007 & +0.062 & +0.039 & +0.026 \\ 
  1.0e-05 	 & 1.0e-04 	 & 10 & 77 	 & -0.007 & +0.062 & +0.039 & +0.026 \\ 
- 1.0e-05 	 & 1.0e-05 	 & 10 & 104 	 & -0.008 & +0.062 & +0.039 & +0.026 \\ 
+ %1.0e-05 	 & 1.0e-05 	 & 10 & 104 	 & -0.008 & +0.062 & +0.039 & +0.026 \\ 
  1.0e-05 	 & 1.0e-06 	 & 10 & 92 	 & -0.007 & +0.062 & +0.039 & +0.026 \\
@@
  1.0e-06 	 & 1.0e+00 	 & 10 & 163 	 & +0.003 & +0.064 & +0.039 & +0.019 \\ 
- 1.0e-06 	 & 1.0e-01 	 & 10 & 218 	 & -0.006 & +0.062 & +0.039 & +0.018 \\ 
+ %1.0e-06 	 & 1.0e-01 	 & 10 & 218 	 & -0.006 & +0.062 & +0.039 & +0.018 \\ 
  1.0e-06 	 & 1.0e-02 	 & 10 & 134 	 & -0.008 & +0.062 & +0.039 & +0.023 \\ 
- 1.0e-06 	 & 1.0e-03 	 & 10 & 79 	 & -0.006 & +0.062 & +0.039 & +0.026 \\ 
+ %1.0e-06 	 & 1.0e-03 	 & 10 & 79 	 & -0.006 & +0.062 & +0.039 & +0.026 \\ 
  1.0e-06 	 & 1.0e-04 	 & 10 & 107 	 & -0.007 & +0.062 & +0.039 & +0.026 \\ 
- 1.0e-06 	 & 1.0e-05 	 & 10 & 103 	 & -0.008 & +0.062 & +0.039 & +0.026 \\ 
+ %1.0e-06 	 & 1.0e-05 	 & 10 & 103 	 & -0.008 & +0.062 & +0.039 & +0.026 \\ 
  1.0e-06 	 & 1.0e-06 	 & 10 & 91 	 & -0.008 & +0.062 & +0.039 & +0.026 \\  
@@
  1.0e+00 	 & 1.0e+00 	 & 10 & 218 	 & +4.266 & +0.304 & +0.092 & +0.135 \\ 
- 1.0e+00 	 & 1.0e-01 	 & 10 & 223 	 & +4.565 & +0.304 & +0.090 & +0.142 \\ 
+ %1.0e+00 	 & 1.0e-01 	 & 10 & 223 	 & +4.565 & +0.304 & +0.090 & +0.142 \\ 
  1.0e+00 	 & 1.0e-02 	 & 10 & 199 	 & +4.268 & +0.305 & +0.090 & +0.143 \\ 
- 1.0e+00 	 & 1.0e-03 	 & 10 & 222 	 & +4.274 & +0.305 & +0.090 & +0.143 \\ 
+% 1.0e+00 	 & 1.0e-03 	 & 10 & 222 	 & +4.274 & +0.305 & +0.090 & +0.143 \\ 
  1.0e+00 	 & 1.0e-04 	 & 10 & 211 	 & +4.448 & +0.306 & +0.090 & +0.143 \\ 
- 1.0e+00 	 & 1.0e-05 	 & 10 & 227 	 & +4.527 & +0.304 & +0.090 & +0.143 \\ 
+% 1.0e+00 	 & 1.0e-05 	 & 10 & 227 	 & +4.527 & +0.304 & +0.090 & +0.143 \\ 
  1.0e+00 	 & 1.0e-06 	 & 10 & 263 	 & +4.266 & +0.306 & +0.091 & +0.143 \\
@@
  1.0e-01 	 & 1.0e+00 	 & 10 & 167 	 & +0.131 & +0.093 & +0.041 & +0.027 \\ 
- 1.0e-01 	 & 1.0e-01 	 & 10 & 195 	 & +0.125 & +0.093 & +0.039 & +0.046 \\ 
+% 1.0e-01 	 & 1.0e-01 	 & 10 & 195 	 & +0.125 & +0.093 & +0.039 & +0.046 \\ 
  1.0e-01 	 & 1.0e-02 	 & 10 & 218 	 & +0.126 & +0.093 & +0.040 & +0.056 \\ 
- 1.0e-01 	 & 1.0e-03 	 & 10 & 161 	 & +0.129 & +0.094 & +0.040 & +0.057 \\ 
+% 1.0e-01 	 & 1.0e-03 	 & 10 & 161 	 & +0.129 & +0.094 & +0.040 & +0.057 \\ 
  1.0e-01 	 & 1.0e-04 	 & 10 & 180 	 & +0.135 & +0.092 & +0.042 & +0.057 \\ 
- 1.0e-01 	 & 1.0e-05 	 & 10 & 169 	 & +0.123 & +0.093 & +0.041 & +0.057 \\ 
+% 1.0e-01 	 & 1.0e-05 	 & 10 & 169 	 & +0.123 & +0.093 & +0.041 & +0.057 \\ 
  1.0e-01 	 & 1.0e-06 	 & 10 & 201 	 & +0.119 & +0.093 & +0.040 & +0.057 \\
@@
  1.0e-02 	 & 1.0e+00 	 & 10 & 183 	 & +0.013 & +0.067 & +0.040 & +0.018 \\ 
- 1.0e-02 	 & 1.0e-01 	 & 10 & 149 	 & +0.002 & +0.066 & +0.038 & +0.021 \\ 
+% 1.0e-02 	 & 1.0e-01 	 & 10 & 149 	 & +0.002 & +0.066 & +0.038 & +0.021 \\ 
  1.0e-02 	 & 1.0e-02 	 & 10 & 185 	 & -0.005 & +0.065 & +0.040 & +0.040 \\ 
- 1.0e-02 	 & 1.0e-03 	 & 10 & 213 	 & +0.004 & +0.066 & +0.038 & +0.049 \\ 
+% 1.0e-02 	 & 1.0e-03 	 & 10 & 213 	 & +0.004 & +0.066 & +0.038 & +0.049 \\ 
  1.0e-02 	 & 1.0e-04 	 & 10 & 151 	 & +0.008 & +0.066 & +0.039 & +0.047 \\ 
- 1.0e-02 	 & 1.0e-05 	 & 10 & 197 	 & +0.004 & +0.064 & +0.040 & +0.051 \\ 
+% 1.0e-02 	 & 1.0e-05 	 & 10 & 197 	 & +0.004 & +0.064 & +0.040 & +0.051 \\ 
  1.0e-02 	 & 1.0e-06 	 & 10 & 185 	 & +0.012 & +0.063 & +0.038 & +0.049 \\
@@
  1.0e-03 	 & 1.0e+00 	 & 10 & 183 	 & +0.007 & +0.062 & +0.038 & +0.019 \\ 
- 1.0e-03 	 & 1.0e-01 	 & 10 & 181 	 & -0.011 & +0.063 & +0.039 & +0.019 \\ 
+%1.0e-03 	 & 1.0e-01 	 & 10 & 181 	 & -0.011 & +0.063 & +0.039 & +0.019 \\ 
  1.0e-03 	 & 1.0e-02 	 & 10 & 122 	 & -0.008 & +0.063 & +0.040 & +0.025 \\ 
- 1.0e-03 	 & 1.0e-03 	 & 10 & 158 	 & -0.004 & +0.062 & +0.040 & +0.028 \\ 
+% 1.0e-03 	 & 1.0e-03 	 & 10 & 158 	 & -0.004 & +0.062 & +0.040 & +0.028 \\ 
  1.0e-03 	 & 1.0e-04 	 & 10 & 168 	 & -0.013 & +0.063 & +0.038 & +0.029 \\ 
- 1.0e-03 	 & 1.0e-05 	 & 10 & 120 	 & -0.010 & +0.063 & +0.040 & +0.028 \\ 
+% 1.0e-03 	 & 1.0e-05 	 & 10 & 120 	 & -0.010 & +0.063 & +0.040 & +0.028 \\ 
  1.0e-03 	 & 1.0e-06 	 & 10 & 132 	 & -0.002 & +0.062 & +0.039 & +0.028 \\
@@
  1.0e-04 	 & 1.0e+00 	 & 10 & 176 	 & +0.000 & +0.063 & +0.039 & +0.019 \\ 
- 1.0e-04 	 & 1.0e-01 	 & 10 & 180 	 & -0.001 & +0.062 & +0.039 & +0.019 \\ 
+ %1.0e-04 	 & 1.0e-01 	 & 10 & 180 	 & -0.001 & +0.062 & +0.039 & +0.019 \\ 
  1.0e-04 	 & 1.0e-02 	 & 10 & 120 	 & +0.000 & +0.063 & +0.039 & +0.024 \\ 
- 1.0e-04 	 & 1.0e-03 	 & 10 & 119 	 & -0.004 & +0.062 & +0.039 & +0.026 \\ 
+ %1.0e-04 	 & 1.0e-03 	 & 10 & 119 	 & -0.004 & +0.062 & +0.039 & +0.026 \\ 
  1.0e-04 	 & 1.0e-04 	 & 10 & 77 	 & -0.005 & +0.061 & +0.038 & +0.027 \\ 
- 1.0e-04 	 & 1.0e-05 	 & 10 & 104 	 & -0.004 & +0.062 & +0.038 & +0.027 \\ 
+ %1.0e-04 	 & 1.0e-05 	 & 10 & 104 	 & -0.004 & +0.062 & +0.038 & +0.027 \\ 
  1.0e-04 	 & 1.0e-06 	 & 10 & 109 	 & -0.007 & +0.062 & +0.039 & +0.027 \\
@@
  1.0e-05 	 & 1.0e+00 	 & 10 & 220 	 & +0.005 & +0.063 & +0.039 & +0.019 \\ 
- 1.0e-05 	 & 1.0e-01 	 & 10 & 193 	 & -0.009 & +0.062 & +0.039 & +0.019 \\ 
+ %1.0e-05 	 & 1.0e-01 	 & 10 & 193 	 & -0.009 & +0.062 & +0.039 & +0.019 \\ 
  1.0e-05 	 & 1.0e-02 	 & 10 & 163 	 & -0.013 & +0.063 & +0.039 & +0.021 \\ 
- 1.0e-05 	 & 1.0e-03 	 & 10 & 115 	 & -0.007 & +0.063 & +0.040 & +0.026 \\ 
+ %1.0e-05 	 & 1.0e-03 	 & 10 & 115 	 & -0.007 & +0.063 & +0.040 & +0.026 \\ 
  1.0e-05 	 & 1.0e-04 	 & 10 & 82 	 & -0.007 & +0.062 & +0.038 & +0.027 \\ 
- 1.0e-05 	 & 1.0e-05 	 & 10 & 145 	 & -0.001 & +0.062 & +0.039 & +0.027 \\ 
+ %1.0e-05 	 & 1.0e-05 	 & 10 & 145 	 & -0.001 & +0.062 & +0.039 & +0.027 \\ 
  1.0e-05 	 & 1.0e-06 	 & 10 & 147 	 & -0.012 & +0.061 & +0.040 & +0.027 \\
@@
  1.0e-06 	 & 1.0e+00 	 & 10 & 138 	 & +0.002 & +0.063 & +0.039 & +0.019 \\ 
- 1.0e-06 	 & 1.0e-01 	 & 10 & 184 	 & -0.006 & +0.063 & +0.039 & +0.019 \\ 
+ %1.0e-06 	 & 1.0e-01 	 & 10 & 184 	 & -0.006 & +0.063 & +0.039 & +0.019 \\ 
  1.0e-06 	 & 1.0e-02 	 & 10 & 83 	 & -0.006 & +0.063 & +0.040 & +0.025 \\ 
- 1.0e-06 	 & 1.0e-03 	 & 10 & 91 	 & -0.013 & +0.063 & +0.039 & +0.026 \\ 
+ %1.0e-06 	 & 1.0e-03 	 & 10 & 91 	 & -0.013 & +0.063 & +0.039 & +0.026 \\ 
  1.0e-06 	 & 1.0e-04 	 & 10 & 109 	 & -0.005 & +0.062 & +0.038 & +0.027 \\ 
- 1.0e-06 	 & 1.0e-05 	 & 10 & 116 	 & -0.007 & +0.063 & +0.039 & +0.027 \\ 
+ %1.0e-06 	 & 1.0e-05 	 & 10 & 116 	 & -0.007 & +0.063 & +0.039 & +0.027 \\ 
  1.0e-06 	 & 1.0e-06 	 & 10 & 108 	 & +0.001 & +0.062 & +0.040 & +0.027 \\ 
 \end{tabular}}
-\label{Tab::4}
+\label{Tab::Noise0.03}
 \end{table} 
@@
  1.0e+00 	 & 1.0e+00 	 & 10 & 212 	 & +4.268 & +0.310 & +0.073 & +0.138 \\ 
- 1.0e+00 	 & 1.0e-01 	 & 10 & 211 	 & +4.122 & +0.302 & +0.085 & +0.146 \\ 
+ %1.0e+00 	 & 1.0e-01 	 & 10 & 211 	 & +4.122 & +0.302 & +0.085 & +0.146 \\ 
  1.0e+00 	 & 1.0e-02 	 & 10 & 221 	 & +4.773 & +0.298 & +0.089 & +0.147 \\ 
- 1.0e+00 	 & 1.0e-03 	 & 10 & 257 	 & +4.872 & +0.301 & +0.090 & +0.147 \\ 
+ %1.0e+00 	 & 1.0e-03 	 & 10 & 257 	 & +4.872 & +0.301 & +0.090 & +0.147 \\ 
  1.0e+00 	 & 1.0e-04 	 & 10 & 238 	 & +4.186 & +0.293 & +0.097 & +0.148 \\ 
- 1.0e+00 	 & 1.0e-05 	 & 10 & 204 	 & +4.251 & +0.313 & +0.085 & +0.147 \\ 
+ %1.0e+00 	 & 1.0e-05 	 & 10 & 204 	 & +4.251 & +0.313 & +0.085 & +0.147 \\ 
  1.0e+00 	 & 1.0e-06 	 & 10 & 223 	 & +4.493 & +0.310 & +0.085 & +0.147 \\ 
- 1.0e-01 	 & 1.0e+00 	 & 10 & 145 	 & +0.126 & +0.100 & +0.054 & +0.035 \\ 
+ %1.0e-01 	 & 1.0e+00 	 & 10 & 145 	 & +0.126 & +0.100 & +0.054 & +0.035 \\ 
  1.0e-01 	 & 1.0e-01 	 & 10 & 199 	 & +0.115 & +0.125 & +0.026 & +0.060 \\ 
- 1.0e-01 	 & 1.0e-02 	 & 10 & 217 	 & +0.128 & +0.092 & +0.036 & +0.071 \\ 
+ %1.0e-01 	 & 1.0e-02 	 & 10 & 217 	 & +0.128 & +0.092 & +0.036 & +0.071 \\ 
  1.0e-01 	 & 1.0e-03 	 & 10 & 242 	 & +0.109 & +0.093 & +0.031 & +0.073 \\ 
- 1.0e-01 	 & 1.0e-04 	 & 10 & 275 	 & +0.187 & +0.094 & +0.028 & +0.073 \\ 
+ %1.0e-01 	 & 1.0e-04 	 & 10 & 275 	 & +0.187 & +0.094 & +0.028 & +0.073 \\ 
  1.0e-01 	 & 1.0e-05 	 & 10 & 237 	 & +0.048 & +0.099 & +0.039 & +0.073 \\ 
- 1.0e-01 	 & 1.0e-06 	 & 10 & 225 	 & +0.092 & +0.111 & +0.055 & +0.073 \\ 
+ %1.0e-01 	 & 1.0e-06 	 & 10 & 225 	 & +0.092 & +0.111 & +0.055 & +0.073 \\ 
  1.0e-02 	 & 1.0e+00 	 & 10 & 208 	 & +0.017 & +0.075 & +0.037 & +0.029 \\ 
- 1.0e-02 	 & 1.0e-01 	 & 10 & 199 	 & -0.013 & +0.068 & +0.046 & +0.040 \\ 
+ %1.0e-02 	 & 1.0e-01 	 & 10 & 199 	 & -0.013 & +0.068 & +0.046 & +0.040 \\ 
  1.0e-02 	 & 1.0e-02 	 & 10 & 348 	 & -0.043 & +0.073 & +0.041 & +0.063 \\ 
- 1.0e-02 	 & 1.0e-03 	 & 10 & 400 	 & +0.056 & +0.058 & +0.031 & +0.075 \\ 
+% 1.0e-02 	 & 1.0e-03 	 & 10 & 400 	 & +0.056 & +0.058 & +0.031 & +0.075 \\ 
  1.0e-02 	 & 1.0e-04 	 & 10 & 393 	 & -0.050 & +0.088 & +0.044 & +0.077 \\ 
- 1.0e-02 	 & 1.0e-05 	 & 10 & 359 	 & +0.022 & +0.068 & +0.027 & +0.076 \\ 
+ %1.0e-02 	 & 1.0e-05 	 & 10 & 359 	 & +0.022 & +0.068 & +0.027 & +0.076 \\ 
  1.0e-02 	 & 1.0e-06 	 & 10 & 369 	 & +0.001 & +0.074 & +0.024 & +0.076 \\ 
- 1.0e-03 	 & 1.0e+00 	 & 10 & 207 	 & -0.001 & +0.065 & +0.051 & +0.029 \\ 
+ %1.0e-03 	 & 1.0e+00 	 & 10 & 207 	 & -0.001 & +0.065 & +0.051 & +0.029 \\ 
  1.0e-03 	 & 1.0e-01 	 & 10 & 280 	 & +0.028 & +0.051 & +0.053 & +0.038 \\ 
- 1.0e-03 	 & 1.0e-02 	 & 10 & 565 	 & -0.059 & +0.076 & +0.033 & +0.053 \\ 
+ %1.0e-03 	 & 1.0e-02 	 & 10 & 565 	 & -0.059 & +0.076 & +0.033 & +0.053 \\ 
  \rowcolor{orange} 1.0e-03 	 & 1.0e-03 	 & 10 & 673 	 & -0.035 & +0.066 & +0.032 & +0.108 \\ 
- \rowcolor{orange} 1.0e-03 	 & 1.0e-04 	 & 10 & 604 	 & -0.026 & +0.061 & +0.049 & +0.182 \\ 
+ %\rowcolor{orange} 1.0e-03 	 & 1.0e-04 	 & 10 & 604 	 & -0.026 & +0.061 & +0.049 & +0.182 \\ 
  \rowcolor{orange} 1.0e-03 	 & 1.0e-05 	 & 10 & 666 	 & +0.012 & +0.070 & +0.038 & +0.182 \\ 
- \rowcolor{orange} 1.0e-03 	 & 1.0e-06 	 & 10 & 893 	 & +0.027 & +0.070 & +0.022 & +0.180 \\ 
+ %\rowcolor{orange} 1.0e-03 	 & 1.0e-06 	 & 10 & 893 	 & +0.027 & +0.070 & +0.022 & +0.180 \\ 
  1.0e-04 	 & 1.0e+00 	 & 10 & 204 	 & +0.015 & +0.062 & +0.043 & +0.030 \\ 
- 1.0e-04 	 & 1.0e-01 	 & 10 & 269 	 & +0.005 & +0.057 & +0.037 & +0.038 \\ 
+ %1.0e-04 	 & 1.0e-01 	 & 10 & 269 	 & +0.005 & +0.057 & +0.037 & +0.038 \\ 
  1.0e-04 	 & 1.0e-02 	 & 10 & 559 	 & -0.072 & +0.067 & +0.044 & +0.050 \\ 
-\rowcolor{orange} 1.0e-04 	 & 1.0e-03 	 & 10 & 691 	 & -0.023 & +0.055 & +0.040 & +0.175 \\ 
+%\rowcolor{orange} 1.0e-04 	 & 1.0e-03 	 & 10 & 691 	 & -0.023 & +0.055 & +0.040 & +0.175 \\ 
 \rowcolor{red}  1.0e-04 	 & 1.0e-04 	 & 10 & 1001 	 & -0.012 & +0.066 & +0.030 & +0.745 \\ 
-\rowcolor{red}  1.0e-04 	 & 1.0e-05 	 & 10 & 1001 	 & +0.038 & +0.057 & +0.034 & +1.113 \\ 
+%\rowcolor{red}  1.0e-04 	 & 1.0e-05 	 & 10 & 1001 	 & +0.038 & +0.057 & +0.034 & +1.113 \\ 
 \rowcolor{red} 1.0e-04 	 & 1.0e-06 	 & 10 & 1001 	 & +0.015 & +0.063 & +0.035 & +1.127 \\ 
- 1.0e-05 	 & 1.0e+00 	 & 10 & 184 	 & -0.025 & +0.076 & +0.041 & +0.029 \\ 
+% 1.0e-05 	 & 1.0e+00 	 & 10 & 184 	 & -0.025 & +0.076 & +0.041 & +0.029 \\ 
  1.0e-05 	 & 1.0e-01 	 & 10 & 357 	 & -0.011 & +0.070 & +0.052 & +0.038 \\ 
- 1.0e-05 	 & 1.0e-02 	 & 10 & 399 	 & +0.041 & +0.075 & +0.042 & +0.049 \\ 
+% 1.0e-05 	 & 1.0e-02 	 & 10 & 399 	 & +0.041 & +0.075 & +0.042 & +0.049 \\ 
  \rowcolor{orange} 1.0e-05 	 & 1.0e-03 	 & 10 & 689 	 & +0.044 & +0.062 & +0.020 & +0.172 \\ 
-\rowcolor{red} 1.0e-05 	 & 1.0e-04 	 & 10 & 915 	 & +0.030 & +0.077 & +0.039 & +1.027 \\ 
+%\rowcolor{red} 1.0e-05 	 & 1.0e-04 	 & 10 & 915 	 & +0.030 & +0.077 & +0.039 & +1.027 \\ 
 \rowcolor{red} 1.0e-05 	 & 1.0e-05 	 & 10 & 1001 	 & +0.017 & +0.061 & +0.045 & +1.953 \\ 
-\rowcolor{red}  1.0e-05 	 & 1.0e-06 	 & 10 & 1001 	 & -0.018 & +0.071 & +0.045 & +2.545 \\ 
+%\rowcolor{red}  1.0e-05 	 & 1.0e-06 	 & 10 & 1001 	 & -0.018 & +0.071 & +0.045 & +2.545 \\ 
  1.0e-06 	 & 1.0e+00 	 & 10 & 177 	 & +0.060 & +0.069 & +0.039 & +0.029 \\ 
- 1.0e-06 	 & 1.0e-01 	 & 10 & 302 	 & +0.011 & +0.039 & +0.039 & +0.038 \\ 
+% 1.0e-06 	 & 1.0e-01 	 & 10 & 302 	 & +0.011 & +0.039 & +0.039 & +0.038 \\ 
  1.0e-06 	 & 1.0e-02 	 & 10 & 457 	 & +0.011 & +0.055 & +0.036 & +0.050 \\ 
-\rowcolor{orange} 1.0e-06 	 & 1.0e-03 	 & 10 & 738 	 & -0.022 & +0.055 & +0.042 & +0.172 \\ 
+%\rowcolor{orange} 1.0e-06 	 & 1.0e-03 	 & 10 & 738 	 & -0.022 & +0.055 & +0.042 & +0.172 \\ 
 \rowcolor{red}  1.0e-06 	 & 1.0e-04 	 & 10 & 1001 	 & -0.043 & +0.042 & +0.054 & +1.180 \\ 
-\rowcolor{red}  1.0e-06 	 & 1.0e-05 	 & 10 & 1001 	 & +0.006 & +0.052 & +0.033 & +3.365 \\ 
+%\rowcolor{red}  1.0e-06 	 & 1.0e-05 	 & 10 & 1001 	 & +0.006 & +0.052 & +0.033 & +3.365 \\ 
 \rowcolor{red}  1.0e-06 	 & 1.0e-06 	 & 10 & 1001 	 & -0.002 & +0.065 & +0.051 & +3.402 \\ 
 \end{tabular}}
-\label{Tab::5}
+\label{Tab::Noise0.3}
 \end{table}
@@
  1.0e-04 	 & 1.0e+00 	 & 10 & 161 	 & +0.081 & +0.027 & +0.049 & +0.023 \\ 
- 1.0e-04 	 & 1.0e-01 	 & 10 & 185 	 & +0.123 & +0.046 & +0.037 & +0.021 \\ 
+ 1.0e-04 	 & 1.0e+00 	 & 20 & 202 	 & +0.007 & -0.050 & +0.017 & +0.028 \\ 
+ 1.0e-04 	 & 1.0e+00 	 & 40 & 308 	 & -0.032 & -0.081 & +0.002 & +0.031 \\
+
+% 1.0e-04 	 & 1.0e-01 	 & 10 & 185 	 & +0.123 & +0.046 & +0.037 & +0.021 \\ 
+% 1.0e-04 	 & 1.0e-01 	 & 20 & 336 	 & +0.028 & -0.009 & +0.009 & +0.023 \\
+% 1.0e-04 	 & 1.0e-01 	 & 40 & 379 	 & -0.004 & -0.033 & -0.006 & +0.026 \\
+
  1.0e-04 	 & 1.0e-02 	 & 10 & 265 	 & +0.160 & +0.082 & +0.033 & +0.016 \\ 
+ 1.0e-04 	 & 1.0e-02 	 & 20 & 320 	 & +0.025 & +0.025 & +0.015 & +0.013 \\
+ 1.0e-04 	 & 1.0e-02 	 & 40 & 377 	 & +0.006 & +0.006 & -0.001 & +0.008 \\
+
  1.0e-05 	 & 1.0e+00 	 & 10 & 192 	 & +0.083 & +0.026 & +0.049 & +0.023 \\ 
- 1.0e-05 	 & 1.0e-01 	 & 10 & 223 	 & +0.118 & +0.047 & +0.037 & +0.020 \\ 
+ 1.0e-05 	 & 1.0e+00 	 & 20 & 195 	 & +0.007 & -0.051 & +0.017 & +0.029 \\ 
+ 1.0e-05 	 & 1.0e+00 	 & 40 & 212 	 & -0.034 & -0.083 & +0.001 & +0.031 \\
+
+% 1.0e-05 	 & 1.0e-01 	 & 10 & 223 	 & +0.118 & +0.047 & +0.037 & +0.020 \\ 
+%  1.0e-05 	 & 1.0e-01 	 & 20 & 320 	 & +0.029 & -0.011 & +0.009 & +0.026 \\
+%  1.0e-05 	 & 1.0e-01 	 & 40 & 396 	 & -0.007 & -0.036 & -0.006 & +0.028 \\
+
   1.0e-05 	 & 1.0e-02 	 & 10 & 267 	 & +0.159 & +0.084 & +0.033 & +0.016 \\ 
+  1.0e-05 	 & 1.0e-02 	 & 20 & 351 	 & +0.023 & +0.017 & +0.011 & +0.019 \\ 
+  1.0e-05 	 & 1.0e-02 	 & 40 & 374 	 & +0.009 & +0.007 & -0.003 & +0.014 \\
+
  1.0e-06 	 & 1.0e+00 	 & 10 & 176 	 & +0.082 & +0.026 & +0.049 & +0.023 \\ 
- 1.0e-06 	 & 1.0e-01 	 & 10 & 229 	 & +0.120 & +0.046 & +0.037 & +0.021 \\ 
+ 1.0e-06 	 & 1.0e+00 	 & 20 & 224 	 & +0.007 & -0.051 & +0.017 & +0.029 \\ 
+ 1.0e-06 	 & 1.0e+00 	 & 40 & 226 	 & -0.034 & -0.082 & +0.001 & +0.031 \\
+
+% 1.0e-06 	 & 1.0e-01 	 & 10 & 229 	 & +0.120 & +0.046 & +0.037 & +0.021 \\ 
+%  1.0e-06 	 & 1.0e-01 	 & 20 & 334 	 & +0.027 & -0.012 & +0.009 & +0.026 \\  
+% 1.0e-06 	 & 1.0e-01 	 & 40 & 313 	 & -0.007 & -0.037 & -0.006 & +0.030 \\
+
  1.0e-06 	 & 1.0e-02 	 & 10 & 253 	 & +0.156 & +0.080 & +0.033 & +0.018 \\ 
- 1.0e-04 	 & 1.0e+00 	 & 20 & 202 	 & +0.007 & -0.050 & +0.017 & +0.028 \\ 
- 1.0e-04 	 & 1.0e-01 	 & 20 & 336 	 & +0.028 & -0.009 & +0.009 & +0.023 \\
- 1.0e-04 	 & 1.0e-02 	 & 20 & 320 	 & +0.025 & +0.025 & +0.015 & +0.013 \\ 
- 1.0e-05 	 & 1.0e+00 	 & 20 & 195 	 & +0.007 & -0.051 & +0.017 & +0.029 \\ 
- 1.0e-05 	 & 1.0e-01 	 & 20 & 320 	 & +0.029 & -0.011 & +0.009 & +0.026 \\ 
- 1.0e-05 	 & 1.0e-02 	 & 20 & 351 	 & +0.023 & +0.017 & +0.011 & +0.019 \\ 
- 1.0e-06 	 & 1.0e+00 	 & 20 & 224 	 & +0.007 & -0.051 & +0.017 & +0.029 \\ 
- 1.0e-06 	 & 1.0e-01 	 & 20 & 334 	 & +0.027 & -0.012 & +0.009 & +0.026 \\ 
  1.0e-06 	 & 1.0e-02 	 & 20 & 340 	 & +0.020 & +0.016 & +0.012 & +0.019 \\ 
- 1.0e-04 	 & 1.0e+00 	 & 40 & 308 	 & -0.032 & -0.081 & +0.002 & +0.031 \\ 
- 1.0e-04 	 & 1.0e-01 	 & 40 & 379 	 & -0.004 & -0.033 & -0.006 & +0.026 \\ 
- 1.0e-04 	 & 1.0e-02 	 & 40 & 377 	 & +0.006 & +0.006 & -0.001 & +0.008 \\ 
- 1.0e-05 	 & 1.0e+00 	 & 40 & 212 	 & -0.034 & -0.083 & +0.001 & +0.031 \\ 
- 1.0e-05 	 & 1.0e-01 	 & 40 & 396 	 & -0.007 & -0.036 & -0.006 & +0.028 \\ 
- 1.0e-05 	 & 1.0e-02 	 & 40 & 374 	 & +0.009 & +0.007 & -0.003 & +0.014 \\ 
- 1.0e-06 	 & 1.0e+00 	 & 40 & 226 	 & -0.034 & -0.082 & +0.001 & +0.031 \\ 
- 1.0e-06 	 & 1.0e-01 	 & 40 & 313 	 & -0.007 & -0.037 & -0.006 & +0.030 \\ 
  1.0e-06 	 & 1.0e-02 	 & 40 & 368 	 & +0.006 & +0.006 & -0.004 & +0.013 \\ 
 \end{tabular}}
+\label{TAB::half}
 \end{table}
@@
  1.0e-04 	 & 1.0e+00 	 & 10 & 246 	 & -0.046 & +0.038 & +0.023 & +0.031 \\ 
- 1.0e-04 	 & 1.0e-01 	 & 10 & 292 	 & -0.052 & +0.038 & +0.024 & +0.032 \\ 
+ 1.0e-04 	 & 1.0e+00 	 & 20 & 228 	 & -0.008 & +0.016 & +0.009 & +0.006 \\ 
+ 1.0e-04 	 & 1.0e+00 	 & 40 & 279 	 & -0.007 & +0.000 & +0.003 & +0.002 \\
+
+% 1.0e-04 	 & 1.0e-01 	 & 10 & 292 	 & -0.052 & +0.038 & +0.024 & +0.032 \\  
+% 1.0e-04 	 & 1.0e-01 	 & 20 & 331 	 & -0.001 & +0.018 & +0.006 & +0.006 \\ 
+% 1.0e-04 	 & 1.0e-01 	 & 40 & 313 	 & +0.004 & +0.003 & +0.000 & +0.002 \\
+
  1.0e-04 	 & 1.0e-02 	 & 10 & 338 	 & -0.053 & +0.038 & +0.024 & +0.032 \\ 
+  1.0e-04 	 & 1.0e-02 	 & 20 & 367 	 & +0.003 & +0.018 & +0.005 & +0.007 \\
+   1.0e-04 	 & 1.0e-02 	 & 40 & 273 	 & +0.017 & +0.006 & -0.001 & +0.001 \\
+
  1.0e-05 	 & 1.0e+00 	 & 10 & 290 	 & -0.047 & +0.038 & +0.023 & +0.031 \\ 
- 1.0e-05 	 & 1.0e-01 	 & 10 & 316 	 & -0.052 & +0.038 & +0.024 & +0.032 \\ 
+  1.0e-05 	 & 1.0e+00 	 & 20 & 194 	 & -0.008 & +0.016 & +0.009 & +0.006 \\ 
+   1.0e-05 	 & 1.0e+00 	 & 40 & 238 	 & -0.007 & +0.000 & +0.002 & +0.002 \\
+
+% 1.0e-05 	 & 1.0e-01 	 & 10 & 316 	 & -0.052 & +0.038 & +0.024 & +0.032 \\ 
+%  1.0e-05 	 & 1.0e-01 	 & 20 & 312 	 & -0.001 & +0.018 & +0.006 & +0.006 \\ 
+%   1.0e-05 	 & 1.0e-01 	 & 40 & 317 	 & +0.004 & +0.003 & +0.000 & +0.002 \\
+
  1.0e-05 	 & 1.0e-02 	 & 10 & 389 	 & -0.052 & +0.038 & +0.024 & +0.033 \\ 
+  1.0e-05 	 & 1.0e-02 	 & 20 & 266 	 & +0.004 & +0.018 & +0.005 & +0.007 \\ 
+   1.0e-05 	 & 1.0e-02 	 & 40 & 336 	 & +0.015 & +0.005 & -0.001 & +0.001 \\
+
  1.0e-06 	 & 1.0e+00 	 & 10 & 282 	 & -0.047 & +0.038 & +0.023 & +0.031 \\ 
- 1.0e-06 	 & 1.0e-01 	 & 10 & 308 	 & -0.052 & +0.038 & +0.024 & +0.032 \\ 
+  1.0e-06 	 & 1.0e+00 	 & 20 & 179 	 & -0.008 & +0.016 & +0.009 & +0.006 \\ 
+  1.0e-06 	 & 1.0e+00 	 & 40 & 261 	 & -0.007 & +0.000 & +0.002 & +0.002 \\
+
+% 1.0e-06 	 & 1.0e-01 	 & 10 & 308 	 & -0.052 & +0.038 & +0.024 & +0.032 \\ 
+%  1.0e-06 	 & 1.0e-01 	 & 20 & 245 	 & -0.002 & +0.018 & +0.006 & +0.006 \\ 
+%   1.0e-06 	 & 1.0e-01 	 & 40 & 318 	 & +0.004 & +0.003 & +0.000 & +0.002 \\
+
  1.0e-06 	 & 1.0e-02 	 & 10 & 285 	 & -0.052 & +0.038 & +0.024 & +0.032 \\ 
- 1.0e-04 	 & 1.0e+00 	 & 20 & 228 	 & -0.008 & +0.016 & +0.009 & +0.006 \\ 
- 1.0e-04 	 & 1.0e-01 	 & 20 & 331 	 & -0.001 & +0.018 & +0.006 & +0.006 \\ 
- 1.0e-04 	 & 1.0e-02 	 & 20 & 367 	 & +0.003 & +0.018 & +0.005 & +0.007 \\ 
- 1.0e-05 	 & 1.0e+00 	 & 20 & 194 	 & -0.008 & +0.016 & +0.009 & +0.006 \\ 
- 1.0e-05 	 & 1.0e-01 	 & 20 & 312 	 & -0.001 & +0.018 & +0.006 & +0.006 \\ 
- 1.0e-05 	 & 1.0e-02 	 & 20 & 266 	 & +0.004 & +0.018 & +0.005 & +0.007 \\ 
- 1.0e-06 	 & 1.0e+00 	 & 20 & 179 	 & -0.008 & +0.016 & +0.009 & +0.006 \\ 
- 1.0e-06 	 & 1.0e-01 	 & 20 & 245 	 & -0.002 & +0.018 & +0.006 & +0.006 \\ 
  1.0e-06 	 & 1.0e-02 	 & 20 & 362 	 & +0.003 & +0.018 & +0.005 & +0.007 \\ 
- 1.0e-04 	 & 1.0e+00 	 & 40 & 279 	 & -0.007 & +0.000 & +0.003 & +0.002 \\ 
- 1.0e-04 	 & 1.0e-01 	 & 40 & 313 	 & +0.004 & +0.003 & +0.000 & +0.002 \\ 
- 1.0e-04 	 & 1.0e-02 	 & 40 & 273 	 & +0.017 & +0.006 & -0.001 & +0.001 \\ 
- 1.0e-05 	 & 1.0e+00 	 & 40 & 238 	 & -0.007 & +0.000 & +0.002 & +0.002 \\ 
- 1.0e-05 	 & 1.0e-01 	 & 40 & 317 	 & +0.004 & +0.003 & +0.000 & +0.002 \\ 
- 1.0e-05 	 & 1.0e-02 	 & 40 & 336 	 & +0.015 & +0.005 & -0.001 & +0.001 \\ 
- 1.0e-06 	 & 1.0e+00 	 & 40 & 261 	 & -0.007 & +0.000 & +0.002 & +0.002 \\ 
- 1.0e-06 	 & 1.0e-01 	 & 40 & 318 	 & +0.004 & +0.003 & +0.000 & +0.002 \\ 
  1.0e-06 	 & 1.0e-02 	 & 40 & 375 	 & +0.015 & +0.005 & -0.001 & +0.001 \\ 
 \end{tabular}}
+\label{TAB::double}
 \end{table}
@@
 \end{tabular}}
-\label{Tab::1}
+\label{Tab::Hole1}
 \end{table} 
@@
 \end{tabular}}
-\label{Tab::1}
+\label{Tab::Hole2}
 \end{table}

### 2018-10-10 tex/paper.tex
text added, real data not ready

@@
 Therefore, after each time step $dt$ in Eq\ref{Eq::PDE}, it was checked if the time step contained the next observation.
-If it did, then a linear interpolation of the current solution $u$ and previous solution $U_{prev}$ was used approximate the solution corresponding to $t_i$.
+If it did, then a linear interpolation of the current solution $U$ and previous solution $U(t-dt)$ was used approximate the solution corresponding to $t_i$.
 The linear interpolation was given as
 \begin{equation}
-u_{linear}(t) = \frac{\Delta t}{dt} U_{prev}(t) + \frac{dt - \Delta t }{dt} U(t), t \in \lbrace 
+U_{lin}(t) = \frac{\Delta t}{dt} U(t-dt) + \frac{dt - \Delta t }{dt} U(t), \quad t \in \lbrace t-dt, t \rbrace
 \end{equation}
-with $\Delta t$ is the difference between observation time and the time in the forward problem.
+with $\Delta t = t-t_i $
 
@@
 Furthermore, to obtain faster convergence in the optimization, the diffusion coefficients was scaled to have the same magnitude, i.e.
-$D_{\Omega_1}$ was scaled, so that $D_{\Omega_1} = D\sp {s}_{\Omega_1}100$.
+$D_{\Omega_1} = D\sp {s}_{\Omega_1}100$.
+T
+he noise susceptibility was also tested by adding an uniform distribution noise term to the observations.
+The noise term was constructed using numpy random and multiplied with a noise amplitude.
+The noise amplitudes were chosen to be $ 10\%, 100\%$ of the maximum initial boundary conditions, so that negative concentrations are avoided.
 
-The noise susceptibility was also tested by adding an uniform distribution noise term to the observations.
-The noise term was constructed using numpy random and multiplied with a noise amplitude.
-The noise amplitudes were chosen to be $ 10\%, 50\%, 100\%$ of the maximum initial boundary conditions, so that negative concentrations are avoided.
-
-The real data observations had observation times that had an unevenly distribution over 24 hours.
-Thus having  constant time between observations is not realistic.
-Therefore the number of observation and the unevenly distribution of them will be tested.
-To accurately depict the real data observations.
-
-The
+The real data observations had observation times that had an unevenly distribution over 24 hours. Thus having constant time between observations is not realistic.
 
@@
 \end{equation}
-The difference in $S_0$ between observation times were adjusted for in \cite{ringstad2018brain}.  
+The difference in $S_0$ between observation times were adjusted in \cite{ringstad2018brain}.  
 Thus we can express the $T_1$ change due to contrast as 
@@
 There are several forms of tissue damage, one is edema, which can be observed in the MRI due to a lower intensity in the white matter compared to healthy white matter tissue.
-This means that the damaged tissue also have different T1 relaxation times, which will give wrong estimation of tracer concentration.
+This means that the damaged tissue have a different T1 relaxation time, which will give a wrong estimate of tracer concentration.
 
-In \cite{XU2011827} the concentration was computed {\color{red} not used, due to calibration requirements. But could be used.}.
+The estimation of concentration require many parameters, most of these parameters are obtained from the MRI protocol, and the value for $r_1$ is found in the \cite{pmid16230904}.
 
-In [nicholsen ], it is shown that the macroscopic diffusion in the brain can be considered a hindered diffusion with an apparent diffusion coefficient.
-This means that the diffusion parameters in Eq\ref{Eq::PDE}....
-.
-The apparent diffusion coefficient  $D_{adc}$ is defined as
-\begin{equation}
-D = D \lambda\sp{2} fill in subscript,
-\end{equation} 
-with $\lambda$ defined as tourtosity of the brain and $D_{free}$ the free diffusion coefficients.  The tourtosity is a structural parameter, ...
+In \cite{sykova2008diffusion}, it is shown that the macroscopic diffusion in the brain can be considered a hindered diffusion with an apparent diffusion coefficient.
 
@@
 
-Thus the optimized parameters will be compared with the apparent diffusion coefficient obtained form DTI cite DTI. The DTI measure the apparent diffusion coefficient
+\subsection{DTI}
+The validation of the results from the MRI data can be done using diffusion tensor imaging (DTI).
+Diffusion tensor imaging is a MRI-sequence can be used to obtain the apparent diffusion coefficients of water in the brain.
+{\color{red} mer on DTI?
+}
 
-The Stokes-Einstein relation combined with correlation between weight and radius of particles can be used to estimate the diffusion coefficient for Gadovist (600 Da) \cite{VALENCIA2011129}.
-This gives a estimated free diffusion coefficient of
-$  25.72 e-5 \mathrm{mm\sp{2}/s}$.
+The Stokes-Einstein relation combined with th approximation between weight and radius of particles
+\begin{equation}
+D = \frac{k_B T}{ 6 \pi n r} \qquad
+M_w  = \frac{4}{3} \pi \rho r\sp{3}
+\end{equation}
+can be used to estimate the diffusion coefficient for Gadovist (600 Da). {\color{red} Trenger å verifiseres}
+
+\subsection*{MRI Data}
+\begin{figure}
+\centering
+\includegraphics[width=0.80\textwidth]{DTI-zoom.png} 
+\label{FIG::DTI} 
+\caption{The left panel show the anatomical map.
+The middle panel show the apparent diffusion coefficients (ADC) obtained from DTI.
+The right panel shows the computed fractional anisotropy (FA) from the DTI.}
+\end{figure}
 
@@
 }
-
-The gird
 
@@
 The magnitude order of the diffusion coefficient are chosen so that they resemble diffusion coefficient in csf, grey and white matter.
-The forward simulation gave a total of 120 possible observation time points.
+The manufactured forward computation gave a total of 120 possible observation time points.
 These points
-will be denoted as $\tau$.
+will be denoted as $t_i$.
 
-The mesh is patient-specific and was constructed by using the MRI of a patient diagnosed with iNPH.
+The mesh is patient-specific and was constructed by using the MRI of a patient diagnosed with idiopathic normal pressure hydrocephalus (iNPH).
 The software Freesurfer was used in segmentation and creating the polyhedral surfaces of the white and grey matter.
@@
 (BrainMesh code accessibility ?
-) CGAL[?] was used to combine the polyhedral surfaces and to construed the mesh.
-The computational requirement for the resulting mesh was significant, therefore a submesh was also constructed, see Fig.
-??.
+) CGAL \cite{cgal:rty-m3-18b} was used to combine the polyhedral surfaces and to construed the mesh.
+The computational requirement for the resulting mesh was significant, therefore two submesh was also constructed, see Fig.\ref{Fig::Mesh}.
 \begin{figure}
-\includegraphics[width=0.3\textwidth]{mesh-eps-converted-to.pdf} 
+\centering
+\includegraphics[scale=0.2]{mesh.png} 
 \label{figmesh} 
-\caption{Shows the mesh created from the baseline MR image with 3 domains. ( wrap ?? ) }
+\caption{A) Shows the mesh created from the baseline MR image with 3 domains. B) Shows the mesh created from the baseline MR image with 2 domains.  }
+\label{Fig::Mesh}
 \end{figure}
+The 3 domain mesh in Fig.\ref{Fig::Mesh} A, consists of 244318 tetrahedral cells and 22057 vertices, while the 2 domain mesh Fig.\ref{Fig::Mesh} B consists of 335589 tetrahedral cells and 73002 vertices.
 
 \section{Results}
-\begin{itemize}
-\item 2D experiments as have already been done (with and without noise/ with and without observations everywhere in time) 
-\item 2D experiments should highlight the impact of the regularization parameter wrt number of iterations and diffusion 
-coeff 
-\item 3D experiments based on data generated  
-\item 3D experiments based on real data (\comment{lars: we need to try testing this}) 
-\end{itemize}
 
-The relative error norm for a scalar is defined as 
+In presentation of the results, the relative error norm $||\cdot||_{RE}$ is defined as 
 \begin{equation}
@@
 \end{equation}
-with $X$ as an arbitrary scalar parameter.
+with $X$ as an arbitrary scalar parameter. For the boundary parameter $g$, the relative error norm is defined as 
+\begin{equation}
+|| g ||_{RE} = \frac{||g_{found} -g_{true}||_{L(\Omega_1)} }{ ||g_{true}||_{L(\Omega_1)} }
+\end{equation}
 
-The relative error norm for the boundary is defined as 
-\begin{equation}
-|| g ||_{RE(\Omega_1)} = \frac{||g_{found} -g_{true}||_{L(\Omega_1)} }{ ||g_{true}|| }
-\end{equation}
-with $X$ as a vector.
 \subsection{The relaxation parameters}
-
 The robustness of the objective functional defined in Eq.\ref{Eq::F} is dependent on the regularization parameters $\alpha$ and $\beta$.
 Therefore it is important to select regularization parameter values to ensure effective and accurate convergence.
-The evaluation of different regularization parameters was done by solving the optimization  with  different values of $\alpha$ and $\beta$ and compare the resulting states and the manufactured solution.
-The observation times were selected with $t_i \in  \rbrace 2.4, 4.8, 7.2, 9.6, 12.0, 14.4, 16.8, 19.2, 21.6, 24.0 \lbrace$, and the number of time-steps in the forward problem was set to $k= 10$.
+The evaluation of different regularization parameters was done by solving the optimization with different values of $\alpha$ and $\beta$ and compare the controls with the manufactured solution.
+The observation times were selected with $t_i \in  \rbrace$ 2.4, 4.8, 7.2, 9.6, 12.0, 14.4, 16.8, 19.2, 21.6, 24.0 $\lbrace$, and the number of time-steps in the forward problem was set to $k= 10$.
 
@@
 \subsection{The noise susceptibility}
-
 The MRI data contains noise, hence an investigation to the noise susceptibility is needed.
-This is done by adding uniform noise in the range $\brace -n_{amp} , n_{amp} \rbrace $, with $n_{amp}$ defined as noise amplitude, to the manufactured observations.
+This is done by adding uniform noise in the range $\lbrace -n_{amp} , n_{amp} \rbrace $, with $n_{amp}$ defined as noise amplitude, to the manufactured observations.
 Then the optimization was solved by varying the regularization parameters $\alpha$ and $\beta$.
@@
 \subsection{The number of timessteps}
+The PDE uses backward Euler, which is a linear approximation in time.
+This means that the increasing the number of timesteps will allow for a better temporal approximation.
+However, this will also increase the computational cost for each iteration of the L-BFGS-B algorithm.
+Thus finding the number of timesteps for an effective convergence can help for larger meshes.
+The computation vary the timesteps with 10, 20 and 40 timesteps.
+Additionally, the computation will use a few variations of the regularization parameters that gives small relative errors.
 
-The PDE uses backward Euler, which is a linear approximation in time.
-This means that the increasing the number of timesteps will allow for a better temporal approximation, but will also increase the computational cost.
-Thus finding the best number of timesteps can be beneficial.
-
-In Tab.\ref{Tab::1}, we can see that the
+This gave the values presented in Tab.\ref{TAB::timesteps}, and can be seen that increase in the number of timesteps causes a decrease in the relative error.
 
 \subsection{The number of observations}
-
-The dependency on observations is relevant, since the number of observations of MRI data is limited.
+The dependency on observations is relevant, since the number of observations of the MRI data is limited.
 This was investigated by changing the number of observations, and examine the resulting states.
@@
 
-The results are shown in Tab.??, Tab.\ref{TAB::double} and Tab.\ref{TAB::half}. 
+The results are shown in Tab.\ref{TAB::timesteps}, Tab.\ref{TAB::double} and Tab.\ref{TAB::half}.
+In the case of 10 observations, the number of timesteps showed a decrease in the relative error.
+Similar effects was observed for 5 and 20 observations.
+However, the variation of observations did not show a consistent decrease in error.
+The variation in the relative error show sign of oscillations.
+
 \subsection{Sparse observations}
+The MRI data contains observations after the injection of CSF tracer.
+These observation are unevenly distributed in time resulting in large time intervals with no observations.
+Therefore the effect of these temporal gaps in the observations will be evaluated.
+This was done by selecting the observation times as follows  $t_i = \lbrace$0.8, 1.0, 1.2, 1.8, 2.4, 3.6, 5.4, 7.6, 24.0$\rbrace$.
+The regularization parameters was selected, so that the error would be minimized,and noise was also added.
 
-The MRI data contains observations after the injection of CSF tracer.
-These observation are unevenly distributed in time, and thus there are large time intervals with no observations.
-Thus the effect of this temporal gap in the observations will be evaluated.
-This is done by selecting the observation times as follows  $t_i = [0.8, 1.0, 1.2, 1.8, 2.4, 3.6, 5.4, 7.6, 24.0]$.
-Furthermore, the optimal regularization parameters and noise susceptibility was also checked.
+The results are shown in Tab.\ref{Tab::Hole1} and Tab\ref{Tab::Hole2}, and it can be observed that the addition of noise caused $\beta=1.0$ to converge the same.
+Comparing the values in Tab\ref{Tab::Hole1} and Tab.\ref{TAB::timesteps}, showed that the relative error increased.
 
 \subsection{MRI Data} 
-
-The MRI data consisted of the observations at times $t_i \in \lbrace 0.00, 0.16, 0.39, 0.55, 0.77, 2.09, 6.05, 24.06, 47.84, 698.02 \rbrace (hours)$ and $t_i=0.00$ was the observation 1-2 hours after the tracer was injected.
-There was no signifcant visible change in the tracer between the observations at $\lbrace 0.16, 0.39, 0.55, 0.77 \rbrace$.
+The MRI data consisted of the observations at times $t_i \in \lbrace$ 0.00, 0.16, 0.39, 0.55, 0.77, 2.09, 6.05, 24.06, 47.84, 698.02 $\rbrace (hours)$ with the time $t_i=0.00$ as the observation 1-2 hours after the tracer was injected.
+There was no significant visible change in the tracer between the observations at $\lbrace 0.00 0.16, 0.39, 0.55, 0.77 \rbrace$.
 This prompted the focus on the observation times  $0.00 2.09, 6.05, 24.06, 47.84$, which can be seen in Fig.??.
 
-The time range for the selected observations
+The estimation of tracer concentration proved difficult in the CSF compartment.
+Therefore the 2 domain mesh, shown in Fig.\ref{figmesh} was used in the computation.
+Furthermore, bounds were added to the L-BFGS-B algorithm to ensure non-negative boundary controls.
+The resulting states can be seen in Fig.
+??
+and the relative error of control values are displayed in Tab.??
+.
+
+\subsection*{DTI comparison}
+The median diffusion coefficient in the DTI was estimated to be  respectively in white and grey matter to be 8.7e-4 $\mathrm{mm\sp{2}/s}$ and  1.0e-3 $\mathrm{mm\sp{2}/s}$.
+This gives a related diffusion coefficient of tracer to be ??
+and  ??.
 
 \section{Discussion}
+
+\subsection{Manufactures Solution}
+The results from the manufactured solutions showed a robust method to compute diffusion coefficients.
+
+\subsection{Anisotropy}
+The computational model does not take into account the anisotropy in the brain, see Fig\ref{FIG::DTI}.
+
+The region with great FA In Fig\ref{FIG::DTI},  does not show mush concentration of csf.
+Thus the anisotropy does not seem to be a significant factor in the computation.
+This is due to the fact that the optimization require
+
+\subsection{Real Data}
+
+The comparison with DTI use Stokes-Einstein to estimate the measured diffusion coefficient, this will give some error. Furthermore, comparison with molecules of size 600 Da shows
+
+The limited number observations makes it difficult to measure the grey matter diffusion coefficient, since domain depth is about 5 mm {\color{red} cortex thickness}.
+
+Furthermore, the grey domain is more affected by the boundary control. This means that the 
+diffusion paramet
+
+The computational have 2 diffusion coefficient controls, while the DTI values represent a range of measurements,
+
+\section{Sleep}
+There have been reports of increase clearance in rodents that are sleeping.
+This effect can only by a change in the tortuosity since the properties of the molecules do not change.
+This indicates that the model should take into account changes in the apparent diffusion coefficient.
+Thus making the control parameters time dependent.
 
@@
 \caption{The upper row shows the manufactured observation, A ) Shows the manufactured observation at time-point 24 with no noise added.
-B) Shows the manufactured observation at time-point 24 with an noise amplitude of 0.15 {\color{red} explain noise amplitude}.
+B) Shows the manufactured observation at time-point 24 with an noise amplitude of 0.15.
 C)Shows the manufactures observation at time-point 24 with noise amplitude of 0.3.
 The lower row shows the results with optimized parameter obtained with $alpha=0.0001$, $\beta=1.0$ and $k=27$.
-D) Shows the  .
-E)  Shows the  F)  Shows the  }
+D) Shows the resulting state given the observation in A.
+E)  Shows the resulting state given the observation in B .F) Shows the resulting state given the observation in C.
+}
 \end{figure}
@@
 The lower row shows the results with optimized parameter obtained with $alpha=0.0001$, $\beta=1.0$ and $k=27$.
-D) Shows the  .
-E)  Shows the  F)  Shows the  }
+D) Shows the resulting state given the observation in A.
+E)  Shows the resulting state given the observation in B .F) Shows the resulting state given the observation in C.
+}
 \end{figure}
@@
 \resizebox{0.9\textwidth}{!}{\begin{tabular}{*{8}c}
-$\alpha$ & $\beta$ & k  & iter & $ ||D_{\Omega_1}||$ & $ ||D_{\Omega_2}|| $ & $||D_{\Omega_3}||$ & $||g||$ \\
+$\alpha$ & $\beta$ & k  & iter & $ ||D_{\Omega_1}||_{RE}$ & $ ||D_{\Omega_2}||_{RE} $ & $||D_{\Omega_3}||_{RE}$ & $||g||_{RE}$ \\
 \hline
@@
 \resizebox{0.8\textwidth}{!}{\begin{tabular}{*{8}c}
-$\alpha$ & $\beta$ & k  & iter & $ D_{\Omega_1} $ & $ D_{\Omega_2} $ & $D_{\Omega_3} $ & wrong $g$ \\
+$\alpha$ & $\beta$ & k  & iter & $ ||D_{\Omega_1}||_{RE} $ & $||D_{\Omega_2}||_{RE}$ & $||D_{\Omega_3}||_{RE}$ & $||g||_{RE}$\\
 \hline
@@
 \resizebox{0.8\textwidth}{!}{\begin{tabular}{*{8}c}
-$\alpha$ & $\beta$ & k  & iter & $ D_{\Omega_1} $ & $ D_{\Omega_2} $ & $D_{\Omega_3} $ & $g$ \\
+$\alpha$ & $\beta$ & k  & iter & $ ||D_{\Omega_1}||_{RE}$ & $||D_{\Omega_2}||_{RE} $ & $||D_{\Omega_3}||_{RE} $ & $||g||_{RE}$ \\
 \hline
@@
 \centering
-\caption{ $\tau = [4.8, 9.6, 14.4, 19.2, 24.0]$}
+\caption{ Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$, the resulting number of iterations, the relative error of the estimated diffusion coefficients and the relative error for $g$.
+}
 \resizebox{\textwidth}{!}{\begin{tabular}{*{8}c}
-$\alpha$ & $\beta$ & k & iter & $ D_{\Omega_1} = 1000$ & $ D_{\Omega_2} = 4.0 $ & $D_{\Omega_3} = 8.0 $ \\
+$\alpha$ & $\beta$ & k & iter & $ ||D_{\Omega_1}||_{RE}$& $||D_{\Omega_2}||_{RE} $ & $||D_{\Omega_3}||_{RE} $&$||g||_{RE}$ \\
+\hline
+ 1.0e-04 	 & 1.0e+00 	 & 20 & 187 	 & -0.007 & +0.004 & +0.013 & +0.008 \\ 
+ 1.0e-04 	 & 1.0e+00 	 & 40 & 257 	 & -0.019 & -0.019 & +0.005 & +0.007 \\ 
+ %1.0e-04 	 & 1.0e-01 	 & 20 & 367 	 & +0.028 & +0.010 & +0.008 & +0.007 \\
+ %1.0e-04 	 & 1.0e-01 	 & 40 & 422 	 & +0.001 & -0.007 & +0.004 & +0.005 \\  
+ 1.0e-04 	 & 1.0e-02 	 & 20 & 258 	 & +0.068 & +0.023 & +0.005 & +0.006 \\ 
+ 1.0e-04 	 & 1.0e-02 	 & 40 & 339 	 & +0.004 & +0.002 & +0.002 & +0.003 \\   
+ 1.0e-05 	 & 1.0e+00 	 & 20 & 237 	 & -0.006 & +0.004 & +0.013 & +0.008 \\ 
+ 1.0e-05 	 & 1.0e+00 	 & 40 & 358 	 & -0.018 & -0.019 & +0.005 & +0.007 \\  
+ %1.0e-05 	 & 1.0e-01 	 & 20 & 290 	 & +0.026 & +0.010 & +0.008 & +0.007 \\
+ %1.0e-05 	 & 1.0e-01 	 & 40 & 419 	 & +0.001 & -0.007 & +0.004 & +0.005 \\    
+ 1.0e-05 	 & 1.0e-02 	 & 20 & 316 	 & +0.071 & +0.025 & +0.005 & +0.007 \\ 
+ 1.0e-05 	 & 1.0e-02 	 & 40 & 401 	 & +0.004 & +0.003 & +0.002 & +0.004 \\  
+ 1.0e-06 	 & 1.0e+00 	 & 20 & 219 	 & -0.007 & +0.004 & +0.013 & +0.008 \\ 
+ 1.0e-06 	 & 1.0e+00 	 & 40 & 240 	 & -0.020 & -0.019 & +0.005 & +0.007 \\ 
+ %1.0e-06 	 & 1.0e-01 	 & 20 & 250 	 & +0.027 & +0.010 & +0.008 & +0.007 \\ 
+ %1.0e-06 	 & 1.0e-01 	 & 40 & 365 	 & +0.000 & -0.007 & +0.004 & +0.005 \\ 
+ 1.0e-06 	 & 1.0e-02 	 & 20 & 379 	 & +0.070 & +0.025 & +0.005 & +0.007 \\ 
+ 1.0e-06 	 & 1.0e-02 	 & 40 & 386 	 & +0.004 & +0.003 & +0.002 & +0.004 \\ 
+\end{tabular}}
+\label{TAB::timesteps}
+\end{table}
+
+\begin{table}
+\centering
+\caption{ Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$, the resulting number of iterations, the relative error of the estimated diffusion coefficients and the relative error for $g$.
+The observation times were set $t_i \in \lbrace 4.8, 9.6, 14.4, 19.2, 24.0 \rbrace $.
+}
+\resizebox{\textwidth}{!}{\begin{tabular}{*{8}c}
+$\alpha$ & $\beta$ & k & iter & $ ||D_{\Omega_1}||_{RE}$& $||D_{\Omega_2}||_{RE} $ & $||D_{\Omega_3}||_{RE} $&$||g||_{RE}$ \\
 \hline
@@
 \centering
-\caption{ Shows the $\tau = [1.2, 2.4, 3.6, 4.8, 6.0, 7.2, 8.4, 9.6, 10.8, 12.0, 13.2, 14.4, 15.6, 16.8, 17.0, 19.2, 20.4, 21.6, 22.8, 24.0] $}
+\caption{ Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$, the resulting number of iterations, the relative error of the estimated diffusion coefficients and the relative error for $g$.
+The observation times were $t_i \in \lbrace 1.2, 2.4, 3.6, 4.8, 6.0, 7.2, 8.4, 9.6, 10.8, 12.0, 13.2, 14.4, 15.6, 16.8, 17.0, 19.2, 20.4, 21.6, 22.8, 24.0\rbrace $.}
 \resizebox{\textwidth}{!}{\begin{tabular}{*{8}c}
-$\alpha$ & $\beta$ & k & iter & $ D_{\Omega_1} = 1000$ & $ D_{\Omega_2} = 4.0 $ & $D_{\Omega_3} = 8.0 $ \\
+$\alpha$ & $\beta$ & k & iter & $ ||D_{\Omega_1}||_{RE}$ & $ ||D_{\Omega_2}||_{RE}$ & $||D_{\Omega_3}||_{RE} $ & $||g||_{RE}$ \\
 \hline
@@
 \centering
-\caption{$\tau = [0.8, 1.0, 1.2, 1.8, 2.4, 3.6, 5.4, 7.6, 24.0] $ noise 0.0}
+\caption{Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$, the resulting number of iterations, the relative error of the estimated diffusion coefficients and the relative error for $g$.
+The observation times were set $t_i \in \lbrace 0.8, 1.0, 1.2, 1.8, 2.4, 3.6, 5.4, 7.6, 24.0\rbrace $, and zero noise.}
 \resizebox{\textwidth}{!}{\begin{tabular}{*{8}c}
-$\alpha$ & $\beta$ & k & iter & $ D_{\Omega_1} = 1000$ & $ D_{\Omega_2} = 4.0 $ & $D_{\Omega_3} = 8.0 $ \\
- 1.0e-04 	 & 1.0e+00 	 & 40 & 517 	 & -0.034 & -0.006 & -0.022 & +0.058 \\ 
- 1.0e-04 	 & 1.0e-01 	 & 40 & 660 	 & -0.045 & -0.013 & -0.024 & +0.052 \\ 
- 1.0e-04 	 & 1.0e-02 	 & 40 & 283 	 & -0.059 & -0.020 & -0.027 & +0.331 \\ 
- 1.0e-05 	 & 1.0e+00 	 & 40 & 588 	 & -0.034 & -0.006 & -0.022 & +0.060 \\ 
- 1.0e-05 	 & 1.0e-01 	 & 40 & 686 	 & -0.046 & -0.013 & -0.024 & +0.067 \\ 
- 1.0e-05 	 & 1.0e-02 	 & 40 & 400 	 & -0.059 & -0.020 & -0.027 & +0.260 \\ 
- 1.0e-06 	 & 1.0e+00 	 & 40 & 618 	 & -0.034 & -0.006 & -0.022 & +0.058 \\ 
- 1.0e-06 	 & 1.0e-01 	 & 40 & 826 	 & -0.046 & -0.013 & -0.024 & +0.070 \\ 
- 1.0e-06 	 & 1.0e-02 	 & 40 & 632 	 & -0.058 & -0.020 & -0.027 & +0.183 \\
+$\alpha$ & $\beta$ & k & iter &  $ ||D_{\Omega_1}||_{RE}$ & $ ||D_{\Omega_2}||_{RE}$ & $||D_{\Omega_3}||_{RE} $ & $||g||_{RE}$\\
+ 1.0e-04 	 & 1.0e+00 	 & 40 & 453 	 & -0.003 & -0.017 & -0.021 & +0.053 \\
+ 1.0e-04 	 & 1.0e-01 	 & 40 & 491 	 & -0.033 & -0.015 & -0.024 & +0.049 \\ 
+ 1.0e-04 	 & 1.0e-02 	 & 40 & 611 	 & -0.051 & -0.020 & -0.027 & +0.096 \\ 
+ 1.0e-05 	 & 1.0e+00 	 & 40 & 561 	 & -0.004 & -0.016 & -0.021 & +0.053 \\ 
+ 1.0e-05 	 & 1.0e-01 	 & 40 & 688 	 & -0.033 & -0.015 & -0.025 & +0.045 \\ 
+? 1.0e-05 	 & 1.0e-02 	 & 40 & 566 	 & -0.053 & -0.020 & -0.027 & +0.098 \\
+ 1.0e-06 	 & 1.0e+00 	 & 40 & 517 	 & -0.005 & -0.016 & -0.021 & +0.053 \\ 
+ 1.0e-06 	 & 1.0e-01 	 & 40 & 619 	 & -0.033 & -0.015 & -0.025 & +0.044 \\  
+ 1.0e-06 	 & 1.0e-02 	 & 40 & 691 	 & -0.051 & -0.020 & -0.027 & +0.073 \\
 
@@
 \centering
-\caption{$\tau = [0.8, 1.0, 1.2, 1.8, 2.4, 3.6, 5.4, 7.6, 24.0] $ noise 0.3}
+\caption{Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$, the resulting number of iterations, the relative error of the estimated diffusion coefficients and the relative error for $g$.
+The observation times were set $t_i \in \lbrace 0.8, 1.0, 1.2, 1.8, 2.4, 3.6, 5.4, 7.6, 24.0\rbrace $, and with a noise amplitude of 0.3.}
 \resizebox{\textwidth}{!}{\begin{tabular}{*{8}c}
-$\alpha$ & $\beta$ & k & iter & $ D_{\Omega_1} = 1000$ & $ D_{\Omega_2} = 4.0 $ & $D_{\Omega_3} = 8.0 $ \\
+$\alpha$ & $\beta$ & k & iter & $ ||D_{\Omega_1}||_{RE}$ & $  ||D_{\Omega_2}||_{RE}$ & $ ||D_{\Omega_3}||_{RE}$  &$||g||_{RE}$\\
 \hline
- 1.0e-04 	 & 1.0e+00 	 & 40 & 519 	 & +0.003 & +0.029 & +0.035 & +0.067 \\ 
- 1.0e-04 	 & 1.0e-01 	 & 40 & 653 	 & -0.096 & +0.015 & +0.016 & +0.070 \\ 
-\rowcolor{red}  1.0e-04 	 & 1.0e-02 	 & 40 & 575 	 & -0.050 & -0.001 & +0.057 & +0.281 \\ 
- 1.0e-05 	 & 1.0e+00 	 & 40 & 585 	 & -0.050 & -0.007 & +0.017 & +0.068 \\ 
- 1.0e-05 	 & 1.0e-01 	 & 40 & 871 	 & -0.023 & +0.024 & +0.019 & +0.079 \\ 
-\rowcolor{red}  1.0e-05 	 & 1.0e-02 	 & 40 & 466 	 & -0.045 & +0.042 & +0.019 & +0.281 \\ 
- 1.0e-06 	 & 1.0e+00 	 & 40 & 584 	 & -0.045 & +0.019 & +0.006 & +0.071 \\ 
- 1.0e-06 	 & 1.0e-01 	 & 40 & 546 	 & +0.005 & +0.019 & -0.001 & +0.079 \\ 
-\rowcolor{red}  1.0e-06 	 & 1.0e-02 	 & 40 & 648 	 & -0.074 & -0.008 & +0.041 & +0.227 \\ 
+ %1.0e-04 	 & 1.0e+00 	 & 40 & 519 	 & +0.003 & +0.029 & +0.035 & +0.067 \\ 
+% 1.0e-04 	 & 1.0e-01 	 & 40 & 653 	 & -0.096 & +0.015 & +0.016 & +0.070 \\ 
+%\rowcolor{red}  1.0e-04 	 & 1.0e-02 	 & 40 & 575 	 & -0.050 & -0.001 & +0.057 & +0.281 \\ 
+% 1.0e-05 	 & 1.0e+00 	 & 40 & 585 	 & -0.050 & -0.007 & +0.017 & +0.068 \\ 
+% 1.0e-05 	 & 1.0e-01 	 & 40 & 871 	 & -0.023 & +0.024 & +0.019 & +0.079 \\ 
+%\rowcolor{red}  1.0e-05 	 & 1.0e-02 	 & 40 & 466 	 & -0.045 & +0.042 & +0.019 & +0.281 \\ 
+% 1.0e-06 	 & 1.0e+00 	 & 40 & 584 	 & -0.045 & +0.019 & +0.006 & +0.071 \\ 
+% 1.0e-06 	 & 1.0e-01 	 & 40 & 546 	 & +0.005 & +0.019 & -0.001 & +0.079 \\ 
+%\rowcolor{red}  1.0e-06 	 & 1.0e-02 	 & 40 & 648 	 & -0.074 & -0.008 & +0.041 & +0.227 \\
+
+ 1.0e-04 	 & 1.0e+00 	 & 40 & 519 	 & +0.066 & -0.025 & -0.002 & +0.063 \\ 
+ 1.0e-04 	 & 1.0e-01 	 & 40 & 853 	 & -0.047 & -0.013 & -0.001 & +0.078 \\ 
+ 1.0e-04 	 & 1.0e-02 	 & 40 & -	 & -0.062 & -0.005 & -0.018 & +0.223 \\ 
+ 1.0e-05 	 & 1.0e+00 	 & 40 & 455 	 & -0.038 & -0.006 & +0.012 & +0.063 \\ 
+ 1.0e-05 	 & 1.0e-01 	 & 40 & 801 	 & -0.016 & +0.002 & +0.040 & +0.074 \\ 
+ 1.0e-05 	 & 1.0e-02 	 & 40 & 877 	 & -0.060 & +0.017 & +0.010 & +0.198 \\ 
+ 1.0e-06 	 & 1.0e+00 	 & 40 & 575 	 & -0.030 & +0.001 & +0.015 & +0.062 \\ 
+ 1.0e-06 	 & 1.0e-01 	 & 40 & 848 	 & +0.002 & +0.005 & +0.023 & +0.071 \\ 
+ 1.0e-06 	 & 1.0e-02 	 & 40 & -	 & +0.018 & +0.013 & -0.035 & +0.234 \\ 
 \end{tabular}}
@@
 \end{table}
-
-In Tab.
-??
-we observe that the optimal relaxation parameters are found for $\alpha := \lbrace 1.e-4 1.e-5 1.e-6 \rbrace$ and $\beta := \lbrace 1.0 0.1 0.01 \rbrace$.
-This will be the region of interest for the relaxation parameters.
-
-The dependency on number of timesteps can be seen in Fig.??.
 

### 2018-10-11 tex/paper.tex
more text

@@
 \usepackage{geometry}
+\usepackage{subcaption}
 \title{Assessing glymphatic transport velocities by adjoint methods}
@@
 The code used the FEniCS project to solve the PDE, using backwards Euler time discretization and first order continuous Galerkin finite elements.
+The linear problem was solved using GMRES, and bilinear matrix stored in the solver.
+{\color{red} why not amg}
 The module dolfin adjoint ~\cite{farrell2013automated} \kam{correct ref?} was used to solve the PDE constrained optimization problem with the L-BFGS-B algorithm in the python module scipy.
+The convergence criteria for the minimization was set so that $L\sp{inf}$ norm of the project gradient was less than $gtol =1.0e-1$.
 
@@
 $D_{\Omega_1} = D\sp {s}_{\Omega_1}100$.
-T
-he noise susceptibility was also tested by adding an uniform distribution noise term to the observations.
-The noise term was constructed using numpy random and multiplied with a noise amplitude.
-The noise amplitudes were chosen to be $ 10\%, 100\%$ of the maximum initial boundary conditions, so that negative concentrations are avoided.
 
-The real data observations had observation times that had an unevenly distribution over 24 hours. Thus having constant time between observations is not realistic.
+The noise susceptibility was tested by adding an uniform distribution noise term to the observations.
+The noise term was constructed using numpy.random and adjusted so that noise range becomes $\lbrace -n_{amp} , n_{amp} \rbrace $, with $n_{amp}$ defined as noise amplitude.
 
@@
 \begin{equation}
-\frac{1}{T_{1}\sp{c}} = \frac{1}{T_{1}\sp{0}} + r_{1}*C .
+\frac{1}{T_{1}\sp{c}} = \frac{1}{T_{1}\sp{0}} + r_{1}C .
 \label{EQ::contrast}
@@
 \alpha &= \cos ( \theta ) \\
-\beta  &= e\sp{- \sp{T_b}/_{T_1}\sp{0} } \\
-\delta &= e\sp{- \sp{T_a}/_{T_1}\sp{0} } \\
-\gamma &= e\sp{- \sp{T_w}/_{T_1}\sp{0} } \\
-\rho   &= e\sp{- \sp{TR}/_{T_1}\sp{0} }  \\
+\beta  &= e\sp{- \sp{T_b}/_{T_1\sp{0}} } \\
+\delta &= e\sp{- \sp{T_a}/_{T_1\sp{0}} } \\
+\gamma &= e\sp{- \sp{T_w}/_{T_1\sp{0}} } \\
+\rho   &= e\sp{- \sp{TR}/_{T_1\sp{0}}}  \\
 T_w    &= TR - T_a -T_b(m-1)       .\\
@@
 \end{equation}
-The difference in $S_0$ between observation times were adjusted in \cite{ringstad2018brain}.  
+The difference in $S_0$ between observation times were adjusted in \cite{eidevalnes}.  
 Thus we can express the $T_1$ change due to contrast as 
@@
 This makes it possible to  take into account patients specific characteristic, such as tissue damage.
-There are several forms of tissue damage, one is edema, which can be observed in the MRI due to a lower intensity in the white matter compared to healthy white matter tissue.
-This means that the damaged tissue have a different T1 relaxation time, which will give a wrong estimate of tracer concentration.
+There are several forms of tissue damage, which can be observed in the MRI due to a lower intensity in the white matter compared to healthy white matter tissue.
+This means that the damaged tissue have a different T1 relaxation time.
 
-The estimation of concentration require many parameters, most of these parameters are obtained from the MRI protocol, and the value for $r_1$ is found in the \cite{pmid16230904}.
+The estimation of the tracer concentration was precomputed and used the parameters obtained from the T1 map, MPRAGE MRI protocol \cite{eidevalnes} and the value for $r_1$ found in \cite{pmid16230904}.
+In the computation, the function $f(T_1)$ was computed for $ T_1\in \lbrace 200, 4000 \rbrace$ creating a lookup table.
+The lookup table was utilized with the baseline intensity increase to estimate $T_1\sp{c}$, and then the concentration was computed using Eq.\ref{EQ::contrast}.
 
-In \cite{sykova2008diffusion}, it is shown that the macroscopic diffusion in the brain can be considered a hindered diffusion with an apparent diffusion coefficient.
+In \cite{sykova2008diffusion}, it was shown that the macroscopic diffusion in the brain can be considered a hindered diffusion with an apparent diffusion coefficient.
+Thus the computed diffusion coefficients will correspond to the apparent diffusion coefficient.
 
-In the acquired data, the MPRAGE had a high signal to noise ratio and the T1 mapping had low signal in the CSF.
+In the acquired data, the MPRAGE had a high signal to noise ratio and the T1 map had low signal in the CSF.
 This made it difficult to estimate the concentration in the CSF compartment.
 Thus an additional mesh without the CSF compartment was constructed, see Fig.
-??.
+\ref{figmesh}.
 
@@
 The validation of the results from the MRI data can be done using diffusion tensor imaging (DTI).
-Diffusion tensor imaging is a MRI-sequence can be used to obtain the apparent diffusion coefficients of water in the brain.
+Diffusion tensor imaging is a MRI-sequence that is used to obtain the apparent diffusion coefficients of water in the brain.
 {\color{red} mer on DTI?
@@
 
-The Stokes-Einstein relation combined with th approximation between weight and radius of particles
+The diffusivity of the Gadovist (600 Da) is currently not known {\colro{red} Geir vet dere?}, thus the diffusion of (Navn Gd-DPTA (550 Da)  will be used as reference.
+The free diffusion coefficient for Gd-DPTA  3.8e-5$\mathrm{mm\sp{2}/s}$ , and obtained from [cite].
+{\color{red} discussion om hvorfor eller nevne Stoke Einstein her?}
+
+The fractional anisotropy is defined as 
 \begin{equation}
-D = \frac{k_B T}{ 6 \pi n r} \qquad
-M_w  = \frac{4}{3} \pi \rho r\sp{3}
+FA\sp{2} = \frac{ 3(\lambda_1 - MD )\sp{2} +(\lambda_2 - MD )\sp{2} +(\lambda_3 - MD )\sp{2}}{2\lambda\sp{2}_1 + \lambda\sp{2}_2  +\lambda\sp{2}_3 },
 \end{equation}
-can be used to estimate the diffusion coefficient for Gadovist (600 Da). {\color{red} Trenger å verifiseres}
-
-\subsection*{MRI Data}
+with the mean diffusivity $MD$ defined as 
+\begin{equation}
+MD = \frac{\lambda_1 +\lambda_2 +\lambda_3 }{3}.
+\end{equation}
+In these equations $\lambda_i$ denotes the eigenvalues of the diffusion tensor.
 \begin{figure}
@@
 
-The mesh is patient-specific and was constructed by using the MRI of a patient diagnosed with idiopathic normal pressure hydrocephalus (iNPH).
+The mesh construction was patient-specific and was constructed by using the MRI of a patient diagnosed with idiopathic normal pressure hydrocephalus (iNPH).
 The software Freesurfer was used in segmentation and creating the polyhedral surfaces of the white and grey matter.
 Then the use of T2 weighted MRI was used to segment the csf compartment surrounding the cerebral.
-(BrainMesh code accessibility ?
-) CGAL \cite{cgal:rty-m3-18b} was used to combine the polyhedral surfaces and to construed the mesh.
+(BrainMesh code accessibility {\color{red} not fully tested}) CGAL \cite{cgal:rty-m3-18b} was used to combine the polyhedral surfaces and to construed the mesh.
 The computational requirement for the resulting mesh was significant, therefore two submesh was also constructed, see Fig.\ref{Fig::Mesh}.
@@
 \begin{equation}
-|| X ||_{RE} = \frac{X_{found} -X_{true} }{ X_true }
+|| X ||_{RE} = \frac{X_{found} -X_{true} }{ X_{true} }
 \end{equation}
-with $X$ as an arbitrary scalar parameter. For the boundary parameter $g$, the relative error norm is defined as 
+with $X$ as an arbitrary scalar control parameter. For the boundary parameter $g$, the relative error norm is defined as 
 \begin{equation}
-|| g ||_{RE} = \frac{||g_{found} -g_{true}||_{L(\Omega_1)} }{ ||g_{true}||_{L(\Omega_1)} }
+|| g ||_{RE} = \frac{ \sum\limits_t\sp{k}||| g_{found}(t) -g_{true}(t)||_{L(\Omega_1)} }{  \sum\limits_t\sp{k}||g_{true}(t)||_{L(\Omega_1)} }
 \end{equation}
+In the case that the minimization algorithm fails to converge within 1000 iteration will be indicated by a hyphen.
 
@@
 The robustness of the objective functional defined in Eq.\ref{Eq::F} is dependent on the regularization parameters $\alpha$ and $\beta$.
-Therefore it is important to select regularization parameter values to ensure effective and accurate convergence.
+Therefore it is important to select regularization parameter values that ensures an effective and accurate convergence.
 The evaluation of different regularization parameters was done by solving the optimization with different values of $\alpha$ and $\beta$ and compare the controls with the manufactured solution.
-The observation times were selected with $t_i \in  \rbrace$ 2.4, 4.8, 7.2, 9.6, 12.0, 14.4, 16.8, 19.2, 21.6, 24.0 $\lbrace$, and the number of time-steps in the forward problem was set to $k= 10$.
+The observation times were selected with $t_i \in  \lbrace$ 2.4, 4.8, 7.2, 9.6, 12.0, 14.4, 16.8, 19.2, 21.6, 24.0 $\rbrace$, and the number of time-steps in the forward problem was set to $k= 10$.
 
 The results are shown in Tab.\ref{Tab::1} together with the number of iteration used to reach the convergence criteria.
-It can be observed for $\alpha= 1.0$ that there is a significant relative error for $D_{\Omega_1}$.
-The other control parameters also showed an increased error compared to other values of $\alpha$.
-The remaining values of the regularization parameters give small relative error.
+For $\alpha= 1.0$, it can be observed that there is a significant relative error for $D_{\Omega_1}$.
+The other control parameters also show an increased relative error when compared to other values of $\alpha$.
 
@@
 The MRI data contains noise, hence an investigation to the noise susceptibility is needed.
-This is done by adding uniform noise in the range $\lbrace -n_{amp} , n_{amp} \rbrace $, with $n_{amp}$ defined as noise amplitude, to the manufactured observations.
+This was done by adding uniform noise in the range $\lbrace -n_{amp} , n_{amp} \rbrace $, with $n_{amp}$ defined as noise amplitude, to the manufactured observations.
 Then the optimization was solved by varying the regularization parameters $\alpha$ and $\beta$.
@@
 However, the variation of observations did not show a consistent decrease in error.
-The variation in the relative error show sign of oscillations.
+And the variation in the relative error indicates oscillations in the convergence.
 
@@
 Therefore the 2 domain mesh, shown in Fig.\ref{figmesh} was used in the computation.
-Furthermore, bounds were added to the L-BFGS-B algorithm to ensure non-negative boundary controls.
+Furthermore, bounds were added to the L-BFGS-B algorithm to ensure non-negative boundary controls and the convergence criteria was adjusted to $gtol=6.0e-1$.
 The resulting states can be seen in Fig.
@@
 The median diffusion coefficient in the DTI was estimated to be respectively in white and grey matter to be 8.7e-4 $\mathrm{mm\sp{2}/s}$ and  1.0e-3 $\mathrm{mm\sp{2}/s}$.
-This gives a related diffusion coefficient of tracer to be ??
-and  ??.
+This is an increase from the reported values in [insert citation] of XX and XX.
 
@@
 \subsection{Anisotropy}
-The computational model does not take into account the anisotropy in the brain, see Fig\ref{FIG::DTI}.
+The computational model assumes isotropic diffusivity, but the anisotropy in the white matter is well documented, as shown in Fig\ref{FIG::DTI}.
 
-The region with great FA In Fig\ref{FIG::DTI},  does not show mush concentration of csf.
-Thus the anisotropy does not seem to be a significant factor in the computation.
-This is due to the fact that the optimization require
+The anisotropy can be seen by comparing the observations and the states after 48 hours, see Fig ??.
+This observation is after 48 hours, and the amount of tracer inside the anisotropic region is negligible.
+Therefore it would seem that the anisotropy do not have direct impact on the computations, since the computation can asses a static environment.
+
+A more important factor is that of tissue damage, which may causes higher diffusivity.
+In Fig.\ref{FIG::DTI}, it can be observed that the region with high diffusivity also have a high concentration tracer, see Fig ??.
+Since resulting states corresponds with the observation indicates that the computed values are higher than the average ADC value.
 
@@
 
-The comparison with DTI use Stokes-Einstein to estimate the measured diffusion coefficient, this will give some error. Furthermore, comparison with molecules of size 600 Da shows
+The computed diffusion coefficients are in the same magnitude as the values obtained from the DTI. But it can be seen that there is a clear difference between grey matter and white matter values.
 
-The limited number observations makes it difficult to measure the grey matter diffusion coefficient, since domain depth is about 5 mm {\color{red} cortex thickness}.
+The grey matter diffusion coefficient displays a high volatility in the variation of the relaxation parameters, which can be seen in Tab.\ref{Tab::Real-data}.
+This volatility can be caused by the boundary control $g$, which exists along the entire boundary of the grey matter.
+Considering the that the grey matter volume has a depth less than 5 mm makes it susceptible to changes in $g$.
+Therefore this seems likely, given the fact that both relaxation parameters are used to adjust the boundary control.
 
-Furthermore, the grey domain is more affected by the boundary control. This means that the 
-diffusion paramet
+ boundary control, which exists along the external boundary of the grey matter. This
 
-The computational have 2 diffusion coefficient controls, while the DTI values represent a range of measurements,
+A possible solution is to include the CSF compartment, but only use the observation in the white and grey matter.
 
-\section{Sleep}
-There have been reports of increase clearance in rodents that are sleeping.
-This effect can only by a change in the tortuosity since the properties of the molecules do not change.
-This indicates that the model should take into account changes in the apparent diffusion coefficient.
-Thus making the control parameters time dependent.
+The computational have two values for diffusion coefficients, while it can be seen in  Fig.\ref{FIG::DTI} that diffusion coefficients can be considered a spacial function. 
+The controls for diffusion coefficients should be spacial functions, but this would increase the computational cost greatly.
+
+It can also be taken into consideration to model the diffusion coefficients as a function in time, given the report of an increase clearance in rodents during sleeping [insert citation].
+This follows the assumption that the clearance is related to diffusion, which means an increase in diffusivity.
+Since the properties of the tracer molecule do not change, this would mean that the tortuosity decreased, and subsequently increase the value of the ADC.
+
+The hypothesis of the glymphatic system [insert citation] states that the waste is cleared through the veins in the cerebral.
+This gives the tracer an additional pathway that is not considered in the computational.
+The additional pathway can be modeled as a drainage, which can be included in the model as a sink source.
+This sink term can be added to the model as a control.
+
+The concentration estimation is a stepwise process, which required adjustment of the intensity for each observation \cite{eidevalnes}.
+Thus the accumulation of errors can be a factor in the estimation.
+
+The results of the computation using MRI data show a higher volatility of the regularization parameters.
+
+\section{Conclusion}
+The results from the manufactured
+
+However, this method has limitations based on the model and on the acquired data.
+
+The adaptation for a
 
@@
 \newgeometry{top=0.5cm}
+
+ \begin{table}
+\centering
+\caption{ {\color{red} Preliminary data, new runs with different convergence criteria is running.
+No excepted change is assumed see Fig.\ref{fig:gull} } Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$, the resulting number of iterations, the estimated diffusion coefficients based on MRI data.}
+\resizebox{\textwidth}{!}{\begin{tabular}{*{6}c}
+$\alpha$ & $\beta$ & k & iter &  $ ||D_{\Omega_1}||_{RE}$ & $ ||D_{\Omega_2}||_{RE}$ \\
+\hline
+ 1.0e-02 	 & 1.0e+00 	 & 24 & 1001 	 & +0.658 & +0.914 \\ 
+ 1.0e-02 	 & 1.0e-02 	 & 24 & 1001 	 & +0.840 & +0.976 \\ 
+ 1.0e-06 	 & 1.0e+00 	 & 24 & 1001 	 & +0.572 & +0.832 \\ 
+ 1.0e-06 	 & 1.0e-02 	 & 24 & 1001 	 & +0.719 & +0.727 \\
+
+\end{tabular}}
+\label{Tab::Real-data}
+\end{table}
+
+\begin{figure}
+  \begin{subfigure}[b]{0.5\textwidth}
+        \includegraphics[width=\textwidth]{Pic_Grey.png}
+        \caption{ {\color{red} shows that it converges but sufficent to the convergence criteria}}
+        \label{fig:gull}
+    \end{subfigure}
+     \qquad
+     \begin{subfigure}[b]{0.5\textwidth}
+        \includegraphics[width=\textwidth]{Pic_White.png}
+        \caption{ {\color{red} shows that it converges but sufficent to the convergence criteria} }
+        \label{fig:gull}
+    \end{subfigure}
+\end{figure}
 
@@
 \caption{Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$, the resulting number of iterations, the relative error of the estimated optimal parameters for the diffusion coefficients and the relative error for $g$.
-The noise amplitude was set to 0.03, and $\tau =[2.4, 4.8, 7.2, 9.6, 12.0, 14.4, 16.8, 19.2, 21.6, 24.0]$ }
+The noise amplitude was set to 0.03, and $ t_i=[2.4, 4.8, 7.2, 9.6, 12.0, 14.4, 16.8, 19.2, 21.6, 24.0]$ }
 \resizebox{0.8\textwidth}{!}{\begin{tabular}{*{8}c}
@@
 \caption{Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$, the resulting number of iterations, the relative error of the estimated optimal parameters for the diffusion coefficients and the relative error for $g$.
-The noise amplitude was set to 0.3, and $\tau =[2.4, 4.8, 7.2, 9.6, 12.0, 14.4, 16.8, 19.2, 21.6, 24.0]$  }
+The noise amplitude was set to 0.3, and $t_i =[2.4, 4.8, 7.2, 9.6, 12.0, 14.4, 16.8, 19.2, 21.6, 24.0]$  }
 \resizebox{0.8\textwidth}{!}{\begin{tabular}{*{8}c}
@@
 \caption{ Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$, the resulting number of iterations, the relative error of the estimated diffusion coefficients and the relative error for $g$.
-The observation times were $t_i \in \lbrace 1.2, 2.4, 3.6, 4.8, 6.0, 7.2, 8.4, 9.6, 10.8, 12.0, 13.2, 14.4, 15.6, 16.8, 17.0, 19.2, 20.4, 21.6, 22.8, 24.0\rbrace $.}
+The observation times were $t_i \in \lbrace $1.2, 2.4, 3.6, 4.8, 6.0, 7.2, 8.4, 9.6, 10.8, 12.0, 13.2, 14.4, 15.6, 16.8, 17.0, 19.2, 20.4,$ 21.6, 22.8, 24.0\rbrace $.}
 \resizebox{\textwidth}{!}{\begin{tabular}{*{8}c}
@@
 $\alpha$ & $\beta$ & k & iter &  $ ||D_{\Omega_1}||_{RE}$ & $ ||D_{\Omega_2}||_{RE}$ & $||D_{\Omega_3}||_{RE} $ & $||g||_{RE}$\\
+\hline
  1.0e-04 	 & 1.0e+00 	 & 40 & 453 	 & -0.003 & -0.017 & -0.021 & +0.053 \\

### 2018-10-12 tex/paper.tex
reelle data

@@
 
-The diffusivity of the Gadovist (600 Da) is currently not known {\colro{red} Geir vet dere?}, thus the diffusion of (Navn Gd-DPTA (550 Da)  will be used as reference.
-The free diffusion coefficient for Gd-DPTA  3.8e-5$\mathrm{mm\sp{2}/s}$ , and obtained from [cite].
-{\color{red} discussion om hvorfor eller nevne Stoke Einstein her?}
+The diffusivity of the Gadovist (600 Da cite?) was estimated to be similar to the diffusion coefficient of Gd-DPTA (550 Da cite ?).
+This due to the fact that both molecules have similar mass/size, and based Stoke-Einstein equation should have similar diffusion coefficients.
+The free diffusion coefficient for Gd-DPTA  3.8e-5$\mathrm{mm\sp{2}/s}$ was obtained from [cite].
 
@@
 Then the use of T2 weighted MRI was used to segment the csf compartment surrounding the cerebral.
-(BrainMesh code accessibility {\color{red} not fully tested}) CGAL \cite{cgal:rty-m3-18b} was used to combine the polyhedral surfaces and to construed the mesh.
+The module BrainMesh (currently in testing) (BrainMesh code accessibility {\color{red} kan ta med eller bare si CGAL}) CGAL \cite{cgal:rty-m3-18b} was used to combine the polyhedral surfaces and to construed the mesh.
 The computational requirement for the resulting mesh was significant, therefore two submesh was also constructed, see Fig.\ref{Fig::Mesh}.
@@
 The 3 domain mesh in Fig.\ref{Fig::Mesh} A, consists of 244318 tetrahedral cells and 22057 vertices, while the 2 domain mesh Fig.\ref{Fig::Mesh} B consists of 335589 tetrahedral cells and 73002 vertices.
+The dimension of the mesh coordiantes are $\mathrm{mm}$.
 
@@
 The median diffusion coefficient in the DTI was estimated to be respectively in white and grey matter to be 8.7e-4 $\mathrm{mm\sp{2}/s}$ and  1.0e-3 $\mathrm{mm\sp{2}/s}$.
+%This corresponds to 3.1 $\mathrm{mm\sp{2}/h}$ and  3.6 $\mathrm{mm\sp{2}/h}$.
+The self-diffusivity of water have been estimated to be about  3.0e-3$\mathrm{mm\sp{2}/s}$ at 37\sp{o}C.% This corresponds to 10.8 $\mathrm{mm\sp{2}/h}$ and  $\mathrm{mm\sp{2}/h}$.
+
 This is an increase from the reported values in [insert citation] of XX and XX.

### 2018-10-12 tex/paper.tex
reelle data, lagt til

@@
 There was no significant visible change in the tracer between the observations at $\lbrace 0.00 0.16, 0.39, 0.55, 0.77 \rbrace$.
-This prompted the focus on the observation times  $0.00 2.09, 6.05, 24.06, 47.84$, which can be seen in Fig.??.
+This prompted the use of the following observation times  $0.00 2.09, 6.05, 24.06, 47.84$.
 
@@
 Therefore the 2 domain mesh, shown in Fig.\ref{figmesh} was used in the computation.
+The boundary control was set to the external boundary of both domains, and the subscript in $D_w$ and $D_g$ denotes white and grey diffusion coefficients.
 Furthermore, bounds were added to the L-BFGS-B algorithm to ensure non-negative boundary controls and the convergence criteria was adjusted to $gtol=6.0e-1$.
-The resulting states can be seen in Fig.
-??
-and the relative error of control values are displayed in Tab.??
-.
+
+The results are shown in Tab.\ref{Tab::Real-data}, 
+and the observation together with resulting states are displayed in Fig.\ref{Fig::realdata}
 
 \subsection*{DTI comparison}
-The median diffusion coefficient in the DTI was estimated to be respectively in white and grey matter to be 8.7e-4 $\mathrm{mm\sp{2}/s}$ and  1.0e-3 $\mathrm{mm\sp{2}/s}$.
+The median diffusion coefficient in the DTI was estimated to be 8.7e-4 $\mathrm{mm\sp{2}/s}$ in   white matter and 1.0e-3 $\mathrm{mm\sp{2}/s}$ in grey matter.
 %This corresponds to 3.1 $\mathrm{mm\sp{2}/h}$ and  3.6 $\mathrm{mm\sp{2}/h}$.
-The self-diffusivity of water have been estimated to be about  3.0e-3$\mathrm{mm\sp{2}/s}$ at 37\sp{o}C.% This corresponds to 10.8 $\mathrm{mm\sp{2}/h}$ and  $\mathrm{mm\sp{2}/h}$.
+The self-diffusivity of water have been estimated to be around 3.0e-3$\mathrm{mm\sp{2}/s}$ for  $37\sp{o}C$.% This corresponds to 10.8 $\mathrm{mm\sp{2}/h}$ and  $\mathrm{mm\sp{2}/h}$.
 
-This is an increase from the reported values in [insert citation] of XX and XX.
+The reference value of Gd-DPTA was reported to be 3.8e-4 $\mathrm{mm\sp{2}/s}$ in [insert citation].
+The values in Tab.\ref{Tab::Real-data} gives the value-range $1.5e-4 -2.7e-4\mathrm{mm\sp{2}/s}  $ for the grey diffusion coefficient and  $2.2e-4 - 3.3e-4\mathrm{mm\sp{2}/s}$ for the white diffusion coefficient.
+These values are $20 -110 \%$ larger than the expected values for $D_{g}$,  and $100 - 200 \%$ larger than the expected values for $D_{w}$.
+
+The estimation assumes that the tortousity is independent on molecular size.
+
+%The region with high diffusivity in the white matter, shown in Fig\ref{FIG::DTI}, gives a upper bound on the diffusion coefficient to be 1.3 $\mathrm{mm\sp{2}/s}$.
+
+%
+% \begin{table}
+%\centering
+%\caption{Viser omgjøringer,estiamering og prosentvis forskjell for min og max control/optimerte verdier . Unit $\left[ \mathrm{mm\sp{2}/h} \right]$}
+%\resizebox{\textwidth}{!}{\begin{tabular}{*{6}c}
+%$ D\sp{free}_{water} $ & $ D\sp{DTI}__{g} $ & $ D\sp{DTI}_{w} $ & $D\sp{fre}__{Gd-DPTA} $ & $D\sp{ADC}__{g} $ & $ D\sp{ADC}_{w} $ & $ D\sp{ADC}_{g} -D\sp{OPT}_{g} $ &$ D\sp{ADC}_{w} -D\sp{OPT}_{w} $ \\
+%\hline
+%10.8 & 3.64 & 3.13 & 1.37 & 0.46 & 0.40 &  20 - 114 $\%$  & 100- 200 $\%$
+%  -   &  -    & 4.86 &  - &  -   & 0.61 &   -                  &   0 - 100 $\%$       
+%\end{tabular}} 
+%\label{}
+%\end{table} 
+%
+
+{\color{red} tortuoisty mindre for støre molekyler ? }
+%The region with high diffusivity in the white matter, shown in Fig\ref{FIG::DTI}, gives a upper bound on the diffusion coefficient to be 1.3 $\mathrm{mm\sp{2}/s}$
 
@@
 
-\subsection{Anisotropy}
-The computational model assumes isotropic diffusivity, but the anisotropy in the white matter is well documented, as shown in Fig\ref{FIG::DTI}.
+The computational model assumes isotropic diffusivity, but the anisotropy in the white matter is well documented, as shown by the FA in Fig\ref{FIG::DTI}.
+The region with high FA, can also be observed in the observation after 48 hours, shown in Fig.\ref{Fig::realdata}.
+This observation is after 48 hours, and the amount of tracer inside the anisotropic region is negligible.
+Therefore it would seem that the anisotropy do not have direct impact on the computations, since the computation can not evaluate a static environment.
+Thus observation of tracer in anisotropic regions are needed for the integration of anisotropy into the model.
 
-The anisotropy can be seen by comparing the observations and the states after 48 hours, see Fig ??.
-This observation is after 48 hours, and the amount of tracer inside the anisotropic region is negligible.
-Therefore it would seem that the anisotropy do not have direct impact on the computations, since the computation can asses a static environment.
+A more important factor are regions with higher diffusivity.
+In Fig.\ref{FIG::DTI}, it can be observed that the region with high diffusivity also have a high tracer concentration, see Fig \ref{Fig::realdata}.
 
-A more important factor is that of tissue damage, which may causes higher diffusivity.
-In Fig.\ref{FIG::DTI}, it can be observed that the region with high diffusivity also have a high concentration tracer, see Fig ??.
-Since resulting states corresponds with the observation indicates that the computed values are higher than the average ADC value.
-
-\subsection{Real Data}
-
-The computed diffusion coefficients are in the same magnitude as the values obtained from the DTI. But it can be seen that there is a clear difference between grey matter and white matter values.
-
-The grey matter diffusion coefficient displays a high volatility in the variation of the relaxation parameters, which can be seen in Tab.\ref{Tab::Real-data}.
-This volatility can be caused by the boundary control $g$, which exists along the entire boundary of the grey matter.
-Considering the that the grey matter volume has a depth less than 5 mm makes it susceptible to changes in $g$.
-Therefore this seems likely, given the fact that both relaxation parameters are used to adjust the boundary control.
-
- boundary control, which exists along the external boundary of the grey matter. This
-
-A possible solution is to include the CSF compartment, but only use the observation in the white and grey matter.
-
-The computational have two values for diffusion coefficients, while it can be seen in  Fig.\ref{FIG::DTI} that diffusion coefficients can be considered a spacial function. 
-The controls for diffusion coefficients should be spacial functions, but this would increase the computational cost greatly.
+The computational have 2 global controls for the diffusion coefficients, while it can be seen in  Fig.\ref{FIG::DTI} that diffusion coefficients can be considered a spacial function.
 
@@
 Since the properties of the tracer molecule do not change, this would mean that the tortuosity decreased, and subsequently increase the value of the ADC.
+
+In Tab.\ref{Tab::Real-data}, it is shown that the grey matter diffusion coefficient have a consistent increase based on the decrease in the relaxation parameter $\beta$.
+This can be caused by the boundary control $g$, which exists along the entire boundary of the grey matter.
+Considering the that the grey matter volume has a depth less than 5 mm makes it susceptible to changes in $g$.
+Therefore this seems likely, given the fact that both relaxation parameters are used to adjust the boundary control.
+
+A possible solution is to include the CSF compartment, but only use the observation in the white and grey matter.
 
@@
 
-The concentration estimation is a stepwise process, which required adjustment of the intensity for each observation \cite{eidevalnes}.
-Thus the accumulation of errors can be a factor in the estimation.
+\section{Conclusion}
 
-The results of the computation using MRI data show a higher volatility of the regularization parameters.
-
-\section{Conclusion}
-The results from the manufactured
-
-However, this method has limitations based on the model and on the acquired data.
-
-The adaptation for a
-
-\begin{figure}
-\centering
-\includegraphics[scale=0.4]{27-12-hours-scale-0-1-3.png}  
-\caption{The upper row shows the manufactured observation, A ) Shows the manufactured observation at time-point 24 with no noise added.
+%\begin{figure}
+%\centering
+%\includegraphics[scale=0.4]{27-12-hours-scale-0-1-3.png}  
+%\caption{The upper row shows the manufactured observation, A ) Shows the manufactured observation at time-point 24 with no noise added.
 B) Shows the manufactured observation at time-point 24 with an noise amplitude of 0.15.
@@
 }
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[scale=0.4]{27-24-hours-scale-0-1.png}
-\caption{The upper row shows the manufactured observation, A ) Shows the manufactured observation at time-point 24 with no noise added.
+%\end{figure}
+%
+%
+%\begin{figure}
+%\centering
+%\includegraphics[scale=0.4]{27-24-hours-scale-0-1.png}
+%\caption{The upper row shows the manufactured observation, A ) Shows the manufactured observation at time-point 24 with no noise added.
 B) Shows the manufactured observation at time-point 24 with a noise amplitude of 0.15 {\color{red} explain noise ampliutde}.
@@
 }
-\end{figure}
+%\end{figure}
+% 
+% 
+% 
+%
+%
 
@@
 \centering
-\caption{ {\color{red} Preliminary data, new runs with different convergence criteria is running.
-No excepted change is assumed see Fig.\ref{fig:gull} } Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$, the resulting number of iterations, the estimated diffusion coefficients based on MRI data.}
+\caption{Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$, the resulting number of iterations, the estimated diffusion coefficients for grey $D_g$ and white $D_w$ matter based on MRI data.}
 \resizebox{\textwidth}{!}{\begin{tabular}{*{6}c}
-$\alpha$ & $\beta$ & k & iter &  $ ||D_{\Omega_1}||_{RE}$ & $ ||D_{\Omega_2}||_{RE}$ \\
+$\alpha$ & $\beta$ & k & iter &  $ D_{g} \left[ \mathrm{mm\sp{2}/h} \right] $ & $ D_{w} \left[ \mathrm{mm\sp{2}/h} \right]$ \\
 \hline
- 1.0e-02 	 & 1.0e+00 	 & 24 & 1001 	 & +0.658 & +0.914 \\ 
- 1.0e-02 	 & 1.0e-02 	 & 24 & 1001 	 & +0.840 & +0.976 \\ 
- 1.0e-06 	 & 1.0e+00 	 & 24 & 1001 	 & +0.572 & +0.832 \\ 
- 1.0e-06 	 & 1.0e-02 	 & 24 & 1001 	 & +0.719 & +0.727 \\
+ 1.0e-02 	 & 1.0e+00 	 & 48 & 591 	 & 0.648 & 0.893 \\ 
+ 1.0e-02 	 & 1.0e-01 	 & 48 & 461 	 & 0.772 & 0.982 \\ 
+ 1.0e-02 	 & 1.0e-02 	 & 48 & 748 	 & 0.986 & 1.198 \\ 
+ 1.0e-04 	 & 1.0e+00 	 & 48 & 607 	 & 0.551 & 0.815 \\ 
+ 1.0e-04 	 & 1.0e-01 	 & 48 & 598 	 & 0.649 & 0.787 \\ 
+ 1.0e-04 	 & 1.0e-02 	 & 48 & 837 	 & 0.740 & 0.817 \\ 
+ 1.0e-06 	 & 1.0e+00 	 & 48 & 681 	 & 0.557 & 0.811 \\ 
+ 1.0e-06 	 & 1.0e-01 	 & 48 & 780 	 & 0.645 & 0.774 \\ 
+ 1.0e-06 	 & 1.0e-02 	 & 48 & 745 	 & 0.736 & 0.819 \\
 
@@
 \begin{figure}
-  \begin{subfigure}[b]{0.5\textwidth}
-        \includegraphics[width=\textwidth]{Pic_Grey.png}
-        \caption{ {\color{red} shows that it converges but sufficent to the convergence criteria}}
-        \label{fig:gull}
-    \end{subfigure}
-     \qquad
-     \begin{subfigure}[b]{0.5\textwidth}
-        \includegraphics[width=\textwidth]{Pic_White.png}
-        \caption{ {\color{red} shows that it converges but sufficent to the convergence criteria} }
-        \label{fig:gull}
-    \end{subfigure}
+\centering
+\includegraphics[width=0.95\textwidth]{different.png} 
+\caption{Row A) shows the observation at times 2 hours, 6 hours, 24 hours and 48 hours after the first observation with tracer.
+Row B) shows the corresponding states with the relaxation parameters set to $ \alpha=0.01$ and $\beta=0.01$.
+Row C) shows the corresponding states with the relaxation parameters set to $ \alpha=0.0001$ and $\beta=1.0$.
+ Row D) shows the corresponding states with the relaxation parameters set to$ \alpha=1.0e-6$ and $\beta=0.1$. The color-bar was restricted to the range $ \lbrace 0 ,0.5 \rbrace$. }
+\label{Fig::realdata}
 \end{figure}

### 2018-10-13 tex/paper.tex

@@
 
+\begin{figure}
+\centering
+\includegraphics[scale=0.4]{27-12-hours-scale-0-1-3.png}  
+\caption{The upper row shows the manufactured observation, A ) Shows the manufactured observation at time-point 24 with no noise added.
+B) Shows the manufactured observation at time-point 24 with an noise amplitude of 0.15.
+C)Shows the manufactures observation at time-point 24 with noise amplitude of 0.3.
+The lower row shows the results with optimized parameter obtained with $alpha=0.0001$, $\beta=1.0$ and $k=27$.
+D) Shows the resulting state given the observation in A.
+E)  Shows the resulting state given the observation in B .F) Shows the resulting state given the observation in C.
+}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[scale=0.4]{27-24-hours-scale-0-1.png}
+\caption{The upper row shows the manufactured observation, A ) Shows the manufactured observation at time-point 24 with no noise added.
+B) Shows the manufactured observation at time-point 24 with a noise amplitude of 0.15 {\color{red} explain noise ampliutde}.
+C)Shows the manufactures observation at time-point 24 with noise amplitude of 0.3.
+The lower row shows the results with optimized parameter obtained with $alpha=0.0001$, $\beta=1.0$ and $k=27$.
+D) Shows the resulting state given the observation in A.
+E)  Shows the resulting state given the observation in B .F) Shows the resulting state given the observation in C.
+}
+\end{figure}
+
 \newpage 

### 2018-10-14 tex/paper.tex
update

@@
 \begin{abstract}
+bla bla 
 \end{abstract}
@@
 
-A novel pathway called the paravascular pathway was discoved in 2011~\cite{iliff2012paravascular} and later found to be particularly active during sleep~\cite{xie2013sleep}.  
-It has been proposed that this pathway plays an important role in the waste
-clearance of the brain. In particular, since the brain lack a lymphatic system, 
-which elsewhere in our body plays a crucial role in waste clearance, the system has been called the glymphatic system~\cite{jessen2015glymphatic}.  
+A novel pathway of the brain's metabolism system called the paravascular pathway, because it runs in parallel with 
+vasculature system in a surrounding compartment,  
+was discoved in 2011~\cite{iliff2012paravascular}. 
+%Later it was found that this system is particularly active during sleep~\cite{xie2013sleep}.  
+It has been proposed that this pathway plays an important role in the clearance of waste
+from the brain and hereby a malfunction of this system is linked to  the development of dementia such as Alzheimer's and Parkinson's diseases. That is, 
+the lymphatic system plays a crucial role in waste clearance in the rest of our body, but there are no lymph vessels inside
+the brain. As such, the metabolic process of the brain is not well understood and this is surprising since the brain is a very 
+energy demanding organ (about 10 times as demanding as the average organ). The circulatory system of the paravascular pathway 
+has therefore been named the glymphatic system~\cite{jessen2015glymphatic} as it has a similar role as the well-known lymphatic system and because the glia cells 
+are crucial in this system.  
 The glymphatic system remains controversial and modeling attempts
@@
 
-In \cite{ringstad2018brain} brainwide distribution of MRI-contrast was demonstrated during 24 hours after lumbar contrast injection.
-Brain wide distribution by diffusion alone was deemed unlikely by the authors (some of which are part
+In \cite{ringstad2018brain} brain-wide distribution of MRI-contrast was demonstrated during 24 hours after lumbar contrast injection.
+Brain-wide distribution by diffusion alone was deemed unlikely by the authors (some of which are part
 of this study as well). The argument was based on analytical considerations where it was calculated that 50\% contrast enrichment would occur after 
@@
 a corresponding surface of a ball with the same volume. Hence, 
-a more rigorous modeling attempt is warrented. Complicating factors
-are however that the contrast in the surrounding CSF is heterogenous
+a more rigorous modeling attempt is warrented. A complicating factor
+is however that the contrast in the surrounding CSF is heterogenous
 and changes significantly during the 24 hours of the investigations. 
@@
 measured by DTI at a time-scale of XXX \kam{tall her} may not be representative for the process on a
-longer time-scale, at least if the paravascular pathway plays an important role. The fact that the vasculature (mostly 
-the capillary network) occupy around 3\% of the brain volume and the paravascular network is bound to be substatantially
-smaller potentially render it invisible for the DTI investigation while still effective on longer time scales.
+longer time-scale, at least if the paravascular pathway plays an important role. The fact that the vasculature  occupy around 3\% of the brain volume 
+and the paravascular network is substatantially smaller potentially render it invisible at the short time-scales of a DTI investigation 
+while it may still be effective on longer time scales.
 
 Our purpose in this paper is to attempt a more rigorous methodology 
-for assessing the apparent diffusion process. To this end we employ
-adjoint methods to determine the apparent diffusion coefficient 
-that would explain the tracer distribution.
+for assessing the apparent diffusion process where
+the complex geometry of the brain is taken into account. The approach 
+we will take is to solve a PDE constrained optimization problem 
+via adjoint methods. As such we need to assess the sensitivity of
+the approach with respect important parameters such as to regularization parameters, noise levels, 
+time resolution to determine whether this approach is a viable method
+to obtain parameters involved time-scales beyond those of the MRI aquisition.
 
@@
 \includegraphics[width=0.95\textwidth]{PatID-68-new-100.png} 
+\caption{Shows the percentage intensity increase from baseline at different observation times. }
 \label{fig1} 
-\caption{Shows the percentage intensity increase from baseline at different observation times. }
 \end{figure}
@@
 \includegraphics[width=0.95\textwidth]{Zoom-PatID-68.png} 
+\caption{Shows the percentage intensity increase from baseline at different observation times in the slice (marked red in the left panel) used in the subsequent analysis.}
 \label{fig2} 
-\caption{Shows the percentage intensity increase from baseline at different observation times in the slice (marked red in the left panel) used in the subsequent analysis.}
 \end{figure}
-Figure ~\ref{fig1} shows the distribution of tracers during 24 hours, see also~\cite{ringstad2018brain} for further information on the imaging procedure.   
+Figure~\ref{fig1} shows the distribution of tracers during 24 hours, see also~\cite{ringstad2018brain} for further information on the imaging procedure.   
 Our data (not all shown) consist of a total of 10 MRI observations, including a baseline MRI taken before tracer was injected.
 The observation points are distributed with 5 observations within 1-2 hours after injection, 1 observation in the timeframes 2-4 hours, 6-9 hours, 24 hours and 48 hours.
-Figure ~\ref{fig2} shows the slice selected for our computations. 
+Figure~\ref{fig2} shows the slice selected for our computations. 
 The software Freesurfer was used to segment and align each of the observations, which made it possible to estimate voxelwise intensity increase.
@@
 In order to estimate the apparent diffusion coefficient involved in the contrast transportation shown 
-in Figure \ref{fig1} we assume that the process is governed by a diffusion equation and  
+in Figure~\ref{fig1} we assume that the process can be modeled by a diffusion equation and  
 solve a PDE constrained optimization problem where
@@
 diffusion coefficient are solved for by optimizing with
-respect to the observed contrast distribution. 
+respect to the observed contrast distribution. As such, enhanced transportation because of effects such as
+dissipation would result in an apparent diffusion coefficient larger than that predicted by DTI.  
 The objective function was defined as 
@@
 \end{equation}
-with the domain $\Omega$ contains three sub domains, each with a different diffusion coefficient.
-We denote the Cerebral Spinal fluid (CSF) domain as $\Omega_1$, the grey matter as $\Omega_2$ and the white matter as $\Omega_3$.
-
-Here $u$ is the contrast distribution, $D_i$ is the apparent diffusion 
+Here, $u$ is the contrast distribution, $D_i$ is the apparent diffusion 
 coefficient, and $g$ is the boundary condition. Furthermore,  
@@
 \section*{Implementation}
+\kam{Lars, sometimes past tense is used sometimes present tense.}
 The code used the FEniCS project to solve the PDE, using backwards Euler time discretization and first order continuous Galerkin finite elements.
-The linear problem was solved using GMRES, and bilinear matrix stored in the solver.
+The linear problem was solved using GMRES, and bilinear\kam{a matrix is always bilinear} matrix stored in the solver.
 {\color{red} why not amg}
 The module dolfin adjoint ~\cite{farrell2013automated} \kam{correct ref?} was used to solve the PDE constrained optimization problem with the L-BFGS-B algorithm in the python module scipy.
-The convergence criteria for the minimization was set so that $L\sp{inf}$ norm of the project gradient was less than $gtol =1.0e-1$.
+The convergence criteria for the minimization was set so that $L\sp{\infty}$ norm of the project gradient was less than $gtol =1.0e-1$.
+\kam{More info needed gtol not defined.
+}
 
-The implementation used the first observation as initial conditions of Eq.\ref{Eq::PDE}, and for each timestep, the next observation was used as the Dirichlet boundary condition.
+The implementation used the first observation as initial conditions of Eq.\ref{Eq::PDE}, and for each timestep, the next observation was used as the Dirichlet boundary condition \kam{is this true?
+why not use \eqref{observations:interpolation} }.
 The Dirichlet boundary condition was imposed on the external boundary for the domain $D_{\Omega_1}$.
@@
 Therefore, after each time step $dt$ in Eq\ref{Eq::PDE}, it was checked if the time step contained the next observation.
-If it did, then a linear interpolation of the current solution $U$ and previous solution $U(t-dt)$ was used approximate the solution corresponding to $t_i$.
+If it did, then a linear interpolation of the current solution $u_{obs}(t_i)$ and previous solution $u_{obs}(t_{i-1})$ was used approximate the solution corresponding to $t_i$.
 The linear interpolation was given as
 \begin{equation}
-U_{lin}(t) = \frac{\Delta t}{dt} U(t-dt) + \frac{dt - \Delta t }{dt} U(t), \quad t \in \lbrace t-dt, t \rbrace
+\label{observation:interpolation}
+u_{obs}(t) = \frac{\Delta t}{dt} u_{obs}(t_i) + \frac{dt - \Delta t }{dt} u_{obs}(t_{i-1}), \quad t \in \lbrace t-dt, t \rbrace
 \end{equation}
-with $\Delta t = t-t_i $
+with $\Delta t = t-t_i $.  \kam{Check this formula}
 
- \kam{This has to be made clearer. Earlier we used $u_{obs}$ for observation. Also this also only applies if $t_i$ is close to the observations, right?}
-
-The initial values of the optimization algorithm was chosen to be $1,1,1$.
-Furthermore, to obtain faster convergence in the optimization, the diffusion coefficients was scaled to have the same magnitude, i.e.
-$D_{\Omega_1} = D\sp {s}_{\Omega_1}100$.
-
+The initial values of the diffusion coefficients in the optimization algorithm $(D_{CSF}, D_{GM}, D_{WM}) = (1000, 1, 1)$. 
 The noise susceptibility was tested by adding an uniform distribution noise term to the observations.
@@
 seen in Figures \ref{fig1} and \ref{fig2} and the underlying contrast 
-concentration. 
+concentration. We remark that we use a notation common in medical literature and 
+here two letter symbols are common. Hence, below we will use two letter symbols such 
+as $TE$ and $SI$ to keep the notation consistent the presentation of (reference XXXX).   
 The tracer causes the longitudinal(spin-lattice) relaxation time $T_{1}$ to shorten with the following relation
@@
 \end{equation}
-with  $TE$ and $\theta$ respectively denoting the echo time and the flip angle.
-Also $T2\sp{*}$ is transverse magnetization caused by a combination of spin-spin relaxation and magnetic field inhomogeneity.
-It is defined as
+with  $TE$ and $\theta$ respectively denoting the echo time and the flip angle, and $M_{n}$ the magnetization for the n-echo described below. 
+Also $T2\sp{*}$ is transverse magnetization caused by a combination of spin-spin relaxation and magnetic field inhomogeneity. It is defined as 
 \begin{equation}
@@
 \subsection{DTI}
-The validation of the results from the MRI data can be done using diffusion tensor imaging (DTI).
-Diffusion tensor imaging is a MRI-sequence that is used to obtain the apparent diffusion coefficients of water in the brain.
-{\color{red} mer on DTI?
-}
-
+In addition to the T1 and T2 weighted sequences described above we have also obtained diffusion tensor imaging (DTI) to assess the apparent diffusion 
+coefficients on short time-scales. Images are shown in Figure~\ref{FIG:DTI} where the larges diffusion coefficient (shown in 
+red in the middle figure) is shown to be around 0.001 mm$^2$/s. We remark that we have not included possible anisotropy, shown in 
+the right-most image in Figure~\ref{FIG:DTI} and that these images shows the apparent diffusion coefficient for free water molecules (18 Da).      
 The diffusivity of the Gadovist (600 Da cite?) was estimated to be similar to the diffusion coefficient of Gd-DPTA (550 Da cite ?).
@@
 
-\kam{check that all symbols are explained here}
-
 \subsection{PDE constrained optimization algorithm}
@@
 \end{equation}  
-The magnitude order of the diffusion coefficient are chosen so that they resemble diffusion coefficient in csf, grey and white matter.
+The magnitude order of the diffusion coefficient are chosen so that they resemble diffusion coefficient in CSF, grey and white matter.
 The manufactured forward computation gave a total of 120 possible observation time points.
@@
 The software Freesurfer was used in segmentation and creating the polyhedral surfaces of the white and grey matter.
-Then the use of T2 weighted MRI was used to segment the csf compartment surrounding the cerebral.
+Then the use of T2 weighted MRI was used to segment the CSF compartment surrounding the cerebral.
 The module BrainMesh (currently in testing) (BrainMesh code accessibility {\color{red} kan ta med eller bare si CGAL}) CGAL \cite{cgal:rty-m3-18b} was used to combine the polyhedral surfaces and to construed the mesh.
@@
 \section{Results}
-
+Below we will discuss the parameter identification and its sensitivity with respect to 
+regularization parameters, noise and time-resolution. 
 In presentation of the results, the relative error norm  $||\cdot||_{RE}$ is defined as 
@@
 \subsection{The relaxation parameters}
-The robustness of the objective functional defined in Eq.\ref{Eq::F} is dependent on the regularization parameters $\alpha$ and $\beta$.
-Therefore it is important to select regularization parameter values that ensures an effective and accurate convergence.
+To assess the sensitivity of the the objective functional defined in \ref{Eq::F} with respect to the regularization parameters $\alpha$ and $\beta$ 
+we perform a systematic study of the reconstruction of the manufactured solution with respect to a wide range of regularization parameters. 
+Ideally, the approach should have a wide range of parameters in which the reconstruction algorithm yields very similar end-results although
+the convergence may vary substatantially.
  The evaluation of different regularization parameters was done by solving the optimization with different values of $\alpha$ and $\beta$ and compare the controls with the manufactured solution.
@@
 
-The results are shown in Tab.\ref{Tab::1} together with the number of iteration used to reach the convergence criteria.
+The results are shown in Tabel~\ref{Tab::1} together with the number of iteration used to reach the convergence criteria.
 For $\alpha= 1.0$, it can be observed that there is a significant relative error for $D_{\Omega_1}$.
 The other control parameters also show an increased relative error when compared to other values of $\alpha$.
+
+\begin{figure}
+\centering
+\includegraphics[scale=0.2]{convergence_0}  
+\includegraphics[scale=0.2]{convergence_1}  
+\includegraphics[scale=0.2]{convergence_2}  
+\includegraphics[scale=0.2]{convergence_3}  
+\includegraphics[scale=0.2]{convergence_4}  
+\label{convergence}
+\caption{Convergence of the diffusion coefficients, boundary conditions and functional with respect to different $\alpha$ and $\beta$ values. } 
+\end{figure}
 
@@
 Then the optimization was solved by varying the regularization parameters $\alpha$ and $\beta$.
+Figure~\ref{12hourswithnoise} and Figure~\ref{24hourswithnoise} show the reconstruction of the manufactured solution with
+different noise levels with $\alpha=0.0001$ and $\beta=1.0$. Clearly, the reconstruction shown in the lower rows is quite robust with respect to the various levels
+of noise shown in the upper rows.
 
-In Tab.\ref{Tab::Noise0.03}, we can see that a noise amplitude of 0.03, (10$\%$ of maximum initial condition) had negligible effect on the relative error.
-However, in Tab.\ref{Tab::Noise0.3} the noise amplitude was increased to 0.3 (100$\%$ of maximum initial condition) and it is observed that for  $\alpha < 1.0e-3$  $\beta < 1.0e-3$ the optimization failed to converge before reaching maximum iteration of 1000 steps.
+In Tabel~\ref{Tab::Noise0.03}, we can see that a noise amplitude of 0.03, (10$\%$ of maximum initial condition) had negligible effect on the relative error.
+However, in Tabel~\ref{Tab::Noise0.3} the noise amplitude was increased to 0.3 (100$\%$ of maximum initial condition) and it is observed that for  $\alpha < 1.0e-3$  $\beta < 1.0e-3$ the optimization failed to converge before reaching maximum iteration of 1000 steps.
 Furthermore, the relative boundary error $||g||_{RE(\Omega)}$ is  larger for lower values of $\beta$.
 
+\begin{figure}
+\centering
+\includegraphics[scale=0.4]{27-12-hours-scale-0-1-3.png}  
+\caption{The upper row shows the manufactured observation, A ) Shows the manufactured observation at time-point 24 with no noise added.
+B) Shows the manufactured observation at time-point 24 with an noise amplitude of 0.15.
+C)Shows the manufactures observation at time-point 24 with noise amplitude of 0.3.
+The lower row shows the results with optimized parameter obtained with $alpha=0.0001$, $\beta=1.0$ and $k=27$.
+D) Shows the resulting state given the observation in A.
+E)  Shows the resulting state given the observation in B .F) Shows the resulting state given the observation in C.
+}
+\label{12hourswithnoise}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[scale=0.4]{27-24-hours-scale-0-1.png}
+\caption{The upper row shows the manufactured observation, A ) Shows the manufactured observation at time-point 24 with no noise added.
+B) Shows the manufactured observation at time-point 24 with a noise amplitude of 0.15 {\color{red} explain noise ampliutde}.
+C)Shows the manufactures observation at time-point 24 with noise amplitude of 0.3.
+The lower row shows the results with optimized parameter obtained with $alpha=0.0001$, $\beta=1.0$ and $k=27$.
+D) Shows the resulting state given the observation in A.
+E)  Shows the resulting state given the observation in B .F) Shows the resulting state given the observation in C.
+}
+\label{24hourswithnoise}
+\end{figure}
+
 \subsection{The number of timessteps}
-The PDE uses backward Euler, which is a linear approximation in time.
-This means that the increasing the number of timesteps will allow for a better temporal approximation.
-However, this will also increase the computational cost for each iteration of the L-BFGS-B algorithm.
+Increasing the number of timesteps in the simulations potentially allow for a more accurate temporal reconstruction, but at the same time the number of observations per control decreases and the regularization therefore may play a larger role.
+Furthermore,  the computational cost for each iteration of the L-BFGS-B algorithm as one
+forward solve is performed per iteration.
 Thus finding the number of timesteps for an effective convergence can help for larger meshes.
@@
 %
-
-\begin{figure}
-\centering
-\includegraphics[scale=0.4]{27-12-hours-scale-0-1-3.png}  
-\caption{The upper row shows the manufactured observation, A ) Shows the manufactured observation at time-point 24 with no noise added.
-B) Shows the manufactured observation at time-point 24 with an noise amplitude of 0.15.
-C)Shows the manufactures observation at time-point 24 with noise amplitude of 0.3.
-The lower row shows the results with optimized parameter obtained with $alpha=0.0001$, $\beta=1.0$ and $k=27$.
-D) Shows the resulting state given the observation in A.
-E)  Shows the resulting state given the observation in B .F) Shows the resulting state given the observation in C.
-}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[scale=0.4]{27-24-hours-scale-0-1.png}
-\caption{The upper row shows the manufactured observation, A ) Shows the manufactured observation at time-point 24 with no noise added.
-B) Shows the manufactured observation at time-point 24 with a noise amplitude of 0.15 {\color{red} explain noise ampliutde}.
-C)Shows the manufactures observation at time-point 24 with noise amplitude of 0.3.
-The lower row shows the results with optimized parameter obtained with $alpha=0.0001$, $\beta=1.0$ and $k=27$.
-D) Shows the resulting state given the observation in A.
-E)  Shows the resulting state given the observation in B .F) Shows the resulting state given the observation in C.
-}
-\end{figure}
 

### 2018-10-15 forward_problem.py
saving linear interpolation

@@ -114,7 +114,7 @@ class Context(object):
     def return_value(self):
         return None
 
-def functional(mesh_config, V, D, g_list, tau, obs_file, alpha=0.0, beta=0.0, gradient=None, noise=None,save=None):
+def functional(mesh_config, V, D, g_list, tau, obs_file, alpha=0.0, beta=0.0, gradient=None, noise=None,save=None, interp=None):
     class FunctionalContext(Context):
         def __init__(self, mesh_config, V, D, g_list, tau, obs_file, alpha=0.0, beta=0.0, gradient=None ):
             super(FunctionalContext, self).__init__(mesh_config, V, D, g_list)
@@ -137,7 +137,7 @@ def functional(mesh_config, V, D, g_list, tau, obs_file, alpha=0.0, beta=0.0, gr
 
             self.gradient = gradient 
             self.save = save
-
+            self.interp = interp         
   
         def initial_conditions(self):
             self.obs_file.read(self.ic, "%0.2f"%(self.tau[0]))
@@ -172,7 +172,11 @@ def functional(mesh_config, V, D, g_list, tau, obs_file, alpha=0.0, beta=0.0, gr
                    self.save << ( self.d ,self.tau[self.next_tau])
 
 
-                Ulin = Dt/self.dt*U_prev +  (self.dt - Dt)/self.dt*U       
+                Ulin = Dt/self.dt*U_prev +  (self.dt - Dt)/self.dt*U     
+             
+                if self.interp: 
+                    self.interp << ( self.d ,self.tau[self.next_tau])
+  
                 self.J += assemble((Ulin - self.d) ** 2 * self.dx) 
                 # Move on to next observation
                 self.next_tau += 1

### 2018-10-15 main.py

@@ -121,8 +121,10 @@ if __name__ == "__main__":
   
     if Z.save:
        save = File( "Results-{}-{}-{}-{}/observation.pvd".format( Z.alpha, Z.beta,Z.noise,k ) )
+       interp = File( "Results-{}-{}-{}-{}/interpolation.pvd".format( Z.alpha, Z.beta,Z.noise,k ) )
     else:
        save = None
+       interp =None
 
     if Z.generate_observations:
         ic = initial_condition(V, mesh_config)
@@ -131,7 +133,7 @@ if __name__ == "__main__":
         exit()
     else:
         g = bc_guess(g, Z.obs_file, tau, k, noise)
-        J = functional(mesh_config, V, D, g, tau, Z.obs_file, Z.alpha, Z.beta, noise=noise, gradient=Z.scale, save=save)
+        J = functional(mesh_config, V, D, g, tau, Z.obs_file, Z.alpha, Z.beta, noise=noise, gradient=Z.scale, save=save,interp=interp)
 
     ctrls = ([Control(D[i]) for i in range(1, 4)]
              + [Control(g_i) for g_i in g])
@@ -142,7 +144,7 @@ if __name__ == "__main__":
     Jhat.optimize()
 
     
-    opt_ctrls = minimize(Jhat, method="L-BFGS-B", callback = iter_cb, options={"disp": True, "maxiter": Z.maxiter, "gtol": 1.0e-1})
+    opt_ctrls = minimize(Jhat, method="L-BFGS-B", callback = iter_cb, options={"disp": True, "maxiter": Z.maxiter, "gtol": 1.0})
 
     #print("[Constant({}), Constant({}), Constant({})]".format(float(opt_ctrls[0]), float(opt_ctrls[1]), float(opt_ctrls[2])))
     #print(
@@ -151,6 +153,9 @@ if __name__ == "__main__":
         save_control_values(opt_ctrls, Z.save_control_values_file)
 
 
+    dx = (tau[-1]- tau[0])/k
+
+    us= Function(V)
     if Z.save:
        tape = get_working_tape()
 
@@ -158,6 +163,8 @@ if __name__ == "__main__":
        s_blocks = [block for block in tape._blocks if isinstance(block, SolveBlock)]
        states = [block.get_outputs()[0].saved_output for block in s_blocks]
        out =        File("Results-{}-{}-{}-{}/finalstate.pvd".format(Z.alpha,Z.beta, Z.noise,k) )
[…]

### 2018-10-15 tex/paper.tex
reference and text

@@
 \documentclass[11pt,a4paper]{article}
+\usepackage{hyperref}
 \usepackage{color}
@@
 \usepackage{subcaption}
+
 \title{Assessing glymphatic transport velocities by adjoint methods}
@@
 \includegraphics[width=0.95\textwidth]{PatID-68-new-100.png} 
-\caption{Shows the percentage intensity increase from baseline at different observation times. }
+\caption{Shows the percentage intensity increase from baseline at different observation times. The colorbar was restricted to the range $(0,100)$ }
 \label{fig1} 
@@
 \includegraphics[width=0.95\textwidth]{Zoom-PatID-68.png} 
-\caption{Shows the percentage intensity increase from baseline at different observation times in the slice (marked red in the left panel) used in the subsequent analysis.}
+\caption{Shows the percentage intensity increase from baseline at different observation times in the slice (marked red in the left panel) used in the subsequent analysis.The colorbar was restricted to the range $(0,100)$}
 \label{fig2} 
@@
 \section*{Implementation}
-\kam{Lars, sometimes past tense is used sometimes present tense.}
 The code used the FEniCS project to solve the PDE, using backwards Euler time discretization and first order continuous Galerkin finite elements.
-The linear problem was solved using GMRES, and bilinear\kam{a matrix is always bilinear} matrix stored in the solver.
-{\color{red} why not amg}
+The linear problem was solved using GMRES, and the matrix was stored in the solver.
 The module dolfin adjoint ~\cite{farrell2013automated} \kam{correct ref?} was used to solve the PDE constrained optimization problem with the L-BFGS-B algorithm in the python module scipy.
-The convergence criteria for the minimization was set so that $L\sp{\infty}$ norm of the project gradient was less than $gtol =1.0e-1$.
-\kam{More info needed gtol not defined.
-}
+The convergence criteria for the minimization was set so that $max\lbrace | proj x_i | , \quad i = 1, .., N \rbrace \leq gtol=1.0e-1$ where $ proj x_i$ is the i-th component of the projected gradient.
+{\color{red} see scipy }.
 
-The implementation used the first observation as initial conditions of Eq.\ref{Eq::PDE}, and for each timestep, the next observation was used as the Dirichlet boundary condition \kam{is this true?
-why not use \eqref{observations:interpolation} }.
-The Dirichlet boundary condition was imposed on the external boundary for the domain $D_{\Omega_1}$.
+The implementation used the first observation as initial conditions of Eq.\ref{Eq::PDE}.
+Then for each timestep, the next observation was used as the initial value for boundary control $g$.
+The boundary control was imposed on the external boundary for the domain $D_{\Omega_1}$.
 
-Each observations $u_{obs}$ have a fixed time-point $t_i$, these time-points may not overlap with the time discretization in the forward problem.
+The observations $u_{obs}$ have a fixed time-point $t_i$, these time-points may not overlap with the time discretization in the forward problem $t_j$.
 Therefore, after each time step $dt$ in Eq\ref{Eq::PDE}, it was checked if the time step contained the next observation.
-If it did, then a linear interpolation of the current solution $u_{obs}(t_i)$ and previous solution $u_{obs}(t_{i-1})$ was used approximate the solution corresponding to $t_i$.
+If it did, then a linear interpolation of the  current solution $u(t_j)$ and previous solution $u(t_{j-1})$ was used approximate the solution at time $t_i$.
 The linear interpolation was given as
@@
 \label{observation:interpolation}
-u_{obs}(t) = \frac{\Delta t}{dt} u_{obs}(t_i) + \frac{dt - \Delta t }{dt} u_{obs}(t_{i-1}), \quad t \in \lbrace t-dt, t \rbrace
+u(t_i) \approx \frac{\Delta t}{dt} u(t_{j-1}) + \frac{dt - \Delta t }{dt} u(t_{j}), \quad t_i \in \lbrace t_{j-1}, t_j \rbrace
 \end{equation}
-with $\Delta t = t-t_i $.  \kam{Check this formula}
+with $\Delta t = t_k-t_i $.
 
-The initial values of the diffusion coefficients in the optimization algorithm $(D_{CSF}, D_{GM}, D_{WM}) = (1000, 1, 1)$. 
+The initial values of the diffusion coefficients in the optimization algorithm $(D_{CSF}, D_{GM}, D_{WM})=$  $(1, 1, 1)$. However, to increase the convergence rate, $D_{CSF}$ was scaled with $100$. 
 The noise susceptibility was tested by adding an uniform distribution noise term to the observations.
@@
 
+This work was performed on the Abel Cluster, owned by the University of Oslo and Uninett\textbackslash Sigma2, and operated by the Department for Research Computing at USIT,the University of Oslo IT-department.
+\url{http://www.hpc.uio.no/}
 \subsection*{Contrast concentration - Image Intensity Relation}
@@
 seen in Figures \ref{fig1} and \ref{fig2} and the underlying contrast 
-concentration. We remark that we use a notation common in medical literature and 
-here two letter symbols are common. Hence, below we will use two letter symbols such 
-as $TE$ and $SI$ to keep the notation consistent the presentation of (reference XXXX).   
-The tracer causes the longitudinal(spin-lattice) relaxation time $T_{1}$ to shorten with the following relation
+concentration.
+We remark that we use a notation common in medical literature and here two letter symbols are common.
+Hence, below we will use two letter symbols such as $TE$ and $TR$ to keep the notation consistent the presentation of (reference \cite{GOWLAND}, \cite{MPRAGE}).
+The tracer concentration $c$ causes the longitudinal(spin-lattice) relaxation time $T_{1}$ to shorten with the following relation
 \begin{equation}
-\frac{1}{T_{1}\sp{c}} = \frac{1}{T_{1}\sp{0}} + r_{1}C .
+\frac{1}{T_{1}\sp{c}} = \frac{1}{T_{1}\sp{0}} + r_{1}c .
 \label{EQ::contrast}
@@
 The relation between intensity and the relaxation time is non-linear, and is expressed with the following equations.
-The signal intensity $SI$ of the sequence is given by
+The signal intensity $S$ of the sequence is given by
 \begin{equation}
-SI = M_{n} \sin \theta e\sp{ - TE/T_2\sp{*} },
+S = M_{n} \sin \theta e\sp{ - TE/T_2\sp{*} },
 \label{EQ::SI_T2}
@@
 with $TE$ and $\theta$ respectively denoting the echo time and the flip angle, and $M_{n}$ the magnetization for the n-echo described below. 
-Also $T2\sp{*}$ is transverse magnetization caused by a combination of spin-spin relaxation and magnetic field inhomogeneity. It is defined as 
+Also $T_2\sp{*}$ is transverse magnetization caused by a combination of spin-spin relaxation and magnetic field inhomogeneity. It is defined as 
 \begin{equation}
@@
 \end{equation}
-with $T2$ transverse (spin-spin) relaxation time, $\gamma$ is the gyromagnetic ratio and $\Delta B_{in}$ is the magnetic field inhomogeneity across a voxel.
-The expression can be simplified by neglecting the $T2$ term in the signal, since $TE <<T_2\sp{*}$ for this MRI sequence.
+with $T_2$ transverse (spin-spin) relaxation time, $\gamma$ is the gyromagnetic ratio and $\Delta B_{in}$ is the magnetic field inhomogeneity across a voxel.
+The expression can be simplified by neglecting the $T_2$ term in the signal, since $TE <<T_2\sp{*}$ for this MRI sequence.
 Thus Eq.
@@
 \begin{equation}
-SI = M_{n} \sin \theta.
+S = M_{n} \sin \theta.
 \label{EQ::SI}
@@
 The $M_0$ is a calibration constant of the magnetization.
-The center echo denoted as $n=\sp{m}/_2$ will be the signal that we will consider when estimating MRI-contrast.
+The center echo denoted as $n=m/2$ will be the signal that we will consider when estimating MRI-contrast.
 Given Eq.\ref{EQ::SI} we have that relative intensity increase can be written as
 \begin{equation}
-\frac{SI\sp{c}}{SI\sp{0}} = \frac{ M_{n}\sp{c} \sin (\theta)}{ M_{n}\sp{0} \sin (\theta) } ,
+\frac{S\sp{c}}{S\sp{0}} = \frac{ M_{n}\sp{c} \sin (\theta)}{ M_{n}\sp{0} \sin (\theta) } ,
 \end{equation}
@@
 \begin{equation}
-\frac{f(T_{1}\sp{c} ) }{f(T_{1}\sp{0})}  = \frac{SI\sp{c}}{SI\sp{0}} 
+\frac{f(T_{1}\sp{c} ) }{f(T_{1}\sp{0})}  = \frac{S\sp{c}}{S\sp{0}} 
 \end{equation}
-The difference in $S_0$ between observation times were adjusted in \cite{eidevalnes}.  
-Thus we can express the $T_1$ change due to contrast as 
+The difference in the calibraiton constant $M_0$ between observation times were adjusted in \cite{eidevalnes}. Thus we can express the $T_1$ change due to contrast as 
 \begin{equation}
-f ( T_{1}\sp{c} ) = \frac{SI\sp{c}}{SI\sp{0}} f(T_{1}\sp{0}) 
+f ( T_{1}\sp{c} ) = \frac{S\sp{c}}{S\sp{0}} f(T_{1}\sp{0}) 
 \end{equation}
@@
 the right-most image in Figure~\ref{FIG:DTI} and that these images shows the apparent diffusion coefficient for free water molecules (18 Da).      
-The diffusivity of the Gadovist (600 Da cite?) was estimated to be similar to the diffusion coefficient of Gd-DPTA (550 Da cite ?).
+The diffusivity of the Gadovist (600 Da \cite{MGadobutrol}) was estimated to be similar to the diffusion coefficient of Gd-DPTA (550 Da \cite{MGgDPTA}).
 This due to the fact that both molecules have similar mass/size, and based Stoke-Einstein equation should have similar diffusion coefficients.
-The free diffusion coefficient for Gd-DPTA  3.8e-5$\mathrm{mm\sp{2}/s}$ was obtained from [cite].
+The free diffusion coefficient for Gd-DPTA was estimated in \cite{GdDPTA-DIFFUSION} to be 3.8e-4$\mathrm{mm\sp{2}/s}$.
 
@@
 \begin{equation}
-FA\sp{2} = \frac{ 3(\lambda_1 - MD )\sp{2} +(\lambda_2 - MD )\sp{2} +(\lambda_3 - MD )\sp{2}}{2\lambda\sp{2}_1 + \lambda\sp{2}_2  +\lambda\sp{2}_3 },
+FA\sp{2} =  \frac{3}{2} \frac{ (\lambda_1 - MD )\sp{2} +(\lambda_2 - MD )\sp{2} +(\lambda_3 - MD )\sp{2}}{\lambda\sp{2}_1 + \lambda\sp{2}_2  +\lambda\sp{2}_3 },
 \end{equation}
@@
 \end{equation}  
-The magnitude order of the diffusion coefficient are chosen so that they resemble diffusion coefficient in CSF, grey and white matter.
+The magnitude order for $\quad D_{\Omega_2} $ and $\quad D_{\Omega_2}$ were chosen to resemble diffusion coefficient for water in grey and white matter, but the relation between the coeffieicents were not preserved.
+The diffusion coefficent in the csf was chosen given [cite Bryne and Kent].
 The manufactured forward computation gave a total of 120 possible observation time points.
-These points
-will be denoted as $t_i$.
+These points will be denoted as $t_i$.
 
@@
 The software Freesurfer was used in segmentation and creating the polyhedral surfaces of the white and grey matter.
-Then the use of T2 weighted MRI was used to segment the CSF compartment surrounding the cerebral.
+Then the use of T2 weighted MRI was used to segment the CSF compartment surrounding the cerebral and the lateral ventricles.
 The module BrainMesh (currently in testing) (BrainMesh code accessibility {\color{red} kan ta med eller bare si CGAL}) CGAL \cite{cgal:rty-m3-18b} was used to combine the polyhedral surfaces and to construed the mesh.
@@
 \section{Results}
-Below we will discuss the parameter identification and its sensitivity with respect to 
-regularization parameters, noise and time-resolution. 
+Below we will discuss the parameter identification and its sensitivity with respect to regularization parameters, noise and time-resolution. 
 In presentation of the results, the relative error norm  $||\cdot||_{RE}$ is defined as 
@@
 \subsection{The relaxation parameters}
-To assess the sensitivity of the the objective functional defined in \ref{Eq::F} with respect to the regularization parameters $\alpha$ and $\beta$ 
+To assess the sensitivity of the the objective functional defined in Eq.\ref{Eq::F} with respect to the regularization parameters $\alpha$ and $\beta$ 
 we perform a systematic study of the reconstruction of the manufactured solution with respect to a wide range of regularization parameters. 
@@
 C)Shows the manufactures observation at time-point 24 with noise amplitude of 0.3.
-The lower row shows the results with optimized parameter obtained with $alpha=0.0001$, $\beta=1.0$ and $k=27$.
+The lower row shows the results with optimized parameter obtained with $\alpha=0.0001$, $\beta=1.0$ and $k=27$.
 D) Shows the resulting state given the observation in A.
@@
 \caption{The upper row shows the manufactured observation, A ) Shows the manufactured observation at time-point 24 with no noise added.
-B) Shows the manufactured observation at time-point 24 with a noise amplitude of 0.15 {\color{red} explain noise ampliutde}.
+B) Shows the manufactured observation at time-point 24 with a noise amplitude of 0.15.
 C)Shows the manufactures observation at time-point 24 with noise amplitude of 0.3.
-The lower row shows the results with optimized parameter obtained with $alpha=0.0001$, $\beta=1.0$ and $k=27$.
+The lower row shows the results with optimized parameter obtained with $\alpha=0.0001$, $\beta=1.0$ and $k=27$.
 D) Shows the resulting state given the observation in A.
@@
 The MRI data consisted of the observations at times $t_i \in \lbrace$ 0.00, 0.16, 0.39, 0.55, 0.77, 2.09, 6.05, 24.06, 47.84, 698.02 $\rbrace (hours)$ with the time $t_i=0.00$ as the observation 1-2 hours after the tracer was injected.
-There was no significant visible change in the tracer between the observations at $\lbrace 0.00 0.16, 0.39, 0.55, 0.77 \rbrace$.
-This prompted the use of the following observation times  $0.00 2.09, 6.05, 24.06, 47.84$.
+There was no significant visible change in the tracer between the observations at $\lbrace $ 0.00, 0.16, 0.39, 0.55, 0.77 $ \rbrace$.
+This prompted the use of the following observation times  $0.00, 2.09, 6.05, 24.06, 47.84$.
 
@@
 
-The reference value of Gd-DPTA was reported to be 3.8e-4 $\mathrm{mm\sp{2}/s}$ in [insert citation].
-The values in Tab.\ref{Tab::Real-data} gives the value-range $1.5e-4 -2.7e-4\mathrm{mm\sp{2}/s}  $ for the grey diffusion coefficient and  $2.2e-4 - 3.3e-4\mathrm{mm\sp{2}/s}$ for the white diffusion coefficient.
+The reference value for Gd-DPTA was set to 3.8e-4 $\mathrm{mm\sp{2}/s}$.
+The values in Tab.\ref{Tab::Real-data} gives the value-range $1.5e-4 -2.7e-4\mathrm{mm\sp{2}/s}$ for the grey diffusion coefficient and  $2.2e-4 - 3.3e-4\mathrm{mm\sp{2}/s}$ for the white diffusion coefficient.
 These values are $20 -110 \%$ larger than the expected values for $D_{g}$,  and $100 - 200 \%$ larger than the expected values for $D_{w}$.
@@
 \subsection{Manufactures Solution}
-The results from the manufactured solutions showed a robust method to compute diffusion coefficients.
-
+%The results from the manufactured solutions showed a robust method to compute diffusion coefficients. However, the maufactured solutions were constructed .. ? .. .
 The computational model assumes isotropic diffusivity, but the anisotropy in the white matter is well documented, as shown by the FA in Fig\ref{FIG::DTI}.
@@
 A more important factor are regions with higher diffusivity.
-In Fig.\ref{FIG::DTI}, it can be observed that the region with high diffusivity also have a high tracer concentration, see Fig \ref{Fig::realdata}.
+Comparing Fig.\ref{FIG::DTI} and Fig \ref{Fig::realdata}, it can be observed that the region with high diffusivity also have a high tracer concentration.
 
-The computational have 2 global controls for the diffusion coefficients, while it can be seen in  Fig.\ref{FIG::DTI} that diffusion coefficients can be considered a spacial function.
+The computational model have 2 global controls for the diffusion coefficients, while it can be seen in  Fig.\ref{FIG::DTI} that diffusion coefficients can be considered a spacial function.
+Although the implmentaion of spacial control parameters are possible, it would siginificantly increase the computational cost.
+
+The coputational cost dependes on the relaxation parameteres, the number of controls and solution of the PDE.
 
@@
 This follows the assumption that the clearance is related to diffusion, which means an increase in diffusivity.
-Since the properties of the tracer molecule do not change, this would mean that the tortuosity decreased, and subsequently increase the value of the ADC.
+Since the properties of the tracer molecule do not change, this would mean that the tortuosity decreased and followed by an incearse in the ADC.
 
@@
 This can be caused by the boundary control $g$, which exists along the entire boundary of the grey matter.
-Considering the that the grey matter volume has a depth less than 5 mm makes it susceptible to changes in $g$.
-Therefore this seems likely, given the fact that both relaxation parameters are used to adjust the boundary control.
+Considering the that the grey matter volume has a depth less than 3 mm makes it susceptible to changes in $g$.
+This can be observed in the reconstruction in Fig.\ref{12hourswithnoise} and Fig.\ref{24hourswithnoise}, where the nosie is present at the boundary.
+
+Furthermore. in Fig.?? it was shown that the
 
@@
 
+\bibliographystyle{amsplain}
+\bibliography{references}
+
 \newpage 
 \newgeometry{top=0.5cm}
-
- \begin{table}
-\centering
-\caption{Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$, the resulting number of iterations, the estimated diffusion coefficients for grey $D_g$ and white $D_w$ matter based on MRI data.}
-\resizebox{\textwidth}{!}{\begin{tabular}{*{6}c}
-$\alpha$ & $\beta$ & k & iter &  $ D_{g} \left[ \mathrm{mm\sp{2}/h} \right] $ & $ D_{w} \left[ \mathrm{mm\sp{2}/h} \right]$ \\
-\hline
- 1.0e-02 	 & 1.0e+00 	 & 48 & 591 	 & 0.648 & 0.893 \\ 
- 1.0e-02 	 & 1.0e-01 	 & 48 & 461 	 & 0.772 & 0.982 \\ 
- 1.0e-02 	 & 1.0e-02 	 & 48 & 748 	 & 0.986 & 1.198 \\ 
- 1.0e-04 	 & 1.0e+00 	 & 48 & 607 	 & 0.551 & 0.815 \\ 
- 1.0e-04 	 & 1.0e-01 	 & 48 & 598 	 & 0.649 & 0.787 \\ 
- 1.0e-04 	 & 1.0e-02 	 & 48 & 837 	 & 0.740 & 0.817 \\ 
- 1.0e-06 	 & 1.0e+00 	 & 48 & 681 	 & 0.557 & 0.811 \\ 
- 1.0e-06 	 & 1.0e-01 	 & 48 & 780 	 & 0.645 & 0.774 \\ 
- 1.0e-06 	 & 1.0e-02 	 & 48 & 745 	 & 0.736 & 0.819 \\
-
-\end{tabular}}
-\label{Tab::Real-data}
-\end{table}
 
@@
 \hline
-\rowcolor{red}  1.0e+00 	 & 1.0e+00 	 & 10 & 225 	 & +4.148 & +0.304 & +0.092 & +0.135 \\ 
+  1.0e+00 	 & 1.0e+00 	 & 10 & 225 	 & +4.148 & +0.304 & +0.092 & +0.135 \\ 
 %\rowcolor{red}  1.0e+00 	 & 1.0e-01 	 & 10 & 206 	 & +4.272 & +0.305 & +0.091 & +0.142 \\ 
-\rowcolor{red}  1.0e+00 	 & 1.0e-02 	 & 10 & 233 	 & +4.272 & +0.305 & +0.091 & +0.143 \\ 
+ 1.0e+00 	 & 1.0e-02 	 & 10 & 233 	 & +4.272 & +0.305 & +0.091 & +0.143 \\ 
 %\rowcolor{red}  1.0e+00 	 & 1.0e-03 	 & 10 & 208 	 & +4.437 & +0.305 & +0.091 & +0.143 \\ 
-\rowcolor{red}  1.0e+00 	 & 1.0e-04 	 & 10 & 204 	 & +4.271 & +0.306 & +0.091 & +0.143 \\ 
+ 1.0e+00 	 & 1.0e-04 	 & 10 & 204 	 & +4.271 & +0.306 & +0.091 & +0.143 \\ 
 %\rowcolor{red}  1.0e+00 	 & 1.0e-05 	 & 10 & 203 	 & +4.400 & +0.305 & +0.091 & +0.143 \\ 
-\rowcolor{red}  1.0e+00 	 & 1.0e-06 	 & 10 & 222 	 & +4.584 & +0.304 & +0.090 & +0.143 \\
+ 1.0e+00 	 & 1.0e-06 	 & 10 & 222 	 & +4.584 & +0.304 & +0.090 & +0.143 \\
 
- 1.0e-01 	 & 1.0e+00 	 & 10 & 207 	 & +0.127 & +0.093 & +0.041 & +0.027 \\ 
+% 1.0e-01 	 & 1.0e+00 	 & 10 & 207 	 & +0.127 & +0.093 & +0.041 & +0.027 \\ 
  %1.0e-01 	 & 1.0e-01 	 & 10 & 196 	 & +0.121 & +0.093 & +0.041 & +0.046 \\ 
- 1.0e-01 	 & 1.0e-02 	 & 10 & 232 	 & +0.123 & +0.093 & +0.041 & +0.056 \\ 
+% 1.0e-01 	 & 1.0e-02 	 & 10 & 232 	 & +0.123 & +0.093 & +0.041 & +0.056 \\ 
  %1.0e-01 	 & 1.0e-03 	 & 10 & 183 	 & +0.122 & +0.093 & +0.040 & +0.057 \\ 
- 1.0e-01 	 & 1.0e-04 	 & 10 & 212 	 & +0.122 & +0.093 & +0.040 & +0.057 \\ 
+% 1.0e-01 	 & 1.0e-04 	 & 10 & 212 	 & +0.122 & +0.093 & +0.040 & +0.057 \\ 
  %1.0e-01 	 & 1.0e-05 	 & 10 & 168 	 & +0.122 & +0.093 & +0.041 & +0.057 \\
- 1.0e-01 	 & 1.0e-06 	 & 10 & 195 	 & +0.122 & +0.093 & +0.041 & +0.057 \\
+% 1.0e-01 	 & 1.0e-06 	 & 10 & 195 	 & +0.122 & +0.093 & +0.041 & +0.057 \\
 
@@
 
- 1.0e-03 	 & 1.0e+00 	 & 10 & 179 	 & +0.004 & +0.064 & +0.039 & +0.019 \\ 
+ %1.0e-03 	 & 1.0e+00 	 & 10 & 179 	 & +0.004 & +0.064 & +0.039 & +0.019 \\ 
  %1.0e-03 	 & 1.0e-01 	 & 10 & 221 	 & -0.005 & +0.063 & +0.039 & +0.018 \\ 
- 1.0e-03 	 & 1.0e-02 	 & 10 & 89 	 & -0.007 & +0.063 & +0.039 & +0.026 \\ 
+ %1.0e-03 	 & 1.0e-02 	 & 10 & 89 	 & -0.007 & +0.063 & +0.039 & +0.026 \\ 
  %1.0e-03 	 & 1.0e-03 	 & 10 & 77 	 & -0.005 & +0.062 & +0.039 & +0.027 \\ 
- 1.0e-03 	 & 1.0e-04 	 & 10 & 100 	 & -0.006 & +0.062 & +0.039 & +0.027 \\ 
+ %1.0e-03 	 & 1.0e-04 	 & 10 & 100 	 & -0.006 & +0.062 & +0.039 & +0.027 \\ 
  %1.0e-03 	 & 1.0e-05 	 & 10 & 105 	 & -0.006 & +0.062 & +0.039 & +0.027 \\ 
- 1.0e-03 	 & 1.0e-06 	 & 10 & 123 	 & -0.007 & +0.062 & +0.039 & +0.028 \\
+ %1.0e-03 	 & 1.0e-06 	 & 10 & 123 	 & -0.007 & +0.062 & +0.039 & +0.028 \\
 
@@
 
- 1.0e-05 	 & 1.0e+00 	 & 10 & 139 	 & +0.004 & +0.063 & +0.039 & +0.019 \\ 
+ %1.0e-05 	 & 1.0e+00 	 & 10 & 139 	 & +0.004 & +0.063 & +0.039 & +0.019 \\ 
  %1.0e-05 	 & 1.0e-01 	 & 10 & 170 	 & -0.006 & +0.062 & +0.039 & +0.018 \\ 
- 1.0e-05 	 & 1.0e-02 	 & 10 & 182 	 & -0.007 & +0.062 & +0.039 & +0.020 \\ 
+ %1.0e-05 	 & 1.0e-02 	 & 10 & 182 	 & -0.007 & +0.062 & +0.039 & +0.020 \\ 
  %1.0e-05 	 & 1.0e-03 	 & 10 & 70 	 & -0.007 & +0.062 & +0.039 & +0.026 \\ 
- 1.0e-05 	 & 1.0e-04 	 & 10 & 77 	 & -0.007 & +0.062 & +0.039 & +0.026 \\ 
+ %1.0e-05 	 & 1.0e-04 	 & 10 & 77 	 & -0.007 & +0.062 & +0.039 & +0.026 \\ 
  %1.0e-05 	 & 1.0e-05 	 & 10 & 104 	 & -0.008 & +0.062 & +0.039 & +0.026 \\ 
- 1.0e-05 	 & 1.0e-06 	 & 10 & 92 	 & -0.007 & +0.062 & +0.039 & +0.026 \\
+ %1.0e-05 	 & 1.0e-06 	 & 10 & 92 	 & -0.007 & +0.062 & +0.039 & +0.026 \\
 
@@
 
- 1.0e-01 	 & 1.0e+00 	 & 10 & 167 	 & +0.131 & +0.093 & +0.041 & +0.027 \\ 
+ %1.0e-01 	 & 1.0e+00 	 & 10 & 167 	 & +0.131 & +0.093 & +0.041 & +0.027 \\ 
 % 1.0e-01 	 & 1.0e-01 	 & 10 & 195 	 & +0.125 & +0.093 & +0.039 & +0.046 \\ 
- 1.0e-01 	 & 1.0e-02 	 & 10 & 218 	 & +0.126 & +0.093 & +0.040 & +0.056 \\ 
+% 1.0e-01 	 & 1.0e-02 	 & 10 & 218 	 & +0.126 & +0.093 & +0.040 & +0.056 \\ 
 % 1.0e-01 	 & 1.0e-03 	 & 10 & 161 	 & +0.129 & +0.094 & +0.040 & +0.057 \\ 
- 1.0e-01 	 & 1.0e-04 	 & 10 & 180 	 & +0.135 & +0.092 & +0.042 & +0.057 \\ 
+% 1.0e-01 	 & 1.0e-04 	 & 10 & 180 	 & +0.135 & +0.092 & +0.042 & +0.057 \\ 
 % 1.0e-01 	 & 1.0e-05 	 & 10 & 169 	 & +0.123 & +0.093 & +0.041 & +0.057 \\ 
- 1.0e-01 	 & 1.0e-06 	 & 10 & 201 	 & +0.119 & +0.093 & +0.040 & +0.057 \\
+% 1.0e-01 	 & 1.0e-06 	 & 10 & 201 	 & +0.119 & +0.093 & +0.040 & +0.057 \\
 
@@
 
- 1.0e-03 	 & 1.0e+00 	 & 10 & 183 	 & +0.007 & +0.062 & +0.038 & +0.019 \\ 
-%1.0e-03 	 & 1.0e-01 	 & 10 & 181 	 & -0.011 & +0.063 & +0.039 & +0.019 \\ 
- 1.0e-03 	 & 1.0e-02 	 & 10 & 122 	 & -0.008 & +0.063 & +0.040 & +0.025 \\ 
+% 1.0e-03 	 & 1.0e+00 	 & 10 & 183 	 & +0.007 & +0.062 & +0.038 & +0.019 \\ 
+% 1.0e-03 	 & 1.0e-01 	 & 10 & 181 	 & -0.011 & +0.063 & +0.039 & +0.019 \\ 
+% 1.0e-03 	 & 1.0e-02 	 & 10 & 122 	 & -0.008 & +0.063 & +0.040 & +0.025 \\ 
 % 1.0e-03 	 & 1.0e-03 	 & 10 & 158 	 & -0.004 & +0.062 & +0.040 & +0.028 \\ 
- 1.0e-03 	 & 1.0e-04 	 & 10 & 168 	 & -0.013 & +0.063 & +0.038 & +0.029 \\ 
+% 1.0e-03 	 & 1.0e-04 	 & 10 & 168 	 & -0.013 & +0.063 & +0.038 & +0.029 \\ 
 % 1.0e-03 	 & 1.0e-05 	 & 10 & 120 	 & -0.010 & +0.063 & +0.040 & +0.028 \\ 
- 1.0e-03 	 & 1.0e-06 	 & 10 & 132 	 & -0.002 & +0.062 & +0.039 & +0.028 \\
+% 1.0e-03 	 & 1.0e-06 	 & 10 & 132 	 & -0.002 & +0.062 & +0.039 & +0.028 \\
 
@@
 
- 1.0e-05 	 & 1.0e+00 	 & 10 & 220 	 & +0.005 & +0.063 & +0.039 & +0.019 \\ 
+ %1.0e-05 	 & 1.0e+00 	 & 10 & 220 	 & +0.005 & +0.063 & +0.039 & +0.019 \\ 
  %1.0e-05 	 & 1.0e-01 	 & 10 & 193 	 & -0.009 & +0.062 & +0.039 & +0.019 \\ 
- 1.0e-05 	 & 1.0e-02 	 & 10 & 163 	 & -0.013 & +0.063 & +0.039 & +0.021 \\ 
+ %1.0e-05 	 & 1.0e-02 	 & 10 & 163 	 & -0.013 & +0.063 & +0.039 & +0.021 \\ 
  %1.0e-05 	 & 1.0e-03 	 & 10 & 115 	 & -0.007 & +0.063 & +0.040 & +0.026 \\ 
- 1.0e-05 	 & 1.0e-04 	 & 10 & 82 	 & -0.007 & +0.062 & +0.038 & +0.027 \\ 
+ %1.0e-05 	 & 1.0e-04 	 & 10 & 82 	 & -0.007 & +0.062 & +0.038 & +0.027 \\ 
  %1.0e-05 	 & 1.0e-05 	 & 10 & 145 	 & -0.001 & +0.062 & +0.039 & +0.027 \\ 
- 1.0e-05 	 & 1.0e-06 	 & 10 & 147 	 & -0.012 & +0.061 & +0.040 & +0.027 \\
+ %1.0e-05 	 & 1.0e-06 	 & 10 & 147 	 & -0.012 & +0.061 & +0.040 & +0.027 \\
 
@@
  %1.0e-01 	 & 1.0e+00 	 & 10 & 145 	 & +0.126 & +0.100 & +0.054 & +0.035 \\ 
- 1.0e-01 	 & 1.0e-01 	 & 10 & 199 	 & +0.115 & +0.125 & +0.026 & +0.060 \\ 
+ %1.0e-01 	 & 1.0e-01 	 & 10 & 199 	 & +0.115 & +0.125 & +0.026 & +0.060 \\ 
  %1.0e-01 	 & 1.0e-02 	 & 10 & 217 	 & +0.128 & +0.092 & +0.036 & +0.071 \\ 
- 1.0e-01 	 & 1.0e-03 	 & 10 & 242 	 & +0.109 & +0.093 & +0.031 & +0.073 \\ 
+ %1.0e-01 	 & 1.0e-03 	 & 10 & 242 	 & +0.109 & +0.093 & +0.031 & +0.073 \\ 
  %1.0e-01 	 & 1.0e-04 	 & 10 & 275 	 & +0.187 & +0.094 & +0.028 & +0.073 \\ 
- 1.0e-01 	 & 1.0e-05 	 & 10 & 237 	 & +0.048 & +0.099 & +0.039 & +0.073 \\ 
+ %1.0e-01 	 & 1.0e-05 	 & 10 & 237 	 & +0.048 & +0.099 & +0.039 & +0.073 \\ 
  %1.0e-01 	 & 1.0e-06 	 & 10 & 225 	 & +0.092 & +0.111 & +0.055 & +0.073 \\ 
@@
  %1.0e-03 	 & 1.0e+00 	 & 10 & 207 	 & -0.001 & +0.065 & +0.051 & +0.029 \\ 
- 1.0e-03 	 & 1.0e-01 	 & 10 & 280 	 & +0.028 & +0.051 & +0.053 & +0.038 \\ 
+% 1.0e-03 	 & 1.0e-01 	 & 10 & 280 	 & +0.028 & +0.051 & +0.053 & +0.038 \\ 
  %1.0e-03 	 & 1.0e-02 	 & 10 & 565 	 & -0.059 & +0.076 & +0.033 & +0.053 \\ 
- \rowcolor{orange} 1.0e-03 	 & 1.0e-03 	 & 10 & 673 	 & -0.035 & +0.066 & +0.032 & +0.108 \\ 
+% 1.0e-03 	 & 1.0e-03 	 & 10 & 673 	 & -0.035 & +0.066 & +0.032 & +0.108 \\ 
  %\rowcolor{orange} 1.0e-03 	 & 1.0e-04 	 & 10 & 604 	 & -0.026 & +0.061 & +0.049 & +0.182 \\ 
- \rowcolor{orange} 1.0e-03 	 & 1.0e-05 	 & 10 & 666 	 & +0.012 & +0.070 & +0.038 & +0.182 \\ 
+ %1.0e-03 	 & 1.0e-05 	 & 10 & 666 	 & +0.012 & +0.070 & +0.038 & +0.182 \\ 
  %\rowcolor{orange} 1.0e-03 	 & 1.0e-06 	 & 10 & 893 	 & +0.027 & +0.070 & +0.022 & +0.180 \\ 
@@
 %\rowcolor{orange} 1.0e-04 	 & 1.0e-03 	 & 10 & 691 	 & -0.023 & +0.055 & +0.040 & +0.175 \\ 
-\rowcolor{red}  1.0e-04 	 & 1.0e-04 	 & 10 & 1001 	 & -0.012 & +0.066 & +0.030 & +0.745 \\ 
+ 1.0e-04 	 & 1.0e-04 	 & 10 & -	 & -0.012 & +0.066 & +0.030 & +0.745 \\ 
 %\rowcolor{red}  1.0e-04 	 & 1.0e-05 	 & 10 & 1001 	 & +0.038 & +0.057 & +0.034 & +1.113 \\ 
-\rowcolor{red} 1.0e-04 	 & 1.0e-06 	 & 10 & 1001 	 & +0.015 & +0.063 & +0.035 & +1.127 \\ 
+1.0e-04 	 & 1.0e-06 	 & 10 & -	 & +0.015 & +0.063 & +0.035 & +1.127 \\ 
 % 1.0e-05 	 & 1.0e+00 	 & 10 & 184 	 & -0.025 & +0.076 & +0.041 & +0.029 \\ 
- 1.0e-05 	 & 1.0e-01 	 & 10 & 357 	 & -0.011 & +0.070 & +0.052 & +0.038 \\ 
+ %1.0e-05 	 & 1.0e-01 	 & 10 & 357 	 & -0.011 & +0.070 & +0.052 & +0.038 \\ 
 % 1.0e-05 	 & 1.0e-02 	 & 10 & 399 	 & +0.041 & +0.075 & +0.042 & +0.049 \\ 
- \rowcolor{orange} 1.0e-05 	 & 1.0e-03 	 & 10 & 689 	 & +0.044 & +0.062 & +0.020 & +0.172 \\ 
+%1.0e-05 	 & 1.0e-03 	 & 10 & 689 	 & +0.044 & +0.062 & +0.020 & +0.172 \\ 
 %\rowcolor{red} 1.0e-05 	 & 1.0e-04 	 & 10 & 915 	 & +0.030 & +0.077 & +0.039 & +1.027 \\ 
-\rowcolor{red} 1.0e-05 	 & 1.0e-05 	 & 10 & 1001 	 & +0.017 & +0.061 & +0.045 & +1.953 \\ 
-%\rowcolor{red}  1.0e-05 	 & 1.0e-06 	 & 10 & 1001 	 & -0.018 & +0.071 & +0.045 & +2.545 \\ 
+ %1.0e-05 	 & 1.0e-05 	 & 10 & - 	 & +0.017 & +0.061 & +0.045 & +1.953 \\ 
+%\rowcolor{red}  1.0e-05 	 & 1.0e-06 	 & 10 & - 	 & -0.018 & +0.071 & +0.045 & +2.545 \\ 
  1.0e-06 	 & 1.0e+00 	 & 10 & 177 	 & +0.060 & +0.069 & +0.039 & +0.029 \\ 
@@
 %\rowcolor{orange} 1.0e-06 	 & 1.0e-03 	 & 10 & 738 	 & -0.022 & +0.055 & +0.042 & +0.172 \\ 
-\rowcolor{red}  1.0e-06 	 & 1.0e-04 	 & 10 & 1001 	 & -0.043 & +0.042 & +0.054 & +1.180 \\ 
+ 1.0e-06 	 & 1.0e-04 	 & 10 & -	 & -0.043 & +0.042 & +0.054 & +1.180 \\ 
 %\rowcolor{red}  1.0e-06 	 & 1.0e-05 	 & 10 & 1001 	 & +0.006 & +0.052 & +0.033 & +3.365 \\ 
-\rowcolor{red}  1.0e-06 	 & 1.0e-06 	 & 10 & 1001 	 & -0.002 & +0.065 & +0.051 & +3.402 \\ 
+ 1.0e-06 	 & 1.0e-06 	 & 10 & 1001 	 & -0.002 & +0.065 & +0.051 & +3.402 \\ 
 \end{tabular}}
@@
  1.0e-04 	 & 1.0e-02 	 & 40 & 339 	 & +0.004 & +0.002 & +0.002 & +0.003 \\   
- 1.0e-05 	 & 1.0e+00 	 & 20 & 237 	 & -0.006 & +0.004 & +0.013 & +0.008 \\ 
- 1.0e-05 	 & 1.0e+00 	 & 40 & 358 	 & -0.018 & -0.019 & +0.005 & +0.007 \\  
+% 1.0e-05 	 & 1.0e+00 	 & 20 & 237 	 & -0.006 & +0.004 & +0.013 & +0.008 \\ 
+ %1.0e-05 	 & 1.0e+00 	 & 40 & 358 	 & -0.018 & -0.019 & +0.005 & +0.007 \\  
  %1.0e-05 	 & 1.0e-01 	 & 20 & 290 	 & +0.026 & +0.010 & +0.008 & +0.007 \\
  %1.0e-05 	 & 1.0e-01 	 & 40 & 419 	 & +0.001 & -0.007 & +0.004 & +0.005 \\    
- 1.0e-05 	 & 1.0e-02 	 & 20 & 316 	 & +0.071 & +0.025 & +0.005 & +0.007 \\ 
- 1.0e-05 	 & 1.0e-02 	 & 40 & 401 	 & +0.004 & +0.003 & +0.002 & +0.004 \\  
+ %1.0e-05 	 & 1.0e-02 	 & 20 & 316 	 & +0.071 & +0.025 & +0.005 & +0.007 \\ 
+ %1.0e-05 	 & 1.0e-02 	 & 40 & 401 	 & +0.004 & +0.003 & +0.002 & +0.004 \\  
  1.0e-06 	 & 1.0e+00 	 & 20 & 219 	 & -0.007 & +0.004 & +0.013 & +0.008 \\ 
@@
  1.0e-05 	 & 1.0e-01 	 & 40 & 688 	 & -0.033 & -0.015 & -0.025 & +0.045 \\ 
-? 1.0e-05 	 & 1.0e-02 	 & 40 & 566 	 & -0.053 & -0.020 & -0.027 & +0.098 \\
+ 1.0e-05 	 & 1.0e-02 	 & 40 & 566 	 & -0.053 & -0.020 & -0.027 & +0.098 \\
  1.0e-06 	 & 1.0e+00 	 & 40 & 517 	 & -0.005 & -0.016 & -0.021 & +0.053 \\ 
@@
 
-\bibliographystyle{amsplain}
-\bibliography{references}
+\begin{table}
+\centering
+\caption{Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$, the resulting number of iterations, the estimated diffusion coefficients for grey $D_g$ and white $D_w$ matter based on MRI data.}
+\resizebox{\textwidth}{!}{\begin{tabular}{*{6}c}
+$\alpha$ & $\beta$ & k & iter &  $ D_{g} \left[ \mathrm{mm\sp{2}/h} \right] $ & $ D_{w} \left[ \mathrm{mm\sp{2}/h} \right]$ \\
+\hline
+ 1.0e-02 	 & 1.0e+00 	 & 48 & 591 	 & 0.648 & 0.893 \\ 
+ 1.0e-02 	 & 1.0e-01 	 & 48 & 461 	 & 0.772 & 0.982 \\ 
+ 1.0e-02 	 & 1.0e-02 	 & 48 & 748 	 & 0.986 & 1.198 \\ 
+ 1.0e-04 	 & 1.0e+00 	 & 48 & 607 	 & 0.551 & 0.815 \\ 
+ 1.0e-04 	 & 1.0e-01 	 & 48 & 598 	 & 0.649 & 0.787 \\ 
+ 1.0e-04 	 & 1.0e-02 	 & 48 & 837 	 & 0.740 & 0.817 \\ 
+ 1.0e-06 	 & 1.0e+00 	 & 48 & 681 	 & 0.557 & 0.811 \\ 
+ 1.0e-06 	 & 1.0e-01 	 & 48 & 780 	 & 0.645 & 0.774 \\ 
+ 1.0e-06 	 & 1.0e-02 	 & 48 & 745 	 & 0.736 & 0.819 \\
+
+\end{tabular}}
+\label{Tab::Real-data}
+\end{table}
 

### 2018-10-16 tex/paper.tex
text corrections
new figures and text

@@
 Figure~\ref{fig2} shows the slice selected for our computations. 
-The software Freesurfer was used to segment and align each of the observations, which made it possible to estimate voxelwise intensity increase.
+The software Freesurfer {\color{red} citation needed, Hvilken ? } was used to segment and align each of the observations, which made it possible to estimate voxelwise intensity increase.
 
@@
 The module dolfin adjoint ~\cite{farrell2013automated} \kam{correct ref?} was used to solve the PDE constrained optimization problem with the L-BFGS-B algorithm in the python module scipy.
-The convergence criteria for the minimization was set so that $max\lbrace | proj x_i | , \quad i = 1, .., N \rbrace \leq gtol=1.0e-1$ where $ proj x_i$ is the i-th component of the projected gradient.
-{\color{red} see scipy }.
-
-The implementation used the first observation as initial conditions of Eq.\ref{Eq::PDE}.
-Then for each timestep, the next observation was used as the initial value for boundary control $g$.
-The boundary control was imposed on the external boundary for the domain $D_{\Omega_1}$.
+The convergence criteria for the minimization was set so that $max \lbrace | \text{proj} \hspace*{0.2cm} x_i | , \quad i = 1, .., N \rbrace \leq gtol=1.0e-1$ where $x_i$ is the i-th component of the gradient.
+{\color{red} From scipy :The iteration will stop when $max\lbrace | \text{proj} \hspace*{0.2cm} g_i | , \quad i = 1, .., N \rbrace \leq gtol $  where $pg_i$ is the i-th component of the projected gradient.}
 
@@
 \end{equation}
-with $\Delta t = t_k-t_i $.
+with $\Delta t = t_j-t_i$.
 
-The initial values of the diffusion coefficients in the optimization algorithm $(D_{CSF}, D_{GM}, D_{WM})=$  $(1, 1, 1)$. However, to increase the convergence rate, $D_{CSF}$ was scaled with $100$. 
+The implementation used the first observation as initial conditions of Eq.\ref{Eq::PDE}.
+Then for each timestep, the next observation was used as the initial value for boundary control $g$, which was imposed on the external boundary of the domain $\Omega_1$.
+The initial values of the diffusion coefficients in the optimization algorithm $(D_{CSF}, D_{GM}, D_{WM})=$  $(1, 1, 1)$.
+However, to increase the convergence rate, $D_{CSF}$ was scaled with $100$.
+
 The noise susceptibility was tested by adding an uniform distribution noise term to the observations.
@@
 \end{equation}
-In article  \cite{MPRAGE}, the term $M_n$ is defined as the magnetization for the n-echo 
+In article \cite{GOWLAND}, the term $M_n$ is defined as the magnetization for the n-echo 
 \begin{equation}
@@
 This makes it possible to  take into account patients specific characteristic, such as tissue damage.
-There are several forms of tissue damage, which can be observed in the MRI due to a lower intensity in the white matter compared to healthy white matter tissue.
-This means that the damaged tissue have a different T1 relaxation time.
+There are several forms of tissue damage that can be observed in the MRI due to a lower intensity in the white matter compared to healthy white matter tissue, hence damaged tissue have different T1 relaxation time.
 
@@
 Thus an additional mesh without the CSF compartment was constructed, see Fig.
-\ref{figmesh}.
+\ref{Fig::Mesh}.
 
@@
 In addition to the T1 and T2 weighted sequences described above we have also obtained diffusion tensor imaging (DTI) to assess the apparent diffusion 
-coefficients on short time-scales. Images are shown in Figure~\ref{FIG:DTI} where the larges diffusion coefficient (shown in 
+coefficients on short time-scales. Images are shown in Figure~\ref{figuredti} where the larges diffusion coefficient (shown in 
 red in the middle figure) is shown to be around 0.001 mm$^2$/s. We remark that we have not included possible anisotropy, shown in 
-the right-most image in Figure~\ref{FIG:DTI} and that these images shows the apparent diffusion coefficient for free water molecules (18 Da).      
+the right-most image in Figure~\ref{figuredti} and that these images shows the apparent diffusion coefficient for free water molecules (18 Da).      
 The diffusivity of the Gadovist (600 Da \cite{MGadobutrol}) was estimated to be similar to the diffusion coefficient of Gd-DPTA (550 Da \cite{MGgDPTA}).
@@
 \includegraphics[width=0.80\textwidth]{DTI-zoom.png} 
-\label{FIG::DTI} 
 \caption{The left panel show the anatomical map.
@@
 The right panel shows the computed fractional anisotropy (FA) from the DTI.}
+\label{figuredti} 
 \end{figure}
@@
 \includegraphics[scale=0.2]{mesh.png} 
-\label{figmesh} 
 \caption{A) Shows the mesh created from the baseline MR image with 3 domains. B) Shows the mesh created from the baseline MR image with 2 domains.  }
@@
 \begin{equation}
-|| X ||_{RE} = \frac{X_{found} -X_{true} }{ X_{true} }
+ X\sp{rel} = \frac{X_{found} -X_{true} }{ X_{true} }
 \end{equation}
@@
 \begin{equation}
-|| g ||_{RE} = \frac{ \sum\limits_t\sp{k}||| g_{found}(t) -g_{true}(t)||_{L(\Omega_1)} }{  \sum\limits_t\sp{k}||g_{true}(t)||_{L(\Omega_1)} }
+|| g ||\sp{rel}_{L\sp{2}(\Omega_1)} = \frac{ \sum\limits_t\sp{k}| g_{found}(t) -g_{true}(t)||_{L(\Omega_1)} }{  \sum\limits_t\sp{k}||g_{true}(t)||_{L(\Omega_1)} }
 \end{equation}
@@
 The results are shown in Tabel~\ref{Tab::1} together with the number of iteration used to reach the convergence criteria.
-For $\alpha= 1.0$, it can be observed that there is a significant relative error for $D_{\Omega_1}$.
-The other control parameters also show an increased relative error when compared to other values of $\alpha$.
+It can be observed that for all $\alpha=1.0$ had significant relative error for $D_{\Omega_1}$, and this can also be observed for all $\beta=100$.
+These parameter selections fails to reconstructed the manufacured solutions, due to $g$ influence on $F$
 
@@
 \centering
-\includegraphics[scale=0.2]{convergence_0}  
-\includegraphics[scale=0.2]{convergence_1}  
-\includegraphics[scale=0.2]{convergence_2}  
-\includegraphics[scale=0.2]{convergence_3}  
-\includegraphics[scale=0.2]{convergence_4}  
+\includegraphics[scale=0.2]{Convergence0}  
+\includegraphics[scale=0.2]{Convergence1}  
+\includegraphics[scale=0.2]{Convergence2}  
+\includegraphics[scale=0.2]{Convergence3}  
+\includegraphics[scale=0.2]{Convergence4}  
 \label{convergence}
 \caption{Convergence of the diffusion coefficients, boundary conditions and functional with respect to different $\alpha$ and $\beta$ values. } 
+\end{figure}
+
+\subsection{The number of timessteps}
+Increasing the number of timesteps in the computations potentially allow for a more accurate temporal reconstruction, but at the same time the number of observations per control decreases and the regularization therefore may play a larger role.
+Furthermore, the computational cost will increases due the number of iterations in the forward problem.
+Therefore finding the number of timesteps for an effective convergence can help for larger meshes.
+The computation used different regularization parameters with 10, 20 and 40 timesteps.
+
+The reults are show in Tab.\ref{TAB::timesteps}, and can be seen that for $\alpha=1.0$ the relative error increases with the number of timesteps.
+While for values $\alpha < 1.0 $, the relative error decreases with increasing number of timesteps.
+
+This prompted to look at the boundary control $g$ through time by selecting high and low values of $\alpha$ and $\beta$, see Fig \ref{boundarycontrol}.
+Figure \ref{boundarycontrol} displays oscillations for $\alpha=1.0$ with $k=40$.
+The oscillation peaks correlate with the observation times.
+It can also be observed that $\alpha=1.0e-4$ and $\beta=1.0e-4$ there is a small oscillation.
+
+\subsection{The number of observations}
+The dependency on observations is relevant, since the number of observations of the MRI data is limited.
+This was investigated by changing the number of observations, and examine the resulting states.
+The number of observation were chosen to be 5, 10  and 20, and times were set to be evenly spaced.
+The range of regularization parameters were restricted to values that had previously low relative error.
+
+The results are shown in Tab.\ref{TAB::timesteps}, Tab.\ref{TAB::double} and Tab.\ref{TAB::half}.
+In the case of 10 observations, the number of timesteps showed a decrease in the relative error.
+Similar effects was observed for 5 and 20 observations.
+
+The relative boundary error for $\beta=1.0$  in Table~\ref{TAB::half} have similar value, independent on number of timesteps. This not the case for
+
+The spikes in Figure ~\ref{boundarycontrol} relates to the observation points $t_i$.
+
+\begin{figure}
+\centering
+\includegraphics[scale=0.2]{boundary_control.png}  
+\caption{ Displays plots over time for a selection of points at the boundary of $\Omega_1$ with different regularization parameters and number of timesteps $k$.
+The left panel shows the legend for the plot over time, together with the selection of points.
+The middel panel shows the average bounadry value $g$ for different regularization parameter with $k=10$.
+The right panel shows the average bounadry value $g$ for different regularization parameter with $k=40$.
+}
+\label{boundarycontrol}
 \end{figure}
@@
 \centering
-\includegraphics[scale=0.4]{27-12-hours-scale-0-1-3.png}  
+\includegraphics[scale=0.4]{12-clrscl-0413-regp--40-interp-white-2.png}  
 \caption{The upper row shows the manufactured observation, A ) Shows the manufactured observation at time-point 24 with no noise added.
@@
 \centering
-\includegraphics[scale=0.4]{27-24-hours-scale-0-1.png}
+\includegraphics[scale=0.4]{24-clrscl-0212-regp--40-interp.png}
 \caption{The upper row shows the manufactured observation, A ) Shows the manufactured observation at time-point 24 with no noise added.
@@
 C)Shows the manufactures observation at time-point 24 with noise amplitude of 0.3.
-The lower row shows the results with optimized parameter obtained with $\alpha=0.0001$, $\beta=1.0$ and $k=27$.
+The lower row shows the results with optimized parameter obtained with $\alpha=0.0001$, $\beta=1.0$ and $k=20$.
 D) Shows the resulting state given the observation in A.
@@
 
-\subsection{The number of timessteps}
-Increasing the number of timesteps in the simulations potentially allow for a more accurate temporal reconstruction, but at the same time the number of observations per control decreases and the regularization therefore may play a larger role.
-Furthermore,  the computational cost for each iteration of the L-BFGS-B algorithm as one
-forward solve is performed per iteration.
-Thus finding the number of timesteps for an effective convergence can help for larger meshes.
-The computation vary the timesteps with 10, 20 and 40 timesteps.
-Additionally, the computation will use a few variations of the regularization parameters that gives small relative errors.
-
-This gave the values presented in Tab.\ref{TAB::timesteps}, and can be seen that increase in the number of timesteps causes a decrease in the relative error.
-
-\subsection{The number of observations}
-The dependency on observations is relevant, since the number of observations of the MRI data is limited.
-This was investigated by changing the number of observations, and examine the resulting states.
-The number of observation were chosen to be 5, 10  and 20, and times were set to be evenly spaced.
-
-The results are shown in Tab.\ref{TAB::timesteps}, Tab.\ref{TAB::double} and Tab.\ref{TAB::half}.
-In the case of 10 observations, the number of timesteps showed a decrease in the relative error.
-Similar effects was observed for 5 and 20 observations.
-However, the variation of observations did not show a consistent decrease in error.
-And the variation in the relative error indicates oscillations in the convergence.
-
-\subsection{Sparse observations}
-The MRI data contains observations after the injection of CSF tracer.
+%\subsection{Sparse observations}
+%The MRI data contains observations after the injection of CSF tracer.
 These observation are unevenly distributed in time resulting in large time intervals with no observations.
@@
 The regularization parameters was selected, so that the error would be minimized,and noise was also added.
-
-The results are shown in Tab.\ref{Tab::Hole1} and Tab\ref{Tab::Hole2}, and it can be observed that the addition of noise caused $\beta=1.0$ to converge the same.
+%
+%The results are shown in Tab.\ref{Tab::Hole1} and Tab\ref{Tab::Hole2}, and it can be observed that the addition of noise caused $\beta=1.0$ to converge the same.
 Comparing the values in Tab\ref{Tab::Hole1} and Tab.\ref{TAB::timesteps}, showed that the relative error increased.
@@
 The estimation of tracer concentration proved difficult in the CSF compartment.
-Therefore the 2 domain mesh, shown in Fig.\ref{figmesh} was used in the computation.
+Therefore the 2 domain mesh, shown in Fig.\ref{Fig::Mesh} was used in the computation.
 The boundary control was set to the external boundary of both domains, and the subscript in $D_w$ and $D_g$ denotes white and grey diffusion coefficients.
 Furthermore, bounds were added to the L-BFGS-B algorithm to ensure non-negative boundary controls and the convergence criteria was adjusted to $gtol=6.0e-1$.
+The number of timesteps were selceted to be $k=48$, which gives approximate $dt = 1 hour$.
 
@@
 \subsection*{DTI comparison}
-The median diffusion coefficient in the DTI was estimated to be 8.7e-4 $\mathrm{mm\sp{2}/s}$ in   white matter and 1.0e-3 $\mathrm{mm\sp{2}/s}$ in grey matter.
-%This corresponds to 3.1 $\mathrm{mm\sp{2}/h}$ and  3.6 $\mathrm{mm\sp{2}/h}$.
-The self-diffusivity of water have been estimated to be around 3.0e-3$\mathrm{mm\sp{2}/s}$ for  $37\sp{o}C$.% This corresponds to 10.8 $\mathrm{mm\sp{2}/h}$ and  $\mathrm{mm\sp{2}/h}$.
 
-The reference value for Gd-DPTA was set to 3.8e-4 $\mathrm{mm\sp{2}/s}$.
-The values in Tab.\ref{Tab::Real-data} gives the value-range $1.5e-4 -2.7e-4\mathrm{mm\sp{2}/s}$ for the grey diffusion coefficient and  $2.2e-4 - 3.3e-4\mathrm{mm\sp{2}/s}$ for the white diffusion coefficient.
-These values are $20 -110 \%$ larger than the expected values for $D_{g}$,  and $100 - 200 \%$ larger than the expected values for $D_{w}$.
+% \begin{table}
+%\centering
+%\caption{Viser omgjøringer,estiamering og prosentvis forskjell for min og max control/optimerte verdier . Unit $\left[ \mathrm{mm\sp{2}/h} \right]$}
+%\begin{tabular}{*{2}c}
+% Parameter    & Value \\
+%\hline
+%Median 
+%\end{tabular}
+%\label{}
+%\end{table} 
+%%
 
-The estimation assumes that the tortousity is independent on molecular size.
+The median diffusion coefficient in the DTI was estimated to be $8.7e-4 \mathrm{mm\sp{2}/s}$ in white matter and $1.0e-3 \mathrm{mm\sp{2}/s}$ in grey matter.
+This corresponds to $1.85$ and $1.73$ in tortuosity, given that the self-diffusivity of water has been estimated to be around $3.0e-3\mathrm{mm\sp{2}/s}$ at $37\sp{o}C$.% This corresponds to 10.8 $\mathrm{mm\sp{2}/h}$ and  $\mathrm{mm\sp{2}/h}$.
+Then by using the reference value $3.8e-4 \mathrm{mm\sp{2}/s}$ for Gd-DPTA gives an estimate for the diffusion coefficient in the grey and white matter to respecitvly be $ 1.26\mathrm{mm\sp{2}/s}$ adn $1.10 \mathrm{mm\sp{2}/s}$.
+This estiamtion assums that the tortuoisty is indepedent on molecular size ?
+.
+
+The oscillation in Fig.\ref{boundarycontrol} showed a large discrepency in the states between observations.
+Therefore the states after 36 hours were examined, see Figure  ~\ref{statecomparison}, and the upper rows some indications of non- optimal regularization parameters.
+This prompt the exclusion of the corresponding valeus, which gives an average computed values $0.65 \mathrm{mm\sp{2}/h}$ and  $0.80 \mathrm{mm\sp{2}/h}$ in respectively grey and white matter.
+Scaled to $\mathrm{mm\sp{2}/s}$ gives $1.8 \mathrm{mm\sp{2}/s}$ and $2.22 \mathrm{mm\sp{2}/s}$.
+
+This gives a relative errot of $42 \%$ in grey matter and $ 100 %$ in white matter comparied the estimted values.
+
+The computation require that there is tracer present to compute the diffusion coefficient.
+In Fig.\ref{Fig::realdata}, it can be seen that there are regions with neglible amount of tracers and vice versa.
+Considering $1.3 \mathrm{mm\sp{2}/s}$ as the upper boound gives an estimated upper bound $1.43$ diffusion coefficient in the white matter.
+This relative error of $54%$ difference.
 
@@
 % 
-
-{\color{red} tortuoisty mindre for støre molekyler ? }
 %The region with high diffusivity in the white matter, shown in Fig\ref{FIG::DTI}, gives a upper bound on the diffusion coefficient to be 1.3 $\mathrm{mm\sp{2}/s}$
@@
 
-\subsection{Manufactures Solution}
 %The results from the manufactured solutions showed a robust method to compute diffusion coefficients. However, the maufactured solutions were constructed .. ? .. .
-The computational model assumes isotropic diffusivity, but the anisotropy in the white matter is well documented, as shown by the FA in Fig\ref{FIG::DTI}.
+The computational model assumes isotropic diffusivity, but the anisotropy in the white matter is well documented, as shown by the FA in Fig\ref{figuredti}.
 The region with high FA, can also be observed in the observation after 48 hours, shown in Fig.\ref{Fig::realdata}.
@@
 A more important factor are regions with higher diffusivity.
-Comparing Fig.\ref{FIG::DTI} and Fig \ref{Fig::realdata}, it can be observed that the region with high diffusivity also have a high tracer concentration.
+Comparing Fig.\ref{figuredti} and Fig \ref{Fig::realdata}, it can be observed that the region with high diffusivity also have a high tracer concentration.
 
-The computational model have 2 global controls for the diffusion coefficients, while it can be seen in  Fig.\ref{FIG::DTI} that diffusion coefficients can be considered a spacial function.
+The computational model have 2 global controls for the diffusion coefficients, while it can be seen in  Fig.\ref{figuredti} that diffusion coefficients can be considered a spacial function.
 Although the implmentaion of spacial control parameters are possible, it would siginificantly increase the computational cost.
@@
 This can be observed in the reconstruction in Fig.\ref{12hourswithnoise} and Fig.\ref{24hourswithnoise}, where the nosie is present at the boundary.
-
-Furthermore. in Fig.?? it was shown that the
 
@@
 
-\newpage 
-\newgeometry{top=0.5cm}
-
 \begin{figure}
@@
 
+\begin{figure}
+\centering
+\includegraphics[width=0.95\textwidth]{Statecomparison36h-pinta.png} 
+\caption{ Displays the states for different regularixation parameters after 36 h.}
+\label{statecomparison}
+\end{figure}
+
 \begin{table}
@@
 }
-\resizebox{0.9\textwidth}{!}{\begin{tabular}{*{8}c}
-$\alpha$ & $\beta$ & k  & iter & $ ||D_{\Omega_1}||_{RE}$ & $ ||D_{\Omega_2}||_{RE} $ & $||D_{\Omega_3}||_{RE}$ & $||g||_{RE}$ \\
+\begin{tabular}{*{8}c}
+$\alpha$ & $\beta$ & k  & iter & $ D_{\Omega_1}\sp{rel}$ & $ D_{\Omega_2}\sp{rel} $ & $D_{\Omega_3}\sp{rel}$ & $||g||_{rel}$ \\
 \hline
+  1.0e+00 	 & 1.0e+02 	 & 10 & 499 	 & +5.125 & +0.278 & +0.105 & +0.127 \\ 
   1.0e+00 	 & 1.0e+00 	 & 10 & 225 	 & +4.148 & +0.304 & +0.092 & +0.135 \\ 
@@
 % 1.0e-01 	 & 1.0e-06 	 & 10 & 195 	 & +0.122 & +0.093 & +0.041 & +0.057 \\ 
-
+1.0e-02 	 & 1.0e+02 	 & 10 & 228 	 & +0.702 & +0.106 & +0.035 & +0.033 \\ 
  1.0e-02 	 & 1.0e+00 	 & 10 & 227 	 & +0.015 & +0.067 & +0.039 & +0.018 \\ 
@@
 
+ 1.0e-04 	 & 1.0e+02 	 & 10 & 167 	 & +0.688 & +0.104 & +0.035 & +0.032 \\ 
  1.0e-04 	 & 1.0e+00 	 & 10 & 236 	 & +0.004 & +0.063 & +0.039 & +0.019 \\ 
@@
  %1.0e-05 	 & 1.0e-06 	 & 10 & 92 	 & -0.007 & +0.062 & +0.039 & +0.026 \\ 
-
+ 1.0e-06 	 & 1.0e+02 	 & 10 & 210 	 & +0.685 & +0.104 & +0.035 & +0.032 \\ 
  1.0e-06 	 & 1.0e+00 	 & 10 & 163 	 & +0.003 & +0.064 & +0.039 & +0.019 \\ 
@@
  1.0e-06 	 & 1.0e-06 	 & 10 & 91 	 & -0.008 & +0.062 & +0.039 & +0.026 \\  
-\end{tabular}}
+\end{tabular}
 \label{Tab::1}
+\end{table}
+
+\begin{table}
+\centering
+\caption{ Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$, the resulting number of iterations, the relative error of the estimated diffusion coefficients and the relative error for $g$.
+}
+\begin{tabular}{*{8}c}
+$\alpha$ & $\beta$ & k & iter & $ D_{\Omega_1}\sp{rel}$& $D_{\Omega_2}\sp{rel} $ & $D_{\Omega_3}\sp{rel} $&$|| g ||\sp{rel}_{L\sp{2}(\Omega_1)} $ \\
+\hline
+ %1.0e+00 	 & 1.0e+00 	 & 10 & 128 	 & +1.587 & +0.217 & +0.091 & +0.119 \\ 
+ 1.0e+00 	 & 1.0e+00 	 & 20 & 268 	 & +5.537 & +0.321 & +0.152 & +0.128 \\ 
+ 1.0e+00 	 & 1.0e+00 	 & 40 & 381 	 & +12.346 & +0.890 & +0.249 & +0.154\\
+
+% 1.0e+00 	 & 1.0e-04 	 & 10 & 130 	 & +1.558 & +0.216 & +0.091 & +0.119 \\ 
+ 1.0e+00 	 & 1.0e-04 	 & 20 & 497 	 & +19.414 & +1.514 & +0.422 & +0.259\\ 
+ 1.0e+00 	 & 1.0e-04 	 & 40 & 872 	 & +63.564 & +18.579 & +17.218 & +0.641 \\
+
+% 1.0e-04 	 & 1.0e+00 	 & 10 & 140 	 & -0.048 & +0.032 & +0.035 & +0.026 \\ 
+ 1.0e-04 	 & 1.0e+00 	 & 20 & 165 	 & +0.006 & +0.000 & +0.008 & +0.007 \\ 
+ 1.0e-04 	 & 1.0e+00 	 & 40 & 285 	 & +0.005 & -0.013 & +0.000 & +0.003 \\ 
+ 1.0e-04 	 & 1.0e+00 	 & 20 & 187 	 & -0.007 & +0.004 & +0.013 & +0.008 \\ 
+ 1.0e-04 	 & 1.0e+00 	 & 40 & 257 	 & -0.019 & -0.019 & +0.005 & +0.007 \\ 
+ %1.0e-04 	 & 1.0e-01 	 & 20 & 367 	 & +0.028 & +0.010 & +0.008 & +0.007 \\
+ %1.0e-04 	 & 1.0e-01 	 & 40 & 422 	 & +0.001 & -0.007 & +0.004 & +0.005 \\  
+ 1.0e-04 	 & 1.0e-02 	 & 20 & 258 	 & +0.068 & +0.023 & +0.005 & +0.006 \\ 
+ 1.0e-04 	 & 1.0e-02 	 & 40 & 339 	 & +0.004 & +0.002 & +0.002 & +0.003 \\
+
+ %1.0e-04 	 & 1.0e-04 	 & 10 & 113 	 & -0.060 & +0.030 & +0.036 & +0.026 \\ 
+ 1.0e-04 	 & 1.0e-04 	 & 20 & 322 	 & +0.105 & +0.031 & -0.003 & +0.020 \\ 
+ 1.0e-04 	 & 1.0e-04 	 & 40 & 358 	 & -0.011 & -0.005 & -0.003 & +0.004 \\
+
+% 1.0e-05 	 & 1.0e+00 	 & 20 & 237 	 & -0.006 & +0.004 & +0.013 & +0.008 \\ 
+ %1.0e-05 	 & 1.0e+00 	 & 40 & 358 	 & -0.018 & -0.019 & +0.005 & +0.007 \\  
+ %1.0e-05 	 & 1.0e-01 	 & 20 & 290 	 & +0.026 & +0.010 & +0.008 & +0.007 \\
+ %1.0e-05 	 & 1.0e-01 	 & 40 & 419 	 & +0.001 & -0.007 & +0.004 & +0.005 \\    
+ %1.0e-05 	 & 1.0e-02 	 & 20 & 316 	 & +0.071 & +0.025 & +0.005 & +0.007 \\ 
+ %1.0e-05 	 & 1.0e-02 	 & 40 & 401 	 & +0.004 & +0.003 & +0.002 & +0.004 \\  
+ 1.0e-06 	 & 1.0e+00 	 & 20 & 219 	 & -0.007 & +0.004 & +0.013 & +0.008 \\ 
+ 1.0e-06 	 & 1.0e+00 	 & 40 & 240 	 & -0.020 & -0.019 & +0.005 & +0.007 \\ 
+ %1.0e-06 	 & 1.0e-01 	 & 20 & 250 	 & +0.027 & +0.010 & +0.008 & +0.007 \\ 
+ %1.0e-06 	 & 1.0e-01 	 & 40 & 365 	 & +0.000 & -0.007 & +0.004 & +0.005 \\ 
+ 1.0e-06 	 & 1.0e-02 	 & 20 & 379 	 & +0.070 & +0.025 & +0.005 & +0.007 \\ 
+ 1.0e-06 	 & 1.0e-02 	 & 40 & 386 	 & +0.004 & +0.003 & +0.002 & +0.004 \\ 
+\end{tabular}
+\label{TAB::timesteps}
+\end{table}
+
+\begin{table}
+\centering
+\caption{ Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$, the resulting number of iterations, the relative error of the estimated diffusion coefficients and the relative error for $g$.
+The observation times were set $t_i \in \lbrace 4.8, 9.6, 14.4, 19.2, 24.0 \rbrace $.
+}
+\begin{tabular}{*{8}c}
+$\alpha$ & $\beta$ & k & iter & $ D_{\Omega_1}\sp{rel}$& $D_{\Omega_2}\sp{rel} $ & $D_{\Omega_3}\sp{rel} $&$|| g ||\sp{rel}_{L\sp{2}(\Omega_1)} $ \\
+\hline
+ 1.0e-04 	 & 1.0e+00 	 & 10 & 161 	 & +0.081 & +0.027 & +0.049 & +0.023 \\ 
+ 1.0e-04 	 & 1.0e+00 	 & 20 & 202 	 & +0.007 & -0.050 & +0.017 & +0.028 \\ 
+ 1.0e-04 	 & 1.0e+00 	 & 40 & 308 	 & -0.032 & -0.081 & +0.002 & +0.031 \\
+
+% 1.0e-04 	 & 1.0e-01 	 & 10 & 185 	 & +0.123 & +0.046 & +0.037 & +0.021 \\ 
+% 1.0e-04 	 & 1.0e-01 	 & 20 & 336 	 & +0.028 & -0.009 & +0.009 & +0.023 \\
+% 1.0e-04 	 & 1.0e-01 	 & 40 & 379 	 & -0.004 & -0.033 & -0.006 & +0.026 \\
+
+ 1.0e-04 	 & 1.0e-02 	 & 10 & 265 	 & +0.160 & +0.082 & +0.033 & +0.016 \\ 
+ 1.0e-04 	 & 1.0e-02 	 & 20 & 320 	 & +0.025 & +0.025 & +0.015 & +0.013 \\
+ 1.0e-04 	 & 1.0e-02 	 & 40 & 377 	 & +0.006 & +0.006 & -0.001 & +0.008 \\
+
+% 1.0e-05 	 & 1.0e+00 	 & 10 & 192 	 & +0.083 & +0.026 & +0.049 & +0.023 \\ 
+% 1.0e-05 	 & 1.0e+00 	 & 20 & 195 	 & +0.007 & -0.051 & +0.017 & +0.029 \\ 
+% 1.0e-05 	 & 1.0e+00 	 & 40 & 212 	 & -0.034 & -0.083 & +0.001 & +0.031 \\
+
+% 1.0e-05 	 & 1.0e-01 	 & 10 & 223 	 & +0.118 & +0.047 & +0.037 & +0.020 \\ 
+%  1.0e-05 	 & 1.0e-01 	 & 20 & 320 	 & +0.029 & -0.011 & +0.009 & +0.026 \\
+%  1.0e-05 	 & 1.0e-01 	 & 40 & 396 	 & -0.007 & -0.036 & -0.006 & +0.028 \\
+
+%  1.0e-05 	 & 1.0e-02 	 & 10 & 267 	 & +0.159 & +0.084 & +0.033 & +0.016 \\ 
+%  1.0e-05 	 & 1.0e-02 	 & 20 & 351 	 & +0.023 & +0.017 & +0.011 & +0.019 \\ 
+%  1.0e-05 	 & 1.0e-02 	 & 40 & 374 	 & +0.009 & +0.007 & -0.003 & +0.014 \\
+
+ 1.0e-06 	 & 1.0e+00 	 & 10 & 176 	 & +0.082 & +0.026 & +0.049 & +0.023 \\ 
+ 1.0e-06 	 & 1.0e+00 	 & 20 & 224 	 & +0.007 & -0.051 & +0.017 & +0.029 \\ 
+ 1.0e-06 	 & 1.0e+00 	 & 40 & 226 	 & -0.034 & -0.082 & +0.001 & +0.031 \\
+
+% 1.0e-06 	 & 1.0e-01 	 & 10 & 229 	 & +0.120 & +0.046 & +0.037 & +0.021 \\ 
+%  1.0e-06 	 & 1.0e-01 	 & 20 & 334 	 & +0.027 & -0.012 & +0.009 & +0.026 \\  
+% 1.0e-06 	 & 1.0e-01 	 & 40 & 313 	 & -0.007 & -0.037 & -0.006 & +0.030 \\
+
+ 1.0e-06 	 & 1.0e-02 	 & 10 & 253 	 & +0.156 & +0.080 & +0.033 & +0.018 \\ 
+ 1.0e-06 	 & 1.0e-02 	 & 20 & 340 	 & +0.020 & +0.016 & +0.012 & +0.019 \\ 
+ 1.0e-06 	 & 1.0e-02 	 & 40 & 368 	 & +0.006 & +0.006 & -0.004 & +0.013 \\ 
+\end{tabular}
+\label{TAB::half}
+\end{table}
+
+\begin{table}
+\centering
+\caption{ Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$, the resulting number of iterations, the relative error of the estimated diffusion coefficients and the relative error for $g$.
+The observation times were $t_i \in \lbrace $1.2, 2.4, 3.6, 4.8, 6.0, 7.2, 8.4, 9.6, 10.8, 12.0, 13.2, 14.4, 15.6, 16.8, 17.0, 19.2, 20.4,$ 21.6, 22.8, 24.0\rbrace $.}
+\begin{tabular}{*{8}c}
+$\alpha$ & $\beta$ & k & iter & $ D_{\Omega_1}\sp{rel}$ & $ D_{\Omega_2}\sp{rel}$ & $D_{\Omega_3}\sp{rel} $ & $|| g ||\sp{rel}_{L\sp{2}(\Omega_1)} $ \\
+\hline
+ 1.0e-04 	 & 1.0e+00 	 & 10 & 246 	 & -0.046 & +0.038 & +0.023 & +0.031 \\ 
+ 1.0e-04 	 & 1.0e+00 	 & 20 & 228 	 & -0.008 & +0.016 & +0.009 & +0.006 \\ 
+ 1.0e-04 	 & 1.0e+00 	 & 40 & 279 	 & -0.007 & +0.000 & +0.003 & +0.002 \\
+
+% 1.0e-04 	 & 1.0e-01 	 & 10 & 292 	 & -0.052 & +0.038 & +0.024 & +0.032 \\  
+% 1.0e-04 	 & 1.0e-01 	 & 20 & 331 	 & -0.001 & +0.018 & +0.006 & +0.006 \\ 
+% 1.0e-04 	 & 1.0e-01 	 & 40 & 313 	 & +0.004 & +0.003 & +0.000 & +0.002 \\
+
+ 1.0e-04 	 & 1.0e-02 	 & 10 & 338 	 & -0.053 & +0.038 & +0.024 & +0.032 \\ 
+  1.0e-04 	 & 1.0e-02 	 & 20 & 367 	 & +0.003 & +0.018 & +0.005 & +0.007 \\
+   1.0e-04 	 & 1.0e-02 	 & 40 & 273 	 & +0.017 & +0.006 & -0.001 & +0.001 \\
+
+% 1.0e-05 	 & 1.0e+00 	 & 10 & 290 	 & -0.047 & +0.038 & +0.023 & +0.031 \\ 
+%  1.0e-05 	 & 1.0e+00 	 & 20 & 194 	 & -0.008 & +0.016 & +0.009 & +0.006 \\ 
+%   1.0e-05 	 & 1.0e+00 	 & 40 & 238 	 & -0.007 & +0.000 & +0.002 & +0.002 \\
+
+% 1.0e-05 	 & 1.0e-01 	 & 10 & 316 	 & -0.052 & +0.038 & +0.024 & +0.032 \\ 
+%  1.0e-05 	 & 1.0e-01 	 & 20 & 312 	 & -0.001 & +0.018 & +0.006 & +0.006 \\ 
+%   1.0e-05 	 & 1.0e-01 	 & 40 & 317 	 & +0.004 & +0.003 & +0.000 & +0.002 \\
+
+ %1.0e-05 	 & 1.0e-02 	 & 10 & 389 	 & -0.052 & +0.038 & +0.024 & +0.033 \\ 
+ % 1.0e-05 	 & 1.0e-02 	 & 20 & 266 	 & +0.004 & +0.018 & +0.005 & +0.007 \\ 
+ %  1.0e-05 	 & 1.0e-02 	 & 40 & 336 	 & +0.015 & +0.005 & -0.001 & +0.001 \\
+
+ 1.0e-06 	 & 1.0e+00 	 & 10 & 282 	 & -0.047 & +0.038 & +0.023 & +0.031 \\ 
+  1.0e-06 	 & 1.0e+00 	 & 20 & 179 	 & -0.008 & +0.016 & +0.009 & +0.006 \\ 
+  1.0e-06 	 & 1.0e+00 	 & 40 & 261 	 & -0.007 & +0.000 & +0.002 & +0.002 \\
+
+% 1.0e-06 	 & 1.0e-01 	 & 10 & 308 	 & -0.052 & +0.038 & +0.024 & +0.032 \\ 
+%  1.0e-06 	 & 1.0e-01 	 & 20 & 245 	 & -0.002 & +0.018 & +0.006 & +0.006 \\ 
+%   1.0e-06 	 & 1.0e-01 	 & 40 & 318 	 & +0.004 & +0.003 & +0.000 & +0.002 \\
+
+ 1.0e-06 	 & 1.0e-02 	 & 10 & 285 	 & -0.052 & +0.038 & +0.024 & +0.032 \\ 
+ 1.0e-06 	 & 1.0e-02 	 & 20 & 362 	 & +0.003 & +0.018 & +0.005 & +0.007 \\ 
+ 1.0e-06 	 & 1.0e-02 	 & 40 & 375 	 & +0.015 & +0.005 & -0.001 & +0.001 \\ 
+\end{tabular}
+\label{TAB::double}
 \end{table}
@@
 The noise amplitude was set to 0.03, and $ t_i=[2.4, 4.8, 7.2, 9.6, 12.0, 14.4, 16.8, 19.2, 21.6, 24.0]$ }
-\resizebox{0.8\textwidth}{!}{\begin{tabular}{*{8}c}
-$\alpha$ & $\beta$ & k  & iter & $ ||D_{\Omega_1}||_{RE} $ & $||D_{\Omega_2}||_{RE}$ & $||D_{\Omega_3}||_{RE}$ & $||g||_{RE}$\\
+\begin{tabular}{*{8}c}
+$\alpha$ & $\beta$ & k  & iter & $ D_{\Omega_1}\sp{rel} $ & $D_{\Omega_2}\sp{rel}$ & $D_{\Omega_3}\sp{rel}$ & $|| g ||\sp{rel}_{L\sp{2}(\Omega_1)} $\\
 \hline
- 1.0e+00 	 & 1.0e+00 	 & 10 & 218 	 & +4.266 & +0.304 & +0.092 & +0.135 \\ 
+ %1.0e+00 	 & 1.0e+00 	 & 10 & 218 	 & +4.266 & +0.304 & +0.092 & +0.135 \\ 
  %1.0e+00 	 & 1.0e-01 	 & 10 & 223 	 & +4.565 & +0.304 & +0.090 & +0.142 \\ 
- 1.0e+00 	 & 1.0e-02 	 & 10 & 199 	 & +4.268 & +0.305 & +0.090 & +0.143 \\ 
+% 1.0e+00 	 & 1.0e-02 	 & 10 & 199 	 & +4.268 & +0.305 & +0.090 & +0.143 \\ 
 % 1.0e+00 	 & 1.0e-03 	 & 10 & 222 	 & +4.274 & +0.305 & +0.090 & +0.143 \\ 
- 1.0e+00 	 & 1.0e-04 	 & 10 & 211 	 & +4.448 & +0.306 & +0.090 & +0.143 \\ 
+% 1.0e+00 	 & 1.0e-04 	 & 10 & 211 	 & +4.448 & +0.306 & +0.090 & +0.143 \\ 
 % 1.0e+00 	 & 1.0e-05 	 & 10 & 227 	 & +4.527 & +0.304 & +0.090 & +0.143 \\ 
- 1.0e+00 	 & 1.0e-06 	 & 10 & 263 	 & +4.266 & +0.306 & +0.091 & +0.143 \\
+%1.0e+00 	 & 1.0e-06 	 & 10 & 263 	 & +4.266 & +0.306 & +0.091 & +0.143 \\
 
@@
  1.0e-06 	 & 1.0e-06 	 & 10 & 108 	 & +0.001 & +0.062 & +0.040 & +0.027 \\ 
-\end{tabular}}
+\end{tabular}
 \label{Tab::Noise0.03}
@@
 The noise amplitude was set to 0.3, and $t_i =[2.4, 4.8, 7.2, 9.6, 12.0, 14.4, 16.8, 19.2, 21.6, 24.0]$  }
-\resizebox{0.8\textwidth}{!}{\begin{tabular}{*{8}c}
-$\alpha$ & $\beta$ & k  & iter & $ ||D_{\Omega_1}||_{RE}$ & $||D_{\Omega_2}||_{RE} $ & $||D_{\Omega_3}||_{RE} $ & $||g||_{RE}$ \\
+\begin{tabular}{*{8}c}
+$\alpha$ & $\beta$ & k  & iter & $ D_{\Omega_1}\sp{rel}$ & $D_{\Omega_2}\sp{rel} $ & $D_{\Omega_3}\sp{rel} $ & $|| g ||\sp{rel}_{L\sp{2}(\Omega_1)} $ \\
 \hline
- 1.0e+00 	 & 1.0e+00 	 & 10 & 212 	 & +4.268 & +0.310 & +0.073 & +0.138 \\ 
+% 1.0e+00 	 & 1.0e+00 	 & 10 & 212 	 & +4.268 & +0.310 & +0.073 & +0.138 \\ 
  %1.0e+00 	 & 1.0e-01 	 & 10 & 211 	 & +4.122 & +0.302 & +0.085 & +0.146 \\ 
- 1.0e+00 	 & 1.0e-02 	 & 10 & 221 	 & +4.773 & +0.298 & +0.089 & +0.147 \\ 
+% 1.0e+00 	 & 1.0e-02 	 & 10 & 221 	 & +4.773 & +0.298 & +0.089 & +0.147 \\ 
  %1.0e+00 	 & 1.0e-03 	 & 10 & 257 	 & +4.872 & +0.301 & +0.090 & +0.147 \\ 
- 1.0e+00 	 & 1.0e-04 	 & 10 & 238 	 & +4.186 & +0.293 & +0.097 & +0.148 \\ 
+% 1.0e+00 	 & 1.0e-04 	 & 10 & 238 	 & +4.186 & +0.293 & +0.097 & +0.148 \\ 
  %1.0e+00 	 & 1.0e-05 	 & 10 & 204 	 & +4.251 & +0.313 & +0.085 & +0.147 \\ 
- 1.0e+00 	 & 1.0e-06 	 & 10 & 223 	 & +4.493 & +0.310 & +0.085 & +0.147 \\ 
+% 1.0e+00 	 & 1.0e-06 	 & 10 & 223 	 & +4.493 & +0.310 & +0.085 & +0.147 \\ 
  %1.0e-01 	 & 1.0e+00 	 & 10 & 145 	 & +0.126 & +0.100 & +0.054 & +0.035 \\ 
@@
 %\rowcolor{red}  1.0e-06 	 & 1.0e-05 	 & 10 & 1001 	 & +0.006 & +0.052 & +0.033 & +3.365 \\ 
- 1.0e-06 	 & 1.0e-06 	 & 10 & 1001 	 & -0.002 & +0.065 & +0.051 & +3.402 \\ 
-\end{tabular}}
+ 1.0e-06 	 & 1.0e-06 	 & 10 & - & -0.002 & +0.065 & +0.051 & +3.402 \\ 
+\end{tabular}
 \label{Tab::Noise0.3}
@@
 
-\begin{table}
-\centering
-\caption{ Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$, the resulting number of iterations, the relative error of the estimated diffusion coefficients and the relative error for $g$.
-}
-\resizebox{\textwidth}{!}{\begin{tabular}{*{8}c}
-$\alpha$ & $\beta$ & k & iter & $ ||D_{\Omega_1}||_{RE}$& $||D_{\Omega_2}||_{RE} $ & $||D_{\Omega_3}||_{RE} $&$||g||_{RE}$ \\
-\hline
- 1.0e-04 	 & 1.0e+00 	 & 20 & 187 	 & -0.007 & +0.004 & +0.013 & +0.008 \\ 
- 1.0e-04 	 & 1.0e+00 	 & 40 & 257 	 & -0.019 & -0.019 & +0.005 & +0.007 \\ 
- %1.0e-04 	 & 1.0e-01 	 & 20 & 367 	 & +0.028 & +0.010 & +0.008 & +0.007 \\
- %1.0e-04 	 & 1.0e-01 	 & 40 & 422 	 & +0.001 & -0.007 & +0.004 & +0.005 \\  
- 1.0e-04 	 & 1.0e-02 	 & 20 & 258 	 & +0.068 & +0.023 & +0.005 & +0.006 \\ 
- 1.0e-04 	 & 1.0e-02 	 & 40 & 339 	 & +0.004 & +0.002 & +0.002 & +0.003 \\   
-% 1.0e-05 	 & 1.0e+00 	 & 20 & 237 	 & -0.006 & +0.004 & +0.013 & +0.008 \\ 
- %1.0e-05 	 & 1.0e+00 	 & 40 & 358 	 & -0.018 & -0.019 & +0.005 & +0.007 \\  
- %1.0e-05 	 & 1.0e-01 	 & 20 & 290 	 & +0.026 & +0.010 & +0.008 & +0.007 \\
- %1.0e-05 	 & 1.0e-01 	 & 40 & 419 	 & +0.001 & -0.007 & +0.004 & +0.005 \\    
- %1.0e-05 	 & 1.0e-02 	 & 20 & 316 	 & +0.071 & +0.025 & +0.005 & +0.007 \\ 
- %1.0e-05 	 & 1.0e-02 	 & 40 & 401 	 & +0.004 & +0.003 & +0.002 & +0.004 \\  
- 1.0e-06 	 & 1.0e+00 	 & 20 & 219 	 & -0.007 & +0.004 & +0.013 & +0.008 \\ 
- 1.0e-06 	 & 1.0e+00 	 & 40 & 240 	 & -0.020 & -0.019 & +0.005 & +0.007 \\ 
- %1.0e-06 	 & 1.0e-01 	 & 20 & 250 	 & +0.027 & +0.010 & +0.008 & +0.007 \\ 
- %1.0e-06 	 & 1.0e-01 	 & 40 & 365 	 & +0.000 & -0.007 & +0.004 & +0.005 \\ 
- 1.0e-06 	 & 1.0e-02 	 & 20 & 379 	 & +0.070 & +0.025 & +0.005 & +0.007 \\ 
- 1.0e-06 	 & 1.0e-02 	 & 40 & 386 	 & +0.004 & +0.003 & +0.002 & +0.004 \\ 
-\end{tabular}}
-\label{TAB::timesteps}
-\end{table}
-
-\begin{table}
-\centering
-\caption{ Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$, the resulting number of iterations, the relative error of the estimated diffusion coefficients and the relative error for $g$.
-The observation times were set $t_i \in \lbrace 4.8, 9.6, 14.4, 19.2, 24.0 \rbrace $.
-}
-\resizebox{\textwidth}{!}{\begin{tabular}{*{8}c}
-$\alpha$ & $\beta$ & k & iter & $ ||D_{\Omega_1}||_{RE}$& $||D_{\Omega_2}||_{RE} $ & $||D_{\Omega_3}||_{RE} $&$||g||_{RE}$ \\
-\hline
- 1.0e-04 	 & 1.0e+00 	 & 10 & 161 	 & +0.081 & +0.027 & +0.049 & +0.023 \\ 
- 1.0e-04 	 & 1.0e+00 	 & 20 & 202 	 & +0.007 & -0.050 & +0.017 & +0.028 \\ 
- 1.0e-04 	 & 1.0e+00 	 & 40 & 308 	 & -0.032 & -0.081 & +0.002 & +0.031 \\
-
-% 1.0e-04 	 & 1.0e-01 	 & 10 & 185 	 & +0.123 & +0.046 & +0.037 & +0.021 \\ 
-% 1.0e-04 	 & 1.0e-01 	 & 20 & 336 	 & +0.028 & -0.009 & +0.009 & +0.023 \\
-% 1.0e-04 	 & 1.0e-01 	 & 40 & 379 	 & -0.004 & -0.033 & -0.006 & +0.026 \\
-
- 1.0e-04 	 & 1.0e-02 	 & 10 & 265 	 & +0.160 & +0.082 & +0.033 & +0.016 \\ 
- 1.0e-04 	 & 1.0e-02 	 & 20 & 320 	 & +0.025 & +0.025 & +0.015 & +0.013 \\
- 1.0e-04 	 & 1.0e-02 	 & 40 & 377 	 & +0.006 & +0.006 & -0.001 & +0.008 \\
-
- 1.0e-05 	 & 1.0e+00 	 & 10 & 192 	 & +0.083 & +0.026 & +0.049 & +0.023 \\ 
- 1.0e-05 	 & 1.0e+00 	 & 20 & 195 	 & +0.007 & -0.051 & +0.017 & +0.029 \\ 
- 1.0e-05 	 & 1.0e+00 	 & 40 & 212 	 & -0.034 & -0.083 & +0.001 & +0.031 \\
-
-% 1.0e-05 	 & 1.0e-01 	 & 10 & 223 	 & +0.118 & +0.047 & +0.037 & +0.020 \\ 
-%  1.0e-05 	 & 1.0e-01 	 & 20 & 320 	 & +0.029 & -0.011 & +0.009 & +0.026 \\
-%  1.0e-05 	 & 1.0e-01 	 & 40 & 396 	 & -0.007 & -0.036 & -0.006 & +0.028 \\
-
-  1.0e-05 	 & 1.0e-02 	 & 10 & 267 	 & +0.159 & +0.084 & +0.033 & +0.016 \\ 
-  1.0e-05 	 & 1.0e-02 	 & 20 & 351 	 & +0.023 & +0.017 & +0.011 & +0.019 \\ 
-  1.0e-05 	 & 1.0e-02 	 & 40 & 374 	 & +0.009 & +0.007 & -0.003 & +0.014 \\
-
- 1.0e-06 	 & 1.0e+00 	 & 10 & 176 	 & +0.082 & +0.026 & +0.049 & +0.023 \\ 
- 1.0e-06 	 & 1.0e+00 	 & 20 & 224 	 & +0.007 & -0.051 & +0.017 & +0.029 \\ 
- 1.0e-06 	 & 1.0e+00 	 & 40 & 226 	 & -0.034 & -0.082 & +0.001 & +0.031 \\
-
-% 1.0e-06 	 & 1.0e-01 	 & 10 & 229 	 & +0.120 & +0.046 & +0.037 & +0.021 \\ 
-%  1.0e-06 	 & 1.0e-01 	 & 20 & 334 	 & +0.027 & -0.012 & +0.009 & +0.026 \\  
-% 1.0e-06 	 & 1.0e-01 	 & 40 & 313 	 & -0.007 & -0.037 & -0.006 & +0.030 \\
-
- 1.0e-06 	 & 1.0e-02 	 & 10 & 253 	 & +0.156 & +0.080 & +0.033 & +0.018 \\ 
- 1.0e-06 	 & 1.0e-02 	 & 20 & 340 	 & +0.020 & +0.016 & +0.012 & +0.019 \\ 
- 1.0e-06 	 & 1.0e-02 	 & 40 & 368 	 & +0.006 & +0.006 & -0.004 & +0.013 \\ 
-\end{tabular}}
-\label{TAB::half}
-\end{table}
-
-\begin{table}
-\centering
-\caption{ Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$, the resulting number of iterations, the relative error of the estimated diffusion coefficients and the relative error for $g$.
-The observation times were $t_i \in \lbrace $1.2, 2.4, 3.6, 4.8, 6.0, 7.2, 8.4, 9.6, 10.8, 12.0, 13.2, 14.4, 15.6, 16.8, 17.0, 19.2, 20.4,$ 21.6, 22.8, 24.0\rbrace $.}
-\resizebox{\textwidth}{!}{\begin{tabular}{*{8}c}
-$\alpha$ & $\beta$ & k & iter & $ ||D_{\Omega_1}||_{RE}$ & $ ||D_{\Omega_2}||_{RE}$ & $||D_{\Omega_3}||_{RE} $ & $||g||_{RE}$ \\
-\hline
- 1.0e-04 	 & 1.0e+00 	 & 10 & 246 	 & -0.046 & +0.038 & +0.023 & +0.031 \\ 
- 1.0e-04 	 & 1.0e+00 	 & 20 & 228 	 & -0.008 & +0.016 & +0.009 & +0.006 \\ 
- 1.0e-04 	 & 1.0e+00 	 & 40 & 279 	 & -0.007 & +0.000 & +0.003 & +0.002 \\
-
-% 1.0e-04 	 & 1.0e-01 	 & 10 & 292 	 & -0.052 & +0.038 & +0.024 & +0.032 \\  
-% 1.0e-04 	 & 1.0e-01 	 & 20 & 331 	 & -0.001 & +0.018 & +0.006 & +0.006 \\ 
-% 1.0e-04 	 & 1.0e-01 	 & 40 & 313 	 & +0.004 & +0.003 & +0.000 & +0.002 \\
-
- 1.0e-04 	 & 1.0e-02 	 & 10 & 338 	 & -0.053 & +0.038 & +0.024 & +0.032 \\ 
-  1.0e-04 	 & 1.0e-02 	 & 20 & 367 	 & +0.003 & +0.018 & +0.005 & +0.007 \\
-   1.0e-04 	 & 1.0e-02 	 & 40 & 273 	 & +0.017 & +0.006 & -0.001 & +0.001 \\
-
- 1.0e-05 	 & 1.0e+00 	 & 10 & 290 	 & -0.047 & +0.038 & +0.023 & +0.031 \\ 
-  1.0e-05 	 & 1.0e+00 	 & 20 & 194 	 & -0.008 & +0.016 & +0.009 & +0.006 \\ 
-   1.0e-05 	 & 1.0e+00 	 & 40 & 238 	 & -0.007 & +0.000 & +0.002 & +0.002 \\
-
-% 1.0e-05 	 & 1.0e-01 	 & 10 & 316 	 & -0.052 & +0.038 & +0.024 & +0.032 \\ 
-%  1.0e-05 	 & 1.0e-01 	 & 20 & 312 	 & -0.001 & +0.018 & +0.006 & +0.006 \\ 
-%   1.0e-05 	 & 1.0e-01 	 & 40 & 317 	 & +0.004 & +0.003 & +0.000 & +0.002 \\
-
- 1.0e-05 	 & 1.0e-02 	 & 10 & 389 	 & -0.052 & +0.038 & +0.024 & +0.033 \\ 
-  1.0e-05 	 & 1.0e-02 	 & 20 & 266 	 & +0.004 & +0.018 & +0.005 & +0.007 \\ 
-   1.0e-05 	 & 1.0e-02 	 & 40 & 336 	 & +0.015 & +0.005 & -0.001 & +0.001 \\
-
- 1.0e-06 	 & 1.0e+00 	 & 10 & 282 	 & -0.047 & +0.038 & +0.023 & +0.031 \\ 
-  1.0e-06 	 & 1.0e+00 	 & 20 & 179 	 & -0.008 & +0.016 & +0.009 & +0.006 \\ 
-  1.0e-06 	 & 1.0e+00 	 & 40 & 261 	 & -0.007 & +0.000 & +0.002 & +0.002 \\
-
-% 1.0e-06 	 & 1.0e-01 	 & 10 & 308 	 & -0.052 & +0.038 & +0.024 & +0.032 \\ 
-%  1.0e-06 	 & 1.0e-01 	 & 20 & 245 	 & -0.002 & +0.018 & +0.006 & +0.006 \\ 
-%   1.0e-06 	 & 1.0e-01 	 & 40 & 318 	 & +0.004 & +0.003 & +0.000 & +0.002 \\
-
- 1.0e-06 	 & 1.0e-02 	 & 10 & 285 	 & -0.052 & +0.038 & +0.024 & +0.032 \\ 
- 1.0e-06 	 & 1.0e-02 	 & 20 & 362 	 & +0.003 & +0.018 & +0.005 & +0.007 \\ 
- 1.0e-06 	 & 1.0e-02 	 & 40 & 375 	 & +0.015 & +0.005 & -0.001 & +0.001 \\ 
-\end{tabular}}
-\label{TAB::double}
-\end{table}
-
-\begin{table}
-\centering
-\caption{Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$, the resulting number of iterations, the relative error of the estimated diffusion coefficients and the relative error for $g$.
+%
+%
+%\begin{table}
+%\centering
+%\caption{Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$, the resulting number of iterations, the relative error of the estimated diffusion coefficients and the relative error for $g$.
 The observation times were set $t_i \in \lbrace 0.8, 1.0, 1.2, 1.8, 2.4, 3.6, 5.4, 7.6, 24.0\rbrace $, and zero noise.}
-\resizebox{\textwidth}{!}{\begin{tabular}{*{8}c}
-$\alpha$ & $\beta$ & k & iter &  $ ||D_{\Omega_1}||_{RE}$ & $ ||D_{\Omega_2}||_{RE}$ & $||D_{\Omega_3}||_{RE} $ & $||g||_{RE}$\\
-\hline
- 1.0e-04 	 & 1.0e+00 	 & 40 & 453 	 & -0.003 & -0.017 & -0.021 & +0.053 \\
- 1.0e-04 	 & 1.0e-01 	 & 40 & 491 	 & -0.033 & -0.015 & -0.024 & +0.049 \\ 
- 1.0e-04 	 & 1.0e-02 	 & 40 & 611 	 & -0.051 & -0.020 & -0.027 & +0.096 \\ 
- 1.0e-05 	 & 1.0e+00 	 & 40 & 561 	 & -0.004 & -0.016 & -0.021 & +0.053 \\ 
- 1.0e-05 	 & 1.0e-01 	 & 40 & 688 	 & -0.033 & -0.015 & -0.025 & +0.045 \\ 
- 1.0e-05 	 & 1.0e-02 	 & 40 & 566 	 & -0.053 & -0.020 & -0.027 & +0.098 \\
- 1.0e-06 	 & 1.0e+00 	 & 40 & 517 	 & -0.005 & -0.016 & -0.021 & +0.053 \\ 
- 1.0e-06 	 & 1.0e-01 	 & 40 & 619 	 & -0.033 & -0.015 & -0.025 & +0.044 \\  
- 1.0e-06 	 & 1.0e-02 	 & 40 & 691 	 & -0.051 & -0.020 & -0.027 & +0.073 \\
-
-\end{tabular}}
-\label{Tab::Hole1}
-\end{table} 
-\begin{table}
-\centering
-\caption{Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$, the resulting number of iterations, the relative error of the estimated diffusion coefficients and the relative error for $g$.
+%\resizebox{\textwidth}{!}{\begin{tabular}{*{8}c}
+%$\alpha$ & $\beta$ & k & iter &  $ D_{\Omega_1}\sp{rel}$ & $ D_{\Omega_2}\sp{rel}$ & $D_{\Omega_3}\sp{rel} $ & $|| g ||\sp{rel}_{L\sp{2}(\Omega_1)} $\\
+%\hline
+% 1.0e-04 	 & 1.0e+00 	 & 40 & 453 	 & -0.003 & -0.017 & -0.021 & +0.053 \\
+% 1.0e-04 	 & 1.0e-01 	 & 40 & 491 	 & -0.033 & -0.015 & -0.024 & +0.049 \\ 
+% 1.0e-04 	 & 1.0e-02 	 & 40 & 611 	 & -0.051 & -0.020 & -0.027 & +0.096 \\ 
+% %1.0e-05 	 & 1.0e+00 	 & 40 & 561 	 & -0.004 & -0.016 & -0.021 & +0.053 \\ 
+% %1.0e-05 	 & 1.0e-01 	 & 40 & 688 	 & -0.033 & -0.015 & -0.025 & +0.045 \\ 
+% %1.0e-05 	 & 1.0e-02 	 & 40 & 566 	 & -0.053 & -0.020 & -0.027 & +0.098 \\
+% 1.0e-06 	 & 1.0e+00 	 & 40 & 517 	 & -0.005 & -0.016 & -0.021 & +0.053 \\ 
+% 1.0e-06 	 & 1.0e-01 	 & 40 & 619 	 & -0.033 & -0.015 & -0.025 & +0.044 \\  
+% 1.0e-06 	 & 1.0e-02 	 & 40 & 691 	 & -0.051 & -0.020 & -0.027 & +0.073 \\ 
+%
+%
+%\end{tabular}}
+%\label{Tab::Hole1}
+%\end{table} 
+%\begin{table}
+%\centering
+%\caption{Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$, the resulting number of iterations, the relative error of the estimated diffusion coefficients and the relative error for $g$.
 The observation times were set $t_i \in \lbrace 0.8, 1.0, 1.2, 1.8, 2.4, 3.6, 5.4, 7.6, 24.0\rbrace $, and with a noise amplitude of 0.3.}
-\resizebox{\textwidth}{!}{\begin{tabular}{*{8}c}
-$\alpha$ & $\beta$ & k & iter & $ ||D_{\Omega_1}||_{RE}$ & $  ||D_{\Omega_2}||_{RE}$ & $ ||D_{\Omega_3}||_{RE}$  &$||g||_{RE}$\\
-\hline
- %1.0e-04 	 & 1.0e+00 	 & 40 & 519 	 & +0.003 & +0.029 & +0.035 & +0.067 \\ 
-% 1.0e-04 	 & 1.0e-01 	 & 40 & 653 	 & -0.096 & +0.015 & +0.016 & +0.070 \\ 
-%\rowcolor{red}  1.0e-04 	 & 1.0e-02 	 & 40 & 575 	 & -0.050 & -0.001 & +0.057 & +0.281 \\ 
-% 1.0e-05 	 & 1.0e+00 	 & 40 & 585 	 & -0.050 & -0.007 & +0.017 & +0.068 \\ 
-% 1.0e-05 	 & 1.0e-01 	 & 40 & 871 	 & -0.023 & +0.024 & +0.019 & +0.079 \\ 
-%\rowcolor{red}  1.0e-05 	 & 1.0e-02 	 & 40 & 466 	 & -0.045 & +0.042 & +0.019 & +0.281 \\ 
-% 1.0e-06 	 & 1.0e+00 	 & 40 & 584 	 & -0.045 & +0.019 & +0.006 & +0.071 \\ 
-% 1.0e-06 	 & 1.0e-01 	 & 40 & 546 	 & +0.005 & +0.019 & -0.001 & +0.079 \\ 
-%\rowcolor{red}  1.0e-06 	 & 1.0e-02 	 & 40 & 648 	 & -0.074 & -0.008 & +0.041 & +0.227 \\
-
- 1.0e-04 	 & 1.0e+00 	 & 40 & 519 	 & +0.066 & -0.025 & -0.002 & +0.063 \\ 
- 1.0e-04 	 & 1.0e-01 	 & 40 & 853 	 & -0.047 & -0.013 & -0.001 & +0.078 \\ 
- 1.0e-04 	 & 1.0e-02 	 & 40 & -	 & -0.062 & -0.005 & -0.018 & +0.223 \\ 
- 1.0e-05 	 & 1.0e+00 	 & 40 & 455 	 & -0.038 & -0.006 & +0.012 & +0.063 \\ 
- 1.0e-05 	 & 1.0e-01 	 & 40 & 801 	 & -0.016 & +0.002 & +0.040 & +0.074 \\ 
- 1.0e-05 	 & 1.0e-02 	 & 40 & 877 	 & -0.060 & +0.017 & +0.010 & +0.198 \\ 
- 1.0e-06 	 & 1.0e+00 	 & 40 & 575 	 & -0.030 & +0.001 & +0.015 & +0.062 \\ 
- 1.0e-06 	 & 1.0e-01 	 & 40 & 848 	 & +0.002 & +0.005 & +0.023 & +0.071 \\ 
- 1.0e-06 	 & 1.0e-02 	 & 40 & -	 & +0.018 & +0.013 & -0.035 & +0.234 \\ 
-\end{tabular}}
-\label{Tab::Hole2}
-\end{table}
+%\resizebox{\textwidth}{!}{\begin{tabular}{*{8}c}
+%$\alpha$ & $\beta$ & k & iter & $ D_{\Omega_1}\sp{rel}$ & $  D_{\Omega_2}\sp{rel}$ & $ D_{\Omega_3}\sp{rel}$  &$|| g ||\sp{rel}_{L\sp{2}(\Omega_1)} $\\
+%\hline
+% %1.0e-04 	 & 1.0e+00 	 & 40 & 519 	 & +0.003 & +0.029 & +0.035 & +0.067 \\ 
+%% 1.0e-04 	 & 1.0e-01 	 & 40 & 653 	 & -0.096 & +0.015 & +0.016 & +0.070 \\ 
+%%\rowcolor{red}  1.0e-04 	 & 1.0e-02 	 & 40 & 575 	 & -0.050 & -0.001 & +0.057 & +0.281 \\ 
+%% 1.0e-05 	 & 1.0e+00 	 & 40 & 585 	 & -0.050 & -0.007 & +0.017 & +0.068 \\ 
+%% 1.0e-05 	 & 1.0e-01 	 & 40 & 871 	 & -0.023 & +0.024 & +0.019 & +0.079 \\ 
+%%\rowcolor{red}  1.0e-05 	 & 1.0e-02 	 & 40 & 466 	 & -0.045 & +0.042 & +0.019 & +0.281 \\ 
+%% 1.0e-06 	 & 1.0e+00 	 & 40 & 584 	 & -0.045 & +0.019 & +0.006 & +0.071 \\ 
+%% 1.0e-06 	 & 1.0e-01 	 & 40 & 546 	 & +0.005 & +0.019 & -0.001 & +0.079 \\ 
+%%\rowcolor{red}  1.0e-06 	 & 1.0e-02 	 & 40 & 648 	 & -0.074 & -0.008 & +0.041 & +0.227 \\ 
+%
+% 1.0e-04 	 & 1.0e+00 	 & 40 & 519 	 & +0.066 & -0.025 & -0.002 & +0.063 \\ 
+% 1.0e-04 	 & 1.0e-01 	 & 40 & 853 	 & -0.047 & -0.013 & -0.001 & +0.078 \\ 
+% 1.0e-04 	 & 1.0e-02 	 & 40 & -	 & -0.062 & -0.005 & -0.018 & +0.223 \\ 
+% %1.0e-05 	 & 1.0e+00 	 & 40 & 455 	 & -0.038 & -0.006 & +0.012 & +0.063 \\ 
+% %1.0e-05 	 & 1.0e-01 	 & 40 & 801 	 & -0.016 & +0.002 & +0.040 & +0.074 \\ 
+% %1.0e-05 	 & 1.0e-02 	 & 40 & 877 	 & -0.060 & +0.017 & +0.010 & +0.198 \\ 
+% 1.0e-06 	 & 1.0e+00 	 & 40 & 575 	 & -0.030 & +0.001 & +0.015 & +0.062 \\ 
+% 1.0e-06 	 & 1.0e-01 	 & 40 & 848 	 & +0.002 & +0.005 & +0.023 & +0.071 \\ 
+% 1.0e-06 	 & 1.0e-02 	 & 40 & -	 & +0.018 & +0.013 & -0.035 & +0.234 \\ 
+%\end{tabular}}
+%\label{Tab::Hole2}
+%\end{table}
 
@@
 \caption{Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$, the resulting number of iterations, the estimated diffusion coefficients for grey $D_g$ and white $D_w$ matter based on MRI data.}
-\resizebox{\textwidth}{!}{\begin{tabular}{*{6}c}
+\begin{tabular}{*{6}c}
 $\alpha$ & $\beta$ & k & iter &  $ D_{g} \left[ \mathrm{mm\sp{2}/h} \right] $ & $ D_{w} \left[ \mathrm{mm\sp{2}/h} \right]$ \\
 \hline
+ %1.0e-02    & 1.0e+02   & 48 & 714      & 0.564 & 0.952 ?? \\ 
  1.0e-02 	 & 1.0e+00 	 & 48 & 591 	 & 0.648 & 0.893 \\ 
@@
  1.0e-02 	 & 1.0e-02 	 & 48 & 748 	 & 0.986 & 1.198 \\ 
+ %1.0e-04    & 1.0e+02   & 48 & 815      & 0.470 & 0.928 \\ 
  1.0e-04 	 & 1.0e+00 	 & 48 & 607 	 & 0.551 & 0.815 \\ 
@@
  1.0e-04 	 & 1.0e-02 	 & 48 & 837 	 & 0.740 & 0.817 \\
+ %1.0e-06    & 1.0e+02   & 48 & 729      & 0.428 & 0.948 \\ 
  1.0e-06 	 & 1.0e+00 	 & 48 & 681 	 & 0.557 & 0.811 \\ 
@@
 
-\end{tabular}}
+\end{tabular}
 \label{Tab::Real-data}

### 2018-10-17 tex/paper.tex
restruct

@@
 
-\subsection*{Mathematical Model}
-In order to estimate the apparent diffusion coefficient involved in the contrast transportation shown 
-in Figure~\ref{fig1} we assume that the process can be modeled by a diffusion equation and  
-solve a PDE constrained optimization problem where
-the contrast distribution, boundary conditions, and apparent
-diffusion coefficient are solved for by optimizing with
-respect to the observed contrast distribution. As such, enhanced transportation because of effects such as
-dissipation would result in an apparent diffusion coefficient larger than that predicted by DTI.  
-The objective function was defined as 
-\begin{equation}
-\min_{u,g} F = \quad \sum\limits_i\sp{n} \int\limits_{\Omega} |u(t_i) - u_{obs}(t_i)| \mathrm{d}\Omega + \frac{\alpha}{2} \int\limits_{0}\sp{T} || g ||_{L\sp{2}(\partial\Omega)} \mathrm{d}t + \frac{\beta}{2} \int\limits_{0}\sp{T} || \dot{g} ||_{L\sp{2}(\partial\Omega)}\mathrm{d}t
-\label{EQ::objf}
-\end{equation}
-subject to   
-\begin{equation}
-\begin{aligned}
-\frac{\partial u}{\partial t} = \nabla \cdot  D_i \nabla u \qquad \text{in} \qquad \Omega \times \left\lbrace 0 , T \right)  \\
-u=g(t) \qquad \text{on} \qquad \partial\Omega  \times \left\lbrace 0 , T \right) 
-\end{aligned}
-\label{Eq::PDE}
-\end{equation}
-Here, $u$ is the contrast distribution, $D_i$ is the apparent diffusion 
-coefficient, and $g$ is the boundary condition. Furthermore,  
-the domain $\Omega$ contains three sub domains, each with a different diffusion coefficient.
-We denote the Cerebral Spinal fluid (CSF) domain as $\Omega_1$, the grey matter as $\Omega_2$ and the white matter as $\Omega_3$.
-The apparent
-diffusion constant is assumed constant within the CSF, grey and 
-white matter but each region may have different constants.  
-The $\alpha$ and $\beta$ parameters are regularization parameters 
-and $u_{obs}$ are observations at certain time-points.
-
-\section*{Implementation}
-The code used the FEniCS project to solve the PDE, using backwards Euler time discretization and first order continuous Galerkin finite elements.
-The linear problem was solved using GMRES, and the matrix was stored in the solver.
-The module dolfin adjoint ~\cite{farrell2013automated} \kam{correct ref?} was used to solve the PDE constrained optimization problem with the L-BFGS-B algorithm in the python module scipy.
-The convergence criteria for the minimization was set so that $max \lbrace | \text{proj} \hspace*{0.2cm} x_i | , \quad i = 1, .., N \rbrace \leq gtol=1.0e-1$ where $x_i$ is the i-th component of the gradient.
-{\color{red} From scipy :The iteration will stop when $max\lbrace | \text{proj} \hspace*{0.2cm} g_i | , \quad i = 1, .., N \rbrace \leq gtol $  where $pg_i$ is the i-th component of the projected gradient.}
-
-The observations $u_{obs}$ have a fixed time-point $t_i$, these time-points may not overlap with the time discretization in the forward problem $t_j$.
-Therefore, after each time step $dt$ in Eq\ref{Eq::PDE}, it was checked if the time step contained the next observation.
-If it did, then a linear interpolation of the  current solution $u(t_j)$ and previous solution $u(t_{j-1})$ was used approximate the solution at time $t_i$.
-The linear interpolation was given as
-\begin{equation}
-\label{observation:interpolation}
-u(t_i) \approx \frac{\Delta t}{dt} u(t_{j-1}) + \frac{dt - \Delta t }{dt} u(t_{j}), \quad t_i \in \lbrace t_{j-1}, t_j \rbrace
-\end{equation}
-with $\Delta t = t_j-t_i$.
-
-The implementation used the first observation as initial conditions of Eq.\ref{Eq::PDE}.
-Then for each timestep, the next observation was used as the initial value for boundary control $g$, which was imposed on the external boundary of the domain $\Omega_1$.
-The initial values of the diffusion coefficients in the optimization algorithm $(D_{CSF}, D_{GM}, D_{WM})=$  $(1, 1, 1)$.
-However, to increase the convergence rate, $D_{CSF}$ was scaled with $100$.
-
-The noise susceptibility was tested by adding an uniform distribution noise term to the observations.
-The noise term was constructed using numpy.random and adjusted so that noise range becomes $\lbrace -n_{amp} , n_{amp} \rbrace $, with $n_{amp}$ defined as noise amplitude.
-
-This work was performed on the Abel Cluster, owned by the University of Oslo and Uninett\textbackslash Sigma2, and operated by the Department for Research Computing at USIT,the University of Oslo IT-department.
-\url{http://www.hpc.uio.no/}
 \subsection*{Contrast concentration - Image Intensity Relation}
@@
 \end{equation}
-The difference in the calibraiton constant $M_0$ between observation times were adjusted in \cite{eidevalnes}. Thus we can express the $T_1$ change due to contrast as 
+The intensity difference between observation times were adjusted in \cite{eidevalnes}. Thus we can express the $T_1$ change due to contrast as 
 \begin{equation}
@@
 There are several forms of tissue damage that can be observed in the MRI due to a lower intensity in the white matter compared to healthy white matter tissue, hence damaged tissue have different T1 relaxation time.
-
-The estimation of the tracer concentration was precomputed and used the parameters obtained from the T1 map, MPRAGE MRI protocol \cite{eidevalnes} and the value for $r_1$ found in \cite{pmid16230904}.
-In the computation, the function $f(T_1)$ was computed for $ T_1\in \lbrace 200, 4000 \rbrace$ creating a lookup table.
-The lookup table was utilized with the baseline intensity increase to estimate $T_1\sp{c}$, and then the concentration was computed using Eq.\ref{EQ::contrast}.
-
-In \cite{sykova2008diffusion}, it was shown that the macroscopic diffusion in the brain can be considered a hindered diffusion with an apparent diffusion coefficient.
-Thus the computed diffusion coefficients will correspond to the apparent diffusion coefficient.
-
-In the acquired data, the MPRAGE had a high signal to noise ratio and the T1 map had low signal in the CSF.
-This made it difficult to estimate the concentration in the CSF compartment.
-Thus an additional mesh without the CSF compartment was constructed, see Fig.
-\ref{Fig::Mesh}.
 
@@
 
-\subsection{PDE constrained optimization algorithm}
+\subsection*{Mathematical Model}
 
-\kam{
-Noen detaljer her om element methode, optimerings algoritme, prekondisjonering
-grid, osv. 
-}
+In \cite{sykova2008diffusion}, It was shown that the macroscopic diffusion in the brain can be considered a hindered diffusion with an apparent diffusion coefficient.
+
+In order to estimate the apparent diffusion coefficient involved in the contrast transportation shown in Figure~\ref{fig1} we assume that the process can be modeled by a diffusion equation and solve a PDE constrained optimization problem where
+the contrast distribution, boundary conditions, and apparent
+diffusion coefficient are solved for by optimizing with
+respect to the observed contrast distribution. As such, enhanced transportation because of effects such as
+dissipation would result in an apparent diffusion coefficient larger than that predicted by DTI.  
+The objective function was defined as 
+\begin{equation}
+\min_{u,g} F = \quad \sum\limits_i\sp{n} \int\limits_{\Omega} |u(t_i) - u_{obs}(t_i)| \mathrm{d}\Omega + \frac{\alpha}{2} \int\limits_{0}\sp{T} || g ||_{L\sp{2}(\partial\Omega)} \mathrm{d}t + \frac{\beta}{2} \int\limits_{0}\sp{T} || \dot{g} ||_{L\sp{2}(\partial\Omega)}\mathrm{d}t
+\label{EQ::objf}
+\end{equation}
+subject to   
+\begin{equation}
+\begin{aligned}
+\frac{\partial u}{\partial t} = \nabla \cdot  D_i \nabla u \qquad \text{in} \qquad \Omega \times \left\lbrace 0 , T \right)  \\
+u=g(t) \qquad \text{on} \qquad \partial\Omega  \times \left\lbrace 0 , T \right) 
+\end{aligned}
+\label{Eq::PDE}
+\end{equation}
+Here, $u$ is the contrast distribution, $D_i$ is the apparent diffusion 
+coefficient, and $g$ is the boundary condition. Furthermore,  
+the domain $\Omega$ contains three sub domains, each with a different diffusion coefficient.
+We denote the Cerebral Spinal fluid (CSF) domain as $\Omega_1$, the grey matter as $\Omega_2$ and the white matter as $\Omega_3$.
+The apparent
+diffusion constant is assumed constant within the CSF, grey and 
+white matter but each region may have different constants.  
+The $\alpha$ and $\beta$ parameters are regularization parameters 
+and $u_{obs}$ are observations at certain time-points.
 
@@
 \end{equation}  
-The magnitude order for $\quad D_{\Omega_2} $ and $\quad D_{\Omega_2}$ were chosen to resemble diffusion coefficient for water in grey and white matter, but the relation between the coeffieicents were not preserved.
-The diffusion coefficent in the csf was chosen given [cite Bryne and Kent].
+The magnitude order for $\quad D_{\Omega_2} $ and $\quad D_{\Omega_2}$ were chosen to resemble diffusion coefficient for water in grey and white matter, but the relation between the coefficients were not preserved.
+The diffusion coefficient in the CSF was chosen given [cite Bryne and Kent], and the initial condition was set to 1.0 in $\Omega_1$ and 0 elsewhere.
 The manufactured forward computation gave a total of 120 possible observation time points.
@@
 The dimension of the mesh coordiantes are $\mathrm{mm}$.
+
+\section*{Implementation}
+The estimation of the tracer concentration was precomputed and used the parameters obtained from the T1 map, MPRAGE MRI protocol \cite{eidevalnes} and the value for $r_1$ found in \cite{pmid16230904}.
+In the computation, the function $f(T_1)$ was computed for $ T_1\in \lbrace 200, 4000 \rbrace$ creating a lookup table.
+The lookup table was utilized with the baseline intensity increase to estimate $T_1\sp{c}$, and then the concentration was computed using Eq.\ref{EQ::contrast}.
+
+%In the acquired data, the MPRAGE had a high signal to noise ratio and the T1 map had low signal in the CSF.
+This made it difficult to estimate the concentration in the CSF compartment.
+Thus an additional mesh without the CSF compartment was constructed, see Fig.
+\ref{Fig::Mesh}.
+
+The code used the FEniCS project to solve the PDE, using backwards Euler time discretization and first order continuous Galerkin finite elements.
+The linear problem was solved using GMRES, and the matrix was stored in the solver.
+The module dolfin adjoint ~\cite{farrell2013automated} \kam{correct ref?} was used to solve the PDE constrained optimization problem with the L-BFGS-B algorithm in the python module scipy.
+The convergence criteria for the minimization was set so that $max \lbrace | \text{proj} \hspace*{0.2cm} x_i | , \quad i = 1, .., N \rbrace \leq gtol=1.0e-1$ where $x_i$ is the i-th component of the gradient.
+{\color{red} From scipy :The iteration will stop when $max\lbrace | \text{proj} \hspace*{0.2cm} g_i | , \quad i = 1, .., N \rbrace \leq gtol $  where $pg_i$ is the i-th component of the projected gradient.}
+
+The observations $u_{obs}$ have a fixed time-point $t_i$, these time-points may not overlap with the time discretization in the forward problem $t_j$.
+Therefore, after each time step $dt$ in Eq\ref{Eq::PDE}, it was checked if the time step contained the next observation.
+If it did, then a linear interpolation of the  current solution $u(t_j)$ and previous solution $u(t_{j-1})$ was used approximate the solution at time $t_i$.
+The linear interpolation was given as
+\begin{equation}
+\label{observation:interpolation}
+u(t_i) \approx \frac{\Delta t}{dt} u(t_{j-1}) + \frac{dt - \Delta t }{dt} u(t_{j}), \quad t_i \in \lbrace t_{j-1}, t_j \rbrace
+\end{equation}
+with $\Delta t = t_j-t_i$.
+
+The implementation used the first observation as initial conditions of Eq.\ref{Eq::PDE}.
+Then for each timestep, the next observation was used as the initial value for boundary control $g$, which was imposed on the external boundary of the domain $\Omega_1$.
+The initial values of the diffusion coefficients in the optimization algorithm $(D_{CSF}, D_{GM}, D_{WM})=$  $(1, 1, 1)$.
+However, to increase the convergence rate, $D_{CSF}$ was scaled with $100$.
+
+The noise susceptibility was tested by adding an uniform distribution noise term to the observations.
+The noise term was constructed using numpy.random and adjusted so that noise range becomes $\lbrace -n_{amp} , n_{amp} \rbrace $, with $n_{amp}$ defined as noise amplitude.
+
+This work was performed on the Abel Cluster, owned by the University of Oslo and Uninett\textbackslash Sigma2, and operated by the Department for Research Computing at USIT,the University of Oslo IT-department.
+\url{http://www.hpc.uio.no/}
 
@@
 The left panel shows the legend for the plot over time, together with the selection of points.
-The middel panel shows the average bounadry value $g$ for different regularization parameter with $k=10$.
-The right panel shows the average bounadry value $g$ for different regularization parameter with $k=40$.
+The middle panel shows the average boundary value $g$ for different regularization parameter with $k=10$.
+The right panel shows the average boundary value $g$ for different regularization parameter with $k=40$.
 }
@@
 Furthermore, bounds were added to the L-BFGS-B algorithm to ensure non-negative boundary controls and the convergence criteria was adjusted to $gtol=6.0e-1$.
-The number of timesteps were selceted to be $k=48$, which gives approximate $dt = 1 hour$.
+The number of timesteps were selected to be $k=24$ $k=48$, which gives $dt = 2 hour$ and $dt = 1 hour$.
 
-The results are shown in Tab.\ref{Tab::Real-data}, 
-and the observation together with resulting states are displayed in Fig.\ref{Fig::realdata}
+The results are shown in Tab.\ref{Tab::Real-data}, and the observations after 12 and 48 hours were compared with the corresponding states.
 
@@
 This corresponds to $1.85$ and $1.73$ in tortuosity, given that the self-diffusivity of water has been estimated to be around $3.0e-3\mathrm{mm\sp{2}/s}$ at $37\sp{o}C$.% This corresponds to 10.8 $\mathrm{mm\sp{2}/h}$ and  $\mathrm{mm\sp{2}/h}$.
-Then by using the reference value $3.8e-4 \mathrm{mm\sp{2}/s}$ for Gd-DPTA gives an estimate for the diffusion coefficient in the grey and white matter to respecitvly be $ 1.26\mathrm{mm\sp{2}/s}$ adn $1.10 \mathrm{mm\sp{2}/s}$.
-This estiamtion assums that the tortuoisty is indepedent on molecular size ?
-.
+Then by using the reference value $3.8e-4 \mathrm{mm\sp{2}/s}$ for Gd-DPTA gives an estimate for the diffusion coefficient in the grey and white matter to respectively be $ 1.26\mathrm{mm\sp{2}/s}$ and $1.10 \mathrm{mm\sp{2}/s}$.
+This estimation assumes that the tortuosity is independent on molecular size .
 
-The oscillation in Fig.\ref{boundarycontrol} showed a large discrepency in the states between observations.
-Therefore the states after 36 hours were examined, see Figure  ~\ref{statecomparison}, and the upper rows some indications of non- optimal regularization parameters.
-This prompt the exclusion of the corresponding valeus, which gives an average computed values $0.65 \mathrm{mm\sp{2}/h}$ and  $0.80 \mathrm{mm\sp{2}/h}$ in respectively grey and white matter.
+The oscillation in Fig.\ref{boundarycontrol} showed a large discrepancy in the states between observations.
+Therefore the states with $k=48$ were examined after 36 hours, see Figure\ref{statecomparison}.
+It can be observed that the upper right row displays a discrepancy, which likely due to wrong regularization parameters.
+This prompt the exclusion of the corresponding values, which gives an average computed values $0.65 \mathrm{mm\sp{2}/h}$ and  $0.80 \mathrm{mm\sp{2}/h}$ in respectively grey and white matter.
 Scaled to $\mathrm{mm\sp{2}/s}$ gives $1.8 \mathrm{mm\sp{2}/s}$ and $2.22 \mathrm{mm\sp{2}/s}$.
 
-This gives a relative errot of $42 \%$ in grey matter and $ 100 %$ in white matter comparied the estimted values.
+This gives a relative error of $42 \%$ in grey matter and $ 100 \%$ in white matter compared to the estimated values.
 
 The computation require that there is tracer present to compute the diffusion coefficient.
-In Fig.\ref{Fig::realdata}, it can be seen that there are regions with neglible amount of tracers and vice versa.
-Considering $1.3 \mathrm{mm\sp{2}/s}$ as the upper boound gives an estimated upper bound $1.43$ diffusion coefficient in the white matter.
-This relative error of $54%$ difference.
+In Fig.\ref{Fig::realdata}, it can be seen that there are regions with negligible amount of tracers and vice versa.
+Considering $1.3 \mathrm{mm\sp{2}/s}$ as the upper bound gives an estimated upper bound $1.43$ diffusion coefficient in the white matter.
+This relative error of $54\%$ difference {\color{red} compare with dispersion, NB bare k 48 er brukt, k 24 skal med}
 
@@
 \section{Discussion}
+The computational model assumes isotropic diffusivity, but the anisotropy in the white matter is well documented, as shown by the FA in Fig\ref{figuredti}.
+Furthermore, it can be seen in Figure~\ref{Fig::realdata} that the region with high FA have negligible amounts of tracer present.
+Therefore it would seem that the anisotropy do not have direct impact on the computations, since the computation can not evaluate a static environment.
+Therefore  observation of tracer in regions with anisotropy can be considered a requirement for adding anisotropy to the model.
 
-%The results from the manufactured solutions showed a robust method to compute diffusion coefficients. However, the maufactured solutions were constructed .. ? .. .
-The computational model assumes isotropic diffusivity, but the anisotropy in the white matter is well documented, as shown by the FA in Fig\ref{figuredti}.
-The region with high FA, can also be observed in the observation after 48 hours, shown in Fig.\ref{Fig::realdata}.
-This observation is after 48 hours, and the amount of tracer inside the anisotropic region is negligible.
-Therefore it would seem that the anisotropy do not have direct impact on the computations, since the computation can not evaluate a static environment.
-Thus observation of tracer in anisotropic regions are needed for the integration of anisotropy into the model.
-
-A more important factor are regions with higher diffusivity.
-Comparing Fig.\ref{figuredti} and Fig \ref{Fig::realdata}, it can be observed that the region with high diffusivity also have a high tracer concentration.
+The regions with high diffusivity in Figure~\ref{figuredti},  have significant amount of diffusivity as seen in Figure~\ref{Fig::realdata}
 
 The computational model have 2 global controls for the diffusion coefficients, while it can be seen in  Fig.\ref{figuredti} that diffusion coefficients can be considered a spacial function.
-Although the implmentaion of spacial control parameters are possible, it would siginificantly increase the computational cost.
-
-The coputational cost dependes on the relaxation parameteres, the number of controls and solution of the PDE.
+Although the implementation of spacial control parameters are possible, it would significantly increase the computational cost.
 
@@
 This follows the assumption that the clearance is related to diffusion, which means an increase in diffusivity.
-Since the properties of the tracer molecule do not change, this would mean that the tortuosity decreased and followed by an incearse in the ADC.
+Since the properties of the tracer molecule do not change, this would mean that the tortuosity decreased and followed by an increase in the ADC.
 
@@
 Considering the that the grey matter volume has a depth less than 3 mm makes it susceptible to changes in $g$.
-This can be observed in the reconstruction in Fig.\ref{12hourswithnoise} and Fig.\ref{24hourswithnoise}, where the nosie is present at the boundary.
-
-A possible solution is to include the CSF compartment, but only use the observation in the white and grey matter.
+This can be observed in the reconstruction in Fig.\ref{12hourswithnoise} and Fig.\ref{24hourswithnoise}, where the noise is present at the boundary.
 
@@
 % 
+\section{References}
 
@@
 \caption{Row A) shows the observation at times 2 hours, 6 hours, 24 hours and 48 hours after the first observation with tracer.
-Row B) shows the corresponding states with the relaxation parameters set to $ \alpha=0.01$ and $\beta=0.01$.
-Row C) shows the corresponding states with the relaxation parameters set to $ \alpha=0.0001$ and $\beta=1.0$.
- Row D) shows the corresponding states with the relaxation parameters set to$ \alpha=1.0e-6$ and $\beta=0.1$. The color-bar was restricted to the range $ \lbrace 0 ,0.5 \rbrace$. }
+Row B) shows the corresponding states with the relaxation parameters $\alpha=0.01$ and $\beta=0.01$ and $k=48$.
+Row C) shows the corresponding states with the relaxation parameters $\alpha=0.0001$ and $\beta=1.0$ and $k=48$
+ Row D) shows the corresponding states with the relaxation parameters $\alpha=1.0e-6$ and $\beta=0.1$ and $k=48$. The color-bar was restricted to the range $ \lbrace 0 ,0.5 \rbrace$. }
 \label{Fig::realdata}
@@
 \includegraphics[width=0.95\textwidth]{Statecomparison36h-pinta.png} 
-\caption{ Displays the states for different regularixation parameters after 36 h.}
+\caption{ Displays the states for different regularization parameters after 36 hours for $k=48$.}
 \label{statecomparison}
@@
 \hline
+
  %1.0e+00 	 & 1.0e+00 	 & 10 & 128 	 & +1.587 & +0.217 & +0.091 & +0.119 \\
+
  1.0e+00 	 & 1.0e+00 	 & 20 & 268 	 & +5.537 & +0.321 & +0.152 & +0.128 \\ 
  1.0e+00 	 & 1.0e+00 	 & 40 & 381 	 & +12.346 & +0.890 & +0.249 & +0.154\\
+
+ 1.0e+00 	 & 1.0e-02 	 & 20 & 407 	 & +17.676 & +1.417 & +0.402 & +0.251 \\ 
+ 1.0e+00 	 & 1.0e-02 	 & 40 & 873 	 & +61.467 & +17.965 & +16.437 & +0.614 \\
 
@@
 
+ 1.0e-02 	 & 1.0e+00 	 & 20 & 157 	 & +0.016 & +0.004 & +0.008 & +0.007 \\ 
+ 1.0e-02 	 & 1.0e+00 	 & 40 & 277 	 & +0.020 & -0.006 & +0.001 & +0.003 \\
+
+ 1.0e-02 	 & 1.0e-02 	 & 20 & 447 	 & +0.130 & +0.055 & -0.000 & +0.016 \\ 
+ 1.0e-02 	 & 1.0e-02 	 & 40 & 458 	 & +0.098 & +0.088 & +0.002 & +0.023 \\
+
+ 1.0e-02 	 & 1.0e-04 	 & 20 & 595 	 & +0.175 & +0.081 & -0.003 & +0.090 \\ 
+ 1.0e-02 	 & 1.0e-04 	 & 40 & 976 	 & +0.320 & +0.398 & +0.088 & +0.226 \\
+
 % 1.0e-04 	 & 1.0e+00 	 & 10 & 140 	 & -0.048 & +0.032 & +0.035 & +0.026 \\ 
@@
  1.0e-04 	 & 1.0e+00 	 & 40 & 285 	 & +0.005 & -0.013 & +0.000 & +0.003 \\ 
- 1.0e-04 	 & 1.0e+00 	 & 20 & 187 	 & -0.007 & +0.004 & +0.013 & +0.008 \\ 
- 1.0e-04 	 & 1.0e+00 	 & 40 & 257 	 & -0.019 & -0.019 & +0.005 & +0.007 \\ 
  %1.0e-04 	 & 1.0e-01 	 & 20 & 367 	 & +0.028 & +0.010 & +0.008 & +0.007 \\
@@
  1.0e-06 	 & 1.0e-02 	 & 40 & 386 	 & +0.004 & +0.003 & +0.002 & +0.004 \\
+
+ 1.0e-06 	 & 1.0e-04 	 & 20 & 356 	 & +0.101 & +0.028 & -0.002 & +0.021 \\ 
+ 1.0e-06 	 & 1.0e-04 	 & 40 & 410 	 & -0.011 & -0.002 & -0.003 & +0.004 \\ 
 \end{tabular}
@@
 \hline
+
+ %1.0e-04 	 & 1.0e+02 	 & 10 & 895 	 & +22.689 & +0.254 & +0.008 & +0.024 \\ 
+ %1.0e-04 	 & 1.0e+02 	 & 20 & 1001 	 & +13.781 & +0.142 & -0.026 & +0.025 \\
+ %1.0e-04 	 & 1.0e+02 	 & 40 & 1001 	 & +9.368 & +0.089 & -0.042 & +0.026 \\
+
+% 1.0e-06 	 & 1.0e+02 	 & 10 & 919 	 & +19.507 & +0.255 & +0.008 & +0.024 \\ 
+% 1.0e-06 	 & 1.0e+02 	 & 20 & 999 	 & +15.032 & +0.141 & -0.026 & +0.025 \\ 
+% 1.0e-06 	 & 1.0e+02 	 & 40 & 1001 	 & +9.809 & +0.088 & -0.043 & +0.026 \\
+
+ 1.0e-02 	 & 1.0e+00 	 & 10 & 144 	 & +0.091 & +0.011 & +0.026 & +0.020 \\ 
+ 1.0e-02 	 & 1.0e+00 	 & 20 & 181 	 & +0.089 & -0.003 & -0.001 & +0.008 \\ 
+ 1.0e-02 	 & 1.0e+00 	 & 40 & 209 	 & +0.066 & -0.025 & -0.011 & +0.004 \\
+
+ 1.0e-02 	 & 1.0e-02 	 & 10 & 368 	 & +0.183 & +0.066 & +0.026 & +0.084 \\
+ 1.0e-02 	 & 1.0e-02 	 & 20 & 451 	 & +3.859 & +3.282 & +2.577 & +0.302 \\ 
+ 1.0e-02 	 & 1.0e-02 	 & 40 & 518 	 & +7.347 & +6.417 & +5.478 & +0.384 \\
+
  1.0e-04 	 & 1.0e+00 	 & 10 & 161 	 & +0.081 & +0.027 & +0.049 & +0.023 \\ 
@@
 \hline
+
+ 1.0e-02 	 & 1.0e+00 	 & 10 & 283 	 & -0.062 & +0.026 & +0.022 & +0.033 \\ 
+ 1.0e-02 	 & 1.0e+00 	 & 20 & 208 	 & -0.012 & +0.012 & +0.008 & +0.007 \\ 
+ 1.0e-02 	 & 1.0e+00 	 & 40 & 201 	 & +0.002 & +0.001 & +0.002 & +0.002 \\
+
+ 1.0e-02 	 & 1.0e-02 	 & 10 & 238 	 & -0.068 & +0.026 & +0.022 & +0.033 \\ 
+ 1.0e-02 	 & 1.0e-02 	 & 20 & 492 	 & -0.001 & +0.013 & +0.004 & +0.010 \\ 
+ 1.0e-02 	 & 1.0e-02 	 & 40 & 572 	 & +0.040 & +0.014 & -0.002 & +0.004 \\
+
  1.0e-04 	 & 1.0e+00 	 & 10 & 246 	 & -0.046 & +0.038 & +0.023 & +0.031 \\ 
@@
 \hline
+ 1.0e-02 	 & 1.0e+00 	 & 24 & 503 	 & +0.659 & +0.918 \\ 
+ 1.0e-02 	 & 1.0e-01 	 & 24 & 716 	 & +0.771 & +0.969 \\ 
+ 1.0e-02 	 & 1.0e-02 	 & 24 & 505 	 & +0.836 & +0.974 \\ 
+ 1.0e-04 	 & 1.0e+00 	 & 24 & 206 	 & +0.553 & +0.828 \\ 
+ 1.0e-04 	 & 1.0e-01 	 & 24 & 440 	 & +0.651 & +0.789 \\ 
+ 1.0e-04 	 & 1.0e-02 	 & 24 & 597 	 & +0.718 & +0.739 \\ 
+ 1.0e-06 	 & 1.0e+00 	 & 24 & 439 	 & +0.570 & +0.830 \\ 
+ 1.0e-06 	 & 1.0e-01 	 & 24 & 583 	 & +0.656 & +0.793 \\ 
+ 1.0e-06 	 & 1.0e-02 	 & 24 & 742 	 & +0.721 & +0.729 \\
+
  %1.0e-02    & 1.0e+02   & 48 & 714      & 0.564 & 0.952 ?? \\ 

### 2018-10-17 main.py

@@ -69,7 +69,7 @@ if __name__ == "__main__":
     parser.add_argument('--beta', default=0.001, type=float)
     parser.add_argument('--noise', default=0.0, type=float)
     parser.add_argument('--tol', default=0.001, type=float)
-    parser.add_argument('--D', default=[1000, 2, 1], type=float, nargs=3)
+    parser.add_argument('--D', default=[1000, 4 , 8], type=float, nargs=3)
     parser.add_argument('--mesh', default="mesh_invers_contrast.h5", type=str)
     parser.add_argument("--tau", nargs="+", type=float)
     parser.add_argument("--k", type=int)
@@ -97,7 +97,7 @@ if __name__ == "__main__":
     correct_g = bc(correct_g, V,tau,k, mesh_config)
     
     if Z.generate_observations:
-        ic = initial_condition(V, mesh_config)
+        ic =Function(V)
         g = bc(g, V,tau,k, mesh_config)
         generate_observations(mesh_config, V, D, g, ic, tau, Z.obs_file)
         exit()

### 2018-10-17 tex/paper.tex
various updates

@@
 \section{Introduction}
-
-A novel pathway of the brain's metabolism system called the paravascular pathway, because it runs in parallel with 
-vasculature system in a surrounding compartment,  
-was discoved in 2011~\cite{iliff2012paravascular}. 
-%Later it was found that this system is particularly active during sleep~\cite{xie2013sleep}.  
-It has been proposed that this pathway plays an important role in the clearance of waste
-from the brain and hereby a malfunction of this system is linked to  the development of dementia such as Alzheimer's and Parkinson's diseases. That is, 
-the lymphatic system plays a crucial role in waste clearance in the rest of our body, but there are no lymph vessels inside
-the brain. As such, the metabolic process of the brain is not well understood and this is surprising since the brain is a very 
-energy demanding organ (about 10 times as demanding as the average organ). The circulatory system of the paravascular pathway 
-has therefore been named the glymphatic system~\cite{jessen2015glymphatic} as it has a similar role as the well-known lymphatic system and because the glia cells 
-are crucial in this system.  
-The glymphatic system remains controversial and modeling attempts
-has so far mostly failed to explain the biomechanics of the system~\cite{asgari2016glymphatic, holter2017interstitial, smith2017glymphatic}\kam{Lars: vi trenger flere her}. A proper biomechanical 
-understanding of the pathway has significant potential because
-dementia such as Alzheimer´s and Parkinson´s diseases are
-associated with accumulation of metabolic waste such as
-amyloid-beta and CSF-tau.
+Recent breakthroughs in medicine have linked diseases like Alzheimer's to insufficient sleep through a novel biomechanical mechanism called the glymphatic system 
+that is responsible for waste clearance. 
+In 2011,~\cite{iliff2012paravascular} discovered a novel system within our brain's metabolism system, which changed our understanding of the brain. 
+The system involves a new pathway, called the paravascular pathway as it runs in parallel with vasculature system in a surrounding compartment.
+The important novelty in the 2011 findings was that waste from the brain is cleared through the paravascular path, and that a malfunction of this system 
+is linked to the development of dementia such as Alzheimer's and Parkinson's diseases. In 2013,~\cite{xie2013sleep} found
+that this system is particularly active during sleep.
+These mentioned breakthroughs were all performed in mice. In 2018,  
+the project's collaborators for the first time demonstrated the action of
+this system in humans, and that the action of the system differs
+between healthy controls and patients with dementia~\cite{ringstad2018brain}. 
+However, the biomechanical mechanisms behind this is not well understood,
+and so far the modeling attempts have mostly failed~\cite{asgari2016glymphatic, holter2017interstitial, smith2017glymphatic}. 
+In particular the system seems to facilitate waste transport faster than  
+the diffusion, which since the pioneering works of \cite{sykova2008diffusion} 
+has been the prevailing paradigm. Here, we aim to investigate whether PDE constrained optimization can be used
+to assess the effective diffusion coefficient on long time-scales (hours or days).
+
+%A novel pathway of the brain's metabolism system called the paravascular pathway, because it runs in parallel with 
+%vasculature system in a surrounding compartment,  
+%was discoved in 2011~\cite{iliff2012paravascular}. 
+%%Later it was found that this system is particularly active during sleep~\cite{xie2013sleep}.  
+%It has been proposed that this pathway plays an important role in the clearance of waste
+%from the brain and hereby a malfunction of this system is linked to  the development of dementia such as Alzheimer's and Parkinson's diseases. That is, 
+%the lymphatic system plays a crucial role in waste clearance in the rest of our body, but there are no lymph vessels inside
+%the brain. As such, the metabolic process of the brain is not well understood and this is surprising since the brain is a very 
+%energy demanding organ (about 10 times as demanding as the average organ). The circulatory system of the paravascular pathway 
+%has therefore been named the glymphatic system~\cite{jessen2015glymphatic} as it has a similar role as the well-known lymphatic system and because the glia cells 
+%are crucial in this system.  
+%The glymphatic system remains controversial and modeling attempts
+%has so far mostly failed to explain the biomechanics of the system~\cite{asgari2016glymphatic, holter2017interstitial, smith2017glymphatic}\kam{Lars: vi trenger flere her}. A proper biomechanical 
+%understanding of the pathway has significant potential because
+%dementia such as Alzheimer´s and Parkinson´s diseases are
+%associated with accumulation of metabolic waste such as
+%amyloid-beta and CSF-tau.
 
@@
 for assessing the apparent diffusion process where
-the complex geometry of the brain is taken into account. The approach 
-we will take is to solve a PDE constrained optimization problem 
-via adjoint methods. As such we need to assess the sensitivity of
+the complex geometry of the brain is taken into account and time-scales of hours or days are taken into approach. 
+The approach we will take is to solve a PDE constrained optimization problem 
+via adjoint methods where we have sparse observations on selected time-points, around 10 acquisitions during 24 hours, but throught
+the complete domain. Hence, the challenges faced from a mathematical point of view 
+are that 1) the images are subject to noise, resolution in space is limited to slightly less than (1 mm)$^3$ and 
+the sparse observations throught the time domain.  As such we need to assess the sensitivity of
 the approach with respect important parameters such as to regularization parameters, noise levels, 
 time resolution to determine whether this approach is a viable method
-to obtain parameters involved time-scales beyond those of the MRI aquisition.
-
-\subsection*{MRI Data}
+to obtain parameters involved time-scales beyond those of the MRI aquisition. We remark that the purpose
+of this paper is a systematic study of the mathematical challenges faces and that assessing  
+whether clearance is goverened by a process that is faster than diffusion is not the topic of the current paper.
+
+An outline of the paper is as follows. 
+In Section 2 we present the methodology of the paper. Section 2.1-2.3 contains a detailed description of the medical imaging 
+relevant to this study and do not expect the reader to have prior knowledge of medical imaging. Section 2.4
+describes the PDE constrained optimization problem and the corresponding solution algorithm, while 2.5 presents
+a test problem using a manufactured solution that is used for method verification. Section 2.6 describes the implementation 
+in FEniCS. In Section 3 we present the results and have a rather extensive discussion of the verification performed
+using a manufactured solution (Section 3.1-3.3) before we present the results obtained by real observations in Section 3.4     
+and a comparison with DTI data in Section 3.5. Finally, in Section 4, the methodology and results are discussed.
+
+\section{Methodology}
+
+Section 2.1-2.3 describes the details of the imaging relevant for this study. More details can however be
+found in e.g. \cite{ringstad2018brain}. Section 2.4-2.5 describe the solution of PDE constrained optimization problems and
+its implementation in FEniCS. The exposition is, however, brief and we refer to XXX for more details.
+
+\subsection{MRI Data}
 \begin{figure}
@@
 
-\subsection*{Contrast concentration - Image Intensity Relation}
+\subsection{Contrast concentration - Image Intensity Relation}
 Below, we briefly describe the relationship between the imaging intensity 
@@
 
-\subsection{DTI}
+\subsection{Diffusion tensor imaging}
 In addition to the T1 and T2 weighted sequences described above we have also obtained diffusion tensor imaging (DTI) to assess the apparent diffusion 
@@
 
-\subsection*{Mathematical Model}
+\subsection{Mathematical Model}
 
@@
 
-\subsection*{Manufactured Solution}
+\subsection{Manufactured Solution}
 In order to verify our strategy and test the dependency of the
@@
 
-\section*{Implementation}
+\section{Implementation}
 The estimation of the tracer concentration was precomputed and used the parameters obtained from the T1 map, MPRAGE MRI protocol \cite{eidevalnes} and the value for $r_1$ found in \cite{pmid16230904}.
@@
 \section{Results}
+
+\subsection{Verification in terms of the manufactured solution}
+
 Below we will discuss the parameter identification and its sensitivity with respect to regularization parameters, noise and time-resolution. 
@@
 
-\subsection{The relaxation parameters}
+\subsubsection{The relaxation parameters}
 To assess the sensitivity of the the objective functional defined in Eq.\ref{Eq::F} with respect to the regularization parameters $\alpha$ and $\beta$ 
@@
 
-\subsection{The number of timessteps}
+\subsubsection{The number of timessteps}
 Increasing the number of timesteps in the computations potentially allow for a more accurate temporal reconstruction, but at the same time the number of observations per control decreases and the regularization therefore may play a larger role.
@@
 
-\subsection{The number of observations}
+\subsubsection{The number of observations}
 The dependency on observations is relevant, since the number of observations of the MRI data is limited.
@@
 
-\subsection{The noise susceptibility}
+\subsubsection{The noise susceptibility}
 The MRI data contains noise, hence an investigation to the noise susceptibility is needed.
@@
 
-\subsection{MRI Data} 
+\subsection{A Real case}
+
+\subsubsection{Results obtained when using real observations}
 The MRI data consisted of the observations at times $t_i \in \lbrace$ 0.00, 0.16, 0.39, 0.55, 0.77, 2.09, 6.05, 24.06, 47.84, 698.02 $\rbrace (hours)$ with the time $t_i=0.00$ as the observation 1-2 hours after the tracer was injected.
@@
 
-\subsection*{DTI comparison}
+\subsubsection{Comparison with results obtained from DTI analysis}
 
@@
 \section{Discussion}
-The computational model assumes isotropic diffusivity, but the anisotropy in the white matter is well documented, as shown by the FA in Fig\ref{figuredti}.
-Furthermore, it can be seen in Figure~\ref{Fig::realdata} that the region with high FA have negligible amounts of tracer present.
+
+The methodology presented here for identification of diffusion coefficients and boundary conditions with application to the glymphatic system appears to work quite 
+well for regularization parameters varying by orders of magnitude. It is particularly interesting to see that the procedure efficiently removes noise as demonstrated
+in the Figures \ref{12hourswithnoise} and \ref{24hourswithnoise} with noise levels of 30\% \kam{is this correctly stated}. 
+Crucial in our application is the interplay between the regularization term that regulates the smoothness of the boundary conditions as well as
+the integrate magnitude of the boundary conditions over time, i.e. $\alpha$ and $\beta$, and the
+importance of interplay of these parameter increases with the number of time steps. This is, however, not surprising because our observations are sparse
+in time and hence an oscillating boundary condition in time will minimized the integrated boundary condition at the cost of reducing the smoothness in time.
+
+While a more comprehensive study involving more patients would be required in order to assess whether the clearance here happens faster than diffusion (\kam{egentlig er
+vel dette det motsatte av clearance} a few remarks are in order. We find that the diffusion coefficients is XXX larger than what was found by the DTI modality.  
+However, we have not yet been able to assessment the self-diffusion of water as well as the diffusivity of Gadovist used in this study in phantom models. As such 
+the constants in equation XXX must be taken with caution. Furthermore,    
+the computational model assumes isotropic diffusivity, but the anisotropy in the white matter is well documented, as shown by the FA in Fig\ref{figuredti}.
+It can be seen in Figure~\ref{Fig::realdata} that the region with high FA have negligible amounts of tracer present.
 Therefore it would seem that the anisotropy do not have direct impact on the computations, since the computation can not evaluate a static environment.
 Therefore  observation of tracer in regions with anisotropy can be considered a requirement for adding anisotropy to the model.
-
 The regions with high diffusivity in Figure~\ref{figuredti},  have significant amount of diffusivity as seen in Figure~\ref{Fig::realdata} 
-
 The computational model have 2 global controls for the diffusion coefficients, while it can be seen in  Fig.\ref{figuredti} that diffusion coefficients can be considered a spacial function.

### 2018-10-19 tex/paper.tex
refs and text added

@@
 for assessing the apparent diffusion process where
-the complex geometry of the brain is taken into account and time-scales of hours or days are taken into approach. 
+the complex geometry of the brain is taken into account and time-scales of hours or days are taken into account. 
 The approach we will take is to solve a PDE constrained optimization problem 
-via adjoint methods where we have sparse observations on selected time-points, around 10 acquisitions during 24 hours, but throught
+via adjoint methods where we have sparse observations on selected time-points, around 10 acquisitions during 24 hours, but through
 the complete domain. Hence, the challenges faced from a mathematical point of view 
 are that 1) the images are subject to noise, resolution in space is limited to slightly less than (1 mm)$^3$ and 
-the sparse observations throught the time domain.  As such we need to assess the sensitivity of
+the sparse observations through the time domain.  As such we need to assess the sensitivity of
 the approach with respect important parameters such as to regularization parameters, noise levels, 
 time resolution to determine whether this approach is a viable method
-to obtain parameters involved time-scales beyond those of the MRI aquisition. We remark that the purpose
-of this paper is a systematic study of the mathematical challenges faces and that assessing  
-whether clearance is goverened by a process that is faster than diffusion is not the topic of the current paper.
+to obtain parameters involved time-scales beyond those of the MRI acquisition. We remark that the purpose
+of this paper is a systematic study of the mathematical challenges and that assessing  
+whether clearance is governed by a process that is faster than diffusion is not the topic of the current paper.
 
@@
 a test problem using a manufactured solution that is used for method verification. Section 2.6 describes the implementation 
-in FEniCS. In Section 3 we present the results and have a rather extensive discussion of the verification performed
+in FEniCS \cite{LoggMardalEtAl2012a}. In Section 3 we present the results and have a rather extensive discussion of the verification performed
 using a manufactured solution (Section 3.1-3.3) before we present the results obtained by real observations in Section 3.4     
@@
 We remark that we use a notation common in medical literature and here two letter symbols are common.
-Hence, below we will use two letter symbols such as $TE$ and $TR$ to keep the notation consistent the presentation of (reference \cite{GOWLAND}, \cite{MPRAGE}).
+Hence, below we will use two letter symbols such as $TE$ and $TR$ to keep the notation consistent the presentation in \cite{GOWLAND}\cite{MPRAGE}.
 The tracer concentration $c$ causes the longitudinal(spin-lattice) relaxation time $T_{1}$ to shorten with the following relation
@@
 \end{equation}
+{\color{red} kommer inversion prepared fram ?}
 In article \cite{GOWLAND}, the term $M_n$ is defined as the magnetization for the n-echo 
@@
 This due to the fact that both molecules have similar mass/size, and based Stoke-Einstein equation should have similar diffusion coefficients.
-The free diffusion coefficient for Gd-DPTA was estimated in \cite{GdDPTA-DIFFUSION} to be 3.8e-4$\mathrm{mm\sp{2}/s}$.
+The free diffusion coefficient for Gd-DPTA was estimated in \cite{GdDPTA-DIFFUSION} to be $3.8e-4\mathrm{mm\sp{2}/s}$.
 
@@
 \begin{equation}
-\min_{u,g} F = \quad \sum\limits_i\sp{n} \int\limits_{\Omega} |u(t_i) - u_{obs}(t_i)| \mathrm{d}\Omega + \frac{\alpha}{2} \int\limits_{0}\sp{T} || g ||_{L\sp{2}(\partial\Omega)} \mathrm{d}t + \frac{\beta}{2} \int\limits_{0}\sp{T} || \dot{g} ||_{L\sp{2}(\partial\Omega)}\mathrm{d}t
+\min_{D,g} F = \quad \sum\limits_i\sp{n} \int\limits_{\Omega} |u(t_i) - u_{obs}(t_i)|\sp{2} \mathrm{d}\Omega + \frac{\alpha}{2} \int\limits_{0}\sp{T} || g ||\sp{2}_{L\sp{2}(\partial\Omega)} \mathrm{d}t + \frac{\beta}{2} \int\limits_{0}\sp{T} || \dot{g} ||\sp{2}_{L\sp{2}(\partial\Omega)}\mathrm{d}t
 \label{EQ::objf}
@@
 The apparent
-diffusion constant is assumed constant within the CSF, grey and 
-white matter but each region may have different constants.  
-The $\alpha$ and $\beta$ parameters are regularization parameters 
+diffusion constant is assumed to be constant within the CSF, grey and 
+white matter but each region may have different values.  
+The $\alpha$ and $\beta$ parameters are non-negative regularization parameters 
 and $u_{obs}$ are observations at certain time-points.
@@
 In order to verify our strategy and test the dependency of the
-regularization paramters, we perform a test case with a
+regularization parameters, we perform a test case with a
 known solution.  
@@
 \end{equation}  
-The magnitude order for $\quad D_{\Omega_2} $ and $\quad D_{\Omega_2}$ were chosen to resemble diffusion coefficient for water in grey and white matter, but the relation between the coefficients were not preserved.
-The diffusion coefficient in the CSF was chosen given [cite Bryne and Kent], and the initial condition was set to 1.0 in $\Omega_1$ and 0 elsewhere.
-The manufactured forward computation gave a total of 120 possible observation time points.
-These points will be denoted as $t_i$.
-
-The mesh construction was patient-specific and was constructed by using the MRI of a patient diagnosed with idiopathic normal pressure hydrocephalus (iNPH).
+The magnitude order for $D_{\Omega_1} $ and $D_{\Omega_2}$ were chosen to resemble diffusion coefficient for water in grey and white matter, but the relation between the coefficients were not preserved.
+The diffusion coefficient in the CSF was chosen given [cite Bryne and Kent], and the initial condition was set to 0 everywhere.
+%and the initial condition was set to 1.0 in $\Omega_1$ and 0 elsewhere.
+The manufactured forward computation gave a total of 120 possible observation time points. These points will be denoted as $t_i$.
+
+The mesh construction was patient-specific and used the MRI of a patient diagnosed with idiopathic normal pressure hydrocephalus (iNPH).
 The software Freesurfer was used in segmentation and creating the polyhedral surfaces of the white and grey matter.
-Then the use of T2 weighted MRI was used to segment the CSF compartment surrounding the cerebral and the lateral ventricles.
-The module BrainMesh (currently in testing) (BrainMesh code accessibility {\color{red} kan ta med eller bare si CGAL}) CGAL \cite{cgal:rty-m3-18b} was used to combine the polyhedral surfaces and to construed the mesh.
+Then the use of T2 weighted MRI \cite{eidevalnes} was used to segment the CSF compartment surrounding the cerebral and the lateral ventricles.
+CGAL \cite{cgal:rty-m3-18b} was used to combine the polyhedral surfaces and to construed the mesh, the code can be found ??
+.
 The computational requirement for the resulting mesh was significant, therefore two submesh was also constructed, see Fig.\ref{Fig::Mesh}.
@@
 
-The code used the FEniCS project to solve the PDE, using backwards Euler time discretization and first order continuous Galerkin finite elements.
+The code used the FEniCS project (v.2017.2)  to solve the PDE, using backwards Euler time discretization and first order continuous Galerkin finite elements.
 The linear problem was solved using GMRES, and the matrix was stored in the solver.
-The module dolfin adjoint ~\cite{farrell2013automated} \kam{correct ref?} was used to solve the PDE constrained optimization problem with the L-BFGS-B algorithm in the python module scipy.
-The convergence criteria for the minimization was set so that $max \lbrace | \text{proj} \hspace*{0.2cm} x_i | , \quad i = 1, .., N \rbrace \leq gtol=1.0e-1$ where $x_i$ is the i-th component of the gradient.
+The module dolfin adjoint ~\cite{farrell2013automated} \kam{correct ref?}  was used to solve the PDE constrained optimization problem with the L-BFGS-B algorithm in the python module scipy \cite{LBFGSB1},\cite{LBFGSB2}.
+
+The convergence criteria for the minimization was set so that $|| x ||_{L\sp{inf}} \leq \epsilon=1.0e-1$ with $x$ denoting the projected gradient.
 {\color{red} From scipy :The iteration will stop when $max\lbrace | \text{proj} \hspace*{0.2cm} g_i | , \quad i = 1, .., N \rbrace \leq gtol $  where $pg_i$ is the i-th component of the projected gradient.}
 
-The observations $u_{obs}$ have a fixed time-point $t_i$, these time-points may not overlap with the time discretization in the forward problem $t_j$.
-Therefore, after each time step $dt$ in Eq\ref{Eq::PDE}, it was checked if the time step contained the next observation.
-If it did, then a linear interpolation of the  current solution $u(t_j)$ and previous solution $u(t_{j-1})$ was used approximate the solution at time $t_i$.
+The observations $u_{obs}$ have a fixed time-points $t_i$, these time-points may not overlap with the time discretization in the forward problem $t_j$.
+Therefore a linear interpolation of the current solution $u(t_j)$ and previous solution $u(t_{j-1})$ was used approximate the solution at time $t_i$.
 The linear interpolation was given as
@@
 \end{equation}
-with $\Delta t = t_j-t_i$.
+with $\Delta t = t_j-t_i$ and $dt  = t_{j} - t_{j-1}$.
 
 The implementation used the first observation as initial conditions of Eq.\ref{Eq::PDE}.
-Then for each timestep, the next observation was used as the initial value for boundary control $g$, which was imposed on the external boundary of the domain $\Omega_1$.
-The initial values of the diffusion coefficients in the optimization algorithm $(D_{CSF}, D_{GM}, D_{WM})=$  $(1, 1, 1)$.
-However, to increase the convergence rate, $D_{CSF}$ was scaled with $100$.
-
-The noise susceptibility was tested by adding an uniform distribution noise term to the observations.
-The noise term was constructed using numpy.random and adjusted so that noise range becomes $\lbrace -n_{amp} , n_{amp} \rbrace $, with $n_{amp}$ defined as noise amplitude.
+Then for each time-step, the next observation was used as the initial value for boundary control $g$, which was imposed on the external boundary of the domain $\Omega_1$.
+In order to increase the convergence rate, $D_{CSF}$ was scaled so that $D_{CSF} = 100 D_{CSF}\sp{\star} $.
+The initial values of the diffusion coefficients in the optimization algorithm was $(D_{CSF}\sp{\star}, D_{GM}, D_{WM})=$  $(1, 1, 1)$.
+
+The noise susceptibility was tested by adding a uniform distribution noise term to the observations.
+The noise term was constructed using the random library in numpy and adjusted so that noise range becomes $\lbrace -n_{amp} , n_{amp} \rbrace $, with $n_{amp}$ defined as noise amplitude.
 
@@
 Below we will discuss the parameter identification and its sensitivity with respect to regularization parameters, noise and time-resolution.
-In presentation of the results, the relative error norm  $||\cdot||_{RE}$ is defined as 
+In presentation of the results, the relative error norm is defined as
 \begin{equation}
@@
 \subsubsection{The relaxation parameters}
-To assess the sensitivity of the the objective functional defined in Eq.\ref{Eq::F} with respect to the regularization parameters $\alpha$ and $\beta$ 
-we perform a systematic study of the reconstruction of the manufactured solution with respect to a wide range of regularization parameters. 
-Ideally, the approach should have a wide range of parameters in which the reconstruction algorithm yields very similar end-results although
-the convergence may vary substatantially.
+
+The convergence of the objective functional $F$ is influenced by the values of the regularization parameters $\alpha$ and $\beta$.
+Therefore the convergence was examined by a systematic study of the reconstruction of the manufactured solution with respect to a wide range of regularization parameters.
+
+%To assess the sensitivity of the the objective functional defined in Eq.\ref{Eq::F} with respect to the regularization parameters $\alpha$ and $\beta$ 
+%we perform a systematic study of the reconstruction of the manufactured solution with respect to a wide range of regularization parameters.
+
+Ideally, the approach should have a wide range of parameters in which the reconstruction algorithm yields very similar end-results although the convergence may vary substantially.
 The evaluation of different regularization parameters was done by solving the optimization with different values of $\alpha$ and $\beta$ and compare the controls with the manufactured solution.
-The observation times were selected with $t_i \in  \lbrace$ 2.4, 4.8, 7.2, 9.6, 12.0, 14.4, 16.8, 19.2, 21.6, 24.0 $\rbrace$, and the number of time-steps in the forward problem was set to $k= 10$.
-
-The results are shown in Tabel~\ref{Tab::1} together with the number of iteration used to reach the convergence criteria.
-It can be observed that for all $\alpha=1.0$ had significant relative error for $D_{\Omega_1}$, and this can also be observed for all $\beta=100$.
-These parameter selections fails to reconstructed the manufacured solutions, due to $g$ influence on $F$
+The observation times were selected with $t_i \in  \lbrace$ 2.4, 4.8, 7.2, 9.6, 12.0, 14.4, 16.8, 19.2, 21.6, 24.0 $\rbrace$, and the number of time-steps $k$ in the forward problem was set to $10$.
+
+The results shown in Tabel~\ref{Tab::1} shows similar end-result for most regularization parameters.
+However, in the case of $ \alpha=1.0$ the relative error over 100\% higher then for other values of $\alpha$.
+Furthermore, it can also be seen in the table that $ \forall \beta=100.0$ there is about 70\% relative error for $D_{\Omega_1}$ and approximate 10\% error for $D_{\Omega_2}$, which is higher than other values of $\beta$.
+
+From the results it can be discerned that $\alpha =1.0$ and $\beta=100.0$ represent an upper  boundary where the residual is no longer the dominant term in the objective functional.
 
@@
 \subsubsection{The number of timessteps}
-Increasing the number of timesteps in the computations potentially allow for a more accurate temporal reconstruction, but at the same time the number of observations per control decreases and the regularization therefore may play a larger role.
-Furthermore, the computational cost will increases due the number of iterations in the forward problem.
-Therefore finding the number of timesteps for an effective convergence can help for larger meshes.
+Increasing the number of time-steps in the computations can potentially allow for a more accurate temporal reconstruction, but at the same time the number of observations per control decreases and the regularization may therefore play a larger role.
+Furthermore, the computational cost will rise due to additional number of time-steps.
+%Thus finding the optimal number of time-steps can give an effective convergence for larger problems . 
 The computation used different regularization parameters with 10, 20 and 40 timesteps.
 
-The reults are show in Tab.\ref{TAB::timesteps}, and can be seen that for $\alpha=1.0$ the relative error increases with the number of timesteps.
-While for values $\alpha < 1.0 $, the relative error decreases with increasing number of timesteps.
-
-This prompted to look at the boundary control $g$ through time by selecting high and low values of $\alpha$ and $\beta$, see Fig \ref{boundarycontrol}.
+The results are given in Tab.\ref{TAB::timesteps}, and it can be seen $\forall \alpha=1.0$ that the relative error becomes bigger with more time-steps.
+This behavior can also be seen for $\alpha=1.0e-2$ and $\beta = 1.0e-4 , 1.0e-6$, and followed by a rise in the number of iterations.
+The increase time-steps causes most values of regularization parameters to increase number of iterations, but for some values the number of iterations decreases.
+These values share that $\alpha $ is a magnitude 2 lower than $ \beta$,i.e $\alpha=1.0e-2$ and $\beta =1.0$.
+This indicates that $\alpha $ should be smaller than $\beta$ to achieve optimal convergence.
+But taking into account the values in Table ~\ref{Tab::1} ??
+
+Given the boundary control $g$ through time by selecting high and low values of $\alpha$ and $\beta$, see Fig \ref{boundarycontrol}.
 Figure \ref{boundarycontrol} displays oscillations for $\alpha=1.0$ with $k=40$.
@@
 The number of observation were chosen to be 5, 10  and 20, and times were set to be evenly spaced.
-The range of regularization parameters were restricted to values that had previously low relative error.
+The range of regularization parameters were restricted to values that have low relative error.
 
 The results are shown in Tab.\ref{TAB::timesteps}, Tab.\ref{TAB::double} and Tab.\ref{TAB::half}.
-In the case of 10 observations, the number of timesteps showed a decrease in the relative error.
-Similar effects was observed for 5 and 20 observations.
-
-The relative boundary error for $\beta=1.0$  in Table~\ref{TAB::half} have similar value, independent on number of timesteps. This not the case for
-
-The spikes in Figure ~\ref{boundarycontrol} relates to the observation points $t_i$.
+In Tab.\ref{TAB::half}, the values $\alpha =1.0e-2$ and $\beta=1.0e-2,1.0e-4$ gives a surge in the relative error with more time-steps.
+This behavior is neither visible in Tab.\ref{TAB::timesteps} and Tab.\ref{TAB::double} given the same regularization parameters.
+
+In Table ~\ref{TAB::double} some values have a drastic change in convergence rate with increase of number of iteration (Hypothesis $i < k$ is better than $i = k$, i is number of observations)
+
+The observations functions as stabilization for the functional so that the error between observations becomes smaller, which gives a broader rang of adequate regularization parameters.
 
@@
 In Tabel~\ref{Tab::Noise0.03}, we can see that a noise amplitude of 0.03, (10$\%$ of maximum initial condition) had negligible effect on the relative error.
-However, in Tabel~\ref{Tab::Noise0.3} the noise amplitude was increased to 0.3 (100$\%$ of maximum initial condition) and it is observed that for  $\alpha < 1.0e-3$  $\beta < 1.0e-3$ the optimization failed to converge before reaching maximum iteration of 1000 steps.
+However, in Tabel~\ref{Tab::Noise0.3} the noise amplitude was increased to 0.3 (100$\%$ of maximum initial condition) and it is observed that for  $\alpha \leq 1.0e-4$  and $\beta \leq 1.0e-4$ the optimization failed to converge before reaching maximum iteration of 1000 steps.
 Furthermore, the relative boundary error $||g||_{RE(\Omega)}$ is  larger for lower values of $\beta$.
+
+Tt can be concluded from the results that increasing the number of iterations gives rise to oscillations for poor regularizations parameters.
 
@@
 Furthermore, bounds were added to the L-BFGS-B algorithm to ensure non-negative boundary controls and the convergence criteria was adjusted to $gtol=6.0e-1$.
-The number of timesteps were selected to be $k=24$ $k=48$, which gives $dt = 2 hour$ and $dt = 1 hour$.
+The number of timesteps were selected to be $k=24$ and $k=48$, which gives $dt = 2 hour$ and $dt = 1 hour$.
 
@@
 This corresponds to $1.85$ and $1.73$ in tortuosity, given that the self-diffusivity of water has been estimated to be around $3.0e-3\mathrm{mm\sp{2}/s}$ at $37\sp{o}C$.% This corresponds to 10.8 $\mathrm{mm\sp{2}/h}$ and  $\mathrm{mm\sp{2}/h}$.
-Then by using the reference value $3.8e-4 \mathrm{mm\sp{2}/s}$ for Gd-DPTA gives an estimate for the diffusion coefficient in the grey and white matter to respectively be $ 1.26\mathrm{mm\sp{2}/s}$ and $1.10 \mathrm{mm\sp{2}/s}$.
+Then by using the reference value $3.8e-4 \mathrm{mm\sp{2}/s}$ for Gd-DPTA gives an estimate for the diffusion coefficient in the grey and white matter to respectively be $ 1.26e-4\mathrm{mm\sp{2}/s}$ and $1.10e-4 \mathrm{mm\sp{2}/s}$.
 This estimation assumes that the tortuosity is independent on molecular size .
@@
 It can be observed that the upper right row displays a discrepancy, which likely due to wrong regularization parameters.
-This prompt the exclusion of the corresponding values, which gives an average computed values $0.65 \mathrm{mm\sp{2}/h}$ and  $0.80 \mathrm{mm\sp{2}/h}$ in respectively grey and white matter.
-Scaled to $\mathrm{mm\sp{2}/s}$ gives $1.8 \mathrm{mm\sp{2}/s}$ and $2.22 \mathrm{mm\sp{2}/s}$.
-
+This prompt the exclusion of the corresponding values, which gives an average computed values $??
+\mathrm{mm\sp{2}/h}$ and  $??
+\mathrm{mm\sp{2}/h}$ in respectively grey and white matter.
+Scaled to $\mathrm{mm\sp{2}/s}$ gives $1.8e-4\mathrm{mm\sp{2}/s}$ and $2.22e-4 \mathrm{mm\sp{2}/s}$.
+
+\subsection*{Compare high DTI values with computed}
 This gives a relative error of $42 \%$ in grey matter and $ 100 \%$ in white matter compared to the estimated values.
@@
 The computation require that there is tracer present to compute the diffusion coefficient.
-In Fig.\ref{Fig::realdata}, it can be seen that there are regions with negligible amount of tracers and vice versa.
-Considering $1.3 \mathrm{mm\sp{2}/s}$ as the upper bound gives an estimated upper bound $1.43$ diffusion coefficient in the white matter.
-This relative error of $54\%$ difference {\color{red} compare with dispersion, NB bare k 48 er brukt, k 24 skal med}
+In Fig.\ref{Fig::realdata}, it can be seen that there were regions with negligible amount of tracers and vice versa.
+
+The observation after 24 hours was used to compute the area containing $90\%$ of the  concentration in white matter.
+This area was then used to calculate the median diffusion coefficient given the data in Figure ~\ref{figuredti}, and it was estimated to be  $??
+e-3 \mathrm{mm\sp{2}/s}$.
+This correspondence to a tracer diffusion coefficient of $??e-4 \mathrm{mm\sp{2}/h}$ , which gives a relative error of $??\%$ difference compared to the computed values.
 
@@
 well for regularization parameters varying by orders of magnitude. It is particularly interesting to see that the procedure efficiently removes noise as demonstrated
-in the Figures \ref{12hourswithnoise} and \ref{24hourswithnoise} with noise levels of 30\% \kam{is this correctly stated}. 
+in the Figures \ref{12hourswithnoise} and \ref{24hourswithnoise} with noise levels of 30\% \kam{is this correctly stated}{\color{red} (0.3,-0.3) added to all values with peak of 1.3 at 12 h }. 
 Crucial in our application is the interplay between the regularization term that regulates the smoothness of the boundary conditions as well as
@@
 The regions with high diffusivity in Figure~\ref{figuredti},  have significant amount of diffusivity as seen in Figure~\ref{Fig::realdata}
+
 The computational model have 2 global controls for the diffusion coefficients, while it can be seen in  Fig.\ref{figuredti} that diffusion coefficients can be considered a spacial function.
@@
 \caption{Shows the regularization parameters $\alpha$ and $\beta$, number of timesteps $k$ and number of observation $\tau$ with the resulting number of iterations and the relative error for the control parameters.
-}
+{\color{red} check pvd }.}
 \begin{tabular}{*{8}c}
@@
 \hline 
-  1.0e+00 	 & 1.0e+02 	 & 10 & 499 	 & +5.125 & +0.278 & +0.105 & +0.127 \\ 
-  1.0e+00 	 & 1.0e+00 	 & 10 & 225 	 & +4.148 & +0.304 & +0.092 & +0.135 \\ 
-%\rowcolor{red}  1.0e+00 	 & 1.0e-01 	 & 10 & 206 	 & +4.272 & +0.305 & +0.091 & +0.142 \\ 
- 1.0e+00 	 & 1.0e-02 	 & 10 & 233 	 & +4.272 & +0.305 & +0.091 & +0.143 \\ 
-%\rowcolor{red}  1.0e+00 	 & 1.0e-03 	 & 10 & 208 	 & +4.437 & +0.305 & +0.091 & +0.143 \\ 
- 1.0e+00 	 & 1.0e-04 	 & 10 & 204 	 & +4.271 & +0.306 & +0.091 & +0.143 \\ 
-%\rowcolor{red}  1.0e+00 	 & 1.0e-05 	 & 10 & 203 	 & +4.400 & +0.305 & +0.091 & +0.143 \\ 
- 1.0e+00 	 & 1.0e-06 	 & 10 & 222 	 & +4.584 & +0.304 & +0.090 & +0.143 \\
-
-% 1.0e-01 	 & 1.0e+00 	 & 10 & 207 	 & +0.127 & +0.093 & +0.041 & +0.027 \\ 
- %1.0e-01 	 & 1.0e-01 	 & 10 & 196 	 & +0.121 & +0.093 & +0.041 & +0.046 \\ 
-% 1.0e-01 	 & 1.0e-02 	 & 10 & 232 	 & +0.123 & +0.093 & +0.041 & +0.056 \\ 
- %1.0e-01 	 & 1.0e-03 	 & 10 & 183 	 & +0.122 & +0.093 & +0.040 & +0.057 \\ 
-% 1.0e-01 	 & 1.0e-04 	 & 10 & 212 	 & +0.122 & +0.093 & +0.040 & +0.057 \\ 
- %1.0e-01 	 & 1.0e-05 	 & 10 & 168 	 & +0.122 & +0.093 & +0.041 & +0.057 \\
-% 1.0e-01 	 & 1.0e-06 	 & 10 & 195 	 & +0.122 & +0.093 & +0.041 & +0.057 \\ 
- 1.0e-02 	 & 1.0e+02 	 & 10 & 228 	 & +0.702 & +0.106 & +0.035 & +0.033 \\ 
- 1.0e-02 	 & 1.0e+00 	 & 10 & 227 	 & +0.015 & +0.067 & +0.039 & +0.018 \\ 
- %1.0e-02 	 & 1.0e-01 	 & 10 & 153 	 & +0.006 & +0.065 & +0.039 & +0.021 \\ 
- 1.0e-02 	 & 1.0e-02 	 & 10 & 184 	 & +0.005 & +0.065 & +0.039 & +0.039 \\ 
- %1.0e-02 	 & 1.0e-03 	 & 10 & 176 	 & +0.004 & +0.065 & +0.039 & +0.048 \\ 
- 1.0e-02 	 & 1.0e-04 	 & 10 & 195 	 & +0.005 & +0.065 & +0.039 & +0.049 \\ 
- %1.0e-02 	 & 1.0e-05 	 & 10 & 215 	 & +0.004 & +0.065 & +0.039 & +0.051 \\ 
- 1.0e-02 	 & 1.0e-06 	 & 10 & 205 	 & +0.005 & +0.065 & +0.039 & +0.050 \\
-
- %1.0e-03 	 & 1.0e+00 	 & 10 & 179 	 & +0.004 & +0.064 & +0.039 & +0.019 \\ 
- %1.0e-03 	 & 1.0e-01 	 & 10 & 221 	 & -0.005 & +0.063 & +0.039 & +0.018 \\ 
- %1.0e-03 	 & 1.0e-02 	 & 10 & 89 	 & -0.007 & +0.063 & +0.039 & +0.026 \\ 
- %1.0e-03 	 & 1.0e-03 	 & 10 & 77 	 & -0.005 & +0.062 & +0.039 & +0.027 \\ 
- %1.0e-03 	 & 1.0e-04 	 & 10 & 100 	 & -0.006 & +0.062 & +0.039 & +0.027 \\ 
- %1.0e-03 	 & 1.0e-05 	 & 10 & 105 	 & -0.006 & +0.062 & +0.039 & +0.027 \\ 
- %1.0e-03 	 & 1.0e-06 	 & 10 & 123 	 & -0.007 & +0.062 & +0.039 & +0.028 \\
-
- 1.0e-04 	 & 1.0e+02 	 & 10 & 167 	 & +0.688 & +0.104 & +0.035 & +0.032 \\ 
- 1.0e-04 	 & 1.0e+00 	 & 10 & 236 	 & +0.004 & +0.063 & +0.039 & +0.019 \\ 
- %1.0e-04 	 & 1.0e-01 	 & 10 & 195 	 & -0.006 & +0.062 & +0.039 & +0.018 \\ 
- 1.0e-04 	 & 1.0e-02 	 & 10 & 152 	 & -0.006 & +0.062 & +0.039 & +0.022 \\ 
- %1.0e-04 	 & 1.0e-03 	 & 10 & 119 	 & -0.008 & +0.062 & +0.039 & +0.026 \\ 
- 1.0e-04 	 & 1.0e-04 	 & 10 & 106 	 & -0.007 & +0.062 & +0.039 & +0.026 \\ 
- %1.0e-04 	 & 1.0e-05 	 & 10 & 109 	 & -0.007 & +0.062 & +0.039 & +0.026 \\ 
- 1.0e-04 	 & 1.0e-06 	 & 10 & 99 	 & -0.008 & +0.062 & +0.039 & +0.026 \\
-
- %1.0e-05 	 & 1.0e+00 	 & 10 & 139 	 & +0.004 & +0.063 & +0.039 & +0.019 \\ 
- %1.0e-05 	 & 1.0e-01 	 & 10 & 170 	 & -0.006 & +0.062 & +0.039 & +0.018 \\ 
- %1.0e-05 	 & 1.0e-02 	 & 10 & 182 	 & -0.007 & +0.062 & +0.039 & +0.020 \\ 
- %1.0e-05 	 & 1.0e-03 	 & 10 & 70 	 & -0.007 & +0.062 & +0.039 & +0.026 \\ 
- %1.0e-05 	 & 1.0e-04 	 & 10 & 77 	 & -0.007 & +0.062 & +0.039 & +0.026 \\ 
- %1.0e-05 	 & 1.0e-05 	 & 10 & 104 	 & -0.008 & +0.062 & +0.039 & +0.026 \\ 
- %1.0e-05 	 & 1.0e-06 	 & 10 & 92 	 & -0.007 & +0.062 & +0.039 & +0.026 \\ 
- 1.0e-06 	 & 1.0e+02 	 & 10 & 210 	 & +0.685 & +0.104 & +0.035 & +0.032 \\ 
- 1.0e-06 	 & 1.0e+00 	 & 10 & 163 	 & +0.003 & +0.064 & +0.039 & +0.019 \\ 
- %1.0e-06 	 & 1.0e-01 	 & 10 & 218 	 & -0.006 & +0.062 & +0.039 & +0.018 \\ 
- 1.0e-06 	 & 1.0e-02 	 & 10 & 134 	 & -0.008 & +0.062 & +0.039 & +0.023 \\ 
- %1.0e-06 	 & 1.0e-03 	 & 10 & 79 	 & -0.006 & +0.062 & +0.039 & +0.026 \\ 
- 1.0e-06 	 & 1.0e-04 	 & 10 & 107 	 & -0.007 & +0.062 & +0.039 & +0.026 \\ 
- %1.0e-06 	 & 1.0e-05 	 & 10 & 103 	 & -0.008 & +0.062 & +0.039 & +0.026 \\ 
- 1.0e-06 	 & 1.0e-06 	 & 10 & 91 	 & -0.008 & +0.062 & +0.039 & +0.026 \\  
+ 1.0e+00 	 & 1.0e+02 	 & 10 & 437 	 & +4.631 & +0.283 & +0.103 & +0.127 \\ 
+ 1.0e+00 	 & 1.0e+00 	 & 10 & 129 	 & +1.638 & +0.224 & +0.089 & +0.119 \\ 
+ 1.0e+00 	 & 1.0e-02 	 & 10 & 129 	 & +1.602 & +0.223 & +0.089 & +0.119 \\ 
+ 1.0e+00 	 & 1.0e-04 	 & 10 & 151 	 & +1.608 & +0.223 & +0.089 & +0.119 \\ 
+ 1.0e+00 	 & 1.0e-06 	 & 10 & 133 	 & +1.603 & +0.223 & +0.089 & +0.119 \\ 
+ 1.0e-02 	 & 1.0e+02 	 & 10 & 186 	 & +0.649 & +0.111 & +0.036 & +0.033 \\ 
+ 1.0e-02 	 & 1.0e+00 	 & 10 & 125 	 & -0.027 & +0.041 & +0.036 & +0.026 \\ 
+ 1.0e-02 	 & 1.0e-02 	 & 10 & 133 	 & -0.039 & +0.039 & +0.036 & +0.026 \\ 
+ 1.0e-02 	 & 1.0e-04 	 & 10 & 108 	 & -0.039 & +0.039 & +0.036 & +0.026 \\ 
+ 1.0e-02 	 & 1.0e-06 	 & 10 & 154 	 & -0.039 & +0.039 & +0.036 & +0.026 \\ 
+ 1.0e-04 	 & 1.0e+02 	 & 10 & 212 	 & +0.636 & +0.108 & +0.035 & +0.032 \\ 
+ 1.0e-04 	 & 1.0e+00 	 & 10 & 143 	 & -0.036 & +0.039 & +0.035 & +0.026 \\ 
+ 1.0e-04 	 & 1.0e-02 	 & 10 & 108 	 & -0.047 & +0.037 & +0.036 & +0.026 \\ 
+ 1.0e-04 	 & 1.0e-04 	 & 10 & 158 	 & -0.047 & +0.037 & +0.036 & +0.026 \\ 
+ 1.0e-04 	 & 1.0e-06 	 & 10 & 142 	 & -0.047 & +0.037 & +0.036 & +0.026 \\ 
+ 1.0e-06 	 & 1.0e+02 	 & 10 & 203 	 & +0.636 & +0.108 & +0.035 & +0.032 \\ 
+ 1.0e-06 	 & 1.0e+00 	 & 10 & 117 	 & -0.035 & +0.039 & +0.035 & +0.026 \\ 
+ 1.0e-06 	 & 1.0e-02 	 & 10 & 120 	 & -0.047 & +0.037 & +0.036 & +0.026 \\ 
+ 1.0e-06 	 & 1.0e-04 	 & 10 & 122 	 & -0.047 & +0.037 & +0.036 & +0.026 \\ 
+ 1.0e-06 	 & 1.0e-06 	 & 10 & 133 	 & -0.047 & +0.037 & +0.036 & +0.026 \\ 
+%  1.0e+00 	 & 1.0e+02 	 & 10 & 499 	 & +5.125 & +0.278 & +0.105 & +0.127 \\ 
+%  1.0e+00 	 & 1.0e+00 	 & 10 & 225 	 & +4.148 & +0.304 & +0.092 & +0.135 \\ 
+%%\rowcolor{red}  1.0e+00 	 & 1.0e-01 	 & 10 & 206 	 & +4.272 & +0.305 & +0.091 & +0.142 \\ 
+% 1.0e+00 	 & 1.0e-02 	 & 10 & 233 	 & +4.272 & +0.305 & +0.091 & +0.143 \\ 
+%%\rowcolor{red}  1.0e+00 	 & 1.0e-03 	 & 10 & 208 	 & +4.437 & +0.305 & +0.091 & +0.143 \\ 
+% 1.0e+00 	 & 1.0e-04 	 & 10 & 204 	 & +4.271 & +0.306 & +0.091 & +0.143 \\ 
+%%\rowcolor{red}  1.0e+00 	 & 1.0e-05 	 & 10 & 203 	 & +4.400 & +0.305 & +0.091 & +0.143 \\ 
+% 1.0e+00 	 & 1.0e-06 	 & 10 & 222 	 & +4.584 & +0.304 & +0.090 & +0.143 \\
+% 
+%% 1.0e-01 	 & 1.0e+00 	 & 10 & 207 	 & +0.127 & +0.093 & +0.041 & +0.027 \\ 
+% %1.0e-01 	 & 1.0e-01 	 & 10 & 196 	 & +0.121 & +0.093 & +0.041 & +0.046 \\ 
+%% 1.0e-01 	 & 1.0e-02 	 & 10 & 232 	 & +0.123 & +0.093 & +0.041 & +0.056 \\ 
+% %1.0e-01 	 & 1.0e-03 	 & 10 & 183 	 & +0.122 & +0.093 & +0.040 & +0.057 \\ 
+%% 1.0e-01 	 & 1.0e-04 	 & 10 & 212 	 & +0.122 & +0.093 & +0.040 & +0.057 \\ 
+% %1.0e-01 	 & 1.0e-05 	 & 10 & 168 	 & +0.122 & +0.093 & +0.041 & +0.057 \\
+%% 1.0e-01 	 & 1.0e-06 	 & 10 & 195 	 & +0.122 & +0.093 & +0.041 & +0.057 \\ 
+% 1.0e-02 	 & 1.0e+02 	 & 10 & 228 	 & +0.702 & +0.106 & +0.035 & +0.033 \\ 
+% 1.0e-02 	 & 1.0e+00 	 & 10 & 227 	 & +0.015 & +0.067 & +0.039 & +0.018 \\ 
+% %1.0e-02 	 & 1.0e-01 	 & 10 & 153 	 & +0.006 & +0.065 & +0.039 & +0.021 \\ 
+% 1.0e-02 	 & 1.0e-02 	 & 10 & 184 	 & +0.005 & +0.065 & +0.039 & +0.039 \\ 
+% %1.0e-02 	 & 1.0e-03 	 & 10 & 176 	 & +0.004 & +0.065 & +0.039 & +0.048 \\ 
+% 1.0e-02 	 & 1.0e-04 	 & 10 & 195 	 & +0.005 & +0.065 & +0.039 & +0.049 \\ 
+% %1.0e-02 	 & 1.0e-05 	 & 10 & 215 	 & +0.004 & +0.065 & +0.039 & +0.051 \\ 
+% 1.0e-02 	 & 1.0e-06 	 & 10 & 205 	 & +0.005 & +0.065 & +0.039 & +0.050 \\ 
+%
+% %1.0e-03 	 & 1.0e+00 	 & 10 & 179 	 & +0.004 & +0.064 & +0.039 & +0.019 \\ 
+% %1.0e-03 	 & 1.0e-01 	 & 10 & 221 	 & -0.005 & +0.063 & +0.039 & +0.018 \\ 
+% %1.0e-03 	 & 1.0e-02 	 & 10 & 89 	 & -0.007 & +0.063 & +0.039 & +0.026 \\ 
+% %1.0e-03 	 & 1.0e-03 	 & 10 & 77 	 & -0.005 & +0.062 & +0.039 & +0.027 \\ 
+% %1.0e-03 	 & 1.0e-04 	 & 10 & 100 	 & -0.006 & +0.062 & +0.039 & +0.027 \\ 
+% %1.0e-03 	 & 1.0e-05 	 & 10 & 105 	 & -0.006 & +0.062 & +0.039 & +0.027 \\ 
+% %1.0e-03 	 & 1.0e-06 	 & 10 & 123 	 & -0.007 & +0.062 & +0.039 & +0.028 \\ 
+%
+% 1.0e-04 	 & 1.0e+02 	 & 10 & 167 	 & +0.688 & +0.104 & +0.035 & +0.032 \\ 
+% 1.0e-04 	 & 1.0e+00 	 & 10 & 236 	 & +0.004 & +0.063 & +0.039 & +0.019 \\ 
+% %1.0e-04 	 & 1.0e-01 	 & 10 & 195 	 & -0.006 & +0.062 & +0.039 & +0.018 \\ 
+% 1.0e-04 	 & 1.0e-02 	 & 10 & 152 	 & -0.006 & +0.062 & +0.039 & +0.022 \\ 
+% %1.0e-04 	 & 1.0e-03 	 & 10 & 119 	 & -0.008 & +0.062 & +0.039 & +0.026 \\ 
+% 1.0e-04 	 & 1.0e-04 	 & 10 & 106 	 & -0.007 & +0.062 & +0.039 & +0.026 \\ 
+% %1.0e-04 	 & 1.0e-05 	 & 10 & 109 	 & -0.007 & +0.062 & +0.039 & +0.026 \\ 
+% 1.0e-04 	 & 1.0e-06 	 & 10 & 99 	 & -0.008 & +0.062 & +0.039 & +0.026 \\
+% 
+% %1.0e-05 	 & 1.0e+00 	 & 10 & 139 	 & +0.004 & +0.063 & +0.039 & +0.019 \\ 
+% %1.0e-05 	 & 1.0e-01 	 & 10 & 170 	 & -0.006 & +0.062 & +0.039 & +0.018 \\ 
+% %1.0e-05 	 & 1.0e-02 	 & 10 & 182 	 & -0.007 & +0.062 & +0.039 & +0.020 \\ 
+% %1.0e-05 	 & 1.0e-03 	 & 10 & 70 	 & -0.007 & +0.062 & +0.039 & +0.026 \\ 
+% %1.0e-05 	 & 1.0e-04 	 & 10 & 77 	 & -0.007 & +0.062 & +0.039 & +0.026 \\ 
+% %1.0e-05 	 & 1.0e-05 	 & 10 & 104 	 & -0.008 & +0.062 & +0.039 & +0.026 \\ 
+% %1.0e-05 	 & 1.0e-06 	 & 10 & 92 	 & -0.007 & +0.062 & +0.039 & +0.026 \\ 
+% 1.0e-06 	 & 1.0e+02 	 & 10 & 210 	 & +0.685 & +0.104 & +0.035 & +0.032 \\ 
+% 1.0e-06 	 & 1.0e+00 	 & 10 & 163 	 & +0.003 & +0.064 & +0.039 & +0.019 \\ 
+% %1.0e-06 	 & 1.0e-01 	 & 10 & 218 	 & -0.006 & +0.062 & +0.039 & +0.018 \\ 
+% 1.0e-06 	 & 1.0e-02 	 & 10 & 134 	 & -0.008 & +0.062 & +0.039 & +0.023 \\ 
+% %1.0e-06 	 & 1.0e-03 	 & 10 & 79 	 & -0.006 & +0.062 & +0.039 & +0.026 \\ 
+% 1.0e-06 	 & 1.0e-04 	 & 10 & 107 	 & -0.007 & +0.062 & +0.039 & +0.026 \\ 
+% %1.0e-06 	 & 1.0e-05 	 & 10 & 103 	 & -0.008 & +0.062 & +0.039 & +0.026 \\ 
+% 1.0e-06 	 & 1.0e-06 	 & 10 & 91 	 & -0.008 & +0.062 & +0.039 & +0.026 \\  
 \end{tabular}
@@
 \caption{ Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$, the resulting number of iterations, the relative error of the estimated diffusion coefficients and the relative error for $g$.
-}
+{\color{red} check pvd }}
 \begin{tabular}{*{8}c}
@@
 \hline
-
- %1.0e+00 	 & 1.0e+00 	 & 10 & 128 	 & +1.587 & +0.217 & +0.091 & +0.119 \\
-
- 1.0e+00 	 & 1.0e+00 	 & 20 & 268 	 & +5.537 & +0.321 & +0.152 & +0.128 \\ 
- 1.0e+00 	 & 1.0e+00 	 & 40 & 381 	 & +12.346 & +0.890 & +0.249 & +0.154\\
-
- 1.0e+00 	 & 1.0e-02 	 & 20 & 407 	 & +17.676 & +1.417 & +0.402 & +0.251 \\ 
- 1.0e+00 	 & 1.0e-02 	 & 40 & 873 	 & +61.467 & +17.965 & +16.437 & +0.614 \\
-
-% 1.0e+00 	 & 1.0e-04 	 & 10 & 130 	 & +1.558 & +0.216 & +0.091 & +0.119 \\ 
- 1.0e+00 	 & 1.0e-04 	 & 20 & 497 	 & +19.414 & +1.514 & +0.422 & +0.259\\ 
- 1.0e+00 	 & 1.0e-04 	 & 40 & 872 	 & +63.564 & +18.579 & +17.218 & +0.641 \\
-
- 1.0e-02 	 & 1.0e+00 	 & 20 & 157 	 & +0.016 & +0.004 & +0.008 & +0.007 \\ 
- 1.0e-02 	 & 1.0e+00 	 & 40 & 277 	 & +0.020 & -0.006 & +0.001 & +0.003 \\
-
- 1.0e-02 	 & 1.0e-02 	 & 20 & 447 	 & +0.130 & +0.055 & -0.000 & +0.016 \\ 
- 1.0e-02 	 & 1.0e-02 	 & 40 & 458 	 & +0.098 & +0.088 & +0.002 & +0.023 \\
-
- 1.0e-02 	 & 1.0e-04 	 & 20 & 595 	 & +0.175 & +0.081 & -0.003 & +0.090 \\ 
- 1.0e-02 	 & 1.0e-04 	 & 40 & 976 	 & +0.320 & +0.398 & +0.088 & +0.226 \\
-
-% 1.0e-04 	 & 1.0e+00 	 & 10 & 140 	 & -0.048 & +0.032 & +0.035 & +0.026 \\ 
- 1.0e-04 	 & 1.0e+00 	 & 20 & 165 	 & +0.006 & +0.000 & +0.008 & +0.007 \\ 
- 1.0e-04 	 & 1.0e+00 	 & 40 & 285 	 & +0.005 & -0.013 & +0.000 & +0.003 \\ 
- %1.0e-04 	 & 1.0e-01 	 & 20 & 367 	 & +0.028 & +0.010 & +0.008 & +0.007 \\
- %1.0e-04 	 & 1.0e-01 	 & 40 & 422 	 & +0.001 & -0.007 & +0.004 & +0.005 \\  
- 1.0e-04 	 & 1.0e-02 	 & 20 & 258 	 & +0.068 & +0.023 & +0.005 & +0.006 \\ 
- 1.0e-04 	 & 1.0e-02 	 & 40 & 339 	 & +0.004 & +0.002 & +0.002 & +0.003 \\
-
- %1.0e-04 	 & 1.0e-04 	 & 10 & 113 	 & -0.060 & +0.030 & +0.036 & +0.026 \\ 
- 1.0e-04 	 & 1.0e-04 	 & 20 & 322 	 & +0.105 & +0.031 & -0.003 & +0.020 \\ 
- 1.0e-04 	 & 1.0e-04 	 & 40 & 358 	 & -0.011 & -0.005 & -0.003 & +0.004 \\
-
-% 1.0e-05 	 & 1.0e+00 	 & 20 & 237 	 & -0.006 & +0.004 & +0.013 & +0.008 \\ 
- %1.0e-05 	 & 1.0e+00 	 & 40 & 358 	 & -0.018 & -0.019 & +0.005 & +0.007 \\  
- %1.0e-05 	 & 1.0e-01 	 & 20 & 290 	 & +0.026 & +0.010 & +0.008 & +0.007 \\
- %1.0e-05 	 & 1.0e-01 	 & 40 & 419 	 & +0.001 & -0.007 & +0.004 & +0.005 \\    
- %1.0e-05 	 & 1.0e-02 	 & 20 & 316 	 & +0.071 & +0.025 & +0.005 & +0.007 \\ 
- %1.0e-05 	 & 1.0e-02 	 & 40 & 401 	 & +0.004 & +0.003 & +0.002 & +0.004 \\  
- 1.0e-06 	 & 1.0e+00 	 & 20 & 219 	 & -0.007 & +0.004 & +0.013 & +0.008 \\ 
- 1.0e-06 	 & 1.0e+00 	 & 40 & 240 	 & -0.020 & -0.019 & +0.005 & +0.007 \\ 
- %1.0e-06 	 & 1.0e-01 	 & 20 & 250 	 & +0.027 & +0.010 & +0.008 & +0.007 \\ 
- %1.0e-06 	 & 1.0e-01 	 & 40 & 365 	 & +0.000 & -0.007 & +0.004 & +0.005 \\ 
- 1.0e-06 	 & 1.0e-02 	 & 20 & 379 	 & +0.070 & +0.025 & +0.005 & +0.007 \\ 
- 1.0e-06 	 & 1.0e-02 	 & 40 & 386 	 & +0.004 & +0.003 & +0.002 & +0.004 \\
-
- 1.0e-06 	 & 1.0e-04 	 & 20 & 356 	 & +0.101 & +0.028 & -0.002 & +0.021 \\ 
- 1.0e-06 	 & 1.0e-04 	 & 40 & 410 	 & -0.011 & -0.002 & -0.003 & +0.004 \\ 
+ 1.0e+00 	 & 1.0e+02 	 & 20 & 600 	 & +6.412 & +0.175 & +0.086 & +0.124 \\
+ 1.0e+00 	 & 1.0e+02 	 & 40 &  -   & +6.702 & +0.130 & +0.082 & +0.125 \\  
+ 1.0e+00 	 & 1.0e+00 	 & 20 & 300 	 & +5.538 & +0.324 & +0.148 & +0.128 \\ 
+ 1.0e+00 	 & 1.0e+00 	 & 40 & 346 	 & +11.392 & +0.873 & +0.242 & +0.154 \\ 
+ 1.0e+00 	 & 1.0e-02 	 & 20 & 415 	 & +18.156 & +1.378  & +0.389  & +0.251 \\ 
+ 1.0e+00 	 & 1.0e-02 	 & 40 & 856 	 & +64.050 & +17.408 & +15.950 & +0.614 \\ 
+ 1.0e+00 	 & 1.0e-04 	 & 20 & 417 	 & +17.747 & +1.465  & +0.406  & +0.258 \\ 
+ 1.0e+00 	 & 1.0e-04 	 & 40 & 946 	 & +72.594 & +17.985 & +16.702 & +0.641 \\
+ 1.0e+00 	 & 1.0e-06 	 & 20 & 399 	 & +17.407 & +1.466  & +0.406  & +0.258 \\ 
+ 1.0e+00 	 & 1.0e-06 	 & 40 & 863 	 & +60.448 & +18.043 & +16.732 & +0.641 \\
+ \hline
+ 1.0e-02 	 & 1.0e+02 	 & 20 & 351 	 & +0.865 & +0.001 & +0.017 & +0.027 \\ 
+ 1.0e-02 	 & 1.0e+02 	 & 40 & 404 	 & +0.846 & -0.049 & +0.010 & +0.026 \\ 
+ 1.0e-02 	 & 1.0e+00 	 & 20 & 254 	 & +0.018 & +0.007 & +0.008 & +0.007 \\ 
+ 1.0e-02 	 & 1.0e+00 	 & 40 & 218 	 & +0.020 & -0.006 & +0.001 & +0.003 \\ 
+ 1.0e-02 	 & 1.0e-02 	 & 20 & 381 	 & +0.127 & +0.057 & -0.001 & +0.016 \\ 
+ 1.0e-02 	 & 1.0e-02 	 & 40 & 543 	 & +0.099 & +0.087 & +0.002 & +0.023 \\
+ 1.0e-02 	 & 1.0e-04 	 & 20 & 641 	 & +0.171 & +0.082 & -0.003 & +0.091 \\ 
+ 1.0e-02 	 & 1.0e-04 	 & 40 & 879 	 & +0.303 & +0.383 & +0.079 & +0.222 \\ 
+ 1.0e-02 	 & 1.0e-06 	 & 20 & 547 	 & +0.173 & +0.084 & -0.003 & +0.092 \\
+ 1.0e-02 	 & 1.0e-06 	 & 40 & 844 	 & +0.332 & +0.416 & +0.095 & +0.239 \\ 
+ \hline 
+ 1.0e-04 	 & 1.0e+02 	 & 20 & 257 	 & +0.853 & -0.001 & +0.017 & +0.026 \\ 
+ 1.0e-04 	 & 1.0e+02 	 & 40 & 532 	 & +0.822 & -0.051 & +0.010 & +0.026 \\ 
+ 1.0e-04 	 & 1.0e+00 	 & 20 & 164 	 & +0.008 & +0.003 & +0.008 & +0.007 \\ 
+ 1.0e-04 	 & 1.0e+00 	 & 40 & 203 	 & +0.005 & -0.012 & +0.001 & +0.003 \\  
+ 1.0e-04 	 & 1.0e-02 	 & 20 & 313 	 & +0.071 & +0.021 & -0.001 & +0.007 \\ 
+ 1.0e-04 	 & 1.0e-02 	 & 40 & 294 	 & +0.004 & +0.004 & -0.001 & +0.001 \\ 
+ 1.0e-04 	 & 1.0e-04 	 & 20 & 265 	 & +0.108 & +0.035 & -0.002 & +0.014 \\
+ 1.0e-04 	 & 1.0e-04 	 & 40 & 401 	 & -0.010 & -0.002 & -0.002 & +0.004 \\ 
+ 1.0e-04 	 & 1.0e-06 	 & 20 & 452 	 & +0.066 & +0.021 & -0.003 & +0.031 \\ 
+ 1.0e-04 	 & 1.0e-06 	 & 40 & 330 	 & -0.014 & -0.013 & -0.003 & +0.004 \\ 
+ \hline
+ 1.0e-06 	 & 1.0e+02 	 & 20 & 274 	 & +0.850 & -0.001 & +0.017 & +0.026 \\ 
+ 1.0e-06 	 & 1.0e+02 	 & 40 & 496 	 & +0.821 & -0.051 & +0.010 & +0.026 \\
+ 1.0e-06 	 & 1.0e+00 	 & 20 & 176 	 & +0.008 & +0.003 & +0.008 & +0.007 \\ 
+ 1.0e-06 	 & 1.0e+00 	 & 40 & 207 	 & +0.006 & -0.012 & +0.001 & +0.003 \\ 
+ 1.0e-06 	 & 1.0e-02 	 & 20 & 223 	 & +0.075 & +0.024 & -0.001 & +0.007 \\ 
+ 1.0e-06 	 & 1.0e-02 	 & 40 & 392 	 & +0.000 & -0.001 & -0.001 & +0.002 \\ 
+ 1.0e-06 	 & 1.0e-04 	 & 20 & 429 	 & +0.085 & +0.027 & -0.002 & +0.025 \\ 
+ 1.0e-06 	 & 1.0e-04 	 & 40 & 241 	 & -0.020 & -0.030 & -0.005 & +0.005 \\ 
+ 1.0e-06 	 & 1.0e-06 	 & 20 & 591 	 & +0.060 & +0.021 & -0.003 & +0.048 \\ 
+ 1.0e-06 	 & 1.0e-06 	 & 40 & 343 	 & -0.014 & -0.010 & -0.003 & +0.004 \\ 
+% %1.0e+00 	 & 1.0e+00 	 & 10 & 128 	 & +1.587 & +0.217 & +0.091 & +0.119 \\ 
+% 
+% 1.0e+00 	 & 1.0e+00 	 & 20 & 268 	 & +5.537 & +0.321 & +0.152 & +0.128 \\ 
+% 1.0e+00 	 & 1.0e+00 	 & 40 & 381 	 & +12.346 & +0.890 & +0.249 & +0.154\\ 
+% 
+% 1.0e+00 	 & 1.0e-02 	 & 20 & 407 	 & +17.676 & +1.417 & +0.402 & +0.251 \\ 
+% 1.0e+00 	 & 1.0e-02 	 & 40 & 873 	 & +61.467 & +17.965 & +16.437 & +0.614 \\ 
+% 
+%% 1.0e+00 	 & 1.0e-04 	 & 10 & 130 	 & +1.558 & +0.216 & +0.091 & +0.119 \\ 
+% 1.0e+00 	 & 1.0e-04 	 & 20 & 497 	 & +19.414 & +1.514 & +0.422 & +0.259\\ 
+% 1.0e+00 	 & 1.0e-04 	 & 40 & 872 	 & +63.564 & +18.579 & +17.218 & +0.641 \\ 
+%
+% 1.0e-02 	 & 1.0e+00 	 & 20 & 157 	 & +0.016 & +0.004 & +0.008 & +0.007 \\ 
+% 1.0e-02 	 & 1.0e+00 	 & 40 & 277 	 & +0.020 & -0.006 & +0.001 & +0.003 \\ 
+% 
+% 1.0e-02 	 & 1.0e-02 	 & 20 & 447 	 & +0.130 & +0.055 & -0.000 & +0.016 \\ 
+% 1.0e-02 	 & 1.0e-02 	 & 40 & 458 	 & +0.098 & +0.088 & +0.002 & +0.023 \\ 
+% 
+% 1.0e-02 	 & 1.0e-04 	 & 20 & 595 	 & +0.175 & +0.081 & -0.003 & +0.090 \\ 
+% 1.0e-02 	 & 1.0e-04 	 & 40 & 976 	 & +0.320 & +0.398 & +0.088 & +0.226 \\ 
+% 
+%% 1.0e-04 	 & 1.0e+00 	 & 10 & 140 	 & -0.048 & +0.032 & +0.035 & +0.026 \\ 
+% 1.0e-04 	 & 1.0e+00 	 & 20 & 165 	 & +0.006 & +0.000 & +0.008 & +0.007 \\ 
+% 1.0e-04 	 & 1.0e+00 	 & 40 & 285 	 & +0.005 & -0.013 & +0.000 & +0.003 \\ 
+% %1.0e-04 	 & 1.0e-01 	 & 20 & 367 	 & +0.028 & +0.010 & +0.008 & +0.007 \\
+% %1.0e-04 	 & 1.0e-01 	 & 40 & 422 	 & +0.001 & -0.007 & +0.004 & +0.005 \\  
+% 1.0e-04 	 & 1.0e-02 	 & 20 & 258 	 & +0.068 & +0.023 & +0.005 & +0.006 \\ 
+% 1.0e-04 	 & 1.0e-02 	 & 40 & 339 	 & +0.004 & +0.002 & +0.002 & +0.003 \\  
+% 
+% %1.0e-04 	 & 1.0e-04 	 & 10 & 113 	 & -0.060 & +0.030 & +0.036 & +0.026 \\ 
+% 1.0e-04 	 & 1.0e-04 	 & 20 & 322 	 & +0.105 & +0.031 & -0.003 & +0.020 \\ 
+% 1.0e-04 	 & 1.0e-04 	 & 40 & 358 	 & -0.011 & -0.005 & -0.003 & +0.004 \\ 
+% 
+%% 1.0e-05 	 & 1.0e+00 	 & 20 & 237 	 & -0.006 & +0.004 & +0.013 & +0.008 \\ 
+% %1.0e-05 	 & 1.0e+00 	 & 40 & 358 	 & -0.018 & -0.019 & +0.005 & +0.007 \\  
+% %1.0e-05 	 & 1.0e-01 	 & 20 & 290 	 & +0.026 & +0.010 & +0.008 & +0.007 \\
+% %1.0e-05 	 & 1.0e-01 	 & 40 & 419 	 & +0.001 & -0.007 & +0.004 & +0.005 \\    
+% %1.0e-05 	 & 1.0e-02 	 & 20 & 316 	 & +0.071 & +0.025 & +0.005 & +0.007 \\ 
+% %1.0e-05 	 & 1.0e-02 	 & 40 & 401 	 & +0.004 & +0.003 & +0.002 & +0.004 \\  
+% 1.0e-06 	 & 1.0e+00 	 & 20 & 219 	 & -0.007 & +0.004 & +0.013 & +0.008 \\ 
+% 1.0e-06 	 & 1.0e+00 	 & 40 & 240 	 & -0.020 & -0.019 & +0.005 & +0.007 \\ 
+% %1.0e-06 	 & 1.0e-01 	 & 20 & 250 	 & +0.027 & +0.010 & +0.008 & +0.007 \\ 
+% %1.0e-06 	 & 1.0e-01 	 & 40 & 365 	 & +0.000 & -0.007 & +0.004 & +0.005 \\ 
+% 1.0e-06 	 & 1.0e-02 	 & 20 & 379 	 & +0.070 & +0.025 & +0.005 & +0.007 \\ 
+% 1.0e-06 	 & 1.0e-02 	 & 40 & 386 	 & +0.004 & +0.003 & +0.002 & +0.004 \\ 
+% 
+% 1.0e-06 	 & 1.0e-04 	 & 20 & 356 	 & +0.101 & +0.028 & -0.002 & +0.021 \\ 
+% 1.0e-06 	 & 1.0e-04 	 & 40 & 410 	 & -0.011 & -0.002 & -0.003 & +0.004 \\ 
 \end{tabular}
@@
 \hline
-
- %1.0e-04 	 & 1.0e+02 	 & 10 & 895 	 & +22.689 & +0.254 & +0.008 & +0.024 \\ 
- %1.0e-04 	 & 1.0e+02 	 & 20 & 1001 	 & +13.781 & +0.142 & -0.026 & +0.025 \\
- %1.0e-04 	 & 1.0e+02 	 & 40 & 1001 	 & +9.368 & +0.089 & -0.042 & +0.026 \\
-
-% 1.0e-06 	 & 1.0e+02 	 & 10 & 919 	 & +19.507 & +0.255 & +0.008 & +0.024 \\ 
-% 1.0e-06 	 & 1.0e+02 	 & 20 & 999 	 & +15.032 & +0.141 & -0.026 & +0.025 \\ 
-% 1.0e-06 	 & 1.0e+02 	 & 40 & 1001 	 & +9.809 & +0.088 & -0.043 & +0.026 \\
-
- 1.0e-02 	 & 1.0e+00 	 & 10 & 144 	 & +0.091 & +0.011 & +0.026 & +0.020 \\ 
- 1.0e-02 	 & 1.0e+00 	 & 20 & 181 	 & +0.089 & -0.003 & -0.001 & +0.008 \\ 
- 1.0e-02 	 & 1.0e+00 	 & 40 & 209 	 & +0.066 & -0.025 & -0.011 & +0.004 \\
-
- 1.0e-02 	 & 1.0e-02 	 & 10 & 368 	 & +0.183 & +0.066 & +0.026 & +0.084 \\
- 1.0e-02 	 & 1.0e-02 	 & 20 & 451 	 & +3.859 & +3.282 & +2.577 & +0.302 \\ 
- 1.0e-02 	 & 1.0e-02 	 & 40 & 518 	 & +7.347 & +6.417 & +5.478 & +0.384 \\
-
- 1.0e-04 	 & 1.0e+00 	 & 10 & 161 	 & +0.081 & +0.027 & +0.049 & +0.023 \\ 
- 1.0e-04 	 & 1.0e+00 	 & 20 & 202 	 & +0.007 & -0.050 & +0.017 & +0.028 \\ 
- 1.0e-04 	 & 1.0e+00 	 & 40 & 308 	 & -0.032 & -0.081 & +0.002 & +0.031 \\
-
-% 1.0e-04 	 & 1.0e-01 	 & 10 & 185 	 & +0.123 & +0.046 & +0.037 & +0.021 \\ 
-% 1.0e-04 	 & 1.0e-01 	 & 20 & 336 	 & +0.028 & -0.009 & +0.009 & +0.023 \\
-% 1.0e-04 	 & 1.0e-01 	 & 40 & 379 	 & -0.004 & -0.033 & -0.006 & +0.026 \\
-
- 1.0e-04 	 & 1.0e-02 	 & 10 & 265 	 & +0.160 & +0.082 & +0.033 & +0.016 \\ 
- 1.0e-04 	 & 1.0e-02 	 & 20 & 320 	 & +0.025 & +0.025 & +0.015 & +0.013 \\
- 1.0e-04 	 & 1.0e-02 	 & 40 & 377 	 & +0.006 & +0.006 & -0.001 & +0.008 \\
-
-% 1.0e-05 	 & 1.0e+00 	 & 10 & 192 	 & +0.083 & +0.026 & +0.049 & +0.023 \\ 
-% 1.0e-05 	 & 1.0e+00 	 & 20 & 195 	 & +0.007 & -0.051 & +0.017 & +0.029 \\ 
-% 1.0e-05 	 & 1.0e+00 	 & 40 & 212 	 & -0.034 & -0.083 & +0.001 & +0.031 \\
-
-% 1.0e-05 	 & 1.0e-01 	 & 10 & 223 	 & +0.118 & +0.047 & +0.037 & +0.020 \\ 
-%  1.0e-05 	 & 1.0e-01 	 & 20 & 320 	 & +0.029 & -0.011 & +0.009 & +0.026 \\
-%  1.0e-05 	 & 1.0e-01 	 & 40 & 396 	 & -0.007 & -0.036 & -0.006 & +0.028 \\
-
-%  1.0e-05 	 & 1.0e-02 	 & 10 & 267 	 & +0.159 & +0.084 & +0.033 & +0.016 \\ 
-%  1.0e-05 	 & 1.0e-02 	 & 20 & 351 	 & +0.023 & +0.017 & +0.011 & +0.019 \\ 
-%  1.0e-05 	 & 1.0e-02 	 & 40 & 374 	 & +0.009 & +0.007 & -0.003 & +0.014 \\
-
- 1.0e-06 	 & 1.0e+00 	 & 10 & 176 	 & +0.082 & +0.026 & +0.049 & +0.023 \\ 
- 1.0e-06 	 & 1.0e+00 	 & 20 & 224 	 & +0.007 & -0.051 & +0.017 & +0.029 \\ 
- 1.0e-06 	 & 1.0e+00 	 & 40 & 226 	 & -0.034 & -0.082 & +0.001 & +0.031 \\
-
-% 1.0e-06 	 & 1.0e-01 	 & 10 & 229 	 & +0.120 & +0.046 & +0.037 & +0.021 \\ 
-%  1.0e-06 	 & 1.0e-01 	 & 20 & 334 	 & +0.027 & -0.012 & +0.009 & +0.026 \\  
-% 1.0e-06 	 & 1.0e-01 	 & 40 & 313 	 & -0.007 & -0.037 & -0.006 & +0.030 \\
-
- 1.0e-06 	 & 1.0e-02 	 & 10 & 253 	 & +0.156 & +0.080 & +0.033 & +0.018 \\ 
- 1.0e-06 	 & 1.0e-02 	 & 20 & 340 	 & +0.020 & +0.016 & +0.012 & +0.019 \\ 
- 1.0e-06 	 & 1.0e-02 	 & 40 & 368 	 & +0.006 & +0.006 & -0.004 & +0.013 \\ 
+ 1.0e-02 	 & 1.0e+00 	 & 10 & 151 	 & +0.095 & +0.015 & +0.028 & +0.020 \\ 
+ 1.0e-02 	 & 1.0e+00 	 & 20 & 165 	 & +0.092 & -0.001 & -0.001 & +0.008 \\ 
+ 1.0e-02 	 & 1.0e+00 	 & 40 & 228 	 & +0.067 & -0.024 & -0.011 & +0.005 \\
+
+ 1.0e-02 	 & 1.0e-02 	 & 10 & 330 	 & +0.190 & +0.074 & +0.027 & +0.083 \\ 
+ 1.0e-02 	 & 1.0e-02 	 & 20 & 455 	 & +3.882 & +3.297 & +2.583 & +0.304 \\ 
+  1.0e-02 	 & 1.0e-02 	 & 40 & 523 	 & +7.466 & +6.454 & +5.537 & +0.388 \\
+
+ 1.0e-02 	 & 1.0e-04 	 & 10 & 428 	 & +0.196 & +0.076 & +0.032 & +0.163 \\ 
+ 1.0e-02 	 & 1.0e-04 	 & 20 & 571 	 & +7.402 & +6.421 & +5.405 & +0.680 \\ 
+ 1.0e-02 	 & 1.0e-04 	 & 40 & 747 	 & +15.386 & +13.764 & +12.196 & +0.841 \\
+
+  1.0e-04 	 & 1.0e+00 	 & 10 & 147 	 & +0.081 & +0.008 & +0.023 & +0.020 \\ 
+  1.0e-04 	 & 1.0e+00 	 & 20 & 167 	 & +0.051 & -0.026 & -0.009 & +0.008 \\ 
+  1.0e-04 	 & 1.0e+00 	 & 40 & 148 	 & +0.018 & -0.057 & -0.020 & +0.005 \\
+
+ 1.0e-04 	 & 1.0e-02 	 & 10 & 255 	 & +0.171 & +0.087 & +0.010 & +0.021 \\ 
+ 1.0e-04 	 & 1.0e-02 	 & 20 & 216 	 & -0.005 & -0.006 & -0.008 & +0.008 \\ 
+ 1.0e-04 	 & 1.0e-02 	 & 40 & 386 	 & -0.004 & -0.012 & -0.015 & +0.004 \\
+
+ 1.0e-04 	 & 1.0e-04 	 & 10 & 284 	 & +0.059 & +0.052 & +0.010 & +0.051 \\ 
+ 1.0e-04 	 & 1.0e-04 	 & 20 & 256 	 & -0.048 & -0.045 & -0.024 & +0.020 \\ 
+  1.0e-04 	 & 1.0e-04 	 & 40 & 277 	 & -0.071 & -0.074 & -0.050 & +0.018 \\
+
+ 1.0e-06 	 & 1.0e+00 	 & 10 & 163 	 & +0.082 & +0.008 & +0.023 & +0.020 \\ 
+ 1.0e-06 	 & 1.0e+00 	 & 20 & 156 	 & +0.054 & -0.027 & -0.009 & +0.008 \\ 
+ 1.0e-06 	 & 1.0e+00 	 & 40 & 284 	 & +0.020 & -0.055 & -0.019 & +0.005 \\
+
+ 1.0e-06 	 & 1.0e-02 	 & 10 & 290 	 & +0.155 & +0.075 & +0.011 & +0.021 \\ 
+ 1.0e-06 	 & 1.0e-02 	 & 20 & 239 	 & -0.004 & +0.002 & -0.006 & +0.008 \\ 
+ 1.0e-06 	 & 1.0e-02 	 & 40 & 378 	 & -0.005 & -0.013 & -0.016 & +0.004 \\
+
+ 1.0e-06 	 & 1.0e-04 	 & 10 & 264 	 & +0.070 & +0.056 & +0.009 & +0.050 \\ 
+ 1.0e-06 	 & 1.0e-04 	 & 20 & 234 	 & -0.047 & -0.044 & -0.029 & +0.020 \\
+ 1.0e-06 	 & 1.0e-04 	 & 40 & 324 	 & -0.070 & -0.070 & -0.052 & +0.017 \\
+
+%
+% %1.0e-04 	 & 1.0e+02 	 & 10 & 895 	 & +22.689 & +0.254 & +0.008 & +0.024 \\ 
+% %1.0e-04 	 & 1.0e+02 	 & 20 & 1001 	 & +13.781 & +0.142 & -0.026 & +0.025 \\
+% %1.0e-04 	 & 1.0e+02 	 & 40 & 1001 	 & +9.368 & +0.089 & -0.042 & +0.026 \\
+% 
+%% 1.0e-06 	 & 1.0e+02 	 & 10 & 919 	 & +19.507 & +0.255 & +0.008 & +0.024 \\ 
+%% 1.0e-06 	 & 1.0e+02 	 & 20 & 999 	 & +15.032 & +0.141 & -0.026 & +0.025 \\ 
+%% 1.0e-06 	 & 1.0e+02 	 & 40 & 1001 	 & +9.809 & +0.088 & -0.043 & +0.026 \\ 
+% 
+% 1.0e-02 	 & 1.0e+00 	 & 10 & 144 	 & +0.091 & +0.011 & +0.026 & +0.020 \\ 
+% 1.0e-02 	 & 1.0e+00 	 & 20 & 181 	 & +0.089 & -0.003 & -0.001 & +0.008 \\ 
+% 1.0e-02 	 & 1.0e+00 	 & 40 & 209 	 & +0.066 & -0.025 & -0.011 & +0.004 \\ 
+%  
+% 1.0e-02 	 & 1.0e-02 	 & 10 & 368 	 & +0.183 & +0.066 & +0.026 & +0.084 \\
+% 1.0e-02 	 & 1.0e-02 	 & 20 & 451 	 & +3.859 & +3.282 & +2.577 & +0.302 \\ 
+% 1.0e-02 	 & 1.0e-02 	 & 40 & 518 	 & +7.347 & +6.417 & +5.478 & +0.384 \\ 
+% 
+% 1.0e-04 	 & 1.0e+00 	 & 10 & 161 	 & +0.081 & +0.027 & +0.049 & +0.023 \\ 
+% 1.0e-04 	 & 1.0e+00 	 & 20 & 202 	 & +0.007 & -0.050 & +0.017 & +0.028 \\ 
+% 1.0e-04 	 & 1.0e+00 	 & 40 & 308 	 & -0.032 & -0.081 & +0.002 & +0.031 \\
+%  
+%% 1.0e-04 	 & 1.0e-01 	 & 10 & 185 	 & +0.123 & +0.046 & +0.037 & +0.021 \\ 
+%% 1.0e-04 	 & 1.0e-01 	 & 20 & 336 	 & +0.028 & -0.009 & +0.009 & +0.023 \\
+%% 1.0e-04 	 & 1.0e-01 	 & 40 & 379 	 & -0.004 & -0.033 & -0.006 & +0.026 \\ 
+% 
+% 1.0e-04 	 & 1.0e-02 	 & 10 & 265 	 & +0.160 & +0.082 & +0.033 & +0.016 \\ 
+% 1.0e-04 	 & 1.0e-02 	 & 20 & 320 	 & +0.025 & +0.025 & +0.015 & +0.013 \\
+% 1.0e-04 	 & 1.0e-02 	 & 40 & 377 	 & +0.006 & +0.006 & -0.001 & +0.008 \\ 
+%  
+% 
+%% 1.0e-05 	 & 1.0e+00 	 & 10 & 192 	 & +0.083 & +0.026 & +0.049 & +0.023 \\ 
+%% 1.0e-05 	 & 1.0e+00 	 & 20 & 195 	 & +0.007 & -0.051 & +0.017 & +0.029 \\ 
+%% 1.0e-05 	 & 1.0e+00 	 & 40 & 212 	 & -0.034 & -0.083 & +0.001 & +0.031 \\ 
+% 
+%% 1.0e-05 	 & 1.0e-01 	 & 10 & 223 	 & +0.118 & +0.047 & +0.037 & +0.020 \\ 
+%%  1.0e-05 	 & 1.0e-01 	 & 20 & 320 	 & +0.029 & -0.011 & +0.009 & +0.026 \\
+%%  1.0e-05 	 & 1.0e-01 	 & 40 & 396 	 & -0.007 & -0.036 & -0.006 & +0.028 \\ 
+%  
+%  
+%%  1.0e-05 	 & 1.0e-02 	 & 10 & 267 	 & +0.159 & +0.084 & +0.033 & +0.016 \\ 
+%%  1.0e-05 	 & 1.0e-02 	 & 20 & 351 	 & +0.023 & +0.017 & +0.011 & +0.019 \\ 
+%%  1.0e-05 	 & 1.0e-02 	 & 40 & 374 	 & +0.009 & +0.007 & -0.003 & +0.014 \\ 
+%  
+%  
+% 1.0e-06 	 & 1.0e+00 	 & 10 & 176 	 & +0.082 & +0.026 & +0.049 & +0.023 \\ 
+% 1.0e-06 	 & 1.0e+00 	 & 20 & 224 	 & +0.007 & -0.051 & +0.017 & +0.029 \\ 
+% 1.0e-06 	 & 1.0e+00 	 & 40 & 226 	 & -0.034 & -0.082 & +0.001 & +0.031 \\ 
+%  
+%% 1.0e-06 	 & 1.0e-01 	 & 10 & 229 	 & +0.120 & +0.046 & +0.037 & +0.021 \\ 
+%%  1.0e-06 	 & 1.0e-01 	 & 20 & 334 	 & +0.027 & -0.012 & +0.009 & +0.026 \\  
+%% 1.0e-06 	 & 1.0e-01 	 & 40 & 313 	 & -0.007 & -0.037 & -0.006 & +0.030 \\
+%  
+% 1.0e-06 	 & 1.0e-02 	 & 10 & 253 	 & +0.156 & +0.080 & +0.033 & +0.018 \\ 
+% 1.0e-06 	 & 1.0e-02 	 & 20 & 340 	 & +0.020 & +0.016 & +0.012 & +0.019 \\ 
+% 1.0e-06 	 & 1.0e-02 	 & 40 & 368 	 & +0.006 & +0.006 & -0.004 & +0.013 \\ 
 \end{tabular}
@@
 
- 1.0e-02 	 & 1.0e+00 	 & 10 & 283 	 & -0.062 & +0.026 & +0.022 & +0.033 \\ 
- 1.0e-02 	 & 1.0e+00 	 & 20 & 208 	 & -0.012 & +0.012 & +0.008 & +0.007 \\ 
- 1.0e-02 	 & 1.0e+00 	 & 40 & 201 	 & +0.002 & +0.001 & +0.002 & +0.002 \\
-
- 1.0e-02 	 & 1.0e-02 	 & 10 & 238 	 & -0.068 & +0.026 & +0.022 & +0.033 \\ 
- 1.0e-02 	 & 1.0e-02 	 & 20 & 492 	 & -0.001 & +0.013 & +0.004 & +0.010 \\ 
- 1.0e-02 	 & 1.0e-02 	 & 40 & 572 	 & +0.040 & +0.014 & -0.002 & +0.004 \\
-
- 1.0e-04 	 & 1.0e+00 	 & 10 & 246 	 & -0.046 & +0.038 & +0.023 & +0.031 \\ 
- 1.0e-04 	 & 1.0e+00 	 & 20 & 228 	 & -0.008 & +0.016 & +0.009 & +0.006 \\ 
- 1.0e-04 	 & 1.0e+00 	 & 40 & 279 	 & -0.007 & +0.000 & +0.003 & +0.002 \\
-
-% 1.0e-04 	 & 1.0e-01 	 & 10 & 292 	 & -0.052 & +0.038 & +0.024 & +0.032 \\  
-% 1.0e-04 	 & 1.0e-01 	 & 20 & 331 	 & -0.001 & +0.018 & +0.006 & +0.006 \\ 
-% 1.0e-04 	 & 1.0e-01 	 & 40 & 313 	 & +0.004 & +0.003 & +0.000 & +0.002 \\
-
- 1.0e-04 	 & 1.0e-02 	 & 10 & 338 	 & -0.053 & +0.038 & +0.024 & +0.032 \\ 
-  1.0e-04 	 & 1.0e-02 	 & 20 & 367 	 & +0.003 & +0.018 & +0.005 & +0.007 \\
-   1.0e-04 	 & 1.0e-02 	 & 40 & 273 	 & +0.017 & +0.006 & -0.001 & +0.001 \\
-
-% 1.0e-05 	 & 1.0e+00 	 & 10 & 290 	 & -0.047 & +0.038 & +0.023 & +0.031 \\ 
-%  1.0e-05 	 & 1.0e+00 	 & 20 & 194 	 & -0.008 & +0.016 & +0.009 & +0.006 \\ 
-%   1.0e-05 	 & 1.0e+00 	 & 40 & 238 	 & -0.007 & +0.000 & +0.002 & +0.002 \\
-
-% 1.0e-05 	 & 1.0e-01 	 & 10 & 316 	 & -0.052 & +0.038 & +0.024 & +0.032 \\ 
-%  1.0e-05 	 & 1.0e-01 	 & 20 & 312 	 & -0.001 & +0.018 & +0.006 & +0.006 \\ 
-%   1.0e-05 	 & 1.0e-01 	 & 40 & 317 	 & +0.004 & +0.003 & +0.000 & +0.002 \\
-
- %1.0e-05 	 & 1.0e-02 	 & 10 & 389 	 & -0.052 & +0.038 & +0.024 & +0.033 \\ 
- % 1.0e-05 	 & 1.0e-02 	 & 20 & 266 	 & +0.004 & +0.018 & +0.005 & +0.007 \\ 
- %  1.0e-05 	 & 1.0e-02 	 & 40 & 336 	 & +0.015 & +0.005 & -0.001 & +0.001 \\
-
- 1.0e-06 	 & 1.0e+00 	 & 10 & 282 	 & -0.047 & +0.038 & +0.023 & +0.031 \\ 
-  1.0e-06 	 & 1.0e+00 	 & 20 & 179 	 & -0.008 & +0.016 & +0.009 & +0.006 \\ 
-  1.0e-06 	 & 1.0e+00 	 & 40 & 261 	 & -0.007 & +0.000 & +0.002 & +0.002 \\
-
-% 1.0e-06 	 & 1.0e-01 	 & 10 & 308 	 & -0.052 & +0.038 & +0.024 & +0.032 \\ 
-%  1.0e-06 	 & 1.0e-01 	 & 20 & 245 	 & -0.002 & +0.018 & +0.006 & +0.006 \\ 
-%   1.0e-06 	 & 1.0e-01 	 & 40 & 318 	 & +0.004 & +0.003 & +0.000 & +0.002 \\
-
- 1.0e-06 	 & 1.0e-02 	 & 10 & 285 	 & -0.052 & +0.038 & +0.024 & +0.032 \\ 
- 1.0e-06 	 & 1.0e-02 	 & 20 & 362 	 & +0.003 & +0.018 & +0.005 & +0.007 \\ 
- 1.0e-06 	 & 1.0e-02 	 & 40 & 375 	 & +0.015 & +0.005 & -0.001 & +0.001 \\ 
+ 1.0e-02 	 & 1.0e+00 	 & 10 & 250 	 & -0.038 & +0.035 & +0.019 & +0.033 \\ 
+ 1.0e-02 	 & 1.0e+00 	 & 20 & 225 	 & -0.002 & +0.015 & +0.007 & +0.007 \\ 
+ 1.0e-02 	 & 1.0e+00 	 & 40 & 255 	 & +0.003 & +0.002 & +0.001 & +0.002 \\
+
+ 1.0e-02 	 & 1.0e-02 	 & 10 & 180 	 & -0.042 & +0.034 & +0.020 & +0.033 \\ 
+ 1.0e-02 	 & 1.0e-02 	 & 20 & 445 	 & +0.010 & +0.017 & +0.003 & +0.010 \\ 
+  1.0e-02 	 & 1.0e-02 	 & 40 & 429 	 & +0.037 & +0.014 & -0.003 & +0.004 \\
+
+ 1.0e-02 	 & 1.0e-04 	 & 10 & 208 	 & -0.042 & +0.034 & +0.020 & +0.033 \\ 
+  1.0e-02 	 & 1.0e-04 	 & 20 & 530 	 & +0.012 & +0.017 & +0.003 & +0.020 \\ 
+ 1.0e-02 	 & 1.0e-04 	 & 40 & - 	 & +0.064 & +0.023 & -0.005 & +0.072 \\
+
+ 1.0e-04 	 & 1.0e+00 	 & 10 & 209 	 & -0.043 & +0.033 & +0.019 & +0.033 \\ 
+ 1.0e-04 	 & 1.0e+00 	 & 20 & 212 	 & -0.007 & +0.014 & +0.007 & +0.007 \\ 
+ 1.0e-04 	 & 1.0e+00 	 & 40 & 258 	 & -0.002 & +0.001 & +0.001 & +0.002 \\
+
+ 1.0e-04 	 & 1.0e-02 	 & 10 & 258 	 & -0.047 & +0.033 & +0.020 & +0.033 \\ 
+ 1.0e-04 	 & 1.0e-02 	 & 20 & 391 	 & +0.005 & +0.016 & +0.003 & +0.008 \\ 
+ 1.0e-04 	 & 1.0e-02 	 & 40 & 261 	 & +0.014 & +0.005 & -0.002 & +0.001 \\
+
+ 1.0e-04 	 & 1.0e-04 	 & 10 & 267 	 & -0.047 & +0.033 & +0.020 & +0.033 \\ 
+ 1.0e-04 	 & 1.0e-04 	 & 20 & 769 	 & +0.008 & +0.016 & +0.003 & +0.016 \\
+ 1.0e-04 	 & 1.0e-04 	 & 40 & 375 	 & +0.027 & +0.005 & -0.003 & +0.002 \\
+
+ 1.0e-06 	 & 1.0e+00 	 & 10 & 198 	 & -0.042 & +0.033 & +0.019 & +0.033 \\ 
+ 1.0e-06 	 & 1.0e+00 	 & 20 & 222 	 & -0.007 & +0.014 & +0.007 & +0.007 \\ 
+ 1.0e-06 	 & 1.0e+00 	 & 40 & 280 	 & -0.001 & +0.001 & +0.001 & +0.002 \\
+
+ 1.0e-06 	 & 1.0e-02 	 & 10 & 279 	 & -0.047 & +0.033 & +0.020 & +0.033 \\ 
+ 1.0e-06 	 & 1.0e-02 	 & 20 & 312 	 & +0.005 & +0.016 & +0.003 & +0.008 \\ 
+ 1.0e-06 	 & 1.0e-02 	 & 40 & 379 	 & +0.015 & +0.005 & -0.002 & +0.001 \\
+
+ 1.0e-06 	 & 1.0e-04 	 & 10 & 251 	 & -0.047 & +0.033 & +0.020 & +0.033 \\ 
+ 1.0e-06 	 & 1.0e-04 	 & 20 & 778 	 & +0.008 & +0.016 & +0.002 & +0.018 \\ 
+ 1.0e-06 	 & 1.0e-04 	 & 40 & 191 	 & +0.017 & +0.004 & -0.002 & +0.002 \\
+
+%
+% 1.0e-02 	 & 1.0e+00 	 & 10 & 283 	 & -0.062 & +0.026 & +0.022 & +0.033 \\ 
+% 1.0e-02 	 & 1.0e+00 	 & 20 & 208 	 & -0.012 & +0.012 & +0.008 & +0.007 \\ 
+% 1.0e-02 	 & 1.0e+00 	 & 40 & 201 	 & +0.002 & +0.001 & +0.002 & +0.002 \\ 
+% 
+% 
+% 1.0e-02 	 & 1.0e-02 	 & 10 & 238 	 & -0.068 & +0.026 & +0.022 & +0.033 \\ 
+% 1.0e-02 	 & 1.0e-02 	 & 20 & 492 	 & -0.001 & +0.013 & +0.004 & +0.010 \\ 
+% 1.0e-02 	 & 1.0e-02 	 & 40 & 572 	 & +0.040 & +0.014 & -0.002 & +0.004 \\ 
+% 
+% 
+% 
+% 1.0e-04 	 & 1.0e+00 	 & 10 & 246 	 & -0.046 & +0.038 & +0.023 & +0.031 \\ 
+% 1.0e-04 	 & 1.0e+00 	 & 20 & 228 	 & -0.008 & +0.016 & +0.009 & +0.006 \\ 
+% 1.0e-04 	 & 1.0e+00 	 & 40 & 279 	 & -0.007 & +0.000 & +0.003 & +0.002 \\  
+%  
+%% 1.0e-04 	 & 1.0e-01 	 & 10 & 292 	 & -0.052 & +0.038 & +0.024 & +0.032 \\  
+%% 1.0e-04 	 & 1.0e-01 	 & 20 & 331 	 & -0.001 & +0.018 & +0.006 & +0.006 \\ 
+%% 1.0e-04 	 & 1.0e-01 	 & 40 & 313 	 & +0.004 & +0.003 & +0.000 & +0.002 \\ 
+% 
+% 1.0e-04 	 & 1.0e-02 	 & 10 & 338 	 & -0.053 & +0.038 & +0.024 & +0.032 \\ 
+%  1.0e-04 	 & 1.0e-02 	 & 20 & 367 	 & +0.003 & +0.018 & +0.005 & +0.007 \\
+%   1.0e-04 	 & 1.0e-02 	 & 40 & 273 	 & +0.017 & +0.006 & -0.001 & +0.001 \\  
+%  
+%% 1.0e-05 	 & 1.0e+00 	 & 10 & 290 	 & -0.047 & +0.038 & +0.023 & +0.031 \\ 
+%%  1.0e-05 	 & 1.0e+00 	 & 20 & 194 	 & -0.008 & +0.016 & +0.009 & +0.006 \\ 
+%%   1.0e-05 	 & 1.0e+00 	 & 40 & 238 	 & -0.007 & +0.000 & +0.002 & +0.002 \\ 
+%  
+%% 1.0e-05 	 & 1.0e-01 	 & 10 & 316 	 & -0.052 & +0.038 & +0.024 & +0.032 \\ 
+%%  1.0e-05 	 & 1.0e-01 	 & 20 & 312 	 & -0.001 & +0.018 & +0.006 & +0.006 \\ 
+%%   1.0e-05 	 & 1.0e-01 	 & 40 & 317 	 & +0.004 & +0.003 & +0.000 & +0.002 \\ 
+%   
+%   
+% %1.0e-05 	 & 1.0e-02 	 & 10 & 389 	 & -0.052 & +0.038 & +0.024 & +0.033 \\ 
+% % 1.0e-05 	 & 1.0e-02 	 & 20 & 266 	 & +0.004 & +0.018 & +0.005 & +0.007 \\ 
+% %  1.0e-05 	 & 1.0e-02 	 & 40 & 336 	 & +0.015 & +0.005 & -0.001 & +0.001 \\ 
+%   
+%   
+% 1.0e-06 	 & 1.0e+00 	 & 10 & 282 	 & -0.047 & +0.038 & +0.023 & +0.031 \\ 
+%  1.0e-06 	 & 1.0e+00 	 & 20 & 179 	 & -0.008 & +0.016 & +0.009 & +0.006 \\ 
+%  1.0e-06 	 & 1.0e+00 	 & 40 & 261 	 & -0.007 & +0.000 & +0.002 & +0.002 \\ 
+% 
+%  
+%% 1.0e-06 	 & 1.0e-01 	 & 10 & 308 	 & -0.052 & +0.038 & +0.024 & +0.032 \\ 
+%%  1.0e-06 	 & 1.0e-01 	 & 20 & 245 	 & -0.002 & +0.018 & +0.006 & +0.006 \\ 
+%%   1.0e-06 	 & 1.0e-01 	 & 40 & 318 	 & +0.004 & +0.003 & +0.000 & +0.002 \\
+%
+% 1.0e-06 	 & 1.0e-02 	 & 10 & 285 	 & -0.052 & +0.038 & +0.024 & +0.032 \\ 
+% 1.0e-06 	 & 1.0e-02 	 & 20 & 362 	 & +0.003 & +0.018 & +0.005 & +0.007 \\ 
+% 1.0e-06 	 & 1.0e-02 	 & 40 & 375 	 & +0.015 & +0.005 & -0.001 & +0.001 \\ 
 \end{tabular}
@@
 \hline
- %1.0e+00 	 & 1.0e+00 	 & 10 & 218 	 & +4.266 & +0.304 & +0.092 & +0.135 \\ 
- %1.0e+00 	 & 1.0e-01 	 & 10 & 223 	 & +4.565 & +0.304 & +0.090 & +0.142 \\ 
-% 1.0e+00 	 & 1.0e-02 	 & 10 & 199 	 & +4.268 & +0.305 & +0.090 & +0.143 \\ 
-% 1.0e+00 	 & 1.0e-03 	 & 10 & 222 	 & +4.274 & +0.305 & +0.090 & +0.143 \\ 
-% 1.0e+00 	 & 1.0e-04 	 & 10 & 211 	 & +4.448 & +0.306 & +0.090 & +0.143 \\ 
-% 1.0e+00 	 & 1.0e-05 	 & 10 & 227 	 & +4.527 & +0.304 & +0.090 & +0.143 \\ 
-%1.0e+00 	 & 1.0e-06 	 & 10 & 263 	 & +4.266 & +0.306 & +0.091 & +0.143 \\
-
- %1.0e-01 	 & 1.0e+00 	 & 10 & 167 	 & +0.131 & +0.093 & +0.041 & +0.027 \\ 
-% 1.0e-01 	 & 1.0e-01 	 & 10 & 195 	 & +0.125 & +0.093 & +0.039 & +0.046 \\ 
-% 1.0e-01 	 & 1.0e-02 	 & 10 & 218 	 & +0.126 & +0.093 & +0.040 & +0.056 \\ 
-% 1.0e-01 	 & 1.0e-03 	 & 10 & 161 	 & +0.129 & +0.094 & +0.040 & +0.057 \\ 
-% 1.0e-01 	 & 1.0e-04 	 & 10 & 180 	 & +0.135 & +0.092 & +0.042 & +0.057 \\ 
-% 1.0e-01 	 & 1.0e-05 	 & 10 & 169 	 & +0.123 & +0.093 & +0.041 & +0.057 \\ 
-% 1.0e-01 	 & 1.0e-06 	 & 10 & 201 	 & +0.119 & +0.093 & +0.040 & +0.057 \\
-
- 1.0e-02 	 & 1.0e+00 	 & 10 & 183 	 & +0.013 & +0.067 & +0.040 & +0.018 \\ 
-% 1.0e-02 	 & 1.0e-01 	 & 10 & 149 	 & +0.002 & +0.066 & +0.038 & +0.021 \\ 
- 1.0e-02 	 & 1.0e-02 	 & 10 & 185 	 & -0.005 & +0.065 & +0.040 & +0.040 \\ 
-% 1.0e-02 	 & 1.0e-03 	 & 10 & 213 	 & +0.004 & +0.066 & +0.038 & +0.049 \\ 
- 1.0e-02 	 & 1.0e-04 	 & 10 & 151 	 & +0.008 & +0.066 & +0.039 & +0.047 \\ 
-% 1.0e-02 	 & 1.0e-05 	 & 10 & 197 	 & +0.004 & +0.064 & +0.040 & +0.051 \\ 
- 1.0e-02 	 & 1.0e-06 	 & 10 & 185 	 & +0.012 & +0.063 & +0.038 & +0.049 \\
-
-% 1.0e-03 	 & 1.0e+00 	 & 10 & 183 	 & +0.007 & +0.062 & +0.038 & +0.019 \\ 
-% 1.0e-03 	 & 1.0e-01 	 & 10 & 181 	 & -0.011 & +0.063 & +0.039 & +0.019 \\ 
-% 1.0e-03 	 & 1.0e-02 	 & 10 & 122 	 & -0.008 & +0.063 & +0.040 & +0.025 \\ 
-% 1.0e-03 	 & 1.0e-03 	 & 10 & 158 	 & -0.004 & +0.062 & +0.040 & +0.028 \\ 
-% 1.0e-03 	 & 1.0e-04 	 & 10 & 168 	 & -0.013 & +0.063 & +0.038 & +0.029 \\ 
-% 1.0e-03 	 & 1.0e-05 	 & 10 & 120 	 & -0.010 & +0.063 & +0.040 & +0.028 \\ 
-% 1.0e-03 	 & 1.0e-06 	 & 10 & 132 	 & -0.002 & +0.062 & +0.039 & +0.028 \\
-
- 1.0e-04 	 & 1.0e+00 	 & 10 & 176 	 & +0.000 & +0.063 & +0.039 & +0.019 \\ 
- %1.0e-04 	 & 1.0e-01 	 & 10 & 180 	 & -0.001 & +0.062 & +0.039 & +0.019 \\ 
- 1.0e-04 	 & 1.0e-02 	 & 10 & 120 	 & +0.000 & +0.063 & +0.039 & +0.024 \\ 
- %1.0e-04 	 & 1.0e-03 	 & 10 & 119 	 & -0.004 & +0.062 & +0.039 & +0.026 \\ 
- 1.0e-04 	 & 1.0e-04 	 & 10 & 77 	 & -0.005 & +0.061 & +0.038 & +0.027 \\ 
- %1.0e-04 	 & 1.0e-05 	 & 10 & 104 	 & -0.004 & +0.062 & +0.038 & +0.027 \\ 
- 1.0e-04 	 & 1.0e-06 	 & 10 & 109 	 & -0.007 & +0.062 & +0.039 & +0.027 \\
-
- %1.0e-05 	 & 1.0e+00 	 & 10 & 220 	 & +0.005 & +0.063 & +0.039 & +0.019 \\ 
- %1.0e-05 	 & 1.0e-01 	 & 10 & 193 	 & -0.009 & +0.062 & +0.039 & +0.019 \\ 
- %1.0e-05 	 & 1.0e-02 	 & 10 & 163 	 & -0.013 & +0.063 & +0.039 & +0.021 \\ 
- %1.0e-05 	 & 1.0e-03 	 & 10 & 115 	 & -0.007 & +0.063 & +0.040 & +0.026 \\ 
- %1.0e-05 	 & 1.0e-04 	 & 10 & 82 	 & -0.007 & +0.062 & +0.038 & +0.027 \\ 
- %1.0e-05 	 & 1.0e-05 	 & 10 & 145 	 & -0.001 & +0.062 & +0.039 & +0.027 \\ 
- %1.0e-05 	 & 1.0e-06 	 & 10 & 147 	 & -0.012 & +0.061 & +0.040 & +0.027 \\
-
- 1.0e-06 	 & 1.0e+00 	 & 10 & 138 	 & +0.002 & +0.063 & +0.039 & +0.019 \\ 
- %1.0e-06 	 & 1.0e-01 	 & 10 & 184 	 & -0.006 & +0.063 & +0.039 & +0.019 \\ 
- 1.0e-06 	 & 1.0e-02 	 & 10 & 83 	 & -0.006 & +0.063 & +0.040 & +0.025 \\ 
- %1.0e-06 	 & 1.0e-03 	 & 10 & 91 	 & -0.013 & +0.063 & +0.039 & +0.026 \\ 
- 1.0e-06 	 & 1.0e-04 	 & 10 & 109 	 & -0.005 & +0.062 & +0.038 & +0.027 \\ 
- %1.0e-06 	 & 1.0e-05 	 & 10 & 116 	 & -0.007 & +0.063 & +0.039 & +0.027 \\ 
- 1.0e-06 	 & 1.0e-06 	 & 10 & 108 	 & +0.001 & +0.062 & +0.040 & +0.027 \\ 
+ 1.0e-02 	 & 1.0e+00 	 & 10 & 151 	 & -0.030 & +0.041 & +0.036 & +0.026 \\ 
+ 1.0e-02 	 & 1.0e-02 	 & 10 & 120 	 & -0.032 & +0.039 & +0.036 & +0.026 \\ 
+ 1.0e-02 	 & 1.0e-04 	 & 10 & 125 	 & -0.038 & +0.039 & +0.037 & +0.026 \\ 
+ 1.0e-02 	 & 1.0e-06 	 & 10 & 167 	 & -0.040 & +0.039 & +0.036 & +0.026 \\ 
+ 1.0e-04 	 & 1.0e+00 	 & 10 & 161 	 & -0.038 & +0.039 & +0.035 & +0.026 \\ 
+ 1.0e-04 	 & 1.0e-02 	 & 10 & 95 	 & -0.047 & +0.036 & +0.036 & +0.026 \\ 
+ 1.0e-04 	 & 1.0e-04 	 & 10 & 75 	 & -0.041 & +0.036 & +0.035 & +0.026 \\ 
+ 1.0e-04 	 & 1.0e-06 	 & 10 & 136 	 & -0.044 & +0.036 & +0.036 & +0.026 \\ 
+ 1.0e-06 	 & 1.0e+00 	 & 10 & 134 	 & -0.034 & +0.037 & +0.037 & +0.026 \\ 
+ 1.0e-06 	 & 1.0e-02 	 & 10 & 112 	 & -0.046 & +0.038 & +0.036 & +0.026 \\ 
+ 1.0e-06 	 & 1.0e-04 	 & 10 & 111 	 & -0.043 & +0.036 & +0.037 & +0.026 \\ 
+ 1.0e-06 	 & 1.0e-06 	 & 10 & 214 	 & -0.049 & +0.037 & +0.036 & +0.026 \\
+
+ 1.0e-02 	 & 1.0e+00 	 & 20 & 190 	 & +0.013 & +0.006 & +0.008 & +0.007 \\ 
+ 1.0e-02 	 & 1.0e-02 	 & 20 & 392 	 & +0.126 & +0.057 & +0.001 & +0.017 \\ 
+ 1.0e-02 	 & 1.0e-04 	 & 20 & 677 	 & +0.164 & +0.074 & -0.001 & +0.093 \\ 
+ 1.0e-02 	 & 1.0e-06 	 & 20 & 600 	 & +0.179 & +0.081 & -0.001 & +0.098 \\ 
+ 1.0e-04 	 & 1.0e+00 	 & 20 & 224 	 & +0.006 & +0.004 & +0.008 & +0.007 \\ 
+ 1.0e-04 	 & 1.0e-02 	 & 20 & 465 	 & +0.074 & +0.022 & -0.003 & +0.008 \\ 
+ 1.0e-04 	 & 1.0e-04 	 & 20 & 586 	 & +0.071 & +0.023 & -0.005 & +0.056 \\ 
+ 1.0e-04 	 & 1.0e-06 	 & 20 & 472 	 & +0.081 & +0.024 & -0.003 & +0.056 \\ 
+ 1.0e-06 	 & 1.0e+00 	 & 20 & 157 	 & +0.011 & +0.003 & +0.009 & +0.007 \\ 
+ 1.0e-06 	 & 1.0e-02 	 & 20 & 352 	 & +0.076 & +0.021 & +0.000 & +0.008 \\ 
+ 1.0e-06 	 & 1.0e-04 	 & 20 & 738 	 & +0.083 & +0.026 & -0.004 & +0.065 \\ 
+ 1.0e-06 	 & 1.0e-06 	 & 20 & 599 	 & +0.056 & +0.021 & -0.003 & +0.106 \\
+
+% %1.0e+00 	 & 1.0e+00 	 & 10 & 218 	 & +4.266 & +0.304 & +0.092 & +0.135 \\ 
+% %1.0e+00 	 & 1.0e-01 	 & 10 & 223 	 & +4.565 & +0.304 & +0.090 & +0.142 \\ 
+%% 1.0e+00 	 & 1.0e-02 	 & 10 & 199 	 & +4.268 & +0.305 & +0.090 & +0.143 \\ 
+%% 1.0e+00 	 & 1.0e-03 	 & 10 & 222 	 & +4.274 & +0.305 & +0.090 & +0.143 \\ 
+%% 1.0e+00 	 & 1.0e-04 	 & 10 & 211 	 & +4.448 & +0.306 & +0.090 & +0.143 \\ 
+%% 1.0e+00 	 & 1.0e-05 	 & 10 & 227 	 & +4.527 & +0.304 & +0.090 & +0.143 \\ 
+%%1.0e+00 	 & 1.0e-06 	 & 10 & 263 	 & +4.266 & +0.306 & +0.091 & +0.143 \\ 
+% 
+% %1.0e-01 	 & 1.0e+00 	 & 10 & 167 	 & +0.131 & +0.093 & +0.041 & +0.027 \\ 
+%% 1.0e-01 	 & 1.0e-01 	 & 10 & 195 	 & +0.125 & +0.093 & +0.039 & +0.046 \\ 
+%% 1.0e-01 	 & 1.0e-02 	 & 10 & 218 	 & +0.126 & +0.093 & +0.040 & +0.056 \\ 
+%% 1.0e-01 	 & 1.0e-03 	 & 10 & 161 	 & +0.129 & +0.094 & +0.040 & +0.057 \\ 
+%% 1.0e-01 	 & 1.0e-04 	 & 10 & 180 	 & +0.135 & +0.092 & +0.042 & +0.057 \\ 
+%% 1.0e-01 	 & 1.0e-05 	 & 10 & 169 	 & +0.123 & +0.093 & +0.041 & +0.057 \\ 
+%% 1.0e-01 	 & 1.0e-06 	 & 10 & 201 	 & +0.119 & +0.093 & +0.040 & +0.057 \\ 
+%
+% 1.0e-02 	 & 1.0e+00 	 & 10 & 183 	 & +0.013 & +0.067 & +0.040 & +0.018 \\ 
+%% 1.0e-02 	 & 1.0e-01 	 & 10 & 149 	 & +0.002 & +0.066 & +0.038 & +0.021 \\ 
+% 1.0e-02 	 & 1.0e-02 	 & 10 & 185 	 & -0.005 & +0.065 & +0.040 & +0.040 \\ 
+%% 1.0e-02 	 & 1.0e-03 	 & 10 & 213 	 & +0.004 & +0.066 & +0.038 & +0.049 \\ 
+% 1.0e-02 	 & 1.0e-04 	 & 10 & 151 	 & +0.008 & +0.066 & +0.039 & +0.047 \\ 
+%% 1.0e-02 	 & 1.0e-05 	 & 10 & 197 	 & +0.004 & +0.064 & +0.040 & +0.051 \\ 
+% 1.0e-02 	 & 1.0e-06 	 & 10 & 185 	 & +0.012 & +0.063 & +0.038 & +0.049 \\ 
+%
+%% 1.0e-03 	 & 1.0e+00 	 & 10 & 183 	 & +0.007 & +0.062 & +0.038 & +0.019 \\ 
+%% 1.0e-03 	 & 1.0e-01 	 & 10 & 181 	 & -0.011 & +0.063 & +0.039 & +0.019 \\ 
+%% 1.0e-03 	 & 1.0e-02 	 & 10 & 122 	 & -0.008 & +0.063 & +0.040 & +0.025 \\ 
+%% 1.0e-03 	 & 1.0e-03 	 & 10 & 158 	 & -0.004 & +0.062 & +0.040 & +0.028 \\ 
+%% 1.0e-03 	 & 1.0e-04 	 & 10 & 168 	 & -0.013 & +0.063 & +0.038 & +0.029 \\ 
+%% 1.0e-03 	 & 1.0e-05 	 & 10 & 120 	 & -0.010 & +0.063 & +0.040 & +0.028 \\ 
+%% 1.0e-03 	 & 1.0e-06 	 & 10 & 132 	 & -0.002 & +0.062 & +0.039 & +0.028 \\ 
+%
+% 1.0e-04 	 & 1.0e+00 	 & 10 & 176 	 & +0.000 & +0.063 & +0.039 & +0.019 \\ 
+% %1.0e-04 	 & 1.0e-01 	 & 10 & 180 	 & -0.001 & +0.062 & +0.039 & +0.019 \\ 
+% 1.0e-04 	 & 1.0e-02 	 & 10 & 120 	 & +0.000 & +0.063 & +0.039 & +0.024 \\ 
+% %1.0e-04 	 & 1.0e-03 	 & 10 & 119 	 & -0.004 & +0.062 & +0.039 & +0.026 \\ 
+% 1.0e-04 	 & 1.0e-04 	 & 10 & 77 	 & -0.005 & +0.061 & +0.038 & +0.027 \\ 
+% %1.0e-04 	 & 1.0e-05 	 & 10 & 104 	 & -0.004 & +0.062 & +0.038 & +0.027 \\ 
+% 1.0e-04 	 & 1.0e-06 	 & 10 & 109 	 & -0.007 & +0.062 & +0.039 & +0.027 \\ 
+%
+% %1.0e-05 	 & 1.0e+00 	 & 10 & 220 	 & +0.005 & +0.063 & +0.039 & +0.019 \\ 
+% %1.0e-05 	 & 1.0e-01 	 & 10 & 193 	 & -0.009 & +0.062 & +0.039 & +0.019 \\ 
+% %1.0e-05 	 & 1.0e-02 	 & 10 & 163 	 & -0.013 & +0.063 & +0.039 & +0.021 \\ 
+% %1.0e-05 	 & 1.0e-03 	 & 10 & 115 	 & -0.007 & +0.063 & +0.040 & +0.026 \\ 
+% %1.0e-05 	 & 1.0e-04 	 & 10 & 82 	 & -0.007 & +0.062 & +0.038 & +0.027 \\ 
+% %1.0e-05 	 & 1.0e-05 	 & 10 & 145 	 & -0.001 & +0.062 & +0.039 & +0.027 \\ 
+% %1.0e-05 	 & 1.0e-06 	 & 10 & 147 	 & -0.012 & +0.061 & +0.040 & +0.027 \\ 
+%
+% 1.0e-06 	 & 1.0e+00 	 & 10 & 138 	 & +0.002 & +0.063 & +0.039 & +0.019 \\ 
+% %1.0e-06 	 & 1.0e-01 	 & 10 & 184 	 & -0.006 & +0.063 & +0.039 & +0.019 \\ 
+% 1.0e-06 	 & 1.0e-02 	 & 10 & 83 	 & -0.006 & +0.063 & +0.040 & +0.025 \\ 
+% %1.0e-06 	 & 1.0e-03 	 & 10 & 91 	 & -0.013 & +0.063 & +0.039 & +0.026 \\ 
+% 1.0e-06 	 & 1.0e-04 	 & 10 & 109 	 & -0.005 & +0.062 & +0.038 & +0.027 \\ 
+% %1.0e-06 	 & 1.0e-05 	 & 10 & 116 	 & -0.007 & +0.063 & +0.039 & +0.027 \\ 
+% 1.0e-06 	 & 1.0e-06 	 & 10 & 108 	 & +0.001 & +0.062 & +0.040 & +0.027 \\ 
 \end{tabular}
@@
 \hline
-% 1.0e+00 	 & 1.0e+00 	 & 10 & 212 	 & +4.268 & +0.310 & +0.073 & +0.138 \\ 
- %1.0e+00 	 & 1.0e-01 	 & 10 & 211 	 & +4.122 & +0.302 & +0.085 & +0.146 \\ 
-% 1.0e+00 	 & 1.0e-02 	 & 10 & 221 	 & +4.773 & +0.298 & +0.089 & +0.147 \\ 
- %1.0e+00 	 & 1.0e-03 	 & 10 & 257 	 & +4.872 & +0.301 & +0.090 & +0.147 \\ 
-% 1.0e+00 	 & 1.0e-04 	 & 10 & 238 	 & +4.186 & +0.293 & +0.097 & +0.148 \\ 
- %1.0e+00 	 & 1.0e-05 	 & 10 & 204 	 & +4.251 & +0.313 & +0.085 & +0.147 \\ 
-% 1.0e+00 	 & 1.0e-06 	 & 10 & 223 	 & +4.493 & +0.310 & +0.085 & +0.147 \\ 
- %1.0e-01 	 & 1.0e+00 	 & 10 & 145 	 & +0.126 & +0.100 & +0.054 & +0.035 \\ 
- %1.0e-01 	 & 1.0e-01 	 & 10 & 199 	 & +0.115 & +0.125 & +0.026 & +0.060 \\ 
- %1.0e-01 	 & 1.0e-02 	 & 10 & 217 	 & +0.128 & +0.092 & +0.036 & +0.071 \\ 
- %1.0e-01 	 & 1.0e-03 	 & 10 & 242 	 & +0.109 & +0.093 & +0.031 & +0.073 \\ 
- %1.0e-01 	 & 1.0e-04 	 & 10 & 275 	 & +0.187 & +0.094 & +0.028 & +0.073 \\ 
- %1.0e-01 	 & 1.0e-05 	 & 10 & 237 	 & +0.048 & +0.099 & +0.039 & +0.073 \\ 
- %1.0e-01 	 & 1.0e-06 	 & 10 & 225 	 & +0.092 & +0.111 & +0.055 & +0.073 \\ 
- 1.0e-02 	 & 1.0e+00 	 & 10 & 208 	 & +0.017 & +0.075 & +0.037 & +0.029 \\ 
- %1.0e-02 	 & 1.0e-01 	 & 10 & 199 	 & -0.013 & +0.068 & +0.046 & +0.040 \\ 
- 1.0e-02 	 & 1.0e-02 	 & 10 & 348 	 & -0.043 & +0.073 & +0.041 & +0.063 \\ 
-% 1.0e-02 	 & 1.0e-03 	 & 10 & 400 	 & +0.056 & +0.058 & +0.031 & +0.075 \\ 
- 1.0e-02 	 & 1.0e-04 	 & 10 & 393 	 & -0.050 & +0.088 & +0.044 & +0.077 \\ 
- %1.0e-02 	 & 1.0e-05 	 & 10 & 359 	 & +0.022 & +0.068 & +0.027 & +0.076 \\ 
- 1.0e-02 	 & 1.0e-06 	 & 10 & 369 	 & +0.001 & +0.074 & +0.024 & +0.076 \\ 
- %1.0e-03 	 & 1.0e+00 	 & 10 & 207 	 & -0.001 & +0.065 & +0.051 & +0.029 \\ 
-% 1.0e-03 	 & 1.0e-01 	 & 10 & 280 	 & +0.028 & +0.051 & +0.053 & +0.038 \\ 
- %1.0e-03 	 & 1.0e-02 	 & 10 & 565 	 & -0.059 & +0.076 & +0.033 & +0.053 \\ 
-% 1.0e-03 	 & 1.0e-03 	 & 10 & 673 	 & -0.035 & +0.066 & +0.032 & +0.108 \\ 
- %\rowcolor{orange} 1.0e-03 	 & 1.0e-04 	 & 10 & 604 	 & -0.026 & +0.061 & +0.049 & +0.182 \\ 
- %1.0e-03 	 & 1.0e-05 	 & 10 & 666 	 & +0.012 & +0.070 & +0.038 & +0.182 \\ 
- %\rowcolor{orange} 1.0e-03 	 & 1.0e-06 	 & 10 & 893 	 & +0.027 & +0.070 & +0.022 & +0.180 \\ 
- 1.0e-04 	 & 1.0e+00 	 & 10 & 204 	 & +0.015 & +0.062 & +0.043 & +0.030 \\ 
- %1.0e-04 	 & 1.0e-01 	 & 10 & 269 	 & +0.005 & +0.057 & +0.037 & +0.038 \\ 
- 1.0e-04 	 & 1.0e-02 	 & 10 & 559 	 & -0.072 & +0.067 & +0.044 & +0.050 \\ 
-%\rowcolor{orange} 1.0e-04 	 & 1.0e-03 	 & 10 & 691 	 & -0.023 & +0.055 & +0.040 & +0.175 \\ 
- 1.0e-04 	 & 1.0e-04 	 & 10 & -	 & -0.012 & +0.066 & +0.030 & +0.745 \\ 
-%\rowcolor{red}  1.0e-04 	 & 1.0e-05 	 & 10 & 1001 	 & +0.038 & +0.057 & +0.034 & +1.113 \\ 
-1.0e-04 	 & 1.0e-06 	 & 10 & -	 & +0.015 & +0.063 & +0.035 & +1.127 \\ 
-% 1.0e-05 	 & 1.0e+00 	 & 10 & 184 	 & -0.025 & +0.076 & +0.041 & +0.029 \\ 
- %1.0e-05 	 & 1.0e-01 	 & 10 & 357 	 & -0.011 & +0.070 & +0.052 & +0.038 \\ 
-% 1.0e-05 	 & 1.0e-02 	 & 10 & 399 	 & +0.041 & +0.075 & +0.042 & +0.049 \\ 
-%1.0e-05 	 & 1.0e-03 	 & 10 & 689 	 & +0.044 & +0.062 & +0.020 & +0.172 \\ 
-%\rowcolor{red} 1.0e-05 	 & 1.0e-04 	 & 10 & 915 	 & +0.030 & +0.077 & +0.039 & +1.027 \\ 
- %1.0e-05 	 & 1.0e-05 	 & 10 & - 	 & +0.017 & +0.061 & +0.045 & +1.953 \\ 
-%\rowcolor{red}  1.0e-05 	 & 1.0e-06 	 & 10 & - 	 & -0.018 & +0.071 & +0.045 & +2.545 \\ 
- 1.0e-06 	 & 1.0e+00 	 & 10 & 177 	 & +0.060 & +0.069 & +0.039 & +0.029 \\ 
-% 1.0e-06 	 & 1.0e-01 	 & 10 & 302 	 & +0.011 & +0.039 & +0.039 & +0.038 \\ 
- 1.0e-06 	 & 1.0e-02 	 & 10 & 457 	 & +0.011 & +0.055 & +0.036 & +0.050 \\ 
-%\rowcolor{orange} 1.0e-06 	 & 1.0e-03 	 & 10 & 738 	 & -0.022 & +0.055 & +0.042 & +0.172 \\ 
- 1.0e-06 	 & 1.0e-04 	 & 10 & -	 & -0.043 & +0.042 & +0.054 & +1.180 \\ 
-%\rowcolor{red}  1.0e-06 	 & 1.0e-05 	 & 10 & 1001 	 & +0.006 & +0.052 & +0.033 & +3.365 \\ 
- 1.0e-06 	 & 1.0e-06 	 & 10 & - & -0.002 & +0.065 & +0.051 & +3.402 \\ 
+ 1.0e-02 	 & 1.0e+00 	 & 10 & 144 	 & +0.012 & +0.055 & +0.027 & +0.036 \\ 
+ 1.0e-02 	 & 1.0e-02 	 & 10 & 476 	 & -0.009 & +0.049 & +0.035 & +0.051 \\ 
+ 1.0e-02 	 & 1.0e-04 	 & 10 & 476 	 & -0.097 & +0.042 & +0.054 & +0.054 \\ 
+ 1.0e-02 	 & 1.0e-06 	 & 10 & 558 	 & -0.071 & +0.047 & +0.039 & +0.054 \\ 
+ 1.0e-04 	 & 1.0e+00 	 & 10 & 182 	 & -0.040 & +0.033 & +0.051 & +0.037 \\ 
+ 1.0e-04 	 & 1.0e-02 	 & 10 & 471 	 & +0.021 & +0.038 & +0.036 & +0.056 \\ 
+ 1.0e-04 	 & 1.0e-04 	 & 10 & 792 	 & -0.058 & +0.042 & +0.031 & +0.565 \\ 
+ 1.0e-04 	 & 1.0e-06 	 & 10 &  -   & -0.050 & +0.029 & +0.040 & +1.062 \\ 
+ 1.0e-06 	 & 1.0e+00 	 & 10 & 178 	 & +0.012 & +0.033 & +0.021 & +0.036 \\ 
+ 1.0e-06 	 & 1.0e-02 	 & 10 & 537 	 & -0.018 & +0.040 & +0.025 & +0.057 \\ 
+ 1.0e-06 	 & 1.0e-04 	 & 10 &  -	 & -0.038 & +0.040 & +0.030 & +1.452 \\ 
+ 1.0e-06 	 & 1.0e-06 	 & 10 &  - 	 & +0.003 & +0.035 & +0.046 & +3.621 \\ 
+ 1.0e-02 	 & 1.0e+00 	 & 20 & 213 	 & +0.009 & +0.015 & +0.009 & +0.016 \\ 
+ 1.0e-02 	 & 1.0e-02 	 & 20 & 719 	 & +0.228 & +0.088 & -0.032 & +0.085 \\ 
+ 1.0e-02 	 & 1.0e-04 	 & 20 &  -   & +0.100 & +0.071 & -0.013 & +0.271 \\ 
+ 1.0e-02 	 & 1.0e-06 	 & 20 &   -  & +0.223 & +0.097 & -0.027 & +0.282 \\ 
+ 1.0e-04 	 & 1.0e+00 	 & 20 & 245 	 & +0.038 & +0.013 & -0.001 & +0.016 \\ 
+ 1.0e-04 	 & 1.0e-02 	 & 20 &  - 	 & +0.050 & +0.054 & -0.024 & +0.116 \\ 
+ 1.0e-04 	 & 1.0e-04 	 & 20 &  - 	 & -0.087 & +0.059 & -0.077 & +5.763 \\ 
+ 1.0e-04 	 & 1.0e-06 	 & 20 &  -	 & +0.001 & +0.083 & -0.038 & +7.485 \\ 
+ 1.0e-06 	 & 1.0e+00 	 & 20 & 242 	 & -0.009 & +0.008 & +0.015 & +0.016 \\ 
+ 1.0e-06 	 & 1.0e-02 	 & 20 & 947 	 & +0.122 & +0.093 & -0.040 & +0.115 \\ 
+ 1.0e-06 	 & 1.0e-04 	 & 20 &  - 	 & -0.076 & +0.041 & -0.020 & +7.700 \\ 
+ 1.0e-06 	 & 1.0e-06 	 & 20 &  - 	 & +0.147 & +0.113 & -0.023 & +10.936 \\
+
+%% 1.0e+00 	 & 1.0e+00 	 & 10 & 212 	 & +4.268 & +0.310 & +0.073 & +0.138 \\ 
+% %1.0e+00 	 & 1.0e-01 	 & 10 & 211 	 & +4.122 & +0.302 & +0.085 & +0.146 \\ 
+%% 1.0e+00 	 & 1.0e-02 	 & 10 & 221 	 & +4.773 & +0.298 & +0.089 & +0.147 \\ 
+% %1.0e+00 	 & 1.0e-03 	 & 10 & 257 	 & +4.872 & +0.301 & +0.090 & +0.147 \\ 
+%% 1.0e+00 	 & 1.0e-04 	 & 10 & 238 	 & +4.186 & +0.293 & +0.097 & +0.148 \\ 
+% %1.0e+00 	 & 1.0e-05 	 & 10 & 204 	 & +4.251 & +0.313 & +0.085 & +0.147 \\ 
+%% 1.0e+00 	 & 1.0e-06 	 & 10 & 223 	 & +4.493 & +0.310 & +0.085 & +0.147 \\ 
+% %1.0e-01 	 & 1.0e+00 	 & 10 & 145 	 & +0.126 & +0.100 & +0.054 & +0.035 \\ 
+% %1.0e-01 	 & 1.0e-01 	 & 10 & 199 	 & +0.115 & +0.125 & +0.026 & +0.060 \\ 
+% %1.0e-01 	 & 1.0e-02 	 & 10 & 217 	 & +0.128 & +0.092 & +0.036 & +0.071 \\ 
+% %1.0e-01 	 & 1.0e-03 	 & 10 & 242 	 & +0.109 & +0.093 & +0.031 & +0.073 \\ 
+% %1.0e-01 	 & 1.0e-04 	 & 10 & 275 	 & +0.187 & +0.094 & +0.028 & +0.073 \\ 
+% %1.0e-01 	 & 1.0e-05 	 & 10 & 237 	 & +0.048 & +0.099 & +0.039 & +0.073 \\ 
+% %1.0e-01 	 & 1.0e-06 	 & 10 & 225 	 & +0.092 & +0.111 & +0.055 & +0.073 \\ 
+% 1.0e-02 	 & 1.0e+00 	 & 10 & 208 	 & +0.017 & +0.075 & +0.037 & +0.029 \\ 
+% %1.0e-02 	 & 1.0e-01 	 & 10 & 199 	 & -0.013 & +0.068 & +0.046 & +0.040 \\ 
+% 1.0e-02 	 & 1.0e-02 	 & 10 & 348 	 & -0.043 & +0.073 & +0.041 & +0.063 \\ 
+%% 1.0e-02 	 & 1.0e-03 	 & 10 & 400 	 & +0.056 & +0.058 & +0.031 & +0.075 \\ 
+% 1.0e-02 	 & 1.0e-04 	 & 10 & 393 	 & -0.050 & +0.088 & +0.044 & +0.077 \\ 
+% %1.0e-02 	 & 1.0e-05 	 & 10 & 359 	 & +0.022 & +0.068 & +0.027 & +0.076 \\ 
+% 1.0e-02 	 & 1.0e-06 	 & 10 & 369 	 & +0.001 & +0.074 & +0.024 & +0.076 \\ 
+% %1.0e-03 	 & 1.0e+00 	 & 10 & 207 	 & -0.001 & +0.065 & +0.051 & +0.029 \\ 
+%% 1.0e-03 	 & 1.0e-01 	 & 10 & 280 	 & +0.028 & +0.051 & +0.053 & +0.038 \\ 
+% %1.0e-03 	 & 1.0e-02 	 & 10 & 565 	 & -0.059 & +0.076 & +0.033 & +0.053 \\ 
+%% 1.0e-03 	 & 1.0e-03 	 & 10 & 673 	 & -0.035 & +0.066 & +0.032 & +0.108 \\ 
+% %\rowcolor{orange} 1.0e-03 	 & 1.0e-04 	 & 10 & 604 	 & -0.026 & +0.061 & +0.049 & +0.182 \\ 
+% %1.0e-03 	 & 1.0e-05 	 & 10 & 666 	 & +0.012 & +0.070 & +0.038 & +0.182 \\ 
+% %\rowcolor{orange} 1.0e-03 	 & 1.0e-06 	 & 10 & 893 	 & +0.027 & +0.070 & +0.022 & +0.180 \\ 
+% 1.0e-04 	 & 1.0e+00 	 & 10 & 204 	 & +0.015 & +0.062 & +0.043 & +0.030 \\ 
+% %1.0e-04 	 & 1.0e-01 	 & 10 & 269 	 & +0.005 & +0.057 & +0.037 & +0.038 \\ 
+% 1.0e-04 	 & 1.0e-02 	 & 10 & 559 	 & -0.072 & +0.067 & +0.044 & +0.050 \\ 
+%%\rowcolor{orange} 1.0e-04 	 & 1.0e-03 	 & 10 & 691 	 & -0.023 & +0.055 & +0.040 & +0.175 \\ 
+% 1.0e-04 	 & 1.0e-04 	 & 10 & -	 & -0.012 & +0.066 & +0.030 & +0.745 \\ 
+%%\rowcolor{red}  1.0e-04 	 & 1.0e-05 	 & 10 & 1001 	 & +0.038 & +0.057 & +0.034 & +1.113 \\ 
+%1.0e-04 	 & 1.0e-06 	 & 10 & -	 & +0.015 & +0.063 & +0.035 & +1.127 \\ 
+%% 1.0e-05 	 & 1.0e+00 	 & 10 & 184 	 & -0.025 & +0.076 & +0.041 & +0.029 \\ 
+% %1.0e-05 	 & 1.0e-01 	 & 10 & 357 	 & -0.011 & +0.070 & +0.052 & +0.038 \\ 
+%% 1.0e-05 	 & 1.0e-02 	 & 10 & 399 	 & +0.041 & +0.075 & +0.042 & +0.049 \\ 
+%%1.0e-05 	 & 1.0e-03 	 & 10 & 689 	 & +0.044 & +0.062 & +0.020 & +0.172 \\ 
+%%\rowcolor{red} 1.0e-05 	 & 1.0e-04 	 & 10 & 915 	 & +0.030 & +0.077 & +0.039 & +1.027 \\ 
+% %1.0e-05 	 & 1.0e-05 	 & 10 & - 	 & +0.017 & +0.061 & +0.045 & +1.953 \\ 
+%%\rowcolor{red}  1.0e-05 	 & 1.0e-06 	 & 10 & - 	 & -0.018 & +0.071 & +0.045 & +2.545 \\ 
+% 1.0e-06 	 & 1.0e+00 	 & 10 & 177 	 & +0.060 & +0.069 & +0.039 & +0.029 \\ 
+%% 1.0e-06 	 & 1.0e-01 	 & 10 & 302 	 & +0.011 & +0.039 & +0.039 & +0.038 \\ 
+% 1.0e-06 	 & 1.0e-02 	 & 10 & 457 	 & +0.011 & +0.055 & +0.036 & +0.050 \\ 
+%%\rowcolor{orange} 1.0e-06 	 & 1.0e-03 	 & 10 & 738 	 & -0.022 & +0.055 & +0.042 & +0.172 \\ 
+% 1.0e-06 	 & 1.0e-04 	 & 10 & -	 & -0.043 & +0.042 & +0.054 & +1.180 \\ 
+%%\rowcolor{red}  1.0e-06 	 & 1.0e-05 	 & 10 & 1001 	 & +0.006 & +0.052 & +0.033 & +3.365 \\ 
+% 1.0e-06 	 & 1.0e-06 	 & 10 & - & -0.002 & +0.065 & +0.051 & +3.402 \\ 
 \end{tabular}

### 2018-10-19 tex/paper.tex
reference added

@@
 a corresponding surface of a ball with the same volume. Hence, 
-a more rigorous modeling attempt is warrented. A complicating factor
+a more rigorous modeling attempt is warranted. A complicating factor
 is however that the contrast in the surrounding CSF is heterogenous
@@
 that diffusion was a governing transport mechanism in the brain and estimated to be on the order
-of XXX. This is confirmed with DTI where values of young and healthy are typically around XXX
+of XXX. This is confirmed with DTI where values of young and healthy are typically around $0.7e-3 \mathrm{mm\sp{2}/s}$ \cite{Helenius194}
 while values in dementia typically are XXX \kam{Geir vet du dette?}. Of course diffusion coefficient 
@@
 
+{\color{red} må skrive om B-values og parameter}
+
 The fractional anisotropy is defined as 
@@
 \subsection{Mathematical Model}
-
-In \cite{sykova2008diffusion}, It was shown that the macroscopic diffusion in the brain can be considered a hindered diffusion with an apparent diffusion coefficient.
-
+In \cite{sykova2008diffusion}, it was shown that the macroscopic diffusion in the brain can be considered a hindered diffusion with an apparent diffusion coefficient.
 In order to estimate the apparent diffusion coefficient involved in the contrast transportation shown in Figure~\ref{fig1} we assume that the process can be modeled by a diffusion equation and solve a PDE constrained optimization problem where
@@
 %and the initial condition was set to 1.0 in $\Omega_1$ and 0 elsewhere.
-The manufactured forward computation gave a total of 120 possible observation time points. These points will be denoted as $t_i$.
+The manufactured forward computation gave a total of 120 possible observation times, which  will be denoted as $t_i$.
 
@@
 Then the use of T2 weighted MRI \cite{eidevalnes} was used to segment the CSF compartment surrounding the cerebral and the lateral ventricles.
-CGAL \cite{cgal:rty-m3-18b} was used to combine the polyhedral surfaces and to construed the mesh, the code can be found ??
-.
+CGAL \cite{cgal:rty-m3-18b} was used to combine the polyhedral surfaces and to construed the mesh.
 The computational requirement for the resulting mesh was significant, therefore two submesh was also constructed, see Fig.\ref{Fig::Mesh}.
@@
 The 3 domain mesh in Fig.\ref{Fig::Mesh} A, consists of 244318 tetrahedral cells and 22057 vertices, while the 2 domain mesh Fig.\ref{Fig::Mesh} B consists of 335589 tetrahedral cells and 73002 vertices.
-The dimension of the mesh coordiantes are $\mathrm{mm}$.
+The dimension of the mesh coordinates are $\mathrm{mm}$.
 

### 2018-10-19 tex/paper.tex
update with natbib, citet not working properly, do not know why

--- 2018-10-19 tex/paper.tex
@@
 \usepackage{subcaption}
+\usepackage[numbers]{natbib}
 
@@
 that is responsible for waste clearance. 
-In 2011,~\cite{iliff2012paravascular} discovered a novel system within our brain's metabolism system, which changed our understanding of the brain. 
+In 2011,~\citet{iliff2012paravascular} discovered a novel system within our brain's metabolism system, which changed our understanding of the brain. 
 The system involves a new pathway, called the paravascular pathway as it runs in parallel with vasculature system in a surrounding compartment.
 The important novelty in the 2011 findings was that waste from the brain is cleared through the paravascular path, and that a malfunction of this system 
-is linked to the development of dementia such as Alzheimer's and Parkinson's diseases. In 2013,~\cite{xie2013sleep} found
+is linked to the development of dementia such as Alzheimer's and Parkinson's diseases. In 2013,~\citet{xie2013sleep} found
 that this system is particularly active during sleep.

### 2018-10-20 tex/paper.tex
images added
cleaning and adding text

--- 2018-10-19 tex/paper.tex
@@
 that diffusion was a governing transport mechanism in the brain and estimated to be on the order
-of XXX. This is confirmed with DTI where values of young and healthy are typically around $0.7e-3 \mathrm{mm\sp{2}/s}$ \cite{Helenius194}
+of $1.0e-4 \mathrm{mm\sp{2}/s}$ for large molecules. This is confirmed with DTI where values of young and healthy are typically around $0.7e-3 \mathrm{mm\sp{2}/s}$ \cite{Helenius194}
 while values in dementia typically are XXX \kam{Geir vet du dette?}. Of course diffusion coefficient 
-measured by DTI at a time-scale of XXX \kam{tall her} may not be representative for the process on a
+measured by DTI at a time-scale of 7-30 minutes, may not be representative for the process on a
 longer time-scale, at least if the paravascular pathway plays an important role. The fact that the vasculature  occupy around 3\% of the brain volume 
@@
 The observation points are distributed with 5 observations within 1-2 hours after injection, 1 observation in the timeframes 2-4 hours, 6-9 hours, 24 hours and 48 hours.
-Figure~\ref{fig2} shows the slice selected for our computations. 
+Figure~\ref{fig2} shows the region selected for our computations. 
 The software Freesurfer {\color{red} citation needed, Hvilken ? } was used to segment and align each of the observations, which made it possible to estimate voxelwise intensity increase.
@@
 We remark that we use a notation common in medical literature and here two letter symbols are common.
-Hence, below we will use two letter symbols such as $TE$ and $TR$ to keep the notation consistent the presentation in \cite{GOWLAND}\cite{MPRAGE}.
+Hence, below we will use two letter symbols such as $TE$ and $TR$ to keep the notation consistent the presentation in \cite{GOWLAND, MPRAGE}.
 The tracer concentration $c$ causes the longitudinal(spin-lattice) relaxation time $T_{1}$ to shorten with the following relation
@@
 \end{equation}
-The superscripts indicating with contrast and without contrast and $r_1$ as the relaxivity constant for the MRI-contrast in a medium.
+The superscripts indicating with contrast and without contrast and $r_1$ as the relaxivity constant for the MRI tracer in a medium. 
+The tracer observations were collected using a MRI sequence known as  Magnetization Prepared Rapid Acquisition Gradient Echo (MPRAGE) with an inversion prepared magnetization.
 The relation between intensity and the relaxation time is non-linear, and is expressed with the following equations.
-The signal intensity $S$ of the sequence is given by
+The signal intensity $S$ for this sequence is given by
 \begin{equation}
@@
 \end{equation}
-{\color{red} kommer inversion prepared fram ?}
 In article \cite{GOWLAND}, the term $M_n$ is defined as the magnetization for the n-echo 
@@
 The $M_0$ is a calibration constant of the magnetization.
-The center echo denoted as $n=m/2$ will be the signal that we will consider when estimating MRI-contrast.
+The center echo denoted as $n=m/2$ will be the signal that we will consider when estimating MRI tracer.
 Given Eq.\ref{EQ::SI} we have that relative intensity increase can be written as
@@
 f(T_1) = M_{n}/M_{0} ,
-\label{Eq::F}
+\label{scaledmagnetization}
 \end{equation}
@@
 \end{equation}
-The intensity difference between observation times were adjusted in \cite{eidevalnes}. Thus we can express the $T_1$ change due to contrast as 
+The intensity difference between observation times were adjusted in \cite{eidevalnes}. Thus we can express the $T_1$ change due to tracer as 
 \begin{equation}
@@
 \end{equation}
-and we can then estimate concentration using Eq.\ref{EQ::contrast} if we know $T_{1}\sp{0}$.
+and then estimate the concentration using Eq.\ref{EQ::contrast}.
 The $T_{1}\sp{0}$ values were obtained by T1 mapping the brain using a MRI sequence known as MOLLI5(3)3 \cite{TAYLOR201667}.
 This makes it possible to  take into account patients specific characteristic, such as tissue damage.
-There are several forms of tissue damage that can be observed in the MRI due to a lower intensity in the white matter compared to healthy white matter tissue, hence damaged tissue have different T1 relaxation time.
+Tissue damage can be observed in the MRI due to a lower intensity in the white matter compared to healthy white matter tissue, this causes damaged tissue to have different $T_1$ relaxation time.
 
@@
 The diffusivity of the Gadovist (600 Da \cite{MGadobutrol}) was estimated to be similar to the diffusion coefficient of Gd-DPTA (550 Da \cite{MGgDPTA}).
-This due to the fact that both molecules have similar mass/size, and based Stoke-Einstein equation should have similar diffusion coefficients.
+This due to the fact that both molecules have similar mass, and based Stoke-Einstein equation should have similar diffusion coefficients.
 The free diffusion coefficient for Gd-DPTA was estimated in \cite{GdDPTA-DIFFUSION} to be $3.8e-4\mathrm{mm\sp{2}/s}$.
-
-{\color{red} må skrive om B-values og parameter}
-
 The fractional anisotropy is defined as 
@@
 In \cite{sykova2008diffusion}, it was shown that the macroscopic diffusion in the brain can be considered a hindered diffusion with an apparent diffusion coefficient.
-In order to estimate the apparent diffusion coefficient involved in the contrast transportation shown in Figure~\ref{fig1} we assume that the process can be modeled by a diffusion equation and solve a PDE constrained optimization problem where
-the contrast distribution, boundary conditions, and apparent
+In order to estimate the apparent diffusion coefficient involved in the tracer transportation shown in Figure~\ref{fig1} we assume that the process can be modeled by a diffusion equation.
+Then we solve a PDE constrained optimization problem where
+the tracer distribution, boundary conditions, and apparent
 diffusion coefficient are solved for by optimizing with
-respect to the observed contrast distribution. As such, enhanced transportation because of effects such as
+respect to the observed tracer distribution. As such, enhanced transportation because of effects such as
 dissipation would result in an apparent diffusion coefficient larger than that predicted by DTI.  
@@
 The $\alpha$ and $\beta$ parameters are non-negative regularization parameters 
-and $u_{obs}$ are observations at certain time-points.
+and $u_{obs}$ are observations at certain time-points $t_i$.
 
@@
 %and the initial condition was set to 1.0 in $\Omega_1$ and 0 elsewhere.
-The manufactured forward computation gave a total of 120 possible observation times, which  will be denoted as $t_i$.
+The manufactured forward computation gave a total of 120 possible observation times.
 
@@
 The estimation of the tracer concentration was precomputed and used the parameters obtained from the T1 map, MPRAGE MRI protocol \cite{eidevalnes} and the value for $r_1$ found in \cite{pmid16230904}.
-In the computation, the function $f(T_1)$ was computed for $ T_1\in \lbrace 200, 4000 \rbrace$ creating a lookup table.
+In the computation, the function Eq.\ref{scaledmagnetization} was computed for $ T_1\in \lbrace 200, 4000 \rbrace$ creating a lookup table.
 The lookup table was utilized with the baseline intensity increase to estimate $T_1\sp{c}$, and then the concentration was computed using Eq.\ref{EQ::contrast}.
@@
 The linear problem was solved using GMRES, and the matrix was stored in the solver.
-The module dolfin adjoint ~\cite{farrell2013automated} \kam{correct ref?}  was used to solve the PDE constrained optimization problem with the L-BFGS-B algorithm in the python module scipy \cite{LBFGSB1},\cite{LBFGSB2}.
-
-The convergence criteria for the minimization was set so that $|| x ||_{L\sp{inf}} \leq \epsilon=1.0e-1$ with $x$ denoting the projected gradient.
-{\color{red} From scipy :The iteration will stop when $max\lbrace | \text{proj} \hspace*{0.2cm} g_i | , \quad i = 1, .., N \rbrace \leq gtol $  where $pg_i$ is the i-th component of the projected gradient.}
+The module dolfin adjoint ~\cite{farrell2013automated} \kam{correct ref?}  was used to solve the PDE constrained optimization problem with the L-BFGS-B algorithm in the python module scipy \cite{LBFGSB1, LBFGSB2}.
+
+The convergence criteria for the minimization was set so that 
+\begin{equation}
+x ||_{L\sp{\infty}} \leq \epsilon
+\end{equation} 
+with $\epsilon=1.0e-1$ and $x$ denoting the projected gradient.
 
@@
 
-The results shown in Tabel~\ref{Tab::1} shows similar end-result for most regularization parameters.
+The results shown in Tabel~\ref{Tab::1}, and we can see similar end-result for most regularization parameters.
 However, in the case of $ \alpha=1.0$ the relative error over 100\% higher then for other values of $\alpha$.
-Furthermore, it can also be seen in the table that $ \forall \beta=100.0$ there is about 70\% relative error for $D_{\Omega_1}$ and approximate 10\% error for $D_{\Omega_2}$, which is higher than other values of $\beta$.
-
-From the results it can be discerned that $\alpha =1.0$ and $\beta=100.0$ represent an upper  boundary where the residual is no longer the dominant term in the objective functional.
+Furthermore, it can also be seen in the table that for all $\beta=100.0$ there is about 70\% relative error for $D_{\Omega_1}$ and approximate 10\% error for $D_{\Omega_2}$ .
+
+From the results it can be discerned that $\alpha =1.0$ and $\beta=100.0$ represent an upper boundary where the observations are no longer the dominant term in the objective functional.
 
@@
 \caption{Convergence of the diffusion coefficients, boundary conditions and functional with respect to different $\alpha$ and $\beta$ values. } 
+\label{convergence}
 \end{figure}
@@
 Increasing the number of time-steps in the computations can potentially allow for a more accurate temporal reconstruction, but at the same time the number of observations per control decreases and the regularization may therefore play a larger role.
-Furthermore, the computational cost will rise due to additional number of time-steps.
-%Thus finding the optimal number of time-steps can give an effective convergence for larger problems . 
+Furthermore, the computational cost will rise with additional time-steps.
+Thus finding the optimal number of time-steps can be essential for larger problems.
 The computation used different regularization parameters with 10, 20 and 40 timesteps.
 
-The results are given in Tab.\ref{TAB::timesteps}, and it can be seen $\forall \alpha=1.0$ that the relative error becomes bigger with more time-steps.
-This behavior can also be seen for $\alpha=1.0e-2$ and $\beta = 1.0e-4 , 1.0e-6$, and followed by a rise in the number of iterations.
-The increase time-steps causes most values of regularization parameters to increase number of iterations, but for some values the number of iterations decreases.
+The results are given in Tab.\ref{TAB::timesteps}, and it can be seen for all $\alpha=1.0$ that the relative error becomes bigger with more time-steps.
+This behavior can also be seen for $\alpha=1.0e-2$ and $\beta < 1.0e-2$, which implies an interaction between the regularization parameters.
+Thus $g$ was investigated by plotting boundary points through time for different values of $\alpha$ and $\beta$, see Fig \ref{boundarycontrol}.
+In Figure \ref{boundarycontrol} we can see that more time-steps causes  oscillations for $\alpha=1.0$, and each peak corresponds to a observation time.
+The oscillations are caused by $\alpha$, which tries minimize $g$ between observation times.
+
+It can be seen that more time-steps causes an increase number of iterations, but for some values the number of iterations decreases.
 These values share that $\alpha $ is a magnitude 2 lower than $ \beta$,i.e $\alpha=1.0e-2$ and $\beta =1.0$.
 This indicates that $\alpha $ should be smaller than $\beta$ to achieve optimal convergence.
-But taking into account the values in Table ~\ref{Tab::1} ??
-
-Given the boundary control $g$ through time by selecting high and low values of $\alpha$ and $\beta$, see Fig \ref{boundarycontrol}.
-Figure \ref{boundarycontrol} displays oscillations for $\alpha=1.0$ with $k=40$.
-The oscillation peaks correlate with the observation times.
-It can also be observed that $\alpha=1.0e-4$ and $\beta=1.0e-4$ there is a small oscillation.
+However, the number of iterations in Table ~\ref{Tab::1} are smaller for all regularization parameters.
 
@@
 The dependency on observations is relevant, since the number of observations of the MRI data is limited.
-This was investigated by changing the number of observations, and examine the resulting states.
-The number of observation were chosen to be 5, 10  and 20, and times were set to be evenly spaced.
-The range of regularization parameters were restricted to values that have low relative error.
+This was investigated by changing the number of observations, and examine the results.
+The number of observation were chosen to be 5, 10  and 20, and the observation times were evenly spaced.
+The range of regularization parameters were restricted to values that displayed low relative error.
 
 The results are shown in Tab.\ref{TAB::timesteps}, Tab.\ref{TAB::double} and Tab.\ref{TAB::half}.
-In Tab.\ref{TAB::half}, the values $\alpha =1.0e-2$ and $\beta=1.0e-2,1.0e-4$ gives a surge in the relative error with more time-steps.
-This behavior is neither visible in Tab.\ref{TAB::timesteps} and Tab.\ref{TAB::double} given the same regularization parameters.
-
-In Table ~\ref{TAB::double} some values have a drastic change in convergence rate with increase of number of iteration (Hypothesis $i < k$ is better than $i = k$, i is number of observations)
-
-The observations functions as stabilization for the functional so that the error between observations becomes smaller, which gives a broader rang of adequate regularization parameters.
+In Tab.\ref{TAB::half}, the values $\alpha =1.0e-2$ and $\beta<1.0$ gives a surge in the relative error with more time-steps.
+This behavior is neither visible in Tab.\ref{TAB::timesteps} or Tab.\ref{TAB::double} given the same regularization parameters.
+It seems likely that this error is caused by oscillations, seen in Figure~\ref{boundarycontrol}.
+
+The observations acts as stabilization for the functional, which gives a broader range of adequate regularization parameters.
+
+%In Table ~\ref{TAB::double}, we can see that $\aplha < 1.0e-2$ and $\beta =1.0e-2$ have a drastic change in the number of iteration for $20$ time-steps.
 
@@
 However, in Tabel~\ref{Tab::Noise0.3} the noise amplitude was increased to 0.3 (100$\%$ of maximum initial condition) and it is observed that for  $\alpha \leq 1.0e-4$  and $\beta \leq 1.0e-4$ the optimization failed to converge before reaching maximum iteration of 1000 steps.
-Furthermore, the relative boundary error $||g||_{RE(\Omega)}$ is  larger for lower values of $\beta$.
-
-Tt can be concluded from the results that increasing the number of iterations gives rise to oscillations for poor regularizations parameters.
+Furthermore, the relative boundary error $||g||\sp{rel}_{L\sp{2}(\Omega_1)}$ is larger for lower values of $\beta$.
 
@@
 \centering
-\includegraphics[scale=0.4]{12-clrscl-0413-regp--40-interp-white-2.png}  
+\includegraphics[scale=0.4]{noise-12.png}  
 \caption{The upper row shows the manufactured observation, A ) Shows the manufactured observation at time-point 24 with no noise added.
@@
 \centering
-\includegraphics[scale=0.4]{24-clrscl-0212-regp--40-interp.png}
+\includegraphics[scale=0.4]{noise-24.png}
 \caption{The upper row shows the manufactured observation, A ) Shows the manufactured observation at time-point 24 with no noise added.
@@
 The boundary control was set to the external boundary of both domains, and the subscript in $D_w$ and $D_g$ denotes white and grey diffusion coefficients.
-Furthermore, bounds were added to the L-BFGS-B algorithm to ensure non-negative boundary controls and the convergence criteria was adjusted to $gtol=6.0e-1$.
+Furthermore, bounds were added to the L-BFGS-B algorithm to ensure non-negative boundary controls and the convergence criteria was adjusted to $\epsilon=6.0e-1$.
 The number of timesteps were selected to be $k=24$ and $k=48$, which gives $dt = 2 hour$ and $dt = 1 hour$.
 
-The results are shown in Tab.\ref{Tab::Real-data}, and the observations after 12 and 48 hours were compared with the corresponding states.
+The results are shown in Tab.\ref{Tab::Real-data}, and the observations after 12 and 48 hours were compared with the corresponding states in Figure~\ref{Fig::realdata}.
 
@@
 
-% \begin{table}
-%\centering
-%\caption{Viser omgjøringer,estiamering og prosentvis forskjell for min og max control/optimerte verdier . Unit $\left[ \mathrm{mm\sp{2}/h} \right]$}
-%\begin{tabular}{*{2}c}
-% Parameter    & Value \\
-%\hline
-%Median 
-%\end{tabular}
-%\label{}
-%\end{table} 
-%%
-
 The median diffusion coefficient in the DTI was estimated to be $8.7e-4 \mathrm{mm\sp{2}/s}$ in white matter and $1.0e-3 \mathrm{mm\sp{2}/s}$ in grey matter.
-This corresponds to $1.85$ and $1.73$ in tortuosity, given that the self-diffusivity of water has been estimated to be around $3.0e-3\mathrm{mm\sp{2}/s}$ at $37\sp{o}C$.% This corresponds to 10.8 $\mathrm{mm\sp{2}/h}$ and  $\mathrm{mm\sp{2}/h}$.
-Then by using the reference value $3.8e-4 \mathrm{mm\sp{2}/s}$ for Gd-DPTA gives an estimate for the diffusion coefficient in the grey and white matter to respectively be $ 1.26e-4\mathrm{mm\sp{2}/s}$ and $1.10e-4 \mathrm{mm\sp{2}/s}$.
-This estimation assumes that the tortuosity is independent on molecular size .
+This corresponds to $1.85$ and $1.73$ in tortuosity, given that the self-diffusivity of water has been estimated to be around $3.0e-3\mathrm{mm\sp{2}/s}$ at $37\sp{o}C$.
+For the reference value $3.8e-4 \mathrm{mm\sp{2}/s}$ for Gd-DPTA gives an estimate for the diffusion coefficient in the grey and white matter to respectively be $ 1.26e-4\mathrm{mm\sp{2}/s}$ and $1.10e-4 \mathrm{mm\sp{2}/s}$.
+This estimation assumes that the tortuosity is independent on molecular size.
 
@@
 Therefore the states with $k=48$ were examined after 36 hours, see Figure\ref{statecomparison}.
-It can be observed that the upper right row displays a discrepancy, which likely due to wrong regularization parameters.
-This prompt the exclusion of the corresponding values, which gives an average computed values $??
-\mathrm{mm\sp{2}/h}$ and  $??
-\mathrm{mm\sp{2}/h}$ in respectively grey and white matter.
+It can be observed that the upper right row displays a discrepancy, which likely due to inadequate regularization parameters.
+Furthermore, we can see that for $\alpha=1.0e-2$ there is a clear discrepancy in the diffusion coefficents compared to other values $\alpha$.
+This prompt the exclusion of the corresponding values, which gives an average computed values $ 0.65 \mathrm{mm\sp{2}/h}$ and  $ 0.8 \mathrm{mm\sp{2}/h}$ in respectively grey and white matter.
 Scaled to $\mathrm{mm\sp{2}/s}$ gives $1.8e-4\mathrm{mm\sp{2}/s}$ and $2.22e-4 \mathrm{mm\sp{2}/s}$.
@@
 
-The computation require that there is tracer present to compute the diffusion coefficient.
 In Fig.\ref{Fig::realdata}, it can be seen that there were regions with negligible amount of tracers and vice versa.
-
-The observation after 24 hours was used to compute the area containing $90\%$ of the  concentration in white matter.
-This area was then used to calculate the median diffusion coefficient given the data in Figure ~\ref{figuredti}, and it was estimated to be  $??
-e-3 \mathrm{mm\sp{2}/s}$.
-This correspondence to a tracer diffusion coefficient of $??e-4 \mathrm{mm\sp{2}/h}$ , which gives a relative error of $??\%$ difference compared to the computed values.
+The regions with above average amount of tracers corresponds with high diffusivity regions in Figure~\ref{figuredti}.
+This suggests that the computed diffusion coefficients corresponds to these values.
+The ADC value in the high diffusivity regions are closer to  $1.4e-3 \mathrm{mm\sp{2}/s}$ {\color{red}adjust scale in ADC image ?}, which corresponds to estimated diffusion coefficent of value $1.5e-3 \mathrm{mm\sp{2}/s}$.
+This gives a relative error of $ 46 \%$ compared to the computed values.
 
@@
 well for regularization parameters varying by orders of magnitude. It is particularly interesting to see that the procedure efficiently removes noise as demonstrated
-in the Figures \ref{12hourswithnoise} and \ref{24hourswithnoise} with noise levels of 30\% \kam{is this correctly stated}{\color{red} (0.3,-0.3) added to all values with peak of 1.3 at 12 h }. 
+in the Figures \ref{12hourswithnoise} and \ref{24hourswithnoise} with noise levels of 30\% \kam{is this correctly stated}{\color{red} (0.3,-0.3) added to all values in range (0,g(t))}. 
 Crucial in our application is the interplay between the regularization term that regulates the smoothness of the boundary conditions as well as
@@
 \section{Conclusion}
+
+It can be concluded from the results that increasing the number of iterations gives rise to oscillations for poor regularizations parameters.
 
@@
 \hline
- 1.0e-02 	 & 1.0e+00 	 & 24 & 503 	 & +0.659 & +0.918 \\ 
- 1.0e-02 	 & 1.0e-01 	 & 24 & 716 	 & +0.771 & +0.969 \\ 
- 1.0e-02 	 & 1.0e-02 	 & 24 & 505 	 & +0.836 & +0.974 \\ 
- 1.0e-04 	 & 1.0e+00 	 & 24 & 206 	 & +0.553 & +0.828 \\ 
- 1.0e-04 	 & 1.0e-01 	 & 24 & 440 	 & +0.651 & +0.789 \\ 
- 1.0e-04 	 & 1.0e-02 	 & 24 & 597 	 & +0.718 & +0.739 \\ 
- 1.0e-06 	 & 1.0e+00 	 & 24 & 439 	 & +0.570 & +0.830 \\ 
- 1.0e-06 	 & 1.0e-01 	 & 24 & 583 	 & +0.656 & +0.793 \\ 
- 1.0e-06 	 & 1.0e-02 	 & 24 & 742 	 & +0.721 & +0.729 \\
+ 1.0e-02 	 & 1.0e+00 	 & 24 & 503 	 & 0.659 & 0.918 \\ 
+ 1.0e-02 	 & 1.0e-01 	 & 24 & 716 	 & 0.771 & 0.969 \\ 
+ 1.0e-02 	 & 1.0e-02 	 & 24 & 505 	 & 0.836 & 0.974 \\ 
+ 1.0e-04 	 & 1.0e+00 	 & 24 & 206 	 & 0.553 & 0.828 \\ 
+ 1.0e-04 	 & 1.0e-01 	 & 24 & 440 	 & 0.651 & 0.789 \\ 
+ 1.0e-04 	 & 1.0e-02 	 & 24 & 597 	 & 0.718 & 0.739 \\ 
+ 1.0e-06 	 & 1.0e+00 	 & 24 & 439 	 & 0.570 & 0.830 \\ 
+ 1.0e-06 	 & 1.0e-01 	 & 24 & 583 	 & 0.656 & 0.793 \\ 
+ 1.0e-06 	 & 1.0e-02 	 & 24 & 742 	 & 0.721 & 0.729 \\
 

### 2018-10-22 tex/paper.tex
more added

@@
 
-\title{Assessing glymphatic transport velocities by adjoint methods}
+\title{Assessing paravascular transport in the parenchyma by PDE constrained optimization.}
 
@@
 \section{Introduction}
-Recent breakthroughs in medicine have linked diseases like Alzheimer's to insufficient sleep through a novel biomechanical mechanism called the glymphatic system 
+Recent breakthroughs in medicine have linked neurodegenerative diseases like Alzheimer's to insufficient sleep through a novel fluid mechanism called the glymphatic system 
 that is responsible for waste clearance. 
-In 2011,~\cite{iliff2012paravascular} discovered a novel system within our brain's metabolism system, which changed our understanding of the brain. 
+In 2011,~\citet{iliff2012paravascular} discovered a novel system within our brain's metabolism system, which changed our understanding of the brain. 
 The system involves a new pathway, called the paravascular pathway as it runs in parallel with vasculature system in a surrounding compartment.
 The important novelty in the 2011 findings was that waste from the brain is cleared through the paravascular path, and that a malfunction of this system 
-is linked to the development of dementia such as Alzheimer's and Parkinson's diseases. In 2013,~\cite{xie2013sleep} found
+is linked to the development of dementia such as Alzheimer's and Parkinson's diseases. In 2013,~\citet{xie2013sleep} found
 that this system is particularly active during sleep.
 These mentioned breakthroughs were all performed in mice. In 2018,  
-the project's collaborators for the first time demonstrated the action of
+it was for the first time demonstrated the action of
 this system in humans, and that the action of the system differs
-between healthy controls and patients with dementia~\cite{ringstad2018brain}. 
-However, the biomechanical mechanisms behind this is not well understood,
-and so far the modeling attempts have mostly failed~\cite{asgari2016glymphatic, holter2017interstitial, smith2017glymphatic}. 
+between healthy controls and patients with dementia~\citet{ringstad2018brain}. 
+However, the biomechanical mechanisms behind this is not well understood from a fluid mechanics perspective,
+and so far the modeling attempts have mostly failed~\citet{asgari2016glymphatic, holter2017interstitial, smith2017glymphatic}. 
 In particular the system seems to facilitate waste transport faster than  
-the diffusion, which since the pioneering works of \cite{sykova2008diffusion} 
+the diffusion, which since the pioneering works of \citet{sykova2008diffusion} 
 has been the prevailing paradigm. Here, we aim to investigate whether PDE constrained optimization can be used
@@
 In \cite{ringstad2018brain} brain-wide distribution of MRI-contrast was demonstrated during 24 hours after lumbar contrast injection.
-Brain-wide distribution by diffusion alone was deemed unlikely by the authors (some of which are part
-of this study as well). The argument was based on analytical considerations where it was calculated that 50\% contrast enrichment would occur after 
+Brain-wide distribution by diffusion alone was deemed unlikely by the authors (some of which are co-authors).
+The argument was based on analytical considerations where it was calculated that 50\% contrast enrichment would occur after
 55 hours using the error function which is valid for planar diffusion. However, 
@@
 Furthermore, images were obtained only at a few time-points during the investigations in \cite{ringstad2018brain}.
+As such the sparseness i times prevent a direct computation of the diffusion coefficients.
 
@@
 The approach we will take is to solve a PDE constrained optimization problem 
-via adjoint methods where we have sparse observations on selected time-points, around 10 acquisitions during 24 hours, but through
+via adjoint methods where we have sparse observations on selected time-points, around 10 acquisitions during 24 hours. But through
 the complete domain. Hence, the challenges faced from a mathematical point of view 
-are that 1) the images are subject to noise, resolution in space is limited to slightly less than (1 mm)$^3$ and 
+are that 1) the images are subject to noise, 2) resolution in space is limited to slightly less than (1 mm)$^3$ and 3)
 the sparse observations through the time domain.  As such we need to assess the sensitivity of
-the approach with respect important parameters such as to regularization parameters, noise levels, 
+the approach with respect important parameters such as to regularization parameters, noise levels and 
 time resolution to determine whether this approach is a viable method
-to obtain parameters involved time-scales beyond those of the MRI acquisition. We remark that the purpose
+to obtain parameters involved time-scales. We remark that the purpose
 of this paper is a systematic study of the mathematical challenges and that assessing  
@@
 In Section 2 we present the methodology of the paper. Section 2.1-2.3 contains a detailed description of the medical imaging 
-relevant to this study and do not expect the reader to have prior knowledge of medical imaging. Section 2.4
+relevant to this study as we do not expect the reader to have prior knowledge of medical imaging. Section 2.4
 describes the PDE constrained optimization problem and the corresponding solution algorithm, while 2.5 presents
@@
 Our data (not all shown) consist of a total of 10 MRI observations, including a baseline MRI taken before tracer was injected.
-The observation points are distributed with 5 observations within 1-2 hours after injection, 1 observation in the timeframes 2-4 hours, 6-9 hours, 24 hours and 48 hours.
+The observation points are distributed with 5 observations within 1-2 hours after injection, a single observation in the timeframes 2-4 hours, 6-9 hours, 24 hours and 48 hours.
 Figure~\ref{fig2} shows the region selected for our computations. 
-The software Freesurfer {\color{red} citation needed, Hvilken ? } was used to segment and align each of the observations, which made it possible to estimate voxelwise intensity increase.
+The software Freesurfer \cite{Dale1999179, FischlLiuDale, spf2007, reuter:robreg10} was used to segment and align each of the observations, which made it possible to estimate voxelwise intensity increase.
+
+The MRI data is obtained from a larger study, which invloves around 100 patients with similar MRI acquisitions.
+However, due to the clinical factor, some of the parameters involved are different.
+Thus a thorough analysis is needed to obtain a robust and accurate method.
 
@@
 \end{equation}
-The superscripts indicating with contrast and without contrast and $r_1$ as the relaxivity constant for the MRI tracer in a medium. 
+The superscripts indicating with contrast $T_{1}\sp{c}$ and without contrast $T_{1}\sp{0}$ and $r_1$ as the relaxivity constant for the MRI tracer in a medium. 
 The tracer observations were collected using a MRI sequence known as  Magnetization Prepared Rapid Acquisition Gradient Echo (MPRAGE) with an inversion prepared magnetization.
@@
 The expression can be simplified by neglecting the $T_2$ term in the signal, since $TE <<T_2\sp{*}$ for this MRI sequence.
-Thus Eq.
-\ref{EQ::SI_T2} becomes
+Thus \eqref{EQ::SI_T2} becomes
 \begin{equation}
@@
 \end{equation}
-which gives the following relation 
+which can be seen in Figure () . 
+This gives the following relation 
 \begin{equation}
@@
 \end{equation}
-The intensity difference between observation times were adjusted in \cite{eidevalnes}. Thus we can express the $T_1$ change due to tracer as 
+The intensity difference between observation times were adjusted in \cite{eidevalnes}. Thus we can express the change in $T_1$ due to tracer as 
 \begin{equation}
@@
 \end{equation}
-and then estimate the concentration using Eq.\ref{EQ::contrast}.
+and then estimate the concentration using \eqref{EQ::contrast}.
 The $T_{1}\sp{0}$ values were obtained by T1 mapping the brain using a MRI sequence known as MOLLI5(3)3 \cite{TAYLOR201667}.
-This makes it possible to  take into account patients specific characteristic, such as tissue damage.
-Tissue damage can be observed in the MRI due to a lower intensity in the white matter compared to healthy white matter tissue, this causes damaged tissue to have different $T_1$ relaxation time.
+This takes into account patients specific characteristic, such as tissue damage.
+Tissue damage can be observed in the MRI due to a lower intensity in the white matter compared to healthy white matter tissue, thus damaged tissue have different $T_1$ relaxation time.
+
+\begin{figure}
+\centering
+\includegraphics[width=0.70\textwidth]{T1function.png} 
+\caption{Show the  function defined in \eqref{scaledmagnetization}. }
+\label{figuredti} 
+\end{figure}
 
@@
 coefficients on short time-scales. Images are shown in Figure~\ref{figuredti} where the larges diffusion coefficient (shown in 
-red in the middle figure) is shown to be around 0.001 mm$^2$/s. We remark that we have not included possible anisotropy, shown in 
+red in the middle figure) is shown to be around $1.0e-3 mm^2/s$. We remark that we have not included possible anisotropy, shown in 
 the right-most image in Figure~\ref{figuredti} and that these images shows the apparent diffusion coefficient for free water molecules (18 Da).      
@@
 
-\subsection{Manufactured Solution}
-In order to verify our strategy and test the dependency of the
-regularization parameters, we perform a test case with a
-known solution.  
-The manufactured observations was obtained by forward computation of Eq.\ref{Eq::PDE} with the Dirichlet boundary condition defined as
-\begin{equation}
-g(t)_{\partial \Omega_1} = 0.3 +0.167t - 0.007t\sp{2} \qquad  0 \leq t \leq 24.
-\label{EQ::DIRI}
-\end{equation}
-The timestep was $dt = 0.02$, and the diffusion coefficients were selected to be 
-\begin{equation}
-D_{\Omega_1} = 1000 \quad , \quad D_{\Omega_2} = 4.0 \quad , \quad D_{\Omega_3} = 8.0 
-\end{equation}  
-The magnitude order for $D_{\Omega_1} $ and $D_{\Omega_2}$ were chosen to resemble diffusion coefficient for water in grey and white matter, but the relation between the coefficients were not preserved.
-The diffusion coefficient in the CSF was chosen given [cite Bryne and Kent], and the initial condition was set to 0 everywhere.
-%and the initial condition was set to 1.0 in $\Omega_1$ and 0 elsewhere.
-The manufactured forward computation gave a total of 120 possible observation times.
-
 The mesh construction was patient-specific and used the MRI of a patient diagnosed with idiopathic normal pressure hydrocephalus (iNPH).
@@
 
+\subsection{Manufactured Solution}
+In order to asses the robustness and accuracy of our strategy and test the dependency of the
+regularization parameters, we perform a test case with a
+known solution.  
+The manufactured observations was obtained by forward computation of Eq.\ref{Eq::PDE} with the Dirichlet boundary condition defined as
+\begin{equation}
+g(t)_{\partial \Omega_1} = 0.3 +0.167t - 0.007t\sp{2} \qquad  0 \leq t \leq 24.
+\label{EQ::DIRI}
+\end{equation}
+The timestep was $dt = 0.02$, and the diffusion coefficients were selected to be 
+\begin{equation}
+D_{\Omega_1} = 1000 \quad , \quad D_{\Omega_2} = 4.0 \quad , \quad D_{\Omega_3} = 8.0 
+\end{equation}  
+The magnitude order for $D_{\Omega_1} $ and $D_{\Omega_2}$ were chosen to resemble diffusion coefficient for water in grey and white matter, but the relation between the coefficients were not preserved.
+The diffusion coefficient in the CSF was chosen given [cite Bryne and Kent], and the initial condition was set to 0 everywhere.
+%and the initial condition was set to 1.0 in $\Omega_1$ and 0 elsewhere.
+The manufactured forward computation gave a total of 120 possible observation times.
+
 \section{Implementation}
@@
 \begin{equation}
-x ||_{L\sp{\infty}} \leq \epsilon
+||x ||_{L\sp{\infty}} \leq \epsilon
 \end{equation} 
@@
 
+\subsection{Acknowledgement}
 This work was performed on the Abel Cluster, owned by the University of Oslo and Uninett\textbackslash Sigma2, and operated by the Department for Research Computing at USIT,the University of Oslo IT-department.
@@
 Below we will discuss the parameter identification and its sensitivity with respect to regularization parameters, noise and time-resolution.
-In presentation of the results, the relative error norm is defined as
+In presentation of the results, the relative error is defined as
 \begin{equation}
@@
 \begin{equation}
-|| g ||\sp{rel}_{L\sp{2}(\Omega_1)} = \frac{ \sum\limits_t\sp{k}| g_{found}(t) -g_{true}(t)||_{L(\Omega_1)} }{  \sum\limits_t\sp{k}||g_{true}(t)||_{L(\Omega_1)} }
-\end{equation}
-In the case that the minimization algorithm fails to converge within 1000 iteration will be indicated by a hyphen.
+|| g ||\sp{rel}_{L\sp{2}(\Omega_1)} = \frac{ \sum\limits_t\sp{k}|| g_{found}(t) -g_{true}(t)||_{L(\Omega_1)} }{  \sum\limits_t\sp{k}||g_{true}(t)||_{L(\Omega_1)} }
+\end{equation}
+In the case that the minimization algorithm fails to converge within 1000 iteration will be indicated by a hyphen in Table~\ref{TAB::timesteps} Table~\ref{TAB::double}} and Table~\ref{Tab::Noise0.3}
 
@@
 
-From the results it can be discerned that $\alpha =1.0$ and $\beta=100.0$ represent an upper boundary where the observations are no longer the dominant term in the objective functional.
+From the results it can be discerned that $\alpha =1.0$ and $\beta=100.0$ represent an upper threshold where the observations are no longer the dominant term in the objective functional.
 
@@
 Thus finding the optimal number of time-steps can be essential for larger problems.
-The computation used different regularization parameters with 10, 20 and 40 timesteps.
+The computation varied the regularization parameters with 20 and 40 timesteps.
 
@@
 This behavior can also be seen for $\alpha=1.0e-2$ and $\beta < 1.0e-2$, which implies an interaction between the regularization parameters.
-Thus $g$ was investigated by plotting boundary points through time for different values of $\alpha$ and $\beta$, see Fig \ref{boundarycontrol}.
+Therefore $g$ was investigated by plotting boundary points through time for different values of $\alpha$ and $\beta$, see Fig \ref{boundarycontrol}.
 In Figure \ref{boundarycontrol} we can see that more time-steps causes  oscillations for $\alpha=1.0$, and each peak corresponds to a observation time.
-The oscillations are caused by $\alpha$, which tries minimize $g$ between observation times.
+These oscillations are caused by $\alpha$, which tries minimize $g$ between observation times.
 
@@
 This was investigated by changing the number of observations, and examine the results.
-The number of observation were chosen to be 5, 10  and 20, and the observation times were evenly spaced.
-The range of regularization parameters were restricted to values that displayed low relative error.
-
-The results are shown in Tab.\ref{TAB::timesteps}, Tab.\ref{TAB::double} and Tab.\ref{TAB::half}.
+The number of observation were chosen to be 5 and 20, and the observation times were evenly spaced.
+
+The results are shown in Tab.\ref{TAB::double} and Tab.\ref{TAB::half}.
 In Tab.\ref{TAB::half}, the values $\alpha =1.0e-2$ and $\beta<1.0$ gives a surge in the relative error with more time-steps.
@@
 \subsubsection{Results obtained when using real observations}
-The MRI data consisted of the observations at times $t_i \in \lbrace$ 0.00, 0.16, 0.39, 0.55, 0.77, 2.09, 6.05, 24.06, 47.84, 698.02 $\rbrace (hours)$ with the time $t_i=0.00$ as the observation 1-2 hours after the tracer was injected.
+The MRI data consisted of the observations at times $t_i \in \lbrace$ 0.00, 0.16, 0.39, 0.55, 0.77, 2.09, 6.05, 24., 48., 698.
+$\rbrace (hours)$ with the time $t_i=0.00$ as the observation 1-2 hours after the tracer was injected.
 There was no significant visible change in the tracer between the observations at $\lbrace $ 0.00, 0.16, 0.39, 0.55, 0.77 $ \rbrace$.
-This prompted the use of the following observation times  $0.00, 2.09, 6.05, 24.06, 47.84$.
+This prompted the use of the following observation times  $0.00, 2.09, 6.05, 24., 48.$.
 
@@
 The results are shown in Tab.\ref{Tab::Real-data}, and the observations after 12 and 48 hours were compared with the corresponding states in Figure~\ref{Fig::realdata}.
+From Table~\ref{Tab::Real-data},it can be observed that $D_w$ have a higher value for $\alpha =1.0e-2$.
 
@@
 The median diffusion coefficient in the DTI was estimated to be $8.7e-4 \mathrm{mm\sp{2}/s}$ in white matter and $1.0e-3 \mathrm{mm\sp{2}/s}$ in grey matter.
-This corresponds to $1.85$ and $1.73$ in tortuosity, given that the self-diffusivity of water has been estimated to be around $3.0e-3\mathrm{mm\sp{2}/s}$ at $37\sp{o}C$.
-For the reference value $3.8e-4 \mathrm{mm\sp{2}/s}$ for Gd-DPTA gives an estimate for the diffusion coefficient in the grey and white matter to respectively be $ 1.26e-4\mathrm{mm\sp{2}/s}$ and $1.10e-4 \mathrm{mm\sp{2}/s}$.
+This corresponds to a tortuosity of $1.85$ and $1.73$, given that the self-diffusivity of water has been estimated to be around $3.0e-3\mathrm{mm\sp{2}/s}$ at $37\sp{o}C$.
+Fhe reference value $3.8e-4 \mathrm{mm\sp{2}/s}$ for Gd-DPTA gives an estimate for the apparent diffusion coefficient in the grey and white matter to respectively be $ 1.26e-4\mathrm{mm\sp{2}/s}$ and $1.10e-4 \mathrm{mm\sp{2}/s}$.
 This estimation assumes that the tortuosity is independent on molecular size.
@@
 It can be observed that the upper right row displays a discrepancy, which likely due to inadequate regularization parameters.
-Furthermore, we can see that for $\alpha=1.0e-2$ there is a clear discrepancy in the diffusion coefficents compared to other values $\alpha$.
+Furthermore, we can see that for $\alpha=1.0e-2$ there is a clear discrepancy in the diffusion coefficients compared to other values $\alpha$.
 This prompt the exclusion of the corresponding values, which gives an average computed values $ 0.65 \mathrm{mm\sp{2}/h}$ and  $ 0.8 \mathrm{mm\sp{2}/h}$ in respectively grey and white matter.
-Scaled to $\mathrm{mm\sp{2}/s}$ gives $1.8e-4\mathrm{mm\sp{2}/s}$ and $2.22e-4 \mathrm{mm\sp{2}/s}$.
+Scaled to $\mathrm{mm\sp{2}/s}$ gives the corresponding values $1.8e-4\mathrm{mm\sp{2}/s}$ and $2.22e-4 \mathrm{mm\sp{2}/s}$.
 
 \subsection*{Compare high DTI values with computed}
-This gives a relative error of $42 \%$ in grey matter and $ 100 \%$ in white matter compared to the estimated values.
+This gives a difference of $42 \%$ in grey matter and $ 100 \%$ in white matter compared to the estimated values using DTI.
 
@@
 This suggests that the computed diffusion coefficients corresponds to these values.
-The ADC value in the high diffusivity regions are closer to  $1.4e-3 \mathrm{mm\sp{2}/s}$ {\color{red}adjust scale in ADC image ?}, which corresponds to estimated diffusion coefficent of value $1.5e-3 \mathrm{mm\sp{2}/s}$.
-This gives a relative error of $ 46 \%$ compared to the computed values.
+The ADC value in the high diffusivity regions are closer to  $1.4e-3 \mathrm{mm\sp{2}/s}$, which corresponds to estimated diffusion coefficient of value $1.5e-3 \mathrm{mm\sp{2}/s}$.
+This gives a difference of $ 46 \%$ compared to the computed values.
 
@@
 The computational model have 2 global controls for the diffusion coefficients, while it can be seen in  Fig.\ref{figuredti} that diffusion coefficients can be considered a spacial function.
-Although the implementation of spacial control parameters are possible, it would significantly increase the computational cost.
-
-It can also be taken into consideration to model the diffusion coefficients as a function in time, given the report of an increase clearance in rodents during sleeping [insert citation].
-This follows the assumption that the clearance is related to diffusion, which means an increase in diffusivity.
-Since the properties of the tracer molecule do not change, this would mean that the tortuosity decreased and followed by an increase in the ADC.
+The implementation control parameters for each dofs would significantly increase the computational cost.
+The option using region specific control parameters seems to be a better option, since the diffusivity appears to be regional.
+It can also be taken into consideration to model the diffusion coefficients as a function in time, given the report of an increase clearance in rodents during sleeping \cite{xie2013sleep}.
+This would indicate a time-dependent diffusivity, since the clearance in the brain is driven by diffusion.
+The time-dependency would correspond to a change in tortuosity, since properties of the tracer molecule do not change.
 
@@
 
-The hypothesis of the glymphatic system [insert citation] states that the waste is cleared through the veins in the cerebral.
-This gives the tracer an additional pathway that is not considered in the computational.
-The additional pathway can be modeled as a drainage, which can be included in the model as a sink source.
-This sink term can be added to the model as a control.
+The hypothesis of the glymphatic system \cite{iliff2012paravascular} states that the waste is cleared through the veins in the parenchyma.
+This gives the tracer additional pathways that is not considered in the computational model.
+These additional pathways can be modeled as a drainage, which can be included as a control source term.
 

### 2018-10-22 tex/paper.tex
update

@@
 These additional pathways can be modeled as a drainage, which can be included as a control source term.
+
+Previous studies~\cite{holter2017interstitial, smith2017glymphatic} suggest that diffusion dominates in the interstitium. Furthermore, 
+~\cite{asgari2016glymphatic, brynjfm, diem?} have found that dissipation in the paravascular spaces adds less than a factor two
+to diffusion for solute transportation. If we take into account then that the vasculature occupy 3-5\% of the volume
+of the brain and the paravascular space presumably occupy less space, then the factor 30\% (?) that we find here 
+seems significant and it is difficult to explain or ignore.
 

### 2018-10-22 tex/paper.tex
update
more text

@@
 \includegraphics[width=0.70\textwidth]{T1function.png} 
-\caption{Show the  function defined in \eqref{scaledmagnetization}. }
+\caption{Show the  function defined in \eqref{scaledmagnetization} with the white region indicating $T_1$ values for white matter,the grey region indicating $T_1$ values for grey matter,the blue region indicating $T_1$ values for CSF.
+}
 \label{figuredti} 
@@
 \end{equation}
-In the case that the minimization algorithm fails to converge within 1000 iteration will be indicated by a hyphen in Table~\ref{TAB::timesteps} Table~\ref{TAB::double}} and Table~\ref{Tab::Noise0.3}
+In the case that the minimization algorithm fails to converge within 1000 iteration will be indicated by a hyphen in Table~\ref{TAB::timesteps}, Table~\ref{TAB::double} and Table~\ref{Tab::Noise0.3}
 
@@
 
-The convergence of the objective functional $F$ is influenced by the values of the regularization parameters $\alpha$ and $\beta$.
+The convergence of the minimization is influenced by the values of the regularization parameters $\alpha$ and $\beta$.
 Therefore the convergence was examined by a systematic study of the reconstruction of the manufactured solution with respect to a wide range of regularization parameters.
@@
 In Tabel~\ref{Tab::Noise0.03}, we can see that a noise amplitude of 0.03, (10$\%$ of maximum initial condition) had negligible effect on the relative error.
-However, in Tabel~\ref{Tab::Noise0.3} the noise amplitude was increased to 0.3 (100$\%$ of maximum initial condition) and it is observed that for  $\alpha \leq 1.0e-4$  and $\beta \leq 1.0e-4$ the optimization failed to converge before reaching maximum iteration of 1000 steps.
-Furthermore, the relative boundary error $||g||\sp{rel}_{L\sp{2}(\Omega_1)}$ is larger for lower values of $\beta$.
+Then in Tabel~\ref{Tab::Noise0.3} the noise amplitude was increased to 0.3 (100$\%$ of maximum initial condition), which gave a visible effect.
+The noise addition caused the number of iteration to increase, and in combination with more timesteps caused the optimization not to convergence for $\beta < 1.0$.
+Furthermore, the relative boundary error $||g||\sp{rel}_{L\sp{2}(\Omega_1)}$ is significantly larger for $\alpha< 1.0e-2 $ and $\beta < 1.0e-2$.
 
@@
 The results are shown in Tab.\ref{Tab::Real-data}, and the observations after 12 and 48 hours were compared with the corresponding states in Figure~\ref{Fig::realdata}.
-From Table~\ref{Tab::Real-data},it can be observed that $D_w$ have a higher value for $\alpha =1.0e-2$.
+From Table~\ref{Tab::Real-data},it can be observed that $D_w$ have 24\% higher value on average for $\alpha =1.0e-2$.
+It can also be observed that the $D_g$ have a consistent increases with a decreasing $\beta$.
 
@@
 
-\subsection*{Compare high DTI values with computed}
+\subsection*{Compare high DTI values in white matter with computed}
 This gives a difference of $42 \%$ in grey matter and $ 100 \%$ in white matter compared to the estimated values using DTI.
@@
 \section{Discussion}
-
 The methodology presented here for identification of diffusion coefficients and boundary conditions with application to the glymphatic system appears to work quite 
-well for regularization parameters varying by orders of magnitude. It is particularly interesting to see that the procedure efficiently removes noise as demonstrated
-in the Figures \ref{12hourswithnoise} and \ref{24hourswithnoise} with noise levels of 30\% \kam{is this correctly stated}{\color{red} (0.3,-0.3) added to all values in range (0,g(t))}. 
+well for regularization parameters varying by orders of magnitude.
+The regularization parameters  $\alpha \in \lbrace 1.0e-6, 1.0e-2 \rbrace$, $\beta \in \lbrace 1.0e-2 , 1.0 \rbrace$ with the requirement $\alpha / \beta < 1.0e-2$ gave a relative error of
+4.1\% in grey matter and 3.6 \% in white matter. It is particularly interesting to see that the procedure efficiently removes noise as demonstrated
+in the Figures \ref{12hourswithnoise} and \ref{24hourswithnoise} with noise amplitude of 23\% of maximum value.
+However, the addition of noise required that $\beta = 1.0 $ to obtain consistent convergence.
 Crucial in our application is the interplay between the regularization term that regulates the smoothness of the boundary conditions as well as
@@
 in time and hence an oscillating boundary condition in time will minimized the integrated boundary condition at the cost of reducing the smoothness in time.
+The selected range of regularization parameters showed a decrease in error with more timesteps, rather than oscillation.
 
 While a more comprehensive study involving more patients would be required in order to assess whether the clearance here happens faster than diffusion (\kam{egentlig er
-vel dette det motsatte av clearance} a few remarks are in order. We find that the diffusion coefficients is XXX larger than what was found by the DTI modality.  
+vel dette det motsatte av clearance} a few remarks are in order. We find that the diffusion coefficients is 42-100\% larger than what was found by the DTI modality.  
 However, we have not yet been able to assessment the self-diffusion of water as well as the diffusivity of Gadovist used in this study in phantom models. As such 
@@
 
-\section{Conclusion}
-
-It can be concluded from the results that increasing the number of iterations gives rise to oscillations for poor regularizations parameters.
+%\section{Conclusion}
+
+%It can be concluded from the results that increasing the number of iterations gives rise to oscillations for poor regularizations parameters.
 
@@
 \bibliography{references}
+
+\clearpage
 

### 2018-10-22 tex/paper.tex
text

@@
 \includegraphics[width=0.95\textwidth]{Zoom-PatID-68.png} 
-\caption{Shows the percentage intensity increase from baseline at different observation times in the slice (marked red in the left panel) used in the subsequent analysis.The colorbar was restricted to the range $(0,100)$}
+\caption{Shows the percentage intensity increase from baseline at different observation times in the slice (marked red in the left panel) used in the subsequent analysis.The color bar was restricted to the range $(0,100)$}
 \label{fig2} 
@@
 
-The MRI data is obtained from a larger study, which invloves around 100 patients with similar MRI acquisitions.
-However, due to the clinical factor, some of the parameters involved are different.
-Thus a thorough analysis is needed to obtain a robust and accurate method.
+The MRI data was part of a larger study, which involves around 100 patients with the same MRI acquisitions.
+However, there are clinical differences in each patient, thus a thorough analysis is needed to obtain a robust and accurate method.
 
@@
 \alpha &= \cos ( \theta ) \\
-\beta  &= e\sp{- \sp{T_b}/_{T_1\sp{0}} } \\
-\delta &= e\sp{- \sp{T_a}/_{T_1\sp{0}} } \\
-\gamma &= e\sp{- \sp{T_w}/_{T_1\sp{0}} } \\
-\rho   &= e\sp{- \sp{TR}/_{T_1\sp{0}}}  \\
+\beta  &= e\sp{- \sp{T_b}/_{T_1\sp{c}} } \\
+\delta &= e\sp{- \sp{T_a}/_{T_1\sp{c}} } \\
+\gamma &= e\sp{- \sp{T_w}/_{T_1\sp{c}} } \\
+\rho   &= e\sp{- \sp{TR}/_{T_1\sp{c}}}  \\
 T_w    &= TR - T_a -T_b(m-1)       .\\
@@
 \includegraphics[width=0.70\textwidth]{T1function.png} 
-\caption{Show the  function defined in \eqref{scaledmagnetization} with the white region indicating $T_1$ values for white matter,the grey region indicating $T_1$ values for grey matter,the blue region indicating $T_1$ values for CSF.
+\caption{Show the  function defined in \eqref{scaledmagnetization} where the white region indicates $T_1$ values for white matter,the grey region indicates $T_1$ values for grey matter,the blue region indicates $T_1$ values for CSF.
 }
@@
 The diffusivity of the Gadovist (600 Da \cite{MGadobutrol}) was estimated to be similar to the diffusion coefficient of Gd-DPTA (550 Da \cite{MGgDPTA}).
-This due to the fact that both molecules have similar mass, and based Stoke-Einstein equation should have similar diffusion coefficients.
-The free diffusion coefficient for Gd-DPTA was estimated in \cite{GdDPTA-DIFFUSION} to be $3.8e-4\mathrm{mm\sp{2}/s}$.
+This due to the fact that both molecules have similar mass, and based on Stoke-Einstein equation should have similar diffusion coefficients.
+The free diffusion coefficient for Gd-DPTA was estimated in \citet{GdDPTA-DIFFUSION} to be $3.8e-4\mathrm{mm\sp{2}/s}$.
 The fractional anisotropy is defined as 
@@
 Then the use of T2 weighted MRI \cite{eidevalnes} was used to segment the CSF compartment surrounding the cerebral and the lateral ventricles.
-CGAL \cite{cgal:rty-m3-18b} was used to combine the polyhedral surfaces and to construed the mesh.
+CGAL \cite{cgal:rty-m3-18b} was used to combine the polyhedral surfaces and to construct the mesh.
 The computational requirement for the resulting mesh was significant, therefore two submesh was also constructed, see Fig.\ref{Fig::Mesh}.
@@
 The module dolfin adjoint ~\cite{farrell2013automated} \kam{correct ref?}  was used to solve the PDE constrained optimization problem with the L-BFGS-B algorithm in the python module scipy \cite{LBFGSB1, LBFGSB2}.
-
 The convergence criteria for the minimization was set so that
@@
 
-The observations $u_{obs}$ have a fixed time-points $t_i$, these time-points may not overlap with the time discretization in the forward problem $t_j$.
+The observations $u_{obs}$ have a fixed time-points $t_i$, these time-points may not coincide  with the time discretization in the forward problem $t_j$.
 Therefore a linear interpolation of the current solution $u(t_j)$ and previous solution $u(t_{j-1})$ was used approximate the solution at time $t_i$.
@@
 The noise susceptibility was tested by adding a uniform distribution noise term to the observations.
-The noise term was constructed using the random library in numpy and adjusted so that noise range becomes $\lbrace -n_{amp} , n_{amp} \rbrace $, with $n_{amp}$ defined as noise amplitude.
-
-\subsection{Acknowledgement}
+The noise term was constructed using the random library in numpy and adjusted so that the noise range becomes $\lbrace -n_{amp} , n_{amp} \rbrace $, with $n_{amp}$ denoted as noise amplitude.
+
+\subsection{Acknowledgements}
 This work was performed on the Abel Cluster, owned by the University of Oslo and Uninett\textbackslash Sigma2, and operated by the Department for Research Computing at USIT,the University of Oslo IT-department.
@@
 \subsection{Verification in terms of the manufactured solution}
-
 Below we will discuss the parameter identification and its sensitivity with respect to regularization parameters, noise and time-resolution.
@@
 Thus finding the optimal number of time-steps can be essential for larger problems.
-The computation varied the regularization parameters with 20 and 40 timesteps.
+The computation used a width range the regularization parameters, ans the number of timesteps were selected to be 20 and 40.
 
@@
 In Figure \ref{boundarycontrol} we can see that more time-steps causes oscillations for $\alpha=1.0$, and each peak corresponds to a observation time.
-These oscillations are caused by $\alpha$, which tries minimize $g$ between observation times.
-
-It can be seen that more time-steps causes an increase number of iterations, but for some values the number of iterations decreases.
+These oscillations are caused by the value selection of $\alpha$, which tries minimize $g$ between observation times.
+
+%It can be seen that more time-steps causes an increase number of iterations, but for some values the number of iterations decreases.
 These values share that $\alpha $ is a magnitude 2 lower than $ \beta$,i.e $\alpha=1.0e-2$ and $\beta =1.0$.
@@
 In Tab.\ref{TAB::half}, the values $\alpha =1.0e-2$ and $\beta<1.0$ gives a surge in the relative error with more time-steps.
-This behavior is neither visible in Tab.\ref{TAB::timesteps} or Tab.\ref{TAB::double} given the same regularization parameters.
-It seems likely that this error is caused by oscillations, seen in Figure~\ref{boundarycontrol}.
-
-The observations acts as stabilization for the functional, which gives a broader range of adequate regularization parameters.
+This behavior is neither visible in Tab.\ref{TAB::timesteps} or in  Tab.\ref{TAB::double} for the same regularization parameters.
+The ratio observations per control indicates that the increase in relative error is due to oscillations, similar to those seen in Figure~\ref{boundarycontrol}.
+Thus the observations acts as stabilization for the functional, which gives a broader range of adequate regularization parameters.
 
@@
 Then the optimization was solved by varying the regularization parameters $\alpha$ and $\beta$.
-Figure~\ref{12hourswithnoise} and Figure~\ref{24hourswithnoise} show the reconstruction of the manufactured solution with
+Figure~\ref{12hourswithnoise} and Figure~\ref{24hourswithnoise} shows the reconstruction of the manufactured solution at
 different noise levels with $\alpha=0.0001$ and $\beta=1.0$. Clearly, the reconstruction shown in the lower rows is quite robust with respect to the various levels
@@
 Then in Tabel~\ref{Tab::Noise0.3} the noise amplitude was increased to 0.3 (100$\%$ of maximum initial condition), which gave a visible effect.
-The noise addition caused the number of iteration to increase, and in combination with more timesteps caused the optimization not to convergence for $\beta < 1.0$.
+The noise caused the number of iteration to increase, and with more timesteps caused the optimization not to convergence for $\beta < 1.0$.
 Furthermore, the relative boundary error $||g||\sp{rel}_{L\sp{2}(\Omega_1)}$ is significantly larger for $\alpha< 1.0e-2 $ and $\beta < 1.0e-2$.
@@
 This corresponds to a tortuosity of $1.85$ and $1.73$, given that the self-diffusivity of water has been estimated to be around $3.0e-3\mathrm{mm\sp{2}/s}$ at $37\sp{o}C$.
-Fhe reference value $3.8e-4 \mathrm{mm\sp{2}/s}$ for Gd-DPTA gives an estimate for the apparent diffusion coefficient in the grey and white matter to respectively be $ 1.26e-4\mathrm{mm\sp{2}/s}$ and $1.10e-4 \mathrm{mm\sp{2}/s}$.
+Then the reference value $3.8e-4 \mathrm{mm\sp{2}/s}$ for Gd-DPTA gives an estimate for the apparent diffusion coefficient in the grey and white matter to  be $ 1.26e-4\mathrm{mm\sp{2}/s}$ and $1.10e-4 \mathrm{mm\sp{2}/s}$ respectively.
 This estimation assumes that the tortuosity is independent on molecular size.
@@
 Furthermore, we can see that for $\alpha=1.0e-2$ there is a clear discrepancy in the diffusion coefficients compared to other values $\alpha$.
-This prompt the exclusion of the corresponding values, which gives an average computed values $ 0.65 \mathrm{mm\sp{2}/h}$ and  $ 0.8 \mathrm{mm\sp{2}/h}$ in respectively grey and white matter.
+This prompt the exclusion of these values, which gives an average computed values $ 0.65 \mathrm{mm\sp{2}/h}$ and  $ 0.8 \mathrm{mm\sp{2}/h}$ in grey and white matter.
 Scaled to $\mathrm{mm\sp{2}/s}$ gives the corresponding values $1.8e-4\mathrm{mm\sp{2}/s}$ and $2.22e-4 \mathrm{mm\sp{2}/s}$.
@@
 This suggests that the computed diffusion coefficients corresponds to these values.
-The ADC value in the high diffusivity regions are closer to  $1.4e-3 \mathrm{mm\sp{2}/s}$, which corresponds to estimated diffusion coefficient of value $1.5e-3 \mathrm{mm\sp{2}/s}$.
+The ADC value in the high diffusivity regions are approximately  $1.4e-3 \mathrm{mm\sp{2}/s}$, which corresponds to estimated diffusion coefficient of value $1.5e-3 \mathrm{mm\sp{2}/s}$.
 This gives a difference of $ 46 \%$ compared to the computed values.
@@
 Therefore  observation of tracer in regions with anisotropy can be considered a requirement for adding anisotropy to the model.
-The regions with high diffusivity in Figure~\ref{figuredti},  have significant amount of diffusivity as seen in Figure~\ref{Fig::realdata}
-
-The computational model have 2 global controls for the diffusion coefficients, while it can be seen in  Fig.\ref{figuredti} that diffusion coefficients can be considered a spacial function.
-The implementation control parameters for each dofs would significantly increase the computational cost.
+
+The computational model uses 2 global controls for the diffusion coefficients, while it can be seen in  Fig.\ref{figuredti} that diffusion coefficients can be considered a spacial function.
+The implementation control parameters for each degree of freedom, would significantly increase the computational cost.
 The option using region specific control parameters seems to be a better option, since the diffusivity appears to be regional.

### 2018-10-23 tex/paper.tex
update

@@
 \newcommand{\kam}[1]{\textcolor{blue}{#1}}
+\newcommand{\fixme}[1]{\textcolor{orange}{#1}}
 
@@
 In 2011,~\citet{iliff2012paravascular} discovered a novel system within our brain's metabolism system, which changed our understanding of the brain. 
-The system involves a new pathway, called the paravascular pathway as it runs in parallel with vasculature system in a surrounding compartment.
+The system involves a new pathway, called the paravascular pathway as it runs in parallel with the vasculature system in a surrounding compartment.
 The important novelty in the 2011 findings was that waste from the brain is cleared through the paravascular path, and that a malfunction of this system 
@@
 that this system is particularly active during sleep.
-These mentioned breakthroughs were all performed in mice. In 2018,  
-it was for the first time demonstrated the action of
-this system in humans, and that the action of the system differs
+These mentioned breakthroughs were all performed in mice. In 2018, the action of the glymphatic system was for the first time demonstrated in humans. Further, it was shown that this action differs
 between healthy controls and patients with dementia~\citet{ringstad2018brain}.
-However, the biomechanical mechanisms behind this is not well understood from a fluid mechanics perspective,
+However, the biomechanical mechanisms behind the glymphatic system is not well understood from a fluid mechanics perspective,
 and so far the modeling attempts have mostly failed~\citet{asgari2016glymphatic, holter2017interstitial, smith2017glymphatic}. 
 In particular the system seems to facilitate waste transport faster than  
-the diffusion, which since the pioneering works of \citet{sykova2008diffusion} 
-has been the prevailing paradigm. Here, we aim to investigate whether PDE constrained optimization can be used
-to assess the effective diffusion coefficient on long time-scales (hours or days).
+the diffusion \fixme{which diffusion?}, which since the pioneering works of \citet{sykova2008diffusion} 
+has been the prevailing paradigm.
 
@@
 In \cite{ringstad2018brain} brain-wide distribution of MRI-contrast was demonstrated during 24 hours after lumbar contrast injection.
-Brain-wide distribution by diffusion alone was deemed unlikely by the authors (some of which are co-authors).
+Brain-wide distribution by diffusion alone was deemed unlikely by the authors (some of which are co-authors of this paper).
 The argument was based on analytical considerations where it was calculated that 50\% contrast enrichment would occur after
@@
 a more rigorous modeling attempt is warranted. A complicating factor
-is however that the contrast in the surrounding CSF is heterogenous
+is however that the contrast in the surrounding cerebral spinal fluid (CSF) is heterogenous
 and changes significantly during the 24 hours of the investigations. 
 Furthermore, images were obtained only at a few time-points during the investigations in \cite{ringstad2018brain}.
-As such the sparseness i times prevent a direct computation of the diffusion coefficients.
-
-The pioneering works of Sykov{\'a} and Nicholson~\cite{sykova2008diffusion} demonstrated
+As such, the sparseness in time prevents a direct computation of the diffusion coefficients.
+
+The pioneering work of Sykov{\'a} and Nicholson~\cite{sykova2008diffusion} demonstrated
 that diffusion was a governing transport mechanism in the brain and estimated to be on the order
-of $1.0e-4 \mathrm{mm\sp{2}/s}$ for large molecules. This is confirmed with DTI where values of young and healthy are typically around $0.7e-3 \mathrm{mm\sp{2}/s}$ \cite{Helenius194}
-while values in dementia typically are XXX \kam{Geir vet du dette?}. Of course diffusion coefficient 
+of $1.0e-4 \mathrm{mm\sp{2}/s}$ for large molecules.
+This is confirmed with diffusion tensor imaging (DTI) where young and healthy subjects have typical diffusion values of around $0.7e-3 \mathrm{mm\sp{2}/s}$ \cite{Helenius194}
+while subjects with dementia typically have values of XXX \kam{Geir vet du dette?}. Of course diffusion coefficients, 
 measured by DTI at a time-scale of 7-30 minutes, may not be representative for the process on a
-longer time-scale, at least if the paravascular pathway plays an important role. The fact that the vasculature  occupy around 3\% of the brain volume 
-and the paravascular network is substatantially smaller potentially render it invisible at the short time-scales of a DTI investigation 
+longer time-scale, at least if the paravascular pathway plays an important role. The fact that the vasculature system occupies around 3\% of the brain volume 
+and the paravascular network is substantially smaller potentially renders it \fixme{what is it here?} invisible at the short time-scales of a DTI investigation 
 while it may still be effective on longer time scales.
@@
 for assessing the apparent diffusion process where
-the complex geometry of the brain is taken into account and time-scales of hours or days are taken into account. 
-The approach we will take is to solve a PDE constrained optimization problem 
-via adjoint methods where we have sparse observations on selected time-points, around 10 acquisitions during 24 hours. But through
+the complex geometry of the brain as well as time-scales of hours or days are taken into account.
+\fixme{In this paper, we aim to investigate whether we can assess the effective diffusion coefficient on long time-scales (hours or days), by fitting a diffusion model to magnetic resonance imaging (MRI) data.}
+Our approach is to solve an optimization problem constrained by a partial differential equation (PDE) using the adjoint method where we have sparse observations on selected time-points, around 10 acquisitions during 24 hours, but through
 the complete domain. Hence, the challenges faced from a mathematical point of view 
@@
 the sparse observations through the time domain.  As such we need to assess the sensitivity of
-the approach with respect important parameters such as to regularization parameters, noise levels and 
+the approach with respect to important parameters such as the regularization parameters, noise levels and 
 time resolution to determine whether this approach is a viable method
@@
 
-Section 2.1-2.3 describes the details of the imaging relevant for this study. More details can however be
-found in e.g. \cite{ringstad2018brain}. Section 2.4-2.5 describe the solution of PDE constrained optimization problems and
+Sections 2.1-2.3 describe the details of the imaging relevant for this study. More details can however be
+found in e.g. \cite{ringstad2018brain}. Sections 2.4-2.5 describe the solution of PDE constrained optimization problems and
 its implementation in FEniCS. The exposition is, however, brief and we refer to XXX for more details.
@@
 \includegraphics[width=0.95\textwidth]{PatID-68-new-100.png} 
-\caption{Shows the percentage intensity increase from baseline at different observation times. The colorbar was restricted to the range $(0,100)$ }
+\caption{Shows the percentage intensity increase from baseline at different observation times. The colorbar was restricted to the range $(0,100)$.}
 \label{fig1} 
@@
 \includegraphics[width=0.95\textwidth]{Zoom-PatID-68.png} 
-\caption{Shows the percentage intensity increase from baseline at different observation times in the slice (marked red in the left panel) used in the subsequent analysis.The color bar was restricted to the range $(0,100)$}
+\caption{Shows the percentage intensity increase from baseline at different observation times in the slice (marked red in the left panel) used in the subsequent analysis.
+The color bar was restricted to the range $(0,100)$.
+}
 \label{fig2} 
@@
 Our data (not all shown) consist of a total of 10 MRI observations, including a baseline MRI taken before tracer was injected.
-The observation points are distributed with 5 observations within 1-2 hours after injection, a single observation in the timeframes 2-4 hours, 6-9 hours, 24 hours and 48 hours.
+The observation points are distributed over 5 observations within 1-2 hours after injection, a single observation in the timeframes 2-4 hours, 6-9 hours, 24 hours and 48 hours.
 Figure~\ref{fig2} shows the region selected for our computations. 
@@
 We remark that we use a notation common in medical literature and here two letter symbols are common.
-Hence, below we will use two letter symbols such as $TE$ and $TR$ to keep the notation consistent the presentation in \cite{GOWLAND, MPRAGE}.
+Hence, below we will use two letter symbols such as $TE$ and $TR$ to keep the notation consistent with the presentation in \cite{GOWLAND, MPRAGE}.
 The tracer concentration $c$ causes the longitudinal(spin-lattice) relaxation time $T_{1}$ to shorten with the following relation
@@
 \end{equation}
-The superscripts indicating with contrast $T_{1}\sp{c}$ and without contrast $T_{1}\sp{0}$ and $r_1$ as the relaxivity constant for the MRI tracer in a medium. 
+The superscripts indicate relaxation time with contrast $T_{1}\sp{c}$ and without contrast $T_{1}\sp{0}$, and $r_1$ is the relaxivity constant for the MRI tracer in a medium. 
 The tracer observations were collected using a MRI sequence known as  Magnetization Prepared Rapid Acquisition Gradient Echo (MPRAGE) with an inversion prepared magnetization.
@@
 \end{equation}
-Here $T_b$ is known as the echo spacing, $T_a$ is the inversion time, $T_w$ the time delay, $TR$ as the repetition time, $m$ is the number of echo spacings and $T1$ is the longitudinal(spin-lattice) relaxation time for a given medium.
+Here $T_b$ is known as the echo spacing, $T_a$ is the inversion time, $T_w$ the time delay, $TR$ as the repetition time, $m$ is the number of echo spacings and $T1$ \fixme{Should this be subscripted?} is the longitudinal(spin-lattice) relaxation time for a given medium.
 The $M_0$ is a calibration constant of the magnetization.
 The center echo denoted as $n=m/2$ will be the signal that we will consider when estimating MRI tracer.
-Given Eq.\ref{EQ::SI} we have that relative intensity increase can be written as
-\begin{equation}
-\frac{S\sp{c}}{S\sp{0}} = \frac{ M_{n}\sp{c} \sin (\theta)}{ M_{n}\sp{0} \sin (\theta) } ,
+Given Eq.\ref{EQ::SI} we have that the relative intensity increase can be written as
+\begin{equation}
+\frac{S\sp{c}}{S\sp{0}} = \frac{ M_{n}\sp{c} \sin (\theta)}{ M_{n}\sp{0} \sin (\theta) }.
 \end{equation}
@@
 \end{equation}
-which can be seen in Figure () . 
+which can be seen in Figure \ref{figuredti}. 
 This gives the following relation 
@@
 Tissue damage can be observed in the MRI due to a lower intensity in the white matter compared to healthy white matter tissue, thus damaged tissue have different $T_1$ relaxation time.
+\fixme{How is $r_1$ computed?}
 
@@
 \includegraphics[width=0.70\textwidth]{T1function.png} 
-\caption{Show the  function defined in \eqref{scaledmagnetization} where the white region indicates $T_1$ values for white matter,the grey region indicates $T_1$ values for grey matter,the blue region indicates $T_1$ values for CSF.
+\caption{Shows the  function defined in \eqref{scaledmagnetization} where the white region indicates $T_1$ values for white matter, the grey region indicates $T_1$ values for grey matter, the blue region indicates $T_1$ values for CSF.
 }
@@
 \subsection{Diffusion tensor imaging}
-In addition to the T1 and T2 weighted sequences described above we have also obtained diffusion tensor imaging (DTI) to assess the apparent diffusion 
-coefficients on short time-scales. Images are shown in Figure~\ref{figuredti} where the larges diffusion coefficient (shown in 
+In addition to the T1 and T2 weighted sequences described above we have also obtained diffusion tensor imaging to assess the apparent diffusion 
+coefficients on short time-scales. Images are shown in Figure~\ref{figuredti} where the largest diffusion coefficient (shown in 
 red in the middle figure) is shown to be around $1.0e-3 mm^2/s$. We remark that we have not included possible anisotropy, shown in 
-the right-most image in Figure~\ref{figuredti} and that these images shows the apparent diffusion coefficient for free water molecules (18 Da).      
+the right-most image in Figure~\ref{figuredti} and that these images show the apparent diffusion coefficient for free water molecules (18 Da).      
 The diffusivity of the Gadovist (600 Da \cite{MGadobutrol}) was estimated to be similar to the diffusion coefficient of Gd-DPTA (550 Da \cite{MGgDPTA}).
-This due to the fact that both molecules have similar mass, and based on Stoke-Einstein equation should have similar diffusion coefficients.
+This is due to the fact that both molecules have similar mass, and based on Stoke-Einstein equation should have similar diffusion coefficients.
 The free diffusion coefficient for Gd-DPTA was estimated in \citet{GdDPTA-DIFFUSION} to be $3.8e-4\mathrm{mm\sp{2}/s}$.
@@
 \begin{equation}
-\min_{D,g} F = \quad \sum\limits_i\sp{n} \int\limits_{\Omega} |u(t_i) - u_{obs}(t_i)|\sp{2} \mathrm{d}\Omega + \frac{\alpha}{2} \int\limits_{0}\sp{T} || g ||\sp{2}_{L\sp{2}(\partial\Omega)} \mathrm{d}t + \frac{\beta}{2} \int\limits_{0}\sp{T} || \dot{g} ||\sp{2}_{L\sp{2}(\partial\Omega)}\mathrm{d}t
+\min_{D,g} \quad \sum\limits_{i=1}\sp{n} \int\limits_{\Omega} |u(t_i) - u_{obs}(t_i)|\sp{2} \mathrm{d}\Omega + \int\limits_{0}\sp{T} \int\limits_{\partial \Omega_1} \frac{\alpha}{2} | g |\sp{2} + \frac{\beta}{2} \left| \frac{\partial g}{\partial t} \right|\sp{2} \mathrm{d}\Omega \mathrm{d}t
 \label{EQ::objf}
@@
 \begin{aligned}
-\frac{\partial u}{\partial t} = \nabla \cdot  D_i \nabla u \qquad \text{in} \qquad \Omega \times \left\lbrace 0 , T \right)  \\
-u=g(t) \qquad \text{on} \qquad \partial\Omega  \times \left\lbrace 0 , T \right) 
+\frac{\partial u}{\partial t} &= \nabla \cdot  D \nabla u && \text{in} \qquad \Omega \times \left\lbrace 0 , T \right)  \\
+u&=g && \text{on} \qquad \partial\Omega_1  \times \left\lbrace 0 , T \right) 
 \end{aligned}
@@
 \end{equation}
-Here, $u$ is the contrast distribution, $D_i$ is the apparent diffusion 
-coefficient, and $g$ is the boundary condition. Furthermore,  
-the domain $\Omega$ contains three sub domains, each with a different diffusion coefficient.
-We denote the Cerebral Spinal fluid (CSF) domain as $\Omega_1$, the grey matter as $\Omega_2$ and the white matter as $\Omega_3$.
+Here, $u$ is the contrast distribution, $D$ is the apparent diffusion 
+coefficient, $g$ is the boundary condition, $\Omega$ is the domain, and $T$ is the final simulation time.
+\fixme{Should we use $c$ instead of $u$?} We assume that the domain $\Omega$ consists of three sub domains, each with a different diffusion coefficient.
+We denote the CSF domain as $\Omega_1$, the grey matter as $\Omega_2$ and the white matter as $\Omega_3$.
 The apparent
@@
 white matter but each region may have different values.  
+The Dirichlet boundary condition is only applied on the outer facing boundary of the CSF domain, $\partial \Omega_1$. Homogeneous Neumann conditions are applied on the remaining boundaries.
 The $\alpha$ and $\beta$ parameters are non-negative regularization parameters 
-and $u_{obs}$ are observations at certain time-points $t_i$.
+and $u_{obs}$ are the observations at time-points $t_i$.
 
 The mesh construction was patient-specific and used the MRI of a patient diagnosed with idiopathic normal pressure hydrocephalus (iNPH).
-The software Freesurfer was used in segmentation and creating the polyhedral surfaces of the white and grey matter.
-Then the use of T2 weighted MRI \cite{eidevalnes} was used to segment the CSF compartment surrounding the cerebral and the lateral ventricles.
+The software Freesurfer was used to segment and create the polyhedral surfaces of the white and grey matter.
+Then the T2 weighted MRI \cite{eidevalnes} was used to segment the CSF compartment surrounding the cerebral and the lateral ventricles.
 CGAL \cite{cgal:rty-m3-18b} was used to combine the polyhedral surfaces and to construct the mesh.
-The computational requirement for the resulting mesh was significant, therefore two submesh was also constructed, see Fig.\ref{Fig::Mesh}.
+The computational requirement for the resulting mesh was significant, therefore two submeshes was also constructed, see Fig.\ref{Fig::Mesh}.
 \begin{figure}
@@
 \includegraphics[scale=0.2]{mesh.png} 
-\caption{A) Shows the mesh created from the baseline MR image with 3 domains. B) Shows the mesh created from the baseline MR image with 2 domains.  }
+\caption{A) Shows the mesh created from the baseline MR image with 3 domains.
+B) Shows the mesh created from the baseline MR image with 2 domains.
+\fixme{Add explaination for which color corresponds to which domain}  }
 \label{Fig::Mesh}
 \end{figure}
-The 3 domain mesh in Fig.\ref{Fig::Mesh} A, consists of 244318 tetrahedral cells and 22057 vertices, while the 2 domain mesh Fig.\ref{Fig::Mesh} B consists of 335589 tetrahedral cells and 73002 vertices.
-The dimension of the mesh coordinates are $\mathrm{mm}$.
+The 3 domain mesh in Fig.\ref{Fig::Mesh} A, consists of 244318 tetrahedral cells and 22057 vertices, while the 2 domain mesh (without the CSF compartment) Fig.\ref{Fig::Mesh} B consists of 335589 tetrahedral cells and 73002 vertices.
+The dimension of the mesh coordinates are \fixme{missing value} $\mathrm{mm}$.
 
 \subsection{Manufactured Solution}
-In order to asses the robustness and accuracy of our strategy and test the dependency of the
-regularization parameters, we perform a test case with a
+In order to asses the robustness and accuracy of our strategy and test the dependency of the computed diffusion coefficients $D$ on the
+regularization parameters $\alpha$ and $\beta$, we perform a test case with a
 known solution.  
-The manufactured observations was obtained by forward computation of Eq.\ref{Eq::PDE} with the Dirichlet boundary condition defined as
-\begin{equation}
-g(t)_{\partial \Omega_1} = 0.3 +0.167t - 0.007t\sp{2} \qquad  0 \leq t \leq 24.
+The manufactured observations were obtained by forward computation of Eq.\ref{Eq::PDE} with the Dirichlet boundary condition defined as
+\begin{equation}
+g(t) = 0.3 +0.167t - 0.007t\sp{2} \qquad \text{ for } 0 \leq t \leq 24.
 \label{EQ::DIRI}
 \end{equation}
-The timestep was $dt = 0.02$, and the diffusion coefficients were selected to be 
-\begin{equation}
-D_{\Omega_1} = 1000 \quad , \quad D_{\Omega_2} = 4.0 \quad , \quad D_{\Omega_3} = 8.0 
+The timestep was $dt = 0.02$, and the diffusion coefficients were selected to be \fixme{describe discretisation in time and space}
+\begin{equation}
+D_{\Omega_1} = 1000.0, \quad D_{\Omega_2} = 4.0, \quad D_{\Omega_3} = 8.0 
 \end{equation}  
@@
 The diffusion coefficient in the CSF was chosen given [cite Bryne and Kent], and the initial condition was set to 0 everywhere.
-%and the initial condition was set to 1.0 in $\Omega_1$ and 0 elsewhere.
-The manufactured forward computation gave a total of 120 possible observation times.
+\fixme{Check consistency of notation for $D_{\Omega_3}$, for example in next section it was called $D_{CSF}$} %and the initial condition was set to 1.0 in $\Omega_1$ and 0 elsewhere.
+The manufactured forward computation gave a total of 120 possible observation times. \fixme{Should this be 1200? 24/0.02 = 1200}.
 
 \section{Implementation}
-The estimation of the tracer concentration was precomputed and used the parameters obtained from the T1 map, MPRAGE MRI protocol \cite{eidevalnes} and the value for $r_1$ found in \cite{pmid16230904}.
+The tracer concentration was estimated in a preprocessing step, using the parameters obtained from the T1 \fixme{should this be subscripted?
+Otherwise unclear.} map, MPRAGE MRI protocol \cite{eidevalnes} and the value for $r_1$ found in \cite{pmid16230904} \fixme{rewritten sentence, please check}.
 In the computation, the function Eq.\ref{scaledmagnetization} was computed for $ T_1\in \lbrace 200, 4000 \rbrace$ creating a lookup table.
@@
 
-The code used the FEniCS project (v.2017.2) to solve the PDE, using backwards Euler time discretization and first order continuous Galerkin finite elements.
-The linear problem was solved using GMRES, and the matrix was stored in the solver.
-The module dolfin adjoint ~\cite{farrell2013automated} \kam{correct ref?}  was used to solve the PDE constrained optimization problem with the L-BFGS-B algorithm in the python module scipy \cite{LBFGSB1, LBFGSB2}.
-The convergence criteria for the minimization was set so that
-\begin{equation}
-||x ||_{L\sp{\infty}} \leq \epsilon
-\end{equation} 
-with $\epsilon=1.0e-1$ and $x$ denoting the projected gradient.
-
-The observations $u_{obs}$ have a fixed time-points $t_i$, these time-points may not coincide  with the time discretization in the forward problem $t_j$.
-Therefore a linear interpolation of the current solution $u(t_j)$ and previous solution $u(t_{j-1})$ was used approximate the solution at time $t_i$.
-The linear interpolation was given as
+The solver for \eqref{Eq::PDE} was implemented using the FEniCS project (v.2017.2), using backwards Euler time discretization and first order continuous Galerkin finite elements in space.
+The resulting linear problems were solved using GMRES.
+The module dolfin-adjoint \cite{farrell2013automated, funke2013framework} was used to automatically derive and solve the adjoint problem, and to solve the PDE constrained optimization problem with the L-BFGS-B algorithm \cite{LBFGSB1, LBFGSB2}.
+The optimization was stopped when the $L^\infty$-norm of the projected gradient of the objective functional dropped below $1.0e-1$.
+
+The observations $u_{obs}$ have fixed time-points.
+However, these time-points may not coincide  with the time discretization in the forward problem $t_j$.
+Therefore, we linearly interpolated the computed solutions onto the observation time points using the formula
 \begin{equation}
 \label{observation:interpolation}
-u(t_i) \approx \frac{\Delta t}{dt} u(t_{j-1}) + \frac{dt - \Delta t }{dt} u(t_{j}), \quad t_i \in \lbrace t_{j-1}, t_j \rbrace
-\end{equation}
-with $\Delta t = t_j-t_i$ and $dt  = t_{j} - t_{j-1}$.
+u(t) \approx \frac{\Delta t}{dt} u(t_{j-1}) + \frac{dt - \Delta t }{dt} u(t_{j}), \quad t \in \lbrace t_{j-1}, t_j \rbrace
+\end{equation}
+with $\Delta t = t_j-t$ and $dt = t_j - t_{j-1}$.
 
 The implementation used the first observation as initial conditions of Eq.\ref{Eq::PDE}.
-Then for each time-step, the next observation was used as the initial value for boundary control $g$, which was imposed on the external boundary of the domain $\Omega_1$.
-In order to increase the convergence rate, $D_{CSF}$ was scaled so that $D_{CSF} = 100 D_{CSF}\sp{\star} $.
-The initial values of the diffusion coefficients in the optimization algorithm was $(D_{CSF}\sp{\star}, D_{GM}, D_{WM})=$  $(1, 1, 1)$.
-
-The noise susceptibility was tested by adding a uniform distribution noise term to the observations.
-The noise term was constructed using the random library in numpy and adjusted so that the noise range becomes $\lbrace -n_{amp} , n_{amp} \rbrace $, with $n_{amp}$ denoted as noise amplitude.
+Then for each time-step, the next observation was used as the initial value for boundary control $g$.
+In order to increase the convergence speed of the optimization, $D_{CSF}$ was scaled so that $D_{CSF} = 100 D_{CSF}\sp{\star} $.
+The initial values of the diffusion coefficients in the optimization algorithm were $(D_{CSF}\sp{\star}, D_{GM}, D_{WM})=$  $(1, 1, 1)$.
+\fixme{Different $D$ notation compare to previous sections}
+
+The noise susceptibility was tested by adding a uniform \fixme{pointwise?} distribution noise to the observations.
+The noise term was constructed using the random library in numpy and adjusted so that the noise range was $\lbrace -n_{amp} , n_{amp} \rbrace $, with $n_{amp}$ denoted as noise amplitude.
 
 \subsection{Acknowledgements}
-This work was performed on the Abel Cluster, owned by the University of Oslo and Uninett\textbackslash Sigma2, and operated by the Department for Research Computing at USIT,the University of Oslo IT-department.
+The computational experiments were performed on the Abel Cluster, owned by the University of Oslo and Uninett\textbackslash Sigma2, and operated by the Department for Research Computing at USIT,the University of Oslo IT-department.
 \url{http://www.hpc.uio.no/}
@@
 \subsection{Verification in terms of the manufactured solution}
-Below we will discuss the parameter identification and its sensitivity with respect to regularization parameters, noise and time-resolution.
-In presentation of the results, the relative error is defined as
-\begin{equation}
- X\sp{rel} = \frac{X_{found} -X_{true} }{ X_{true} }
-\end{equation}
-with $X$ as an arbitrary scalar control parameter. For the boundary parameter $g$, the relative error norm is defined as 
-\begin{equation}
-|| g ||\sp{rel}_{L\sp{2}(\Omega_1)} = \frac{ \sum\limits_t\sp{k}|| g_{found}(t) -g_{true}(t)||_{L(\Omega_1)} }{  \sum\limits_t\sp{k}||g_{true}(t)||_{L(\Omega_1)} }
-\end{equation}
-In the case that the minimization algorithm fails to converge within 1000 iteration will be indicated by a hyphen in Table~\ref{TAB::timesteps}, Table~\ref{TAB::double} and Table~\ref{Tab::Noise0.3}
+Below we will discuss the parameter identification and its sensitivity with respect to the regularization parameters, noise and time-resolution \fixme{of the forward model or observations?}.
+When presenting the results, we denote the relative error of the diffusion parameters as
+\begin{equation}
+ D_{\Omega_i}\sp{rel} = \frac{D_{\Omega_i}\sp{found} -D_{\Omega_i}\sp{true} }{D_{\Omega_i}\sp{true} }, \text{ for } i=1,2,3
+\end{equation}
+For the boundary parameter $g$, the relative error norm is defined as 
+\begin{equation}
+|| g ||\sp{rel} = \frac{ \sum\limits_{t_j} || g_{found}(t_j) -g_{true}(t_j)||_{L^2(\Omega_1)} }{  \sum\limits_{t_j}||g_{true}(t_j)||_{L^2(\Omega_1)} }
+\end{equation}
+The case when the minimization algorithm fails to converge within 1000 iteration will be indicated by a hyphen in Table~\ref{TAB::timesteps}, Table~\ref{TAB::double} and Table~\ref{Tab::Noise0.3}
 
@@
 
-The convergence of the minimization is influenced by the values of the regularization parameters $\alpha$ and $\beta$.
+The convergence as well as the result of the minimization is influenced by the values of the regularization parameters $\alpha$ and $\beta$.
 Therefore the convergence was examined by a systematic study of the reconstruction of the manufactured solution with respect to a wide range of regularization parameters.
@@
 
-Ideally, the approach should have a wide range of parameters in which the reconstruction algorithm yields very similar end-results although the convergence may vary substantially.
-The evaluation of different regularization parameters was done by solving the optimization with different values of $\alpha$ and $\beta$ and compare the controls with the manufactured solution.
-The observation times were selected with $t_i \in  \lbrace$ 2.4, 4.8, 7.2, 9.6, 12.0, 14.4, 16.8, 19.2, 21.6, 24.0 $\rbrace$, and the number of time-steps $k$ in the forward problem was set to $10$.
-
-The results shown in Tabel~\ref{Tab::1}, and we can see similar end-result for most regularization parameters.
-However, in the case of $ \alpha=1.0$ the relative error over 100\% higher then for other values of $\alpha$.
-Furthermore, it can also be seen in the table that for all $\beta=100.0$ there is about 70\% relative error for $D_{\Omega_1}$ and approximate 10\% error for $D_{\Omega_2}$ .
+Ideally, our approach should have a wide range of parameters in which the reconstruction algorithm yields very similar end-results although the convergence may vary substantially.
+The evaluation of different regularization parameters was done by solving the optimization with different values of $\alpha$ and $\beta$ and comparing the computed $D$ and $g$ values with the manufactured solution.
+The observation times were set to $\lbrace$ 2.4, 4.8, 7.2, 9.6, 12.0, 14.4, 16.8, 19.2, 21.6, 24.0 $\rbrace$, and the number of time-steps $k$ in the forward problem was set to $10$.
+
+The results are shown in Table~\ref{Tab::1}.
+We can see that the optimization computed similar end-result for most regularization parameters.
+More specifically, for $\alpha \leq 1e-2$ and $\beta \leq 1e-0$ the relative errors for all optimization parameters are below $5\%$.
+ However, in the case of $ \alpha=1.0$ the relative error is over 100\% higher then for other values of $\alpha$.
+Furthermore, for all $\beta=100.0$ there is about 70\% relative error for $D_{\Omega_1}$ and approximate 10\% error for $D_{\Omega_2}$ .
 
@@
 \label{convergence}
-\caption{Convergence of the diffusion coefficients, boundary conditions and functional with respect to different $\alpha$ and $\beta$ values. } 
+\caption{Convergence plots of the diffusion coefficients, boundary conditions and functional with respect to different $\alpha$ and $\beta$ values.
+\fixme{Font and figures are too small, and figure is not referenced.} }
 \label{convergence}
@@
 Thus finding the optimal number of time-steps can be essential for larger problems.
-The computation used a width range the regularization parameters, ans the number of timesteps were selected to be 20 and 40.
-
-The results are given in Tab.\ref{TAB::timesteps}, and it can be seen for all $\alpha=1.0$ that the relative error becomes bigger with more time-steps.
+The computation used a wide range the regularization parameters, and the number of timesteps were selected to be 20 and 40.
+
+The results are given in Table~\ref{TAB::timesteps}.
+It can be seen for all $\alpha=1.0$ that the relative error becomes bigger with more time-steps.
 This behavior can also be seen for $\alpha=1.0e-2$ and $\beta < 1.0e-2$, which implies an interaction between the regularization parameters.
@@
 The dependency on observations is relevant, since the number of observations of the MRI data is limited.
-This was investigated by changing the number of observations, and examine the results.
+This dependency was investigated by changing the number of observations, and by examining the results.
 The number of observation were chosen to be 5 and 20, and the observation times were evenly spaced.
 
-The results are shown in Tab.\ref{TAB::double} and Tab.\ref{TAB::half}.
-In Tab.\ref{TAB::half}, the values $\alpha =1.0e-2$ and $\beta<1.0$ gives a surge in the relative error with more time-steps.
+The results for 5 observations is shown in Table~\ref{TAB::half} and for 20 observations is shown in Table~\ref{TAB::double}.
+In Table~\ref{TAB::half}, the values $\alpha =1.0e-2$ and $\beta<1.0$ gives a surge in the relative error with more time-steps.
 This behavior is neither visible in Tab.\ref{TAB::timesteps} or in  Tab.\ref{TAB::double} for the same regularization parameters.
@@
 The right panel shows the average boundary value $g$ for different regularization parameter with $k=40$.
-}
+\fixme{Increase font size.} }
 \label{boundarycontrol}
@@
 The MRI data contains noise, hence an investigation to the noise susceptibility is needed.
-This was done by adding uniform noise in the range $\lbrace -n_{amp} , n_{amp} \rbrace $, with $n_{amp}$ defined as noise amplitude, to the manufactured observations.
+This was done by adding uniform \fixme{pointwise?} noise in the range $\lbrace -n_{amp} , n_{amp} \rbrace $, with $n_{amp}$ defined as noise amplitude, to the manufactured observations.
 Then the optimization was solved by varying the regularization parameters $\alpha$ and $\beta$.
-Figure~\ref{12hourswithnoise} and Figure~\ref{24hourswithnoise} shows the reconstruction of the manufactured solution at
+Figure~\ref{12hourswithnoise} and Figure~\ref{24hourswithnoise} show the reconstruction of the manufactured solution at
 different noise levels with $\alpha=0.0001$ and $\beta=1.0$. Clearly, the reconstruction shown in the lower rows is quite robust with respect to the various levels
@@
 
-In Tabel~\ref{Tab::Noise0.03}, we can see that a noise amplitude of 0.03, (10$\%$ of maximum initial condition) had negligible effect on the relative error.
-Then in Tabel~\ref{Tab::Noise0.3} the noise amplitude was increased to 0.3 (100$\%$ of maximum initial condition), which gave a visible effect.
+In Table~\ref{Tab::Noise0.03}, we can see that a noise amplitude of 0.03, (10$\%$ of maximum initial condition) had negligible effect on the relative errors \fixme{compared to what?
+Add reference to a table to compare with.}.
+Then in Table~\ref{Tab::Noise0.3} the noise amplitude was increased to 0.3 (100$\%$ of maximum initial condition), which gave a visible effect.
 The noise caused the number of iteration to increase, and with more timesteps caused the optimization not to convergence for $\beta < 1.0$.
@@
 Therefore the 2 domain mesh, shown in Fig.\ref{Fig::Mesh} was used in the computation.
-The boundary control was set to the external boundary of both domains, and the subscript in $D_w$ and $D_g$ denotes white and grey diffusion coefficients.
+The boundary control was set to the external boundary of both domains, and the subscript in $D_w$ and $D_g$ \fixme{check consistency of notation.} denotes white and grey diffusion coefficients.
 Furthermore, bounds were added to the L-BFGS-B algorithm to ensure non-negative boundary controls and the convergence criteria was adjusted to $\epsilon=6.0e-1$.
@@
 The results are shown in Tab.\ref{Tab::Real-data}, and the observations after 12 and 48 hours were compared with the corresponding states in Figure~\ref{Fig::realdata}.
-From Table~\ref{Tab::Real-data},it can be observed that $D_w$ have 24\% higher value on average for $\alpha =1.0e-2$.
+From Table~\ref{Tab::Real-data},it can be observed that $D_w$ has 24\% higher value on average for $\alpha =1.0e-2$.
 It can also be observed that the $D_g$ have a consistent increases with a decreasing $\beta$.
@@
 
-The median diffusion coefficient in the DTI was estimated to be $8.7e-4 \mathrm{mm\sp{2}/s}$ in white matter and $1.0e-3 \mathrm{mm\sp{2}/s}$ in grey matter.
+The median diffusion coefficient in the DTI was estimated to be \fixme{The spaces between minus sign should be removed in scientific notation of numbers.} $8.7e-4 \mathrm{mm\sp{2}/s}$ in white matter and $1.0e-3 \mathrm{mm\sp{2}/s}$ in grey matter.
 This corresponds to a tortuosity of $1.85$ and $1.73$, given that the self-diffusivity of water has been estimated to be around $3.0e-3\mathrm{mm\sp{2}/s}$ at $37\sp{o}C$.
@@
 \subsection*{Compare high DTI values in white matter with computed}
+\fixme{Can we remove this subsection header?}
 This gives a difference of $42 \%$ in grey matter and $ 100 \%$ in white matter compared to the estimated values using DTI.
@@
 \centering
-\caption{Shows the regularization parameters $\alpha$ and $\beta$, number of timesteps $k$ and number of observation $\tau$ with the resulting number of iterations and the relative error for the control parameters.
+\caption{Shows the regularization parameters $\alpha$ and $\beta$, number of timesteps $k$ \fixme{and number of observation $\tau$} with the resulting number of optimization iterations and the relative error for the control parameters.
 {\color{red} check pvd }.}
 \begin{tabular}{*{8}c}
-$\alpha$ & $\beta$ & k  & iter & $ D_{\Omega_1}\sp{rel}$ & $ D_{\Omega_2}\sp{rel} $ & $D_{\Omega_3}\sp{rel}$ & $||g||_{rel}$ \\
+$\alpha$ & $\beta$ & k  & iter & $ D_{\Omega_1}\sp{rel}$ & $ D_{\Omega_2}\sp{rel} $ & $D_{\Omega_3}\sp{rel}$ & $||g||^{rel}$ \\
 \hline 
@@
  1.0e+00 	 & 1.0e-06 	 & 10 & 133 	 & +1.603 & +0.223 & +0.089 & +0.119 \\ 
+ \hline
  1.0e-02 	 & 1.0e+02 	 & 10 & 186 	 & +0.649 & +0.111 & +0.036 & +0.033 \\ 
@@
  1.0e-02 	 & 1.0e-06 	 & 10 & 154 	 & -0.039 & +0.039 & +0.036 & +0.026 \\ 
+ \hline
  1.0e-04 	 & 1.0e+02 	 & 10 & 212 	 & +0.636 & +0.108 & +0.035 & +0.032 \\ 
@@
  1.0e-04 	 & 1.0e-06 	 & 10 & 142 	 & -0.047 & +0.037 & +0.036 & +0.026 \\ 
+ \hline
  1.0e-06 	 & 1.0e+02 	 & 10 & 203 	 & +0.636 & +0.108 & +0.035 & +0.032 \\ 

### 2018-10-23 tex/paper.tex
fixme corrections

@@
 \newcommand{\fixme}[1]{\textcolor{orange}{#1}}
-
+\newcommand{\lars}[1]{\textcolor{magenta}{#1}}
 \author{Lars Magnus Valnes, Sebastian K. Mitusch, Geir A. Ringstad, \\ 
@@
 In particular the system seems to facilitate waste transport faster than  
-the diffusion \fixme{which diffusion?}, which since the pioneering works of \citet{sykova2008diffusion} 
+the diffusion \lars{?} \fixme{which diffusion?}, which since the pioneering works of \citet{sykova2008diffusion} 
 has been the prevailing paradigm.
@@
 that diffusion was a governing transport mechanism in the brain and estimated to be on the order
-of $1.0e-4 \mathrm{mm\sp{2}/s}$ for large molecules.
-This is confirmed with diffusion tensor imaging (DTI) where young and healthy subjects have typical diffusion values of around $0.7e-3 \mathrm{mm\sp{2}/s}$ \cite{Helenius194}
+of $1.0\mathrm{e}{-4} \mathrm{mm\sp{2}/s}$ for large molecules.
+This is confirmed with diffusion tensor imaging (DTI) where young and healthy subjects have typical diffusion values in white matter around $0.7-0.9\mathrm{e}{-3} \mathrm{mm\sp{2}/s}$ \cite{Helenius194},
 while subjects with dementia typically have values of XXX \kam{Geir vet du dette?}. Of course diffusion coefficients, 
@@
 \end{equation}
-Here $T_b$ is known as the echo spacing, $T_a$ is the inversion time, $T_w$ the time delay, $TR$ as the repetition time, $m$ is the number of echo spacings and $T1$ \fixme{Should this be subscripted?} is the longitudinal(spin-lattice) relaxation time for a given medium.
+Here $T_b$ is known as the echo spacing, $T_a$ is the inversion time, $T_w$ the time delay, $TR$ as the repetition time, $m$ is the number of echo spacings and $T_1$ is the longitudinal(spin-lattice) relaxation time for a given medium.
 The $M_0$ is a calibration constant of the magnetization.
@@
 Tissue damage can be observed in the MRI due to a lower intensity in the white matter compared to healthy white matter tissue, thus damaged tissue have different $T_1$ relaxation time.
-\fixme{How is $r_1$ computed?}
+\lars{ The estimation of $r_1$ is done through experiments.}  \fixme{How is $r_1$ computed?}
 
@@
 
+\lars{ should we have a section about Image Acquisition?}
+
 \subsection{Diffusion tensor imaging}
@@
 coefficients on short time-scales. Images are shown in Figure~\ref{figuredti} where the largest diffusion coefficient (shown in 
-red in the middle figure) is shown to be around $1.0e-3 mm^2/s$. We remark that we have not included possible anisotropy, shown in 
+red in the middle figure) is shown to be around $1.0\mathrm{e}{-3} mm^2/s$. We remark that we have not included possible anisotropy, shown in 
 the right-most image in Figure~\ref{figuredti} and that these images show the apparent diffusion coefficient for free water molecules (18 Da).      
@@
 This is due to the fact that both molecules have similar mass, and based on Stoke-Einstein equation should have similar diffusion coefficients.
-The free diffusion coefficient for Gd-DPTA was estimated in \citet{GdDPTA-DIFFUSION} to be $3.8e-4\mathrm{mm\sp{2}/s}$.
+The free diffusion coefficient for Gd-DPTA was estimated in \citet{GdDPTA-DIFFUSION} to be $3.8\mathrm{e}{-4}\mathrm{mm\sp{2}/s}$.
 The fractional anisotropy is defined as 
@@
 \begin{equation}
-\min_{D,g} \quad \sum\limits_{i=1}\sp{n} \int\limits_{\Omega} |u(t_i) - u_{obs}(t_i)|\sp{2} \mathrm{d}\Omega + \int\limits_{0}\sp{T} \int\limits_{\partial \Omega_1} \frac{\alpha}{2} | g |\sp{2} + \frac{\beta}{2} \left| \frac{\partial g}{\partial t} \right|\sp{2} \mathrm{d}\Omega \mathrm{d}t
+\min_{D,g} \quad \sum\limits_{i=1}\sp{n} \int\limits_{\Omega} |u(t_i) - u_{obs}(t_i)|\sp{2} \mathrm{d}\Omega + \int\limits_{0}\sp{T} \int\limits_{\partial \Omega_1} \left( \frac{\alpha}{2} | g |\sp{2} + \frac{\beta}{2} \left| \frac{\partial g}{\partial t} \right|\sp{2} \right) \mathrm{d}\Omega \mathrm{d}t
 \label{EQ::objf}
@@
 coefficient, $g$ is the boundary condition, $\Omega$ is the domain, and $T$ is the final simulation time.
-\fixme{Should we use $c$ instead of $u$?} We assume that the domain $\Omega$ consists of three sub domains, each with a different diffusion coefficient.
+\lars{We use c in section 2.2 }\fixme{Should we use $c$ instead of $u$?} We assume that the domain $\Omega$ consists of three sub domains, each with a different diffusion coefficient.
 We denote the CSF domain as $\Omega_1$, the grey matter as $\Omega_2$ and the white matter as $\Omega_3$.
@@
 B) Shows the mesh created from the baseline MR image with 2 domains.
-\fixme{Add explaination for which color corresponds to which domain}  }
+The blue domain corresponds to $\Omega_1$, the purple domain corresponds to $\Omega_2$ and the white domain corresponds to $\Omega_3$ }
 \label{Fig::Mesh}
@@
 The 3 domain mesh in Fig.\ref{Fig::Mesh} A, consists of 244318 tetrahedral cells and 22057 vertices, while the 2 domain mesh (without the CSF compartment) Fig.\ref{Fig::Mesh} B consists of 335589 tetrahedral cells and 73002 vertices.
-The dimension of the mesh coordinates are \fixme{missing value} $\mathrm{mm}$.
+The mesh coordinates (X,Y,Z) are given in $\mathrm{mm}$ \lars{ with $X \in \lbrace -70.5,-18\rbrace, Y \in \lbrace -73.5,28.8  \rbrace ,Z \in \lbrace 16.6,60.7 \rbrace$ }.
 
@@
 \end{equation}
-The timestep was $dt = 0.02$, and the diffusion coefficients were selected to be \fixme{describe discretisation in time and space}
+The timestep was $dt = 0.2$, and the diffusion coefficients were selected to be \fixme{describe discretisation in time and space}\lars{ cell-radius ratio ? angle ?}
 \begin{equation}
@@
 The magnitude order for $D_{\Omega_1} $ and $D_{\Omega_2}$ were chosen to resemble diffusion coefficient for water in grey and white matter, but the relation between the coefficients were not preserved.
-The diffusion coefficient in the CSF was chosen given [cite Bryne and Kent], and the initial condition was set to 0 everywhere.
-\fixme{Check consistency of notation for $D_{\Omega_3}$, for example in next section it was called $D_{CSF}$} %and the initial condition was set to 1.0 in $\Omega_1$ and 0 elsewhere.
-The manufactured forward computation gave a total of 120 possible observation times. \fixme{Should this be 1200? 24/0.02 = 1200}.
+The diffusion coefficient in the CSF was chosen given \citet{Haga}, and the initial condition was set to 0 everywhere.
+%and the initial condition was set to 1.0 in $\Omega_1$ and 0 elsewhere.
+The manufactured forward computation gave a total of 120 possible observation times.
 
 \section{Implementation}
-The tracer concentration was estimated in a preprocessing step, using the parameters obtained from the T1 \fixme{should this be subscripted?
-Otherwise unclear.} map, MPRAGE MRI protocol \cite{eidevalnes} and the value for $r_1$ found in \cite{pmid16230904} \fixme{rewritten sentence, please check}.
+The tracer concentration was estimated in a preprocessing step, using the parameters obtained from the T1-map, MPRAGE MRI protocol \cite{eidevalnes} and the value for $r_1$ found in \cite{pmid16230904}.
 In the computation, the function Eq.\ref{scaledmagnetization} was computed for $ T_1\in \lbrace 200, 4000 \rbrace$ creating a lookup table.
@@
 The module dolfin-adjoint \cite{farrell2013automated, funke2013framework} was used to automatically derive and solve the adjoint problem, and to solve the PDE constrained optimization problem with the L-BFGS-B algorithm \cite{LBFGSB1, LBFGSB2}.
-The optimization was stopped when the $L^\infty$-norm of the projected gradient of the objective functional dropped below $1.0e-1$.
+The optimization was stopped when the $L^\infty$-norm of the projected gradient of the objective functional dropped below $1.0\mathrm{e}{-1}$.
 
@@
 Then for each time-step, the next observation was used as the initial value for boundary control $g$.
-In order to increase the convergence speed of the optimization, $D_{CSF}$ was scaled so that $D_{CSF} = 100 D_{CSF}\sp{\star} $.
-The initial values of the diffusion coefficients in the optimization algorithm were $(D_{CSF}\sp{\star}, D_{GM}, D_{WM})=$  $(1, 1, 1)$.
-\fixme{Different $D$ notation compare to previous sections}
-
-The noise susceptibility was tested by adding a uniform \fixme{pointwise?} distribution noise to the observations.
+In order to increase the convergence speed of the optimization, $D_{\Omega_1}$ was scaled so that $D_{\Omega_1} = 100 D_{\Omega_1}\sp{\star} $.
+The initial values of the diffusion coefficients in the optimization algorithm were $(D_{\Omega_1}\sp{\star}, D_{\Omega_2}, D_{\Omega_3})=$  $(1, 1, 1)$.
+
+The noise susceptibility was tested by pointwise adding a uniform distributed noise to the observations.
 The noise term was constructed using the random library in numpy and adjusted so that the noise range was $\lbrace -n_{amp} , n_{amp} \rbrace $, with $n_{amp}$ denoted as noise amplitude.
@@
 
-The results are shown in Table~\ref{Tab::1}.
+The results are shown in Table~\ref{Tab::1} and the convergence is shown in Figure~\ref{convergence}.
 We can see that the optimization computed similar end-result for most regularization parameters.
-More specifically, for $\alpha \leq 1e-2$ and $\beta \leq 1e-0$ the relative errors for all optimization parameters are below $5\%$.
- However, in the case of $ \alpha=1.0$ the relative error is over 100\% higher then for other values of $\alpha$.
+More specifically, for $\alpha \leq 1\mathrm{e}{-2}$ and $\beta \leq 1e-0$ the relative errors for all optimization parameters are below $5\%$.However, in the case of $ \alpha=1.0$ the relative error is over 100\% higher then for other values of $\alpha$.
 Furthermore, for all $\beta=100.0$ there is about 70\% relative error for $D_{\Omega_1}$ and approximate 10\% error for $D_{\Omega_2}$ .
@@
 \centering
-\includegraphics[scale=0.2]{Convergence0}  
-\includegraphics[scale=0.2]{Convergence1}  
-\includegraphics[scale=0.2]{Convergence2}  
-\includegraphics[scale=0.2]{Convergence3}  
-\includegraphics[scale=0.2]{Convergence4}  
+\includegraphics[scale=0.18]{Convergence-plot.png}   
 \label{convergence}
-\caption{Convergence plots of the diffusion coefficients, boundary conditions and functional with respect to different $\alpha$ and $\beta$ values.
-\fixme{Font and figures are too small, and figure is not referenced.} }
+\caption{Convergence plots of the diffusion coefficients, boundary conditions and functional with respect to different $\alpha$ and $\beta$ values. } 
 \label{convergence}
@@
 It can be seen for all $\alpha=1.0$ that the relative error becomes bigger with more time-steps.
-This behavior can also be seen for $\alpha=1.0e-2$ and $\beta < 1.0e-2$, which implies an interaction between the regularization parameters.
+This behavior can also be seen for $\alpha=1.0\mathrm{e}{-2}$ and $\beta < 1.0\mathrm{e}{-2}$, which implies an interaction between the regularization parameters.
 Therefore $g$ was investigated by plotting boundary points through time for different values of $\alpha$ and $\beta$, see Fig \ref{boundarycontrol}.
@@
 The results for 5 observations is shown in Table~\ref{TAB::half} and for 20 observations is shown in Table~\ref{TAB::double}.
-In Table~\ref{TAB::half}, the values $\alpha =1.0e-2$ and $\beta<1.0$ gives a surge in the relative error with more time-steps.
+In Table~\ref{TAB::half}, the values $\alpha =1.0\mathrm{e}{-2}$ and $\beta<1.0$ gives a surge in the relative error with more time-steps.
 This behavior is neither visible in Tab.\ref{TAB::timesteps} or in  Tab.\ref{TAB::double} for the same regularization parameters.
@@
 The right panel shows the average boundary value $g$ for different regularization parameter with $k=40$.
-\fixme{Increase font size.} }
+\lars{Er i gang} \fixme{Increase font size.} }
 \label{boundarycontrol}
@@
 The MRI data contains noise, hence an investigation to the noise susceptibility is needed.
-This was done by adding uniform \fixme{pointwise?} noise in the range $\lbrace -n_{amp} , n_{amp} \rbrace $, with $n_{amp}$ defined as noise amplitude, to the manufactured observations.
+This was done by pointwise adding uniform distributed noise in the range $\lbrace -n_{amp} , n_{amp} \rbrace $, with $n_{amp}$ defined as noise amplitude, to the manufactured observations.
 Then the optimization was solved by varying the regularization parameters $\alpha$ and $\beta$.
@@
 
-In Table~\ref{Tab::Noise0.03}, we can see that a noise amplitude of 0.03, (10$\%$ of maximum initial condition) had negligible effect on the relative errors \fixme{compared to what?
-Add reference to a table to compare with.}.
+In Table~\ref{Tab::Noise0.03}, we can see that a noise amplitude of 0.03, (10$\%$ of maximum initial condition) had negligible effect on the relative errors compared zero noise in Table~\ref{Tab::1} and Table~\ref{TAB::timesteps}.
 Then in Table~\ref{Tab::Noise0.3} the noise amplitude was increased to 0.3 (100$\%$ of maximum initial condition), which gave a visible effect.
 The noise caused the number of iteration to increase, and with more timesteps caused the optimization not to convergence for $\beta < 1.0$.
-Furthermore, the relative boundary error $||g||\sp{rel}_{L\sp{2}(\Omega_1)}$ is significantly larger for $\alpha< 1.0e-2 $ and $\beta < 1.0e-2$.
+Furthermore, the relative boundary error $||g||\sp{rel}_{L\sp{2}(\Omega_1)}$ is significantly larger for $\alpha< 1.0\mathrm{e}{-2} $ and $\beta < 1.0\mathrm{e}{-2}$.
 
@@
 Therefore the 2 domain mesh, shown in Fig.\ref{Fig::Mesh} was used in the computation.
-The boundary control was set to the external boundary of both domains, and the subscript in $D_w$ and $D_g$ \fixme{check consistency of notation.} denotes white and grey diffusion coefficients.
-Furthermore, bounds were added to the L-BFGS-B algorithm to ensure non-negative boundary controls and the convergence criteria was adjusted to $\epsilon=6.0e-1$.
+The boundary control was set to the external boundary of both domains, and the subscript in $D_w$ and $D_g$\fixme{check consistency of notation.}\lars{Kent what do you think ?
+easier to relate grey to g and white to w } denotes white and grey diffusion coefficients.
+Furthermore, bounds were added to the L-BFGS-B algorithm to ensure non-negative boundary controls and the convergence criteria was adjusted to $\epsilon=6.0\mathrm{e}{-1}$.
 The number of timesteps were selected to be $k=24$ and $k=48$, which gives $dt = 2 hour$ and $dt = 1 hour$.
@@
 The results are shown in Tab.\ref{Tab::Real-data}, and the observations after 12 and 48 hours were compared with the corresponding states in Figure~\ref{Fig::realdata}.
-From Table~\ref{Tab::Real-data},it can be observed that $D_w$ has 24\% higher value on average for $\alpha =1.0e-2$.
+From Table~\ref{Tab::Real-data},it can be observed that $D_w$ has 24\% higher value on average for $\alpha =1.0\mathrm{e}{-2}$.
 It can also be observed that the $D_g$ have a consistent increases with a decreasing $\beta$.
@@
 
-The median diffusion coefficient in the DTI was estimated to be \fixme{The spaces between minus sign should be removed in scientific notation of numbers.} $8.7e-4 \mathrm{mm\sp{2}/s}$ in white matter and $1.0e-3 \mathrm{mm\sp{2}/s}$ in grey matter.
-This corresponds to a tortuosity of $1.85$ and $1.73$, given that the self-diffusivity of water has been estimated to be around $3.0e-3\mathrm{mm\sp{2}/s}$ at $37\sp{o}C$.
-Then the reference value $3.8e-4 \mathrm{mm\sp{2}/s}$ for Gd-DPTA gives an estimate for the apparent diffusion coefficient in the grey and white matter to  be $ 1.26e-4\mathrm{mm\sp{2}/s}$ and $1.10e-4 \mathrm{mm\sp{2}/s}$ respectively.
+The median diffusion coefficient in the DTI was estimated to be $8.7\mathrm{e}{-4} \mathrm{mm\sp{2}/s}$ in white matter and $1.0\mathrm{e}{-3} \mathrm{mm\sp{2}/s}$ in grey matter.
+This corresponds to a tortuosity of $1.85$ and $1.73$, given that the self-diffusivity of water has been estimated to be around $3.0\mathrm{e}{-3}\mathrm{mm\sp{2}/s}$ at $37\sp{o}C$.
+Then the reference value $3.8\mathrm{e}{-4} \mathrm{mm\sp{2}/s}$ for Gd-DPTA gives an estimate for the apparent diffusion coefficient in the grey and white matter to  be $ 1.26\mathrm{e}{-4}\mathrm{mm\sp{2}/s}$ and $1.10\mathrm{e}{-4} \mathrm{mm\sp{2}/s}$ respectively.
 This estimation assumes that the tortuosity is independent on molecular size.
@@
 It can be observed that the upper right row displays a discrepancy, which likely due to inadequate regularization parameters.
-Furthermore, we can see that for $\alpha=1.0e-2$ there is a clear discrepancy in the diffusion coefficients compared to other values $\alpha$.
+Furthermore, we can see that for $\alpha=1.0\mathrm{e}{-2}$ there is a clear discrepancy in the diffusion coefficients compared to other values $\alpha$.
 This prompt the exclusion of these values, which gives an average computed values $ 0.65 \mathrm{mm\sp{2}/h}$ and  $ 0.8 \mathrm{mm\sp{2}/h}$ in grey and white matter.
-Scaled to $\mathrm{mm\sp{2}/s}$ gives the corresponding values $1.8e-4\mathrm{mm\sp{2}/s}$ and $2.22e-4 \mathrm{mm\sp{2}/s}$.
-
-\subsection*{Compare high DTI values in white matter with computed}
-\fixme{Can we remove this subsection header?}
-This gives a difference of $42 \%$ in grey matter and $ 100 \%$ in white matter compared to the estimated values using DTI.
+Scaled to $\mathrm{mm\sp{2}/s}$ gives the corresponding values $1.8\mathrm{e}{-4}\mathrm{mm\sp{2}/s}$ and $2.22\mathrm{e}{-4} \mathrm{mm\sp{2}/s}$.
+This gives a difference of 42\% in grey matter and $ 100 \%$ in white matter compared to the estimated values using DTI.
+
+%\subsection*{Compare high DTI values in white matter with computed}
+%\fixme{Can we remove this subsection header?}
 
@@
 This suggests that the computed diffusion coefficients corresponds to these values.
-The ADC value in the high diffusivity regions are approximately  $1.4e-3 \mathrm{mm\sp{2}/s}$, which corresponds to estimated diffusion coefficient of value $1.5e-3 \mathrm{mm\sp{2}/s}$.
+The ADC value in the high diffusivity regions are approximately  $1.4\mathrm{e}{-3} \mathrm{mm\sp{2}/s}$, which corresponds to estimated diffusion coefficient of value $1.5\mathrm{e}{-3} \mathrm{mm\sp{2}/s}$.
 This gives a difference of $ 46 \%$ compared to the computed values.
@@
 well for regularization parameters varying by orders of magnitude.
-The regularization parameters  $\alpha \in \lbrace 1.0e-6, 1.0e-2 \rbrace$, $\beta \in \lbrace 1.0e-2 , 1.0 \rbrace$ with the requirement $\alpha / \beta < 1.0e-2$ gave a relative error of
+The regularization parameters  $\alpha \in \lbrace 1.0e-6, 1.0\mathrm{e}{-2} \rbrace$, $\beta \in \lbrace 1.0\mathrm{e}{-2} , 1.0 \rbrace$ with the requirement $\alpha / \beta < 1.0\mathrm{e}{-2}$ gave a relative error of
 4.1\% in grey matter and 3.6 \% in white matter. It is particularly interesting to see that the procedure efficiently removes noise as demonstrated
@@
 Previous studies~\cite{holter2017interstitial, smith2017glymphatic} suggest that diffusion dominates in the interstitium. Furthermore, 
-~\cite{asgari2016glymphatic, brynjfm, diem?} have found that dissipation in the paravascular spaces adds less than a factor two
+~\cite{asgari2016glymphatic, brynjfm, Diem} have found that dissipation in the paravascular spaces adds less than a factor two
 to diffusion for solute transportation. If we take into account then that the vasculature occupy 3-5\% of the volume
@@
 \centering
-\caption{Shows the regularization parameters $\alpha$ and $\beta$, number of timesteps $k$ \fixme{and number of observation $\tau$} with the resulting number of optimization iterations and the relative error for the control parameters.
-{\color{red} check pvd }.}
+\caption{Shows the regularization parameters $\alpha$ and $\beta$, number of timesteps $k$   \fixme{and number of observation $t_i$} with the resulting number of optimization iterations and the relative error for the control parameters.\lars{The number of observation times were XX, constant for each table.} }
 \begin{tabular}{*{8}c}
@@
 \caption{ Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$, the resulting number of iterations, the relative error of the estimated diffusion coefficients and the relative error for $g$.
-{\color{red} check pvd }}
+}
 \begin{tabular}{*{8}c}

### 2018-10-24 tex/paper.tex
updates

@@
 that is responsible for waste clearance. 
-In 2011,~\citet{iliff2012paravascular} discovered a novel system within our brain's metabolism system, which changed our understanding of the brain. 
+In 2011,~\citet{iliff2012paravascular} discovered a novel system within our brain's metabolic system, which changed our understanding of the brain. 
 The system involves a new pathway, called the paravascular pathway as it runs in parallel with the vasculature system in a surrounding compartment.
@@
 These mentioned breakthroughs were all performed in mice. In 2018, the action of the glymphatic system was for the first time demonstrated in humans. Further, it was shown that this action differs
-between healthy controls and patients with dementia~\citet{ringstad2018brain}.
+between healthy controls and patients with dementia~\cite{ringstad2018brain}.
 However, the biomechanical mechanisms behind the glymphatic system is not well understood from a fluid mechanics perspective,
-and so far the modeling attempts have mostly failed~\citet{asgari2016glymphatic, holter2017interstitial, smith2017glymphatic}. 
+and so far the modeling attempts have mostly failed~\cite{asgari2016glymphatic, holter2017interstitial, smith2017glymphatic}. 
 In particular the system seems to facilitate waste transport faster than  
-the diffusion \lars{?} \fixme{which diffusion?}, which since the pioneering works of \citet{sykova2008diffusion} 
+the extracellular diffusion, which since the pioneering works of \citet{sykova2008diffusion} 
 has been the prevailing paradigm.
@@
 This is confirmed with diffusion tensor imaging (DTI) where young and healthy subjects have typical diffusion values in white matter around $0.7-0.9\mathrm{e}{-3} \mathrm{mm\sp{2}/s}$ \cite{Helenius194},
-while subjects with dementia typically have values of XXX \kam{Geir vet du dette?}. Of course diffusion coefficients, 
+while subjects with dementia typically have values of XXX \kam{Geir enig?}. Of course diffusion coefficients, 
 measured by DTI at a time-scale of 7-30 minutes, may not be representative for the process on a
 longer time-scale, at least if the paravascular pathway plays an important role. The fact that the vasculature system occupies around 3\% of the brain volume 
-and the paravascular network is substantially smaller potentially renders it \fixme{what is it here?} invisible at the short time-scales of a DTI investigation 
-while it may still be effective on longer time scales.
+and the paravascular network is substantially smaller potentially renders the paravascular transport  invisible at the short time-scales of a DTI acquisition while it may still be effective on longer time scales.
 
 Our purpose in this paper is to attempt a more rigorous methodology 
-for assessing the apparent diffusion process where
+for assessing the paravascular transport process where
 the complex geometry of the brain as well as time-scales of hours or days are taken into account.
-\fixme{In this paper, we aim to investigate whether we can assess the effective diffusion coefficient on long time-scales (hours or days), by fitting a diffusion model to magnetic resonance imaging (MRI) data.}
+That is, we aim to investigate whether we can assess an effective diffusion coefficient on long time-scales (hours or days), by fitting a diffusion model to magnetic resonance imaging (MRI) data.
+If the fit between observation and model is good and we identify diffusion coefficients that are
+in line with those predicted by DTI then paravascular transport can be ignored on the scale of our study. 
 Our approach is to solve an optimization problem constrained by a partial differential equation (PDE) using the adjoint method where we have sparse observations on selected time-points, around 10 acquisitions during 24 hours, but through
@@
 
-Sections 2.1-2.3 describe the details of the imaging relevant for this study. More details can however be
+Sections 2.1-2.3 briefly describe the details of the imaging relevant for this study. More details on the MRI protocols can be
 found in e.g. \cite{ringstad2018brain}. Sections 2.4-2.5 describe the solution of PDE constrained optimization problems and
@@
 \lars{We use c in section 2.2 }\fixme{Should we use $c$ instead of $u$?} We assume that the domain $\Omega$ consists of three sub domains, each with a different diffusion coefficient.
-We denote the CSF domain as $\Omega_1$, the grey matter as $\Omega_2$ and the white matter as $\Omega_3$.
+We denote the CSF (or subarachnoid) domain as $\Omega_1=\Omega_{CSF}$, the grey matter as $\Omega_{GM}$ and the white matter as $\Omega_{WM}$.
 The apparent
@@
 \includegraphics[scale=0.2]{mesh.png} 
-\caption{A) Shows the mesh created from the baseline MR image with 3 domains.
-B) Shows the mesh created from the baseline MR image with 2 domains.
-The blue domain corresponds to $\Omega_1$, the purple domain corresponds to $\Omega_2$ and the white domain corresponds to $\Omega_3$ }
+\caption{The leftmost image A) shows the mesh created from the baseline MR image with 3 domains, while the rightmost image  B) shows the mesh created from the baseline MR image with 2 domains.
+The blue domain corresponds to CSF domain, $\Omega_{CSF}$, the purple domain corresponds to grey matter,  $\Omega_{GM}$, and the white domain corresponds to white matter, $\Omega_{WM}$.
+}
 \label{Fig::Mesh}
@@
 The diffusion coefficient in the CSF was chosen given \citet{Haga}, and the initial condition was set to 0 everywhere.
-%and the initial condition was set to 1.0 in $\Omega_1$ and 0 elsewhere.
+\fixme{some more details}%and the initial condition was set to 1.0 in $\Omega_1$ and 0 elsewhere.
 The manufactured forward computation gave a total of 120 possible observation times.
@@
 \subsection{Verification in terms of the manufactured solution}
-Below we will discuss the parameter identification and its sensitivity with respect to the regularization parameters, noise and time-resolution \fixme{of the forward model or observations?}.
+Below we will discuss the parameter identification and its sensitivity with respect to the regularization parameters, noise, number of observations and time-resolution of the forward model.
 When presenting the results, we denote the relative error of the diffusion parameters as
@@
 Therefore the 2 domain mesh, shown in Fig.\ref{Fig::Mesh} was used in the computation.
-The boundary control was set to the external boundary of both domains, and the subscript in $D_w$ and $D_g$\fixme{check consistency of notation.}\lars{Kent what do you think ?
-easier to relate grey to g and white to w } denotes white and grey diffusion coefficients.
+The boundary control was set to the external boundary of both domains, and the subscript in $D_{GM}$ and $D_{WM}$ denotes grey and white matter diffusion coefficients.
 Furthermore, bounds were added to the L-BFGS-B algorithm to ensure non-negative boundary controls and the convergence criteria was adjusted to $\epsilon=6.0\mathrm{e}{-1}$.
@@
 
-While a more comprehensive study involving more patients would be required in order to assess whether the clearance here happens faster than diffusion (\kam{egentlig er
-vel dette det motsatte av clearance} a few remarks are in order. We find that the diffusion coefficients is 42-100\% larger than what was found by the DTI modality.  
+While a more comprehensive study involving more patients would be required in order to assess clearance in health and disease, a few remarks here are in order. 
+First of all, the process investigated here is the clearance of Gadovist from CSF into the interstitium which may differ from the clearance of metabolic waste 
+from the interstitium via the CSF. That said, 
+we find that the diffusion coefficients is 42-100\% larger than what was found by the DTI modality. As such, we predict that the paravascular system 
+plays a significant role.  
 However, we have not yet been able to assessment the self-diffusion of water as well as the diffusivity of Gadovist used in this study in phantom models. As such 
@@
 %
-\section{References}
-
-\bibliographystyle{amsplain}
+
+\bibliographystyle{plainnat}
 \bibliography{references}

### 2018-10-24 tex/paper.tex
update

@@
 The 3 domain mesh in Fig.\ref{Fig::Mesh} A, consists of 244318 tetrahedral cells and 22057 vertices, while the 2 domain mesh (without the CSF compartment) Fig.\ref{Fig::Mesh} B consists of 335589 tetrahedral cells and 73002 vertices.
-The mesh coordinates (X,Y,Z) are given in $\mathrm{mm}$ \lars{ with $X \in \lbrace -70.5,-18\rbrace, Y \in \lbrace -73.5,28.8  \rbrace ,Z \in \lbrace 16.6,60.7 \rbrace$ }.
+%The mesh coordinates (X,Y,Z) are given in $\mathrm{mm}$ \lars{ with $X \in \lbrace -70.5,-18\rbrace, Y \in \lbrace -73.5,28.8  \rbrace ,Z \in \lbrace 16.6,60.7 \rbrace$ }.
 
@@
 \end{equation}
-The timestep was $dt = 0.2$, and the diffusion coefficients were selected to be \fixme{describe discretisation in time and space}\lars{ cell-radius ratio ? angle ?}
+The timestep was $dt = 0.2$, and the diffusion coefficients were selected to be 
+%\fixme{describe discretisation in time and space}\lars{ cell-radius ratio ? angle ?}
 \begin{equation}
@@
 The noise term was constructed using the random library in numpy and adjusted so that the noise range was $\lbrace -n_{amp} , n_{amp} \rbrace $, with $n_{amp}$ denoted as noise amplitude.
-
-\subsection{Acknowledgements}
-The computational experiments were performed on the Abel Cluster, owned by the University of Oslo and Uninett\textbackslash Sigma2, and operated by the Department for Research Computing at USIT,the University of Oslo IT-department.
-\url{http://www.hpc.uio.no/}
 
@@
 %
+
+\subsection{Acknowledgements}
+The computational experiments were performed on the Abel Cluster, owned by the University of Oslo and Uninett\textbackslash Sigma2, and operated by the Department for Research Computing at USIT,the University of Oslo IT-department.
+\url{http://www.hpc.uio.no/}
 

### 2018-10-24 tex/paper.tex
added pde constrain opt ref
fix ref and comments

@@
 a more rigorous modeling attempt is warranted. A complicating factor
-is however that the contrast in the surrounding cerebral spinal fluid (CSF) is heterogenous
+is however that the contrast in the surrounding cerebral spinal fluid (CSF) is heterogeneous
 and changes significantly during the 24 hours of the investigations. 
@@
 of $1.0\mathrm{e}{-4} \mathrm{mm\sp{2}/s}$ for large molecules.
-This is confirmed with diffusion tensor imaging (DTI) where young and healthy subjects have typical diffusion values in white matter around $0.7-0.9\mathrm{e}{-3} \mathrm{mm\sp{2}/s}$ \cite{Helenius194},
-while subjects with dementia typically have values of XXX \kam{Geir enig?}. Of course diffusion coefficients, 
+This is confirmed with diffusion tensor imaging (DTI) where young and healthy subjects have typical diffusion values in white matter around $0.7-0.9\mathrm{e}{-3} \mathrm{mm\sp{2}/s}$ \citet{Helenius194},
+while subjects with dementia typically have higher value and variation \cite{goujon2018can} . Of course diffusion coefficients, 
 measured by DTI at a time-scale of 7-30 minutes, may not be representative for the process on a
-longer time-scale, at least if the paravascular pathway plays an important role. The fact that the vasculature system occupies around 3\% of the brain volume 
+longer time-scale, at least if the paravascular pathway plays an important role. The fact that the vascular system occupies around 3\% of the brain volume 
 and the paravascular network is substantially smaller potentially renders the paravascular transport  invisible at the short time-scales of a DTI acquisition while it may still be effective on longer time scales.
@@
 the complete domain. Hence, the challenges faced from a mathematical point of view 
-are that 1) the images are subject to noise, 2) resolution in space is limited to slightly less than (1 mm)$^3$ and 3)
+are that 1) the images are subject to noise, 2) resolution in space is limited to slightly less than (1 $\mathrm{mm}^3$ and 3)
 the sparse observations through the time domain.  As such we need to assess the sensitivity of
@@
 found in e.g. \cite{ringstad2018brain}. Sections 2.4-2.5 describe the solution of PDE constrained optimization problems and
-its implementation in FEniCS. The exposition is, however, brief and we refer to XXX for more details.
+its implementation in FEniCS. The exposition is, however, brief and we refer to e.g. \cite{hinze2008optimization} for more details.
 
@@
 The center echo denoted as $n=m/2$ will be the signal that we will consider when estimating MRI tracer.
-Given Eq.\ref{EQ::SI} we have that the relative intensity increase can be written as
+Given \eqref{EQ::SI} we have that the relative intensity increase can be written as
 \begin{equation}
@@
 and then estimate the concentration using \eqref{EQ::contrast}.
-The $T_{1}\sp{0}$ values were obtained by T1 mapping the brain using a MRI sequence known as MOLLI5(3)3 \cite{TAYLOR201667}.
+The $T_{1}\sp{0}$ values were obtained by T1-mapping the brain using a MRI sequence known as MOLLI5(3)3 \cite{TAYLOR201667}.
 This takes into account patients specific characteristic, such as tissue damage.
 Tissue damage can be observed in the MRI due to a lower intensity in the white matter compared to healthy white matter tissue, thus damaged tissue have different $T_1$ relaxation time.
-\lars{ The estimation of $r_1$ is done through experiments.}  \fixme{How is $r_1$ computed?}
+The tracer concentration was estimated in a preprocessing step, using the parameters obtained from the T1-map, MPRAGE MRI protocol \cite{eidevalnes} and the value for $r_1$ found in \cite{pmid16230904}.
+In the computation, the function \eqref{scaledmagnetization} was computed for $ T_1\in \lbrace 200, 4000 \rbrace$ creating a lookup table.
+The lookup table was utilized with the baseline intensity increase to estimate $T_1\sp{c}$, and then the concentration was computed using \eqref{EQ::contrast}.
 
@@
 }
-\label{figuredti} 
-\end{figure}
-
-\lars{ should we have a section about Image Acquisition?}
+\label{figureF} 
+\end{figure}
 
@@
 \subsection{Mathematical Model}
-In \cite{sykova2008diffusion}, it was shown that the macroscopic diffusion in the brain can be considered a hindered diffusion with an apparent diffusion coefficient.
+In \citet{sykova2008diffusion}, it was shown that the macroscopic diffusion in the brain can be considered a hindered diffusion with an apparent diffusion coefficient (ADC).
+The relation between the diffusion coefficients were defined as
+\begin{equation}
+ \lambda =  \sqrt {D/D_{ADC}}
+\label{tortuosity}
+\end{equation}
+with $\lambda$ denoted as the tortuosity.
 In order to estimate the apparent diffusion coefficient involved in the tracer transportation shown in Figure~\ref{fig1} we assume that the process can be modeled by a diffusion equation.
@@
 coefficient, $g$ is the boundary condition, $\Omega$ is the domain, and $T$ is the final simulation time.
-\lars{We use c in section 2.2 }\fixme{Should we use $c$ instead of $u$?} We assume that the domain $\Omega$ consists of three sub domains, each with a different diffusion coefficient.
-We denote the CSF (or subarachnoid) domain as $\Omega_1=\Omega_{CSF}$, the grey matter as $\Omega_{GM}$ and the white matter as $\Omega_{WM}$.
+We assume that the domain $\Omega$ consists of three sub domains, each with a different diffusion coefficient.
+We denote the CSF (subarachnoid and lateral ventricle) domain as $\Omega_1=\Omega_{CSF}$, the grey matter as $\Omega_{GM}$ and the white matter as $\Omega_{WM}$.
 The apparent
@@
 known solution.  
-The manufactured observations were obtained by forward computation of Eq.\ref{Eq::PDE} with the Dirichlet boundary condition defined as
+The manufactured observations were obtained by forward computation of \eqref{Eq::PDE} with the Dirichlet boundary condition defined as
 \begin{equation}
@@
 \end{equation}
-The timestep was $dt = 0.2$, and the diffusion coefficients were selected to be 
+The initial condition was set to 0 everywhere, the timestep was $dt = 0.2$, and the diffusion coefficients were selected to be 
 %\fixme{describe discretisation in time and space}\lars{ cell-radius ratio ? angle ?}
@@
 The magnitude order for $D_{\Omega_1} $ and $D_{\Omega_2}$ were chosen to resemble diffusion coefficient for water in grey and white matter, but the relation between the coefficients were not preserved.
-The diffusion coefficient in the CSF was chosen given \citet{Haga}, and the initial condition was set to 0 everywhere.
-\fixme{some more details}%and the initial condition was set to 1.0 in $\Omega_1$ and 0 elsewhere.
-The manufactured forward computation gave a total of 120 possible observation times.
+In \citet{Haga}, the drug concentration moved 1 cm per 20 seconds in the cervical region, thus $D_{\Omega_3}$  was set to 1000.
+The manufactured forward computation produced a total of 120 possible observation times.
 
 \section{Implementation}
-The tracer concentration was estimated in a preprocessing step, using the parameters obtained from the T1-map, MPRAGE MRI protocol \cite{eidevalnes} and the value for $r_1$ found in \cite{pmid16230904}.
-In the computation, the function Eq.\ref{scaledmagnetization} was computed for $ T_1\in \lbrace 200, 4000 \rbrace$ creating a lookup table.
-The lookup table was utilized with the baseline intensity increase to estimate $T_1\sp{c}$, and then the concentration was computed using Eq.\ref{EQ::contrast}.
-
 %In the acquired data, the MPRAGE had a high signal to noise ratio and the T1 map had low signal in the CSF.
@@
 
-The implementation used the first observation as initial conditions of Eq.\ref{Eq::PDE}.
+The implementation used the first observation as initial conditions of \eqref{Eq::PDE}.
 Then for each time-step, the next observation was used as the initial value for boundary control $g$.
@@
 \includegraphics[scale=0.18]{Convergence-plot.png}   
-\label{convergence}
 \caption{Convergence plots of the diffusion coefficients, boundary conditions and functional with respect to different $\alpha$ and $\beta$ values. } 
@@
 \centering
-\includegraphics[scale=0.2]{boundary_control.png}  
+\includegraphics[scale=0.21]{boundary_control.png}  
 \caption{ Displays plots over time for a selection of points at the boundary of $\Omega_1$ with different regularization parameters and number of timesteps $k$.
@@
 The right panel shows the average boundary value $g$ for different regularization parameter with $k=40$.
-\lars{Er i gang} \fixme{Increase font size.} }
+}
 \label{boundarycontrol}
@@
 Therefore the 2 domain mesh, shown in Fig.\ref{Fig::Mesh} was used in the computation.
-The boundary control was set to the external boundary of both domains, and the subscript in $D_{GM}$ and $D_{WM}$ denotes grey and white matter diffusion coefficients.
-Furthermore, bounds were added to the L-BFGS-B algorithm to ensure non-negative boundary controls and the convergence criteria was adjusted to $\epsilon=6.0\mathrm{e}{-1}$.
+The boundary control was set to the external boundary of both domains, and the subscript in $D_{\Omega_{GM}}$ and $D_{\Omega_{WM}}$ denotes grey and white matter diffusion coefficients.
+Furthermore, bounds were added to the L-BFGS-B algorithm to ensure non-negative boundary controls and the convergence criteria was adjusted so that the optimization was stopped when the $L^\infty$-norm of the projected gradient of the objective functional dropped below $6.0\mathrm{e}{-1}$.
 The number of timesteps were selected to be $k=24$ and $k=48$, which gives $dt = 2 hour$ and $dt = 1 hour$.
@@
 The results are shown in Tab.\ref{Tab::Real-data}, and the observations after 12 and 48 hours were compared with the corresponding states in Figure~\ref{Fig::realdata}.
-From Table~\ref{Tab::Real-data},it can be observed that $D_w$ has 24\% higher value on average for $\alpha =1.0\mathrm{e}{-2}$.
-It can also be observed that the $D_g$ have a consistent increases with a decreasing $\beta$.
+From Table~\ref{Tab::Real-data},it can be observed that $D_{\Omega_{WM}}$ has 24\% higher value on average for $\alpha =1.0\mathrm{e}{-2}$.
+It can also be observed that the $D_{\Omega_{GM}}$ have a consistent increases with a decreasing $\beta$.
 
@@
 plays a significant role.  
-However, we have not yet been able to assessment the self-diffusion of water as well as the diffusivity of Gadovist used in this study in phantom models. As such 
-the constants in equation XXX must be taken with caution. Furthermore,    
+However, we have not yet been able to assess the self-diffusion of water as well as the diffusivity of Gadovist used in this study with phantom models. As such 
+the values used with \eqref{tortuosity} must be taken with caution. Furthermore,    
 the computational model assumes isotropic diffusivity, but the anisotropy in the white matter is well documented, as shown by the FA in Fig\ref{figuredti}.
@@
 \centering
-\caption{Shows the regularization parameters $\alpha$ and $\beta$, number of timesteps $k$   \fixme{and number of observation $t_i$} with the resulting number of optimization iterations and the relative error for the control parameters.\lars{The number of observation times were XX, constant for each table.} }
+\caption{Shows the regularization parameters $\alpha$ and $\beta$, number of timesteps $k$ with the resulting number of optimization iterations and the relative error for the control parameters.
+The observations times were chosen $ t_i=[2.4, 4.8,$ 7.2, 9.6, 12.0, 14.4, $16.8, 19.2, 21.6, 24.0]$ }
 \begin{tabular}{*{8}c}
@@
  1.0e-06 	 & 1.0e-06 	 & 10 & 133 	 & -0.047 & +0.037 & +0.036 & +0.026 \\
-%  1.0e+00 	 & 1.0e+02 	 & 10 & 499 	 & +5.125 & +0.278 & +0.105 & +0.127 \\ 
-%  1.0e+00 	 & 1.0e+00 	 & 10 & 225 	 & +4.148 & +0.304 & +0.092 & +0.135 \\ 
-%%\rowcolor{red}  1.0e+00 	 & 1.0e-01 	 & 10 & 206 	 & +4.272 & +0.305 & +0.091 & +0.142 \\ 
-% 1.0e+00 	 & 1.0e-02 	 & 10 & 233 	 & +4.272 & +0.305 & +0.091 & +0.143 \\ 
-%%\rowcolor{red}  1.0e+00 	 & 1.0e-03 	 & 10 & 208 	 & +4.437 & +0.305 & +0.091 & +0.143 \\ 
-% 1.0e+00 	 & 1.0e-04 	 & 10 & 204 	 & +4.271 & +0.306 & +0.091 & +0.143 \\ 
-%%\rowcolor{red}  1.0e+00 	 & 1.0e-05 	 & 10 & 203 	 & +4.400 & +0.305 & +0.091 & +0.143 \\ 
-% 1.0e+00 	 & 1.0e-06 	 & 10 & 222 	 & +4.584 & +0.304 & +0.090 & +0.143 \\
-% 
-%% 1.0e-01 	 & 1.0e+00 	 & 10 & 207 	 & +0.127 & +0.093 & +0.041 & +0.027 \\ 
-% %1.0e-01 	 & 1.0e-01 	 & 10 & 196 	 & +0.121 & +0.093 & +0.041 & +0.046 \\ 
-%% 1.0e-01 	 & 1.0e-02 	 & 10 & 232 	 & +0.123 & +0.093 & +0.041 & +0.056 \\ 
-% %1.0e-01 	 & 1.0e-03 	 & 10 & 183 	 & +0.122 & +0.093 & +0.040 & +0.057 \\ 
-%% 1.0e-01 	 & 1.0e-04 	 & 10 & 212 	 & +0.122 & +0.093 & +0.040 & +0.057 \\ 
-% %1.0e-01 	 & 1.0e-05 	 & 10 & 168 	 & +0.122 & +0.093 & +0.041 & +0.057 \\
-%% 1.0e-01 	 & 1.0e-06 	 & 10 & 195 	 & +0.122 & +0.093 & +0.041 & +0.057 \\ 
-% 1.0e-02 	 & 1.0e+02 	 & 10 & 228 	 & +0.702 & +0.106 & +0.035 & +0.033 \\ 
-% 1.0e-02 	 & 1.0e+00 	 & 10 & 227 	 & +0.015 & +0.067 & +0.039 & +0.018 \\ 
-% %1.0e-02 	 & 1.0e-01 	 & 10 & 153 	 & +0.006 & +0.065 & +0.039 & +0.021 \\ 
-% 1.0e-02 	 & 1.0e-02 	 & 10 & 184 	 & +0.005 & +0.065 & +0.039 & +0.039 \\ 
-% %1.0e-02 	 & 1.0e-03 	 & 10 & 176 	 & +0.004 & +0.065 & +0.039 & +0.048 \\ 
-% 1.0e-02 	 & 1.0e-04 	 & 10 & 195 	 & +0.005 & +0.065 & +0.039 & +0.049 \\ 
-% %1.0e-02 	 & 1.0e-05 	 & 10 & 215 	 & +0.004 & +0.065 & +0.039 & +0.051 \\ 
-% 1.0e-02 	 & 1.0e-06 	 & 10 & 205 	 & +0.005 & +0.065 & +0.039 & +0.050 \\ 
-%
-% %1.0e-03 	 & 1.0e+00 	 & 10 & 179 	 & +0.004 & +0.064 & +0.039 & +0.019 \\ 
-% %1.0e-03 	 & 1.0e-01 	 & 10 & 221 	 & -0.005 & +0.063 & +0.039 & +0.018 \\ 
-% %1.0e-03 	 & 1.0e-02 	 & 10 & 89 	 & -0.007 & +0.063 & +0.039 & +0.026 \\ 
-% %1.0e-03 	 & 1.0e-03 	 & 10 & 77 	 & -0.005 & +0.062 & +0.039 & +0.027 \\ 
-% %1.0e-03 	 & 1.0e-04 	 & 10 & 100 	 & -0.006 & +0.062 & +0.039 & +0.027 \\ 
-% %1.0e-03 	 & 1.0e-05 	 & 10 & 105 	 & -0.006 & +0.062 & +0.039 & +0.027 \\ 
-% %1.0e-03 	 & 1.0e-06 	 & 10 & 123 	 & -0.007 & +0.062 & +0.039 & +0.028 \\ 
-%
-% 1.0e-04 	 & 1.0e+02 	 & 10 & 167 	 & +0.688 & +0.104 & +0.035 & +0.032 \\ 
-% 1.0e-04 	 & 1.0e+00 	 & 10 & 236 	 & +0.004 & +0.063 & +0.039 & +0.019 \\ 
-% %1.0e-04 	 & 1.0e-01 	 & 10 & 195 	 & -0.006 & +0.062 & +0.039 & +0.018 \\ 
-% 1.0e-04 	 & 1.0e-02 	 & 10 & 152 	 & -0.006 & +0.062 & +0.039 & +0.022 \\ 
-% %1.0e-04 	 & 1.0e-03 	 & 10 & 119 	 & -0.008 & +0.062 & +0.039 & +0.026 \\ 
-% 1.0e-04 	 & 1.0e-04 	 & 10 & 106 	 & -0.007 & +0.062 & +0.039 & +0.026 \\ 
-% %1.0e-04 	 & 1.0e-05 	 & 10 & 109 	 & -0.007 & +0.062 & +0.039 & +0.026 \\ 
-% 1.0e-04 	 & 1.0e-06 	 & 10 & 99 	 & -0.008 & +0.062 & +0.039 & +0.026 \\
-% 
-% %1.0e-05 	 & 1.0e+00 	 & 10 & 139 	 & +0.004 & +0.063 & +0.039 & +0.019 \\ 
-% %1.0e-05 	 & 1.0e-01 	 & 10 & 170 	 & -0.006 & +0.062 & +0.039 & +0.018 \\ 
-% %1.0e-05 	 & 1.0e-02 	 & 10 & 182 	 & -0.007 & +0.062 & +0.039 & +0.020 \\ 
-% %1.0e-05 	 & 1.0e-03 	 & 10 & 70 	 & -0.007 & +0.062 & +0.039 & +0.026 \\ 
-% %1.0e-05 	 & 1.0e-04 	 & 10 & 77 	 & -0.007 & +0.062 & +0.039 & +0.026 \\ 
-% %1.0e-05 	 & 1.0e-05 	 & 10 & 104 	 & -0.008 & +0.062 & +0.039 & +0.026 \\ 
-% %1.0e-05 	 & 1.0e-06 	 & 10 & 92 	 & -0.007 & +0.062 & +0.039 & +0.026 \\ 
-% 1.0e-06 	 & 1.0e+02 	 & 10 & 210 	 & +0.685 & +0.104 & +0.035 & +0.032 \\ 
-% 1.0e-06 	 & 1.0e+00 	 & 10 & 163 	 & +0.003 & +0.064 & +0.039 & +0.019 \\ 
-% %1.0e-06 	 & 1.0e-01 	 & 10 & 218 	 & -0.006 & +0.062 & +0.039 & +0.018 \\ 
-% 1.0e-06 	 & 1.0e-02 	 & 10 & 134 	 & -0.008 & +0.062 & +0.039 & +0.023 \\ 
-% %1.0e-06 	 & 1.0e-03 	 & 10 & 79 	 & -0.006 & +0.062 & +0.039 & +0.026 \\ 
-% 1.0e-06 	 & 1.0e-04 	 & 10 & 107 	 & -0.007 & +0.062 & +0.039 & +0.026 \\ 
-% %1.0e-06 	 & 1.0e-05 	 & 10 & 103 	 & -0.008 & +0.062 & +0.039 & +0.026 \\ 
-% 1.0e-06 	 & 1.0e-06 	 & 10 & 91 	 & -0.008 & +0.062 & +0.039 & +0.026 \\  
+
 \end{tabular}
@@
 \caption{ Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$, the resulting number of iterations, the relative error of the estimated diffusion coefficients and the relative error for $g$.
-}
+The observations times were chosen $ t_i=[2.4, 4.8,$ 7.2, 9.6, 12.0, 14.4, $16.8, 19.2, 21.6, 24.0]$ }
 \begin{tabular}{*{8}c}
-$\alpha$ & $\beta$ & k & iter & $ D_{\Omega_1}\sp{rel}$& $D_{\Omega_2}\sp{rel} $ & $D_{\Omega_3}\sp{rel} $&$|| g ||\sp{rel}_{L\sp{2}(\Omega_1)} $ \\
+$\alpha$ & $\beta$ & k & iter & $ D_{\Omega_1}\sp{rel}$& $D_{\Omega_2}\sp{rel} $ & $D_{\Omega_3}\sp{rel} $&$|| g ||\sp{rel} $ \\
 \hline
@@
  1.0e-06 	 & 1.0e-06 	 & 40 & 343 	 & -0.014 & -0.010 & -0.003 & +0.004 \\
-% %1.0e+00 	 & 1.0e+00 	 & 10 & 128 	 & +1.587 & +0.217 & +0.091 & +0.119 \\ 
-% 
-% 1.0e+00 	 & 1.0e+00 	 & 20 & 268 	 & +5.537 & +0.321 & +0.152 & +0.128 \\ 
-% 1.0e+00 	 & 1.0e+00 	 & 40 & 381 	 & +12.346 & +0.890 & +0.249 & +0.154\\ 
-% 
-% 1.0e+00 	 & 1.0e-02 	 & 20 & 407 	 & +17.676 & +1.417 & +0.402 & +0.251 \\ 
-% 1.0e+00 	 & 1.0e-02 	 & 40 & 873 	 & +61.467 & +17.965 & +16.437 & +0.614 \\ 
-% 
-%% 1.0e+00 	 & 1.0e-04 	 & 10 & 130 	 & +1.558 & +0.216 & +0.091 & +0.119 \\ 
-% 1.0e+00 	 & 1.0e-04 	 & 20 & 497 	 & +19.414 & +1.514 & +0.422 & +0.259\\ 
-% 1.0e+00 	 & 1.0e-04 	 & 40 & 872 	 & +63.564 & +18.579 & +17.218 & +0.641 \\ 
-%
-% 1.0e-02 	 & 1.0e+00 	 & 20 & 157 	 & +0.016 & +0.004 & +0.008 & +0.007 \\ 
-% 1.0e-02 	 & 1.0e+00 	 & 40 & 277 	 & +0.020 & -0.006 & +0.001 & +0.003 \\ 
-% 
-% 1.0e-02 	 & 1.0e-02 	 & 20 & 447 	 & +0.130 & +0.055 & -0.000 & +0.016 \\ 
-% 1.0e-02 	 & 1.0e-02 	 & 40 & 458 	 & +0.098 & +0.088 & +0.002 & +0.023 \\ 
-% 
-% 1.0e-02 	 & 1.0e-04 	 & 20 & 595 	 & +0.175 & +0.081 & -0.003 & +0.090 \\ 
-% 1.0e-02 	 & 1.0e-04 	 & 40 & 976 	 & +0.320 & +0.398 & +0.088 & +0.226 \\ 
-% 
-%% 1.0e-04 	 & 1.0e+00 	 & 10 & 140 	 & -0.048 & +0.032 & +0.035 & +0.026 \\ 
-% 1.0e-04 	 & 1.0e+00 	 & 20 & 165 	 & +0.006 & +0.000 & +0.008 & +0.007 \\ 
-% 1.0e-04 	 & 1.0e+00 	 & 40 & 285 	 & +0.005 & -0.013 & +0.000 & +0.003 \\ 
-% %1.0e-04 	 & 1.0e-01 	 & 20 & 367 	 & +0.028 & +0.010 & +0.008 & +0.007 \\
-% %1.0e-04 	 & 1.0e-01 	 & 40 & 422 	 & +0.001 & -0.007 & +0.004 & +0.005 \\  
-% 1.0e-04 	 & 1.0e-02 	 & 20 & 258 	 & +0.068 & +0.023 & +0.005 & +0.006 \\ 
-% 1.0e-04 	 & 1.0e-02 	 & 40 & 339 	 & +0.004 & +0.002 & +0.002 & +0.003 \\  
-% 
-% %1.0e-04 	 & 1.0e-04 	 & 10 & 113 	 & -0.060 & +0.030 & +0.036 & +0.026 \\ 
-% 1.0e-04 	 & 1.0e-04 	 & 20 & 322 	 & +0.105 & +0.031 & -0.003 & +0.020 \\ 
-% 1.0e-04 	 & 1.0e-04 	 & 40 & 358 	 & -0.011 & -0.005 & -0.003 & +0.004 \\ 
-% 
-%% 1.0e-05 	 & 1.0e+00 	 & 20 & 237 	 & -0.006 & +0.004 & +0.013 & +0.008 \\ 
-% %1.0e-05 	 & 1.0e+00 	 & 40 & 358 	 & -0.018 & -0.019 & +0.005 & +0.007 \\  
-% %1.0e-05 	 & 1.0e-01 	 & 20 & 290 	 & +0.026 & +0.010 & +0.008 & +0.007 \\
-% %1.0e-05 	 & 1.0e-01 	 & 40 & 419 	 & +0.001 & -0.007 & +0.004 & +0.005 \\    
-% %1.0e-05 	 & 1.0e-02 	 & 20 & 316 	 & +0.071 & +0.025 & +0.005 & +0.007 \\ 
-% %1.0e-05 	 & 1.0e-02 	 & 40 & 401 	 & +0.004 & +0.003 & +0.002 & +0.004 \\  
-% 1.0e-06 	 & 1.0e+00 	 & 20 & 219 	 & -0.007 & +0.004 & +0.013 & +0.008 \\ 
-% 1.0e-06 	 & 1.0e+00 	 & 40 & 240 	 & -0.020 & -0.019 & +0.005 & +0.007 \\ 
-% %1.0e-06 	 & 1.0e-01 	 & 20 & 250 	 & +0.027 & +0.010 & +0.008 & +0.007 \\ 
-% %1.0e-06 	 & 1.0e-01 	 & 40 & 365 	 & +0.000 & -0.007 & +0.004 & +0.005 \\ 
-% 1.0e-06 	 & 1.0e-02 	 & 20 & 379 	 & +0.070 & +0.025 & +0.005 & +0.007 \\ 
-% 1.0e-06 	 & 1.0e-02 	 & 40 & 386 	 & +0.004 & +0.003 & +0.002 & +0.004 \\ 
-% 
-% 1.0e-06 	 & 1.0e-04 	 & 20 & 356 	 & +0.101 & +0.028 & -0.002 & +0.021 \\ 
-% 1.0e-06 	 & 1.0e-04 	 & 40 & 410 	 & -0.011 & -0.002 & -0.003 & +0.004 \\ 
+
 \end{tabular}
@@
 \caption{ Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$, the resulting number of iterations, the relative error of the estimated diffusion coefficients and the relative error for $g$.
-The observation times were set $t_i \in \lbrace 4.8, 9.6, 14.4, 19.2, 24.0 \rbrace $.
+The observation times were set $t_i = [ 4.8, 9.6, 14.4, 19.2, 24.0 ] $.
 }
 \begin{tabular}{*{8}c}
-$\alpha$ & $\beta$ & k & iter & $ D_{\Omega_1}\sp{rel}$& $D_{\Omega_2}\sp{rel} $ & $D_{\Omega_3}\sp{rel} $&$|| g ||\sp{rel}_{L\sp{2}(\Omega_1)} $ \\
+$\alpha$ & $\beta$ & k & iter & $ D_{\Omega_1}\sp{rel}$& $D_{\Omega_2}\sp{rel} $ & $D_{\Omega_3}\sp{rel} $&$|| g ||\sp{rel} $ \\
 \hline
@@
 
-%
-% %1.0e-04 	 & 1.0e+02 	 & 10 & 895 	 & +22.689 & +0.254 & +0.008 & +0.024 \\ 
-% %1.0e-04 	 & 1.0e+02 	 & 20 & 1001 	 & +13.781 & +0.142 & -0.026 & +0.025 \\
-% %1.0e-04 	 & 1.0e+02 	 & 40 & 1001 	 & +9.368 & +0.089 & -0.042 & +0.026 \\
-% 
-%% 1.0e-06 	 & 1.0e+02 	 & 10 & 919 	 & +19.507 & +0.255 & +0.008 & +0.024 \\ 
-%% 1.0e-06 	 & 1.0e+02 	 & 20 & 999 	 & +15.032 & +0.141 & -0.026 & +0.025 \\ 
-%% 1.0e-06 	 & 1.0e+02 	 & 40 & 1001 	 & +9.809 & +0.088 & -0.043 & +0.026 \\ 
-% 
-% 1.0e-02 	 & 1.0e+00 	 & 10 & 144 	 & +0.091 & +0.011 & +0.026 & +0.020 \\ 
-% 1.0e-02 	 & 1.0e+00 	 & 20 & 181 	 & +0.089 & -0.003 & -0.001 & +0.008 \\ 
-% 1.0e-02 	 & 1.0e+00 	 & 40 & 209 	 & +0.066 & -0.025 & -0.011 & +0.004 \\ 
-%  
-% 1.0e-02 	 & 1.0e-02 	 & 10 & 368 	 & +0.183 & +0.066 & +0.026 & +0.084 \\
-% 1.0e-02 	 & 1.0e-02 	 & 20 & 451 	 & +3.859 & +3.282 & +2.577 & +0.302 \\ 
-% 1.0e-02 	 & 1.0e-02 	 & 40 & 518 	 & +7.347 & +6.417 & +5.478 & +0.384 \\ 
-% 
-% 1.0e-04 	 & 1.0e+00 	 & 10 & 161 	 & +0.081 & +0.027 & +0.049 & +0.023 \\ 
-% 1.0e-04 	 & 1.0e+00 	 & 20 & 202 	 & +0.007 & -0.050 & +0.017 & +0.028 \\ 
-% 1.0e-04 	 & 1.0e+00 	 & 40 & 308 	 & -0.032 & -0.081 & +0.002 & +0.031 \\
-%  
-%% 1.0e-04 	 & 1.0e-01 	 & 10 & 185 	 & +0.123 & +0.046 & +0.037 & +0.021 \\ 
-%% 1.0e-04 	 & 1.0e-01 	 & 20 & 336 	 & +0.028 & -0.009 & +0.009 & +0.023 \\
-%% 1.0e-04 	 & 1.0e-01 	 & 40 & 379 	 & -0.004 & -0.033 & -0.006 & +0.026 \\ 
-% 
-% 1.0e-04 	 & 1.0e-02 	 & 10 & 265 	 & +0.160 & +0.082 & +0.033 & +0.016 \\ 
-% 1.0e-04 	 & 1.0e-02 	 & 20 & 320 	 & +0.025 & +0.025 & +0.015 & +0.013 \\
-% 1.0e-04 	 & 1.0e-02 	 & 40 & 377 	 & +0.006 & +0.006 & -0.001 & +0.008 \\ 
-%  
-% 
-%% 1.0e-05 	 & 1.0e+00 	 & 10 & 192 	 & +0.083 & +0.026 & +0.049 & +0.023 \\ 
-%% 1.0e-05 	 & 1.0e+00 	 & 20 & 195 	 & +0.007 & -0.051 & +0.017 & +0.029 \\ 
-%% 1.0e-05 	 & 1.0e+00 	 & 40 & 212 	 & -0.034 & -0.083 & +0.001 & +0.031 \\ 
-% 
-%% 1.0e-05 	 & 1.0e-01 	 & 10 & 223 	 & +0.118 & +0.047 & +0.037 & +0.020 \\ 
-%%  1.0e-05 	 & 1.0e-01 	 & 20 & 320 	 & +0.029 & -0.011 & +0.009 & +0.026 \\
-%%  1.0e-05 	 & 1.0e-01 	 & 40 & 396 	 & -0.007 & -0.036 & -0.006 & +0.028 \\ 
-%  
-%  
-%%  1.0e-05 	 & 1.0e-02 	 & 10 & 267 	 & +0.159 & +0.084 & +0.033 & +0.016 \\ 
-%%  1.0e-05 	 & 1.0e-02 	 & 20 & 351 	 & +0.023 & +0.017 & +0.011 & +0.019 \\ 
-%%  1.0e-05 	 & 1.0e-02 	 & 40 & 374 	 & +0.009 & +0.007 & -0.003 & +0.014 \\ 
-%  
-%  
-% 1.0e-06 	 & 1.0e+00 	 & 10 & 176 	 & +0.082 & +0.026 & +0.049 & +0.023 \\ 
-% 1.0e-06 	 & 1.0e+00 	 & 20 & 224 	 & +0.007 & -0.051 & +0.017 & +0.029 \\ 
-% 1.0e-06 	 & 1.0e+00 	 & 40 & 226 	 & -0.034 & -0.082 & +0.001 & +0.031 \\ 
-%  
-%% 1.0e-06 	 & 1.0e-01 	 & 10 & 229 	 & +0.120 & +0.046 & +0.037 & +0.021 \\ 
-%%  1.0e-06 	 & 1.0e-01 	 & 20 & 334 	 & +0.027 & -0.012 & +0.009 & +0.026 \\  
-%% 1.0e-06 	 & 1.0e-01 	 & 40 & 313 	 & -0.007 & -0.037 & -0.006 & +0.030 \\
-%  
-% 1.0e-06 	 & 1.0e-02 	 & 10 & 253 	 & +0.156 & +0.080 & +0.033 & +0.018 \\ 
-% 1.0e-06 	 & 1.0e-02 	 & 20 & 340 	 & +0.020 & +0.016 & +0.012 & +0.019 \\ 
-% 1.0e-06 	 & 1.0e-02 	 & 40 & 368 	 & +0.006 & +0.006 & -0.004 & +0.013 \\ 
 \end{tabular}
@@
 \caption{ Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$, the resulting number of iterations, the relative error of the estimated diffusion coefficients and the relative error for $g$.
-The observation times were $t_i \in \lbrace $1.2, 2.4, 3.6, 4.8, 6.0, 7.2, 8.4, 9.6, 10.8, 12.0, 13.2, 14.4, 15.6, 16.8, 17.0, 19.2, 20.4,$ 21.6, 22.8, 24.0\rbrace $.}
+The observation times were $t_i = [ $1.2, 2.4, 3.6, 4.8, 6.0, 7.2, 8.4, 9.6, 10.8, 12.0, 13.2, 14.4, 15.6, 16.8, 17.0, 19.2, 20.4,$ 21.6, 22.8, 24.0 ]$.}
 \begin{tabular}{*{8}c}
-$\alpha$ & $\beta$ & k & iter & $ D_{\Omega_1}\sp{rel}$ & $ D_{\Omega_2}\sp{rel}$ & $D_{\Omega_3}\sp{rel} $ & $|| g ||\sp{rel}_{L\sp{2}(\Omega_1)} $ \\
+$\alpha$ & $\beta$ & k & iter & $ D_{\Omega_1}\sp{rel}$ & $ D_{\Omega_2}\sp{rel}$ & $D_{\Omega_3}\sp{rel} $ & $|| g ||\sp{rel} $ \\
 \hline
@@
 
-%
-% 1.0e-02 	 & 1.0e+00 	 & 10 & 283 	 & -0.062 & +0.026 & +0.022 & +0.033 \\ 
-% 1.0e-02 	 & 1.0e+00 	 & 20 & 208 	 & -0.012 & +0.012 & +0.008 & +0.007 \\ 
-% 1.0e-02 	 & 1.0e+00 	 & 40 & 201 	 & +0.002 & +0.001 & +0.002 & +0.002 \\ 
-% 
-% 
-% 1.0e-02 	 & 1.0e-02 	 & 10 & 238 	 & -0.068 & +0.026 & +0.022 & +0.033 \\ 
-% 1.0e-02 	 & 1.0e-02 	 & 20 & 492 	 & -0.001 & +0.013 & +0.004 & +0.010 \\ 
-% 1.0e-02 	 & 1.0e-02 	 & 40 & 572 	 & +0.040 & +0.014 & -0.002 & +0.004 \\ 
-% 
-% 
-% 
-% 1.0e-04 	 & 1.0e+00 	 & 10 & 246 	 & -0.046 & +0.038 & +0.023 & +0.031 \\ 
-% 1.0e-04 	 & 1.0e+00 	 & 20 & 228 	 & -0.008 & +0.016 & +0.009 & +0.006 \\ 
-% 1.0e-04 	 & 1.0e+00 	 & 40 & 279 	 & -0.007 & +0.000 & +0.003 & +0.002 \\  
-%  
-%% 1.0e-04 	 & 1.0e-01 	 & 10 & 292 	 & -0.052 & +0.038 & +0.024 & +0.032 \\  
-%% 1.0e-04 	 & 1.0e-01 	 & 20 & 331 	 & -0.001 & +0.018 & +0.006 & +0.006 \\ 
-%% 1.0e-04 	 & 1.0e-01 	 & 40 & 313 	 & +0.004 & +0.003 & +0.000 & +0.002 \\ 
-% 
-% 1.0e-04 	 & 1.0e-02 	 & 10 & 338 	 & -0.053 & +0.038 & +0.024 & +0.032 \\ 
-%  1.0e-04 	 & 1.0e-02 	 & 20 & 367 	 & +0.003 & +0.018 & +0.005 & +0.007 \\
-%   1.0e-04 	 & 1.0e-02 	 & 40 & 273 	 & +0.017 & +0.006 & -0.001 & +0.001 \\  
-%  
-%% 1.0e-05 	 & 1.0e+00 	 & 10 & 290 	 & -0.047 & +0.038 & +0.023 & +0.031 \\ 
-%%  1.0e-05 	 & 1.0e+00 	 & 20 & 194 	 & -0.008 & +0.016 & +0.009 & +0.006 \\ 
-%%   1.0e-05 	 & 1.0e+00 	 & 40 & 238 	 & -0.007 & +0.000 & +0.002 & +0.002 \\ 
-%  
-%% 1.0e-05 	 & 1.0e-01 	 & 10 & 316 	 & -0.052 & +0.038 & +0.024 & +0.032 \\ 
-%%  1.0e-05 	 & 1.0e-01 	 & 20 & 312 	 & -0.001 & +0.018 & +0.006 & +0.006 \\ 
-%%   1.0e-05 	 & 1.0e-01 	 & 40 & 317 	 & +0.004 & +0.003 & +0.000 & +0.002 \\ 
-%   
-%   
-% %1.0e-05 	 & 1.0e-02 	 & 10 & 389 	 & -0.052 & +0.038 & +0.024 & +0.033 \\ 
-% % 1.0e-05 	 & 1.0e-02 	 & 20 & 266 	 & +0.004 & +0.018 & +0.005 & +0.007 \\ 
-% %  1.0e-05 	 & 1.0e-02 	 & 40 & 336 	 & +0.015 & +0.005 & -0.001 & +0.001 \\ 
-%   
-%   
-% 1.0e-06 	 & 1.0e+00 	 & 10 & 282 	 & -0.047 & +0.038 & +0.023 & +0.031 \\ 
-%  1.0e-06 	 & 1.0e+00 	 & 20 & 179 	 & -0.008 & +0.016 & +0.009 & +0.006 \\ 
-%  1.0e-06 	 & 1.0e+00 	 & 40 & 261 	 & -0.007 & +0.000 & +0.002 & +0.002 \\ 
-% 
-%  
-%% 1.0e-06 	 & 1.0e-01 	 & 10 & 308 	 & -0.052 & +0.038 & +0.024 & +0.032 \\ 
-%%  1.0e-06 	 & 1.0e-01 	 & 20 & 245 	 & -0.002 & +0.018 & +0.006 & +0.006 \\ 
-%%   1.0e-06 	 & 1.0e-01 	 & 40 & 318 	 & +0.004 & +0.003 & +0.000 & +0.002 \\
-%
-% 1.0e-06 	 & 1.0e-02 	 & 10 & 285 	 & -0.052 & +0.038 & +0.024 & +0.032 \\ 
-% 1.0e-06 	 & 1.0e-02 	 & 20 & 362 	 & +0.003 & +0.018 & +0.005 & +0.007 \\ 
-% 1.0e-06 	 & 1.0e-02 	 & 40 & 375 	 & +0.015 & +0.005 & -0.001 & +0.001 \\ 
 \end{tabular}
@@
 \begin{tabular}{*{8}c}
-$\alpha$ & $\beta$ & k  & iter & $ D_{\Omega_1}\sp{rel} $ & $D_{\Omega_2}\sp{rel}$ & $D_{\Omega_3}\sp{rel}$ & $|| g ||\sp{rel}_{L\sp{2}(\Omega_1)} $\\
+$\alpha$ & $\beta$ & k  & iter & $ D_{\Omega_1}\sp{rel} $ & $D_{\Omega_2}\sp{rel}$ & $D_{\Omega_3}\sp{rel}$ & $|| g ||\sp{rel} $\\
 \hline
@@
 
-% %1.0e+00 	 & 1.0e+00 	 & 10 & 218 	 & +4.266 & +0.304 & +0.092 & +0.135 \\ 
-% %1.0e+00 	 & 1.0e-01 	 & 10 & 223 	 & +4.565 & +0.304 & +0.090 & +0.142 \\ 
-%% 1.0e+00 	 & 1.0e-02 	 & 10 & 199 	 & +4.268 & +0.305 & +0.090 & +0.143 \\ 
-%% 1.0e+00 	 & 1.0e-03 	 & 10 & 222 	 & +4.274 & +0.305 & +0.090 & +0.143 \\ 
-%% 1.0e+00 	 & 1.0e-04 	 & 10 & 211 	 & +4.448 & +0.306 & +0.090 & +0.143 \\ 
-%% 1.0e+00 	 & 1.0e-05 	 & 10 & 227 	 & +4.527 & +0.304 & +0.090 & +0.143 \\ 
-%%1.0e+00 	 & 1.0e-06 	 & 10 & 263 	 & +4.266 & +0.306 & +0.091 & +0.143 \\ 
-% 
-% %1.0e-01 	 & 1.0e+00 	 & 10 & 167 	 & +0.131 & +0.093 & +0.041 & +0.027 \\ 
-%% 1.0e-01 	 & 1.0e-01 	 & 10 & 195 	 & +0.125 & +0.093 & +0.039 & +0.046 \\ 
-%% 1.0e-01 	 & 1.0e-02 	 & 10 & 218 	 & +0.126 & +0.093 & +0.040 & +0.056 \\ 
-%% 1.0e-01 	 & 1.0e-03 	 & 10 & 161 	 & +0.129 & +0.094 & +0.040 & +0.057 \\ 
-%% 1.0e-01 	 & 1.0e-04 	 & 10 & 180 	 & +0.135 & +0.092 & +0.042 & +0.057 \\ 
-%% 1.0e-01 	 & 1.0e-05 	 & 10 & 169 	 & +0.123 & +0.093 & +0.041 & +0.057 \\ 
-%% 1.0e-01 	 & 1.0e-06 	 & 10 & 201 	 & +0.119 & +0.093 & +0.040 & +0.057 \\ 
-%
-% 1.0e-02 	 & 1.0e+00 	 & 10 & 183 	 & +0.013 & +0.067 & +0.040 & +0.018 \\ 
-%% 1.0e-02 	 & 1.0e-01 	 & 10 & 149 	 & +0.002 & +0.066 & +0.038 & +0.021 \\ 
-% 1.0e-02 	 & 1.0e-02 	 & 10 & 185 	 & -0.005 & +0.065 & +0.040 & +0.040 \\ 
-%% 1.0e-02 	 & 1.0e-03 	 & 10 & 213 	 & +0.004 & +0.066 & +0.038 & +0.049 \\ 
-% 1.0e-02 	 & 1.0e-04 	 & 10 & 151 	 & +0.008 & +0.066 & +0.039 & +0.047 \\ 
-%% 1.0e-02 	 & 1.0e-05 	 & 10 & 197 	 & +0.004 & +0.064 & +0.040 & +0.051 \\ 
-% 1.0e-02 	 & 1.0e-06 	 & 10 & 185 	 & +0.012 & +0.063 & +0.038 & +0.049 \\ 
-%
-%% 1.0e-03 	 & 1.0e+00 	 & 10 & 183 	 & +0.007 & +0.062 & +0.038 & +0.019 \\ 
-%% 1.0e-03 	 & 1.0e-01 	 & 10 & 181 	 & -0.011 & +0.063 & +0.039 & +0.019 \\ 
-%% 1.0e-03 	 & 1.0e-02 	 & 10 & 122 	 & -0.008 & +0.063 & +0.040 & +0.025 \\ 
-%% 1.0e-03 	 & 1.0e-03 	 & 10 & 158 	 & -0.004 & +0.062 & +0.040 & +0.028 \\ 
-%% 1.0e-03 	 & 1.0e-04 	 & 10 & 168 	 & -0.013 & +0.063 & +0.038 & +0.029 \\ 
-%% 1.0e-03 	 & 1.0e-05 	 & 10 & 120 	 & -0.010 & +0.063 & +0.040 & +0.028 \\ 
-%% 1.0e-03 	 & 1.0e-06 	 & 10 & 132 	 & -0.002 & +0.062 & +0.039 & +0.028 \\ 
-%
-% 1.0e-04 	 & 1.0e+00 	 & 10 & 176 	 & +0.000 & +0.063 & +0.039 & +0.019 \\ 
-% %1.0e-04 	 & 1.0e-01 	 & 10 & 180 	 & -0.001 & +0.062 & +0.039 & +0.019 \\ 
-% 1.0e-04 	 & 1.0e-02 	 & 10 & 120 	 & +0.000 & +0.063 & +0.039 & +0.024 \\ 
-% %1.0e-04 	 & 1.0e-03 	 & 10 & 119 	 & -0.004 & +0.062 & +0.039 & +0.026 \\ 
-% 1.0e-04 	 & 1.0e-04 	 & 10 & 77 	 & -0.005 & +0.061 & +0.038 & +0.027 \\ 
-% %1.0e-04 	 & 1.0e-05 	 & 10 & 104 	 & -0.004 & +0.062 & +0.038 & +0.027 \\ 
-% 1.0e-04 	 & 1.0e-06 	 & 10 & 109 	 & -0.007 & +0.062 & +0.039 & +0.027 \\ 
-%
-% %1.0e-05 	 & 1.0e+00 	 & 10 & 220 	 & +0.005 & +0.063 & +0.039 & +0.019 \\ 
-% %1.0e-05 	 & 1.0e-01 	 & 10 & 193 	 & -0.009 & +0.062 & +0.039 & +0.019 \\ 
-% %1.0e-05 	 & 1.0e-02 	 & 10 & 163 	 & -0.013 & +0.063 & +0.039 & +0.021 \\ 
-% %1.0e-05 	 & 1.0e-03 	 & 10 & 115 	 & -0.007 & +0.063 & +0.040 & +0.026 \\ 
-% %1.0e-05 	 & 1.0e-04 	 & 10 & 82 	 & -0.007 & +0.062 & +0.038 & +0.027 \\ 
-% %1.0e-05 	 & 1.0e-05 	 & 10 & 145 	 & -0.001 & +0.062 & +0.039 & +0.027 \\ 
-% %1.0e-05 	 & 1.0e-06 	 & 10 & 147 	 & -0.012 & +0.061 & +0.040 & +0.027 \\ 
-%
-% 1.0e-06 	 & 1.0e+00 	 & 10 & 138 	 & +0.002 & +0.063 & +0.039 & +0.019 \\ 
-% %1.0e-06 	 & 1.0e-01 	 & 10 & 184 	 & -0.006 & +0.063 & +0.039 & +0.019 \\ 
-% 1.0e-06 	 & 1.0e-02 	 & 10 & 83 	 & -0.006 & +0.063 & +0.040 & +0.025 \\ 
-% %1.0e-06 	 & 1.0e-03 	 & 10 & 91 	 & -0.013 & +0.063 & +0.039 & +0.026 \\ 
-% 1.0e-06 	 & 1.0e-04 	 & 10 & 109 	 & -0.005 & +0.062 & +0.038 & +0.027 \\ 
-% %1.0e-06 	 & 1.0e-05 	 & 10 & 116 	 & -0.007 & +0.063 & +0.039 & +0.027 \\ 
-% 1.0e-06 	 & 1.0e-06 	 & 10 & 108 	 & +0.001 & +0.062 & +0.040 & +0.027 \\ 
 \end{tabular}
@@
 \begin{tabular}{*{8}c}
-$\alpha$ & $\beta$ & k  & iter & $ D_{\Omega_1}\sp{rel}$ & $D_{\Omega_2}\sp{rel} $ & $D_{\Omega_3}\sp{rel} $ & $|| g ||\sp{rel}_{L\sp{2}(\Omega_1)} $ \\
+$\alpha$ & $\beta$ & k  & iter & $ D_{\Omega_1}\sp{rel}$ & $D_{\Omega_2}\sp{rel} $ & $D_{\Omega_3}\sp{rel} $ & $|| g ||\sp{rel} $ \\
 \hline
@@
 
-%% 1.0e+00 	 & 1.0e+00 	 & 10 & 212 	 & +4.268 & +0.310 & +0.073 & +0.138 \\ 
-% %1.0e+00 	 & 1.0e-01 	 & 10 & 211 	 & +4.122 & +0.302 & +0.085 & +0.146 \\ 
-%% 1.0e+00 	 & 1.0e-02 	 & 10 & 221 	 & +4.773 & +0.298 & +0.089 & +0.147 \\ 
-% %1.0e+00 	 & 1.0e-03 	 & 10 & 257 	 & +4.872 & +0.301 & +0.090 & +0.147 \\ 
-%% 1.0e+00 	 & 1.0e-04 	 & 10 & 238 	 & +4.186 & +0.293 & +0.097 & +0.148 \\ 
-% %1.0e+00 	 & 1.0e-05 	 & 10 & 204 	 & +4.251 & +0.313 & +0.085 & +0.147 \\ 
-%% 1.0e+00 	 & 1.0e-06 	 & 10 & 223 	 & +4.493 & +0.310 & +0.085 & +0.147 \\ 
-% %1.0e-01 	 & 1.0e+00 	 & 10 & 145 	 & +0.126 & +0.100 & +0.054 & +0.035 \\ 
-% %1.0e-01 	 & 1.0e-01 	 & 10 & 199 	 & +0.115 & +0.125 & +0.026 & +0.060 \\ 
-% %1.0e-01 	 & 1.0e-02 	 & 10 & 217 	 & +0.128 & +0.092 & +0.036 & +0.071 \\ 
-% %1.0e-01 	 & 1.0e-03 	 & 10 & 242 	 & +0.109 & +0.093 & +0.031 & +0.073 \\ 
-% %1.0e-01 	 & 1.0e-04 	 & 10 & 275 	 & +0.187 & +0.094 & +0.028 & +0.073 \\ 
-% %1.0e-01 	 & 1.0e-05 	 & 10 & 237 	 & +0.048 & +0.099 & +0.039 & +0.073 \\ 
-% %1.0e-01 	 & 1.0e-06 	 & 10 & 225 	 & +0.092 & +0.111 & +0.055 & +0.073 \\ 
-% 1.0e-02 	 & 1.0e+00 	 & 10 & 208 	 & +0.017 & +0.075 & +0.037 & +0.029 \\ 
-% %1.0e-02 	 & 1.0e-01 	 & 10 & 199 	 & -0.013 & +0.068 & +0.046 & +0.040 \\ 
-% 1.0e-02 	 & 1.0e-02 	 & 10 & 348 	 & -0.043 & +0.073 & +0.041 & +0.063 \\ 
-%% 1.0e-02 	 & 1.0e-03 	 & 10 & 400 	 & +0.056 & +0.058 & +0.031 & +0.075 \\ 
-% 1.0e-02 	 & 1.0e-04 	 & 10 & 393 	 & -0.050 & +0.088 & +0.044 & +0.077 \\ 
-% %1.0e-02 	 & 1.0e-05 	 & 10 & 359 	 & +0.022 & +0.068 & +0.027 & +0.076 \\ 
-% 1.0e-02 	 & 1.0e-06 	 & 10 & 369 	 & +0.001 & +0.074 & +0.024 & +0.076 \\ 
-% %1.0e-03 	 & 1.0e+00 	 & 10 & 207 	 & -0.001 & +0.065 & +0.051 & +0.029 \\ 
-%% 1.0e-03 	 & 1.0e-01 	 & 10 & 280 	 & +0.028 & +0.051 & +0.053 & +0.038 \\ 
-% %1.0e-03 	 & 1.0e-02 	 & 10 & 565 	 & -0.059 & +0.076 & +0.033 & +0.053 \\ 
-%% 1.0e-03 	 & 1.0e-03 	 & 10 & 673 	 & -0.035 & +0.066 & +0.032 & +0.108 \\ 
-% %\rowcolor{orange} 1.0e-03 	 & 1.0e-04 	 & 10 & 604 	 & -0.026 & +0.061 & +0.049 & +0.182 \\ 
-% %1.0e-03 	 & 1.0e-05 	 & 10 & 666 	 & +0.012 & +0.070 & +0.038 & +0.182 \\ 
-% %\rowcolor{orange} 1.0e-03 	 & 1.0e-06 	 & 10 & 893 	 & +0.027 & +0.070 & +0.022 & +0.180 \\ 
-% 1.0e-04 	 & 1.0e+00 	 & 10 & 204 	 & +0.015 & +0.062 & +0.043 & +0.030 \\ 
-% %1.0e-04 	 & 1.0e-01 	 & 10 & 269 	 & +0.005 & +0.057 & +0.037 & +0.038 \\ 
-% 1.0e-04 	 & 1.0e-02 	 & 10 & 559 	 & -0.072 & +0.067 & +0.044 & +0.050 \\ 
-%%\rowcolor{orange} 1.0e-04 	 & 1.0e-03 	 & 10 & 691 	 & -0.023 & +0.055 & +0.040 & +0.175 \\ 
-% 1.0e-04 	 & 1.0e-04 	 & 10 & -	 & -0.012 & +0.066 & +0.030 & +0.745 \\ 
-%%\rowcolor{red}  1.0e-04 	 & 1.0e-05 	 & 10 & 1001 	 & +0.038 & +0.057 & +0.034 & +1.113 \\ 
-%1.0e-04 	 & 1.0e-06 	 & 10 & -	 & +0.015 & +0.063 & +0.035 & +1.127 \\ 
-%% 1.0e-05 	 & 1.0e+00 	 & 10 & 184 	 & -0.025 & +0.076 & +0.041 & +0.029 \\ 
-% %1.0e-05 	 & 1.0e-01 	 & 10 & 357 	 & -0.011 & +0.070 & +0.052 & +0.038 \\ 
-%% 1.0e-05 	 & 1.0e-02 	 & 10 & 399 	 & +0.041 & +0.075 & +0.042 & +0.049 \\ 
-%%1.0e-05 	 & 1.0e-03 	 & 10 & 689 	 & +0.044 & +0.062 & +0.020 & +0.172 \\ 
-%%\rowcolor{red} 1.0e-05 	 & 1.0e-04 	 & 10 & 915 	 & +0.030 & +0.077 & +0.039 & +1.027 \\ 
-% %1.0e-05 	 & 1.0e-05 	 & 10 & - 	 & +0.017 & +0.061 & +0.045 & +1.953 \\ 
-%%\rowcolor{red}  1.0e-05 	 & 1.0e-06 	 & 10 & - 	 & -0.018 & +0.071 & +0.045 & +2.545 \\ 
-% 1.0e-06 	 & 1.0e+00 	 & 10 & 177 	 & +0.060 & +0.069 & +0.039 & +0.029 \\ 
-%% 1.0e-06 	 & 1.0e-01 	 & 10 & 302 	 & +0.011 & +0.039 & +0.039 & +0.038 \\ 
-% 1.0e-06 	 & 1.0e-02 	 & 10 & 457 	 & +0.011 & +0.055 & +0.036 & +0.050 \\ 
-%%\rowcolor{orange} 1.0e-06 	 & 1.0e-03 	 & 10 & 738 	 & -0.022 & +0.055 & +0.042 & +0.172 \\ 
-% 1.0e-06 	 & 1.0e-04 	 & 10 & -	 & -0.043 & +0.042 & +0.054 & +1.180 \\ 
-%%\rowcolor{red}  1.0e-06 	 & 1.0e-05 	 & 10 & 1001 	 & +0.006 & +0.052 & +0.033 & +3.365 \\ 
-% 1.0e-06 	 & 1.0e-06 	 & 10 & - & -0.002 & +0.065 & +0.051 & +3.402 \\ 
 \end{tabular}
@@
 
-%
-%
-%\begin{table}
-%\centering
-%\caption{Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$, the resulting number of iterations, the relative error of the estimated diffusion coefficients and the relative error for $g$.
-The observation times were set $t_i \in \lbrace 0.8, 1.0, 1.2, 1.8, 2.4, 3.6, 5.4, 7.6, 24.0\rbrace $, and zero noise.}
-%\resizebox{\textwidth}{!}{\begin{tabular}{*{8}c}
-%$\alpha$ & $\beta$ & k & iter &  $ D_{\Omega_1}\sp{rel}$ & $ D_{\Omega_2}\sp{rel}$ & $D_{\Omega_3}\sp{rel} $ & $|| g ||\sp{rel}_{L\sp{2}(\Omega_1)} $\\
-%\hline
-% 1.0e-04 	 & 1.0e+00 	 & 40 & 453 	 & -0.003 & -0.017 & -0.021 & +0.053 \\
-% 1.0e-04 	 & 1.0e-01 	 & 40 & 491 	 & -0.033 & -0.015 & -0.024 & +0.049 \\ 
-% 1.0e-04 	 & 1.0e-02 	 & 40 & 611 	 & -0.051 & -0.020 & -0.027 & +0.096 \\ 
-% %1.0e-05 	 & 1.0e+00 	 & 40 & 561 	 & -0.004 & -0.016 & -0.021 & +0.053 \\ 
-% %1.0e-05 	 & 1.0e-01 	 & 40 & 688 	 & -0.033 & -0.015 & -0.025 & +0.045 \\ 
-% %1.0e-05 	 & 1.0e-02 	 & 40 & 566 	 & -0.053 & -0.020 & -0.027 & +0.098 \\
-% 1.0e-06 	 & 1.0e+00 	 & 40 & 517 	 & -0.005 & -0.016 & -0.021 & +0.053 \\ 
-% 1.0e-06 	 & 1.0e-01 	 & 40 & 619 	 & -0.033 & -0.015 & -0.025 & +0.044 \\  
-% 1.0e-06 	 & 1.0e-02 	 & 40 & 691 	 & -0.051 & -0.020 & -0.027 & +0.073 \\ 
-%
-%
-%\end{tabular}}
-%\label{Tab::Hole1}
-%\end{table} 
-%\begin{table}
-%\centering
-%\caption{Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$, the resulting number of iterations, the relative error of the estimated diffusion coefficients and the relative error for $g$.
-The observation times were set $t_i \in \lbrace 0.8, 1.0, 1.2, 1.8, 2.4, 3.6, 5.4, 7.6, 24.0\rbrace $, and with a noise amplitude of 0.3.}
-%\resizebox{\textwidth}{!}{\begin{tabular}{*{8}c}
-%$\alpha$ & $\beta$ & k & iter & $ D_{\Omega_1}\sp{rel}$ & $  D_{\Omega_2}\sp{rel}$ & $ D_{\Omega_3}\sp{rel}$  &$|| g ||\sp{rel}_{L\sp{2}(\Omega_1)} $\\
-%\hline
-% %1.0e-04 	 & 1.0e+00 	 & 40 & 519 	 & +0.003 & +0.029 & +0.035 & +0.067 \\ 
-%% 1.0e-04 	 & 1.0e-01 	 & 40 & 653 	 & -0.096 & +0.015 & +0.016 & +0.070 \\ 
-%%\rowcolor{red}  1.0e-04 	 & 1.0e-02 	 & 40 & 575 	 & -0.050 & -0.001 & +0.057 & +0.281 \\ 
-%% 1.0e-05 	 & 1.0e+00 	 & 40 & 585 	 & -0.050 & -0.007 & +0.017 & +0.068 \\ 
-%% 1.0e-05 	 & 1.0e-01 	 & 40 & 871 	 & -0.023 & +0.024 & +0.019 & +0.079 \\ 
-%%\rowcolor{red}  1.0e-05 	 & 1.0e-02 	 & 40 & 466 	 & -0.045 & +0.042 & +0.019 & +0.281 \\ 
-%% 1.0e-06 	 & 1.0e+00 	 & 40 & 584 	 & -0.045 & +0.019 & +0.006 & +0.071 \\ 
-%% 1.0e-06 	 & 1.0e-01 	 & 40 & 546 	 & +0.005 & +0.019 & -0.001 & +0.079 \\ 
-%%\rowcolor{red}  1.0e-06 	 & 1.0e-02 	 & 40 & 648 	 & -0.074 & -0.008 & +0.041 & +0.227 \\ 
-%
-% 1.0e-04 	 & 1.0e+00 	 & 40 & 519 	 & +0.066 & -0.025 & -0.002 & +0.063 \\ 
-% 1.0e-04 	 & 1.0e-01 	 & 40 & 853 	 & -0.047 & -0.013 & -0.001 & +0.078 \\ 
-% 1.0e-04 	 & 1.0e-02 	 & 40 & -	 & -0.062 & -0.005 & -0.018 & +0.223 \\ 
-% %1.0e-05 	 & 1.0e+00 	 & 40 & 455 	 & -0.038 & -0.006 & +0.012 & +0.063 \\ 
-% %1.0e-05 	 & 1.0e-01 	 & 40 & 801 	 & -0.016 & +0.002 & +0.040 & +0.074 \\ 
-% %1.0e-05 	 & 1.0e-02 	 & 40 & 877 	 & -0.060 & +0.017 & +0.010 & +0.198 \\ 
-% 1.0e-06 	 & 1.0e+00 	 & 40 & 575 	 & -0.030 & +0.001 & +0.015 & +0.062 \\ 
-% 1.0e-06 	 & 1.0e-01 	 & 40 & 848 	 & +0.002 & +0.005 & +0.023 & +0.071 \\ 
-% 1.0e-06 	 & 1.0e-02 	 & 40 & -	 & +0.018 & +0.013 & -0.035 & +0.234 \\ 
-%\end{tabular}}
-%\label{Tab::Hole2}
-%\end{table}
-
 \begin{table}
 \centering
-\caption{Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$, the resulting number of iterations, the estimated diffusion coefficients for grey $D_g$ and white $D_w$ matter based on MRI data.}
+\caption{Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$, the resulting number of iterations, the estimated diffusion coefficients for grey $D_{\Omega_{GM}}$ and white $D_{\Omega_{WM}}$ matter based on MRI data.}
 \begin{tabular}{*{6}c}
-$\alpha$ & $\beta$ & k & iter &  $ D_{g} \left[ \mathrm{mm\sp{2}/h} \right] $ & $ D_{w} \left[ \mathrm{mm\sp{2}/h} \right]$ \\
+$\alpha$ & $\beta$ & k & iter &  $ D_{\Omega_{GM}} \left[ \mathrm{mm\sp{2}/h} \right] $ & $ D_{\Omega_{WM}} \left[ \mathrm{mm\sp{2}/h} \right]$ \\
 \hline

### 2018-10-25 tex/paper.tex
update
small update

@@
 In particular the system seems to facilitate waste transport faster than  
-the extracellular diffusion, which since the pioneering works of \citet{sykova2008diffusion} 
-has been the prevailing paradigm.
+the extracellular diffusion, which has been the prevailing paradigm since the pioneering works of \citet{sykova2008diffusion}.
 
@@
 However, the addition of noise required that $\beta = 1.0 $ to obtain consistent convergence.
-Crucial in our application is the interplay between the regularization term that regulates the smoothness of the boundary conditions as well as
-the integrate magnitude of the boundary conditions over time, i.e. $\alpha$ and $\beta$, and the
-importance of interplay of these parameter increases with the number of time steps. This is, however, not surprising because our observations are sparse
-in time and hence an oscillating boundary condition in time will minimized the integrated boundary condition at the cost of reducing the smoothness in time.
+Crucial in our application is the interplay between the regularization term that regulates the smoothness of the boundary conditions as well as the integrated magnitude of the boundary conditions over time, i.e.
+$\alpha$ and $\beta$.
+Further, we observed that the importance of interplay of these parameters increases with the number of time steps.
+This is, however, not surprising because our observations are sparse
+in time and hence an oscillating boundary condition in time will minimize the integrated boundary condition at the cost of reducing the smoothness in time.
 The selected range of regularization parameters showed a decrease in error with more timesteps, rather than oscillation.
@@
 The computational model uses 2 global controls for the diffusion coefficients, while it can be seen in  Fig.\ref{figuredti} that diffusion coefficients can be considered a spacial function.
-The implementation control parameters for each degree of freedom, would significantly increase the computational cost.
-The option using region specific control parameters seems to be a better option, since the diffusivity appears to be regional.
-It can also be taken into consideration to model the diffusion coefficients as a function in time, given the report of an increase clearance in rodents during sleeping \cite{xie2013sleep}.
+However, the implementation of control parameters for each degree of freedom would significantly increase the computational cost.
+Since the diffusivity appears to be regional, using region specific control parameters seems to be a better option.
+It can also be taken into consideration to model the diffusion coefficients as a function in time, given the report of increased clearance in rodents during sleep \cite{xie2013sleep}.
 This would indicate a time-dependent diffusivity, since the clearance in the brain is driven by diffusion.
@@
 This can be caused by the boundary control $g$, which exists along the entire boundary of the grey matter.
-Considering the that the grey matter volume has a depth less than 3 mm makes it susceptible to changes in $g$.
+Considering that the grey matter volume has a depth less than 3 mm makes it susceptible to changes in $g$.
 This can be observed in the reconstruction in Fig.\ref{12hourswithnoise} and Fig.\ref{24hourswithnoise}, where the noise is present at the boundary.
@@
 
-\bibliographystyle{plainnat}
+%\bibliographystyle{plainnat}
+\bibliographystyle{abbrvnat}
 \bibliography{references}

### 2018-10-27 tex/paper.tex
changed text

@@
 
-\title{Assessing paravascular transport in the parenchyma by PDE constrained optimization.}
+\title{Assessing paravascular transport in the parenchyma by PDE (partial differential equations) constrained optimization.}
 
@@
 \section{Introduction}
-Recent breakthroughs in medicine have linked neurodegenerative diseases like Alzheimer's to insufficient sleep through a novel fluid mechanism called the glymphatic system 
-that is responsible for waste clearance. 
-In 2011,~\citet{iliff2012paravascular} discovered a novel system within our brain's metabolic system, which changed our understanding of the brain. 
-The system involves a new pathway, called the paravascular pathway as it runs in parallel with the vasculature system in a surrounding compartment.
-The important novelty in the 2011 findings was that waste from the brain is cleared through the paravascular path, and that a malfunction of this system 
-is linked to the development of dementia such as Alzheimer's and Parkinson's diseases. In 2013,~\citet{xie2013sleep} found
-that this system is particularly active during sleep.
-These mentioned breakthroughs were all performed in mice. In 2018, the action of the glymphatic system was for the first time demonstrated in humans. Further, it was shown that this action differs
-between healthy controls and patients with dementia~\cite{ringstad2018brain}.
-However, the biomechanical mechanisms behind the glymphatic system is not well understood from a fluid mechanics perspective,
+In 2012, Iliff et al ~\citet{iliff2012paravascular} provided evidence for a a brain-wide paravascular system, denoted the glymphatic system, which is a pathway for transport of fluids and solutes.
+It was proposed to have an important metabolic role by providing a pathway for clearance of waste solutes from the brain.
+Evidence was given that the activity of the glymphatic system increases during sleep ~\citet{xie2013sleep}, thus linking sleep to clearance of toxic substances from the brain.
+The glymphatic system seems to become impaired during aging, and failure of the glymphatic system may play a role in neurodegenerative disease and development of Alzheimer's disease.
+Evidence for a brain-wide glymphatic system in humans was first obtained in 2015 \citet{eide2015mri}, and in 2017 \citet{ringstad2018brain} provided evidence that glymphatic function is deteriorated in individuals with dementia, as compared to controls.
+Several aspects of the glympahtic system are still debated, for example whether glymphatic transport of solutes is by convective mechanisms or by diffusion.
+
+%Recent breakthroughs in medicine have linked neurodegenerative diseases like Alzheimer's to insufficient sleep through a novel fluid mechanism called the glymphatic system 
+%that is responsible for waste clearance. 
+%In 2011,~\citet{iliff2012paravascular} discovered a novel system within our brain's metabolic system, which changed our understanding of the brain. 
+%The system involves a new pathway, called the paravascular pathway as it runs in parallel with the vasculature system in a surrounding compartment.
+%The important novelty in the 2011 findings was that waste from the brain is cleared through the paravascular path, and that a malfunction of this system 
+%is linked to the development of dementia such as Alzheimer's and Parkinson's diseases. In 2013,~\citet{xie2013sleep} found
+%that this system is particularly active during sleep.
+%These mentioned breakthroughs were all performed in mice.
+In 2018, the action of the glymphatic system was for the first time demonstrated in humans.
+Further, it was shown that this action differs between healthy controls and patients with dementia~\cite{ringstad2018brain}.
+%However, the biomechanical mechanisms behind the glymphatic system is not well understood from a fluid mechanics perspective,
+%and so far the modeling attempts have mostly failed~\cite{asgari2016glymphatic, holter2017interstitial, smith2017glymphatic}. 
+%In particular the system seems to facilitate waste transport faster than  
+%the extracellular diffusion, which has been the prevailing paradigm since the pioneering works of \citet{sykova2008diffusion}.
+
+The biomechanical mechanisms are not well understood from a fluid mechanics perspective,
 and so far the modeling attempts have mostly failed~\cite{asgari2016glymphatic, holter2017interstitial, smith2017glymphatic}. 
 In particular the system seems to facilitate waste transport faster than  
-the extracellular diffusion, which has been the prevailing paradigm since the pioneering works of \citet{sykova2008diffusion}.
+the extracellular diffusion, which has been the prevailing paradigm since the pioneering works of \citet{sykova2008diffusion}
 
@@
 
-The pioneering work of Sykov{\'a} and Nicholson~\cite{sykova2008diffusion} demonstrated
-that diffusion was a governing transport mechanism in the brain and estimated to be on the order
-of $1.0\mathrm{e}{-4} \mathrm{mm\sp{2}/s}$ for large molecules.
+The work of Sykov{\'a} and Nicholson~\cite{sykova2008diffusion} demonstrated
+that diffusion was a governing transport mechanism in the brain and with an estimated order of magnitude $1.0\mathrm{e}{-4} \mathrm{mm\sp{2}/s}$ for large molecules.
 This is confirmed with diffusion tensor imaging (DTI) where young and healthy subjects have typical diffusion values in white matter around $0.7-0.9\mathrm{e}{-3} \mathrm{mm\sp{2}/s}$ \citet{Helenius194},
@@
 measured by DTI at a time-scale of 7-30 minutes, may not be representative for the process on a
-longer time-scale, at least if the paravascular pathway plays an important role. The fact that the vascular system occupies around 3\% of the brain volume 
+longer time-scale, at least if the paravascular pathway plays an important role. The fact that the vascular system occupies around X\% of the brain volume 
 and the paravascular network is substantially smaller potentially renders the paravascular transport  invisible at the short time-scales of a DTI acquisition while it may still be effective on longer time scales.
@@
 \includegraphics[width=0.95\textwidth]{PatID-68-new-100.png} 
-\caption{Shows the percentage intensity increase from baseline at different observation times. The colorbar was restricted to the range $(0,100)$.}
+\caption{Shows the percentage change in T1 signal unit ratios from baseline at different observation times.
+The colorbar was restricted to the range $(0,100)$.\fixme{copyright issues}.
+\lars{Reconstructed based on data obtained from \cite{eidevalnes}.
+eller fjerne upper row?
+} }
 \label{fig1} 
@@
 \includegraphics[width=0.95\textwidth]{Zoom-PatID-68.png} 
-\caption{Shows the percentage intensity increase from baseline at different observation times in the slice (marked red in the left panel) used in the subsequent analysis.
+\caption{Shows the percentage change in T1 signal unit ratios from baseline at different observation times in the slice (marked red in the left panel) used in the subsequent analysis.
 The color bar was restricted to the range $(0,100)$.
@@
 \end{figure}
-Figure~\ref{fig1} shows the distribution of tracers during 24 hours, see also~\cite{ringstad2018brain} for further information on the imaging procedure.   
+Figure~\ref{fig1} shows distribution of a CSF tracer, as a percentage change in T1 signal unit ratios, see also~\cite{ringstad2018brain} for further information on the imaging procedure.   
 Our data (not all shown) consist of a total of 10 MRI observations, including a baseline MRI taken before tracer was injected.
@@
 
-The MRI data was part of a larger study, which involves around 100 patients with the same MRI acquisitions.
+%The MRI data was part of a larger study, which involves around 100 patients with the same MRI acquisitions.
 However, there are clinical differences in each patient, thus a thorough analysis is needed to obtain a robust and accurate method.
@@
 the right-most image in Figure~\ref{figuredti} and that these images show the apparent diffusion coefficient for free water molecules (18 Da).      
-The diffusivity of the Gadovist (600 Da \cite{MGadobutrol}) was estimated to be similar to the diffusion coefficient of Gd-DPTA (550 Da \cite{MGgDPTA}).
+The diffusivity of the Gadovist (\fixme{600} Da \cite{MGadobutrol}) was estimated to be similar to the diffusion coefficient of Gd-DPTA (550 Da \cite{MGgDPTA}).
 This is due to the fact that both molecules have similar mass, and based on Stoke-Einstein equation should have similar diffusion coefficients.
@@
 \end{figure}
-The 3 domain mesh in Fig.\ref{Fig::Mesh} A, consists of 244318 tetrahedral cells and 22057 vertices, while the 2 domain mesh (without the CSF compartment) Fig.\ref{Fig::Mesh} B consists of 335589 tetrahedral cells and 73002 vertices.
+The 3 domain mesh in Figure~\ref{Fig::Mesh} A, consists of 244318 tetrahedral cells and 22057 vertices, while the 2 domain mesh (without the CSF compartment) Figure~\ref{Fig::Mesh} B consists of 335589 tetrahedral cells and 73002 vertices.
 %The mesh coordinates (X,Y,Z) are given in $\mathrm{mm}$ \lars{ with $X \in \lbrace -70.5,-18\rbrace, Y \in \lbrace -73.5,28.8  \rbrace ,Z \in \lbrace 16.6,60.7 \rbrace$ }.
@@
 Therefore it would seem that the anisotropy do not have direct impact on the computations, since the computation can not evaluate a static environment.
-Therefore  observation of tracer in regions with anisotropy can be considered a requirement for adding anisotropy to the model.
+Hence observations of tracer in regions with anisotropy can be considered a requirement for adding anisotropy to the model.
 
@@
 It can also be taken into consideration to model the diffusion coefficients as a function in time, given the report of increased clearance in rodents during sleep \cite{xie2013sleep}.
-This would indicate a time-dependent diffusivity, since the clearance in the brain is driven by diffusion.
-The time-dependency would correspond to a change in tortuosity, since properties of the tracer molecule do not change.
+This would indicate a time-dependent diffusivity, given that the clearance in the brain is driven by diffusion.
+%The time-dependency would correspond to a change in tortuosity, since properties of the tracer molecule do not change.
+The hypothesis of the glymphatic system \cite{iliff2012paravascular} states that the waste is cleared through the veins in the parenchyma.
+This gives the tracer additional pathways that is not considered in the computational model.
+These additional pathways can be modeled as a drainage, which can be included as a control source term.
 
@@
 
-The hypothesis of the glymphatic system \cite{iliff2012paravascular} states that the waste is cleared through the veins in the parenchyma.
-This gives the tracer additional pathways that is not considered in the computational model.
-These additional pathways can be modeled as a drainage, which can be included as a control source term.
-
 Previous studies~\cite{holter2017interstitial, smith2017glymphatic} suggest that diffusion dominates in the interstitium. Furthermore, 
@@
 seems significant and it is difficult to explain or ignore.
+
+In summary, using this model, we estimated diffusion coefficients that were 43-100\% larger than estimated by DTI acquisitions.
+Our results indicate that dissipation of solutes along the paravascular rout has a factor of 30, as compared to diffusion alone.
+However, the present study did not examine whether transport is by convective mechanisms.
 

### 2018-10-27 tex/paper.tex
changed text

@@
 In \cite{ringstad2018brain} brain-wide distribution of MRI-contrast was demonstrated during 24 hours after lumbar contrast injection.
-Brain-wide distribution by diffusion alone was deemed unlikely by the authors (some of which are co-authors of this paper).
+Brain-wide distribution by diffusion alone was deemed unlikely by the authors.
 The argument was based on analytical considerations where it was calculated that 50\% contrast enrichment would occur after
@@
 Figure~\ref{fig2} shows the region selected for our computations. 
-The software Freesurfer \cite{Dale1999179, FischlLiuDale, spf2007, reuter:robreg10} was used to segment and align each of the observations, which made it possible to estimate voxelwise intensity increase.
+The software Freesurfer \cite{Dale1999179, FischlLiuDale, spf2007, reuter:robreg10} was used to segment and align each of the observations, which made it possible to estimate voxelwise signal increase.
 
@@
 
-\subsection{Contrast concentration - Image Intensity Relation}
-Below, we briefly describe the relationship between the imaging intensity 
+\subsection{Contrast concentration - Image Signal Relation}
+Below, we briefly describe the relationship between the imaging signal 
 seen in Figures \ref{fig1} and \ref{fig2} and the underlying contrast 
@@
 The tracer observations were collected using a MRI sequence known as  Magnetization Prepared Rapid Acquisition Gradient Echo (MPRAGE) with an inversion prepared magnetization.
-The relation between intensity and the relaxation time is non-linear, and is expressed with the following equations.
-The signal intensity $S$ for this sequence is given by
+The relation between signal and the relaxation time is non-linear, and is expressed with the following equations.
+The signal value $S$ for this sequence is given by
 \begin{equation}
@@
 The center echo denoted as $n=m/2$ will be the signal that we will consider when estimating MRI tracer.
-Given \eqref{EQ::SI} we have that the relative intensity increase can be written as
+Given \eqref{EQ::SI} we have that the relative signal increase can be written as
 \begin{equation}
@@
 \end{equation}
-The intensity difference between observation times were adjusted in \cite{eidevalnes}. Thus we can express the change in $T_1$ due to tracer as 
+The signal difference between observation times were adjusted in \cite{eidevalnes}. Thus we can express the change in $T_1$ due to tracer as 
 \begin{equation}
@@
 This takes into account patients specific characteristic, such as tissue damage.
-Tissue damage can be observed in the MRI due to a lower intensity in the white matter compared to healthy white matter tissue, thus damaged tissue have different $T_1$ relaxation time.
+Tissue damage can be observed in the MRI due to a lower signal in the white matter compared to healthy white matter tissue, thus damaged tissue have different $T_1$ relaxation time.
 The tracer concentration was estimated in a preprocessing step, using the parameters obtained from the T1-map, MPRAGE MRI protocol \cite{eidevalnes} and the value for $r_1$ found in \cite{pmid16230904}.
 In the computation, the function \eqref{scaledmagnetization} was computed for $ T_1\in \lbrace 200, 4000 \rbrace$ creating a lookup table.
-The lookup table was utilized with the baseline intensity increase to estimate $T_1\sp{c}$, and then the concentration was computed using \eqref{EQ::contrast}.
+The lookup table was utilized with the baseline signal increase to estimate $T_1\sp{c}$, and then the concentration was computed using \eqref{EQ::contrast}.
 

### 2018-10-27 tex/paper.tex
changed text

@@
 
-\title{Assessing paravascular transport in the parenchyma by PDE (partial differential equations) constrained optimization.}
+\title{Assessing paravascular transport in the parenchyma by partial differential equation (PDE) constrained optimization.}
 
@@
 \section{Introduction}
-In 2012, Iliff et al ~\citet{iliff2012paravascular} provided evidence for a a brain-wide paravascular system, denoted the glymphatic system, which is a pathway for transport of fluids and solutes.
+In 2012, ~\citet{iliff2012paravascular} provided evidence for a a brain-wide paravascular system, denoted the glymphatic system, which is a pathway for transport of fluids and solutes.
 It was proposed to have an important metabolic role by providing a pathway for clearance of waste solutes from the brain.
@@
 measured by DTI at a time-scale of 7-30 minutes, may not be representative for the process on a
-longer time-scale, at least if the paravascular pathway plays an important role. The fact that the vascular system occupies around X\% of the brain volume 
+longer time-scale, at least if the paravascular pathway plays an important role. The fact that the vascular system occupies around 3\% \fixme{Eide ? } of the brain volume 
 and the paravascular network is substantially smaller potentially renders the paravascular transport  invisible at the short time-scales of a DTI acquisition while it may still be effective on longer time scales.
@@
 the complex geometry of the brain as well as time-scales of hours or days are taken into account.
-That is, we aim to investigate whether we can assess an effective diffusion coefficient on long time-scales (hours or days), by fitting a diffusion model to magnetic resonance imaging (MRI) data.
+%That is,
+Thus we aim to investigate whether we can assess an effective diffusion coefficient on long time-scales (hours or days), by fitting a diffusion model to magnetic resonance imaging (MRI) data.
 If the fit between observation and model is good and we identify diffusion coefficients that are
@@
 the complete domain. Hence, the challenges faced from a mathematical point of view 
-are that 1) the images are subject to noise, 2) resolution in space is limited to slightly less than (1 $\mathrm{mm}^3$ and 3)
-the sparse observations through the time domain.  As such we need to assess the sensitivity of
-the approach with respect to important parameters such as the regularization parameters, noise levels and 
-time resolution to determine whether this approach is a viable method
-to obtain parameters involved time-scales. We remark that the purpose
+are that 1) the images are subject to noise, 2) resolution in space is limited to slightly less than 1 $\mathrm{mm}^3$ and 3)
+the sparse observations through the time domain. 
+Therefore we need to assess the sensitivity of the approach with respect to important factors, such noise levels and time resolution to determine whether this approach is a viable method to obtain parameters involved time-scales.
+
+%As such we need to assess the sensitivity of the approach with respect to important parameters such as the regularization parameters, noise levels and  time resolution to determine whether this approach is a viable method to obtain parameters involved time-scales.
+We remark that the purpose
 of this paper is a systematic study of the mathematical challenges and that assessing  
@@
 and then estimate the concentration using \eqref{EQ::contrast}.
-The $T_{1}\sp{0}$ values were obtained by T1-mapping the brain using a MRI sequence known as MOLLI5(3)3 \cite{TAYLOR201667}.
+The $T_{1}\sp{0}$ values were obtained by T1-mapping of the brain using a MRI sequence known as MOLLI5(3)3 \cite{TAYLOR201667}.
 This takes into account patients specific characteristic, such as tissue damage.
@@
 coefficients on short time-scales. Images are shown in Figure~\ref{figuredti} where the largest diffusion coefficient (shown in 
-red in the middle figure) is shown to be around $1.0\mathrm{e}{-3} mm^2/s$. We remark that we have not included possible anisotropy, shown in 
+red in the middle figure) is shown to be around $1.0\mathrm{e}{-3}  \mathrm{mm^2/s}$. We remark that we have not included possible anisotropy, shown in 
 the right-most image in Figure~\ref{figuredti} and that these images show the apparent diffusion coefficient for free water molecules (18 Da).      
 The diffusivity of the Gadovist (\fixme{600} Da \cite{MGadobutrol}) was estimated to be similar to the diffusion coefficient of Gd-DPTA (550 Da \cite{MGgDPTA}).
-This is due to the fact that both molecules have similar mass, and based on Stoke-Einstein equation should have similar diffusion coefficients.
+This is due to the fact that both molecules have similar mass, and based on Stoke-Einstein equation should also have similar diffusion coefficients.
 The free diffusion coefficient for Gd-DPTA was estimated in \citet{GdDPTA-DIFFUSION} to be $3.8\mathrm{e}{-4}\mathrm{mm\sp{2}/s}$.
@@
 In order to estimate the apparent diffusion coefficient involved in the tracer transportation shown in Figure~\ref{fig1} we assume that the process can be modeled by a diffusion equation. 
-Then we solve a PDE constrained optimization problem where
-the tracer distribution, boundary conditions, and apparent
-diffusion coefficient are solved for by optimizing with
-respect to the observed tracer distribution. As such, enhanced transportation because of effects such as
-dissipation would result in an apparent diffusion coefficient larger than that predicted by DTI.  
-The objective function was defined as 
+Then we constructed an optimization problem with the aim to minimize the difference between the observed and the modeled tracer distribution by optimizing the boundary conditions and the apparent diffusion coefficient.%Then we solve a PDE constrained optimization problem where the tracer distribution, boundary conditions, and apparent diffusion coefficient are solved for by optimizing with respect to the observed tracer distribution \lars{Ikke helt oversiktlig}.
+Thus enhanced transportation because of effects such as dissipation would result in an apparent diffusion coefficient larger than that predicted by DTI.The objective function was defined as 
 \begin{equation}
@@
 \frac{\partial u}{\partial t} &= \nabla \cdot  D \nabla u && \text{in} \qquad \Omega \times \left\lbrace 0 , T \right)  \\
-u&=g && \text{on} \qquad \partial\Omega_1  \times \left\lbrace 0 , T \right) 
+u&=g && \text{on} \qquad \partial\Omega  \times \left\lbrace 0 , T \right) 
 \end{aligned}
@@
 Furthermore, the computational cost will rise with additional time-steps.
-Thus finding the optimal number of time-steps can be essential for larger problems.
+Thus finding the optimal number of time-steps can be essential for solving larger problems.
 The computation used a wide range the regularization parameters, and the number of timesteps were selected to be 20 and 40.
@@
 Figure~\ref{12hourswithnoise} and Figure~\ref{24hourswithnoise} show the reconstruction of the manufactured solution at
-different noise levels with $\alpha=0.0001$ and $\beta=1.0$. Clearly, the reconstruction shown in the lower rows is quite robust with respect to the various levels
+different noise levels with $\alpha=0.0001$,$\beta=1.0$ and $k=20$. Clearly, the reconstruction shown in the lower rows is quite robust with respect to the various levels
 of noise shown in the upper rows.
@@
 The noise caused the number of iteration to increase, and with more timesteps caused the optimization not to convergence for $\beta < 1.0$.
-Furthermore, the relative boundary error $||g||\sp{rel}_{L\sp{2}(\Omega_1)}$ is significantly larger for $\alpha< 1.0\mathrm{e}{-2} $ and $\beta < 1.0\mathrm{e}{-2}$.
+Furthermore, the relative boundary error $||g||\sp{rel}$ is significantly larger for $\alpha< 1.0\mathrm{e}{-2} $ and $\beta < 1.0\mathrm{e}{-2}$.
 
@@
 The MRI data consisted of the observations at times $t_i \in \lbrace$ 0.00, 0.16, 0.39, 0.55, 0.77, 2.09, 6.05, 24., 48., 698.
-$\rbrace (hours)$ with the time $t_i=0.00$ as the observation 1-2 hours after the tracer was injected.
+$\rbrace \mathrm{(hours)}$ with the time $t_i=0.00$ as the observation 1-2 hours after the tracer was injected.
 There was no significant visible change in the tracer between the observations at $\lbrace $ 0.00, 0.16, 0.39, 0.55, 0.77 $ \rbrace$.
@@
 Furthermore, bounds were added to the L-BFGS-B algorithm to ensure non-negative boundary controls and the convergence criteria was adjusted so that the optimization was stopped when the $L^\infty$-norm of the projected gradient of the objective functional dropped below $6.0\mathrm{e}{-1}$.
-The number of timesteps were selected to be $k=24$ and $k=48$, which gives $dt = 2 hour$ and $dt = 1 hour$.
+The number of timesteps were selected to be $k=24$ and $k=48$, which gives $dt = 2 \mathrm{h}$ and $dt = 1 \mathrm{h}$.
 
@@
 Then the reference value $3.8\mathrm{e}{-4} \mathrm{mm\sp{2}/s}$ for Gd-DPTA gives an estimate for the apparent diffusion coefficient in the grey and white matter to  be $ 1.26\mathrm{e}{-4}\mathrm{mm\sp{2}/s}$ and $1.10\mathrm{e}{-4} \mathrm{mm\sp{2}/s}$ respectively.
-This estimation assumes that the tortuosity is independent on molecular size.
+This estimation assumes that the tortuosity is independent for molecules with mass lower than 1kDa.
 
@@
 Furthermore, we can see that for $\alpha=1.0\mathrm{e}{-2}$ there is a clear discrepancy in the diffusion coefficients compared to other values $\alpha$.
-This prompt the exclusion of these values, which gives an average computed values $ 0.65 \mathrm{mm\sp{2}/h}$ and  $ 0.8 \mathrm{mm\sp{2}/h}$ in grey and white matter.
+Excluding the values with $\alpha=1.0\mathrm{e}{-2}$ gives an average of $ 0.65 \mathrm{mm\sp{2}/h}$ in grey matter and $ 0.8 \mathrm{mm\sp{2}/h}$ in and white matter.
 Scaled to $\mathrm{mm\sp{2}/s}$ gives the corresponding values $1.8\mathrm{e}{-4}\mathrm{mm\sp{2}/s}$ and $2.22\mathrm{e}{-4} \mathrm{mm\sp{2}/s}$.
@@
 well for regularization parameters varying by orders of magnitude.
-The regularization parameters  $\alpha \in \lbrace 1.0e-6, 1.0\mathrm{e}{-2} \rbrace$, $\beta \in \lbrace 1.0\mathrm{e}{-2} , 1.0 \rbrace$ with the requirement $\alpha / \beta < 1.0\mathrm{e}{-2}$ gave a relative error of
+The regularization parameters  $\alpha \in \lbrace 1.0\mathrm{e-6}, 1.0\mathrm{e}{-2} \rbrace$, $\beta \in \lbrace 1.0\mathrm{e}{-2} , 1.0 \rbrace$ with the requirement $\alpha / \beta < 1.0\mathrm{e}{-2}$ gave a relative error of
 4.1\% in grey matter and 3.6 \% in white matter. It is particularly interesting to see that the procedure efficiently removes noise as demonstrated
@@
 the values used with \eqref{tortuosity} must be taken with caution. Furthermore,    
-the computational model assumes isotropic diffusivity, but the anisotropy in the white matter is well documented, as shown by the FA in Fig\ref{figuredti}.
+the computational model assumes isotropic diffusivity, but the anisotropy in the white matter is well documented, as shown by the FA in Figure~\ref{figuredti}.
 It can be seen in Figure~\ref{Fig::realdata} that the region with high FA have negligible amounts of tracer present.
 Therefore it would seem that the anisotropy do not have direct impact on the computations, since the computation can not evaluate a static environment.
-Hence observations of tracer in regions with anisotropy can be considered a requirement for adding anisotropy to the model.
+Thus observations of tracer in regions with anisotropy can be considered a requirement before adding anisotropy to the model.
 
-The computational model uses 2 global controls for the diffusion coefficients, while it can be seen in  Fig.\ref{figuredti} that diffusion coefficients can be considered a spacial function.
+The computational model uses 2 global controls for the diffusion coefficients, while it can be seen in  Figure~\ref{figuredti} that diffusion coefficients can be considered a spacial function.
 However, the implementation of control parameters for each degree of freedom would significantly increase the computational cost.
@@
 
-In Tab.\ref{Tab::Real-data}, it is shown that the grey matter diffusion coefficient have a consistent increase based on the decrease in the relaxation parameter $\beta$.
-This can be caused by the boundary control $g$, which exists along the entire boundary of the grey matter.
-Considering that the grey matter volume has a depth less than 3 mm makes it susceptible to changes in $g$.
+In Tab.\ref{Tab::Real-data}, it was shown that the grey matter diffusion coefficient had a negative correlation with the relaxation parameter $\beta$.
+This was caused by the boundary control $g$, which exists along the entire boundary of the grey matter.
+Considering that the grey matter volume has an average thickness less than 3 mm makes it susceptible to changes in $g$.
 This can be observed in the reconstruction in Fig.\ref{12hourswithnoise} and Fig.\ref{24hourswithnoise}, where the noise is present at the boundary.
@@
 Row B) shows the corresponding states with the relaxation parameters $\alpha=0.01$ and $\beta=0.01$ and $k=48$.
-Row C) shows the corresponding states with the relaxation parameters $\alpha=0.0001$ and $\beta=1.0$ and $k=48$
- Row D) shows the corresponding states with the relaxation parameters $\alpha=1.0e-6$ and $\beta=0.1$ and $k=48$. The color-bar was restricted to the range $ \lbrace 0 ,0.5 \rbrace$. }
+Row C) shows the corresponding states with the relaxation parameters $\alpha=1.0\mathrm{e-4}$ and $\beta=1.0$ and $k=48$
+ Row D) shows the corresponding states with the relaxation parameters $\alpha=1.0\mathrm{e-6}$ and $\beta=0.1$ and $k=48$. The color-bar was restricted to the range $ \lbrace 0 ,0.5 \rbrace$. }
 \label{Fig::realdata}

### 2018-10-27 tex/paper.tex
changed text

@@
 the right-most image in Figure~\ref{figuredti} and that these images show the apparent diffusion coefficient for free water molecules (18 Da).      
-The diffusivity of the Gadovist (\fixme{600} Da \cite{MGadobutrol}) was estimated to be similar to the diffusion coefficient of Gd-DPTA (550 Da \cite{MGgDPTA}).
+The diffusivity of the Gadovist \cite{MGadobutrol} was estimated to be similar to the diffusion coefficient of Gd-DPTA (550 Da \cite{MGgDPTA}).
 This is due to the fact that both molecules have similar mass, and based on Stoke-Einstein equation should also have similar diffusion coefficients.

### 2018-10-28 tex/paper.tex
Supplementary added

@@
 More specifically, for $\alpha \leq 1\mathrm{e}{-2}$ and $\beta \leq 1e-0$ the relative errors for all optimization parameters are below $5\%$.However, in the case of $ \alpha=1.0$ the relative error is over 100\% higher then for other values of $\alpha$.
-Furthermore, for all $\beta=100.0$ there is about 70\% relative error for $D_{\Omega_1}$ and approximate 10\% error for $D_{\Omega_2}$ .
-
+Furthermore, for all $\beta=100.0$ there is about 70\% relative error for $D_{\Omega_1}$ and approximate 10\% error for $D_{\Omega_2}$.
 From the results it can be discerned that $\alpha =1.0$ and $\beta=100.0$ represent an upper threshold where the observations are no longer the dominant term in the objective functional.
@@
 
+\begin{figure}
+\centering
+\includegraphics[scale=0.21]{boundary_control.png}  
+\caption{ Displays plots over time for a selection of points at the boundary of $\Omega_1$ with different regularization parameters and number of timesteps $k$.
+The left panel shows the legend for the plot over time, together with the selection of points.
+The middle panel shows the average boundary value $g$ for different regularization parameter with $k=10$.
+The right panel shows the average boundary value $g$ for different regularization parameter with $k=40$.
+}
+\label{boundarycontrol}
+\end{figure}
+
 \subsubsection{The number of observations}
@@
 %In Table ~\ref{TAB::double}, we can see that $\aplha < 1.0e-2$ and $\beta =1.0e-2$ have a drastic change in the number of iteration for $20$ time-steps.
-
-\begin{figure}
-\centering
-\includegraphics[scale=0.21]{boundary_control.png}  
-\caption{ Displays plots over time for a selection of points at the boundary of $\Omega_1$ with different regularization parameters and number of timesteps $k$.
-The left panel shows the legend for the plot over time, together with the selection of points.
-The middle panel shows the average boundary value $g$ for different regularization parameter with $k=10$.
-The right panel shows the average boundary value $g$ for different regularization parameter with $k=40$.
-}
-\label{boundarycontrol}
-\end{figure}
 
@@
 
-In Tab.\ref{Tab::Real-data}, it was shown that the grey matter diffusion coefficient had a negative correlation with the relaxation parameter $\beta$.
+In Table~\ref{Tab::Real-data}, it was shown that the grey matter diffusion coefficient had a negative correlation with the relaxation parameter $\beta$.
 This was caused by the boundary control $g$, which exists along the entire boundary of the grey matter.
@@
 
+\begin{table}[t]
+\centering
+\caption{Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$, the resulting number of iterations, the relative error of the estimated optimal parameters for the diffusion coefficients and the relative error for $g$.
+The noise amplitude was set to 0.3, and $t_i =[2.4, 4.8, 7.2, 9.6, 12.0, 14.4, 16.8, 19.2, 21.6, 24.0]$  }
+\begin{tabular}{*{8}c}
+$\alpha$ & $\beta$ & k  & iter & $ D_{\Omega_1}\sp{rel}$ & $D_{\Omega_2}\sp{rel} $ & $D_{\Omega_3}\sp{rel} $ & $|| g ||\sp{rel} $ \\
+\hline
+ 1.0e-02 	 & 1.0e+00 	 & 10 & 144 	 & +0.012 & +0.055 & +0.027 & +0.036 \\ 
+ 1.0e-02 	 & 1.0e-02 	 & 10 & 476 	 & -0.009 & +0.049 & +0.035 & +0.051 \\ 
+ 1.0e-02 	 & 1.0e-04 	 & 10 & 476 	 & -0.097 & +0.042 & +0.054 & +0.054 \\ 
+ 1.0e-02 	 & 1.0e-06 	 & 10 & 558 	 & -0.071 & +0.047 & +0.039 & +0.054 \\ 
+ 1.0e-04 	 & 1.0e+00 	 & 10 & 182 	 & -0.040 & +0.033 & +0.051 & +0.037 \\ 
+ 1.0e-04 	 & 1.0e-02 	 & 10 & 471 	 & +0.021 & +0.038 & +0.036 & +0.056 \\ 
+ 1.0e-04 	 & 1.0e-04 	 & 10 & 792 	 & -0.058 & +0.042 & +0.031 & +0.565 \\ 
+ 1.0e-04 	 & 1.0e-06 	 & 10 &  -   & -0.050 & +0.029 & +0.040 & +1.062 \\ 
+ 1.0e-06 	 & 1.0e+00 	 & 10 & 178 	 & +0.012 & +0.033 & +0.021 & +0.036 \\ 
+ 1.0e-06 	 & 1.0e-02 	 & 10 & 537 	 & -0.018 & +0.040 & +0.025 & +0.057 \\ 
+ 1.0e-06 	 & 1.0e-04 	 & 10 &  -	 & -0.038 & +0.040 & +0.030 & +1.452 \\ 
+ 1.0e-06 	 & 1.0e-06 	 & 10 &  - 	 & +0.003 & +0.035 & +0.046 & +3.621 \\ 
+ 1.0e-02 	 & 1.0e+00 	 & 20 & 213 	 & +0.009 & +0.015 & +0.009 & +0.016 \\ 
+ 1.0e-02 	 & 1.0e-02 	 & 20 & 719 	 & +0.228 & +0.088 & -0.032 & +0.085 \\ 
+ 1.0e-02 	 & 1.0e-04 	 & 20 &  -   & +0.100 & +0.071 & -0.013 & +0.271 \\ 
+ 1.0e-02 	 & 1.0e-06 	 & 20 &   -  & +0.223 & +0.097 & -0.027 & +0.282 \\ 
+ 1.0e-04 	 & 1.0e+00 	 & 20 & 245 	 & +0.038 & +0.013 & -0.001 & +0.016 \\ 
+ 1.0e-04 	 & 1.0e-02 	 & 20 &  - 	 & +0.050 & +0.054 & -0.024 & +0.116 \\ 
+ 1.0e-04 	 & 1.0e-04 	 & 20 &  - 	 & -0.087 & +0.059 & -0.077 & +5.763 \\ 
+ 1.0e-04 	 & 1.0e-06 	 & 20 &  -	 & +0.001 & +0.083 & -0.038 & +7.485 \\ 
+ 1.0e-06 	 & 1.0e+00 	 & 20 & 242 	 & -0.009 & +0.008 & +0.015 & +0.016 \\ 
+ 1.0e-06 	 & 1.0e-02 	 & 20 & 947 	 & +0.122 & +0.093 & -0.040 & +0.115 \\ 
+ 1.0e-06 	 & 1.0e-04 	 & 20 &  - 	 & -0.076 & +0.041 & -0.020 & +7.700 \\ 
+ 1.0e-06 	 & 1.0e-06 	 & 20 &  - 	 & +0.147 & +0.113 & -0.023 & +10.936 \\
+
+\end{tabular}
+\label{Tab::Noise0.3}
+\end{table}
+
+\begin{table}
+\centering
+\caption{Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$, the resulting number of iterations, the estimated diffusion coefficients for grey $D_{\Omega_{GM}}$ and white $D_{\Omega_{WM}}$ matter based on MRI data.}
+\begin{tabular}{*{6}c}
+$\alpha$ & $\beta$ & k & iter &  $ D_{\Omega_{GM}} \left[ \mathrm{mm\sp{2}/h} \right] $ & $ D_{\Omega_{WM}} \left[ \mathrm{mm\sp{2}/h} \right]$ \\
+\hline
+ 1.0e-02 	 & 1.0e+00 	 & 24 & 503 	 & 0.659 & 0.918 \\ 
+ 1.0e-02 	 & 1.0e-01 	 & 24 & 716 	 & 0.771 & 0.969 \\ 
+ 1.0e-02 	 & 1.0e-02 	 & 24 & 505 	 & 0.836 & 0.974 \\ 
+ 1.0e-04 	 & 1.0e+00 	 & 24 & 206 	 & 0.553 & 0.828 \\ 
+ 1.0e-04 	 & 1.0e-01 	 & 24 & 440 	 & 0.651 & 0.789 \\ 
+ 1.0e-04 	 & 1.0e-02 	 & 24 & 597 	 & 0.718 & 0.739 \\ 
+ 1.0e-06 	 & 1.0e+00 	 & 24 & 439 	 & 0.570 & 0.830 \\ 
+ 1.0e-06 	 & 1.0e-01 	 & 24 & 583 	 & 0.656 & 0.793 \\ 
+ 1.0e-06 	 & 1.0e-02 	 & 24 & 742 	 & 0.721 & 0.729 \\
+
+ %1.0e-02    & 1.0e+02   & 48 & 714      & 0.564 & 0.952 ?? \\ 
+ 1.0e-02 	 & 1.0e+00 	 & 48 & 591 	 & 0.648 & 0.893 \\ 
+ 1.0e-02 	 & 1.0e-01 	 & 48 & 461 	 & 0.772 & 0.982 \\ 
+ 1.0e-02 	 & 1.0e-02 	 & 48 & 748 	 & 0.986 & 1.198 \\ 
+ %1.0e-04    & 1.0e+02   & 48 & 815      & 0.470 & 0.928 \\ 
+ 1.0e-04 	 & 1.0e+00 	 & 48 & 607 	 & 0.551 & 0.815 \\ 
+ 1.0e-04 	 & 1.0e-01 	 & 48 & 598 	 & 0.649 & 0.787 \\ 
+ 1.0e-04 	 & 1.0e-02 	 & 48 & 837 	 & 0.740 & 0.817 \\
+ %1.0e-06    & 1.0e+02   & 48 & 729      & 0.428 & 0.948 \\ 
+ 1.0e-06 	 & 1.0e+00 	 & 48 & 681 	 & 0.557 & 0.811 \\ 
+ 1.0e-06 	 & 1.0e-01 	 & 48 & 780 	 & 0.645 & 0.774 \\ 
+ 1.0e-06 	 & 1.0e-02 	 & 48 & 745 	 & 0.736 & 0.819 \\
+
+\end{tabular}
+\label{Tab::Real-data}
+\end{table}
+
+\section{Supplementary}
 \begin{table}
@@
 \end{table}
-\begin{table}[t]
-\centering
-\caption{Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$, the resulting number of iterations, the relative error of the estimated optimal parameters for the diffusion coefficients and the relative error for $g$.
-The noise amplitude was set to 0.3, and $t_i =[2.4, 4.8, 7.2, 9.6, 12.0, 14.4, 16.8, 19.2, 21.6, 24.0]$  }
-\begin{tabular}{*{8}c}
-$\alpha$ & $\beta$ & k  & iter & $ D_{\Omega_1}\sp{rel}$ & $D_{\Omega_2}\sp{rel} $ & $D_{\Omega_3}\sp{rel} $ & $|| g ||\sp{rel} $ \\
-\hline
- 1.0e-02 	 & 1.0e+00 	 & 10 & 144 	 & +0.012 & +0.055 & +0.027 & +0.036 \\ 
- 1.0e-02 	 & 1.0e-02 	 & 10 & 476 	 & -0.009 & +0.049 & +0.035 & +0.051 \\ 
- 1.0e-02 	 & 1.0e-04 	 & 10 & 476 	 & -0.097 & +0.042 & +0.054 & +0.054 \\ 
- 1.0e-02 	 & 1.0e-06 	 & 10 & 558 	 & -0.071 & +0.047 & +0.039 & +0.054 \\ 
- 1.0e-04 	 & 1.0e+00 	 & 10 & 182 	 & -0.040 & +0.033 & +0.051 & +0.037 \\ 
- 1.0e-04 	 & 1.0e-02 	 & 10 & 471 	 & +0.021 & +0.038 & +0.036 & +0.056 \\ 
- 1.0e-04 	 & 1.0e-04 	 & 10 & 792 	 & -0.058 & +0.042 & +0.031 & +0.565 \\ 
- 1.0e-04 	 & 1.0e-06 	 & 10 &  -   & -0.050 & +0.029 & +0.040 & +1.062 \\ 
- 1.0e-06 	 & 1.0e+00 	 & 10 & 178 	 & +0.012 & +0.033 & +0.021 & +0.036 \\ 
- 1.0e-06 	 & 1.0e-02 	 & 10 & 537 	 & -0.018 & +0.040 & +0.025 & +0.057 \\ 
- 1.0e-06 	 & 1.0e-04 	 & 10 &  -	 & -0.038 & +0.040 & +0.030 & +1.452 \\ 
- 1.0e-06 	 & 1.0e-06 	 & 10 &  - 	 & +0.003 & +0.035 & +0.046 & +3.621 \\ 
- 1.0e-02 	 & 1.0e+00 	 & 20 & 213 	 & +0.009 & +0.015 & +0.009 & +0.016 \\ 
- 1.0e-02 	 & 1.0e-02 	 & 20 & 719 	 & +0.228 & +0.088 & -0.032 & +0.085 \\ 
- 1.0e-02 	 & 1.0e-04 	 & 20 &  -   & +0.100 & +0.071 & -0.013 & +0.271 \\ 
- 1.0e-02 	 & 1.0e-06 	 & 20 &   -  & +0.223 & +0.097 & -0.027 & +0.282 \\ 
- 1.0e-04 	 & 1.0e+00 	 & 20 & 245 	 & +0.038 & +0.013 & -0.001 & +0.016 \\ 
- 1.0e-04 	 & 1.0e-02 	 & 20 &  - 	 & +0.050 & +0.054 & -0.024 & +0.116 \\ 
- 1.0e-04 	 & 1.0e-04 	 & 20 &  - 	 & -0.087 & +0.059 & -0.077 & +5.763 \\ 
- 1.0e-04 	 & 1.0e-06 	 & 20 &  -	 & +0.001 & +0.083 & -0.038 & +7.485 \\ 
- 1.0e-06 	 & 1.0e+00 	 & 20 & 242 	 & -0.009 & +0.008 & +0.015 & +0.016 \\ 
- 1.0e-06 	 & 1.0e-02 	 & 20 & 947 	 & +0.122 & +0.093 & -0.040 & +0.115 \\ 
- 1.0e-06 	 & 1.0e-04 	 & 20 &  - 	 & -0.076 & +0.041 & -0.020 & +7.700 \\ 
- 1.0e-06 	 & 1.0e-06 	 & 20 &  - 	 & +0.147 & +0.113 & -0.023 & +10.936 \\
-
-\end{tabular}
-\label{Tab::Noise0.3}
-\end{table}
-
-\begin{table}
-\centering
-\caption{Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$, the resulting number of iterations, the estimated diffusion coefficients for grey $D_{\Omega_{GM}}$ and white $D_{\Omega_{WM}}$ matter based on MRI data.}
-\begin{tabular}{*{6}c}
-$\alpha$ & $\beta$ & k & iter &  $ D_{\Omega_{GM}} \left[ \mathrm{mm\sp{2}/h} \right] $ & $ D_{\Omega_{WM}} \left[ \mathrm{mm\sp{2}/h} \right]$ \\
-\hline
- 1.0e-02 	 & 1.0e+00 	 & 24 & 503 	 & 0.659 & 0.918 \\ 
- 1.0e-02 	 & 1.0e-01 	 & 24 & 716 	 & 0.771 & 0.969 \\ 
- 1.0e-02 	 & 1.0e-02 	 & 24 & 505 	 & 0.836 & 0.974 \\ 
- 1.0e-04 	 & 1.0e+00 	 & 24 & 206 	 & 0.553 & 0.828 \\ 
- 1.0e-04 	 & 1.0e-01 	 & 24 & 440 	 & 0.651 & 0.789 \\ 
- 1.0e-04 	 & 1.0e-02 	 & 24 & 597 	 & 0.718 & 0.739 \\ 
- 1.0e-06 	 & 1.0e+00 	 & 24 & 439 	 & 0.570 & 0.830 \\ 
- 1.0e-06 	 & 1.0e-01 	 & 24 & 583 	 & 0.656 & 0.793 \\ 
- 1.0e-06 	 & 1.0e-02 	 & 24 & 742 	 & 0.721 & 0.729 \\
-
- %1.0e-02    & 1.0e+02   & 48 & 714      & 0.564 & 0.952 ?? \\ 
- 1.0e-02 	 & 1.0e+00 	 & 48 & 591 	 & 0.648 & 0.893 \\ 
- 1.0e-02 	 & 1.0e-01 	 & 48 & 461 	 & 0.772 & 0.982 \\ 
- 1.0e-02 	 & 1.0e-02 	 & 48 & 748 	 & 0.986 & 1.198 \\ 
- %1.0e-04    & 1.0e+02   & 48 & 815      & 0.470 & 0.928 \\ 
- 1.0e-04 	 & 1.0e+00 	 & 48 & 607 	 & 0.551 & 0.815 \\ 
- 1.0e-04 	 & 1.0e-01 	 & 48 & 598 	 & 0.649 & 0.787 \\ 
- 1.0e-04 	 & 1.0e-02 	 & 48 & 837 	 & 0.740 & 0.817 \\
- %1.0e-06    & 1.0e+02   & 48 & 729      & 0.428 & 0.948 \\ 
- 1.0e-06 	 & 1.0e+00 	 & 48 & 681 	 & 0.557 & 0.811 \\ 
- 1.0e-06 	 & 1.0e-01 	 & 48 & 780 	 & 0.645 & 0.774 \\ 
- 1.0e-06 	 & 1.0e-02 	 & 48 & 745 	 & 0.736 & 0.819 \\
-
-\end{tabular}
-\label{Tab::Real-data}
-\end{table}
 

### 2018-10-28 tex/paper.tex
Moved text to supplementary

@@
 measured by DTI at a time-scale of 7-30 minutes, may not be representative for the process on a
-longer time-scale, at least if the paravascular pathway plays an important role. The fact that the vascular system occupies around 3\% \fixme{Eide ? } of the brain volume 
+longer time-scale, at least if the paravascular pathway plays an important role. The fact that the vascular system occupies around 3\% of the brain volume  \cite{nicholson2001diffusion},
 and the paravascular network is substantially smaller potentially renders the paravascular transport  invisible at the short time-scales of a DTI acquisition while it may still be effective on longer time scales.
@@
 \includegraphics[width=0.95\textwidth]{PatID-68-new-100.png} 
-\caption{Shows the percentage change in T1 signal unit ratios from baseline at different observation times.
-The colorbar was restricted to the range $(0,100)$.\fixme{copyright issues}.
-\lars{Reconstructed based on data obtained from \cite{eidevalnes}.
-eller fjerne upper row?
-} }
+\caption{Shows the percentage change in T1 signal unit ratios from baseline at different observation times. The colorbar was restricted to the range $(0,100)$. }
 \label{fig1} 
@@
 the right-most image in Figure~\ref{figuredti} and that these images show the apparent diffusion coefficient for free water molecules (18 Da).      
-The diffusivity of the Gadovist \cite{MGadobutrol} was estimated to be similar to the diffusion coefficient of Gd-DPTA (550 Da \cite{MGgDPTA}).
+The diffusivity of the Gadovist (600 Da) \cite{MGadobutrol} was estimated to be similar to the diffusion coefficient of Gd-DPTA (550 Da) \cite{MGgDPTA}.
 This is due to the fact that both molecules have similar mass, and based on Stoke-Einstein equation should also have similar diffusion coefficients.
@@
 CGAL \cite{cgal:rty-m3-18b} was used to combine the polyhedral surfaces and to construct the mesh.
-The computational requirement for the resulting mesh was significant, therefore two submeshes was also constructed, see Fig.\ref{Fig::Mesh}.
+The computational requirement for the resulting mesh was significant, therefore two submeshes was also constructed, see Figure~\ref{Fig::Mesh}.
 \begin{figure}
@@
 
-\subsubsection{The number of timessteps}
-Increasing the number of time-steps in the computations can potentially allow for a more accurate temporal reconstruction, but at the same time the number of observations per control decreases and the regularization may therefore play a larger role.
-Furthermore, the computational cost will rise with additional time-steps.
-Thus finding the optimal number of time-steps can be essential for solving larger problems.
-The computation used a wide range the regularization parameters, and the number of timesteps were selected to be 20 and 40.
-
-The results are given in Table~\ref{TAB::timesteps}.
-It can be seen for all $\alpha=1.0$ that the relative error becomes bigger with more time-steps.
-This behavior can also be seen for $\alpha=1.0\mathrm{e}{-2}$ and $\beta < 1.0\mathrm{e}{-2}$, which implies an interaction between the regularization parameters.
-Therefore $g$ was investigated by plotting boundary points through time for different values of $\alpha$ and $\beta$, see Fig \ref{boundarycontrol}.
-In Figure \ref{boundarycontrol} we can see that more time-steps causes oscillations for $\alpha=1.0$, and each peak corresponds to a observation time.
+In Figure~\ref{boundarycontrol} we can see that more time-steps causes oscillations for $\alpha=1.0$, and each peak corresponds to a observation time.
 These oscillations are caused by the value selection of $\alpha$, which tries minimize $g$ between observation times.
@@
 
-\subsubsection{The number of observations}
-The dependency on observations is relevant, since the number of observations of the MRI data is limited.
-This dependency was investigated by changing the number of observations, and by examining the results.
-The number of observation were chosen to be 5 and 20, and the observation times were evenly spaced.
-
-The results for 5 observations is shown in Table~\ref{TAB::half} and for 20 observations is shown in Table~\ref{TAB::double}.
-In Table~\ref{TAB::half}, the values $\alpha =1.0\mathrm{e}{-2}$ and $\beta<1.0$ gives a surge in the relative error with more time-steps.
-This behavior is neither visible in Tab.\ref{TAB::timesteps} or in  Tab.\ref{TAB::double} for the same regularization parameters.
-The ratio observations per control indicates that the increase in relative error is due to oscillations, similar to those seen in Figure~\ref{boundarycontrol}.
-Thus the observations acts as stabilization for the functional, which gives a broader range of adequate regularization parameters.
-
 %In Table ~\ref{TAB::double}, we can see that $\aplha < 1.0e-2$ and $\beta =1.0e-2$ have a drastic change in the number of iteration for $20$ time-steps.
@@
 of noise shown in the upper rows.      
-
-In Table~\ref{Tab::Noise0.03}, we can see that a noise amplitude of 0.03, (10$\%$ of maximum initial condition) had negligible effect on the relative errors compared zero noise in Table~\ref{Tab::1} and Table~\ref{TAB::timesteps}.
-Then in Table~\ref{Tab::Noise0.3} the noise amplitude was increased to 0.3 (100$\%$ of maximum initial condition), which gave a visible effect.
+In Table~\ref{Tab::Noise0.3} the noise amplitude was set to 0.3 (100$\%$ of maximum initial condition), which gave a visible effect.
 The noise caused the number of iteration to increase, and with more timesteps caused the optimization not to convergence for $\beta < 1.0$.
@@
 The estimation of tracer concentration proved difficult in the CSF compartment.
-Therefore the 2 domain mesh, shown in Fig.\ref{Fig::Mesh} was used in the computation.
+Therefore the 2 domain mesh, shown in Figure~\ref{Fig::Mesh} was used in the computation.
 The boundary control was set to the external boundary of both domains, and the subscript in $D_{\Omega_{GM}}$ and $D_{\Omega_{WM}}$ denotes grey and white matter diffusion coefficients.
@@
 
-The results are shown in Tab.\ref{Tab::Real-data}, and the observations after 12 and 48 hours were compared with the corresponding states in Figure~\ref{Fig::realdata}.
-From Table~\ref{Tab::Real-data},it can be observed that $D_{\Omega_{WM}}$ has 24\% higher value on average for $\alpha =1.0\mathrm{e}{-2}$.
+The results are shown in Table~\ref{Tab::Real-data}, and the observations after 12 and 48 hours were compared with the corresponding states in Figure~\ref{Fig::realdata}.
+From Table~\ref{Tab::Real-data}, it can be observed that $D_{\Omega_{WM}}$ has 24\% higher value on average for $\alpha =1.0\mathrm{e}{-2}$.
 It can also be observed that the $D_{\Omega_{GM}}$ have a consistent increases with a decreasing $\beta$.
@@
 
-The oscillation in Fig.\ref{boundarycontrol} showed a large discrepancy in the states between observations.
+The oscillation in Figure~\ref{boundarycontrol} showed a large discrepancy in the states between observations.
 Therefore the states with $k=48$ were examined after 36 hours, see Figure\ref{statecomparison}.
@@
 
-In Fig.\ref{Fig::realdata}, it can be seen that there were regions with negligible amount of tracers and vice versa.
+In Figure~\ref{Fig::realdata}, it can be seen that there were regions with negligible amount of tracers and vice versa.
 The regions with above average amount of tracers corresponds with high diffusivity regions in Figure~\ref{figuredti}.
@@
 Considering that the grey matter volume has an average thickness less than 3 mm makes it susceptible to changes in $g$.
-This can be observed in the reconstruction in Fig.\ref{12hourswithnoise} and Fig.\ref{24hourswithnoise}, where the noise is present at the boundary.
+This can be observed in the reconstruction in Figure~\ref{12hourswithnoise} and Figure~\ref{24hourswithnoise}, where the noise is present at the boundary.
 
@@
 \caption{Shows the regularization parameters $\alpha$ and $\beta$, number of timesteps $k$ with the resulting number of optimization iterations and the relative error for the control parameters.
-The observations times were chosen $ t_i=[2.4, 4.8,$ 7.2, 9.6, 12.0, 14.4, $16.8, 19.2, 21.6, 24.0]$ }
+The observations times were chosen $ t_i=[2.4, 4.8,$ 7.2, 9.6, 12.0, 14.4, $16.8, 19.2, 21.6, 24.0]$.}
 \begin{tabular}{*{8}c}
@@
  1.0e+00 	 & 1.0e-06 	 & 10 & 133 	 & +1.603 & +0.223 & +0.089 & +0.119 \\
- \hline
+
  1.0e-02 	 & 1.0e+02 	 & 10 & 186 	 & +0.649 & +0.111 & +0.036 & +0.033 \\ 
@@
  1.0e-02 	 & 1.0e-06 	 & 10 & 154 	 & -0.039 & +0.039 & +0.036 & +0.026 \\
- \hline
+
  1.0e-04 	 & 1.0e+02 	 & 10 & 212 	 & +0.636 & +0.108 & +0.035 & +0.032 \\ 
@@
  1.0e-04 	 & 1.0e-06 	 & 10 & 142 	 & -0.047 & +0.037 & +0.036 & +0.026 \\
- \hline
+
  1.0e-06 	 & 1.0e+02 	 & 10 & 203 	 & +0.636 & +0.108 & +0.035 & +0.032 \\ 
@@
 
+\clearpage
 \section{Supplementary}
+
+\subsubsection{The number of timessteps}
+Increasing the number of time-steps in the computations can potentially allow for a more accurate temporal reconstruction, but at the same time the number of observations per control decreases and the regularization may therefore play a larger role.
+Furthermore, the computational cost will rise with additional time-steps.
+Thus finding the optimal number of time-steps can be essential for solving larger problems.
+The computation used a wide range the regularization parameters, and the number of timesteps were selected to be 20 and 40.
+
+The results are given in Table~\ref{TAB::timesteps}.
+It can be seen for all $\alpha=1.0$ that the relative error becomes bigger with more time-steps.
+This behavior can also be seen for $\alpha=1.0\mathrm{e}{-2}$ and $\beta < 1.0\mathrm{e}{-2}$, which implies an interaction between the regularization parameters.
+Therefore $g$ was investigated by plotting boundary points through time for different values of $\alpha$ and $\beta$, see Fig \ref{boundarycontrol}.
+
 \begin{table}
@@
 \end{table}
+
+\subsubsection{The number of observations}
+The dependency on observations is relevant, since the number of observations of the MRI data is limited.
+This dependency was investigated by changing the number of observations, and by examining the results.
+The number of observation were chosen to be 5 and 20, and the observation times were evenly spaced.
+
+The results for 5 observations is shown in Table~\ref{TAB::half} and for 20 observations is shown in Table~\ref{TAB::double}.
+In Table~\ref{TAB::half}, the values $\alpha =1.0\mathrm{e}{-2}$ and $\beta<1.0$ gives a surge in the relative error with more time-steps.
+This behavior is neither visible in Table~\ref{TAB::timesteps} or in  Table~\ref{TAB::double} for the same regularization parameters.
+The ratio observations per control indicates that the increase in relative error is due to oscillations, similar to those seen in Figure~\ref{boundarycontrol}.
+Thus the observations acts as stabilization for the functional, which gives a broader range of adequate regularization parameters.
 
@@
 
-\newpage
+In Table~\ref{Tab::Noise0.03}, we can see that a noise amplitude of 0.03, (10$\%$ of maximum initial condition) had negligible effect on the relative errors compared zero noise in Table~\ref{Tab::1} and Table~\ref{TAB::timesteps}.
+
 \begin{table}

### 2018-10-28 tex/paper.tex
abstract added

@@
 \begin{abstract}
-bla bla 
+The proposed glymphatic system suggest a new mechanism for waste clearance from the brain, and has sparked new research on Alzheimer's disease where one of the defining features
+is that metabolic waste accumulate within the brain.
+The glympahtic hypothesis is still controversial, but experimental investigations in rodents as well as novel MRI investigations in humans indicates the existence of a similar system.
+However, a proper theoretical foundation is currently missing from the biomechanical point of view.
+In particular, a crucial question in the current debate is how much the system accelerate
+waste clearance when compared to extracellular diffusion alone. Therefore
+we will in this paper evaluate to what extent partial differential constrained optimization methods can be used to identify modeling parameters for glymphatic transport.
+We assume that the transport can be modeled by a diffusion equation, representing extracellular diffusion and possibly dissipation caused by the glymphatic system.
+
+%The recently proposed glymphatic system propose a new mechanism for waste
+%clearance from the brain and has opened for a new paradigm in        
+%research on Alzheimer's disease where one of the defining features
+%is that metabolic waste accumulate within the brain. The glymphatic system is still controversial and while
+%experimental investigations in rodents as well as novel MRI investigations in humans
+%provide evidence for the existence of this system, a proper theoretical
+%foundation is currently missing from the bio-mechanical point of view. In particular,
+%a crucial question in the current debate is how much the system accelerate
+%waste clearance when compared to extra-cellular diffusion alone. In this paper,
+%we will therefore evaluate to what extent partial differential constrained optimization methods
+%can be used to identify modeling parameters for glymphatic transport when we    
+%assume that the underlying equation can be represented by a diffusion equation
+%representing extra-cellular diffusion and possibly dissipation caused by the glymphatic system.
 \end{abstract}

### 2018-10-28 tex/paper.tex
update

@@
 
-\title{Assessing paravascular transport in the parenchyma by partial differential equation (PDE) constrained optimization.}
+\title{Assessing paravascular transport in the parenchyma by partial differential equation (PDE) constrained optimization}
 
@@
 
-In Figure~\ref{boundarycontrol} we can see that more time-steps causes oscillations for $\alpha=1.0$, and each peak corresponds to a observation time.
-These oscillations are caused by the value selection of $\alpha$, which tries minimize $g$ between observation times.
+In Figure~\ref{boundarycontrol} we can see that more time-steps causes oscillations if $\alpha\gg\beta$ and the number of time-steps are much larger than the number of observations.
+For instance, as seen by the the pink line for $\alpha=1.0$ and $\beta=0.0001$ the peaks corresponds to a observations.
+These oscillations are caused by the strong weighting of $\alpha$, which leads to minimizing of $g$ between observation times.
+Further tests are documented in the Supplementary.
 
@@
 to diffusion for solute transportation. If we take into account then that the vasculature occupy 3-5\% of the volume
-of the brain and the paravascular space presumably occupy less space, then the factor 30\% (?) that we find here 
+of the brain and the paravascular space presumably occupy less space the 42-100\% that we find here 
 seems significant and it is difficult to explain or ignore.
 
-In summary, using this model, we estimated diffusion coefficients that were 43-100\% larger than estimated by DTI acquisitions.
+%In summary, using this model, we estimated diffusion coefficients that were 42-100\% larger than estimated by DTI acquisitions.
 Our results indicate that dissipation of solutes along the paravascular rout has a factor of 30, as compared to diffusion alone.
 However, the present study did not examine whether transport is by convective mechanisms.
+%
 

### 2018-10-28 tex/paper.tex
Supplementary

@@
 \end{equation}
-The case when the minimization algorithm fails to converge within 1000 iteration will be indicated by a hyphen in Table~\ref{TAB::timesteps}, Table~\ref{TAB::double} and Table~\ref{Tab::Noise0.3}
+The case when the minimization algorithm fails to converge within 1000 iteration will be indicated by a hyphen in Table~\ref{Tab::Noise0.3}
 
@@
 These oscillations are caused by the strong weighting of $\alpha$, which leads to minimizing of $g$ between observation times.
-Further tests are documented in the Supplementary.
+Tests with variation in the number of timesteps and observations are documented in the Supplementary.
 
@@
 Furthermore, the relative boundary error $||g||\sp{rel}$ is significantly larger for $\alpha< 1.0\mathrm{e}{-2} $ and $\beta < 1.0\mathrm{e}{-2}$.
+Results with noise  amplitudes at 0.03 are listed in the Supplementary.
 

### 2018-10-28 tex/paper.tex
update

@@
 This was done by pointwise adding uniform distributed noise in the range $\lbrace -n_{amp} , n_{amp} \rbrace $, with $n_{amp}$ defined as noise amplitude, to the manufactured observations.
-Then the optimization was solved by varying the regularization parameters $\alpha$ and $\beta$.
+Then the optimization was performed for various regularization parameters $\alpha$ and $\beta$.
 Figure~\ref{12hourswithnoise} and Figure~\ref{24hourswithnoise} show the reconstruction of the manufactured solution at
@@
 This corresponds to a tortuosity of $1.85$ and $1.73$, given that the self-diffusivity of water has been estimated to be around $3.0\mathrm{e}{-3}\mathrm{mm\sp{2}/s}$ at $37\sp{o}C$.
-Then the reference value $3.8\mathrm{e}{-4} \mathrm{mm\sp{2}/s}$ for Gd-DPTA gives an estimate for the apparent diffusion coefficient in the grey and white matter to  be $ 1.26\mathrm{e}{-4}\mathrm{mm\sp{2}/s}$ and $1.10\mathrm{e}{-4} \mathrm{mm\sp{2}/s}$ respectively.
+The reference value $3.8\mathrm{e}{-4} \mathrm{mm\sp{2}/s}$ for Gd-DPTA then gives an estimate for the apparent diffusion coefficient in the grey and white matter to  be $ 1.26\mathrm{e}{-4}\mathrm{mm\sp{2}/s}$ and $1.10\mathrm{e}{-4} \mathrm{mm\sp{2}/s}$ respectively.
 This estimation assumes that the tortuosity is independent for molecules with mass lower than 1kDa.
@@
 The oscillation in Figure~\ref{boundarycontrol} showed a large discrepancy in the states between observations.
-Therefore the states with $k=48$ were examined after 36 hours, see Figure\ref{statecomparison}.
+Therefore the states with $k=48$ were examined after 36 hours, see Figure~\ref{statecomparison}.
 It can be observed that the upper right row displays a discrepancy, which likely due to inadequate regularization parameters.
@@
 The regularization parameters  $\alpha \in \lbrace 1.0\mathrm{e-6}, 1.0\mathrm{e}{-2} \rbrace$, $\beta \in \lbrace 1.0\mathrm{e}{-2} , 1.0 \rbrace$ with the requirement $\alpha / \beta < 1.0\mathrm{e}{-2}$ gave a relative error of
-4.1\% in grey matter and 3.6 \% in white matter. It is particularly interesting to see that the procedure efficiently removes noise as demonstrated
+4.1\% in grey matter and 3.6 \% in white matter when tested against a manifactured solution. It is particularly interesting to see that the procedure efficiently removes noise as demonstrated
 in the Figures \ref{12hourswithnoise} and \ref{24hourswithnoise} with noise amplitude of 23\% of maximum value.
@@
 from the interstitium via the CSF. That said, 
-we find that the diffusion coefficients is 42-100\% larger than what was found by the DTI modality. As such, we predict that the paravascular system 
+we find that the diffusion coefficients is 42\% larger in grey matter and 100\% larger in white matter  than what was found by the DTI modality. As such, we predict that the paravascular system 
 plays a significant role.  
@@
 
-The computational model uses 2 global controls for the diffusion coefficients, while it can be seen in  Figure~\ref{figuredti} that diffusion coefficients can be considered a spacial function.
-However, the implementation of control parameters for each degree of freedom would significantly increase the computational cost.
+The computational model uses 2 global controls for the diffusion coefficients, while it can be seen in  Figure~\ref{figuredti} that diffusion coefficients can be considered a spatial function.
+However, the implementation of control parameters for each degree of freedom would significantly increase the computational cost and increase the demand for regularization.
 Since the diffusivity appears to be regional, using region specific control parameters seems to be a better option.
@@
 to diffusion for solute transportation. If we take into account then that the vasculature occupy 3-5\% of the volume
-of the brain and the paravascular space presumably occupy less space the 42-100\% that we find here 
-seems significant and it is difficult to explain or ignore.
+of the brain and the paravascular space presumably occupy less space, the 42\% increase in grey matter and 100\% in white matter  that we find here seem significant and the results point towards of the glymphatic clearance.
 

### 2018-10-28 tex/paper.tex
update

@@
 The glymphatic system seems to become impaired during aging, and failure of the glymphatic system may play a role in neurodegenerative disease and development of Alzheimer's disease.
-Evidence for a brain-wide glymphatic system in humans was first obtained in 2015 \citet{eide2015mri}, and in 2017 \citet{ringstad2018brain} provided evidence that glymphatic function is deteriorated in individuals with dementia, as compared to controls.
+Evidence for a brain-wide glymphatic system in humans was first obtained in 2015 \citet{eide2015mri}, and in 2018 \citet{ringstad2018brain} provided evidence that glymphatic function is deteriorated in individuals with dementia, as compared to controls.
 Several aspects of the glympahtic system are still debated, for example whether glymphatic transport of solutes is by convective mechanisms or by diffusion.

### 2018-10-28 tex/paper.tex
reference corrections

--- 2018-10-28 tex/paper.tex
@@
-\documentclass[11pt,a4paper]{article}
+\documentclass[12pt,a4paper]{article}
 \usepackage{hyperref}
@@
 that diffusion was a governing transport mechanism in the brain and with an estimated order of magnitude $1.0\mathrm{e}{-4} \mathrm{mm\sp{2}/s}$ for large molecules.
-This is confirmed with diffusion tensor imaging (DTI) where young and healthy subjects have typical diffusion values in white matter around $0.7-0.9\mathrm{e}{-3} \mathrm{mm\sp{2}/s}$ \citet{Helenius194},
-while subjects with dementia typically have higher value and variation \cite{goujon2018can} . Of course diffusion coefficients, 
+This is confirmed with diffusion tensor imaging (DTI) where young and healthy subjects have typical diffusion values in white matter around $0.7-0.9\mathrm{e}{-3} \mathrm{mm\sp{2}/s}$ \citet{Helenius194}, while subjects with dementia typically have higher value and variation \cite{goujon2018can}.
+Of course diffusion coefficients,
 measured by DTI at a time-scale of 7-30 minutes, may not be representative for the process on a
@@
 Below, we briefly describe the relationship between the imaging signal 
-seen in Figures \ref{fig1} and \ref{fig2} and the underlying contrast 
+seen in Figures~\ref{fig1} and \ref{fig2} and the underlying contrast 
 concentration.
@@
 \end{equation}
-which can be seen in Figure \ref{figuredti}. 
+which can be seen in Figure~\ref{figuredti}. 
 This gives the following relation 
@@
 4.1\% in grey matter and 3.6 \% in white matter. It is particularly interesting to see that the procedure efficiently removes noise as demonstrated
-in the Figures \ref{12hourswithnoise} and \ref{24hourswithnoise} with noise amplitude of 23\% of maximum value.
+in the Figures ~\ref{12hourswithnoise} and ~\ref{24hourswithnoise} with noise amplitude of 23\% of maximum value.
 However, the addition of noise required that $\beta = 1.0 $ to obtain consistent convergence.

### 2018-10-29 tex/paper.tex
update

@@
 \begin{abstract}
-The proposed glymphatic system suggest a new mechanism for waste clearance from the brain, and has sparked new research on Alzheimer's disease where one of the defining features
+The proposed glymphatic system suggests a new mechanism for waste clearance from the brain, and has sparked new research on Alzheimer's disease where one of the defining features
 is that metabolic waste accumulate within the brain.
-The glympahtic hypothesis is still controversial, but experimental investigations in rodents as well as novel MRI investigations in humans indicates the existence of a similar system.
-However, a proper theoretical foundation is currently missing from the biomechanical point of view.
+The glympahtic hypothesis is still controversial, but experimental investigations in rodents as well as novel MRI investigations in humans indicates the existence of such a system.
+A proper theoretical foundation
+that explains the fluid transfer mechanisms from first principles however is currently missing.
 In particular, a crucial question in the current debate is how much the system accelerate
@@
 We assume that the transport can be modeled by a diffusion equation, representing extracellular diffusion and possibly dissipation caused by the glymphatic system.
+The observations are obtained from novel MRI techniques that
+aim to quantify long-term (hours/days) transfer mechanism in the brain.
 

### 2018-10-29 tex/paper.tex
text change

@@
 ~\cite{asgari2016glymphatic, brynjfm, Diem} have found that dissipation in the paravascular spaces adds less than a factor two
-to diffusion for solute transportation. If we take into account then that the vasculature occupy 3-5\% of the volume
-of the brain and the paravascular space presumably occupy less space the 42-100\% that we find here 
-seems significant and it is difficult to explain or ignore.
-
+to diffusion for solute transportation. If we consider that the vasculature system occupy 3\% of the brain volume
+%of the brain 
+and that the paravascular space presumably occupy less space. Then the 42-100\% that we find here seems significant and it is difficult to explain or ignore.     
 %In summary, using this model, we estimated diffusion coefficients that were 42-100\% larger than estimated by DTI acquisitions.

### 2018-10-29 tex/paper.tex
removed one ref

@@
 \newcommand{\lars}[1]{\textcolor{magenta}{#1}}
-\author{Lars Magnus Valnes, Sebastian K. Mitusch, Geir A. Ringstad, \\ 
+\author{Lars Magnus Valnes, Sebastian K. Mitusch, Geir Ringstad, \\ 
 Per Kristian Eide, Simon W. Funke, Kent-Andre Mardal }
@@
 It was proposed to have an important metabolic role by providing a pathway for clearance of waste solutes from the brain.
-Evidence was given that the activity of the glymphatic system increases during sleep ~\citet{xie2013sleep}, thus linking sleep to clearance of toxic substances from the brain.
+Evidence was given that the activity of the glymphatic system increases during  sleep by ~\citet{xie2013sleep}, thus linking sleep to clearance of toxic substances from the brain.
 The glymphatic system seems to become impaired during aging, and failure of the glymphatic system may play a role in neurodegenerative disease and development of Alzheimer's disease.
-Evidence for a brain-wide glymphatic system in humans was first obtained in 2015 \citet{eide2015mri}, and in 2018 \citet{ringstad2018brain} provided evidence that glymphatic function is deteriorated in individuals with dementia, as compared to controls.
+Evidence for a brain-wide glymphatic system in humans was first obtained in 2015 by \citet{eide2015mri}, and in 2018 \citet{ringstad2018brain} provided evidence that glymphatic function is deteriorated in individuals with dementia, as compared to controls.
 Several aspects of the glympahtic system are still debated, for example whether glymphatic transport of solutes is by convective mechanisms or by diffusion.
@@
 that diffusion was a governing transport mechanism in the brain and with an estimated order of magnitude $1.0\mathrm{e}{-4} \mathrm{mm\sp{2}/s}$ for large molecules.
-This is confirmed with diffusion tensor imaging (DTI) where young and healthy subjects have typical diffusion values in white matter around $0.7-0.9\mathrm{e}{-3} \mathrm{mm\sp{2}/s}$ \citet{Helenius194}, while subjects with dementia typically have higher value and variation \cite{goujon2018can}.
-Of course diffusion coefficients,
+This is confirmed with diffusion tensor imaging (DTI) where young and healthy subjects have typical diffusion values in white matter around $0.7-0.9\mathrm{e}{-3} \mathrm{mm\sp{2}/s}$ \citet{Helenius194},
+while subjects with dementia typically have higher value and variation \cite{goujon2018can} . Of course diffusion coefficients, 
 measured by DTI at a time-scale of 7-30 minutes, may not be representative for the process on a
@@
 \end{equation}
-The signal difference between observation times were adjusted in \cite{eidevalnes}. Thus we can express the change in $T_1$ due to tracer as 
+The signal difference between observation times were adjusted in \cite{ringstad2018brain}. Thus we can express the change in $T_1$ due to tracer as 
 \begin{equation}
@@
 Tissue damage can be observed in the MRI due to a lower signal in the white matter compared to healthy white matter tissue, thus damaged tissue have different $T_1$ relaxation time.
-The tracer concentration was estimated in a preprocessing step, using the parameters obtained from the T1-map, MPRAGE MRI protocol \cite{eidevalnes} and the value for $r_1$ found in \cite{pmid16230904}.
+The tracer concentration was estimated in a preprocessing step, using the parameters obtained from the T1-map, MPRAGE MRI protocol \cite{ringstad2018brain} and the value for $r_1$ found in \cite{pmid16230904}.
 In the computation, the function \eqref{scaledmagnetization} was computed for $ T_1\in \lbrace 200, 4000 \rbrace$ creating a lookup table.
@@
 \includegraphics[width=0.80\textwidth]{DTI-zoom.png} 
-\caption{The left panel show the anatomical map.
-The middle panel show the apparent diffusion coefficients (ADC) obtained from DTI.
+\caption{The left panel shows the anatomical map.
+The middle panel shows the apparent diffusion coefficients (ADC) obtained from DTI.
 The right panel shows the computed fractional anisotropy (FA) from the DTI.}
@@
 The software Freesurfer was used to segment and create the polyhedral surfaces of the white and grey matter.
-Then the T2 weighted MRI \cite{eidevalnes} was used to segment the CSF compartment surrounding the cerebral and the lateral ventricles.
+Then the T2 weighted MRI \cite{ringstad2018brain} was used to segment the CSF compartment surrounding the cerebral and the lateral ventricles.
 CGAL \cite{cgal:rty-m3-18b} was used to combine the polyhedral surfaces and to construct the mesh.
@@
 \subsubsection{Comparison with results obtained from DTI analysis}
-
 The median diffusion coefficient in the DTI was estimated to be $8.7\mathrm{e}{-4} \mathrm{mm\sp{2}/s}$ in white matter and $1.0\mathrm{e}{-3} \mathrm{mm\sp{2}/s}$ in grey matter.
 This corresponds to a tortuosity of $1.85$ and $1.73$, given that the self-diffusivity of water has been estimated to be around $3.0\mathrm{e}{-3}\mathrm{mm\sp{2}/s}$ at $37\sp{o}C$.
-Then the reference value $3.8\mathrm{e}{-4} \mathrm{mm\sp{2}/s}$ for Gd-DPTA gives an estimate for the apparent diffusion coefficient in the grey and white matter to  be $ 1.26\mathrm{e}{-4}\mathrm{mm\sp{2}/s}$ and $1.10\mathrm{e}{-4} \mathrm{mm\sp{2}/s}$ respectively.
+The reference value $3.8\mathrm{e}{-4} \mathrm{mm\sp{2}/s}$ for Gd-DPTA then gives an estimate for the apparent diffusion coefficient in the grey and white matter to  be $ 1.26\mathrm{e}{-4}\mathrm{mm\sp{2}/s}$ and $1.10\mathrm{e}{-4} \mathrm{mm\sp{2}/s}$ respectively.
 This estimation assumes that the tortuosity is independent for molecules with mass lower than 1kDa.
@@
 The regularization parameters  $\alpha \in \lbrace 1.0\mathrm{e-6}, 1.0\mathrm{e}{-2} \rbrace$, $\beta \in \lbrace 1.0\mathrm{e}{-2} , 1.0 \rbrace$ with the requirement $\alpha / \beta < 1.0\mathrm{e}{-2}$ gave a relative error of
-4.1\% in grey matter and 3.6 \% in white matter. It is particularly interesting to see that the procedure efficiently removes noise as demonstrated
-in the Figures ~\ref{12hourswithnoise} and ~\ref{24hourswithnoise} with noise amplitude of 23\% of maximum value.
+4.1\% in grey matter and 3.6 \% in white matter when tested against a manifactured solution. It is particularly interesting to see that the procedure efficiently removes noise as demonstrated
+in the Figures \ref{12hourswithnoise} and \ref{24hourswithnoise} with noise amplitude of 23\% of maximum value.
 However, the addition of noise required that $\beta = 1.0 $ to obtain consistent convergence.
@@
 from the interstitium via the CSF. That said, 
-we find that the diffusion coefficients is 42-100\% larger than what was found by the DTI modality. As such, we predict that the paravascular system 
+we find that the diffusion coefficients is 42\% larger in grey matter and 100\% larger in white matter than what was found by the DTI modality. As such, we predict that the paravascular system 
 plays a significant role.  
@@
 %of the brain 
-and that the paravascular space presumably occupy less space. Then the 42-100\% that we find here seems significant and it is difficult to explain or ignore.     
+and the paravascular space presumably occupy less space.
+Then the 42\% increase in grey matter and 100\% in white matter that we find here seem significant and the results point towards of the glymphatic clearance.
 %In summary, using this model, we estimated diffusion coefficients that were 42-100\% larger than estimated by DTI acquisitions.

### 2018-10-29 tex/paper.tex
correcting sections

@@
 in FEniCS \cite{LoggMardalEtAl2012a}. In Section 3 we present the results and have a rather extensive discussion of the verification performed
-using a manufactured solution (Section 3.1-3.3) before we present the results obtained by real observations in Section 3.4     
-and a comparison with DTI data in Section 3.5. Finally, in Section 4, the methodology and results are discussed.
+using a manufactured solution (Section 3.1) before we present the results obtained by real observations in Section 3.2.1    
+and a comparison with DTI data in Section 3.2.2. Finally, in Section 4, the methodology and results are discussed.
 
@@
 \end{figure}
-Figure~\ref{fig1} shows distribution of a CSF tracer, as a percentage change in T1 signal unit ratios, see also~\cite{ringstad2018brain} for further information on the imaging procedure.   
-Our data (not all shown) consist of a total of 10 MRI observations, including a baseline MRI taken before tracer was injected.
+Figure~\ref{fig1} shows distribution of MRI-contrast%CSF tracer
+, as a percentage change in T1 signal unit ratios, see also~\cite{ringstad2018brain} for further information on the imaging procedure.   
+Our data (not all shown) consist of a total of 10 MRI observations, including a baseline MRI taken before the contrast was injected.
 The observation points are distributed over 5 observations within 1-2 hours after injection, a single observation in the timeframes 2-4 hours, 6-9 hours, 24 hours and 48 hours.
@@
 Hence, below we will use two letter symbols such as $TE$ and $TR$ to keep the notation consistent with the presentation in \cite{GOWLAND, MPRAGE}.
-The tracer concentration $c$ causes the longitudinal(spin-lattice) relaxation time $T_{1}$ to shorten with the following relation
+The contrast concentration $c$ causes the longitudinal(spin-lattice) relaxation time $T_{1}$ to shorten with the following relation
 \begin{equation}
@@
 \end{equation}
-The superscripts indicate relaxation time with contrast $T_{1}\sp{c}$ and without contrast $T_{1}\sp{0}$, and $r_1$ is the relaxivity constant for the MRI tracer in a medium. 
-The tracer observations were collected using a MRI sequence known as  Magnetization Prepared Rapid Acquisition Gradient Echo (MPRAGE) with an inversion prepared magnetization.
+The superscripts indicate relaxation time with contrast $T_{1}\sp{c}$ and without contrast $T_{1}\sp{0}$, and $r_1$ is the relaxivity constant for the MRI-contrast in a medium. 
+The contrast observations were collected using a MRI sequence known as  Magnetization Prepared Rapid Acquisition Gradient Echo (MPRAGE) with an inversion prepared magnetization.
 The relation between signal and the relaxation time is non-linear, and is expressed with the following equations.
@@
 The $M_0$ is a calibration constant of the magnetization.
-The center echo denoted as $n=m/2$ will be the signal that we will consider when estimating MRI tracer.
+The center echo denoted as $n=m/2$ will be the signal that we will consider when estimating MRI-contrast.
 Given \eqref{EQ::SI} we have that the relative signal increase can be written as
@@
 \end{equation}
-The signal difference between observation times were adjusted in \cite{ringstad2018brain}. Thus we can express the change in $T_1$ due to tracer as 
+The signal difference between observation times were adjusted in \cite{ringstad2018brain}. Thus we can express the change in $T_1$ due to contrast as 
 \begin{equation}
@@
 Tissue damage can be observed in the MRI due to a lower signal in the white matter compared to healthy white matter tissue, thus damaged tissue have different $T_1$ relaxation time.
-The tracer concentration was estimated in a preprocessing step, using the parameters obtained from the T1-map, MPRAGE MRI protocol \cite{ringstad2018brain} and the value for $r_1$ found in \cite{pmid16230904}.
+The contrast concentration was estimated in a preprocessing step, using the parameters obtained from the T1-map, MPRAGE MRI protocol \cite{ringstad2018brain} and the value for $r_1$ found in \cite{pmid16230904}.
 In the computation, the function \eqref{scaledmagnetization} was computed for $ T_1\in \lbrace 200, 4000 \rbrace$ creating a lookup table.
@@
 \centering
-\includegraphics[width=0.80\textwidth]{DTI-zoom.png} 
+\includegraphics[width=0.75\textwidth]{DTI-zoom.png} 
 \caption{The left panel shows the anatomical map.
@@
 with $\lambda$ denoted as the tortuosity.
-In order to estimate the apparent diffusion coefficient involved in the tracer transportation shown in Figure~\ref{fig1} we assume that the process can be modeled by a diffusion equation. 
-Then we constructed an optimization problem with the aim to minimize the difference between the observed and the modeled tracer distribution by optimizing the boundary conditions and the apparent diffusion coefficient.%Then we solve a PDE constrained optimization problem where the tracer distribution, boundary conditions, and apparent diffusion coefficient are solved for by optimizing with respect to the observed tracer distribution \lars{Ikke helt oversiktlig}.
+In order to estimate the apparent diffusion coefficient involved in the contrast transportation shown in Figure~\ref{fig1} we assume that the process can be modeled by a diffusion equation. 
+Then we constructed an optimization problem with the aim to minimize the difference between the observed and the modeled contrast distribution by optimizing the boundary conditions and the apparent diffusion coefficient.%Then we solve a PDE constrained optimization problem where the tracer distribution, boundary conditions, and apparent diffusion coefficient are solved for by optimizing with respect to the observed tracer distribution \lars{Ikke helt oversiktlig}.
 Thus enhanced transportation because of effects such as dissipation would result in an apparent diffusion coefficient larger than that predicted by DTI.The objective function was defined as 
@@
 The 3 domain mesh in Figure~\ref{Fig::Mesh} A, consists of 244318 tetrahedral cells and 22057 vertices, while the 2 domain mesh (without the CSF compartment) Figure~\ref{Fig::Mesh} B consists of 335589 tetrahedral cells and 73002 vertices.
-%The mesh coordinates (X,Y,Z) are given in $\mathrm{mm}$ \lars{ with $X \in \lbrace -70.5,-18\rbrace, Y \in \lbrace -73.5,28.8  \rbrace ,Z \in \lbrace 16.6,60.7 \rbrace$ }.
 
@@
 The initial condition was set to 0 everywhere, the timestep was $dt = 0.2$, and the diffusion coefficients were selected to be 
-%\fixme{describe discretisation in time and space}\lars{ cell-radius ratio ? angle ?}
 \begin{equation}
@@
 
-\section{Implementation}
-%In the acquired data, the MPRAGE had a high signal to noise ratio and the T1 map had low signal in the CSF.
-This made it difficult to estimate the concentration in the CSF compartment.
-Thus an additional mesh without the CSF compartment was constructed, see Fig.
-\ref{Fig::Mesh}.
-
+\subsection{Implementation}
 The solver for \eqref{Eq::PDE} was implemented using the FEniCS project (v.2017.2), using backwards Euler time discretization and first order continuous Galerkin finite elements in space.
@@
 \section{Results}
-
 \subsection{Verification in terms of the manufactured solution}
@@
 \subsubsection{The relaxation parameters}
-
 The convergence as well as the result of the minimization is influenced by the values of the regularization parameters $\alpha$ and $\beta$.
 Therefore the convergence was examined by a systematic study of the reconstruction of the manufactured solution with respect to a wide range of regularization parameters.
-
-%To assess the sensitivity of the the objective functional defined in Eq.\ref{Eq::F} with respect to the regularization parameters $\alpha$ and $\beta$ 
-%we perform a systematic study of the reconstruction of the manufactured solution with respect to a wide range of regularization parameters.
 
@@
 
-%In Table ~\ref{TAB::double}, we can see that $\aplha < 1.0e-2$ and $\beta =1.0e-2$ have a drastic change in the number of iteration for $20$ time-steps.
-
 \subsubsection{The noise susceptibility}
@@
 
-%\subsection{Sparse observations}
-%The MRI data contains observations after the injection of CSF tracer.
-These observation are unevenly distributed in time resulting in large time intervals with no observations.
-Therefore the effect of these temporal gaps in the observations will be evaluated.
-This was done by selecting the observation times as follows  $t_i = \lbrace$0.8, 1.0, 1.2, 1.8, 2.4, 3.6, 5.4, 7.6, 24.0$\rbrace$.
-The regularization parameters was selected, so that the error would be minimized,and noise was also added.
-%
-%The results are shown in Tab.\ref{Tab::Hole1} and Tab\ref{Tab::Hole2}, and it can be observed that the addition of noise caused $\beta=1.0$ to converge the same.
-Comparing the values in Tab\ref{Tab::Hole1} and Tab.\ref{TAB::timesteps}, showed that the relative error increased.
-
 \subsection{A Real case}
@@
 \subsubsection{Results obtained when using real observations}
-The MRI data consisted of the observations at times $t_i \in \lbrace$ 0.00, 0.16, 0.39, 0.55, 0.77, 2.09, 6.05, 24., 48., 698.
-$\rbrace \mathrm{(hours)}$ with the time $t_i=0.00$ as the observation 1-2 hours after the tracer was injected.
-There was no significant visible change in the tracer between the observations at $\lbrace $ 0.00, 0.16, 0.39, 0.55, 0.77 $ \rbrace$.
-This prompted the use of the following observation times  $0.00, 2.09, 6.05, 24., 48.$.
+The MRI data consisted of the observations at times $t_i \in \lbrace$0.00, 0.16, 0.39, 0.55, 0.77, 2.09, 6.05, 24., 48., 698.$\rbrace \mathrm{(hours)}$ with the time $t_i=0.00$ as the observation 1-2 hours after the contrast was injected.
+There was no significant visible change in the contrast between the observations at $\lbrace$0.00, 0.16, 0.39, 0.55, 0.77$\rbrace$.
+This prompted the use of the following observation times  $\lbrace0.00, 2.09, 6.05, 24., 48.\rbrace$.
 
-The estimation of tracer concentration proved difficult in the CSF compartment.
+The estimation of contrast concentration proved difficult in the CSF compartment.
 Therefore the 2 domain mesh, shown in Figure~\ref{Fig::Mesh} was used in the computation.
@@
 
-%\subsection*{Compare high DTI values in white matter with computed}
-%\fixme{Can we remove this subsection header?}
-
-In Figure~\ref{Fig::realdata}, it can be seen that there were regions with negligible amount of tracers and vice versa.
-The regions with above average amount of tracers corresponds with high diffusivity regions in Figure~\ref{figuredti}.
+In Figure~\ref{Fig::realdata}, it can be seen that there were regions with negligible amount of contrast and vice versa.
+The regions with above average amount of contrast corresponds with high diffusivity regions in Figure~\ref{figuredti}.
 This suggests that the computed diffusion coefficients corresponds to these values.
@@
 This gives a difference of $ 46 \%$ compared to the computed values.
-
-%The region with high diffusivity in the white matter, shown in Fig\ref{FIG::DTI}, gives a upper bound on the diffusion coefficient to be 1.3 $\mathrm{mm\sp{2}/s}$.
-
-%
-% \begin{table}
-%\centering
-%\caption{Viser omgjøringer,estiamering og prosentvis forskjell for min og max control/optimerte verdier . Unit $\left[ \mathrm{mm\sp{2}/h} \right]$}
-%\resizebox{\textwidth}{!}{\begin{tabular}{*{6}c}
-%$ D\sp{free}_{water} $ & $ D\sp{DTI}__{g} $ & $ D\sp{DTI}_{w} $ & $D\sp{fre}__{Gd-DPTA} $ & $D\sp{ADC}__{g} $ & $ D\sp{ADC}_{w} $ & $ D\sp{ADC}_{g} -D\sp{OPT}_{g} $ &$ D\sp{ADC}_{w} -D\sp{OPT}_{w} $ \\
-%\hline
-%10.8 & 3.64 & 3.13 & 1.37 & 0.46 & 0.40 &  20 - 114 $\%$  & 100- 200 $\%$
-%  -   &  -    & 4.86 &  - &  -   & 0.61 &   -                  &   0 - 100 $\%$       
-%\end{tabular}} 
-%\label{}
-%\end{table} 
-% 
-%The region with high diffusivity in the white matter, shown in Fig\ref{FIG::DTI}, gives a upper bound on the diffusion coefficient to be 1.3 $\mathrm{mm\sp{2}/s}$
 
@@
 The regularization parameters  $\alpha \in \lbrace 1.0\mathrm{e-6}, 1.0\mathrm{e}{-2} \rbrace$, $\beta \in \lbrace 1.0\mathrm{e}{-2} , 1.0 \rbrace$ with the requirement $\alpha / \beta < 1.0\mathrm{e}{-2}$ gave a relative error of
-4.1\% in grey matter and 3.6 \% in white matter when tested against a manifactured solution. It is particularly interesting to see that the procedure efficiently removes noise as demonstrated
+4.1\% in grey matter and 3.6 \% in white matter when tested against a manufactured solution. It is particularly interesting to see that the procedure efficiently removes noise as demonstrated
 in the Figures \ref{12hourswithnoise} and \ref{24hourswithnoise} with noise amplitude of 23\% of maximum value.
@@
 the computational model assumes isotropic diffusivity, but the anisotropy in the white matter is well documented, as shown by the FA in Figure~\ref{figuredti}.
-It can be seen in Figure~\ref{Fig::realdata} that the region with high FA have negligible amounts of tracer present.
+It can be seen in Figure~\ref{Fig::realdata} that the region with high FA have negligible amounts of contrast present.
 Therefore it would seem that the anisotropy do not have direct impact on the computations, since the computation can not evaluate a static environment.
-Thus observations of tracer in regions with anisotropy can be considered a requirement before adding anisotropy to the model.
+Thus observations of contrast in regions with anisotropy can be considered a requirement before adding anisotropy to the model.
 
@@
 The hypothesis of the glymphatic system \cite{iliff2012paravascular} states that the waste is cleared through the veins in the parenchyma.
-This gives the tracer additional pathways that is not considered in the computational model.
+This gives the contrast additional pathways that is not considered in the computational model.
 These additional pathways can be modeled as a drainage, which can be included as a control source term.
@@
 
-Previous studies~\cite{holter2017interstitial, smith2017glymphatic} suggest that diffusion dominates in the interstitium. Furthermore, 
-~\cite{asgari2016glymphatic, brynjfm, Diem} have found that dissipation in the paravascular spaces adds less than a factor two
-to diffusion for solute transportation. If we consider that the vasculature system occupy 3\% of the brain volume
+Previous studies~\cite{holter2017interstitial, smith2017glymphatic} suggest that diffusion dominates in the interstitium.
+Furthermore, ~\cite{asgari2016glymphatic, brynjfm, Diem} have found that dissipation in the paravascular spaces adds less than a factor two
+to diffusion for solute transportation. If we consider that the vascular system occupy 3\% of the brain volume
 %of the brain 
-and the paravascular space presumably occupy less space.
+and that the paravascular space presumably occupy less space.
 Then the 42\% increase in grey matter and 100\% in white matter that we find here seem significant and the results point towards of the glymphatic clearance.
@@
 \includegraphics[width=0.95\textwidth]{different.png} 
-\caption{Row A) shows the observation at times 2 hours, 6 hours, 24 hours and 48 hours after the first observation with tracer.
+\caption{Row A) shows the observation at times 2 hours, 6 hours, 24 hours and 48 hours after the first observation with contrast.
 Row B) shows the corresponding states with the relaxation parameters $\alpha=0.01$ and $\beta=0.01$ and $k=48$.

### 2018-10-29 tex/paper.tex
removed text

@@
 \end{equation}
-Here $T_b$ is known as the echo spacing, $T_a$ is the inversion time, $T_w$ the time delay, $TR$ as the repetition time, $m$ is the number of echo spacings and $T_1$ is the longitudinal(spin-lattice) relaxation time for a given medium.
-The $M_0$ is a calibration constant of the magnetization.
+Here $T_b$ is known as the echo spacing, $T_a$ is the inversion time, $T_w$ the time delay, $TR$ as the repetition time, $m$ is the number of echo spacings and $M_0$ is a calibration constant for the magnetization.
 The center echo denoted as $n=m/2$ will be the signal that we will consider when estimating MRI-contrast.
@@
 Then we constructed an optimization problem with the aim to minimize the difference between the observed and the modeled contrast distribution by optimizing the boundary conditions and the apparent diffusion coefficient.%Then we solve a PDE constrained optimization problem where the tracer distribution, boundary conditions, and apparent diffusion coefficient are solved for by optimizing with respect to the observed tracer distribution \lars{Ikke helt oversiktlig}.
-Thus enhanced transportation because of effects such as dissipation would result in an apparent diffusion coefficient larger than that predicted by DTI.The objective function was defined as 
+Thus enhanced transportation because of effects such as dissipation would result in an apparent diffusion coefficient larger than that predicted by DTI. The objective function was defined as 
 \begin{equation}
@@
 The magnitude order for $D_{\Omega_1} $ and $D_{\Omega_2}$ were chosen to resemble diffusion coefficient for water in grey and white matter, but the relation between the coefficients were not preserved.
-In \citet{Haga}, the drug concentration moved 1 cm per 20 seconds in the cervical region, thus $D_{\Omega_3}$  was set to 1000.
+In \citet{Haga}, the drug concentration moved 1 cm per 20 seconds in the cervical region, thus $D_{\Omega_1}$  was set to 1000.
 The manufactured forward computation produced a total of 120 possible observation times.
@@
 \end{equation}
-The case when the minimization algorithm fails to converge within 1000 iteration will be indicated by a hyphen in Table~\ref{Tab::Noise0.3}
+The case when the minimization algorithm fails to converge within 1000 iteration will be indicated by a hyphen in Table~\ref{Tab::Noise0.3}.
 
@@
 In Figure~\ref{boundarycontrol} we can see that more time-steps causes oscillations if $\alpha\gg\beta$ and the number of time-steps are much larger than the number of observations.
-For instance, as seen by the the pink line for $\alpha=1.0$ and $\beta=0.0001$ the peaks corresponds to a observations.
+For instance, as seen by the the pink line for $\alpha=1.0$ and $\beta=0.0001$ the peaks corresponds to a observation.
 These oscillations are caused by the strong weighting of $\alpha$, which leads to minimizing of $g$ between observation times.
@@
 Figure~\ref{12hourswithnoise} and Figure~\ref{24hourswithnoise} show the reconstruction of the manufactured solution at
-different noise levels with $\alpha=0.0001$,$\beta=1.0$ and $k=20$. Clearly, the reconstruction shown in the lower rows is quite robust with respect to the various levels
+different noise levels with $\alpha=0.0001$, $\beta=1.0$ and $k=20$. Clearly, the reconstruction shown in the lower rows is quite robust with respect to the various levels
 of noise shown in the upper rows.      

### 2018-10-29 tex/paper.tex
removed text

@@
 The MRI data contains noise, hence an investigation to the noise susceptibility is needed.
-This was done by pointwise adding uniform distributed noise in the range $\lbrace -n_{amp} , n_{amp} \rbrace $, with $n_{amp}$ defined as noise amplitude, to the manufactured observations.
-Then the optimization was performed for various regularization parameters $\alpha$ and $\beta$.
+This was done varying the noise amplitude, and then the optimization was performed for various regularization parameters $\alpha$ and $\beta$.
 Figure~\ref{12hourswithnoise} and Figure~\ref{24hourswithnoise} show the reconstruction of the manufactured solution at

### 2018-10-30 tex/paper.tex
small corrections

@@
 \section{Introduction}
-In 2012, ~\citet{iliff2012paravascular} provided evidence for a a brain-wide paravascular system, denoted the glymphatic system, which is a pathway for transport of fluids and solutes.
+In 2012, ~\citet{iliff2012paravascular} provided evidence for a brain-wide paravascular system, denoted the glymphatic system, which is a pathway for transport of fluids and solutes.
 It was proposed to have an important metabolic role by providing a pathway for clearance of waste solutes from the brain.
@@
 This is confirmed with diffusion tensor imaging (DTI) where young and healthy subjects have typical diffusion values in white matter around $0.7-0.9\mathrm{e}{-3} \mathrm{mm\sp{2}/s}$ \citet{Helenius194},
-while subjects with dementia typically have higher value and variation \cite{goujon2018can} . Of course diffusion coefficients, 
+while subjects with dementia typically have higher value and variation \cite{goujon2018can}. Of course diffusion coefficients, 
 measured by DTI at a time-scale of 7-30 minutes, may not be representative for the process on a
@@
 \end{equation}
-Here $T_b$ is known as the echo spacing, $T_a$ is the inversion time, $T_w$ the time delay, $TR$ as the repetition time, $m$ is the number of echo spacings and $M_0$ is a calibration constant for the magnetization.
+Here $T_b$ is known as the echo spacing time, $T_a$ is the inversion time, $T_w$ the time delay, $TR$ as the repetition time, $m$ is the number of echo spacings and $M_0$ is a calibration constant for the magnetization.
 The center echo denoted as $n=m/2$ will be the signal that we will consider when estimating MRI-contrast.
@@
 The $T_{1}\sp{0}$ values were obtained by T1-mapping of the brain using a MRI sequence known as MOLLI5(3)3 \cite{TAYLOR201667}.
-This takes into account patients specific characteristic, such as tissue damage.
+This takes into account patient specific characteristic, such as tissue damage.
 Tissue damage can be observed in the MRI due to a lower signal in the white matter compared to healthy white matter tissue, thus damaged tissue have different $T_1$ relaxation time.
@@
 In order to estimate the apparent diffusion coefficient involved in the contrast transportation shown in Figure~\ref{fig1} we assume that the process can be modeled by a diffusion equation. 
-Then we constructed an optimization problem with the aim to minimize the difference between the observed and the modeled contrast distribution by optimizing the boundary conditions and the apparent diffusion coefficient.%Then we solve a PDE constrained optimization problem where the tracer distribution, boundary conditions, and apparent diffusion coefficient are solved for by optimizing with respect to the observed tracer distribution \lars{Ikke helt oversiktlig}.
-Thus enhanced transportation because of effects such as dissipation would result in an apparent diffusion coefficient larger than that predicted by DTI. The objective function was defined as 
+Then we constructed an optimization problem with the aim to minimize the difference between the observed and the modeled contrast distribution by optimizing the boundary conditions and the apparent diffusion coefficient.
+Thus enhanced transportation because of effects such as dissipation would result in an apparent diffusion coefficient larger than that predicted by DTI.
+The objective function was defined as
 \begin{equation}
@@
 \subsection{Manufactured Solution}
-In order to asses the robustness and accuracy of our strategy and test the dependency of the computed diffusion coefficients $D$ on the
+In order to assess the robustness and accuracy of our strategy and test the dependency of the computed diffusion coefficients $D$ on the
 regularization parameters $\alpha$ and $\beta$, we perform a test case with a
-known solution.  
-The manufactured observations were obtained by forward computation of \eqref{Eq::PDE} with the Dirichlet boundary condition defined as
+known solution. The manufactured observations were obtained by forward computation of \eqref{Eq::PDE} with the Dirichlet boundary condition defined as
 \begin{equation}
@@
 The evaluation of different regularization parameters was done by solving the optimization with different values of $\alpha$ and $\beta$ and comparing the computed $D$ and $g$ values with the manufactured solution.
-The observation times were set to $\lbrace$ 2.4, 4.8, 7.2, 9.6, 12.0, 14.4, 16.8, 19.2, 21.6, 24.0 $\rbrace$, and the number of time-steps $k$ in the forward problem was set to $10$.
+The observation times were set to $\lbrace$2.4, 4.8, 7.2, 9.6, 12.0, 14.4, 16.8, 19.2, 21.6, 24.0 $\rbrace$, and the number of time-steps $k$ in the forward problem was set to $10$.
 
@@
 We can see that the optimization computed similar end-result for most regularization parameters.
-More specifically, for $\alpha \leq 1\mathrm{e}{-2}$ and $\beta \leq 1e-0$ the relative errors for all optimization parameters are below $5\%$.However, in the case of $ \alpha=1.0$ the relative error is over 100\% higher then for other values of $\alpha$.
+More specifically, for $\alpha \leq 1\mathrm{e}{-2}$ and $\beta \leq 1e-0$ the relative errors for all optimization parameters are below $5\%$.However, in the case of $ \alpha=1.0$ the relative error is over 100\% higher than for other values of $\alpha$.
 Furthermore, for all $\beta=100.0$ there is about 70\% relative error for $D_{\Omega_1}$ and approximate 10\% error for $D_{\Omega_2}$.
@@
 \includegraphics[scale=0.4]{noise-12.png}  
-\caption{The upper row shows the manufactured observation, A ) Shows the manufactured observation at time-point 24 with no noise added.
-B) Shows the manufactured observation at time-point 24 with an noise amplitude of 0.15.
-C)Shows the manufactures observation at time-point 24 with noise amplitude of 0.3.
+\caption{The upper row shows the manufactured observation, A) Shows the manufactured observation at time-point 24 with no noise added.
+B) Shows the manufactured observation at time-point 24 with noise amplitude of 0.15.
+C) Shows the manufactures observation at time-point 24 with noise amplitude of 0.3.
 The lower row shows the results with optimized parameter obtained with $\alpha=0.0001$, $\beta=1.0$ and $k=20$.
@@
 \includegraphics[scale=0.4]{noise-24.png}
-\caption{The upper row shows the manufactured observation, A ) Shows the manufactured observation at time-point 24 with no noise added.
-B) Shows the manufactured observation at time-point 24 with a noise amplitude of 0.15.
-C)Shows the manufactures observation at time-point 24 with noise amplitude of 0.3.
+\caption{The upper row shows the manufactured observation, A) Shows the manufactured observation at time-point 24 with no noise added.
+B) Shows the manufactured observation at time-point 24 with noise amplitude of 0.15.
+C) Shows the manufactures observation at time-point 24 with noise amplitude of 0.3.
 The lower row shows the results with optimized parameter obtained with $\alpha=0.0001$, $\beta=1.0$ and $k=20$.
@@
 \subsubsection{Results obtained when using real observations}
-The MRI data consisted of the observations at times $t_i \in \lbrace$0.00, 0.16, 0.39, 0.55, 0.77, 2.09, 6.05, 24., 48., 698.$\rbrace \mathrm{(hours)}$ with the time $t_i=0.00$ as the observation 1-2 hours after the contrast was injected.
+The MRI data consisted of the observations at times $t_i \in \lbrace$0.00, 0.16, 0.39, 0.55, 0.77, 2.09, 6.05, 24, 48, 698$\rbrace \mathrm{(hours)}$ with the time $t_i=0.00$ as the observation 1-2 hours after the contrast was injected.
 There was no significant visible change in the contrast between the observations at $\lbrace$0.00, 0.16, 0.39, 0.55, 0.77$\rbrace$.
-This prompted the use of the following observation times  $\lbrace0.00, 2.09, 6.05, 24., 48.\rbrace$.
+This prompted the use of the following observation times  $\lbrace0.00, 2.09, 6.05, 24, 48\rbrace$.
 
@@
 \begin{tabular}{*{8}c}
-$\alpha$ & $\beta$ & k  & iter & $ D_{\Omega_1}\sp{rel}$ & $D_{\Omega_2}\sp{rel} $ & $D_{\Omega_3}\sp{rel} $ & $|| g ||\sp{rel} $ \\
+$\alpha$ & $\beta$ & k  & iter & $ D_{\Omega_1}\sp{rel}$ & $D_{\Omega_2}\sp{rel} $ & $D_{\Omega_3}\sp{rel} $ & $||g||\sp{rel} $ \\
 \hline
@@
 \begin{tabular}{*{8}c}
-$\alpha$ & $\beta$ & k & iter & $ D_{\Omega_1}\sp{rel}$& $D_{\Omega_2}\sp{rel} $ & $D_{\Omega_3}\sp{rel} $&$|| g ||\sp{rel} $ \\
+$\alpha$ & $\beta$ & k & iter & $ D_{\Omega_1}\sp{rel}$& $D_{\Omega_2}\sp{rel} $ & $D_{\Omega_3}\sp{rel} $& $||g||\sp{rel} $ \\
 \hline
@@
 \begin{tabular}{*{8}c}
-$\alpha$ & $\beta$ & k & iter & $ D_{\Omega_1}\sp{rel}$ & $ D_{\Omega_2}\sp{rel}$ & $D_{\Omega_3}\sp{rel} $ & $|| g ||\sp{rel} $ \\
+$\alpha$ & $\beta$ & k & iter & $ D_{\Omega_1}\sp{rel}$ & $ D_{\Omega_2}\sp{rel}$ & $D_{\Omega_3}\sp{rel} $ & $||g||\sp{rel} $ \\
 \hline
@@
 \begin{tabular}{*{8}c}
-$\alpha$ & $\beta$ & k  & iter & $ D_{\Omega_1}\sp{rel} $ & $D_{\Omega_2}\sp{rel}$ & $D_{\Omega_3}\sp{rel}$ & $|| g ||\sp{rel} $\\
+$\alpha$ & $\beta$ & k  & iter & $ D_{\Omega_1}\sp{rel} $ & $D_{\Omega_2}\sp{rel}$ & $D_{\Omega_3}\sp{rel}$ & $||g||\sp{rel} $\\
 \hline

### 2018-10-30 tex/paper.tex
minor updates

@@
 
-\title{Assessing paravascular transport in the parenchyma by partial differential equation (PDE) constrained optimization}
+\title{Assessing paravascular transport in the brain by partial differential equation (PDE) constrained optimization}
 
@@
 A proper theoretical foundation
-that explains the fluid transfer mechanisms from first principles however is currently missing.
+that explains the fluid transfer mechanisms from first principles is however currently missing.
 In particular, a crucial question in the current debate is how much the system accelerate
@@
 The work of Sykov{\'a} and Nicholson~\cite{sykova2008diffusion} demonstrated
-that diffusion was a governing transport mechanism in the brain and with an estimated order of magnitude $1.0\mathrm{e}{-4} \mathrm{mm\sp{2}/s}$ for large molecules.
+that diffusion was a governing transport mechanism in the brain at short time-scales and with an estimated order of magnitude $1.0\mathrm{e}{-4} \mathrm{mm\sp{2}/s}$ for large molecules.
 This is confirmed with diffusion tensor imaging (DTI) where young and healthy subjects have typical diffusion values in white matter around $0.7-0.9\mathrm{e}{-3} \mathrm{mm\sp{2}/s}$ \citet{Helenius194},
 while subjects with dementia typically have higher value and variation \cite{goujon2018can}. Of course diffusion coefficients, 
-measured by DTI at a time-scale of 7-30 minutes, may not be representative for the process on a
+measured by DTI at short time-scales may not be representative for the process on a
 longer time-scale, at least if the paravascular pathway plays an important role. The fact that the vascular system occupies around 3\% of the brain volume  \cite{nicholson2001diffusion},
@@
 %That is,
-Thus we aim to investigate whether we can assess an effective diffusion coefficient on long time-scales (hours or days), by fitting a diffusion model to magnetic resonance imaging (MRI) data.
+Thus we aim to investigate whether we can assess an effective diffusion coefficient on long time-scales (hours or days), by fitting a diffusion model to MRI data taken at multiple time-points in which the contrast is spreading through the brain.
 If the fit between observation and model is good and we identify diffusion coefficients that are
@@
 of this paper is a systematic study of the mathematical challenges and that assessing  
-whether clearance is governed by a process that is faster than diffusion is not the topic of the current paper.
+whether clearance is governed by a process that is faster than diffusion is not the topic of the current paper, 
+for that we would need to study several subjects.
 

### 2018-11-11 tex/paper.tex
added affiliations
affiliations

@@
 \usepackage[numbers]{natbib}
-
+\usepackage{authblk}
+\usepackage{ragged2e}
 \title{Assessing paravascular transport in the brain by partial differential equation (PDE) constrained optimization}
@@
 \newcommand{\lars}[1]{\textcolor{magenta}{#1}}
-\author{Lars Magnus Valnes, Sebastian K. Mitusch, Geir Ringstad, \\ 
-Per Kristian Eide, Simon W. Funke, Kent-Andre Mardal }
+
+\renewcommand\Affilfont{\raggedright\small}
+%\renewcommand*{\Affilfont}{\normalsize\normalfont}
+
+\author{Lars Magnus Valnes$\sp{a}$, Sebastian K. Mitusch$\sp{b}$, Geir Ringstad$\sp{c,d}$, \\ 
+Per Kristian Eide$\sp{d,e}$, Simon W. Funke$\sp{b}$, Kent-Andre Mardal$\sp{a,b}$  
+}
+
+\affil{$\sp{a}$Department of Mathematics, University of Oslo, Norway\\
+$\sp{b}$Center for Biomedical Computing, Simula Research Laboratory, Lysaker, Norway \\
+$\sp{c}$Division of Radiology and Nuclear Medicine, Department of Radiology, Oslo \\ \hspace{2pt} University Hospital - Rikshospitalet, Oslo, Norway. \\
+$\sp{d}$Institute of Clinical Medicine, Faculty of Medicine, University of Oslo, Oslo, Norway\\
+$\sp{e}$Department of Neurosurgery, Oslo University Hospital – Rikshospitalet, Oslo, Norway
+
+}
 
@@
 \begin{figure}
-\includegraphics[width=0.95\textwidth]{PatID-68-new-100.png} 
+\includegraphics[width=0.95\textwidth]{PatID-new-100.png} 
 \caption{Shows the percentage change in T1 signal unit ratios from baseline at different observation times. The colorbar was restricted to the range $(0,100)$. }
@@
 \begin{figure}
-\includegraphics[width=0.95\textwidth]{Zoom-PatID-68.png} 
+\includegraphics[width=0.95\textwidth]{Zoom-PatID.png} 
 \caption{Shows the percentage change in T1 signal unit ratios from baseline at different observation times in the slice (marked red in the left panel) used in the subsequent analysis.

### 2018-12-17 tex/paper.tex
needs fixing

@@
 regularization parameters $\alpha$ and $\beta$, we perform a test case with a
-known solution. The manufactured observations were obtained by forward computation of \eqref{Eq::PDE} with the Dirichlet boundary condition defined as
+known solution. The manufactured observations were obtained by forward computation of \eqref{Eq::PDE} with the Dirichlet boundary condition defined as \ficme{Dirichlet boundary $\Omega_1 }
 \begin{equation}

### 2019-02-11 tex/paper.tex
small changes

--- 2018-11-11 tex/paper.tex
@@
 \frac{\partial u}{\partial t} &= \nabla \cdot  D \nabla u && \text{in} \qquad \Omega \times \left\lbrace 0 , T \right)  \\
-u&=g && \text{on} \qquad \partial\Omega  \times \left\lbrace 0 , T \right) 
+u&=g && \text{on} \qquad \partial\Omega_1  \times \left\lbrace 0 , T \right) 
 \end{aligned}
@@
 First of all, the process investigated here is the clearance of Gadovist from CSF into the interstitium which may differ from the clearance of metabolic waste 
-from the interstitium via the CSF. That said, 
-we find that the diffusion coefficients is 42\% larger in grey matter and 100\% larger in white matter than what was found by the DTI modality. As such, we predict that the paravascular system 
-plays a significant role.  
+from the interstitium via the CSF. \fixme{That said, 
+we find that the diffusion coefficients is 42\% larger in grey matter and 100\% larger in white matter than what was found by the DTI modality.
+As such, we predict that the paravascular system  plays a significant role.
+}
 However, we have not yet been able to assess the self-diffusion of water as well as the diffusivity of Gadovist used in this study with phantom models. As such 

### 2019-04-29 tex/rev1/paper.tex
update

--- 2019-02-11 tex/paper.tex
@@
 \usepackage{ragged2e}
-\title{Assessing paravascular transport in the brain by partial differential equation (PDE) constrained optimization}
+\title{
+	Is CSF tracer transporation during 24 hours after infusion explained by diffusion?
+}
 
@@
 aim to quantify long-term (hours/days) transfer mechanism in the brain. 
+\kam{have not looked at the abstract yet}
 
@@
 Evidence was given that the activity of the glymphatic system increases during  sleep by ~\citet{xie2013sleep}, thus linking sleep to clearance of toxic substances from the brain.
-The glymphatic system seems to become impaired during aging, and failure of the glymphatic system may play a role in neurodegenerative disease and development of Alzheimer's disease.
-Evidence for a brain-wide glymphatic system in humans was first obtained in 2015 by \citet{eide2015mri}, and in 2018 \citet{ringstad2018brain} provided evidence that glymphatic function is deteriorated in individuals with dementia, as compared to controls.
-Several aspects of the glympahtic system are still debated, for example whether glymphatic transport of solutes is by convective mechanisms or by diffusion.
+The system proposes that
+the interplay between the cerebrospinal fluid (CSF) and the CSF-filled channels surrounding the vasculature of the brain, traditionally called Wirchow-Robin spaces, are crucial to  
+facilitate this process.  
+These findings are important because both Alzheimer's and Parkinson's diseases are associated with accumulation of metabolic waste products in within various parts of the brain. 
+In \cite{iliff2013brain} a procedure for  investigate paravascular transport was proposed  and tested in a rat's brain. The procedure involved injecting a 
+MRI-contrast into the CSF and image the transportation of the MRI-constrast over a few hours after the injection.  
+The procedure was extended to humans for the first time 
+in 2015 by \citet{eide2015mri} where MRI images where acquired during 48 hours after the injection and quantified in a region-specific manner in 2018 \citet{ringstad2018brain} in individuals with dementia and controls.
+Overall, the MRI-contrast transportation  showed a centripetal and delayed pattern in individuals with dementia as compared with controls~\citet{ringstad2018brain}.
+
+The glympahtic system is controversial as the theory proposes that a significant part of the waste disposal system is driven by convection rather than diffusion. As such
+the system may be much more efficient than if driven by diffusion alone. The theory would also explain why the lymphatic system which elsewhere in our body is crucial for
+removing metabolic waste is not present in the brain even though the brain has a high metabolism; namely that the brain has its own specialized system. 
+The properties of the extracellular diffusion are well-known due to seminal work of Nicholson and colleagues, see  
+~\cite{sykova2008diffusion} for an overview, and is fundamental to for  diffusion tensor imaging (DTI). 
+It has been shown that diffusion coefficients in young and healthy subjects in white matter is around $0.7-0.9\mathrm{e}{-3} \mathrm{mm\sp{2}/s}$ \citet{Helenius194},
+while subjects with dementia typically have higher value and variation \cite{goujon2018can}. 
+For larger molecules such as albumin (65-70 kDa) \citet{cserr1971physiology} estimated that transport by diffusion of a distance of 1 cm would require more than a hundred hours
+and is therefore deemed to slow for the high demands of the brain.  
+The crux of the glymphatic system is as such the fact that conventional DTI imaging is well explained by the traditional view of transportation by extracellular diffusion. 
+However, the paravascular compartments are small, probably less than the vascular compartment that occupy around 3\% of the brain volume. As such, 
+due to its small volume, the paravascular compartment may be dominated by the extracellular compartment at short time-scales, while still being a
+significant contributor on longer time scales.
+
+%Several aspects of the glympahtic system are still debated, for example whether glymphatic transport of solutes is by convective mechanisms or by diffusion.
 
@@
 
-The work of Sykov{\'a} and Nicholson~\cite{sykova2008diffusion} demonstrated
-that diffusion was a governing transport mechanism in the brain at short time-scales and with an estimated order of magnitude $1.0\mathrm{e}{-4} \mathrm{mm\sp{2}/s}$ for large molecules.
-This is confirmed with diffusion tensor imaging (DTI) where young and healthy subjects have typical diffusion values in white matter around $0.7-0.9\mathrm{e}{-3} \mathrm{mm\sp{2}/s}$ \citet{Helenius194},
-while subjects with dementia typically have higher value and variation \cite{goujon2018can}. Of course diffusion coefficients, 
-measured by DTI at short time-scales may not be representative for the process on a
-longer time-scale, at least if the paravascular pathway plays an important role. The fact that the vascular system occupies around 3\% of the brain volume  \cite{nicholson2001diffusion},
-and the paravascular network is substantially smaller potentially renders the paravascular transport  invisible at the short time-scales of a DTI acquisition while it may still be effective on longer time scales.
-
 Our purpose in this paper is to attempt a more rigorous methodology 
@@
 \begin{figure}
-\includegraphics[width=0.95\textwidth]{PatID-new-100.png} 
+\includegraphics[width=0.95\textwidth]{../PatID-new-100.png} 
 \caption{Shows the percentage change in T1 signal unit ratios from baseline at different observation times. The colorbar was restricted to the range $(0,100)$. }
@@
 \begin{figure}
-\includegraphics[width=0.95\textwidth]{Zoom-PatID.png} 
+\includegraphics[width=0.95\textwidth]{../Zoom-PatID.png} 
 \caption{Shows the percentage change in T1 signal unit ratios from baseline at different observation times in the slice (marked red in the left panel) used in the subsequent analysis.
@@
 \centering
-\includegraphics[width=0.70\textwidth]{T1function.png} 
+\includegraphics[width=0.70\textwidth]{../T1function.png} 
 \caption{Shows the  function defined in \eqref{scaledmagnetization} where the white region indicates $T_1$ values for white matter, the grey region indicates $T_1$ values for grey matter, the blue region indicates $T_1$ values for CSF.
@@
 \centering
-\includegraphics[width=0.75\textwidth]{DTI-zoom.png} 
+\includegraphics[width=0.75\textwidth]{../DTI-zoom.png} 
 \caption{The left panel shows the anatomical map.
@@
 \centering
-\includegraphics[scale=0.2]{mesh.png} 
+\includegraphics[scale=0.2]{../mesh.png} 
 \caption{The leftmost image A) shows the mesh created from the baseline MR image with 3 domains, while the rightmost image  B) shows the mesh created from the baseline MR image with 2 domains.
@@
 \centering
-\includegraphics[scale=0.18]{Convergence-plot.png}   
+\includegraphics[scale=0.18]{../Convergence-plot.png}   
 \caption{Convergence plots of the diffusion coefficients, boundary conditions and functional with respect to different $\alpha$ and $\beta$ values. } 
@@
 \centering
-\includegraphics[scale=0.21]{boundary_control.png}  
+\includegraphics[scale=0.21]{../boundary_control.png}  
 \caption{ Displays plots over time for a selection of points at the boundary of $\Omega_1$ with different regularization parameters and number of timesteps $k$.
@@
 \centering
-\includegraphics[scale=0.4]{noise-12.png}  
+\includegraphics[scale=0.4]{../noise-12.png}  
 \caption{The upper row shows the manufactured observation, A) Shows the manufactured observation at time-point 24 with no noise added.
@@
 \centering
-\includegraphics[scale=0.4]{noise-24.png}
+\includegraphics[scale=0.4]{../noise-24.png}
 \caption{The upper row shows the manufactured observation, A) Shows the manufactured observation at time-point 24 with no noise added.
@@
 \centering
-\includegraphics[width=0.95\textwidth]{different.png} 
+\includegraphics[width=0.95\textwidth]{../different.png} 
 \caption{Row A) shows the observation at times 2 hours, 6 hours, 24 hours and 48 hours after the first observation with contrast.
@@
 \centering
-\includegraphics[width=0.95\textwidth]{Statecomparison36h-pinta.png} 
+\includegraphics[width=0.95\textwidth]{../Statecomparison36h-pinta.png} 
 \caption{ Displays the states for different regularization parameters after 36 hours for $k=48$.}

### 2019-04-29 tex/rev1/paper.tex
update

@@
 
-%Several aspects of the glympahtic system are still debated, for example whether glymphatic transport of solutes is by convective mechanisms or by diffusion.
-
-%Recent breakthroughs in medicine have linked neurodegenerative diseases like Alzheimer's to insufficient sleep through a novel fluid mechanism called the glymphatic system 
-%that is responsible for waste clearance. 
-%In 2011,~\citet{iliff2012paravascular} discovered a novel system within our brain's metabolic system, which changed our understanding of the brain. 
-%The system involves a new pathway, called the paravascular pathway as it runs in parallel with the vasculature system in a surrounding compartment.
-%The important novelty in the 2011 findings was that waste from the brain is cleared through the paravascular path, and that a malfunction of this system 
-%is linked to the development of dementia such as Alzheimer's and Parkinson's diseases. In 2013,~\citet{xie2013sleep} found
-%that this system is particularly active during sleep.
-%These mentioned breakthroughs were all performed in mice.
-In 2018, the action of the glymphatic system was for the first time demonstrated in humans.
-Further, it was shown that this action differs between healthy controls and patients with dementia~\cite{ringstad2018brain}.
-%However, the biomechanical mechanisms behind the glymphatic system is not well understood from a fluid mechanics perspective,
-%and so far the modeling attempts have mostly failed~\cite{asgari2016glymphatic, holter2017interstitial, smith2017glymphatic}. 
-%In particular the system seems to facilitate waste transport faster than  
-%the extracellular diffusion, which has been the prevailing paradigm since the pioneering works of \citet{sykova2008diffusion}.
-
-The biomechanical mechanisms are not well understood from a fluid mechanics perspective,
-and so far the modeling attempts have mostly failed~\cite{asgari2016glymphatic, holter2017interstitial, smith2017glymphatic}. 
-In particular the system seems to facilitate waste transport faster than  
-the extracellular diffusion, which has been the prevailing paradigm since the pioneering works of \citet{sykova2008diffusion}
-
-%A novel pathway of the brain's metabolism system called the paravascular pathway, because it runs in parallel with 
-%vasculature system in a surrounding compartment,  
-%was discoved in 2011~\cite{iliff2012paravascular}. 
-%%Later it was found that this system is particularly active during sleep~\cite{xie2013sleep}.  
-%It has been proposed that this pathway plays an important role in the clearance of waste
-%from the brain and hereby a malfunction of this system is linked to  the development of dementia such as Alzheimer's and Parkinson's diseases. That is, 
-%the lymphatic system plays a crucial role in waste clearance in the rest of our body, but there are no lymph vessels inside
-%the brain. As such, the metabolic process of the brain is not well understood and this is surprising since the brain is a very 
-%energy demanding organ (about 10 times as demanding as the average organ). The circulatory system of the paravascular pathway 
-%has therefore been named the glymphatic system~\cite{jessen2015glymphatic} as it has a similar role as the well-known lymphatic system and because the glia cells 
-%are crucial in this system.  
-%The glymphatic system remains controversial and modeling attempts
-%has so far mostly failed to explain the biomechanics of the system~\cite{asgari2016glymphatic, holter2017interstitial, smith2017glymphatic}\kam{Lars: vi trenger flere her}. A proper biomechanical 
-%understanding of the pathway has significant potential because
-%dementia such as Alzheimer´s and Parkinson´s diseases are
-%associated with accumulation of metabolic waste such as
-%amyloid-beta and CSF-tau.
-
 In \cite{ringstad2018brain} brain-wide distribution of MRI-contrast was demonstrated during 24 hours after lumbar contrast injection.
@@
 The argument was based on analytical considerations where it was calculated that 50\% contrast enrichment would occur after
-55 hours using the error function which is valid for planar diffusion. However, 
+55 hours if planar diffusion can be assumed. However, 
 the surface of the brain is folded and is around five times larger than 
@@
 
-Our purpose in this paper is to attempt a more rigorous methodology 
-for assessing the paravascular transport process where
-the complex geometry of the brain as well as time-scales of hours or days are taken into account.
-%That is,
+Our purpose in this paper is to assess the simple question whether the  
+transportation seen in \cite{ringstad2018brain} can be explain by diffusion alone. In order
+to include the complexity of the folding brain surface as well as the non-uniform CSF tracer distribution, we
+will perform finite element simulations of the diffusion process combined with a parameter identification procedure. 
 Thus we aim to investigate whether we can assess an effective diffusion coefficient on long time-scales (hours or days), by fitting a diffusion model to MRI data taken at multiple time-points in which the contrast is spreading through the brain.

### 2019-05-02 tex/rev1/paper.tex
update

@@
 \section{Introduction}
-In 2012, ~\citet{iliff2012paravascular} provided evidence for a brain-wide paravascular system, denoted the glymphatic system, which is a pathway for transport of fluids and solutes.
-It was proposed to have an important metabolic role by providing a pathway for clearance of waste solutes from the brain.
+In 2012, ~\citet{iliff2012paravascular} provided evidence for a new brain-wide circulation system proposed to be crucial in the waste clearance of the brain. As most types
+of dementias are associated with accumulation of metabolic waste within the brain, the new theory is potentially of fundamental importance for
+the pressing challenges of the aging population. The circulation system is called the glymphatic system as it resembles the lymphatic system in the 
+rest of our body and the 'g' highlight the importance of the glia cells.
 Evidence was given that the activity of the glymphatic system increases during  sleep by ~\citet{xie2013sleep}, thus linking sleep to clearance of toxic substances from the brain.
@@
 the interplay between the cerebrospinal fluid (CSF) and the CSF-filled channels surrounding the vasculature of the brain, traditionally called Wirchow-Robin spaces, are crucial to  
-facilitate this process.  
-These findings are important because both Alzheimer's and Parkinson's diseases are associated with accumulation of metabolic waste products in within various parts of the brain. 
+facilitate clearance of waste.  
 In \cite{iliff2013brain} a procedure for  investigate paravascular transport was proposed  and tested in a rat's brain. The procedure involved injecting a 
-MRI-contrast into the CSF and image the transportation of the MRI-constrast over a few hours after the injection.  
+MRI-contrast into the CSF and subsequently image the transportation of the MRI-constrast at multiple time-points during a few hours after the injection.  
 The procedure was extended to humans for the first time 
 in 2015 by \citet{eide2015mri} where MRI images where acquired during 48 hours after the injection and quantified in a region-specific manner in 2018 \citet{ringstad2018brain} in individuals with dementia and controls.
-Overall, the MRI-contrast transportation  showed a centripetal and delayed pattern in individuals with dementia as compared with controls~\citet{ringstad2018brain}.
+Overall, the MRI-contrast transportation  showed a centripetal and delayed pattern in individuals with dementia as compared with controls~\citet{ringstad2018brain} which showed a more centrifugal pattern.
 
@@
 the surface of the brain is folded and is around five times larger than 
-a corresponding surface of a ball with the same volume. Hence, 
-a more rigorous modeling attempt is warranted. A complicating factor
-is however that the contrast in the surrounding cerebral spinal fluid (CSF) is heterogeneous
+a corresponding surface of a ball with the same volume. The increased
+surface-volume ratio of the brain increases the transportation efficiency.  
+On the other hand the contrast in the surrounding cerebral spinal fluid (CSF) is heterogeneous
 and changes significantly during the 24 hours of the investigations. 
-Furthermore, images were obtained only at a few time-points during the investigations in \cite{ringstad2018brain}.
-As such, the sparseness in time prevents a direct computation of the diffusion coefficients.
+The heterogeneous distribution decreases the transportation efficiency as the amount of CSF tracer
+at times is very low. A third difficulty is that  
+MRI images were obtained only at a few time-points (around 10)  during the investigations in \cite{ringstad2018brain} which lasted 48 hours.
 
-Our purpose in this paper is to assess the simple question whether the  
+On this background, our purpose in this paper is to assess the simple question whether the  
 transportation seen in \cite{ringstad2018brain} can be explain by diffusion alone. In order
@@
 Our approach is to solve an optimization problem constrained by a partial differential equation (PDE) using the adjoint method where we have sparse observations on selected time-points, around 10 acquisitions during 24 hours, but through
-the complete domain. Hence, the challenges faced from a mathematical point of view 
-are that 1) the images are subject to noise, 2) resolution in space is limited to slightly less than 1 $\mathrm{mm}^3$ and 3)
-the sparse observations through the time domain. 
-Therefore we need to assess the sensitivity of the approach with respect to important factors, such noise levels and time resolution to determine whether this approach is a viable method to obtain parameters involved time-scales.
-
+the complete domain. 
+%Hence, the challenges faced from a mathematical point of view 
+%are that 1) the images are subject to noise, 2) resolution in space is limited to slightly less than 1 $\mathrm{mm}^3$ and 3)
+%the sparse observations through the time domain. 
+%Therefore we need to assess the sensitivity of the approach with respect to important factors, such noise levels and time resolution to determine whether this approach is a viable method to obtain parameters involved time-scales.
+%
 %As such we need to assess the sensitivity of the approach with respect to important parameters such as the regularization parameters, noise levels and  time resolution to determine whether this approach is a viable method to obtain parameters involved time-scales.
-We remark that the purpose
-of this paper is a systematic study of the mathematical challenges and that assessing  
-whether clearance is governed by a process that is faster than diffusion is not the topic of the current paper, 
-for that we would need to study several subjects.
+%We remark that the purpose
+%of this paper is a systematic study of the mathematical challenges and that assessing  
+%whether clearance is governed by a process that is faster than diffusion is not the topic of the current paper, 
+%for that we would need to study several subjects.
 

### 2019-05-02 tex/rev1/paper.tex
update

@@
 
-\subsection{Contrast concentration - Image Signal Relation}
-Below, we briefly describe the relationship between the imaging signal 
-seen in Figures~\ref{fig1} and \ref{fig2} and the underlying contrast 
-concentration.
-We remark that we use a notation common in medical literature and here two letter symbols are common.
-Hence, below we will use two letter symbols such as $TE$ and $TR$ to keep the notation consistent with the presentation in \cite{GOWLAND, MPRAGE}.
-The contrast concentration $c$ causes the longitudinal(spin-lattice) relaxation time $T_{1}$ to shorten with the following relation
-\begin{equation}
-\frac{1}{T_{1}\sp{c}} = \frac{1}{T_{1}\sp{0}} + r_{1}c .
-\label{EQ::contrast}
-\end{equation}
-The superscripts indicate relaxation time with contrast $T_{1}\sp{c}$ and without contrast $T_{1}\sp{0}$, and $r_1$ is the relaxivity constant for the MRI-contrast in a medium. 
-The contrast observations were collected using a MRI sequence known as  Magnetization Prepared Rapid Acquisition Gradient Echo (MPRAGE) with an inversion prepared magnetization.
-The relation between signal and the relaxation time is non-linear, and is expressed with the following equations.
-The signal value $S$ for this sequence is given by
-\begin{equation}
-S = M_{n} \sin \theta e\sp{ - TE/T_2\sp{*} },
-\label{EQ::SI_T2}
-\end{equation}
-with $TE$ and $\theta$ respectively denoting the echo time and the flip angle, and $M_{n}$ the magnetization for the n-echo described below. 
-Also $T_2\sp{*}$ is transverse magnetization caused by a combination of spin-spin relaxation and magnetic field inhomogeneity. It is defined as 
-\begin{equation}
-\frac{1}{T_2\sp{*}} = \frac{1}{T_2} + \gamma \Delta B_{in} ,
-\end{equation}
-with $T_2$ transverse (spin-spin) relaxation time, $\gamma$ is the gyromagnetic ratio and $\Delta B_{in}$ is the magnetic field inhomogeneity across a voxel.
-The expression can be simplified by neglecting the $T_2$ term in the signal, since $TE <<T_2\sp{*}$ for this MRI sequence.
-Thus \eqref{EQ::SI_T2} becomes
-\begin{equation}
-S = M_{n} \sin \theta.
-\label{EQ::SI}
-\end{equation}
-In article \cite{GOWLAND}, the term $M_n$ is defined as the magnetization for the n-echo 
-\begin{equation}
-M_{n} = M_{0}  \left[ (1-\beta)\frac{(1-(\alpha \beta)\sp{n-1} }{1-\alpha\beta} + (\alpha \beta)\sp{n-1}(1-\gamma) + \gamma ( \alpha \beta)\sp{n-1} \frac{M_{e}}{M_{0}}  \right]   
-\end{equation}
-with 
-\begin{equation}
-\frac{M_{e}}{M_{0}} = - \left[ \frac{ 1 -\delta + \alpha \delta (1-\beta ) \frac{1-\alpha\beta\sp{m}}{1-\alpha \beta} + \alpha\delta(\alpha\beta)\sp{m-1} - \alpha\sp{m}\rho}{1 +\rho \alpha\sp{m} } \right].
-\end{equation}
-Using the following definitions
-\begin{equation}
-\begin{aligned}
-\alpha &= \cos ( \theta ) \\
-\beta  &= e\sp{- \sp{T_b}/_{T_1\sp{c}} } \\
-\delta &= e\sp{- \sp{T_a}/_{T_1\sp{c}} } \\
-\gamma &= e\sp{- \sp{T_w}/_{T_1\sp{c}} } \\
-\rho   &= e\sp{- \sp{TR}/_{T_1\sp{c}}}  \\
-T_w    &= TR - T_a -T_b(m-1)       .\\
-\end{aligned}
-\end{equation}
-Here $T_b$ is known as the echo spacing time, $T_a$ is the inversion time, $T_w$ the time delay, $TR$ as the repetition time, $m$ is the number of echo spacings and $M_0$ is a calibration constant for the magnetization.
-The center echo denoted as $n=m/2$ will be the signal that we will consider when estimating MRI-contrast.
-Given \eqref{EQ::SI} we have that the relative signal increase can be written as
-\begin{equation}
-\frac{S\sp{c}}{S\sp{0}} = \frac{ M_{n}\sp{c} \sin (\theta)}{ M_{n}\sp{0} \sin (\theta) }.
-\end{equation}
-We define that  
-\begin{equation}
-f(T_1) = M_{n}/M_{0} ,
-\label{scaledmagnetization}
-\end{equation}
-which can be seen in Figure~\ref{figuredti}. 
-This gives the following relation 
-\begin{equation}
-\frac{f(T_{1}\sp{c} ) }{f(T_{1}\sp{0})}  = \frac{S\sp{c}}{S\sp{0}} 
-\end{equation}
-The signal difference between observation times were adjusted in \cite{ringstad2018brain}. Thus we can express the change in $T_1$ due to contrast as 
-\begin{equation}
-f ( T_{1}\sp{c} ) = \frac{S\sp{c}}{S\sp{0}} f(T_{1}\sp{0}) 
-\end{equation}
-and then estimate the concentration using \eqref{EQ::contrast}.
-The $T_{1}\sp{0}$ values were obtained by T1-mapping of the brain using a MRI sequence known as MOLLI5(3)3 \cite{TAYLOR201667}.
-This takes into account patient specific characteristic, such as tissue damage.
-Tissue damage can be observed in the MRI due to a lower signal in the white matter compared to healthy white matter tissue, thus damaged tissue have different $T_1$ relaxation time.
-The contrast concentration was estimated in a preprocessing step, using the parameters obtained from the T1-map, MPRAGE MRI protocol \cite{ringstad2018brain} and the value for $r_1$ found in \cite{pmid16230904}.
-In the computation, the function \eqref{scaledmagnetization} was computed for $ T_1\in \lbrace 200, 4000 \rbrace$ creating a lookup table.
-The lookup table was utilized with the baseline signal increase to estimate $T_1\sp{c}$, and then the concentration was computed using \eqref{EQ::contrast}.
-
-\begin{figure}
-\centering
-\includegraphics[width=0.70\textwidth]{../T1function.png} 
-\caption{Shows the  function defined in \eqref{scaledmagnetization} where the white region indicates $T_1$ values for white matter, the grey region indicates $T_1$ values for grey matter, the blue region indicates $T_1$ values for CSF.
-}
-\label{figureF} 
-\end{figure}
-
-\subsection{Diffusion tensor imaging}
-In addition to the T1 and T2 weighted sequences described above we have also obtained diffusion tensor imaging to assess the apparent diffusion 
-coefficients on short time-scales. Images are shown in Figure~\ref{figuredti} where the largest diffusion coefficient (shown in 
-red in the middle figure) is shown to be around $1.0\mathrm{e}{-3}  \mathrm{mm^2/s}$. We remark that we have not included possible anisotropy, shown in 
-the right-most image in Figure~\ref{figuredti} and that these images show the apparent diffusion coefficient for free water molecules (18 Da).      
-The diffusivity of the Gadovist (600 Da) \cite{MGadobutrol} was estimated to be similar to the diffusion coefficient of Gd-DPTA (550 Da) \cite{MGgDPTA}.
-This is due to the fact that both molecules have similar mass, and based on Stoke-Einstein equation should also have similar diffusion coefficients.
-The free diffusion coefficient for Gd-DPTA was estimated in \citet{GdDPTA-DIFFUSION} to be $3.8\mathrm{e}{-4}\mathrm{mm\sp{2}/s}$.
-The fractional anisotropy is defined as 
-\begin{equation}
-FA\sp{2} =  \frac{3}{2} \frac{ (\lambda_1 - MD )\sp{2} +(\lambda_2 - MD )\sp{2} +(\lambda_3 - MD )\sp{2}}{\lambda\sp{2}_1 + \lambda\sp{2}_2  +\lambda\sp{2}_3 },
-\end{equation}
-with the mean diffusivity $MD$ defined as 
-\begin{equation}
-MD = \frac{\lambda_1 +\lambda_2 +\lambda_3 }{3}.
-\end{equation}
-In these equations $\lambda_i$ denotes the eigenvalues of the diffusion tensor.
-\begin{figure}
-\centering
-\includegraphics[width=0.75\textwidth]{../DTI-zoom.png} 
-\caption{The left panel shows the anatomical map.
-The middle panel shows the apparent diffusion coefficients (ADC) obtained from DTI.
-The right panel shows the computed fractional anisotropy (FA) from the DTI.}
-\label{figuredti} 
-\end{figure}
-
 \subsection{Mathematical Model}
@@
 
-\subsection{Manufactured Solution}
-In order to assess the robustness and accuracy of our strategy and test the dependency of the computed diffusion coefficients $D$ on the
-regularization parameters $\alpha$ and $\beta$, we perform a test case with a
-known solution. The manufactured observations were obtained by forward computation of \eqref{Eq::PDE} with the Dirichlet boundary condition defined as 
-\begin{equation}
-g(t) = 0.3 +0.167t - 0.007t\sp{2} \qquad \text{ for } 0 \leq t \leq 24.
-\label{EQ::DIRI}
-\end{equation}
-The initial condition was set to 0 everywhere, the timestep was $dt = 0.2$, and the diffusion coefficients were selected to be 
-\begin{equation}
-D_{\Omega_1} = 1000.0, \quad D_{\Omega_2} = 4.0, \quad D_{\Omega_3} = 8.0 
-\end{equation}  
-The magnitude order for $D_{\Omega_1} $ and $D_{\Omega_2}$ were chosen to resemble diffusion coefficient for water in grey and white matter, but the relation between the coefficients were not preserved.
-In \citet{Haga}, the drug concentration moved 1 cm per 20 seconds in the cervical region, thus $D_{\Omega_1}$  was set to 1000.
-The manufactured forward computation produced a total of 120 possible observation times.
-
-\subsection{Implementation}
-The solver for \eqref{Eq::PDE} was implemented using the FEniCS project (v.2017.2), using backwards Euler time discretization and first order continuous Galerkin finite elements in space.
-The resulting linear problems were solved using GMRES.
-The module dolfin-adjoint \cite{farrell2013automated, funke2013framework} was used to automatically derive and solve the adjoint problem, and to solve the PDE constrained optimization problem with the L-BFGS-B algorithm \cite{LBFGSB1, LBFGSB2}.
-The optimization was stopped when the $L^\infty$-norm of the projected gradient of the objective functional dropped below $1.0\mathrm{e}{-1}$.
-
-The observations $u_{obs}$ have fixed time-points.
-However, these time-points may not coincide  with the time discretization in the forward problem $t_j$.
-Therefore, we linearly interpolated the computed solutions onto the observation time points using the formula
-\begin{equation}
-\label{observation:interpolation}
-u(t) \approx \frac{\Delta t}{dt} u(t_{j-1}) + \frac{dt - \Delta t }{dt} u(t_{j}), \quad t \in \lbrace t_{j-1}, t_j \rbrace
-\end{equation}
-with $\Delta t = t_j-t$ and $dt = t_j - t_{j-1}$.
-
-The implementation used the first observation as initial conditions of \eqref{Eq::PDE}.
-Then for each time-step, the next observation was used as the initial value for boundary control $g$.
-In order to increase the convergence speed of the optimization, $D_{\Omega_1}$ was scaled so that $D_{\Omega_1} = 100 D_{\Omega_1}\sp{\star} $.
-The initial values of the diffusion coefficients in the optimization algorithm were $(D_{\Omega_1}\sp{\star}, D_{\Omega_2}, D_{\Omega_3})=$  $(1, 1, 1)$.
-
-The noise susceptibility was tested by pointwise adding a uniform distributed noise to the observations.
-The noise term was constructed using the random library in numpy and adjusted so that the noise range was $\lbrace -n_{amp} , n_{amp} \rbrace $, with $n_{amp}$ denoted as noise amplitude.
-
 \section{Results}
-\subsection{Verification in terms of the manufactured solution}
-Below we will discuss the parameter identification and its sensitivity with respect to the regularization parameters, noise, number of observations and time-resolution of the forward model.
-When presenting the results, we denote the relative error of the diffusion parameters as
-\begin{equation}
- D_{\Omega_i}\sp{rel} = \frac{D_{\Omega_i}\sp{found} -D_{\Omega_i}\sp{true} }{D_{\Omega_i}\sp{true} }, \text{ for } i=1,2,3
-\end{equation}
-For the boundary parameter $g$, the relative error norm is defined as 
-\begin{equation}
-|| g ||\sp{rel} = \frac{ \sum\limits_{t_j} || g_{found}(t_j) -g_{true}(t_j)||_{L^2(\Omega_1)} }{  \sum\limits_{t_j}||g_{true}(t_j)||_{L^2(\Omega_1)} }
-\end{equation}
-The case when the minimization algorithm fails to converge within 1000 iteration will be indicated by a hyphen in Table~\ref{Tab::Noise0.3}.
-
-\subsubsection{The relaxation parameters}
-The convergence as well as the result of the minimization is influenced by the values of the regularization parameters $\alpha$ and $\beta$.
-Therefore the convergence was examined by a systematic study of the reconstruction of the manufactured solution with respect to a wide range of regularization parameters.
-
-Ideally, our approach should have a wide range of parameters in which the reconstruction algorithm yields very similar end-results although the convergence may vary substantially.
-The evaluation of different regularization parameters was done by solving the optimization with different values of $\alpha$ and $\beta$ and comparing the computed $D$ and $g$ values with the manufactured solution.
-The observation times were set to $\lbrace$2.4, 4.8, 7.2, 9.6, 12.0, 14.4, 16.8, 19.2, 21.6, 24.0 $\rbrace$, and the number of time-steps $k$ in the forward problem was set to $10$.
-
-The results are shown in Table~\ref{Tab::1} and the convergence is shown in Figure~\ref{convergence}.
-We can see that the optimization computed similar end-result for most regularization parameters.
-More specifically, for $\alpha \leq 1\mathrm{e}{-2}$ and $\beta \leq 1e-0$ the relative errors for all optimization parameters are below $5\%$.However, in the case of $ \alpha=1.0$ the relative error is over 100\% higher than for other values of $\alpha$.
-Furthermore, for all $\beta=100.0$ there is about 70\% relative error for $D_{\Omega_1}$ and approximate 10\% error for $D_{\Omega_2}$.
-From the results it can be discerned that $\alpha =1.0$ and $\beta=100.0$ represent an upper threshold where the observations are no longer the dominant term in the objective functional.
-
-\begin{figure}
-\centering
-\includegraphics[scale=0.18]{../Convergence-plot.png}   
-\caption{Convergence plots of the diffusion coefficients, boundary conditions and functional with respect to different $\alpha$ and $\beta$ values. } 
-\label{convergence}
-\end{figure}
-
-In Figure~\ref{boundarycontrol} we can see that more time-steps causes oscillations if $\alpha\gg\beta$ and the number of time-steps are much larger than the number of observations.
-For instance, as seen by the the pink line for $\alpha=1.0$ and $\beta=0.0001$ the peaks corresponds to a observation.
-These oscillations are caused by the strong weighting of $\alpha$, which leads to minimizing of $g$ between observation times.
-Tests with variation in the number of timesteps and observations are documented in the Supplementary.
-
-%It can be seen that more time-steps causes an increase number of iterations, but for some values the number of iterations decreases.
-These values share that $\alpha $ is a magnitude 2 lower than $ \beta$,i.e $\alpha=1.0e-2$ and $\beta =1.0$.
-This indicates that $\alpha $ should be smaller than $\beta$ to achieve optimal convergence.
-However, the number of iterations in Table ~\ref{Tab::1} are smaller for all regularization parameters.
-
-\begin{figure}
-\centering
-\includegraphics[scale=0.21]{../boundary_control.png}  
-\caption{ Displays plots over time for a selection of points at the boundary of $\Omega_1$ with different regularization parameters and number of timesteps $k$.
-The left panel shows the legend for the plot over time, together with the selection of points.
-The middle panel shows the average boundary value $g$ for different regularization parameter with $k=10$.
-The right panel shows the average boundary value $g$ for different regularization parameter with $k=40$.
-}
-\label{boundarycontrol}
-\end{figure}
-
-\subsubsection{The noise susceptibility}
-The MRI data contains noise, hence an investigation to the noise susceptibility is needed.
-This was done varying the noise amplitude, and then the optimization was performed for various regularization parameters $\alpha$ and $\beta$.
-Figure~\ref{12hourswithnoise} and Figure~\ref{24hourswithnoise} show the reconstruction of the manufactured solution at
-different noise levels with $\alpha=0.0001$, $\beta=1.0$ and $k=20$. Clearly, the reconstruction shown in the lower rows is quite robust with respect to the various levels
-of noise shown in the upper rows.      
-In Table~\ref{Tab::Noise0.3} the noise amplitude was set to 0.3 (100$\%$ of maximum initial condition), which gave a visible effect.
-The noise caused the number of iteration to increase, and with more timesteps caused the optimization not to convergence for $\beta < 1.0$.
-Furthermore, the relative boundary error $||g||\sp{rel}$ is significantly larger for $\alpha< 1.0\mathrm{e}{-2} $ and $\beta < 1.0\mathrm{e}{-2}$.
-Results with noise  amplitudes at 0.03 are listed in the Supplementary.
-
-\begin{figure}
-\centering
-\includegraphics[scale=0.4]{../noise-12.png}  
-\caption{The upper row shows the manufactured observation, A) Shows the manufactured observation at time-point 24 with no noise added.
-B) Shows the manufactured observation at time-point 24 with noise amplitude of 0.15.
-C) Shows the manufactures observation at time-point 24 with noise amplitude of 0.3.
-The lower row shows the results with optimized parameter obtained with $\alpha=0.0001$, $\beta=1.0$ and $k=20$.
-D) Shows the resulting state given the observation in A.
-E)  Shows the resulting state given the observation in B .F) Shows the resulting state given the observation in C.
-}
-\label{12hourswithnoise}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[scale=0.4]{../noise-24.png}
-\caption{The upper row shows the manufactured observation, A) Shows the manufactured observation at time-point 24 with no noise added.
-B) Shows the manufactured observation at time-point 24 with noise amplitude of 0.15.
-C) Shows the manufactures observation at time-point 24 with noise amplitude of 0.3.
-The lower row shows the results with optimized parameter obtained with $\alpha=0.0001$, $\beta=1.0$ and $k=20$.
-D) Shows the resulting state given the observation in A.
-E)  Shows the resulting state given the observation in B .F) Shows the resulting state given the observation in C.
-}
-\label{24hourswithnoise}
-\end{figure}
-
 \subsection{A Real case}
@@
 
-\begin{table}
-\centering
-\caption{Shows the regularization parameters $\alpha$ and $\beta$, number of timesteps $k$ with the resulting number of optimization iterations and the relative error for the control parameters.
-The observations times were chosen $ t_i=[2.4, 4.8,$ 7.2, 9.6, 12.0, 14.4, $16.8, 19.2, 21.6, 24.0]$.}
-\begin{tabular}{*{8}c}
-$\alpha$ & $\beta$ & k  & iter & $ D_{\Omega_1}\sp{rel}$ & $ D_{\Omega_2}\sp{rel} $ & $D_{\Omega_3}\sp{rel}$ & $||g||^{rel}$ \\
-\hline 
- 1.0e+00 	 & 1.0e+02 	 & 10 & 437 	 & +4.631 & +0.283 & +0.103 & +0.127 \\ 
- 1.0e+00 	 & 1.0e+00 	 & 10 & 129 	 & +1.638 & +0.224 & +0.089 & +0.119 \\ 
- 1.0e+00 	 & 1.0e-02 	 & 10 & 129 	 & +1.602 & +0.223 & +0.089 & +0.119 \\ 
- 1.0e+00 	 & 1.0e-04 	 & 10 & 151 	 & +1.608 & +0.223 & +0.089 & +0.119 \\ 
- 1.0e+00 	 & 1.0e-06 	 & 10 & 133 	 & +1.603 & +0.223 & +0.089 & +0.119 \\
-
- 1.0e-02 	 & 1.0e+02 	 & 10 & 186 	 & +0.649 & +0.111 & +0.036 & +0.033 \\ 
- 1.0e-02 	 & 1.0e+00 	 & 10 & 125 	 & -0.027 & +0.041 & +0.036 & +0.026 \\ 
- 1.0e-02 	 & 1.0e-02 	 & 10 & 133 	 & -0.039 & +0.039 & +0.036 & +0.026 \\ 
- 1.0e-02 	 & 1.0e-04 	 & 10 & 108 	 & -0.039 & +0.039 & +0.036 & +0.026 \\ 
- 1.0e-02 	 & 1.0e-06 	 & 10 & 154 	 & -0.039 & +0.039 & +0.036 & +0.026 \\
-
- 1.0e-04 	 & 1.0e+02 	 & 10 & 212 	 & +0.636 & +0.108 & +0.035 & +0.032 \\ 
- 1.0e-04 	 & 1.0e+00 	 & 10 & 143 	 & -0.036 & +0.039 & +0.035 & +0.026 \\ 
- 1.0e-04 	 & 1.0e-02 	 & 10 & 108 	 & -0.047 & +0.037 & +0.036 & +0.026 \\ 
- 1.0e-04 	 & 1.0e-04 	 & 10 & 158 	 & -0.047 & +0.037 & +0.036 & +0.026 \\ 
- 1.0e-04 	 & 1.0e-06 	 & 10 & 142 	 & -0.047 & +0.037 & +0.036 & +0.026 \\
-
- 1.0e-06 	 & 1.0e+02 	 & 10 & 203 	 & +0.636 & +0.108 & +0.035 & +0.032 \\ 
- 1.0e-06 	 & 1.0e+00 	 & 10 & 117 	 & -0.035 & +0.039 & +0.035 & +0.026 \\ 
- 1.0e-06 	 & 1.0e-02 	 & 10 & 120 	 & -0.047 & +0.037 & +0.036 & +0.026 \\ 
- 1.0e-06 	 & 1.0e-04 	 & 10 & 122 	 & -0.047 & +0.037 & +0.036 & +0.026 \\ 
- 1.0e-06 	 & 1.0e-06 	 & 10 & 133 	 & -0.047 & +0.037 & +0.036 & +0.026 \\
-
-\end{tabular}
-\label{Tab::1}
-\end{table}
-
-\begin{table}[t]
-\centering
-\caption{Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$, the resulting number of iterations, the relative error of the estimated optimal parameters for the diffusion coefficients and the relative error for $g$.
-The noise amplitude was set to 0.3, and $t_i =[2.4, 4.8, 7.2, 9.6, 12.0, 14.4, 16.8, 19.2, 21.6, 24.0]$  }
-\begin{tabular}{*{8}c}
-$\alpha$ & $\beta$ & k  & iter & $ D_{\Omega_1}\sp{rel}$ & $D_{\Omega_2}\sp{rel} $ & $D_{\Omega_3}\sp{rel} $ & $||g||\sp{rel} $ \\
-\hline
- 1.0e-02 	 & 1.0e+00 	 & 10 & 144 	 & +0.012 & +0.055 & +0.027 & +0.036 \\ 
- 1.0e-02 	 & 1.0e-02 	 & 10 & 476 	 & -0.009 & +0.049 & +0.035 & +0.051 \\ 
- 1.0e-02 	 & 1.0e-04 	 & 10 & 476 	 & -0.097 & +0.042 & +0.054 & +0.054 \\ 
- 1.0e-02 	 & 1.0e-06 	 & 10 & 558 	 & -0.071 & +0.047 & +0.039 & +0.054 \\ 
- 1.0e-04 	 & 1.0e+00 	 & 10 & 182 	 & -0.040 & +0.033 & +0.051 & +0.037 \\ 
- 1.0e-04 	 & 1.0e-02 	 & 10 & 471 	 & +0.021 & +0.038 & +0.036 & +0.056 \\ 
- 1.0e-04 	 & 1.0e-04 	 & 10 & 792 	 & -0.058 & +0.042 & +0.031 & +0.565 \\ 
- 1.0e-04 	 & 1.0e-06 	 & 10 &  -   & -0.050 & +0.029 & +0.040 & +1.062 \\ 
- 1.0e-06 	 & 1.0e+00 	 & 10 & 178 	 & +0.012 & +0.033 & +0.021 & +0.036 \\ 
- 1.0e-06 	 & 1.0e-02 	 & 10 & 537 	 & -0.018 & +0.040 & +0.025 & +0.057 \\ 
- 1.0e-06 	 & 1.0e-04 	 & 10 &  -	 & -0.038 & +0.040 & +0.030 & +1.452 \\ 
- 1.0e-06 	 & 1.0e-06 	 & 10 &  - 	 & +0.003 & +0.035 & +0.046 & +3.621 \\ 
- 1.0e-02 	 & 1.0e+00 	 & 20 & 213 	 & +0.009 & +0.015 & +0.009 & +0.016 \\ 
- 1.0e-02 	 & 1.0e-02 	 & 20 & 719 	 & +0.228 & +0.088 & -0.032 & +0.085 \\ 
- 1.0e-02 	 & 1.0e-04 	 & 20 &  -   & +0.100 & +0.071 & -0.013 & +0.271 \\ 
- 1.0e-02 	 & 1.0e-06 	 & 20 &   -  & +0.223 & +0.097 & -0.027 & +0.282 \\ 
- 1.0e-04 	 & 1.0e+00 	 & 20 & 245 	 & +0.038 & +0.013 & -0.001 & +0.016 \\ 
- 1.0e-04 	 & 1.0e-02 	 & 20 &  - 	 & +0.050 & +0.054 & -0.024 & +0.116 \\ 
- 1.0e-04 	 & 1.0e-04 	 & 20 &  - 	 & -0.087 & +0.059 & -0.077 & +5.763 \\ 
- 1.0e-04 	 & 1.0e-06 	 & 20 &  -	 & +0.001 & +0.083 & -0.038 & +7.485 \\ 
- 1.0e-06 	 & 1.0e+00 	 & 20 & 242 	 & -0.009 & +0.008 & +0.015 & +0.016 \\ 
- 1.0e-06 	 & 1.0e-02 	 & 20 & 947 	 & +0.122 & +0.093 & -0.040 & +0.115 \\ 
- 1.0e-06 	 & 1.0e-04 	 & 20 &  - 	 & -0.076 & +0.041 & -0.020 & +7.700 \\ 
- 1.0e-06 	 & 1.0e-06 	 & 20 &  - 	 & +0.147 & +0.113 & -0.023 & +10.936 \\
-
-\end{tabular}
-\label{Tab::Noise0.3}
-\end{table}
-
-\begin{table}
-\centering
-\caption{Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$, the resulting number of iterations, the estimated diffusion coefficients for grey $D_{\Omega_{GM}}$ and white $D_{\Omega_{WM}}$ matter based on MRI data.}
-\begin{tabular}{*{6}c}
-$\alpha$ & $\beta$ & k & iter &  $ D_{\Omega_{GM}} \left[ \mathrm{mm\sp{2}/h} \right] $ & $ D_{\Omega_{WM}} \left[ \mathrm{mm\sp{2}/h} \right]$ \\
-\hline
- 1.0e-02 	 & 1.0e+00 	 & 24 & 503 	 & 0.659 & 0.918 \\ 
- 1.0e-02 	 & 1.0e-01 	 & 24 & 716 	 & 0.771 & 0.969 \\ 
- 1.0e-02 	 & 1.0e-02 	 & 24 & 505 	 & 0.836 & 0.974 \\ 
- 1.0e-04 	 & 1.0e+00 	 & 24 & 206 	 & 0.553 & 0.828 \\ 
- 1.0e-04 	 & 1.0e-01 	 & 24 & 440 	 & 0.651 & 0.789 \\ 
- 1.0e-04 	 & 1.0e-02 	 & 24 & 597 	 & 0.718 & 0.739 \\ 
- 1.0e-06 	 & 1.0e+00 	 & 24 & 439 	 & 0.570 & 0.830 \\ 
- 1.0e-06 	 & 1.0e-01 	 & 24 & 583 	 & 0.656 & 0.793 \\ 
- 1.0e-06 	 & 1.0e-02 	 & 24 & 742 	 & 0.721 & 0.729 \\
-
- %1.0e-02    & 1.0e+02   & 48 & 714      & 0.564 & 0.952 ?? \\ 
- 1.0e-02 	 & 1.0e+00 	 & 48 & 591 	 & 0.648 & 0.893 \\ 
- 1.0e-02 	 & 1.0e-01 	 & 48 & 461 	 & 0.772 & 0.982 \\ 
- 1.0e-02 	 & 1.0e-02 	 & 48 & 748 	 & 0.986 & 1.198 \\ 
- %1.0e-04    & 1.0e+02   & 48 & 815      & 0.470 & 0.928 \\ 
- 1.0e-04 	 & 1.0e+00 	 & 48 & 607 	 & 0.551 & 0.815 \\ 
- 1.0e-04 	 & 1.0e-01 	 & 48 & 598 	 & 0.649 & 0.787 \\ 
- 1.0e-04 	 & 1.0e-02 	 & 48 & 837 	 & 0.740 & 0.817 \\
- %1.0e-06    & 1.0e+02   & 48 & 729      & 0.428 & 0.948 \\ 
- 1.0e-06 	 & 1.0e+00 	 & 48 & 681 	 & 0.557 & 0.811 \\ 
- 1.0e-06 	 & 1.0e-01 	 & 48 & 780 	 & 0.645 & 0.774 \\ 
- 1.0e-06 	 & 1.0e-02 	 & 48 & 745 	 & 0.736 & 0.819 \\
-
-\end{tabular}
-\label{Tab::Real-data}
-\end{table}
-
-\clearpage
-\section{Supplementary}
-
-\subsubsection{The number of timessteps}
-Increasing the number of time-steps in the computations can potentially allow for a more accurate temporal reconstruction, but at the same time the number of observations per control decreases and the regularization may therefore play a larger role.
-Furthermore, the computational cost will rise with additional time-steps.
-Thus finding the optimal number of time-steps can be essential for solving larger problems.
-The computation used a wide range the regularization parameters, and the number of timesteps were selected to be 20 and 40.
-
-The results are given in Table~\ref{TAB::timesteps}.
-It can be seen for all $\alpha=1.0$ that the relative error becomes bigger with more time-steps.
-This behavior can also be seen for $\alpha=1.0\mathrm{e}{-2}$ and $\beta < 1.0\mathrm{e}{-2}$, which implies an interaction between the regularization parameters.
-Therefore $g$ was investigated by plotting boundary points through time for different values of $\alpha$ and $\beta$, see Fig \ref{boundarycontrol}.
-
-\begin{table}
-\centering
-\caption{ Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$, the resulting number of iterations, the relative error of the estimated diffusion coefficients and the relative error for $g$.
-The observations times were chosen $ t_i=[2.4,  4.8,$ 7.2, 9.6, 12.0, 14.4, $16.8, 19.2, 21.6, 24.0]$ }
-\begin{tabular}{*{8}c}
-$\alpha$ & $\beta$ & k & iter & $ D_{\Omega_1}\sp{rel}$& $D_{\Omega_2}\sp{rel} $ & $D_{\Omega_3}\sp{rel} $&$|| g ||\sp{rel} $ \\
-\hline
- 1.0e+00 	 & 1.0e+02 	 & 20 & 600 	 & +6.412 & +0.175 & +0.086 & +0.124 \\
- 1.0e+00 	 & 1.0e+02 	 & 40 &  -   & +6.702 & +0.130 & +0.082 & +0.125 \\  
- 1.0e+00 	 & 1.0e+00 	 & 20 & 300 	 & +5.538 & +0.324 & +0.148 & +0.128 \\ 
- 1.0e+00 	 & 1.0e+00 	 & 40 & 346 	 & +11.392 & +0.873 & +0.242 & +0.154 \\ 
- 1.0e+00 	 & 1.0e-02 	 & 20 & 415 	 & +18.156 & +1.378  & +0.389  & +0.251 \\ 
- 1.0e+00 	 & 1.0e-02 	 & 40 & 856 	 & +64.050 & +17.408 & +15.950 & +0.614 \\ 
- 1.0e+00 	 & 1.0e-04 	 & 20 & 417 	 & +17.747 & +1.465  & +0.406  & +0.258 \\ 
- 1.0e+00 	 & 1.0e-04 	 & 40 & 946 	 & +72.594 & +17.985 & +16.702 & +0.641 \\
- 1.0e+00 	 & 1.0e-06 	 & 20 & 399 	 & +17.407 & +1.466  & +0.406  & +0.258 \\ 
- 1.0e+00 	 & 1.0e-06 	 & 40 & 863 	 & +60.448 & +18.043 & +16.732 & +0.641 \\
- \hline
- 1.0e-02 	 & 1.0e+02 	 & 20 & 351 	 & +0.865 & +0.001 & +0.017 & +0.027 \\ 
- 1.0e-02 	 & 1.0e+02 	 & 40 & 404 	 & +0.846 & -0.049 & +0.010 & +0.026 \\ 
- 1.0e-02 	 & 1.0e+00 	 & 20 & 254 	 & +0.018 & +0.007 & +0.008 & +0.007 \\ 
- 1.0e-02 	 & 1.0e+00 	 & 40 & 218 	 & +0.020 & -0.006 & +0.001 & +0.003 \\ 
- 1.0e-02 	 & 1.0e-02 	 & 20 & 381 	 & +0.127 & +0.057 & -0.001 & +0.016 \\ 
- 1.0e-02 	 & 1.0e-02 	 & 40 & 543 	 & +0.099 & +0.087 & +0.002 & +0.023 \\
- 1.0e-02 	 & 1.0e-04 	 & 20 & 641 	 & +0.171 & +0.082 & -0.003 & +0.091 \\ 
- 1.0e-02 	 & 1.0e-04 	 & 40 & 879 	 & +0.303 & +0.383 & +0.079 & +0.222 \\ 
- 1.0e-02 	 & 1.0e-06 	 & 20 & 547 	 & +0.173 & +0.084 & -0.003 & +0.092 \\
- 1.0e-02 	 & 1.0e-06 	 & 40 & 844 	 & +0.332 & +0.416 & +0.095 & +0.239 \\ 
- \hline 
- 1.0e-04 	 & 1.0e+02 	 & 20 & 257 	 & +0.853 & -0.001 & +0.017 & +0.026 \\ 
- 1.0e-04 	 & 1.0e+02 	 & 40 & 532 	 & +0.822 & -0.051 & +0.010 & +0.026 \\ 
- 1.0e-04 	 & 1.0e+00 	 & 20 & 164 	 & +0.008 & +0.003 & +0.008 & +0.007 \\ 
- 1.0e-04 	 & 1.0e+00 	 & 40 & 203 	 & +0.005 & -0.012 & +0.001 & +0.003 \\  
- 1.0e-04 	 & 1.0e-02 	 & 20 & 313 	 & +0.071 & +0.021 & -0.001 & +0.007 \\ 
- 1.0e-04 	 & 1.0e-02 	 & 40 & 294 	 & +0.004 & +0.004 & -0.001 & +0.001 \\ 
- 1.0e-04 	 & 1.0e-04 	 & 20 & 265 	 & +0.108 & +0.035 & -0.002 & +0.014 \\
- 1.0e-04 	 & 1.0e-04 	 & 40 & 401 	 & -0.010 & -0.002 & -0.002 & +0.004 \\ 
- 1.0e-04 	 & 1.0e-06 	 & 20 & 452 	 & +0.066 & +0.021 & -0.003 & +0.031 \\ 
- 1.0e-04 	 & 1.0e-06 	 & 40 & 330 	 & -0.014 & -0.013 & -0.003 & +0.004 \\ 
- \hline
- 1.0e-06 	 & 1.0e+02 	 & 20 & 274 	 & +0.850 & -0.001 & +0.017 & +0.026 \\ 
- 1.0e-06 	 & 1.0e+02 	 & 40 & 496 	 & +0.821 & -0.051 & +0.010 & +0.026 \\
- 1.0e-06 	 & 1.0e+00 	 & 20 & 176 	 & +0.008 & +0.003 & +0.008 & +0.007 \\ 
- 1.0e-06 	 & 1.0e+00 	 & 40 & 207 	 & +0.006 & -0.012 & +0.001 & +0.003 \\ 
- 1.0e-06 	 & 1.0e-02 	 & 20 & 223 	 & +0.075 & +0.024 & -0.001 & +0.007 \\ 
- 1.0e-06 	 & 1.0e-02 	 & 40 & 392 	 & +0.000 & -0.001 & -0.001 & +0.002 \\ 
- 1.0e-06 	 & 1.0e-04 	 & 20 & 429 	 & +0.085 & +0.027 & -0.002 & +0.025 \\ 
- 1.0e-06 	 & 1.0e-04 	 & 40 & 241 	 & -0.020 & -0.030 & -0.005 & +0.005 \\ 
- 1.0e-06 	 & 1.0e-06 	 & 20 & 591 	 & +0.060 & +0.021 & -0.003 & +0.048 \\ 
- 1.0e-06 	 & 1.0e-06 	 & 40 & 343 	 & -0.014 & -0.010 & -0.003 & +0.004 \\
-
-\end{tabular}
-\label{TAB::timesteps}
-\end{table}
-
-\subsubsection{The number of observations}
-The dependency on observations is relevant, since the number of observations of the MRI data is limited.
-This dependency was investigated by changing the number of observations, and by examining the results.
-The number of observation were chosen to be 5 and 20, and the observation times were evenly spaced.
-
-The results for 5 observations is shown in Table~\ref{TAB::half} and for 20 observations is shown in Table~\ref{TAB::double}.
-In Table~\ref{TAB::half}, the values $\alpha =1.0\mathrm{e}{-2}$ and $\beta<1.0$ gives a surge in the relative error with more time-steps.
-This behavior is neither visible in Table~\ref{TAB::timesteps} or in  Table~\ref{TAB::double} for the same regularization parameters.
-The ratio observations per control indicates that the increase in relative error is due to oscillations, similar to those seen in Figure~\ref{boundarycontrol}.
-Thus the observations acts as stabilization for the functional, which gives a broader range of adequate regularization parameters.
-
-\begin{table}
-\centering
-\caption{ Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$, the resulting number of iterations, the relative error of the estimated diffusion coefficients and the relative error for $g$.
-The observation times were set $t_i = [ 4.8, 9.6, 14.4, 19.2, 24.0 ] $.
-}
-\begin{tabular}{*{8}c}
-$\alpha$ & $\beta$ & k & iter & $ D_{\Omega_1}\sp{rel}$& $D_{\Omega_2}\sp{rel} $ & $D_{\Omega_3}\sp{rel} $& $||g||\sp{rel} $ \\
-\hline
- 1.0e-02 	 & 1.0e+00 	 & 10 & 151 	 & +0.095 & +0.015 & +0.028 & +0.020 \\ 
- 1.0e-02 	 & 1.0e+00 	 & 20 & 165 	 & +0.092 & -0.001 & -0.001 & +0.008 \\ 
- 1.0e-02 	 & 1.0e+00 	 & 40 & 228 	 & +0.067 & -0.024 & -0.011 & +0.005 \\
-
- 1.0e-02 	 & 1.0e-02 	 & 10 & 330 	 & +0.190 & +0.074 & +0.027 & +0.083 \\ 
- 1.0e-02 	 & 1.0e-02 	 & 20 & 455 	 & +3.882 & +3.297 & +2.583 & +0.304 \\ 
-  1.0e-02 	 & 1.0e-02 	 & 40 & 523 	 & +7.466 & +6.454 & +5.537 & +0.388 \\
-
- 1.0e-02 	 & 1.0e-04 	 & 10 & 428 	 & +0.196 & +0.076 & +0.032 & +0.163 \\ 
- 1.0e-02 	 & 1.0e-04 	 & 20 & 571 	 & +7.402 & +6.421 & +5.405 & +0.680 \\ 
- 1.0e-02 	 & 1.0e-04 	 & 40 & 747 	 & +15.386 & +13.764 & +12.196 & +0.841 \\
-
-  1.0e-04 	 & 1.0e+00 	 & 10 & 147 	 & +0.081 & +0.008 & +0.023 & +0.020 \\ 
-  1.0e-04 	 & 1.0e+00 	 & 20 & 167 	 & +0.051 & -0.026 & -0.009 & +0.008 \\ 
-  1.0e-04 	 & 1.0e+00 	 & 40 & 148 	 & +0.018 & -0.057 & -0.020 & +0.005 \\
-
- 1.0e-04 	 & 1.0e-02 	 & 10 & 255 	 & +0.171 & +0.087 & +0.010 & +0.021 \\ 
- 1.0e-04 	 & 1.0e-02 	 & 20 & 216 	 & -0.005 & -0.006 & -0.008 & +0.008 \\ 
- 1.0e-04 	 & 1.0e-02 	 & 40 & 386 	 & -0.004 & -0.012 & -0.015 & +0.004 \\
-
- 1.0e-04 	 & 1.0e-04 	 & 10 & 284 	 & +0.059 & +0.052 & +0.010 & +0.051 \\ 
- 1.0e-04 	 & 1.0e-04 	 & 20 & 256 	 & -0.048 & -0.045 & -0.024 & +0.020 \\ 
-  1.0e-04 	 & 1.0e-04 	 & 40 & 277 	 & -0.071 & -0.074 & -0.050 & +0.018 \\
-
- 1.0e-06 	 & 1.0e+00 	 & 10 & 163 	 & +0.082 & +0.008 & +0.023 & +0.020 \\ 
- 1.0e-06 	 & 1.0e+00 	 & 20 & 156 	 & +0.054 & -0.027 & -0.009 & +0.008 \\ 
- 1.0e-06 	 & 1.0e+00 	 & 40 & 284 	 & +0.020 & -0.055 & -0.019 & +0.005 \\
-
- 1.0e-06 	 & 1.0e-02 	 & 10 & 290 	 & +0.155 & +0.075 & +0.011 & +0.021 \\ 
- 1.0e-06 	 & 1.0e-02 	 & 20 & 239 	 & -0.004 & +0.002 & -0.006 & +0.008 \\ 
- 1.0e-06 	 & 1.0e-02 	 & 40 & 378 	 & -0.005 & -0.013 & -0.016 & +0.004 \\
-
- 1.0e-06 	 & 1.0e-04 	 & 10 & 264 	 & +0.070 & +0.056 & +0.009 & +0.050 \\ 
- 1.0e-06 	 & 1.0e-04 	 & 20 & 234 	 & -0.047 & -0.044 & -0.029 & +0.020 \\
- 1.0e-06 	 & 1.0e-04 	 & 40 & 324 	 & -0.070 & -0.070 & -0.052 & +0.017 \\
-
-\end{tabular}
-\label{TAB::half}
-\end{table}
-
-\begin{table}
-\centering
-\caption{ Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$, the resulting number of iterations, the relative error of the estimated diffusion coefficients and the relative error for $g$.
-The observation times were $t_i = [ $1.2, 2.4, 3.6, 4.8, 6.0, 7.2, 8.4, 9.6, 10.8, 12.0, 13.2, 14.4, 15.6, 16.8, 17.0, 19.2, 20.4,$ 21.6, 22.8, 24.0 ]$.}
-\begin{tabular}{*{8}c}
-$\alpha$ & $\beta$ & k & iter & $ D_{\Omega_1}\sp{rel}$ & $ D_{\Omega_2}\sp{rel}$ & $D_{\Omega_3}\sp{rel} $ & $||g||\sp{rel} $ \\
-\hline
-
- 1.0e-02 	 & 1.0e+00 	 & 10 & 250 	 & -0.038 & +0.035 & +0.019 & +0.033 \\ 
- 1.0e-02 	 & 1.0e+00 	 & 20 & 225 	 & -0.002 & +0.015 & +0.007 & +0.007 \\ 
- 1.0e-02 	 & 1.0e+00 	 & 40 & 255 	 & +0.003 & +0.002 & +0.001 & +0.002 \\
-
- 1.0e-02 	 & 1.0e-02 	 & 10 & 180 	 & -0.042 & +0.034 & +0.020 & +0.033 \\ 
- 1.0e-02 	 & 1.0e-02 	 & 20 & 445 	 & +0.010 & +0.017 & +0.003 & +0.010 \\ 
-  1.0e-02 	 & 1.0e-02 	 & 40 & 429 	 & +0.037 & +0.014 & -0.003 & +0.004 \\
-
- 1.0e-02 	 & 1.0e-04 	 & 10 & 208 	 & -0.042 & +0.034 & +0.020 & +0.033 \\ 
-  1.0e-02 	 & 1.0e-04 	 & 20 & 530 	 & +0.012 & +0.017 & +0.003 & +0.020 \\ 
- 1.0e-02 	 & 1.0e-04 	 & 40 & - 	 & +0.064 & +0.023 & -0.005 & +0.072 \\
-
- 1.0e-04 	 & 1.0e+00 	 & 10 & 209 	 & -0.043 & +0.033 & +0.019 & +0.033 \\ 
- 1.0e-04 	 & 1.0e+00 	 & 20 & 212 	 & -0.007 & +0.014 & +0.007 & +0.007 \\ 
- 1.0e-04 	 & 1.0e+00 	 & 40 & 258 	 & -0.002 & +0.001 & +0.001 & +0.002 \\
-
- 1.0e-04 	 & 1.0e-02 	 & 10 & 258 	 & -0.047 & +0.033 & +0.020 & +0.033 \\ 
- 1.0e-04 	 & 1.0e-02 	 & 20 & 391 	 & +0.005 & +0.016 & +0.003 & +0.008 \\ 
- 1.0e-04 	 & 1.0e-02 	 & 40 & 261 	 & +0.014 & +0.005 & -0.002 & +0.001 \\
-
- 1.0e-04 	 & 1.0e-04 	 & 10 & 267 	 & -0.047 & +0.033 & +0.020 & +0.033 \\ 
- 1.0e-04 	 & 1.0e-04 	 & 20 & 769 	 & +0.008 & +0.016 & +0.003 & +0.016 \\
- 1.0e-04 	 & 1.0e-04 	 & 40 & 375 	 & +0.027 & +0.005 & -0.003 & +0.002 \\
-
- 1.0e-06 	 & 1.0e+00 	 & 10 & 198 	 & -0.042 & +0.033 & +0.019 & +0.033 \\ 
- 1.0e-06 	 & 1.0e+00 	 & 20 & 222 	 & -0.007 & +0.014 & +0.007 & +0.007 \\ 
- 1.0e-06 	 & 1.0e+00 	 & 40 & 280 	 & -0.001 & +0.001 & +0.001 & +0.002 \\
-
- 1.0e-06 	 & 1.0e-02 	 & 10 & 279 	 & -0.047 & +0.033 & +0.020 & +0.033 \\ 
- 1.0e-06 	 & 1.0e-02 	 & 20 & 312 	 & +0.005 & +0.016 & +0.003 & +0.008 \\ 
- 1.0e-06 	 & 1.0e-02 	 & 40 & 379 	 & +0.015 & +0.005 & -0.002 & +0.001 \\
-
- 1.0e-06 	 & 1.0e-04 	 & 10 & 251 	 & -0.047 & +0.033 & +0.020 & +0.033 \\ 
- 1.0e-06 	 & 1.0e-04 	 & 20 & 778 	 & +0.008 & +0.016 & +0.002 & +0.018 \\ 
- 1.0e-06 	 & 1.0e-04 	 & 40 & 191 	 & +0.017 & +0.004 & -0.002 & +0.002 \\
-
-\end{tabular}
-\label{TAB::double}
-\end{table}
-
-In Table~\ref{Tab::Noise0.03}, we can see that a noise amplitude of 0.03, (10$\%$ of maximum initial condition) had negligible effect on the relative errors compared zero noise in Table~\ref{Tab::1} and Table~\ref{TAB::timesteps}.
-
-\begin{table}
-\centering
-\caption{Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$, the resulting number of iterations, the relative error of the estimated optimal parameters for the diffusion coefficients and the relative error for $g$.
-The noise amplitude was set to 0.03, and $ t_i=[2.4, 4.8, 7.2, 9.6, 12.0, 14.4, 16.8, 19.2, 21.6, 24.0]$ }
-\begin{tabular}{*{8}c}
-$\alpha$ & $\beta$ & k  & iter & $ D_{\Omega_1}\sp{rel} $ & $D_{\Omega_2}\sp{rel}$ & $D_{\Omega_3}\sp{rel}$ & $||g||\sp{rel} $\\
-\hline
- 1.0e-02 	 & 1.0e+00 	 & 10 & 151 	 & -0.030 & +0.041 & +0.036 & +0.026 \\ 
- 1.0e-02 	 & 1.0e-02 	 & 10 & 120 	 & -0.032 & +0.039 & +0.036 & +0.026 \\ 
- 1.0e-02 	 & 1.0e-04 	 & 10 & 125 	 & -0.038 & +0.039 & +0.037 & +0.026 \\ 
- 1.0e-02 	 & 1.0e-06 	 & 10 & 167 	 & -0.040 & +0.039 & +0.036 & +0.026 \\ 
- 1.0e-04 	 & 1.0e+00 	 & 10 & 161 	 & -0.038 & +0.039 & +0.035 & +0.026 \\ 
- 1.0e-04 	 & 1.0e-02 	 & 10 & 95 	 & -0.047 & +0.036 & +0.036 & +0.026 \\ 
- 1.0e-04 	 & 1.0e-04 	 & 10 & 75 	 & -0.041 & +0.036 & +0.035 & +0.026 \\ 
- 1.0e-04 	 & 1.0e-06 	 & 10 & 136 	 & -0.044 & +0.036 & +0.036 & +0.026 \\ 
- 1.0e-06 	 & 1.0e+00 	 & 10 & 134 	 & -0.034 & +0.037 & +0.037 & +0.026 \\ 
- 1.0e-06 	 & 1.0e-02 	 & 10 & 112 	 & -0.046 & +0.038 & +0.036 & +0.026 \\ 
- 1.0e-06 	 & 1.0e-04 	 & 10 & 111 	 & -0.043 & +0.036 & +0.037 & +0.026 \\ 
- 1.0e-06 	 & 1.0e-06 	 & 10 & 214 	 & -0.049 & +0.037 & +0.036 & +0.026 \\
-
- 1.0e-02 	 & 1.0e+00 	 & 20 & 190 	 & +0.013 & +0.006 & +0.008 & +0.007 \\ 
- 1.0e-02 	 & 1.0e-02 	 & 20 & 392 	 & +0.126 & +0.057 & +0.001 & +0.017 \\ 
- 1.0e-02 	 & 1.0e-04 	 & 20 & 677 	 & +0.164 & +0.074 & -0.001 & +0.093 \\ 
- 1.0e-02 	 & 1.0e-06 	 & 20 & 600 	 & +0.179 & +0.081 & -0.001 & +0.098 \\ 
- 1.0e-04 	 & 1.0e+00 	 & 20 & 224 	 & +0.006 & +0.004 & +0.008 & +0.007 \\ 
- 1.0e-04 	 & 1.0e-02 	 & 20 & 465 	 & +0.074 & +0.022 & -0.003 & +0.008 \\ 
- 1.0e-04 	 & 1.0e-04 	 & 20 & 586 	 & +0.071 & +0.023 & -0.005 & +0.056 \\ 
- 1.0e-04 	 & 1.0e-06 	 & 20 & 472 	 & +0.081 & +0.024 & -0.003 & +0.056 \\ 
- 1.0e-06 	 & 1.0e+00 	 & 20 & 157 	 & +0.011 & +0.003 & +0.009 & +0.007 \\ 
- 1.0e-06 	 & 1.0e-02 	 & 20 & 352 	 & +0.076 & +0.021 & +0.000 & +0.008 \\ 
- 1.0e-06 	 & 1.0e-04 	 & 20 & 738 	 & +0.083 & +0.026 & -0.004 & +0.065 \\ 
- 1.0e-06 	 & 1.0e-06 	 & 20 & 599 	 & +0.056 & +0.021 & -0.003 & +0.106 \\
-
-\end{tabular}
-\label{Tab::Noise0.03}
-\end{table}
+%\input{supplementary}
 

### 2019-05-02 tex/rev1/supplementary.tex
update

--- 2018-11-11 tex/paper.tex
@@
-\documentclass[12pt,a4paper]{article}
-\usepackage{hyperref}
-\usepackage{color}
-\usepackage{amsmath, amsthm, amssymb, amsfonts, verbatim}
-\usepackage{graphicx}
-\usepackage[table,x11names]{xcolor}
-\usepackage{geometry}
-\usepackage{subcaption}
-\usepackage[numbers]{natbib}
-\usepackage{authblk}
-\usepackage{ragged2e}
-\title{Assessing paravascular transport in the brain by partial differential equation (PDE) constrained optimization}
+\clearpage
+\section{Supplementary}
 
-\renewcommand{\comment}[1]{\textcolor{red}{#1}}
+\subsection{Verification in terms of the manufactured solution}
+Below we will discuss the parameter identification and its sensitivity with respect to the regularization parameters, noise, number of observations and time-resolution of the forward model.
+When presenting the results, we denote the relative error of the diffusion parameters as
+\begin{equation}
+ D_{\Omega_i}\sp{rel} = \frac{D_{\Omega_i}\sp{found} -D_{\Omega_i}\sp{true} }{D_{\Omega_i}\sp{true} }, \text{ for } i=1,2,3
+\end{equation}
+For the boundary parameter $g$, the relative error norm is defined as 
+\begin{equation}
+|| g ||\sp{rel} = \frac{ \sum\limits_{t_j} || g_{found}(t_j) -g_{true}(t_j)||_{L^2(\Omega_1)} }{  \sum\limits_{t_j}||g_{true}(t_j)||_{L^2(\Omega_1)} }
+\end{equation}
+The case when the minimization algorithm fails to converge within 1000 iteration will be indicated by a hyphen in Table~\ref{Tab::Noise0.3}.
 
-\newcommand{\kam}[1]{\textcolor{blue}{#1}}
-\newcommand{\fixme}[1]{\textcolor{orange}{#1}}
-\newcommand{\lars}[1]{\textcolor{magenta}{#1}}
+\subsubsection{The relaxation parameters}
+The convergence as well as the result of the minimization is influenced by the values of the regularization parameters $\alpha$ and $\beta$.
+Therefore the convergence was examined by a systematic study of the reconstruction of the manufactured solution with respect to a wide range of regularization parameters.
 
-\renewcommand\Affilfont{\raggedright\small}
-%\renewcommand*{\Affilfont}{\normalsize\normalfont}
+Ideally, our approach should have a wide range of parameters in which the reconstruction algorithm yields very similar end-results although the convergence may vary substantially.
+The evaluation of different regularization parameters was done by solving the optimization with different values of $\alpha$ and $\beta$ and comparing the computed $D$ and $g$ values with the manufactured solution.
+The observation times were set to $\lbrace$2.4, 4.8, 7.2, 9.6, 12.0, 14.4, 16.8, 19.2, 21.6, 24.0 $\rbrace$, and the number of time-steps $k$ in the forward problem was set to $10$.
 
-\author{Lars Magnus Valnes$\sp{a}$, Sebastian K. Mitusch$\sp{b}$, Geir Ringstad$\sp{c,d}$, \\ 
-Per Kristian Eide$\sp{d,e}$, Simon W. Funke$\sp{b}$, Kent-Andre Mardal$\sp{a,b}$  
+The results are shown in Table~\ref{Tab::1} and the convergence is shown in Figure~\ref{convergence}.
+We can see that the optimization computed similar end-result for most regularization parameters.
+More specifically, for $\alpha \leq 1\mathrm{e}{-2}$ and $\beta \leq 1e-0$ the relative errors for all optimization parameters are below $5\%$.However, in the case of $ \alpha=1.0$ the relative error is over 100\% higher than for other values of $\alpha$.
+Furthermore, for all $\beta=100.0$ there is about 70\% relative error for $D_{\Omega_1}$ and approximate 10\% error for $D_{\Omega_2}$.
+From the results it can be discerned that $\alpha =1.0$ and $\beta=100.0$ represent an upper threshold where the observations are no longer the dominant term in the objective functional.
+
+\begin{figure}
+\centering
+\includegraphics[scale=0.18]{../Convergence-plot.png}   
+\caption{Convergence plots of the diffusion coefficients, boundary conditions and functional with respect to different $\alpha$ and $\beta$ values. } 
+\label{convergence}
+\end{figure}
+
+In Figure~\ref{boundarycontrol} we can see that more time-steps causes oscillations if $\alpha\gg\beta$ and the number of time-steps are much larger than the number of observations.
+For instance, as seen by the the pink line for $\alpha=1.0$ and $\beta=0.0001$ the peaks corresponds to a observation.
+These oscillations are caused by the strong weighting of $\alpha$, which leads to minimizing of $g$ between observation times.
+Tests with variation in the number of timesteps and observations are documented in the Supplementary.
+
+%It can be seen that more time-steps causes an increase number of iterations, but for some values the number of iterations decreases.
+These values share that $\alpha $ is a magnitude 2 lower than $ \beta$,i.e $\alpha=1.0e-2$ and $\beta =1.0$.
+This indicates that $\alpha $ should be smaller than $\beta$ to achieve optimal convergence.
+However, the number of iterations in Table ~\ref{Tab::1} are smaller for all regularization parameters.
+
+\begin{figure}
+\centering
+\includegraphics[scale=0.21]{../boundary_control.png}  
+\caption{ Displays plots over time for a selection of points at the boundary of $\Omega_1$ with different regularization parameters and number of timesteps $k$.
+The left panel shows the legend for the plot over time, together with the selection of points.
+The middle panel shows the average boundary value $g$ for different regularization parameter with $k=10$.
+The right panel shows the average boundary value $g$ for different regularization parameter with $k=40$.
 }
+\label{boundarycontrol}
+\end{figure}
 
-\affil{$\sp{a}$Department of Mathematics, University of Oslo, Norway\\
-$\sp{b}$Center for Biomedical Computing, Simula Research Laboratory, Lysaker, Norway \\
-$\sp{c}$Division of Radiology and Nuclear Medicine, Department of Radiology, Oslo \\ \hspace{2pt} University Hospital - Rikshospitalet, Oslo, Norway. \\
-$\sp{d}$Institute of Clinical Medicine, Faculty of Medicine, University of Oslo, Oslo, Norway\\
-$\sp{e}$Department of Neurosurgery, Oslo University Hospital – Rikshospitalet, Oslo, Norway
+\subsubsection{The noise susceptibility}
+The MRI data contains noise, hence an investigation to the noise susceptibility is needed.
+This was done varying the noise amplitude, and then the optimization was performed for various regularization parameters $\alpha$ and $\beta$.
+Figure~\ref{12hourswithnoise} and Figure~\ref{24hourswithnoise} show the reconstruction of the manufactured solution at
+different noise levels with $\alpha=0.0001$, $\beta=1.0$ and $k=20$. Clearly, the reconstruction shown in the lower rows is quite robust with respect to the various levels
+of noise shown in the upper rows.      
+In Table~\ref{Tab::Noise0.3} the noise amplitude was set to 0.3 (100$\%$ of maximum initial condition), which gave a visible effect.
+The noise caused the number of iteration to increase, and with more timesteps caused the optimization not to convergence for $\beta < 1.0$.
+Furthermore, the relative boundary error $||g||\sp{rel}$ is significantly larger for $\alpha< 1.0\mathrm{e}{-2} $ and $\beta < 1.0\mathrm{e}{-2}$.
+Results with noise  amplitudes at 0.03 are listed in the Supplementary.
 
+\begin{figure}
+\centering
+\includegraphics[scale=0.4]{../noise-12.png}  
+\caption{The upper row shows the manufactured observation, A) Shows the manufactured observation at time-point 24 with no noise added.
+B) Shows the manufactured observation at time-point 24 with noise amplitude of 0.15.
+C) Shows the manufactures observation at time-point 24 with noise amplitude of 0.3.
+The lower row shows the results with optimized parameter obtained with $\alpha=0.0001$, $\beta=1.0$ and $k=20$.
+D) Shows the resulting state given the observation in A.
+E)  Shows the resulting state given the observation in B .F) Shows the resulting state given the observation in C.
 }
-
-\begin{document}
-\maketitle
-
-\begin{abstract}
-The proposed glymphatic system suggests a new mechanism for waste clearance from the brain, and has sparked new research on Alzheimer's disease where one of the defining features
-is that metabolic waste accumulate within the brain.
-The glympahtic hypothesis is still controversial, but experimental investigations in rodents as well as novel MRI investigations in humans indicates the existence of such a system.
-A proper theoretical foundation
-that explains the fluid transfer mechanisms from first principles is however currently missing.
-In particular, a crucial question in the current debate is how much the system accelerate
-waste clearance when compared to extracellular diffusion alone. Therefore
-we will in this paper evaluate to what extent partial differential constrained optimization methods can be used to identify modeling parameters for glymphatic transport.
-We assume that the transport can be modeled by a diffusion equation, representing extracellular diffusion and possibly dissipation caused by the glymphatic system.
-The observations are obtained from novel MRI techniques that
-aim to quantify long-term (hours/days) transfer mechanism in the brain.
-
-%The recently proposed glymphatic system propose a new mechanism for waste
-%clearance from the brain and has opened for a new paradigm in        
-%research on Alzheimer's disease where one of the defining features
-%is that metabolic waste accumulate within the brain. The glymphatic system is still controversial and while
-%experimental investigations in rodents as well as novel MRI investigations in humans
-%provide evidence for the existence of this system, a proper theoretical
-%foundation is currently missing from the bio-mechanical point of view. In particular,
-%a crucial question in the current debate is how much the system accelerate
-%waste clearance when compared to extra-cellular diffusion alone. In this paper,
-%we will therefore evaluate to what extent partial differential constrained optimization methods
-%can be used to identify modeling parameters for glymphatic transport when we    
-%assume that the underlying equation can be represented by a diffusion equation
-%representing extra-cellular diffusion and possibly dissipation caused by the glymphatic system.
-\end{abstract}
-\section{Introduction}
-In 2012, ~\citet{iliff2012paravascular} provided evidence for a brain-wide paravascular system, denoted the glymphatic system, which is a pathway for transport of fluids and solutes.
-It was proposed to have an important metabolic role by providing a pathway for clearance of waste solutes from the brain.
-Evidence was given that the activity of the glymphatic system increases during  sleep by ~\citet{xie2013sleep}, thus linking sleep to clearance of toxic substances from the brain.
-The glymphatic system seems to become impaired during aging, and failure of the glymphatic system may play a role in neurodegenerative disease and development of Alzheimer's disease.
-Evidence for a brain-wide glymphatic system in humans was first obtained in 2015 by \citet{eide2015mri}, and in 2018 \citet{ringstad2018brain} provided evidence that glymphatic function is deteriorated in individuals with dementia, as compared to controls.
-Several aspects of the glympahtic system are still debated, for example whether glymphatic transport of solutes is by convective mechanisms or by diffusion.
-
-%Recent breakthroughs in medicine have linked neurodegenerative diseases like Alzheimer's to insufficient sleep through a novel fluid mechanism called the glymphatic system 
-%that is responsible for waste clearance. 
-%In 2011,~\citet{iliff2012paravascular} discovered a novel system within our brain's metabolic system, which changed our understanding of the brain. 
-%The system involves a new pathway, called the paravascular pathway as it runs in parallel with the vasculature system in a surrounding compartment.
-%The important novelty in the 2011 findings was that waste from the brain is cleared through the paravascular path, and that a malfunction of this system 
-%is linked to the development of dementia such as Alzheimer's and Parkinson's diseases. In 2013,~\citet{xie2013sleep} found
-%that this system is particularly active during sleep.
-%These mentioned breakthroughs were all performed in mice.
-In 2018, the action of the glymphatic system was for the first time demonstrated in humans.
-Further, it was shown that this action differs between healthy controls and patients with dementia~\cite{ringstad2018brain}.
-%However, the biomechanical mechanisms behind the glymphatic system is not well understood from a fluid mechanics perspective,
-%and so far the modeling attempts have mostly failed~\cite{asgari2016glymphatic, holter2017interstitial, smith2017glymphatic}. 
-%In particular the system seems to facilitate waste transport faster than  
-%the extracellular diffusion, which has been the prevailing paradigm since the pioneering works of \citet{sykova2008diffusion}.
-
-The biomechanical mechanisms are not well understood from a fluid mechanics perspective,
-and so far the modeling attempts have mostly failed~\cite{asgari2016glymphatic, holter2017interstitial, smith2017glymphatic}. 
-In particular the system seems to facilitate waste transport faster than  
-the extracellular diffusion, which has been the prevailing paradigm since the pioneering works of \citet{sykova2008diffusion}
-
-%A novel pathway of the brain's metabolism system called the paravascular pathway, because it runs in parallel with 
-%vasculature system in a surrounding compartment,  
-%was discoved in 2011~\cite{iliff2012paravascular}. 
-%%Later it was found that this system is particularly active during sleep~\cite{xie2013sleep}.  
-%It has been proposed that this pathway plays an important role in the clearance of waste
-%from the brain and hereby a malfunction of this system is linked to  the development of dementia such as Alzheimer's and Parkinson's diseases. That is, 
-%the lymphatic system plays a crucial role in waste clearance in the rest of our body, but there are no lymph vessels inside
-%the brain. As such, the metabolic process of the brain is not well understood and this is surprising since the brain is a very 
-%energy demanding organ (about 10 times as demanding as the average organ). The circulatory system of the paravascular pathway 
-%has therefore been named the glymphatic system~\cite{jessen2015glymphatic} as it has a similar role as the well-known lymphatic system and because the glia cells 
-%are crucial in this system.  
-%The glymphatic system remains controversial and modeling attempts
-%has so far mostly failed to explain the biomechanics of the system~\cite{asgari2016glymphatic, holter2017interstitial, smith2017glymphatic}\kam{Lars: vi trenger flere her}. A proper biomechanical 
-%understanding of the pathway has significant potential because
-%dementia such as Alzheimer´s and Parkinson´s diseases are
-%associated with accumulation of metabolic waste such as
-%amyloid-beta and CSF-tau.
-
-In \cite{ringstad2018brain} brain-wide distribution of MRI-contrast was demonstrated during 24 hours after lumbar contrast injection.
-Brain-wide distribution by diffusion alone was deemed unlikely by the authors.
-The argument was based on analytical considerations where it was calculated that 50\% contrast enrichment would occur after
-55 hours using the error function which is valid for planar diffusion. However, 
-the surface of the brain is folded and is around five times larger than 
-a corresponding surface of a ball with the same volume. Hence, 
-a more rigorous modeling attempt is warranted. A complicating factor
-is however that the contrast in the surrounding cerebral spinal fluid (CSF) is heterogeneous
-and changes significantly during the 24 hours of the investigations. 
-Furthermore, images were obtained only at a few time-points during the investigations in \cite{ringstad2018brain}.
-As such, the sparseness in time prevents a direct computation of the diffusion coefficients.
-
-The work of Sykov{\'a} and Nicholson~\cite{sykova2008diffusion} demonstrated
-that diffusion was a governing transport mechanism in the brain at short time-scales and with an estimated order of magnitude $1.0\mathrm{e}{-4} \mathrm{mm\sp{2}/s}$ for large molecules.
-This is confirmed with diffusion tensor imaging (DTI) where young and healthy subjects have typical diffusion values in white matter around $0.7-0.9\mathrm{e}{-3} \mathrm{mm\sp{2}/s}$ \citet{Helenius194},
-while subjects with dementia typically have higher value and variation \cite{goujon2018can}. Of course diffusion coefficients, 
-measured by DTI at short time-scales may not be representative for the process on a
-longer time-scale, at least if the paravascular pathway plays an important role. The fact that the vascular system occupies around 3\% of the brain volume  \cite{nicholson2001diffusion},
-and the paravascular network is substantially smaller potentially renders the paravascular transport  invisible at the short time-scales of a DTI acquisition while it may still be effective on longer time scales.
-
-Our purpose in this paper is to attempt a more rigorous methodology 
-for assessing the paravascular transport process where
-the complex geometry of the brain as well as time-scales of hours or days are taken into account.
-%That is,
-Thus we aim to investigate whether we can assess an effective diffusion coefficient on long time-scales (hours or days), by fitting a diffusion model to MRI data taken at multiple time-points in which the contrast is spreading through the brain.
-If the fit between observation and model is good and we identify diffusion coefficients that are
-in line with those predicted by DTI then paravascular transport can be ignored on the scale of our study. 
-Our approach is to solve an optimization problem constrained by a partial differential equation (PDE) using the adjoint method where we have sparse observations on selected time-points, around 10 acquisitions during 24 hours, but through
-the complete domain. Hence, the challenges faced from a mathematical point of view 
-are that 1) the images are subject to noise, 2) resolution in space is limited to slightly less than 1 $\mathrm{mm}^3$ and 3)
-the sparse observations through the time domain. 
-Therefore we need to assess the sensitivity of the approach with respect to important factors, such noise levels and time resolution to determine whether this approach is a viable method to obtain parameters involved time-scales.
-
-%As such we need to assess the sensitivity of the approach with respect to important parameters such as the regularization parameters, noise levels and  time resolution to determine whether this approach is a viable method to obtain parameters involved time-scales.
-We remark that the purpose
-of this paper is a systematic study of the mathematical challenges and that assessing  
-whether clearance is governed by a process that is faster than diffusion is not the topic of the current paper, 
-for that we would need to study several subjects.
-
-An outline of the paper is as follows. 
-In Section 2 we present the methodology of the paper. Section 2.1-2.3 contains a detailed description of the medical imaging 
-relevant to this study as we do not expect the reader to have prior knowledge of medical imaging. Section 2.4
-describes the PDE constrained optimization problem and the corresponding solution algorithm, while 2.5 presents
-a test problem using a manufactured solution that is used for method verification. Section 2.6 describes the implementation 
-in FEniCS \cite{LoggMardalEtAl2012a}. In Section 3 we present the results and have a rather extensive discussion of the verification performed
-using a manufactured solution (Section 3.1) before we present the results obtained by real observations in Section 3.2.1    
-and a comparison with DTI data in Section 3.2.2. Finally, in Section 4, the methodology and results are discussed.
-
-\section{Methodology}
-
-Sections 2.1-2.3 briefly describe the details of the imaging relevant for this study. More details on the MRI protocols can be
-found in e.g. \cite{ringstad2018brain}. Sections 2.4-2.5 describe the solution of PDE constrained optimization problems and
-its implementation in FEniCS. The exposition is, however, brief and we refer to e.g. \cite{hinze2008optimization} for more details.
-
-\subsection{MRI Data}
-\begin{figure}
-\includegraphics[width=0.95\textwidth]{PatID-new-100.png} 
-\caption{Shows the percentage change in T1 signal unit ratios from baseline at different observation times. The colorbar was restricted to the range $(0,100)$. }
-\label{fig1} 
+\label{12hourswithnoise}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[width=0.95\textwidth]{Zoom-PatID.png} 
-\caption{Shows the percentage change in T1 signal unit ratios from baseline at different observation times in the slice (marked red in the left panel) used in the subsequent analysis.
-The color bar was restricted to the range $(0,100)$.
+\centering
+\includegraphics[scale=0.4]{../noise-24.png}
+\caption{The upper row shows the manufactured observation, A) Shows the manufactured observation at time-point 24 with no noise added.
+B) Shows the manufactured observation at time-point 24 with noise amplitude of 0.15.
+C) Shows the manufactures observation at time-point 24 with noise amplitude of 0.3.
+The lower row shows the results with optimized parameter obtained with $\alpha=0.0001$, $\beta=1.0$ and $k=20$.
+D) Shows the resulting state given the observation in A.
+E)  Shows the resulting state given the observation in B .F) Shows the resulting state given the observation in C.
 }
-\label{fig2} 
+\label{24hourswithnoise}
 \end{figure}
-Figure~\ref{fig1} shows distribution of MRI-contrast%CSF tracer
-, as a percentage change in T1 signal unit ratios, see also~\cite{ringstad2018brain} for further information on the imaging procedure.   
-Our data (not all shown) consist of a total of 10 MRI observations, including a baseline MRI taken before the contrast was injected.
-The observation points are distributed over 5 observations within 1-2 hours after injection, a single observation in the timeframes 2-4 hours, 6-9 hours, 24 hours and 48 hours.
-Figure~\ref{fig2} shows the region selected for our computations. 
-The software Freesurfer \cite{Dale1999179, FischlLiuDale, spf2007, reuter:robreg10} was used to segment and align each of the observations, which made it possible to estimate voxelwise signal increase.
 
-%The MRI data was part of a larger study, which involves around 100 patients with the same MRI acquisitions.
-However, there are clinical differences in each patient, thus a thorough analysis is needed to obtain a robust and accurate method.
+\subsection{Manufactured Solution}
+In order to assess the robustness and accuracy of our strategy and test the dependency of the computed diffusion coefficients $D$ on the
+regularization parameters $\alpha$ and $\beta$, we perform a test case with a
+known solution. The manufactured observations were obtained by forward computation of \eqref{Eq::PDE} with the Dirichlet boundary condition defined as 
+\begin{equation}
+g(t) = 0.3 +0.167t - 0.007t\sp{2} \qquad \text{ for } 0 \leq t \leq 24.
+\label{EQ::DIRI}
+\end{equation}
+The initial condition was set to 0 everywhere, the timestep was $dt = 0.2$, and the diffusion coefficients were selected to be 
+\begin{equation}
+D_{\Omega_1} = 1000.0, \quad D_{\Omega_2} = 4.0, \quad D_{\Omega_3} = 8.0 
+\end{equation}  
+The magnitude order for $D_{\Omega_1} $ and $D_{\Omega_2}$ were chosen to resemble diffusion coefficient for water in grey and white matter, but the relation between the coefficients were not preserved.
+In \citet{Haga}, the drug concentration moved 1 cm per 20 seconds in the cervical region, thus $D_{\Omega_1}$  was set to 1000.
+The manufactured forward computation produced a total of 120 possible observation times.
+
+\subsection{Implementation}
+The solver for \eqref{Eq::PDE} was implemented using the FEniCS project (v.2017.2), using backwards Euler time discretization and first order continuous Galerkin finite elements in space.
+The resulting linear problems were solved using GMRES.
+The module dolfin-adjoint \cite{farrell2013automated, funke2013framework} was used to automatically derive and solve the adjoint problem, and to solve the PDE constrained optimization problem with the L-BFGS-B algorithm \cite{LBFGSB1, LBFGSB2}.
+The optimization was stopped when the $L^\infty$-norm of the projected gradient of the objective functional dropped below $1.0\mathrm{e}{-1}$.
+
+The observations $u_{obs}$ have fixed time-points.
+However, these time-points may not coincide  with the time discretization in the forward problem $t_j$.
+Therefore, we linearly interpolated the computed solutions onto the observation time points using the formula
+\begin{equation}
+\label{observation:interpolation}
+u(t) \approx \frac{\Delta t}{dt} u(t_{j-1}) + \frac{dt - \Delta t }{dt} u(t_{j}), \quad t \in \lbrace t_{j-1}, t_j \rbrace
+\end{equation}
+with $\Delta t = t_j-t$ and $dt = t_j - t_{j-1}$.
+
+The implementation used the first observation as initial conditions of \eqref{Eq::PDE}.
+Then for each time-step, the next observation was used as the initial value for boundary control $g$.
+In order to increase the convergence speed of the optimization, $D_{\Omega_1}$ was scaled so that $D_{\Omega_1} = 100 D_{\Omega_1}\sp{\star} $.
+The initial values of the diffusion coefficients in the optimization algorithm were $(D_{\Omega_1}\sp{\star}, D_{\Omega_2}, D_{\Omega_3})=$  $(1, 1, 1)$.
+
+The noise susceptibility was tested by pointwise adding a uniform distributed noise to the observations.
+The noise term was constructed using the random library in numpy and adjusted so that the noise range was $\lbrace -n_{amp} , n_{amp} \rbrace $, with $n_{amp}$ denoted as noise amplitude.
 
@@
 \label{figuredti} 
-\end{figure}
-
-\subsection{Mathematical Model}
-In \citet{sykova2008diffusion}, it was shown that the macroscopic diffusion in the brain can be considered a hindered diffusion with an apparent diffusion coefficient (ADC).
-The relation between the diffusion coefficients were defined as
-\begin{equation}
- \lambda =  \sqrt {D/D_{ADC}}
-\label{tortuosity}
-\end{equation}
-with $\lambda$ denoted as the tortuosity.
-In order to estimate the apparent diffusion coefficient involved in the contrast transportation shown in Figure~\ref{fig1} we assume that the process can be modeled by a diffusion equation. 
-Then we constructed an optimization problem with the aim to minimize the difference between the observed and the modeled contrast distribution by optimizing the boundary conditions and the apparent diffusion coefficient.
-Thus enhanced transportation because of effects such as dissipation would result in an apparent diffusion coefficient larger than that predicted by DTI.
-The objective function was defined as
-\begin{equation}
-\min_{D,g} \quad \sum\limits_{i=1}\sp{n} \int\limits_{\Omega} |u(t_i) - u_{obs}(t_i)|\sp{2} \mathrm{d}\Omega + \int\limits_{0}\sp{T} \int\limits_{\partial \Omega_1} \left( \frac{\alpha}{2} | g |\sp{2} + \frac{\beta}{2} \left| \frac{\partial g}{\partial t} \right|\sp{2} \right) \mathrm{d}\Omega \mathrm{d}t
-\label{EQ::objf}
-\end{equation}
-subject to   
-\begin{equation}
-\begin{aligned}
-\frac{\partial u}{\partial t} &= \nabla \cdot  D \nabla u && \text{in} \qquad \Omega \times \left\lbrace 0 , T \right)  \\
-u&=g && \text{on} \qquad \partial\Omega  \times \left\lbrace 0 , T \right) 
-\end{aligned}
-\label{Eq::PDE}
-\end{equation}
-Here, $u$ is the contrast distribution, $D$ is the apparent diffusion 
-coefficient, $g$ is the boundary condition, $\Omega$ is the domain, and $T$ is the final simulation time.
-We assume that the domain $\Omega$ consists of three sub domains, each with a different diffusion coefficient.
-We denote the CSF (subarachnoid and lateral ventricle) domain as $\Omega_1=\Omega_{CSF}$, the grey matter as $\Omega_{GM}$ and the white matter as $\Omega_{WM}$.
-The apparent
-diffusion constant is assumed to be constant within the CSF, grey and 
-white matter but each region may have different values.  
-The Dirichlet boundary condition is only applied on the outer facing boundary of the CSF domain, $\partial \Omega_1$. Homogeneous Neumann conditions are applied on the remaining boundaries.
-The $\alpha$ and $\beta$ parameters are non-negative regularization parameters 
-and $u_{obs}$ are the observations at time-points $t_i$.
-
-The mesh construction was patient-specific and used the MRI of a patient diagnosed with idiopathic normal pressure hydrocephalus (iNPH).
-The software Freesurfer was used to segment and create the polyhedral surfaces of the white and grey matter.
-Then the T2 weighted MRI \cite{ringstad2018brain} was used to segment the CSF compartment surrounding the cerebral and the lateral ventricles.
-CGAL \cite{cgal:rty-m3-18b} was used to combine the polyhedral surfaces and to construct the mesh.
-The computational requirement for the resulting mesh was significant, therefore two submeshes was also constructed, see Figure~\ref{Fig::Mesh}.
-\begin{figure}
-\centering
-\includegraphics[scale=0.2]{mesh.png} 
-\caption{The leftmost image A) shows the mesh created from the baseline MR image with 3 domains, while the rightmost image  B) shows the mesh created from the baseline MR image with 2 domains.
-The blue domain corresponds to CSF domain, $\Omega_{CSF}$, the purple domain corresponds to grey matter,  $\Omega_{GM}$, and the white domain corresponds to white matter, $\Omega_{WM}$.
-}
-\label{Fig::Mesh}
-\end{figure}
-The 3 domain mesh in Figure~\ref{Fig::Mesh} A, consists of 244318 tetrahedral cells and 22057 vertices, while the 2 domain mesh (without the CSF compartment) Figure~\ref{Fig::Mesh} B consists of 335589 tetrahedral cells and 73002 vertices.
-
-\subsection{Manufactured Solution}
-In order to assess the robustness and accuracy of our strategy and test the dependency of the computed diffusion coefficients $D$ on the
-regularization parameters $\alpha$ and $\beta$, we perform a test case with a
-known solution. The manufactured observations were obtained by forward computation of \eqref{Eq::PDE} with the Dirichlet boundary condition defined as
-\begin{equation}
-g(t) = 0.3 +0.167t - 0.007t\sp{2} \qquad \text{ for } 0 \leq t \leq 24.
-\label{EQ::DIRI}
-\end{equation}
-The initial condition was set to 0 everywhere, the timestep was $dt = 0.2$, and the diffusion coefficients were selected to be 
-\begin{equation}
-D_{\Omega_1} = 1000.0, \quad D_{\Omega_2} = 4.0, \quad D_{\Omega_3} = 8.0 
-\end{equation}  
-The magnitude order for $D_{\Omega_1} $ and $D_{\Omega_2}$ were chosen to resemble diffusion coefficient for water in grey and white matter, but the relation between the coefficients were not preserved.
-In \citet{Haga}, the drug concentration moved 1 cm per 20 seconds in the cervical region, thus $D_{\Omega_1}$  was set to 1000.
-The manufactured forward computation produced a total of 120 possible observation times.
-
-\subsection{Implementation}
-The solver for \eqref{Eq::PDE} was implemented using the FEniCS project (v.2017.2), using backwards Euler time discretization and first order continuous Galerkin finite elements in space.
-The resulting linear problems were solved using GMRES.
-The module dolfin-adjoint \cite{farrell2013automated, funke2013framework} was used to automatically derive and solve the adjoint problem, and to solve the PDE constrained optimization problem with the L-BFGS-B algorithm \cite{LBFGSB1, LBFGSB2}.
-The optimization was stopped when the $L^\infty$-norm of the projected gradient of the objective functional dropped below $1.0\mathrm{e}{-1}$.
-
-The observations $u_{obs}$ have fixed time-points.
-However, these time-points may not coincide  with the time discretization in the forward problem $t_j$.
-Therefore, we linearly interpolated the computed solutions onto the observation time points using the formula
-\begin{equation}
-\label{observation:interpolation}
-u(t) \approx \frac{\Delta t}{dt} u(t_{j-1}) + \frac{dt - \Delta t }{dt} u(t_{j}), \quad t \in \lbrace t_{j-1}, t_j \rbrace
-\end{equation}
-with $\Delta t = t_j-t$ and $dt = t_j - t_{j-1}$.
-
-The implementation used the first observation as initial conditions of \eqref{Eq::PDE}.
-Then for each time-step, the next observation was used as the initial value for boundary control $g$.
-In order to increase the convergence speed of the optimization, $D_{\Omega_1}$ was scaled so that $D_{\Omega_1} = 100 D_{\Omega_1}\sp{\star} $.
-The initial values of the diffusion coefficients in the optimization algorithm were $(D_{\Omega_1}\sp{\star}, D_{\Omega_2}, D_{\Omega_3})=$  $(1, 1, 1)$.
-
-The noise susceptibility was tested by pointwise adding a uniform distributed noise to the observations.
-The noise term was constructed using the random library in numpy and adjusted so that the noise range was $\lbrace -n_{amp} , n_{amp} \rbrace $, with $n_{amp}$ denoted as noise amplitude.
-
-\section{Results}
-\subsection{Verification in terms of the manufactured solution}
-Below we will discuss the parameter identification and its sensitivity with respect to the regularization parameters, noise, number of observations and time-resolution of the forward model.
-When presenting the results, we denote the relative error of the diffusion parameters as
-\begin{equation}
- D_{\Omega_i}\sp{rel} = \frac{D_{\Omega_i}\sp{found} -D_{\Omega_i}\sp{true} }{D_{\Omega_i}\sp{true} }, \text{ for } i=1,2,3
-\end{equation}
-For the boundary parameter $g$, the relative error norm is defined as 
-\begin{equation}
-|| g ||\sp{rel} = \frac{ \sum\limits_{t_j} || g_{found}(t_j) -g_{true}(t_j)||_{L^2(\Omega_1)} }{  \sum\limits_{t_j}||g_{true}(t_j)||_{L^2(\Omega_1)} }
-\end{equation}
-The case when the minimization algorithm fails to converge within 1000 iteration will be indicated by a hyphen in Table~\ref{Tab::Noise0.3}.
-
-\subsubsection{The relaxation parameters}
-The convergence as well as the result of the minimization is influenced by the values of the regularization parameters $\alpha$ and $\beta$.
-Therefore the convergence was examined by a systematic study of the reconstruction of the manufactured solution with respect to a wide range of regularization parameters.
-
-Ideally, our approach should have a wide range of parameters in which the reconstruction algorithm yields very similar end-results although the convergence may vary substantially.
-The evaluation of different regularization parameters was done by solving the optimization with different values of $\alpha$ and $\beta$ and comparing the computed $D$ and $g$ values with the manufactured solution.
-The observation times were set to $\lbrace$2.4, 4.8, 7.2, 9.6, 12.0, 14.4, 16.8, 19.2, 21.6, 24.0 $\rbrace$, and the number of time-steps $k$ in the forward problem was set to $10$.
-
-The results are shown in Table~\ref{Tab::1} and the convergence is shown in Figure~\ref{convergence}.
-We can see that the optimization computed similar end-result for most regularization parameters.
-More specifically, for $\alpha \leq 1\mathrm{e}{-2}$ and $\beta \leq 1e-0$ the relative errors for all optimization parameters are below $5\%$.However, in the case of $ \alpha=1.0$ the relative error is over 100\% higher than for other values of $\alpha$.
-Furthermore, for all $\beta=100.0$ there is about 70\% relative error for $D_{\Omega_1}$ and approximate 10\% error for $D_{\Omega_2}$.
-From the results it can be discerned that $\alpha =1.0$ and $\beta=100.0$ represent an upper threshold where the observations are no longer the dominant term in the objective functional.
-
-\begin{figure}
-\centering
-\includegraphics[scale=0.18]{Convergence-plot.png}   
-\caption{Convergence plots of the diffusion coefficients, boundary conditions and functional with respect to different $\alpha$ and $\beta$ values. } 
-\label{convergence}
-\end{figure}
-
-In Figure~\ref{boundarycontrol} we can see that more time-steps causes oscillations if $\alpha\gg\beta$ and the number of time-steps are much larger than the number of observations.
-For instance, as seen by the the pink line for $\alpha=1.0$ and $\beta=0.0001$ the peaks corresponds to a observation.
-These oscillations are caused by the strong weighting of $\alpha$, which leads to minimizing of $g$ between observation times.
-Tests with variation in the number of timesteps and observations are documented in the Supplementary.
-
-%It can be seen that more time-steps causes an increase number of iterations, but for some values the number of iterations decreases.
-These values share that $\alpha $ is a magnitude 2 lower than $ \beta$,i.e $\alpha=1.0e-2$ and $\beta =1.0$.
-This indicates that $\alpha $ should be smaller than $\beta$ to achieve optimal convergence.
-However, the number of iterations in Table ~\ref{Tab::1} are smaller for all regularization parameters.
-
-\begin{figure}
-\centering
-\includegraphics[scale=0.21]{boundary_control.png}  
-\caption{ Displays plots over time for a selection of points at the boundary of $\Omega_1$ with different regularization parameters and number of timesteps $k$.
-The left panel shows the legend for the plot over time, together with the selection of points.
-The middle panel shows the average boundary value $g$ for different regularization parameter with $k=10$.
-The right panel shows the average boundary value $g$ for different regularization parameter with $k=40$.
-}
-\label{boundarycontrol}
-\end{figure}
-
-\subsubsection{The noise susceptibility}
-The MRI data contains noise, hence an investigation to the noise susceptibility is needed.
-This was done varying the noise amplitude, and then the optimization was performed for various regularization parameters $\alpha$ and $\beta$.
-Figure~\ref{12hourswithnoise} and Figure~\ref{24hourswithnoise} show the reconstruction of the manufactured solution at
-different noise levels with $\alpha=0.0001$, $\beta=1.0$ and $k=20$. Clearly, the reconstruction shown in the lower rows is quite robust with respect to the various levels
-of noise shown in the upper rows.      
-In Table~\ref{Tab::Noise0.3} the noise amplitude was set to 0.3 (100$\%$ of maximum initial condition), which gave a visible effect.
-The noise caused the number of iteration to increase, and with more timesteps caused the optimization not to convergence for $\beta < 1.0$.
-Furthermore, the relative boundary error $||g||\sp{rel}$ is significantly larger for $\alpha< 1.0\mathrm{e}{-2} $ and $\beta < 1.0\mathrm{e}{-2}$.
-Results with noise  amplitudes at 0.03 are listed in the Supplementary.
-
-\begin{figure}
-\centering
-\includegraphics[scale=0.4]{noise-12.png}  
-\caption{The upper row shows the manufactured observation, A) Shows the manufactured observation at time-point 24 with no noise added.
-B) Shows the manufactured observation at time-point 24 with noise amplitude of 0.15.
-C) Shows the manufactures observation at time-point 24 with noise amplitude of 0.3.
-The lower row shows the results with optimized parameter obtained with $\alpha=0.0001$, $\beta=1.0$ and $k=20$.
-D) Shows the resulting state given the observation in A.
-E)  Shows the resulting state given the observation in B .F) Shows the resulting state given the observation in C.
-}
-\label{12hourswithnoise}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[scale=0.4]{noise-24.png}
-\caption{The upper row shows the manufactured observation, A) Shows the manufactured observation at time-point 24 with no noise added.
-B) Shows the manufactured observation at time-point 24 with noise amplitude of 0.15.
-C) Shows the manufactures observation at time-point 24 with noise amplitude of 0.3.
-The lower row shows the results with optimized parameter obtained with $\alpha=0.0001$, $\beta=1.0$ and $k=20$.
-D) Shows the resulting state given the observation in A.
-E)  Shows the resulting state given the observation in B .F) Shows the resulting state given the observation in C.
-}
-\label{24hourswithnoise}
-\end{figure}
-
-\subsection{A Real case}
-
-\subsubsection{Results obtained when using real observations}
-The MRI data consisted of the observations at times $t_i \in \lbrace$0.00, 0.16, 0.39, 0.55, 0.77, 2.09, 6.05, 24, 48, 698$\rbrace \mathrm{(hours)}$ with the time $t_i=0.00$ as the observation 1-2 hours after the contrast was injected.
-There was no significant visible change in the contrast between the observations at $\lbrace$0.00, 0.16, 0.39, 0.55, 0.77$\rbrace$.
-This prompted the use of the following observation times  $\lbrace0.00, 2.09, 6.05, 24, 48\rbrace$.
-
-The estimation of contrast concentration proved difficult in the CSF compartment.
-Therefore the 2 domain mesh, shown in Figure~\ref{Fig::Mesh} was used in the computation.
-The boundary control was set to the external boundary of both domains, and the subscript in $D_{\Omega_{GM}}$ and $D_{\Omega_{WM}}$ denotes grey and white matter diffusion coefficients.
-Furthermore, bounds were added to the L-BFGS-B algorithm to ensure non-negative boundary controls and the convergence criteria was adjusted so that the optimization was stopped when the $L^\infty$-norm of the projected gradient of the objective functional dropped below $6.0\mathrm{e}{-1}$.
-The number of timesteps were selected to be $k=24$ and $k=48$, which gives $dt = 2 \mathrm{h}$ and $dt = 1 \mathrm{h}$.
-
-The results are shown in Table~\ref{Tab::Real-data}, and the observations after 12 and 48 hours were compared with the corresponding states in Figure~\ref{Fig::realdata}.
-From Table~\ref{Tab::Real-data}, it can be observed that $D_{\Omega_{WM}}$ has 24\% higher value on average for $\alpha =1.0\mathrm{e}{-2}$.
-It can also be observed that the $D_{\Omega_{GM}}$ have a consistent increases with a decreasing $\beta$.
-
-\subsubsection{Comparison with results obtained from DTI analysis}
-The median diffusion coefficient in the DTI was estimated to be $8.7\mathrm{e}{-4} \mathrm{mm\sp{2}/s}$ in white matter and $1.0\mathrm{e}{-3} \mathrm{mm\sp{2}/s}$ in grey matter.
-This corresponds to a tortuosity of $1.85$ and $1.73$, given that the self-diffusivity of water has been estimated to be around $3.0\mathrm{e}{-3}\mathrm{mm\sp{2}/s}$ at $37\sp{o}C$.
-The reference value $3.8\mathrm{e}{-4} \mathrm{mm\sp{2}/s}$ for Gd-DPTA then gives an estimate for the apparent diffusion coefficient in the grey and white matter to  be $ 1.26\mathrm{e}{-4}\mathrm{mm\sp{2}/s}$ and $1.10\mathrm{e}{-4} \mathrm{mm\sp{2}/s}$ respectively.
-This estimation assumes that the tortuosity is independent for molecules with mass lower than 1kDa.
-
-The oscillation in Figure~\ref{boundarycontrol} showed a large discrepancy in the states between observations.
-Therefore the states with $k=48$ were examined after 36 hours, see Figure~\ref{statecomparison}.
-It can be observed that the upper right row displays a discrepancy, which likely due to inadequate regularization parameters.
-Furthermore, we can see that for $\alpha=1.0\mathrm{e}{-2}$ there is a clear discrepancy in the diffusion coefficients compared to other values $\alpha$.
-Excluding the values with $\alpha=1.0\mathrm{e}{-2}$ gives an average of $ 0.65 \mathrm{mm\sp{2}/h}$ in grey matter and $ 0.8 \mathrm{mm\sp{2}/h}$ in and white matter.
-Scaled to $\mathrm{mm\sp{2}/s}$ gives the corresponding values $1.8\mathrm{e}{-4}\mathrm{mm\sp{2}/s}$ and $2.22\mathrm{e}{-4} \mathrm{mm\sp{2}/s}$.
-This gives a difference of 42\% in grey matter and $ 100 \%$ in white matter compared to the estimated values using DTI.
-
-In Figure~\ref{Fig::realdata}, it can be seen that there were regions with negligible amount of contrast and vice versa.
-The regions with above average amount of contrast corresponds with high diffusivity regions in Figure~\ref{figuredti}.
-This suggests that the computed diffusion coefficients corresponds to these values.
-The ADC value in the high diffusivity regions are approximately  $1.4\mathrm{e}{-3} \mathrm{mm\sp{2}/s}$, which corresponds to estimated diffusion coefficient of value $1.5\mathrm{e}{-3} \mathrm{mm\sp{2}/s}$.
-This gives a difference of $ 46 \%$ compared to the computed values.
-
-\section{Discussion}
-The methodology presented here for identification of diffusion coefficients and boundary conditions with application to the glymphatic system appears to work quite 
-well for regularization parameters varying by orders of magnitude.
-The regularization parameters  $\alpha \in \lbrace 1.0\mathrm{e-6}, 1.0\mathrm{e}{-2} \rbrace$, $\beta \in \lbrace 1.0\mathrm{e}{-2} , 1.0 \rbrace$ with the requirement $\alpha / \beta < 1.0\mathrm{e}{-2}$ gave a relative error of
-4.1\% in grey matter and 3.6 \% in white matter when tested against a manufactured solution. It is particularly interesting to see that the procedure efficiently removes noise as demonstrated
-in the Figures \ref{12hourswithnoise} and \ref{24hourswithnoise} with noise amplitude of 23\% of maximum value.
-However, the addition of noise required that $\beta = 1.0 $ to obtain consistent convergence.
-Crucial in our application is the interplay between the regularization term that regulates the smoothness of the boundary conditions as well as the integrated magnitude of the boundary conditions over time, i.e.
-$\alpha$ and $\beta$.
-Further, we observed that the importance of interplay of these parameters increases with the number of time steps.
-This is, however, not surprising because our observations are sparse
-in time and hence an oscillating boundary condition in time will minimize the integrated boundary condition at the cost of reducing the smoothness in time.
-The selected range of regularization parameters showed a decrease in error with more timesteps, rather than oscillation.
-
-While a more comprehensive study involving more patients would be required in order to assess clearance in health and disease, a few remarks here are in order. 
-First of all, the process investigated here is the clearance of Gadovist from CSF into the interstitium which may differ from the clearance of metabolic waste 
-from the interstitium via the CSF. That said, 
-we find that the diffusion coefficients is 42\% larger in grey matter and 100\% larger in white matter than what was found by the DTI modality. As such, we predict that the paravascular system 
-plays a significant role.  
-However, we have not yet been able to assess the self-diffusion of water as well as the diffusivity of Gadovist used in this study with phantom models. As such 
-the values used with \eqref{tortuosity} must be taken with caution. Furthermore,    
-the computational model assumes isotropic diffusivity, but the anisotropy in the white matter is well documented, as shown by the FA in Figure~\ref{figuredti}.
-It can be seen in Figure~\ref{Fig::realdata} that the region with high FA have negligible amounts of contrast present.
-Therefore it would seem that the anisotropy do not have direct impact on the computations, since the computation can not evaluate a static environment.
-Thus observations of contrast in regions with anisotropy can be considered a requirement before adding anisotropy to the model.
-
-The computational model uses 2 global controls for the diffusion coefficients, while it can be seen in  Figure~\ref{figuredti} that diffusion coefficients can be considered a spatial function.
-However, the implementation of control parameters for each degree of freedom would significantly increase the computational cost and increase the demand for regularization.
-Since the diffusivity appears to be regional, using region specific control parameters seems to be a better option.
-It can also be taken into consideration to model the diffusion coefficients as a function in time, given the report of increased clearance in rodents during sleep \cite{xie2013sleep}.
-This would indicate a time-dependent diffusivity, given that the clearance in the brain is driven by diffusion.
-%The time-dependency would correspond to a change in tortuosity, since properties of the tracer molecule do not change.
-The hypothesis of the glymphatic system \cite{iliff2012paravascular} states that the waste is cleared through the veins in the parenchyma.
-This gives the contrast additional pathways that is not considered in the computational model.
-These additional pathways can be modeled as a drainage, which can be included as a control source term.
-
-In Table~\ref{Tab::Real-data}, it was shown that the grey matter diffusion coefficient had a negative correlation with the relaxation parameter $\beta$.
-This was caused by the boundary control $g$, which exists along the entire boundary of the grey matter.
-Considering that the grey matter volume has an average thickness less than 3 mm makes it susceptible to changes in $g$.
-This can be observed in the reconstruction in Figure~\ref{12hourswithnoise} and Figure~\ref{24hourswithnoise}, where the noise is present at the boundary.
-
-Previous studies~\cite{holter2017interstitial, smith2017glymphatic} suggest that diffusion dominates in the interstitium.
-Furthermore, ~\cite{asgari2016glymphatic, brynjfm, Diem} have found that dissipation in the paravascular spaces adds less than a factor two
-to diffusion for solute transportation. If we consider that the vascular system occupy 3\% of the brain volume
-%of the brain 
-and that the paravascular space presumably occupy less space.
-Then the 42\% increase in grey matter and 100\% in white matter that we find here seem significant and the results point towards of the glymphatic clearance.
-%In summary, using this model, we estimated diffusion coefficients that were 42-100\% larger than estimated by DTI acquisitions.
-Our results indicate that dissipation of solutes along the paravascular rout has a factor of 30, as compared to diffusion alone.
-However, the present study did not examine whether transport is by convective mechanisms.
-%
-
-%\section{Conclusion}
-
-%It can be concluded from the results that increasing the number of iterations gives rise to oscillations for poor regularizations parameters.
-
-%\begin{figure}
-%\centering
-%\includegraphics[scale=0.4]{27-12-hours-scale-0-1-3.png}  
-%\caption{The upper row shows the manufactured observation, A ) Shows the manufactured observation at time-point 24 with no noise added.
-B) Shows the manufactured observation at time-point 24 with an noise amplitude of 0.15.
-C)Shows the manufactures observation at time-point 24 with noise amplitude of 0.3.
-The lower row shows the results with optimized parameter obtained with $alpha=0.0001$, $\beta=1.0$ and $k=27$.
-D) Shows the resulting state given the observation in A.
-E)  Shows the resulting state given the observation in B .F) Shows the resulting state given the observation in C.
-}
-%\end{figure}
-%
-%
-%\begin{figure}
-%\centering
-%\includegraphics[scale=0.4]{27-24-hours-scale-0-1.png}
-%\caption{The upper row shows the manufactured observation, A ) Shows the manufactured observation at time-point 24 with no noise added.
-B) Shows the manufactured observation at time-point 24 with a noise amplitude of 0.15 {\color{red} explain noise ampliutde}.
-C)Shows the manufactures observation at time-point 24 with noise amplitude of 0.3.
-The lower row shows the results with optimized parameter obtained with $alpha=0.0001$, $\beta=1.0$ and $k=27$.
-D) Shows the resulting state given the observation in A.
-E)  Shows the resulting state given the observation in B .F) Shows the resulting state given the observation in C.
-}
-%\end{figure}
-% 
-% 
-% 
-%
-%
-
-\subsection{Acknowledgements}
-The computational experiments were performed on the Abel Cluster, owned by the University of Oslo and Uninett\textbackslash Sigma2, and operated by the Department for Research Computing at USIT,the University of Oslo IT-department.
-\url{http://www.hpc.uio.no/}
-
-%\bibliographystyle{plainnat}
-\bibliographystyle{abbrvnat}
-\bibliography{references}
-
-\clearpage
-
-\begin{figure}
-\centering
-\includegraphics[width=0.95\textwidth]{different.png} 
-\caption{Row A) shows the observation at times 2 hours, 6 hours, 24 hours and 48 hours after the first observation with contrast.
-Row B) shows the corresponding states with the relaxation parameters $\alpha=0.01$ and $\beta=0.01$ and $k=48$.
-Row C) shows the corresponding states with the relaxation parameters $\alpha=1.0\mathrm{e-4}$ and $\beta=1.0$ and $k=48$
- Row D) shows the corresponding states with the relaxation parameters $\alpha=1.0\mathrm{e-6}$ and $\beta=0.1$ and $k=48$. The color-bar was restricted to the range $ \lbrace 0 ,0.5 \rbrace$. }
-\label{Fig::realdata}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=0.95\textwidth]{Statecomparison36h-pinta.png} 
-\caption{ Displays the states for different regularization parameters after 36 hours for $k=48$.}
-\label{statecomparison}
 \end{figure}
@@
 \end{table}
-
-\clearpage
-\section{Supplementary}
 
@@
 \end{table}
-
-\end{document}

### 2019-07-04 tex/rev1/paper.tex

@@
 \usepackage{ragged2e}
+
 \title{
@@
 ~\cite{sykova2008diffusion} for an overview, and is fundamental to for  diffusion tensor imaging (DTI). 
-It has been shown that diffusion coefficients in young and healthy subjects in white matter is around $0.7-0.9\mathrm{e}{-3} \mathrm{mm\sp{2}/s}$ \citet{Helenius194},
+It has been shown that diffusion coefficients in young and healthy subjects in white matter is around $0.7-0.9\times 10^{-3} \mathrm{mm\sp{2}/s}$ \citet{Helenius194},
 while subjects with dementia typically have higher value and variation \cite{goujon2018can}. 
@@
 \subsubsection{Results obtained when using real observations}
-The MRI data consisted of the observations at times $t_i \in \lbrace$0.00, 0.16, 0.39, 0.55, 0.77, 2.09, 6.05, 24, 48, 698$\rbrace \mathrm{(hours)}$ with the time $t_i=0.00$ as the observation 1-2 hours after the contrast was injected.
-There was no significant visible change in the contrast between the observations at $\lbrace$0.00, 0.16, 0.39, 0.55, 0.77$\rbrace$.
-This prompted the use of the following observation times  $\lbrace0.00, 2.09, 6.05, 24, 48\rbrace$.
+The MRI data consisted of the observations at times $t_i$ distributed in the 48 hours time frame with the time $t_i=0.00$ as the first observation 1-2 hours after the contrast was injected.
+There was no significant visible change in the contrast between the observations the first 2 hours, which prompted the use of the following observation times listed in Table ??.
 
@@
 The boundary control was set to the external boundary of both domains, and the subscript in $D_{\Omega_{GM}}$ and $D_{\Omega_{WM}}$ denotes grey and white matter diffusion coefficients.
-Furthermore, bounds were added to the L-BFGS-B algorithm to ensure non-negative boundary controls and the convergence criteria was adjusted so that the optimization was stopped when the $L^\infty$-norm of the projected gradient of the objective functional dropped below $6.0\mathrm{e}{-1}$.
-The number of timesteps were selected to be $k=24$ and $k=48$, which gives $dt = 2 \mathrm{h}$ and $dt = 1 \mathrm{h}$.
-
+Furthermore, bounds were added to the L-BFGS-B algorithm to ensure non-negative boundary controls and the convergence criteria was adjusted so that the optimization was stopped when the $L^\infty$-norm of the projected gradient of the objective functional dropped below $6.0\times 10^{-1}$.
+The other specific  computational parameters are listed in Table ??.
 The results are shown in Table~\ref{Tab::Real-data}, and the observations after 12 and 48 hours were compared with the corresponding states in Figure~\ref{Fig::realdata}.
-From Table~\ref{Tab::Real-data}, it can be observed that $D_{\Omega_{WM}}$ has 24\% higher value on average for $\alpha =1.0\mathrm{e}{-2}$.
+From Table~\ref{Tab::Real-data}, it can be observed that $D_{\Omega_{WM}}$ has 24\% higher value on average for $\alpha =1.0\times 10^{-2}$.
 It can also be observed that the $D_{\Omega_{GM}}$ have a consistent increases with a decreasing $\beta$.
@@
 \subsubsection{Comparison with results obtained from DTI analysis}
-The median diffusion coefficient in the DTI was estimated to be $8.7\mathrm{e}{-4} \mathrm{mm\sp{2}/s}$ in white matter and $1.0\mathrm{e}{-3} \mathrm{mm\sp{2}/s}$ in grey matter.
-This corresponds to a tortuosity of $1.85$ and $1.73$, given that the self-diffusivity of water has been estimated to be around $3.0\mathrm{e}{-3}\mathrm{mm\sp{2}/s}$ at $37\sp{o}C$.
-The reference value $3.8\mathrm{e}{-4} \mathrm{mm\sp{2}/s}$ for Gd-DPTA then gives an estimate for the apparent diffusion coefficient in the grey and white matter to  be $ 1.26\mathrm{e}{-4}\mathrm{mm\sp{2}/s}$ and $1.10\mathrm{e}{-4} \mathrm{mm\sp{2}/s}$ respectively.
+The median diffusion coefficient in the DTI was estimated to be 
+$8.7\times 10\sp{-4} \mathrm{mm\sp{2}/s}$ 
+in white matter and 
+$1.0\times 10\sp{-3} \mathrm{mm\sp{2}/s}$ 
+in grey matter.
+This corresponds to a tortuosity of $1.85$ and $1.73$, given that the self-diffusivity of water has been estimated to be around $3.0\times 10\sp{-3}\mathrm{mm\sp{2}/s}$ at $37\sp{o}C$.
+The reference value $3.8\times 10\sp{-4} \mathrm{mm\sp{2}/s}$ for Gd-DPTA then gives an estimate for the apparent diffusion coefficient in the grey and white matter to  be $ 1.26\times 10\sp{-4}\mathrm{mm\sp{2}/s}$ and $1.10\times 10\sp{-4} \mathrm{mm\sp{2}/s}$ respectively.
 This estimation assumes that the tortuosity is independent for molecules with mass lower than 1kDa.
 
-The oscillation in Figure~\ref{boundarycontrol} showed a large discrepancy in the states between observations.
-Therefore the states with $k=48$ were examined after 36 hours, see Figure~\ref{statecomparison}.
+%The oscillation in Figure~\ref{boundarycontrol} showed a large discrepancy in the states between observations.
+The sparsity of the observations compared to the number of time steps can cause the boundary function $g$ to fluctuate between observations, see Appendix.
+Therefore, the states with $k=48$ were examined after 36 hours, see Figure~\ref{statecomparison}.
 It can be observed that the upper right row displays a discrepancy, which likely due to inadequate regularization parameters.
-Furthermore, we can see that for $\alpha=1.0\mathrm{e}{-2}$ there is a clear discrepancy in the diffusion coefficients compared to other values $\alpha$.
-Excluding the values with $\alpha=1.0\mathrm{e}{-2}$ gives an average of $ 0.65 \mathrm{mm\sp{2}/h}$ in grey matter and $ 0.8 \mathrm{mm\sp{2}/h}$ in and white matter.
-Scaled to $\mathrm{mm\sp{2}/s}$ gives the corresponding values $1.8\mathrm{e}{-4}\mathrm{mm\sp{2}/s}$ and $2.22\mathrm{e}{-4} \mathrm{mm\sp{2}/s}$.
-This gives a difference of 42\% in grey matter and $ 100 \%$ in white matter compared to the estimated values using DTI.
+Furthermore, we can see that for $\alpha=1.0\times 10\sp{-2}$ there is a clear discrepancy in the diffusion coefficients compared to other values of $\alpha$.
+Excluding the values with $\alpha=1.0\times 10\sp{-2}$ gives an average of $ 0.65 \mathrm{mm\sp{2}/h}$ in grey matter and $ 0.8 \mathrm{mm\sp{2}/h}$ in and white matter.
+Scaled to $\mathrm{mm\sp{2}/s}$ gives the corresponding values $1.8\times 10\sp{-4}\mathrm{mm\sp{2}/s}$ and $2.22\times 10\sp{-4} \mathrm{mm\sp{2}/s}$.
+The values are summarized in Table ~\ref{Tablesummerized}, and we obtain a difference of $42\%$ in grey matter and $ 100 \%$ in white matter compared to the estimated values using DTI.
 
@@
 This suggests that the computed diffusion coefficients corresponds to these values.
-The ADC value in the high diffusivity regions are approximately  $1.4\mathrm{e}{-3} \mathrm{mm\sp{2}/s}$, which corresponds to estimated diffusion coefficient of value $1.5\mathrm{e}{-3} \mathrm{mm\sp{2}/s}$.
+The ADC value in the high diffusivity regions are approximately  $1.4\times 10\sp{-3} \mathrm{mm\sp{2}/s}$, which corresponds to estimated diffusion coefficient of value $1.5\time 10\sp{-3} \mathrm{mm\sp{2}/s}$.
 This gives a difference of $ 46 \%$ compared to the computed values.
+
+\begin{table}\centering
+\begin{tabular}{|ccc|}
+\hline
+Description & Model variable  & Value used in the simulation\\
+\hline
+& & \\
+Number of timesteps &  k	 & 24, 48	\\
+& & \\
+\hline
+& & \\
+Observational time points  & $\tau$ &  $\lbrace 0.00,2.0, 6 , 24, 48 \rbrace$	 \\
+& & \\
+\hline
+& & \\
+Timestep & $dt$	 	   &	  1, 2 $\mathrm{hours}$	\\ 
+& & \\
+\hline
+& & \\
+Spacial Regularization & $\alpha$	   &	  $\lbrace 1.0\times10\sp{-6}, 1.0\rbrace$\\ 
+& & \\
+\hline
+& & \\
+Time Regularization   & $\beta$	   &	 $\lbrace 1.0\times10\sp{-6}, 100.0\rbrace$	\\ 
+& & \\
+\hline
+\end{tabular}
+\caption{Forslag}
+\label{model-params-overview}
+\end{table}
+
+\begin{table}\centering
+\begin{tabular}{|ccc|}
+\hline
+   & Estimated & Computed average\\
+\hline
+Grey matter  & $ 1.26\times 10\sp{-4}$   &  $1.8\times 10\sp{-4}$  \\
+White matter & $ 1.10\times 10\sp{-4}$   &  $2.22\times 10\sp{-4}$  \\
+\hline
+\end{tabular}
+\caption{Forslag}
+\label{Tablesummerized}
+\end{table}
 
@@
 well for regularization parameters varying by orders of magnitude. 
-The regularization parameters  $\alpha \in \lbrace 1.0\mathrm{e-6}, 1.0\mathrm{e}{-2} \rbrace$, $\beta \in \lbrace 1.0\mathrm{e}{-2} , 1.0 \rbrace$ with the requirement $\alpha / \beta < 1.0\mathrm{e}{-2}$ gave a relative error of
-4.1\% in grey matter and 3.6 \% in white matter when tested against a manufactured solution. It is particularly interesting to see that the procedure efficiently removes noise as demonstrated
-in the Figures \ref{12hourswithnoise} and \ref{24hourswithnoise} with noise amplitude of 23\% of maximum value.
+%\fixme{The regularization parameters  $\alpha \in \lbrace 1.0\mathrm{e-6}, 1.0\time10\sp{-2} \rbrace$, $\beta \in \lbrace 1.0\times\sp{-2} , 1.0 \rbrace$ with the requirement $\alpha / \beta < 1.0\times 10\sp{-2}$ gave a relative error of
+%4.1\% in grey matter and 3.6 \% in white matter when tested against a manufactured solution. It is particularly interesting to see that the procedure efficiently removes noise as demonstrated
+%in the Figures \ref{12hourswithnoise} and \ref{24hourswithnoise} with noise amplitude of 23\% of maximum value.
 However, the addition of noise required that $\beta = 1.0 $ to obtain consistent convergence.
-Crucial in our application is the interplay between the regularization term that regulates the smoothness of the boundary conditions as well as the integrated magnitude of the boundary conditions over time, i.e.
+%Crucial in our application is the interplay between the regularization term that regulates the smoothness of the boundary conditions as well as the integrated magnitude of the boundary conditions over time, i.e.
 $\alpha$ and $\beta$.
@@
 This is, however, not surprising because our observations are sparse
-in time and hence an oscillating boundary condition in time will minimize the integrated boundary condition at the cost of reducing the smoothness in time.
+%in time and hence an oscillating boundary condition in time will minimize the integrated boundary condition at the cost of reducing the smoothness in time.
 The selected range of regularization parameters showed a decrease in error with more timesteps, rather than oscillation.
+}
 
@@
 First of all, the process investigated here is the clearance of Gadovist from CSF into the interstitium which may differ from the clearance of metabolic waste 
-from the interstitium via the CSF. \fixme{That said, 
+from the interstitium via the CSF. That said, 
 we find that the diffusion coefficients is 42\% larger in grey matter and 100\% larger in white matter than what was found by the DTI modality.
-As such, we predict that the paravascular system  plays a significant role.
-}
+%As such, we predict that the paravascular system  plays a significant role.
 However, we have not yet been able to assess the self-diffusion of water as well as the diffusivity of Gadovist used in this study with phantom models. As such 
@@
 Then the 42\% increase in grey matter and 100\% in white matter that we find here seem significant and the results point towards of the glymphatic clearance.
+
+\section{Insert correctly}
+(The sampling of) The observations on the boundary between CSF and the brain parenchyma suffered from the poor resolution of the T1-map, which lead to high frequency noise on the boundary.
+Therefore we investigates the effect of a gradient regularization parameter, Gaussian smoothing and the projecting the average concentration onto the boundary has ways to reduce the noise.
+
+The implementation of the gradient regularization required that the boundary was decomposed to avoid the boundary values being continuous in different subdomains.
+We decomposed the boundary as seen in Figure ~\ref{markedboundaryvalues}, with the red and blue boundary next to the CSF.
+We defined the red boundary $\partial \Omega_r$ and the blue boundary $\partial \Omega_b$ as Dirichlet boundaries, while the green and yellow were Neumann boundaries.
+The regularization parameter $\gamma$ was added to the functional
+\begin{equation}
+\min_{D,g} \quad \sum\limits_{i=1}\sp{n} \int\limits_{\Omega} |u(t_i) - u_{obs}(t_i)|\sp{2} \mathrm{d}\Omega + \int\limits_{0}\sp{T} \int\limits_{\partial \Omega_{rb}} \left( \frac{\alpha}{2} | g |\sp{2} + \frac{\beta}{2} \left| \frac{\partial g}{\partial t} \right|\sp{2}  \frac{\gamma}{2}| \nabla g  \right) \mathrm{d}\Omega \mathrm{d}t
+\end{equation}
+The boundaries $\Omega_r$ and $\Omega_b$ have very different shapes, and using the same regularization parameter can have different effects on the two boundaries.
+Based on the  observations we saw that that the concentration in the lateral ventricles were more uniform than that in the SAS.
+Therefore, we defined $\gamma$ as
+\begin{equation}
+\gamma = \begin{cases}
+0.01\tilde{\gamma}  \in &\partial \Omega_{b} \\ 
+\tilde{\gamma} \qquad \in  &\partial \Omega_{r}
+\end{cases}  
+\end{equation} 
+with $\tilde{\gamma}$ as the referenced(mentioned in the text) regularization parameter.
+
+The results for the ventricular boundary in Figure ~\ref{VENT} and the SAS boundary in Figure ~\ref{SAS}. The corresponding estimated diffusion coefficient are shown in Figure ??. 
+We see that the gradient regularization has a great effect reducing the noise on the boundaries, but it also changed the computed diffusion coefficients.
+
+The Gaussian smoothing was done with the python module scipy, and the standard deviation examined in the range of 0.3-1.5.
+We observed that the Gaussian smoothing with a standard deviation of 1.5 increased the computed diffusion coefficient by approximately 200\% compared to raw data.
+
+%\begin{table}\centering
+%\begin{tabular}{|ccc|}
+%\hline
+%   & Estimated & Computed (lower,upper)\\
+%\hline
+%Grey matter  & $ 1.26\times 10\sp{-4}$   &     \\
+%White matter & $ 1.10\times 10\sp{-4}$   &     \\
+%\hline
+%\end{tabular}
+%\caption{Forslag}
+%\label{model-params-overview}
+%\end{table}
+
 %In summary, using this model, we estimated diffusion coefficients that were 42-100\% larger than estimated by DTI acquisitions.
@@
 
+ \begin{figure}
+\centering
+\includegraphics[scale=0.3]{../facetfucntion.png} 
+\caption{The images shows the marked boundary values on the mesh. }
+\label{markedboundaryvalues}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[scale=0.35]{../Vent-2.png} 
+\caption{ The images shows the ventricular wall at the same time points.
+The upper row shows the observations with following preprocessing left to right: Raw observations, projection of CSF value onto the boundary, Gaussian smoothing.
+The middle row shows the corresponding states with the regularization parameters $\alpha , \beta \gamma = (10\sp{-6},1.0 ,1.0$).
+The bottom row shows the corresponding states with the regularization parameters $\alpha , \beta \gamma = (10\sp{-6},100.0 ,100.$).
+}
+\label{VENT}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[scale=0.35]{../SAS-2.png} 
+\caption{ The images shows the SAS boundary at the same time points.
+The upper row shows the observations with following preprocessing left to right: Raw observations, projection of CSF value onto the boundary, Gaussian smoothing.
+The middle row shows the corresponding states with the regularization parameters $\alpha , \beta \gamma = (10\sp{-6},1.0 ,1.0$).
+The bottom row shows the corresponding states with the regularization parameters $\alpha , \beta \gamma = (10\sp{-6},100.0 ,100.$).
+}
+\label{SAS}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[scale=0.3]{../diffcoeff.png} 
+\caption{The images shows the computed diffusion coefficients in gray and white matter given different preprocessing steps.  }
+\label{diffcoeff}
+\end{figure}
+
 %\input{supplementary}

### 2019-07-04 tex/rev1/paper.tex
update

@@
 \title{
-	Is CSF tracer transporation during 24 hours after infusion explained by diffusion?
+Can diffusion alone explain brain-wide distribution of CSF tracers within 24 hours?
 }
@@
 The proposed glymphatic system suggests a new mechanism for waste clearance from the brain, and has sparked new research on Alzheimer's disease where one of the defining features
-is that metabolic waste accumulate within the brain.
-The glympahtic hypothesis is still controversial, but experimental investigations in rodents as well as novel MRI investigations in humans indicates the existence of such a system.
-A proper theoretical foundation
-that explains the fluid transfer mechanisms from first principles is however currently missing.
-In particular, a crucial question in the current debate is how much the system accelerate
-waste clearance when compared to extracellular diffusion alone. Therefore
-we will in this paper evaluate to what extent partial differential constrained optimization methods can be used to identify modeling parameters for glymphatic transport.
-We assume that the transport can be modeled by a diffusion equation, representing extracellular diffusion and possibly dissipation caused by the glymphatic system.
-The observations are obtained from novel MRI techniques that
-aim to quantify long-term (hours/days) transfer mechanism in the brain. 
-\kam{have not looked at the abstract yet}
+is that metabolic waste accumulate within the brain. The glympahtic hypothesis is still controversial
+and several biomechanical modeling attempts attempts on microlevel have dismissed the system or its assumptions. 	
+On the macroscopic level, however, there are several findings that supports that transportation solute transportation cannot be explained
+by diffusion alone, which is the current prevailing theoretical foundation of brain waste management. In particular, 
+previous calculation by ourselves in simplified geometries suggested that diffusion alone cannot explain the tracer distributions
+seen in these novel MRI investigations over hours and days. 
+In order to include the complex geometry of the brain as well as the heterogenous CSF flow around the brain, we 
+employed the methods of partial differential constrained optimization in order to  the identify apparent diffusion parameters 
+that best would correspond to the MRI images. Apparent diffusion coefficients that do not match the values those seen in corresponding 
+DTI images would then indicate that diffusion is not sufficient to explain the CSF tracer distribution and would as such be supportive of the glymphatic system. 
+The apparent diffusion coefficients are somewhat larger than what is found in DTI (42\% in grey matter and XX\% in white matter).
 
@@
 of dementias are associated with accumulation of metabolic waste within the brain, the new theory is potentially of fundamental importance for
-the pressing challenges of the aging population. The circulation system is called the glymphatic system as it resembles the lymphatic system in the 
+the pressing challenges of dementia in the aging population. The circulation system is called the glymphatic system as it resembles the lymphatic system in the 
 rest of our body and the 'g' highlight the importance of the glia cells.
 Evidence was given that the activity of the glymphatic system increases during  sleep by ~\citet{xie2013sleep}, thus linking sleep to clearance of toxic substances from the brain.
+
 The system proposes that 
@@
 facilitate clearance of waste.  
+The glympahtic system is still controversial and several computational modeling studies have dismissed the system.  
+For example, the previous studies~\cite{holter2017interstitial, smith2017glymphatic} suggest that diffusion dominates in the interstitium.
+Furthermore, ~\cite{asgari2016glymphatic, brynjfm, Diem} have found that dissipation in the paravascular spaces adds less than a factor two to diffusion for solute transportation.
+All these studies, however, concern the fluid transportation on the microlevel.
+
+On the macroscopic level, using imaging, it is however less clear that diffusion alone provides an adequate explanation. 
 In \cite{iliff2013brain} a procedure for  investigate paravascular transport was proposed  and tested in a rat's brain. The procedure involved injecting a 
@@
 Overall, the MRI-contrast transportation  showed a centripetal and delayed pattern in individuals with dementia as compared with controls~\citet{ringstad2018brain} which showed a more centrifugal pattern.
+It was noted that the CSF-tracer transportation appeard faster than what can be expected from diffusion in simplified geometries.
+However, it was noted that the geometry of
+the brain is quite complex and for instance the surface-to-volume ratio is fivefold that of a ball.
 
-The glympahtic system is controversial as the theory proposes that a significant part of the waste disposal system is driven by convection rather than diffusion. As such
-the system may be much more efficient than if driven by diffusion alone. The theory would also explain why the lymphatic system which elsewhere in our body is crucial for
-removing metabolic waste is not present in the brain even though the brain has a high metabolism; namely that the brain has its own specialized system. 
 The properties of the extracellular diffusion are well-known due to seminal work of Nicholson and colleagues, see  
@@
 due to its small volume, the paravascular compartment may be dominated by the extracellular compartment at short time-scales, while still being a
-significant contributor on longer time scales.
+significant contributor on longer time scales such as those in \cite{ringstad2018brain}.
 
-In \cite{ringstad2018brain} brain-wide distribution of MRI-contrast was demonstrated during 24 hours after lumbar contrast injection.
+%In \cite{ringstad2018brain} brain-wide distribution of MRI-contrast was demonstrated during 24 hours after lumbar contrast injection.
 Brain-wide distribution by diffusion alone was deemed unlikely by the authors.
-The argument was based on analytical considerations where it was calculated that 50\% contrast enrichment would occur after
-55 hours if planar diffusion can be assumed. However, 
-the surface of the brain is folded and is around five times larger than 
-a corresponding surface of a ball with the same volume. The increased
-surface-volume ratio of the brain increases the transportation efficiency.  
-On the other hand the contrast in the surrounding cerebral spinal fluid (CSF) is heterogeneous
-and changes significantly during the 24 hours of the investigations. 
-The heterogeneous distribution decreases the transportation efficiency as the amount of CSF tracer
-at times is very low. A third difficulty is that  
-MRI images were obtained only at a few time-points (around 10)  during the investigations in \cite{ringstad2018brain} which lasted 48 hours.
+The argument was based on analytical considerations where it was calculated that 50\g contrast enrichment would occur after
+%55 hours if planar diffusion can be assumed. However, 
+%the surface of the brain is folded and is around five times larger than 
+%a corresponding surface of a ball with the same volume. The increased
+%surface-volume ratio of the brain increases the transportation efficiency.  
+%On the other hand the contrast in the surrounding cerebral spinal fluid (CSF) is heterogeneous
+%and changes significantly during the 24 hours of the investigations. 
+%The heterogeneous distribution decreases the transportation efficiency as the amount of CSF tracer
+%at times is very low. A third difficulty is that  
+%MRI images were obtained only at a few time-points (around 10)  during the investigations in \cite{ringstad2018brain} which lasted 48 hours. 
+%
 
@@
 The 3 domain mesh in Figure~\ref{Fig::Mesh} A, consists of 244318 tetrahedral cells and 22057 vertices, while the 2 domain mesh (without the CSF compartment) Figure~\ref{Fig::Mesh} B consists of 335589 tetrahedral cells and 73002 vertices.
+
+\section{Numerical Experiments}
+
+The process of estimating the diffusion coefficients in terms of  the PDE constrained optimization problem \eqref{Eq::PDE} is complicated as appropriate parameters, i.e.
+$\alpha$, $\beta$ and $\gamma$,  have
+to be determined and robustness with respect to resolution and noise have to be assessed. Our approach was as follows.
+
+\textbf{Verification of code and the identification of suitable parameters in the case of a manufactored solution.}
+
+In order to verify our code and assess the range of parameters suitable for simulation we performed a series of 
+simulations with regularization parameters, discretization parameters and noise levels.
+
+\textbf{}
 
@@
 
-%\input{supplementary}
+\input{supplementary\_new}
 

### 2019-07-04 tex/rev1/supplementary_new.tex
update

--- 2019-05-02 tex/rev1/supplementary.tex
@@
 
-\subsection{Verification in terms of the manufactured solution}
+\subsection{Testing with a manufactured solution to assess accuracy.}
+
 Below we will discuss the parameter identification and its sensitivity with respect to the regularization parameters, noise, number of observations and time-resolution of the forward model.
@@
 The case when the minimization algorithm fails to converge within 1000 iteration will be indicated by a hyphen in Table~\ref{Tab::Noise0.3}.
-
-\subsubsection{The relaxation parameters}
-The convergence as well as the result of the minimization is influenced by the values of the regularization parameters $\alpha$ and $\beta$.
-Therefore the convergence was examined by a systematic study of the reconstruction of the manufactured solution with respect to a wide range of regularization parameters.
-
-Ideally, our approach should have a wide range of parameters in which the reconstruction algorithm yields very similar end-results although the convergence may vary substantially.
-The evaluation of different regularization parameters was done by solving the optimization with different values of $\alpha$ and $\beta$ and comparing the computed $D$ and $g$ values with the manufactured solution.
-The observation times were set to $\lbrace$2.4, 4.8, 7.2, 9.6, 12.0, 14.4, 16.8, 19.2, 21.6, 24.0 $\rbrace$, and the number of time-steps $k$ in the forward problem was set to $10$.
-
-The results are shown in Table~\ref{Tab::1} and the convergence is shown in Figure~\ref{convergence}.
-We can see that the optimization computed similar end-result for most regularization parameters.
-More specifically, for $\alpha \leq 1\mathrm{e}{-2}$ and $\beta \leq 1e-0$ the relative errors for all optimization parameters are below $5\%$.However, in the case of $ \alpha=1.0$ the relative error is over 100\% higher than for other values of $\alpha$.
-Furthermore, for all $\beta=100.0$ there is about 70\% relative error for $D_{\Omega_1}$ and approximate 10\% error for $D_{\Omega_2}$.
-From the results it can be discerned that $\alpha =1.0$ and $\beta=100.0$ represent an upper threshold where the observations are no longer the dominant term in the objective functional.
-
-\begin{figure}
-\centering
-\includegraphics[scale=0.18]{../Convergence-plot.png}   
-\caption{Convergence plots of the diffusion coefficients, boundary conditions and functional with respect to different $\alpha$ and $\beta$ values. } 
-\label{convergence}
-\end{figure}
-
-In Figure~\ref{boundarycontrol} we can see that more time-steps causes oscillations if $\alpha\gg\beta$ and the number of time-steps are much larger than the number of observations.
-For instance, as seen by the the pink line for $\alpha=1.0$ and $\beta=0.0001$ the peaks corresponds to a observation.
-These oscillations are caused by the strong weighting of $\alpha$, which leads to minimizing of $g$ between observation times.
-Tests with variation in the number of timesteps and observations are documented in the Supplementary.
-
-%It can be seen that more time-steps causes an increase number of iterations, but for some values the number of iterations decreases.
-These values share that $\alpha $ is a magnitude 2 lower than $ \beta$,i.e $\alpha=1.0e-2$ and $\beta =1.0$.
-This indicates that $\alpha $ should be smaller than $\beta$ to achieve optimal convergence.
-However, the number of iterations in Table ~\ref{Tab::1} are smaller for all regularization parameters.
-
-\begin{figure}
-\centering
-\includegraphics[scale=0.21]{../boundary_control.png}  
-\caption{ Displays plots over time for a selection of points at the boundary of $\Omega_1$ with different regularization parameters and number of timesteps $k$.
-The left panel shows the legend for the plot over time, together with the selection of points.
-The middle panel shows the average boundary value $g$ for different regularization parameter with $k=10$.
-The right panel shows the average boundary value $g$ for different regularization parameter with $k=40$.
-}
-\label{boundarycontrol}
-\end{figure}
-
-\subsubsection{The noise susceptibility}
-The MRI data contains noise, hence an investigation to the noise susceptibility is needed.
-This was done varying the noise amplitude, and then the optimization was performed for various regularization parameters $\alpha$ and $\beta$.
-Figure~\ref{12hourswithnoise} and Figure~\ref{24hourswithnoise} show the reconstruction of the manufactured solution at
-different noise levels with $\alpha=0.0001$, $\beta=1.0$ and $k=20$. Clearly, the reconstruction shown in the lower rows is quite robust with respect to the various levels
-of noise shown in the upper rows.      
-In Table~\ref{Tab::Noise0.3} the noise amplitude was set to 0.3 (100$\%$ of maximum initial condition), which gave a visible effect.
-The noise caused the number of iteration to increase, and with more timesteps caused the optimization not to convergence for $\beta < 1.0$.
-Furthermore, the relative boundary error $||g||\sp{rel}$ is significantly larger for $\alpha< 1.0\mathrm{e}{-2} $ and $\beta < 1.0\mathrm{e}{-2}$.
-Results with noise  amplitudes at 0.03 are listed in the Supplementary.
-
-\begin{figure}
-\centering
-\includegraphics[scale=0.4]{../noise-12.png}  
-\caption{The upper row shows the manufactured observation, A) Shows the manufactured observation at time-point 24 with no noise added.
-B) Shows the manufactured observation at time-point 24 with noise amplitude of 0.15.
-C) Shows the manufactures observation at time-point 24 with noise amplitude of 0.3.
-The lower row shows the results with optimized parameter obtained with $\alpha=0.0001$, $\beta=1.0$ and $k=20$.
-D) Shows the resulting state given the observation in A.
-E)  Shows the resulting state given the observation in B .F) Shows the resulting state given the observation in C.
-}
-\label{12hourswithnoise}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[scale=0.4]{../noise-24.png}
-\caption{The upper row shows the manufactured observation, A) Shows the manufactured observation at time-point 24 with no noise added.
-B) Shows the manufactured observation at time-point 24 with noise amplitude of 0.15.
-C) Shows the manufactures observation at time-point 24 with noise amplitude of 0.3.
-The lower row shows the results with optimized parameter obtained with $\alpha=0.0001$, $\beta=1.0$ and $k=20$.
-D) Shows the resulting state given the observation in A.
-E)  Shows the resulting state given the observation in B .F) Shows the resulting state given the observation in C.
-}
-\label{24hourswithnoise}
-\end{figure}
-
-\subsection{Manufactured Solution}
-In order to assess the robustness and accuracy of our strategy and test the dependency of the computed diffusion coefficients $D$ on the
-regularization parameters $\alpha$ and $\beta$, we perform a test case with a
-known solution. The manufactured observations were obtained by forward computation of \eqref{Eq::PDE} with the Dirichlet boundary condition defined as 
-\begin{equation}
-g(t) = 0.3 +0.167t - 0.007t\sp{2} \qquad \text{ for } 0 \leq t \leq 24.
-\label{EQ::DIRI}
-\end{equation}
-The initial condition was set to 0 everywhere, the timestep was $dt = 0.2$, and the diffusion coefficients were selected to be 
-\begin{equation}
-D_{\Omega_1} = 1000.0, \quad D_{\Omega_2} = 4.0, \quad D_{\Omega_3} = 8.0 
-\end{equation}  
-The magnitude order for $D_{\Omega_1} $ and $D_{\Omega_2}$ were chosen to resemble diffusion coefficient for water in grey and white matter, but the relation between the coefficients were not preserved.
-In \citet{Haga}, the drug concentration moved 1 cm per 20 seconds in the cervical region, thus $D_{\Omega_1}$  was set to 1000.
-The manufactured forward computation produced a total of 120 possible observation times.
-
-\subsection{Implementation}
-The solver for \eqref{Eq::PDE} was implemented using the FEniCS project (v.2017.2), using backwards Euler time discretization and first order continuous Galerkin finite elements in space.
-The resulting linear problems were solved using GMRES.
-The module dolfin-adjoint \cite{farrell2013automated, funke2013framework} was used to automatically derive and solve the adjoint problem, and to solve the PDE constrained optimization problem with the L-BFGS-B algorithm \cite{LBFGSB1, LBFGSB2}.
-The optimization was stopped when the $L^\infty$-norm of the projected gradient of the objective functional dropped below $1.0\mathrm{e}{-1}$.
-
-The observations $u_{obs}$ have fixed time-points.
-However, these time-points may not coincide  with the time discretization in the forward problem $t_j$.
-Therefore, we linearly interpolated the computed solutions onto the observation time points using the formula
-\begin{equation}
-\label{observation:interpolation}
-u(t) \approx \frac{\Delta t}{dt} u(t_{j-1}) + \frac{dt - \Delta t }{dt} u(t_{j}), \quad t \in \lbrace t_{j-1}, t_j \rbrace
-\end{equation}
-with $\Delta t = t_j-t$ and $dt = t_j - t_{j-1}$.
-
-The implementation used the first observation as initial conditions of \eqref{Eq::PDE}.
-Then for each time-step, the next observation was used as the initial value for boundary control $g$.
-In order to increase the convergence speed of the optimization, $D_{\Omega_1}$ was scaled so that $D_{\Omega_1} = 100 D_{\Omega_1}\sp{\star} $.
-The initial values of the diffusion coefficients in the optimization algorithm were $(D_{\Omega_1}\sp{\star}, D_{\Omega_2}, D_{\Omega_3})=$  $(1, 1, 1)$.
-
-The noise susceptibility was tested by pointwise adding a uniform distributed noise to the observations.
-The noise term was constructed using the random library in numpy and adjusted so that the noise range was $\lbrace -n_{amp} , n_{amp} \rbrace $, with $n_{amp}$ denoted as noise amplitude.
 
@@
 
-\begin{table}
-\centering
-\caption{Shows the regularization parameters $\alpha$ and $\beta$, number of timesteps $k$ with the resulting number of optimization iterations and the relative error for the control parameters.
-The observations times were chosen $ t_i=[2.4, 4.8,$ 7.2, 9.6, 12.0, 14.4, $16.8, 19.2, 21.6, 24.0]$.}
-\begin{tabular}{*{8}c}
-$\alpha$ & $\beta$ & k  & iter & $ D_{\Omega_1}\sp{rel}$ & $ D_{\Omega_2}\sp{rel} $ & $D_{\Omega_3}\sp{rel}$ & $||g||^{rel}$ \\
-\hline 
- 1.0e+00 	 & 1.0e+02 	 & 10 & 437 	 & +4.631 & +0.283 & +0.103 & +0.127 \\ 
- 1.0e+00 	 & 1.0e+00 	 & 10 & 129 	 & +1.638 & +0.224 & +0.089 & +0.119 \\ 
- 1.0e+00 	 & 1.0e-02 	 & 10 & 129 	 & +1.602 & +0.223 & +0.089 & +0.119 \\ 
- 1.0e+00 	 & 1.0e-04 	 & 10 & 151 	 & +1.608 & +0.223 & +0.089 & +0.119 \\ 
- 1.0e+00 	 & 1.0e-06 	 & 10 & 133 	 & +1.603 & +0.223 & +0.089 & +0.119 \\
-
- 1.0e-02 	 & 1.0e+02 	 & 10 & 186 	 & +0.649 & +0.111 & +0.036 & +0.033 \\ 
- 1.0e-02 	 & 1.0e+00 	 & 10 & 125 	 & -0.027 & +0.041 & +0.036 & +0.026 \\ 
- 1.0e-02 	 & 1.0e-02 	 & 10 & 133 	 & -0.039 & +0.039 & +0.036 & +0.026 \\ 
- 1.0e-02 	 & 1.0e-04 	 & 10 & 108 	 & -0.039 & +0.039 & +0.036 & +0.026 \\ 
- 1.0e-02 	 & 1.0e-06 	 & 10 & 154 	 & -0.039 & +0.039 & +0.036 & +0.026 \\
-
- 1.0e-04 	 & 1.0e+02 	 & 10 & 212 	 & +0.636 & +0.108 & +0.035 & +0.032 \\ 
- 1.0e-04 	 & 1.0e+00 	 & 10 & 143 	 & -0.036 & +0.039 & +0.035 & +0.026 \\ 
- 1.0e-04 	 & 1.0e-02 	 & 10 & 108 	 & -0.047 & +0.037 & +0.036 & +0.026 \\ 
- 1.0e-04 	 & 1.0e-04 	 & 10 & 158 	 & -0.047 & +0.037 & +0.036 & +0.026 \\ 
- 1.0e-04 	 & 1.0e-06 	 & 10 & 142 	 & -0.047 & +0.037 & +0.036 & +0.026 \\
-
- 1.0e-06 	 & 1.0e+02 	 & 10 & 203 	 & +0.636 & +0.108 & +0.035 & +0.032 \\ 
- 1.0e-06 	 & 1.0e+00 	 & 10 & 117 	 & -0.035 & +0.039 & +0.035 & +0.026 \\ 
- 1.0e-06 	 & 1.0e-02 	 & 10 & 120 	 & -0.047 & +0.037 & +0.036 & +0.026 \\ 
- 1.0e-06 	 & 1.0e-04 	 & 10 & 122 	 & -0.047 & +0.037 & +0.036 & +0.026 \\ 
- 1.0e-06 	 & 1.0e-06 	 & 10 & 133 	 & -0.047 & +0.037 & +0.036 & +0.026 \\
-
-\end{tabular}
-\label{Tab::1}
-\end{table}
-
-\begin{table}[t]
-\centering
-\caption{Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$, the resulting number of iterations, the relative error of the estimated optimal parameters for the diffusion coefficients and the relative error for $g$.
-The noise amplitude was set to 0.3, and $t_i =[2.4, 4.8, 7.2, 9.6, 12.0, 14.4, 16.8, 19.2, 21.6, 24.0]$  }
-\begin{tabular}{*{8}c}
-$\alpha$ & $\beta$ & k  & iter & $ D_{\Omega_1}\sp{rel}$ & $D_{\Omega_2}\sp{rel} $ & $D_{\Omega_3}\sp{rel} $ & $||g||\sp{rel} $ \\
-\hline
- 1.0e-02 	 & 1.0e+00 	 & 10 & 144 	 & +0.012 & +0.055 & +0.027 & +0.036 \\ 
- 1.0e-02 	 & 1.0e-02 	 & 10 & 476 	 & -0.009 & +0.049 & +0.035 & +0.051 \\ 
- 1.0e-02 	 & 1.0e-04 	 & 10 & 476 	 & -0.097 & +0.042 & +0.054 & +0.054 \\ 
- 1.0e-02 	 & 1.0e-06 	 & 10 & 558 	 & -0.071 & +0.047 & +0.039 & +0.054 \\ 
- 1.0e-04 	 & 1.0e+00 	 & 10 & 182 	 & -0.040 & +0.033 & +0.051 & +0.037 \\ 
- 1.0e-04 	 & 1.0e-02 	 & 10 & 471 	 & +0.021 & +0.038 & +0.036 & +0.056 \\ 
- 1.0e-04 	 & 1.0e-04 	 & 10 & 792 	 & -0.058 & +0.042 & +0.031 & +0.565 \\ 
- 1.0e-04 	 & 1.0e-06 	 & 10 &  -   & -0.050 & +0.029 & +0.040 & +1.062 \\ 
- 1.0e-06 	 & 1.0e+00 	 & 10 & 178 	 & +0.012 & +0.033 & +0.021 & +0.036 \\ 
- 1.0e-06 	 & 1.0e-02 	 & 10 & 537 	 & -0.018 & +0.040 & +0.025 & +0.057 \\ 
- 1.0e-06 	 & 1.0e-04 	 & 10 &  -	 & -0.038 & +0.040 & +0.030 & +1.452 \\ 
- 1.0e-06 	 & 1.0e-06 	 & 10 &  - 	 & +0.003 & +0.035 & +0.046 & +3.621 \\ 
- 1.0e-02 	 & 1.0e+00 	 & 20 & 213 	 & +0.009 & +0.015 & +0.009 & +0.016 \\ 
- 1.0e-02 	 & 1.0e-02 	 & 20 & 719 	 & +0.228 & +0.088 & -0.032 & +0.085 \\ 
- 1.0e-02 	 & 1.0e-04 	 & 20 &  -   & +0.100 & +0.071 & -0.013 & +0.271 \\ 
- 1.0e-02 	 & 1.0e-06 	 & 20 &   -  & +0.223 & +0.097 & -0.027 & +0.282 \\ 
- 1.0e-04 	 & 1.0e+00 	 & 20 & 245 	 & +0.038 & +0.013 & -0.001 & +0.016 \\ 
- 1.0e-04 	 & 1.0e-02 	 & 20 &  - 	 & +0.050 & +0.054 & -0.024 & +0.116 \\ 
- 1.0e-04 	 & 1.0e-04 	 & 20 &  - 	 & -0.087 & +0.059 & -0.077 & +5.763 \\ 
- 1.0e-04 	 & 1.0e-06 	 & 20 &  -	 & +0.001 & +0.083 & -0.038 & +7.485 \\ 
- 1.0e-06 	 & 1.0e+00 	 & 20 & 242 	 & -0.009 & +0.008 & +0.015 & +0.016 \\ 
- 1.0e-06 	 & 1.0e-02 	 & 20 & 947 	 & +0.122 & +0.093 & -0.040 & +0.115 \\ 
- 1.0e-06 	 & 1.0e-04 	 & 20 &  - 	 & -0.076 & +0.041 & -0.020 & +7.700 \\ 
- 1.0e-06 	 & 1.0e-06 	 & 20 &  - 	 & +0.147 & +0.113 & -0.023 & +10.936 \\
-
-\end{tabular}
-\label{Tab::Noise0.3}
-\end{table}
-
-\begin{table}
-\centering
-\caption{Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$, the resulting number of iterations, the estimated diffusion coefficients for grey $D_{\Omega_{GM}}$ and white $D_{\Omega_{WM}}$ matter based on MRI data.}
-\begin{tabular}{*{6}c}
-$\alpha$ & $\beta$ & k & iter &  $ D_{\Omega_{GM}} \left[ \mathrm{mm\sp{2}/h} \right] $ & $ D_{\Omega_{WM}} \left[ \mathrm{mm\sp{2}/h} \right]$ \\
-\hline
- 1.0e-02 	 & 1.0e+00 	 & 24 & 503 	 & 0.659 & 0.918 \\ 
- 1.0e-02 	 & 1.0e-01 	 & 24 & 716 	 & 0.771 & 0.969 \\ 
- 1.0e-02 	 & 1.0e-02 	 & 24 & 505 	 & 0.836 & 0.974 \\ 
- 1.0e-04 	 & 1.0e+00 	 & 24 & 206 	 & 0.553 & 0.828 \\ 
- 1.0e-04 	 & 1.0e-01 	 & 24 & 440 	 & 0.651 & 0.789 \\ 
- 1.0e-04 	 & 1.0e-02 	 & 24 & 597 	 & 0.718 & 0.739 \\ 
- 1.0e-06 	 & 1.0e+00 	 & 24 & 439 	 & 0.570 & 0.830 \\ 
- 1.0e-06 	 & 1.0e-01 	 & 24 & 583 	 & 0.656 & 0.793 \\ 
- 1.0e-06 	 & 1.0e-02 	 & 24 & 742 	 & 0.721 & 0.729 \\
-
- %1.0e-02    & 1.0e+02   & 48 & 714      & 0.564 & 0.952 ?? \\ 
- 1.0e-02 	 & 1.0e+00 	 & 48 & 591 	 & 0.648 & 0.893 \\ 
- 1.0e-02 	 & 1.0e-01 	 & 48 & 461 	 & 0.772 & 0.982 \\ 
- 1.0e-02 	 & 1.0e-02 	 & 48 & 748 	 & 0.986 & 1.198 \\ 
- %1.0e-04    & 1.0e+02   & 48 & 815      & 0.470 & 0.928 \\ 
- 1.0e-04 	 & 1.0e+00 	 & 48 & 607 	 & 0.551 & 0.815 \\ 
- 1.0e-04 	 & 1.0e-01 	 & 48 & 598 	 & 0.649 & 0.787 \\ 
- 1.0e-04 	 & 1.0e-02 	 & 48 & 837 	 & 0.740 & 0.817 \\
- %1.0e-06    & 1.0e+02   & 48 & 729      & 0.428 & 0.948 \\ 
- 1.0e-06 	 & 1.0e+00 	 & 48 & 681 	 & 0.557 & 0.811 \\ 
- 1.0e-06 	 & 1.0e-01 	 & 48 & 780 	 & 0.645 & 0.774 \\ 
- 1.0e-06 	 & 1.0e-02 	 & 48 & 745 	 & 0.736 & 0.819 \\
-
-\end{tabular}
-\label{Tab::Real-data}
-\end{table}
-
-\subsubsection{The number of timessteps}
-Increasing the number of time-steps in the computations can potentially allow for a more accurate temporal reconstruction, but at the same time the number of observations per control decreases and the regularization may therefore play a larger role.
-Furthermore, the computational cost will rise with additional time-steps.
-Thus finding the optimal number of time-steps can be essential for solving larger problems.
-The computation used a wide range the regularization parameters, and the number of timesteps were selected to be 20 and 40.
-
-The results are given in Table~\ref{TAB::timesteps}.
-It can be seen for all $\alpha=1.0$ that the relative error becomes bigger with more time-steps.
-This behavior can also be seen for $\alpha=1.0\mathrm{e}{-2}$ and $\beta < 1.0\mathrm{e}{-2}$, which implies an interaction between the regularization parameters.
-Therefore $g$ was investigated by plotting boundary points through time for different values of $\alpha$ and $\beta$, see Fig \ref{boundarycontrol}.
-
-\begin{table}
-\centering
-\caption{ Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$, the resulting number of iterations, the relative error of the estimated diffusion coefficients and the relative error for $g$.
-The observations times were chosen $ t_i=[2.4,  4.8,$ 7.2, 9.6, 12.0, 14.4, $16.8, 19.2, 21.6, 24.0]$ }
-\begin{tabular}{*{8}c}
-$\alpha$ & $\beta$ & k & iter & $ D_{\Omega_1}\sp{rel}$& $D_{\Omega_2}\sp{rel} $ & $D_{\Omega_3}\sp{rel} $&$|| g ||\sp{rel} $ \\
-\hline
- 1.0e+00 	 & 1.0e+02 	 & 20 & 600 	 & +6.412 & +0.175 & +0.086 & +0.124 \\
- 1.0e+00 	 & 1.0e+02 	 & 40 &  -   & +6.702 & +0.130 & +0.082 & +0.125 \\  
- 1.0e+00 	 & 1.0e+00 	 & 20 & 300 	 & +5.538 & +0.324 & +0.148 & +0.128 \\ 
- 1.0e+00 	 & 1.0e+00 	 & 40 & 346 	 & +11.392 & +0.873 & +0.242 & +0.154 \\ 
- 1.0e+00 	 & 1.0e-02 	 & 20 & 415 	 & +18.156 & +1.378  & +0.389  & +0.251 \\ 
- 1.0e+00 	 & 1.0e-02 	 & 40 & 856 	 & +64.050 & +17.408 & +15.950 & +0.614 \\ 
- 1.0e+00 	 & 1.0e-04 	 & 20 & 417 	 & +17.747 & +1.465  & +0.406  & +0.258 \\ 
- 1.0e+00 	 & 1.0e-04 	 & 40 & 946 	 & +72.594 & +17.985 & +16.702 & +0.641 \\
- 1.0e+00 	 & 1.0e-06 	 & 20 & 399 	 & +17.407 & +1.466  & +0.406  & +0.258 \\ 
- 1.0e+00 	 & 1.0e-06 	 & 40 & 863 	 & +60.448 & +18.043 & +16.732 & +0.641 \\
- \hline
- 1.0e-02 	 & 1.0e+02 	 & 20 & 351 	 & +0.865 & +0.001 & +0.017 & +0.027 \\ 
- 1.0e-02 	 & 1.0e+02 	 & 40 & 404 	 & +0.846 & -0.049 & +0.010 & +0.026 \\ 
- 1.0e-02 	 & 1.0e+00 	 & 20 & 254 	 & +0.018 & +0.007 & +0.008 & +0.007 \\ 
- 1.0e-02 	 & 1.0e+00 	 & 40 & 218 	 & +0.020 & -0.006 & +0.001 & +0.003 \\ 
- 1.0e-02 	 & 1.0e-02 	 & 20 & 381 	 & +0.127 & +0.057 & -0.001 & +0.016 \\ 
- 1.0e-02 	 & 1.0e-02 	 & 40 & 543 	 & +0.099 & +0.087 & +0.002 & +0.023 \\
- 1.0e-02 	 & 1.0e-04 	 & 20 & 641 	 & +0.171 & +0.082 & -0.003 & +0.091 \\ 
- 1.0e-02 	 & 1.0e-04 	 & 40 & 879 	 & +0.303 & +0.383 & +0.079 & +0.222 \\ 
- 1.0e-02 	 & 1.0e-06 	 & 20 & 547 	 & +0.173 & +0.084 & -0.003 & +0.092 \\
- 1.0e-02 	 & 1.0e-06 	 & 40 & 844 	 & +0.332 & +0.416 & +0.095 & +0.239 \\ 
- \hline 
- 1.0e-04 	 & 1.0e+02 	 & 20 & 257 	 & +0.853 & -0.001 & +0.017 & +0.026 \\ 
- 1.0e-04 	 & 1.0e+02 	 & 40 & 532 	 & +0.822 & -0.051 & +0.010 & +0.026 \\ 
- 1.0e-04 	 & 1.0e+00 	 & 20 & 164 	 & +0.008 & +0.003 & +0.008 & +0.007 \\ 
- 1.0e-04 	 & 1.0e+00 	 & 40 & 203 	 & +0.005 & -0.012 & +0.001 & +0.003 \\  
- 1.0e-04 	 & 1.0e-02 	 & 20 & 313 	 & +0.071 & +0.021 & -0.001 & +0.007 \\ 
- 1.0e-04 	 & 1.0e-02 	 & 40 & 294 	 & +0.004 & +0.004 & -0.001 & +0.001 \\ 
- 1.0e-04 	 & 1.0e-04 	 & 20 & 265 	 & +0.108 & +0.035 & -0.002 & +0.014 \\
- 1.0e-04 	 & 1.0e-04 	 & 40 & 401 	 & -0.010 & -0.002 & -0.002 & +0.004 \\ 
- 1.0e-04 	 & 1.0e-06 	 & 20 & 452 	 & +0.066 & +0.021 & -0.003 & +0.031 \\ 
- 1.0e-04 	 & 1.0e-06 	 & 40 & 330 	 & -0.014 & -0.013 & -0.003 & +0.004 \\ 
- \hline
- 1.0e-06 	 & 1.0e+02 	 & 20 & 274 	 & +0.850 & -0.001 & +0.017 & +0.026 \\ 
- 1.0e-06 	 & 1.0e+02 	 & 40 & 496 	 & +0.821 & -0.051 & +0.010 & +0.026 \\
- 1.0e-06 	 & 1.0e+00 	 & 20 & 176 	 & +0.008 & +0.003 & +0.008 & +0.007 \\ 
- 1.0e-06 	 & 1.0e+00 	 & 40 & 207 	 & +0.006 & -0.012 & +0.001 & +0.003 \\ 
- 1.0e-06 	 & 1.0e-02 	 & 20 & 223 	 & +0.075 & +0.024 & -0.001 & +0.007 \\ 
- 1.0e-06 	 & 1.0e-02 	 & 40 & 392 	 & +0.000 & -0.001 & -0.001 & +0.002 \\ 
- 1.0e-06 	 & 1.0e-04 	 & 20 & 429 	 & +0.085 & +0.027 & -0.002 & +0.025 \\ 
- 1.0e-06 	 & 1.0e-04 	 & 40 & 241 	 & -0.020 & -0.030 & -0.005 & +0.005 \\ 
- 1.0e-06 	 & 1.0e-06 	 & 20 & 591 	 & +0.060 & +0.021 & -0.003 & +0.048 \\ 
- 1.0e-06 	 & 1.0e-06 	 & 40 & 343 	 & -0.014 & -0.010 & -0.003 & +0.004 \\
-
-\end{tabular}
-\label{TAB::timesteps}
-\end{table}
-
-\subsubsection{The number of observations}
-The dependency on observations is relevant, since the number of observations of the MRI data is limited.
-This dependency was investigated by changing the number of observations, and by examining the results.
-The number of observation were chosen to be 5 and 20, and the observation times were evenly spaced.
-
-The results for 5 observations is shown in Table~\ref{TAB::half} and for 20 observations is shown in Table~\ref{TAB::double}.
-In Table~\ref{TAB::half}, the values $\alpha =1.0\mathrm{e}{-2}$ and $\beta<1.0$ gives a surge in the relative error with more time-steps.
-This behavior is neither visible in Table~\ref{TAB::timesteps} or in  Table~\ref{TAB::double} for the same regularization parameters.
-The ratio observations per control indicates that the increase in relative error is due to oscillations, similar to those seen in Figure~\ref{boundarycontrol}.
-Thus the observations acts as stabilization for the functional, which gives a broader range of adequate regularization parameters.
-
-\begin{table}
-\centering
-\caption{ Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$, the resulting number of iterations, the relative error of the estimated diffusion coefficients and the relative error for $g$.
-The observation times were set $t_i = [ 4.8, 9.6, 14.4, 19.2, 24.0 ] $.
-}
-\begin{tabular}{*{8}c}
-$\alpha$ & $\beta$ & k & iter & $ D_{\Omega_1}\sp{rel}$& $D_{\Omega_2}\sp{rel} $ & $D_{\Omega_3}\sp{rel} $& $||g||\sp{rel} $ \\
-\hline
- 1.0e-02 	 & 1.0e+00 	 & 10 & 151 	 & +0.095 & +0.015 & +0.028 & +0.020 \\ 
- 1.0e-02 	 & 1.0e+00 	 & 20 & 165 	 & +0.092 & -0.001 & -0.001 & +0.008 \\ 
- 1.0e-02 	 & 1.0e+00 	 & 40 & 228 	 & +0.067 & -0.024 & -0.011 & +0.005 \\
-
- 1.0e-02 	 & 1.0e-02 	 & 10 & 330 	 & +0.190 & +0.074 & +0.027 & +0.083 \\ 
- 1.0e-02 	 & 1.0e-02 	 & 20 & 455 	 & +3.882 & +3.297 & +2.583 & +0.304 \\ 
-  1.0e-02 	 & 1.0e-02 	 & 40 & 523 	 & +7.466 & +6.454 & +5.537 & +0.388 \\
-
- 1.0e-02 	 & 1.0e-04 	 & 10 & 428 	 & +0.196 & +0.076 & +0.032 & +0.163 \\ 
- 1.0e-02 	 & 1.0e-04 	 & 20 & 571 	 & +7.402 & +6.421 & +5.405 & +0.680 \\ 
- 1.0e-02 	 & 1.0e-04 	 & 40 & 747 	 & +15.386 & +13.764 & +12.196 & +0.841 \\
-
-  1.0e-04 	 & 1.0e+00 	 & 10 & 147 	 & +0.081 & +0.008 & +0.023 & +0.020 \\ 
-  1.0e-04 	 & 1.0e+00 	 & 20 & 167 	 & +0.051 & -0.026 & -0.009 & +0.008 \\ 
-  1.0e-04 	 & 1.0e+00 	 & 40 & 148 	 & +0.018 & -0.057 & -0.020 & +0.005 \\
-
- 1.0e-04 	 & 1.0e-02 	 & 10 & 255 	 & +0.171 & +0.087 & +0.010 & +0.021 \\ 
- 1.0e-04 	 & 1.0e-02 	 & 20 & 216 	 & -0.005 & -0.006 & -0.008 & +0.008 \\ 
- 1.0e-04 	 & 1.0e-02 	 & 40 & 386 	 & -0.004 & -0.012 & -0.015 & +0.004 \\
-
- 1.0e-04 	 & 1.0e-04 	 & 10 & 284 	 & +0.059 & +0.052 & +0.010 & +0.051 \\ 
- 1.0e-04 	 & 1.0e-04 	 & 20 & 256 	 & -0.048 & -0.045 & -0.024 & +0.020 \\ 
-  1.0e-04 	 & 1.0e-04 	 & 40 & 277 	 & -0.071 & -0.074 & -0.050 & +0.018 \\
-
- 1.0e-06 	 & 1.0e+00 	 & 10 & 163 	 & +0.082 & +0.008 & +0.023 & +0.020 \\ 
- 1.0e-06 	 & 1.0e+00 	 & 20 & 156 	 & +0.054 & -0.027 & -0.009 & +0.008 \\ 
- 1.0e-06 	 & 1.0e+00 	 & 40 & 284 	 & +0.020 & -0.055 & -0.019 & +0.005 \\
-
- 1.0e-06 	 & 1.0e-02 	 & 10 & 290 	 & +0.155 & +0.075 & +0.011 & +0.021 \\ 
- 1.0e-06 	 & 1.0e-02 	 & 20 & 239 	 & -0.004 & +0.002 & -0.006 & +0.008 \\ 
- 1.0e-06 	 & 1.0e-02 	 & 40 & 378 	 & -0.005 & -0.013 & -0.016 & +0.004 \\
-
- 1.0e-06 	 & 1.0e-04 	 & 10 & 264 	 & +0.070 & +0.056 & +0.009 & +0.050 \\ 
- 1.0e-06 	 & 1.0e-04 	 & 20 & 234 	 & -0.047 & -0.044 & -0.029 & +0.020 \\
- 1.0e-06 	 & 1.0e-04 	 & 40 & 324 	 & -0.070 & -0.070 & -0.052 & +0.017 \\
-
-\end{tabular}
-\label{TAB::half}
-\end{table}
-
-\begin{table}
-\centering
-\caption{ Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$, the resulting number of iterations, the relative error of the estimated diffusion coefficients and the relative error for $g$.
-The observation times were $t_i = [ $1.2, 2.4, 3.6, 4.8, 6.0, 7.2, 8.4, 9.6, 10.8, 12.0, 13.2, 14.4, 15.6, 16.8, 17.0, 19.2, 20.4,$ 21.6, 22.8, 24.0 ]$.}
-\begin{tabular}{*{8}c}
-$\alpha$ & $\beta$ & k & iter & $ D_{\Omega_1}\sp{rel}$ & $ D_{\Omega_2}\sp{rel}$ & $D_{\Omega_3}\sp{rel} $ & $||g||\sp{rel} $ \\
-\hline
-
- 1.0e-02 	 & 1.0e+00 	 & 10 & 250 	 & -0.038 & +0.035 & +0.019 & +0.033 \\ 
- 1.0e-02 	 & 1.0e+00 	 & 20 & 225 	 & -0.002 & +0.015 & +0.007 & +0.007 \\ 
- 1.0e-02 	 & 1.0e+00 	 & 40 & 255 	 & +0.003 & +0.002 & +0.001 & +0.002 \\
-
- 1.0e-02 	 & 1.0e-02 	 & 10 & 180 	 & -0.042 & +0.034 & +0.020 & +0.033 \\ 
- 1.0e-02 	 & 1.0e-02 	 & 20 & 445 	 & +0.010 & +0.017 & +0.003 & +0.010 \\ 
-  1.0e-02 	 & 1.0e-02 	 & 40 & 429 	 & +0.037 & +0.014 & -0.003 & +0.004 \\
-
- 1.0e-02 	 & 1.0e-04 	 & 10 & 208 	 & -0.042 & +0.034 & +0.020 & +0.033 \\ 
-  1.0e-02 	 & 1.0e-04 	 & 20 & 530 	 & +0.012 & +0.017 & +0.003 & +0.020 \\ 
- 1.0e-02 	 & 1.0e-04 	 & 40 & - 	 & +0.064 & +0.023 & -0.005 & +0.072 \\
-
- 1.0e-04 	 & 1.0e+00 	 & 10 & 209 	 & -0.043 & +0.033 & +0.019 & +0.033 \\ 
- 1.0e-04 	 & 1.0e+00 	 & 20 & 212 	 & -0.007 & +0.014 & +0.007 & +0.007 \\ 
- 1.0e-04 	 & 1.0e+00 	 & 40 & 258 	 & -0.002 & +0.001 & +0.001 & +0.002 \\
-
- 1.0e-04 	 & 1.0e-02 	 & 10 & 258 	 & -0.047 & +0.033 & +0.020 & +0.033 \\ 
- 1.0e-04 	 & 1.0e-02 	 & 20 & 391 	 & +0.005 & +0.016 & +0.003 & +0.008 \\ 
- 1.0e-04 	 & 1.0e-02 	 & 40 & 261 	 & +0.014 & +0.005 & -0.002 & +0.001 \\
-
- 1.0e-04 	 & 1.0e-04 	 & 10 & 267 	 & -0.047 & +0.033 & +0.020 & +0.033 \\ 
- 1.0e-04 	 & 1.0e-04 	 & 20 & 769 	 & +0.008 & +0.016 & +0.003 & +0.016 \\
- 1.0e-04 	 & 1.0e-04 	 & 40 & 375 	 & +0.027 & +0.005 & -0.003 & +0.002 \\
-
- 1.0e-06 	 & 1.0e+00 	 & 10 & 198 	 & -0.042 & +0.033 & +0.019 & +0.033 \\ 
- 1.0e-06 	 & 1.0e+00 	 & 20 & 222 	 & -0.007 & +0.014 & +0.007 & +0.007 \\ 
- 1.0e-06 	 & 1.0e+00 	 & 40 & 280 	 & -0.001 & +0.001 & +0.001 & +0.002 \\
-
- 1.0e-06 	 & 1.0e-02 	 & 10 & 279 	 & -0.047 & +0.033 & +0.020 & +0.033 \\ 
- 1.0e-06 	 & 1.0e-02 	 & 20 & 312 	 & +0.005 & +0.016 & +0.003 & +0.008 \\ 
- 1.0e-06 	 & 1.0e-02 	 & 40 & 379 	 & +0.015 & +0.005 & -0.002 & +0.001 \\
-
- 1.0e-06 	 & 1.0e-04 	 & 10 & 251 	 & -0.047 & +0.033 & +0.020 & +0.033 \\ 
- 1.0e-06 	 & 1.0e-04 	 & 20 & 778 	 & +0.008 & +0.016 & +0.002 & +0.018 \\ 
- 1.0e-06 	 & 1.0e-04 	 & 40 & 191 	 & +0.017 & +0.004 & -0.002 & +0.002 \\
-
-\end{tabular}
-\label{TAB::double}
-\end{table}
-
-In Table~\ref{Tab::Noise0.03}, we can see that a noise amplitude of 0.03, (10$\%$ of maximum initial condition) had negligible effect on the relative errors compared zero noise in Table~\ref{Tab::1} and Table~\ref{TAB::timesteps}.
-
-\begin{table}
-\centering
-\caption{Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$, the resulting number of iterations, the relative error of the estimated optimal parameters for the diffusion coefficients and the relative error for $g$.
-The noise amplitude was set to 0.03, and $ t_i=[2.4, 4.8, 7.2, 9.6, 12.0, 14.4, 16.8, 19.2, 21.6, 24.0]$ }
-\begin{tabular}{*{8}c}
-$\alpha$ & $\beta$ & k  & iter & $ D_{\Omega_1}\sp{rel} $ & $D_{\Omega_2}\sp{rel}$ & $D_{\Omega_3}\sp{rel}$ & $||g||\sp{rel} $\\
-\hline
- 1.0e-02 	 & 1.0e+00 	 & 10 & 151 	 & -0.030 & +0.041 & +0.036 & +0.026 \\ 
- 1.0e-02 	 & 1.0e-02 	 & 10 & 120 	 & -0.032 & +0.039 & +0.036 & +0.026 \\ 
- 1.0e-02 	 & 1.0e-04 	 & 10 & 125 	 & -0.038 & +0.039 & +0.037 & +0.026 \\ 
- 1.0e-02 	 & 1.0e-06 	 & 10 & 167 	 & -0.040 & +0.039 & +0.036 & +0.026 \\ 
- 1.0e-04 	 & 1.0e+00 	 & 10 & 161 	 & -0.038 & +0.039 & +0.035 & +0.026 \\ 
- 1.0e-04 	 & 1.0e-02 	 & 10 & 95 	 & -0.047 & +0.036 & +0.036 & +0.026 \\ 
- 1.0e-04 	 & 1.0e-04 	 & 10 & 75 	 & -0.041 & +0.036 & +0.035 & +0.026 \\ 
- 1.0e-04 	 & 1.0e-06 	 & 10 & 136 	 & -0.044 & +0.036 & +0.036 & +0.026 \\ 
- 1.0e-06 	 & 1.0e+00 	 & 10 & 134 	 & -0.034 & +0.037 & +0.037 & +0.026 \\ 
- 1.0e-06 	 & 1.0e-02 	 & 10 & 112 	 & -0.046 & +0.038 & +0.036 & +0.026 \\ 
- 1.0e-06 	 & 1.0e-04 	 & 10 & 111 	 & -0.043 & +0.036 & +0.037 & +0.026 \\ 
- 1.0e-06 	 & 1.0e-06 	 & 10 & 214 	 & -0.049 & +0.037 & +0.036 & +0.026 \\
-
- 1.0e-02 	 & 1.0e+00 	 & 20 & 190 	 & +0.013 & +0.006 & +0.008 & +0.007 \\ 
- 1.0e-02 	 & 1.0e-02 	 & 20 & 392 	 & +0.126 & +0.057 & +0.001 & +0.017 \\ 
- 1.0e-02 	 & 1.0e-04 	 & 20 & 677 	 & +0.164 & +0.074 & -0.001 & +0.093 \\ 
- 1.0e-02 	 & 1.0e-06 	 & 20 & 600 	 & +0.179 & +0.081 & -0.001 & +0.098 \\ 
- 1.0e-04 	 & 1.0e+00 	 & 20 & 224 	 & +0.006 & +0.004 & +0.008 & +0.007 \\ 
- 1.0e-04 	 & 1.0e-02 	 & 20 & 465 	 & +0.074 & +0.022 & -0.003 & +0.008 \\ 
- 1.0e-04 	 & 1.0e-04 	 & 20 & 586 	 & +0.071 & +0.023 & -0.005 & +0.056 \\ 
- 1.0e-04 	 & 1.0e-06 	 & 20 & 472 	 & +0.081 & +0.024 & -0.003 & +0.056 \\ 
- 1.0e-06 	 & 1.0e+00 	 & 20 & 157 	 & +0.011 & +0.003 & +0.009 & +0.007 \\ 
- 1.0e-06 	 & 1.0e-02 	 & 20 & 352 	 & +0.076 & +0.021 & +0.000 & +0.008 \\ 
- 1.0e-06 	 & 1.0e-04 	 & 20 & 738 	 & +0.083 & +0.026 & -0.004 & +0.065 \\ 
- 1.0e-06 	 & 1.0e-06 	 & 20 & 599 	 & +0.056 & +0.021 & -0.003 & +0.106 \\
-
-\end{tabular}
-\label{Tab::Noise0.03}
-\end{table}
+\section{

### 2019-07-05 tex/rev1/paper.tex
update

@@
 \end{equation}
+\kam{Fiks likningene}
 Here, $u$ is the contrast distribution, $D$ is the apparent diffusion 
@@
 
-\textbf{Verification of code and the identification of suitable parameters in the case of a manufactored solution.}
+\textbf{Manufactored solution.}
 
 In order to verify our code and assess the range of parameters suitable for simulation we performed a series of 
-simulations with regularization parameters, discretization parameters and noise levels.
+simulations with regularization parameters, discretization parameters and noise levels against a 
+known manufactured solution. A total of 141 numerical experiments
+where conducted. The details of the numerical tests can be found in the Supplementary \ref{sup:manu}.
 
@@
 \section{Results}
-\subsection{A Real case}
+
+\subsection{Estimation of diffusion coefficients with a manufactored Solution.} 
+We first ran a series of tests of different $\alpha$ and $\beta$ for the manufactured solutions where we assumed observations every 2.4 hours
+over the course of 24 hours. It was found that for $\alpha \in (10^{-6}, 10^{-2}$ and $\beta\in(10^{-6}, 10^2)$, the error in 
+the diffusion coefficients of both CSF, grey and white matter was less than 7\%. Furthermore,  
+$\alpha \in (10^{-6}, 10^{-2}$ and $\beta\in(10^{-6}, 10^{-2})$ gave errors of less than 1\%. Second, the robustness with respect noise
+was investigated. The noiseamplitude was set to 0.3 which equals the initial condition of the manufactured solution
+and 23\% of the manufactured solution at its max.
+The method was found robust with respect to the noise, as illustrated in the Supplementary Fig~\ref{12hourswithnoise}.
+In fact, for  $\alpha \in (10^{-6}, 10^{-2}$ and $\beta\in(10^{-6}, 10^{-2})$ the error in the diffusion coefficients in CSF was less than 23\% and less than 9.7\% in grey and white matter.
+\kam{Lars: skriv om resten av eksperimentene}
+
+\subsection{Estimation of the diffusion coefficients from the MRI data}
 
@@
 
-\input{supplementary\_new}
+\input{supplementarynew}
 

### 2019-07-05 tex/rev1/supplementarynew.tex
update

--- 2019-05-02 tex/rev1/supplementary.tex
@@
 
-\subsection{Verification in terms of the manufactured solution}
+\subsection{Testing with a manufactured solution to assess accuracy.}
+\label{sup:manu}
+
 Below we will discuss the parameter identification and its sensitivity with respect to the regularization parameters, noise, number of observations and time-resolution of the forward model. 
-When presenting the results, we denote the relative error of the diffusion parameters as
-\begin{equation}
- D_{\Omega_i}\sp{rel} = \frac{D_{\Omega_i}\sp{found} -D_{\Omega_i}\sp{true} }{D_{\Omega_i}\sp{true} }, \text{ for } i=1,2,3
-\end{equation}
-For the boundary parameter $g$, the relative error norm is defined as 
-\begin{equation}
-|| g ||\sp{rel} = \frac{ \sum\limits_{t_j} || g_{found}(t_j) -g_{true}(t_j)||_{L^2(\Omega_1)} }{  \sum\limits_{t_j}||g_{true}(t_j)||_{L^2(\Omega_1)} }
-\end{equation}
-The case when the minimization algorithm fails to converge within 1000 iteration will be indicated by a hyphen in Table~\ref{Tab::Noise0.3}.
-
-\subsubsection{The relaxation parameters}
-The convergence as well as the result of the minimization is influenced by the values of the regularization parameters $\alpha$ and $\beta$.
-Therefore the convergence was examined by a systematic study of the reconstruction of the manufactured solution with respect to a wide range of regularization parameters.
-
-Ideally, our approach should have a wide range of parameters in which the reconstruction algorithm yields very similar end-results although the convergence may vary substantially.
-The evaluation of different regularization parameters was done by solving the optimization with different values of $\alpha$ and $\beta$ and comparing the computed $D$ and $g$ values with the manufactured solution.
-The observation times were set to $\lbrace$2.4, 4.8, 7.2, 9.6, 12.0, 14.4, 16.8, 19.2, 21.6, 24.0 $\rbrace$, and the number of time-steps $k$ in the forward problem was set to $10$.
-
-The results are shown in Table~\ref{Tab::1} and the convergence is shown in Figure~\ref{convergence}.
-We can see that the optimization computed similar end-result for most regularization parameters.
-More specifically, for $\alpha \leq 1\mathrm{e}{-2}$ and $\beta \leq 1e-0$ the relative errors for all optimization parameters are below $5\%$.However, in the case of $ \alpha=1.0$ the relative error is over 100\% higher than for other values of $\alpha$.
-Furthermore, for all $\beta=100.0$ there is about 70\% relative error for $D_{\Omega_1}$ and approximate 10\% error for $D_{\Omega_2}$.
-From the results it can be discerned that $\alpha =1.0$ and $\beta=100.0$ represent an upper threshold where the observations are no longer the dominant term in the objective functional.
-
-\begin{figure}
-\centering
-\includegraphics[scale=0.18]{../Convergence-plot.png}   
-\caption{Convergence plots of the diffusion coefficients, boundary conditions and functional with respect to different $\alpha$ and $\beta$ values. } 
-\label{convergence}
-\end{figure}
-
-In Figure~\ref{boundarycontrol} we can see that more time-steps causes oscillations if $\alpha\gg\beta$ and the number of time-steps are much larger than the number of observations.
-For instance, as seen by the the pink line for $\alpha=1.0$ and $\beta=0.0001$ the peaks corresponds to a observation.
-These oscillations are caused by the strong weighting of $\alpha$, which leads to minimizing of $g$ between observation times.
-Tests with variation in the number of timesteps and observations are documented in the Supplementary.
-
-%It can be seen that more time-steps causes an increase number of iterations, but for some values the number of iterations decreases.
-These values share that $\alpha $ is a magnitude 2 lower than $ \beta$,i.e $\alpha=1.0e-2$ and $\beta =1.0$.
-This indicates that $\alpha $ should be smaller than $\beta$ to achieve optimal convergence.
-However, the number of iterations in Table ~\ref{Tab::1} are smaller for all regularization parameters.
-
-\begin{figure}
-\centering
-\includegraphics[scale=0.21]{../boundary_control.png}  
-\caption{ Displays plots over time for a selection of points at the boundary of $\Omega_1$ with different regularization parameters and number of timesteps $k$.
-The left panel shows the legend for the plot over time, together with the selection of points.
-The middle panel shows the average boundary value $g$ for different regularization parameter with $k=10$.
-The right panel shows the average boundary value $g$ for different regularization parameter with $k=40$.
-}
-\label{boundarycontrol}
-\end{figure}
-
-\subsubsection{The noise susceptibility}
-The MRI data contains noise, hence an investigation to the noise susceptibility is needed.
-This was done varying the noise amplitude, and then the optimization was performed for various regularization parameters $\alpha$ and $\beta$.
-Figure~\ref{12hourswithnoise} and Figure~\ref{24hourswithnoise} show the reconstruction of the manufactured solution at
-different noise levels with $\alpha=0.0001$, $\beta=1.0$ and $k=20$. Clearly, the reconstruction shown in the lower rows is quite robust with respect to the various levels
-of noise shown in the upper rows.      
-In Table~\ref{Tab::Noise0.3} the noise amplitude was set to 0.3 (100$\%$ of maximum initial condition), which gave a visible effect.
-The noise caused the number of iteration to increase, and with more timesteps caused the optimization not to convergence for $\beta < 1.0$.
-Furthermore, the relative boundary error $||g||\sp{rel}$ is significantly larger for $\alpha< 1.0\mathrm{e}{-2} $ and $\beta < 1.0\mathrm{e}{-2}$.
-Results with noise  amplitudes at 0.03 are listed in the Supplementary.
-
-\begin{figure}
-\centering
-\includegraphics[scale=0.4]{../noise-12.png}  
-\caption{The upper row shows the manufactured observation, A) Shows the manufactured observation at time-point 24 with no noise added.
-B) Shows the manufactured observation at time-point 24 with noise amplitude of 0.15.
-C) Shows the manufactures observation at time-point 24 with noise amplitude of 0.3.
-The lower row shows the results with optimized parameter obtained with $\alpha=0.0001$, $\beta=1.0$ and $k=20$.
-D) Shows the resulting state given the observation in A.
-E)  Shows the resulting state given the observation in B .F) Shows the resulting state given the observation in C.
-}
-\label{12hourswithnoise}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[scale=0.4]{../noise-24.png}
-\caption{The upper row shows the manufactured observation, A) Shows the manufactured observation at time-point 24 with no noise added.
-B) Shows the manufactured observation at time-point 24 with noise amplitude of 0.15.
-C) Shows the manufactures observation at time-point 24 with noise amplitude of 0.3.
-The lower row shows the results with optimized parameter obtained with $\alpha=0.0001$, $\beta=1.0$ and $k=20$.
-D) Shows the resulting state given the observation in A.
-E)  Shows the resulting state given the observation in B .F) Shows the resulting state given the observation in C.
-}
-\label{24hourswithnoise}
-\end{figure}
-
-\subsection{Manufactured Solution}
-In order to assess the robustness and accuracy of our strategy and test the dependency of the computed diffusion coefficients $D$ on the
-regularization parameters $\alpha$ and $\beta$, we perform a test case with a
-known solution. The manufactured observations were obtained by forward computation of \eqref{Eq::PDE} with the Dirichlet boundary condition defined as 
+The manufactured observations were obtained by forward computation of \eqref{Eq::PDE} with the Dirichlet boundary condition defined as 
 \begin{equation}
@@
 \end{equation}
-The magnitude order for $D_{\Omega_1} $ and $D_{\Omega_2}$ were chosen to resemble diffusion coefficient for water in grey and white matter, but the relation between the coefficients were not preserved.
-In \citet{Haga}, the drug concentration moved 1 cm per 20 seconds in the cervical region, thus $D_{\Omega_1}$  was set to 1000.
-The manufactured forward computation produced a total of 120 possible observation times.
 
-\subsection{Implementation}
-The solver for \eqref{Eq::PDE} was implemented using the FEniCS project (v.2017.2), using backwards Euler time discretization and first order continuous Galerkin finite elements in space.
-The resulting linear problems were solved using GMRES.
-The module dolfin-adjoint \cite{farrell2013automated, funke2013framework} was used to automatically derive and solve the adjoint problem, and to solve the PDE constrained optimization problem with the L-BFGS-B algorithm \cite{LBFGSB1, LBFGSB2}.
-The optimization was stopped when the $L^\infty$-norm of the projected gradient of the objective functional dropped below $1.0\mathrm{e}{-1}$.
-
-The observations $u_{obs}$ have fixed time-points.
-However, these time-points may not coincide  with the time discretization in the forward problem $t_j$.
-Therefore, we linearly interpolated the computed solutions onto the observation time points using the formula
-\begin{equation}
-\label{observation:interpolation}
-u(t) \approx \frac{\Delta t}{dt} u(t_{j-1}) + \frac{dt - \Delta t }{dt} u(t_{j}), \quad t \in \lbrace t_{j-1}, t_j \rbrace
-\end{equation}
-with $\Delta t = t_j-t$ and $dt = t_j - t_{j-1}$.
-
-The implementation used the first observation as initial conditions of \eqref{Eq::PDE}.
-Then for each time-step, the next observation was used as the initial value for boundary control $g$.
-In order to increase the convergence speed of the optimization, $D_{\Omega_1}$ was scaled so that $D_{\Omega_1} = 100 D_{\Omega_1}\sp{\star} $.
-The initial values of the diffusion coefficients in the optimization algorithm were $(D_{\Omega_1}\sp{\star}, D_{\Omega_2}, D_{\Omega_3})=$  $(1, 1, 1)$.
-
-The noise susceptibility was tested by pointwise adding a uniform distributed noise to the observations.
-The noise term was constructed using the random library in numpy and adjusted so that the noise range was $\lbrace -n_{amp} , n_{amp} \rbrace $, with $n_{amp}$ denoted as noise amplitude.
+\begin{figure}
+\centering
+\includegraphics[scale=0.4]{noise-12.png}  
+\caption{The upper row shows the manufactured observation, A) Shows the manufactured observation at time-point 24 with no noise added.
+B) Shows the manufactured observation after 12 hours with noise amplitude of 0.15.
+C) Shows the manufactures observation after 12 hours with noise amplitude of 0.3.
+The lower row shows the results with optimized parameter obtained with $\alpha=0.0001$, $\beta=1.0$ and $k=20$.
+D) Shows the resulting state given the observation in A.
+E)  Shows the resulting state given the observation in B .F) Shows the resulting state given the observation in C.
+}
+\label{12hourswithnoise}
+\end{figure}
 

### 2019-07-05 tex/rev1/paper.tex
update

@@
 
-\textbf{}
+\textbf{MRI data.}
+
+It can be seen from Fig XX that the boundary conditions is noise. This may be attributed to noise or small errors
+in the segmentation/registration process where voxels close to the boundaries between the brain and CSF are miss-aligned
+by the sub-voxel segementation procedure. In particular, the surfaces can cut a voxel at any plane, not only the planes
+through the voxel vertices. We chose three approaches to handle this problem. \kam{Lars: kan du utbrodere litt her? 
+Jeg synes vi skal beholde også Fig 10 fra tidligere.  }
 
@@
 In fact, for  $\alpha \in (10^{-6}, 10^{-2}$ and $\beta\in(10^{-6}, 10^{-2})$ the error in the diffusion coefficients in CSF was less than 23\% and less than 9.7\% in grey and white matter.
-\kam{Lars: skriv om resten av eksperimentene}
+Because of the much larger
+error in the CSF compartment, we decided to re-mesh with a focus on the grey and white. \kam{Lars: skriv om resten av eksperimentene. Fig 6 og 7 bor med i Suppl}
 
@@
 The upper row shows the observations with following preprocessing left to right: Raw observations, projection of CSF value onto the boundary, Gaussian smoothing.
-The middle row shows the corresponding states with the regularization parameters $\alpha , \beta \gamma = (10\sp{-6},1.0 ,1.0$).
-The bottom row shows the corresponding states with the regularization parameters $\alpha , \beta \gamma = (10\sp{-6},100.0 ,100.$).
+The middle row shows the corresponding states with the regularization parameters $\alpha , \beta \gamma = (10\sp{-6},1.0 ,1.0)$.
+The bottom row shows the corresponding states with the regularization parameters $\alpha , \beta \gamma = (10\sp{-6},100.0 ,100.)$.
 }

### 2019-07-17 tex/rev1/paper.tex
update
updates

--- 2019-07-04 tex/rev1/paper.tex
@@
 \newcommand{\lars}[1]{\textcolor{magenta}{#1}}
+\def\mm2s{mm$\sp{2}$/s}
 
@@
 
-The properties of the extracellular diffusion are well-known due to seminal work of Nicholson and colleagues, see  
-~\cite{sykova2008diffusion} for an overview, and is fundamental to for  diffusion tensor imaging (DTI). 
+The properties of the extracellular diffusion are well-known due to seminal work of Nicholson and colleagues, see~\cite{sykova2008diffusion} for an overview, and is fundamental to for  diffusion tensor imaging (DTI).
 It has been shown that diffusion coefficients in young and healthy subjects in white matter is around $0.7-0.9\times 10^{-3} \mathrm{mm\sp{2}/s}$ \citet{Helenius194},
@@
 the complete domain.
+
+There are really three questions that we want to answer.  
+\begin{itemize}
+\item Is the brain-wide distribution indicative of faster than diffusion transport? 
+\item Is PDE constrained opt. a feasible approach (in terms of accuracy etc.)
+\item Are the data of sufficient quality? 
+\end{itemize}
+
 %Hence, the challenges faced from a mathematical point of view 
@@
 \begin{aligned}
-\frac{\partial u}{\partial t} &= \nabla \cdot  D \nabla u && \text{in} \qquad \Omega \times \left\lbrace 0 , T \right)  \\
+\frac{\partial u}{\partial t} &=  \nabla\sp{2} u && \text{in} \qquad \Omega \times \left\lbrace 0 , T \right)  \\
 u&=g && \text{on} \qquad \partial\Omega_1  \times \left\lbrace 0 , T \right) 
@@
 The mesh construction was patient-specific and used the MRI of a patient diagnosed with idiopathic normal pressure hydrocephalus (iNPH).
-The software Freesurfer was used to segment and create the polyhedral surfaces of the white and grey matter.
+The software Freesurfer was used to segment and create the polyhedral surfaces of the white and cortical grey matter.
 Then the T2 weighted MRI \cite{ringstad2018brain} was used to segment the CSF compartment surrounding the cerebral and the lateral ventricles.
@@
 \section{Numerical Experiments}
-
 The process of estimating the diffusion coefficients in terms of the PDE constrained optimization problem \eqref{Eq::PDE} is complicated as appropriate parameters, i.e.
@@
 
-\textbf{Verification of code and the identification of suitable parameters in the case of a manufactored solution.}
+\textbf{Manufactored solution.}
+In order to verify our code and assess the range of parameters suitable for simulation we performed a series of 
+simulations with regularization parameters, discretization parameters and noise levels against a known manufactured solution. A total of 141 numerical experiments
+where conducted. The details of the numerical tests can be found in the Supplementary \ref{sup:manu}.
 
-In order to verify our code and assess the range of parameters suitable for simulation we performed a series of 
-simulations with regularization parameters, discretization parameters and noise levels.
+\textbf{MRI data.}
+It can be seen from Figure ~\ref{SAS} that the boundary condition contains high frequent noise.
+This may be attributed to noise and small errors in sampling the MRI-data onto the mesh.
+The sampling error can be caused by miss-alignment between different observations, and by inaccuracy of sampling discontinuous voxel data.
+In more detail, the boundary surface is constructed by smoothing voxels to avoid sharp edges, this can cause the boundary vertices to correspond to voxels outside the select range of data.
+Therefore, we investigated three approaches to minimize the sampling error :
+\begin{itemize}
+\item gradient regularization 
+\item projection onto the boundary surface
+\item Gaussian smoothing 
+\end{itemize}
 
-\textbf{}
+The implementation of the gradient regularization required that the boundary was decomposed to avoid the boundary values being continuous over different subdomains.
+We decomposed the boundary as seen in Figure~\ref{markedboundaryvalues}, with the red and blue boundary adjacent to the CSF.
+We defined the red boundary $\partial \Omega_r$ and the blue boundary $\partial \Omega_b$ as Dirichlet boundaries, while the green and yellow were Neumann boundaries.
+The regularization parameter $\gamma$ was added to the functional
+\begin{equation}
+\min_{D,g} \quad \sum\limits_{i=1}\sp{n} \int\limits_{\Omega} |u(t_i) - u_{obs}(t_i)|\sp{2} \mathrm{d}\Omega + \int\limits_{0}\sp{T} \int\limits_{\partial \Omega_{rb}} \left( \frac{\alpha}{2} | g |\sp{2} + \frac{\beta}{2} \left| \frac{\partial g}{\partial t} \right|\sp{2}  + \frac{\gamma}{2}| \nabla g |\sp{2}  \right) \mathrm{d}\Omega \mathrm{d}t
+\end{equation}
+We initially tested gradient regularization with the same parameter $\gamma$ on both boundaries, but the different distribution of tracers on the boundaries made it difficult to find an adequate value.
+It was observed that the concentration in the lateral ventricles were more uniform than that in the SAS, so we defined $\gamma$ as
+\begin{equation}
+\gamma = \begin{cases}
+0.01\tilde{\gamma}  \in &\partial \Omega_{b} \\ 
+\tilde{\gamma} \qquad \in  &\partial \Omega_{r}
+\end{cases}  
+\end{equation} 
+with $\tilde{\gamma}$ as the referenced, i.e. mentioned in the text, regularization parameter.
+The projection of values was implemented by taking the average of the adjacent CSF voxels to the boundary vertices on $\Omega_b$ and $\Omega_r$.
+We used the Gaussian smoothing found in the python-module scipy~\cite{jones2001scipy}, and applied the smoothing to the MRI-data.
+%The projection and smoothing approach changes the observations, while the gradient regularization adds additional term to the functional.
+Therefore a dual method can also be considered,
+%It can be seen from Fig XX that the boundary conditions is noise. This may be attributed to noise or small errors
+%in the segmentation/registration process where voxels close to the boundaries between the brain and CSF are miss-aligned
+%by the sub-voxel segementation procedure. In particular, the surfaces can cut a voxel at any plane, not only the planes
+%through the voxel vertices. We chose three approaches to handle this problem. \kam{Lars: kan du utbrodere litt her? 
+%Jeg synes vi skal beholde også Fig 10 fra tidligere.  }
 
 \section{Results}
-\subsection{A Real case}
+
+\subsection{Estimation of diffusion coefficients with a manufactured solution.} 
+We first ran a series of tests of different $\alpha$ and $\beta$ for the manufactured solutions where we assumed observations every 2.4 hours
+over the course of 24 hours. It was found that for $\alpha \in (10^{-6}, 10^{-2})$ and $\beta\in(10^{-6}, 10^2)$, the error in 
+the diffusion coefficients of both CSF, grey and white matter was less than 7\%. Furthermore,  
+$\alpha \in (10^{-6}, 10^{-2})$ and $\beta\in(10^{-6}, 10^{-2})$ gave errors of less than 1\%. Second, the robustness with respect noise
+was investigated. The noise-amplitude was set to 0.3 which equals the initial condition of the manufactured solution
+and 23\% of the manufactured solution at its max.
+The method was found robust with respect to the noise, as illustrated in the Supplementary Fig~\ref{12hourswithnoise}.
+In fact, for  $\alpha \in (10^{-6}, 10^{-2}$ and $\beta\in(10^{-6}, 10^{-2})$ the error in the diffusion coefficients in CSF was less than 23\% and less than 9.7\% in grey and white matter.
+Because of the much larger
+error in the CSF compartment, we decided to re-mesh with a focus on the grey and white.
+
+The convergence was monitored and shown in Figure~\ref{convergence}, and we can see the different regularization parameters have similar convergence for the diffusion coefficients. 
+We had limited number of MRI observations available, so we also performed tests with variation in the number of time-steps and observations, which are documented in the Supplementary.
+These test used the same setup and parameters as the initial tests, and we analyzed the variation of number of time-steps and observations separately.
+We selected the number of time-steps to 10 and 40, and the number of observations to be 5 and 20.
+We can see that in  Figure~\ref{boundarycontrol} an increase in the number of time-steps causes oscillations for $\alpha\gg\beta$.
+The test of 5 observations gave similar oscillation, which suggests that high ratios between time-steps and observations contributes to oscillations.
+This can be counteracted by selecting high values temporal regularization $\beta$ to enforce a smooth curve.
+
+% For instance, as seen by the the pink line for $\alpha=1.0$ and $\beta=0.0001$ the peaks corresponds to a observation.
+%These oscillations occurs due to the spacial regularization $\alpha$, which minimize the value of $g$ between observation times.
+
+%\subsection{Estimation of diffusion coefficients with a manufactured solution.}
+
+\kam{Lars: skriv om resten av eksperimentene. Fig 6 og 7 bor med i Suppl}
+
+\subsection{Estimation of the diffusion coefficients from the MRI data}
 
 \subsubsection{Results obtained when using real observations}
-The MRI data consisted of the observations at times $t_i$ distributed in the 48 hours time frame with the time $t_i=0.00$ as the first observation 1-2 hours after the contrast was injected.
-There was no significant visible change in the contrast between the observations the first 2 hours, which prompted the use of the following observation times listed in Table ??.
+The MRI data consisted of the observations at times $t_i$ distributed in the 48 hours time frame with the time $t_i=0.00$ \lars{zero?} as the first observation 1-2 hours after the contrast was injected.
+There was no significant visible change in the contrast between the observations the first 2 hours, therefore we used observation times listed in Table ??.
 
-The estimation of contrast concentration proved difficult in the CSF compartment.
-Therefore the 2 domain mesh, shown in Figure~\ref{Fig::Mesh} was used in the computation.
+The estimation of contrast concentration proved difficult in the CSF compartment. Therefore the 2 domain mesh, shown in Figure~\ref{Fig::Mesh} was used in the computation.
+
 The boundary control was set to the external boundary of both domains, and the subscript in $D_{\Omega_{GM}}$ and $D_{\Omega_{WM}}$ denotes grey and white matter diffusion coefficients.
@@
 
-\subsubsection{Comparison with results obtained from DTI analysis}
+\subsubsection{Comparison with data obtained from DTI analysis}
 The median diffusion coefficient in the DTI was estimated to be 
@@
 in grey matter.
-This corresponds to a tortuosity of $1.85$ and $1.73$, given that the self-diffusivity of water has been estimated to be around $3.0\times 10\sp{-3}\mathrm{mm\sp{2}/s}$ at $37\sp{o}C$.
-The reference value $3.8\times 10\sp{-4} \mathrm{mm\sp{2}/s}$ for Gd-DPTA then gives an estimate for the apparent diffusion coefficient in the grey and white matter to  be $ 1.26\times 10\sp{-4}\mathrm{mm\sp{2}/s}$ and $1.10\times 10\sp{-4} \mathrm{mm\sp{2}/s}$ respectively.
+This corresponds to a tortuosity of $1.85$ and $1.73$ given that the self-diffusivity of water has been reported/estimated to be around $3.0\times 10\sp{-3}\mathrm{mm\sp{2}/s}$ at $37\sp{o}C$.
+We estimated the diffusion coefficient of $3.8\times 10\sp{-4} \mathrm{mm\sp{2}/s}$ for Gd-DPTA, which gives an estimate for the apparent diffusion coefficient in the grey and white matter to be $ 1.3\times 10\sp{-4}\mathrm{mm\sp{2}/s}$ and $1.1\times 10\sp{-4}$ \mm2s respectively.
 This estimation assumes that the tortuosity is independent for molecules with mass lower than 1kDa.
 
-%The oscillation in Figure~\ref{boundarycontrol} showed a large discrepancy in the states between observations.
 The sparsity of the observations compared to the number of time steps can cause the boundary function $g$ to fluctuate between observations, see Appendix.
@@
 It can be observed that the upper right row displays a discrepancy, which likely due to inadequate regularization parameters.
-Furthermore, we can see that for $\alpha=1.0\times 10\sp{-2}$ there is a clear discrepancy in the diffusion coefficients compared to other values of $\alpha$.
+
+In Table~\ref{Tab::Real-data}, we can see that for $\alpha=1.0\times 10\sp{-2}$ there is a clear discrepancy in the diffusion coefficients compared to other values of $\alpha$.
 Excluding the values with $\alpha=1.0\times 10\sp{-2}$ gives an average of $ 0.65 \mathrm{mm\sp{2}/h}$ in grey matter and $ 0.8 \mathrm{mm\sp{2}/h}$ in and white matter.
@@
 
-In Figure~\ref{Fig::realdata}, it can be seen that there were regions with negligible amount of contrast and vice versa.
-The regions with above average amount of contrast corresponds with high diffusivity regions in Figure~\ref{figuredti}.
-This suggests that the computed diffusion coefficients corresponds to these values.
-The ADC value in the high diffusivity regions are approximately  $1.4\times 10\sp{-3} \mathrm{mm\sp{2}/s}$, which corresponds to estimated diffusion coefficient of value $1.5\time 10\sp{-3} \mathrm{mm\sp{2}/s}$.
-This gives a difference of $ 46 \%$ compared to the computed values.
+\lars{ Kent enig?: no concentration change will weight all values of diffusion coefficient equally} 
+The estimation based on DTI used uniform weighting of the voxels, but this is not the case for the optimization, which used concentration difference between observations to find the optimal diffusion coefficient.
+This means that static regions in the observations will be weighted less than regions with high concentrations changes.
+In Figure~\ref{Fig::realdata}, we see regions with negligible changes of contrast and vice versa.
+The regions with above average amount of contrast correlates with high diffusivity regions in Figure~\ref{figuredti}.
+This suggests that the computed diffusion coefficients should be closer to these values.
+So we investigated the upper bound of ADC value at approximately $1.4\times 10\sp{-3} \mathrm{mm\sp{2}/s}$, which corresponds to estimated diffusion coefficient of value $1.5\times 10\sp{-3} \mathrm{mm\sp{2}/s}$, which gives a difference of 46\% compared to the computed values.
 
@@
 \hline
-& & \\
+
 Number of timesteps &  k	 & 24, 48	\\
-& & \\
+
 \hline
-& & \\
-Observational time points  & $\tau$ &  $\lbrace 0.00,2.0, 6 , 24, 48 \rbrace$	 \\
-& & \\
+
+Observational time points  & $\tau$ &  $\lbrace 0.0 ,2.0 , 6.0 , 24.0, 48.0 \rbrace$	 \\
+
 \hline
-& & \\
+
 Timestep & $dt$	 	   &	  1, 2 $\mathrm{hours}$	\\
-& & \\
+
 \hline
-& & \\
+
 Spacial Regularization & $\alpha$	   &	  $\lbrace 1.0\times10\sp{-6}, 1.0\rbrace$\\
-& & \\
+
 \hline
-& & \\
+
 Time Regularization   & $\beta$	   &	 $\lbrace 1.0\times10\sp{-6}, 100.0\rbrace$	\\
-& & \\
+
 \hline
 \end{tabular}
-\caption{Forslag}
+\caption{The table shows an overview of the parameters used in case of boundary constrained optimization with MRI data. }
 \label{model-params-overview}
@@
 \hline
-   & Estimated & Computed average\\
+& & \\[-2ex]
+ & Estimated [$\mathrm{mm\sp{2}/s}$]& Computed average [$\mathrm{mm\sp{2}/s}$]\\[1ex]
 \hline
@@
 \end{tabular}
-\caption{Forslag}
+\caption{The table displays the DTI estimated and the computed average diffusion coefficients in gray and white matter.}
 \label{Tablesummerized}
@@
 
+%The MRI observations describes an influx of tracer into an empty compartment filled with an porous medium. In the static state, diffusion will be dominant 
+\lars{Kent: artikkel av sharp,carara og bryn} 
+Recently,   \cite{sharp2019dispersion} (Enhancement is 5.8 times that of molecular diffusion)
+
+\lars{ Questions:
+The fluctuations caused by shear-augmented dispersion is not detected by the DTI?  (why? is it?) }
+
 \section{Insert correctly}
@@
 
-The implementation of the gradient regularization required that the boundary was decomposed to avoid the boundary values being continuous in different subdomains.
+The implementation of the gradient regularization required that the boundary was decomposed to avoid the boundary values being continuous over different subdomains.
 We decomposed the boundary as seen in Figure ~\ref{markedboundaryvalues}, with the red and blue boundary next to the CSF.
@@
 \begin{equation}
-\min_{D,g} \quad \sum\limits_{i=1}\sp{n} \int\limits_{\Omega} |u(t_i) - u_{obs}(t_i)|\sp{2} \mathrm{d}\Omega + \int\limits_{0}\sp{T} \int\limits_{\partial \Omega_{rb}} \left( \frac{\alpha}{2} | g |\sp{2} + \frac{\beta}{2} \left| \frac{\partial g}{\partial t} \right|\sp{2}  \frac{\gamma}{2}| \nabla g  \right) \mathrm{d}\Omega \mathrm{d}t
+\min_{D,g} \quad \sum\limits_{i=1}\sp{n} \int\limits_{\Omega} |u(t_i) - u_{obs}(t_i)|\sp{2} \mathrm{d}\Omega + \int\limits_{0}\sp{T} \int\limits_{\partial \Omega_{rb}} \left( \frac{\alpha}{2} | g |\sp{2} + \frac{\beta}{2} \left| \frac{\partial g}{\partial t} \right|\sp{2}  + \frac{\gamma}{2}| \nabla g |\sp{2}  \right) \mathrm{d}\Omega \mathrm{d}t
 \end{equation}
@@
 \end{equation} 
-with $\tilde{\gamma}$ as the referenced(mentioned in the text) regularization parameter.
+with $\tilde{\gamma}$ as the referenced, i.e. mentioned in the text, regularization parameter.
 

### 2019-07-17 tex/rev1/supplementarynew.tex
update
updates

@@
 
-\section{
+\begin{figure}
+\centering
+\includegraphics[scale=0.21]{../boundary_control.png}  
+\caption{ Displays plots over time for a selection of points at the boundary of $\Omega_1$ with different regularization parameters and number of timesteps $k$.
+The left panel shows the legend for the plot over time, together with the selection of points.
+The middle panel shows the average boundary value $g$ for different regularization parameter with $k=10$.
+The right panel shows the average boundary value $g$ for different regularization parameter with $k=40$.
+}
+\label{boundarycontrol}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[scale=0.18]{../Convergence-plot.png}   
+\caption{Convergence plots of the diffusion coefficients, boundary conditions and functional with respect to different $\alpha$ and $\beta$ values. } 
+\label{convergence}
+\end{figure}

### 2019-07-24 tex/rev1/paper.tex
updates

@@
 \begin{equation}
-\min_{D,g} \quad \sum\limits_{i=1}\sp{n} \int\limits_{\Omega} |u(t_i) - u_{obs}(t_i)|\sp{2} \mathrm{d}\Omega + \int\limits_{0}\sp{T} \int\limits_{\partial \Omega_1} \left( \frac{\alpha}{2} | g |\sp{2} + \frac{\beta}{2} \left| \frac{\partial g}{\partial t} \right|\sp{2} \right) \mathrm{d}\Omega \mathrm{d}t
+\min_{D,g} \quad \sum\limits_{i=1}\sp{n} \int\limits_{\Omega} |u(t_i) - u_{obs}(t_i)|\sp{2} \mathrm{d}\Omega + \int\limits_{0}\sp{T} \int\limits_{\partial \Omega_1} \left( \frac{\alpha}{2} | g |\sp{2} + \frac{\beta}{2} \left| \frac{\partial g}{\partial t} \right|\sp{2} +  \frac{\gamma}{2}| \nabla g |\sp{2} \right) \mathrm{d}\Omega \mathrm{d}t
 \label{EQ::objf}
@@
 The Dirichlet boundary condition is only applied on the outer facing boundary of the CSF domain, $\partial \Omega_1$. Homogeneous Neumann conditions are applied on the remaining boundaries.
-The $\alpha$ and $\beta$ parameters are non-negative regularization parameters 
+The $\alpha$, $\beta$ and $\gamma$ parameters are non-negative regularization parameters 
 and $u_{obs}$ are the observations at time-points $t_i$.
@@
 
-\section{Numerical Experiments}
+%\section{Numerical Experiments}
 The process of estimating the diffusion coefficients in terms of the PDE constrained optimization problem \eqref{Eq::PDE} is complicated as appropriate parameters, i.e.
@@
 We defined the red boundary $\partial \Omega_r$ and the blue boundary $\partial \Omega_b$ as Dirichlet boundaries, while the green and yellow were Neumann boundaries.
-The regularization parameter $\gamma$ was added to the functional
-\begin{equation}
-\min_{D,g} \quad \sum\limits_{i=1}\sp{n} \int\limits_{\Omega} |u(t_i) - u_{obs}(t_i)|\sp{2} \mathrm{d}\Omega + \int\limits_{0}\sp{T} \int\limits_{\partial \Omega_{rb}} \left( \frac{\alpha}{2} | g |\sp{2} + \frac{\beta}{2} \left| \frac{\partial g}{\partial t} \right|\sp{2}  + \frac{\gamma}{2}| \nabla g |\sp{2}  \right) \mathrm{d}\Omega \mathrm{d}t
-\end{equation}
+The regularization parameter $\gamma$ was subsequentally to non-zero in Eq.~\ref{\label{EQ::objf}}.
 We initially tested gradient regularization with the same parameter $\gamma$ on both boundaries, but the different distribution of tracers on the boundaries made it difficult to find an adequate value.
@@
 with $\tilde{\gamma}$ as the referenced, i.e. mentioned in the text, regularization parameter.
-The projection of values was implemented by taking the average of the adjacent CSF voxels to the boundary vertices on $\Omega_b$ and $\Omega_r$.
-We used the Gaussian smoothing found in the python-module scipy~\cite{jones2001scipy}, and applied the smoothing to the MRI-data.
-%The projection and smoothing approach changes the observations, while the gradient regularization adds additional term to the functional.
-Therefore a dual method can also be considered,
+
+The projection method worked by selecting each boundary vertex on $\Omega_b$ and $\Omega_r$, then finding the corresponding voxel using an affine transformation.
+Then for each voxels, we  computed the average of all CSF segmented voxels in a two voxel vicinity.
+The averages was then set to be the observational value for corresponding boundary vertex in the computations.
+
+We used the Gaussian smoothing found in the python-module scipy~\cite{jones2001scipy}, and applied the smoothing to the voxel based MRI-data.
+The smoothing function required that standard deviation of a Gaussian distribution was specified, which was tested in the range 0.3-1.5.
+
+ %The projection and smoothing approach changes the observations, while the gradient regularization adds additional term to the functional. Therefore a dual method can also be considered, 
 %It can be seen from Fig XX that the boundary conditions is noise. This may be attributed to noise or small errors
@@
 \hline
+
+Gradient Regularization   & $\beta$	   &	 $\lbrace 0.0, 100.0\rbrace$	\\ 
 \end{tabular}
@@
 
-\section{Insert correctly}
-(The sampling of) The observations on the boundary between CSF and the brain parenchyma suffered from the poor resolution of the T1-map, which lead to high frequency noise on the boundary.
+%\section{Insert correctly}
+%(The sampling of) The observations on the boundary between CSF and the brain parenchyma suffered from the poor resolution of the T1-map, which lead to high frequency noise on the boundary.
 Therefore we investigates the effect of a gradient regularization parameter, Gaussian smoothing and the projecting the average concentration onto the boundary has ways to reduce the noise.
-
-The implementation of the gradient regularization required that the boundary was decomposed to avoid the boundary values being continuous over different subdomains.
+%
+%The implementation of the gradient regularization required that the boundary was decomposed to avoid the boundary values being continuous over different subdomains.
 We decomposed the boundary as seen in Figure ~\ref{markedboundaryvalues}, with the red and blue boundary next to the CSF.
@@
 The regularization parameter $\gamma$ was added to the functional
-\begin{equation}
-\min_{D,g} \quad \sum\limits_{i=1}\sp{n} \int\limits_{\Omega} |u(t_i) - u_{obs}(t_i)|\sp{2} \mathrm{d}\Omega + \int\limits_{0}\sp{T} \int\limits_{\partial \Omega_{rb}} \left( \frac{\alpha}{2} | g |\sp{2} + \frac{\beta}{2} \left| \frac{\partial g}{\partial t} \right|\sp{2}  + \frac{\gamma}{2}| \nabla g |\sp{2}  \right) \mathrm{d}\Omega \mathrm{d}t
-\end{equation}
-The boundaries $\Omega_r$ and $\Omega_b$ have very different shapes, and using the same regularization parameter can have different effects on the two boundaries.
+%\begin{equation}
+%\min_{D,g} \quad \sum\limits_{i=1}\sp{n} \int\limits_{\Omega} |u(t_i) - u_{obs}(t_i)|\sp{2} \mathrm{d}\Omega + \int\limits_{0}\sp{T} \int\limits_{\partial \Omega_{rb}} \left( \frac{\alpha}{2} | g |\sp{2} + \frac{\beta}{2} \left| \frac{\partial g}{\partial t} \right|\sp{2}  + \frac{\gamma}{2}| \nabla g |\sp{2}  \right) \mathrm{d}\Omega \mathrm{d}t
+%\end{equation}
+%The boundaries $\Omega_r$ and $\Omega_b$ have very different shapes, and using the same regularization parameter can have different effects on the two boundaries.
 Based on the  observations we saw that that the concentration in the lateral ventricles were more uniform than that in the SAS.
 Therefore, we defined $\gamma$ as
-\begin{equation}
-\gamma = \begin{cases}
-0.01\tilde{\gamma}  \in &\partial \Omega_{b} \\ 
-\tilde{\gamma} \qquad \in  &\partial \Omega_{r}
-\end{cases}  
-\end{equation} 
-with $\tilde{\gamma}$ as the referenced, i.e. mentioned in the text, regularization parameter.
-
-The results for the ventricular boundary in Figure ~\ref{VENT} and the SAS boundary in Figure ~\ref{SAS}. The corresponding estimated diffusion coefficient are shown in Figure ??. 
-We see that the gradient regularization has a great effect reducing the noise on the boundaries, but it also changed the computed diffusion coefficients.
-
-The Gaussian smoothing was done with the python module scipy, and the standard deviation examined in the range of 0.3-1.5.
+%\begin{equation}
+%\gamma = \begin{cases}
+%0.01\tilde{\gamma}  \in &\partial \Omega_{b} \\ 
+%\tilde{\gamma} \qquad \in  &\partial \Omega_{r}
+%\end{cases}  
+%\end{equation} 
+%with $\tilde{\gamma}$ as the referenced, i.e. mentioned in the text, regularization parameter.
+%
+%The results for the ventricular boundary in Figure ~\ref{VENT} and the SAS boundary in Figure ~\ref{SAS}. The corresponding estimated diffusion coefficient are shown in Figure ??. 
+%We see that the gradient regularization has a great effect reducing the noise on the boundaries, but it also changed the computed diffusion coefficients.
+%
+%
+%The Gaussian smoothing was done with the python module scipy, and the standard deviation examined in the range of 0.3-1.5.
 We observed that the Gaussian smoothing with a standard deviation of 1.5 increased the computed diffusion coefficient by approximately 200\% compared to raw data.
+%
+%
 

### 2019-07-24 tex/rev1/paper.tex
more updates

@@
 \includegraphics[width=0.95\textwidth]{../Zoom-PatID.png} 
-\caption{Shows the percentage change in T1 signal unit ratios from baseline at different observation times in the slice (marked red in the left panel) used in the subsequent analysis.
+\caption{The image shows the percentage change in T1 signal unit ratios from baseline at different observation times in the slice (marked red in the left panel) used in the subsequent analysis.
 The color bar was restricted to the range $(0,100)$.
@@
 We defined the red boundary $\partial \Omega_r$ and the blue boundary $\partial \Omega_b$ as Dirichlet boundaries, while the green and yellow were Neumann boundaries.
-The regularization parameter $\gamma$ was subsequentally to non-zero in Eq.~\ref{\label{EQ::objf}}.
+The regularization parameter $\gamma$ was subsequently set to be non-zero in Eq.~\ref{EQ::objf}.
 We initially tested gradient regularization with the same parameter $\gamma$ on both boundaries, but the different distribution of tracers on the boundaries made it difficult to find an adequate value.
@@
 The projection method worked by selecting each boundary vertex on $\Omega_b$ and $\Omega_r$, then finding the corresponding voxel using an affine transformation.
-Then for each voxels, we  computed the average of all CSF segmented voxels in a two voxel vicinity.
+Then for each voxels, we  computed the average of all CSF segmented voxels in a three voxel vicinity.
 The averages was then set to be the observational value for corresponding boundary vertex in the computations.
+In order to estimate the CSF concentration, we assumed that the T1 value corresponding to CSF was 3000 ms, which is shown in Fig~\ref{figureF}] in the supplementary.
 
-We used the Gaussian smoothing found in the python-module scipy~\cite{jones2001scipy}, and applied the smoothing to the voxel based MRI-data.
-The smoothing function required that standard deviation of a Gaussian distribution was specified, which was tested in the range 0.3-1.5.
+We used the Gaussian smoothing found in the python-module scipy~\cite{jones2001scipy}, and applied the smoothing to all voxel based MRI observations.
+The smoothing function required that standard deviation of a Gaussian distribution was specified, which was tested in the range 0.3-1.5 mm, with 1.0 mm as length of a voxel.
 
@@
 \subsubsection{Results obtained when using real observations}
-The MRI data consisted of the observations at times $t_i$ distributed in the 48 hours time frame with the time $t_i=0.00$ \lars{zero?} as the first observation 1-2 hours after the contrast was injected.
-There was no significant visible change in the contrast between the observations the first 2 hours, therefore we used observation times listed in Table ??.
+The MRI data consisted of the observations at times $t_i$ distributed in the 48 hours time frame with the time $t_i=0.00$ as the first observation 1-2 hours after the contrast was injected.
+There was no significant visible change in the contrast between the observations the first 2 hours, therefore we used observation times listed in Table\ref{model-params-overview}.
 
-The estimation of contrast concentration proved difficult in the CSF compartment. Therefore the 2 domain mesh, shown in Figure~\ref{Fig::Mesh} was used in the computation.
+%The estimation of contrast concentration proved difficult in the CSF compartment. Therefore the 2 domain mesh, shown in Figure~\ref{Fig::Mesh} was used in the computation.
 
@@
 \lars{Kent: artikkel av sharp,carara og bryn} 
-Recently,   \cite{sharp2019dispersion} (Enhancement is 5.8 times that of molecular diffusion)
+Recently, it was reported in \citet{sharp2019dispersion} that shear-augmented dispersion can contribute to an enhancement upto 5.8 times that of molecular diffusion.
 
-\lars{ Questions:
-The fluctuations caused by shear-augmented dispersion is not detected by the DTI?  (why? is it?) }
+%\lars{ Questions:
+%The fluctuations caused by shear-augmented dispersion is not detected by the DTI?  (why? is it?) }
 

### 2019-07-24 tex/rev1/supplementary.tex
more updates

@@
 \includegraphics[scale=0.18]{../Convergence-plot.png}   
-\caption{Convergence plots of the diffusion coefficients, boundary conditions and functional with respect to different $\alpha$ and $\beta$ values. } 
+\caption{The images shows convergence plots of the diffusion coefficients, boundary conditions and functional with respect to different $\alpha$ and $\beta$ values. } 
 \label{convergence}
@@
 \includegraphics[scale=0.21]{../boundary_control.png}  
-\caption{ Displays plots over time for a selection of points at the boundary of $\Omega_1$ with different regularization parameters and number of timesteps $k$.
+\caption{ The images displays plots over time for a selection of points at the boundary of $\Omega_1$ with different regularization parameters and number of timesteps $k$.
 The left panel shows the legend for the plot over time, together with the selection of points.

### 2019-07-24 tex/rev1/supplementarynew.tex
more updates

@@
 \includegraphics[width=0.70\textwidth]{../T1function.png} 
-\caption{Shows the  function defined in \eqref{scaledmagnetization} where the white region indicates $T_1$ values for white matter, the grey region indicates $T_1$ values for grey matter, the blue region indicates $T_1$ values for CSF.
+\caption{The image shows the function defined in \eqref{scaledmagnetization} where the white region indicates $T_1$ values for white matter, the grey region indicates $T_1$ values for grey matter, the blue region indicates $T_1$ values for CSF.
 }
